### 2024-07-23 RevisedHiddenWeight.tex
Add files via upload

\def\anon{1} %% set to 1 for anonymous submissions, hides acknowledgements and author names
\def\full{1} %% set to 0 for springer proceedings

\ifnum\full=1
\documentclass[11pt]{llncs}

\addtolength{\parskip}{1pt}
\else
\documentclass[10pt, runningheads]{llncs}
\usepackage{times}

\fi

\input{header.tex}

\begin{document}
	\title{Draft: Notes on the revised Hidden weight function}

	\titlerunning{Notes on the revised Hidden weight function}
	\author{
		\mbox{Pierrick M\'eaux}\inst{1}
	}

	\authorrunning{ P. M\'eaux}

	\institute{
	Luxembourg university, Luxembourg\\
		\email{pierrick.meaux@uni.lu}		
	}

	%----------------------------------------------------------------
	\maketitle

\institute{
	University of Luxembourg, Luxembourg\\
	\email{pierrick.meaux@uni.lu}		
}

	\begin{abstract}

	\end{abstract}

\section{Introduction}

\section{Preliminaries}

\subsection{Boolean functions and weightwise considerations}

In this part we recall general concepts on Boolean functions and their weightwise properties we use in this article. 
For a deeper introduction on Boolean functions and their cryptographic parameters we refer to the survey of \eg~\cite{Carlet20} and to~\cite{TOSC:CarMeaRot17} for the weightwise properties, also called properties on the slices.
For $k \in [0,n]$ we denote $\Ekn{k}{n}$ the set $\{x\in \F_2^n \, | \, \w(x)=k  \}$ and call it slice of the Boolean hypercube (of dimension $n$). 
Accordingly, the Boolean hypercube is partitioned into $n+1$ slices where the elements have the same Hamming weight.

\begin{definition}[Boolean Function]\label{def:bool_f}
	A Boolean function $f$ in $n$ variables is a function from $\F_2^n$ to $\F_2$. 
	The set of all Boolean functions in $n$ variables is denoted by $\BN$, and we denote $\BN^*$ the set without the null function.
\end{definition}

To denote when a property or a definition is restricted to a slice we use the subscript $k$. 
For example, for a $n$-variable Boolean function $f$ we denote its support $\supp(f)=\{x\in \F_2^n \, | \, f(x)=1  \}$ and we denote $\suppk{k}(f)$ its support restricted to a slice, that is $\supp(f)\cap \Ekn{k}{n}$.

\begin{definition}[Balancedness]\label{def:balancedness}
	A Boolean function $f\in \BN$ is called balanced if $|\supp(f)|=2^{n-1}=|\supp(f+1)|$.

	For $k\in [0,n]$ the function is said balanced on the slice $k$ if $||\suppk{k}(f)|-|\suppk{k}(f+1)| |\le 1$. In particular when $|\Ekn{k}{n}|$ is even $|\suppk{k}(f)|=|\suppk{k}(f+1)|=|\Ekn{k}{n}|/2$.
\end{definition}

\begin{definition}[Algebraic Normal Form (ANF) and degree]\label{def:anf}
	We call Algebraic Normal Form of a Boolean function $f$ its $n$-variable polynomial representation over $\F_2$ (\textit{i.e.} belonging to $\F_2[x_1,\dots,x_n]/(x_1^2+x_1,\dots,x_n^2+x_n)$):
	\[f(x_1,\dots,x_n)= \sum_{I \subseteq [1,n]} a_I \left( \prod_{i \in I} x_i \right) \]%x_1,\dots,x_n=\sum_{I \subseteq [1,n]} a_I x^I,\]
	where $a_I\in \F_2$. 	
	The (algebraic) degree of $f$, denoted $\degg(f)$ is: \[\degg(f)=\
	\max_{I\subseteq [1,n]}\{ |I|\, | \, a_I=1\}  \text{ if $f$ is not null},0  \text{ otherwise}.\]
\end{definition}

\begin{definition}[Walsh transform and restricted Walsh transform]\label{def:walsh_transform}
	Let $f\in \Bn{n}$ be a Boolean function, its Walsh transform $\wt{f}$ at $a \in \F_2^n$ is defined as:
	\[  \wt{f} (a) := \sum_{x \in \F_2^n} (-1)^{f(x) +  a \cdot x }.\]
	%	The Walsh support is the set $\Wsupp{f}:=\{ a\in \F_2^n\, | \, \wt{f} (a) \neq 0 \}$.
	Let $f\in \Bn{n}$, $S \subset \F_2^n$, its Walsh transform restricted to $S$ at $a \in \F_2^n$ is defined as:
	\[  \wt{f,S} (a) := \sum_{x\in S} (-1)^{f(x)+ax}.\]
	For $S=\Ekn{k}{n}$ we denote $\wt{f,\Ekn{k}{n}} (a)$ by $\wtk{f}{k}(a)$.%, and for $a= 0_{n}$ we denote $\wtk{f}{k}(a)$ as $\wtk{f}{k}(0)$.
\end{definition}

%\begin{definition}[Algebraic Immunity] \label{def:ai}
%	The algebraic immunity of a Boolean function $f\in \Bfn{n}$, denoted as $\AI(f)$, is defined as:
%	\[ \AI(f) = \min_{g \neq 0}\{ \degg(g) \; | \; fg = 0 \; \text{or} \; (f + 1)g = 0 \}{,} \]
%	where $\degg(g)$ is the algebraic degree of $g$.
%	The function $g$ is called an annihilator of $f$ (or $f + 1$). 
%	Additionally we denote $\AN(f) = \min_{g \neq 0}\{ \degg(g) \; | \; fg = 0\}$.
%\end{definition}

\begin{Prop}[Nonlinearity on the slice, adapted from~\cite{TOSC:CarMeaRot17}, Proposition 6]\label{prop:nlk}
	Let $n\in \N^*, k\in [0,n]$, for every $n$-variable Boolean function $f$ over $\Ekn{k}{n}$:
	\[ \NLk{k}(f)=\frac{|\Ekn{k}{n}|}{2} -\frac{\max_{a\in \F_2^n} |\wtk{f}{k}(a)|}{2}  .\]
\end{Prop}

\subsection{Symmetric Functions}

The $n$-variable \emph{Boolean symmetric functions} are those that are constant on each slice $\Ekn{k}{n}$ for $k\in [0,n]$. 
This class has been assiduously studied in the context of cryptography, see \eg \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,CCDS:Meaux21,IEEE:CarMea21}.
In this paper we mainly consider two families of symmetric functions, which are both bases of the symmetric functions:

\begin{definition}[Elementary symmetric functions]
Let $i\in [0,n]$, the elementary symmetric function of degree $i$ in $n$ variables, denoted $\sigma_{i,n}$, is the function which ANF contains all monomials of degree $i$ and no monomials of other degrees. 
\end{definition}
\begin{definition}[Slice indicator functions]
 Let $k\in [0,n]$, the indicator function of the slice of weight $k$ is defined as:
 \[\forall  x\in \mathbb{F}_2^{n}, \quad \phikn{k}{n}(x) = 1 \text{ if and only if } \w(x) = k.\]
\end{definition}
We recall that bent functions are those Boolean functions achieving maximal nonlinearity.

\begin{Prop}[Weightwise restricted Walsh transform and addition of symmetric function (~\cite{INDO:GinMea22}, Proposition $4$)]\label{prop:AddSym}
	Let $n\in \N^*$, $k\in [0,n]$ and $f \in \Bn{n}$, the following holds on $f+\phikn{k}{n}$
	\[\forall a\in \F_2^n, \forall i\in [0,n]\setminus \{k\}, \wtk{f+\phikn{k}{n}}{i}(a)=\wtk{f}{i}(a),\text{ and } \wtk{f+\phikn{k}{n}}{k}(a)=-\wtk{f}{i}(a).\]	
\end{Prop}

\section{Main section}
%\subsection{Restricted Walsh transform of $f$ in a recursive fashion}

We study the function $f$ in an even number of variables $n$ defined as the following:
\[f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=0}^n \phikn{k}{n} x_k.\]

We study the restricted Walsh transform  of $f$ to bound its nonlinearity.

\begin{align*}
\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}\\
&=\sum_{x \in \Ekn{k}{n}} (-1)^{x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}+ ax}\\
&=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ (c)x},
\end{align*}
where $c$ is the $n$-length binary vector such that $c=a+e_k+\sum_{i=n/2+1}^n e_i$ where the $e_i$ denotes the canonical vector with "1" in position $i$.

Accordingly, we can study the restricted Walsh transform of this function by analyzing the one of $\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}$, for all $a$. We introduce the following notations.

\begin{definition}
Let $n\in \N^*$ be an even number, and $a\in \F_2^n$. We denote $d_n$ the function given by: $d_n(x)=\sum_{i \text{ odd}}^n x_i x_{i+1}$, 
and we denote by $\Dnka{n}{k}{a}$:
\[\Dnka{n}{k}{a}= \sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a x}\]
\end{definition}

With these notations we obtain a recursive relation for $\Dnka{n}{k}{a}$, and therefore for $\wtk{f}{k}(a)$, denoting $b=(a_1,\cdots,a_{n-2})$ and $y=(x_1,\cdots,x_{n-2})$:

\begin{align*}
\Dnka{n}{k}{a}&=\sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a x}\\
&=\sum_{x\in \Ekn{k}{n-2}} (-1)^{d_{n-2}(y) +b y}+
\sum_{x\in \Ekn{k-1}{n-2}} (-1)^{d_{n-2}(y) +b y + a_{n-1}}\\
&+\sum_{x\in \Ekn{k-1}{n-2}} (-1)^{d_{n-2}(y) +b y + a_{n}}
+\sum_{x\in \Ekn{k-2}{n-2}} (-1)^{d_{n-2}(y) +b y +1 + a_{n-1}+ a_{n}}\\
&=\Dnka{n}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n}{k-2}{b}.
\end{align*}

Then it gives three cases:
\begin{itemize}
	\item if $a_{n-1}=a_n=0$, then $\Dnka{n}{k}{a}=\Dnka{n}{k}{b}+2\Dnka{n}{k-1}{b}-\Dnka{n}{k-2}{b}$,
	\item if $a_{n-1} \ne a_n$, then $\Dnka{n}{k}{a}=\Dnka{n}{k}{b}+\Dnka{n}{k-2}{b}$,
	\item if $a_{n-1}=a_n=1$, then $\Dnka{n}{k}{a}=\Dnka{n}{k}{b}-2\Dnka{n}{k-1}{b}-\Dnka{n}{k-2}{b}$.
\end{itemize}

In this analysis we considered the different cases depending on the values of $a_{n-1}$ and $a_n$, but the same reasoning applies with any $a_i, a_{i+1}$ where $i$ is odd. 
Thereafter, the value of $\Dnka{n}{k}{a}$ depends only on the number of pairs of $a$ being $(0,0)$, $(1,1)$ or $(0,1)$ or $(1,0)$, and the values $\Dnka{2}{k}{a}$ for $k \in [0,2]$ and $a\in \{ (0,0),(1,1),(0,1)\}$.

The first values of $\Dnka{2}{k}{a}$ are listed in Table~\ref{tab:Dnka}

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		$a$ & $(0,0)$ & $(0,1)$ & $(1,1)$ \\ \hline
		$\Dnka{2}{0}{a}$ &$1$&$1$ & $1$\\ \hline
		$\Dnka{2}{1}{a}$ &$2$& $0$ & $-2$\\ \hline
		$\Dnka{2}{2}{a}$ &$-1$&$1$ & $-1$\\ \hline
	\end{tabular}
	\caption{Values of $\Dnka{2}{k}{a}$}\label{tab:Dnka}
\end{table}

The restricted Walsh transform of $f$ can the be written as \begin{align*}
\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ (c)x}\\
&=\Dnka{n}{k}{d},
\end{align*}
where $d$ is the permutation of $c$ obtained by sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions. Calling $\pi$ this permutation we can write $d=\pi(a)+ \pi(e_k)+ (0,1,0,1,\ldots,0,1)$. 
Accordingly, if $k\le n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2+1$, with one couple of consecutive elements (the first one with an odd index) being $(1,1)$ and all the others $(0,1)$. 
Otherwise,  when $k> n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2-1$, with one couple of consecutive elements (the first one with an odd index) being $(0,0)$ and all the others $(0,1)$.

Denoting by $b$ the vector $\pi(a)+(0,1,0,1,\ldots,0,1)$, we can write the Walsh transform of $f$ in $a$ as:
\[\wt{f}(a)=\sum_{k=0}^n\Dnka{n}{k}{b+\pi(e_k)}.\]

In particular, for $a=0_n$ we can study the balancedness of $f$:
\begin{align*}
\wt{f}(0_n)&=\sum_{k=0}^n\Dnka{n}{k}{(0,1,0,1,\ldots,0,1)+\pi(e_k)}\\
&=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}
\end{align*}
Using the recursive relation we obtain:
\begin{align*}
\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}&= \Dnka{n-2}{k}{(1,1,0,1,\ldots,0,1)} + \Dnka{n-2}{k-2}{(1,1,0,1,\ldots,0,1)} \\
&=\sum_{i=0}^{n/2-1} \binom{n/2-1}{i} \Dnka{2}{k-2i}{(1,1)}\\
&=\binom{n/2-1}{k/2} \Dnka{2}{0}{(1,1)}+ \binom{n/2-1}{(k-1)/2} \Dnka{2}{1}{(1,1)}+ \binom{n/2-1}{k/2-1} \Dnka{2}{2}{(1,1)}\\
&=\binom{n/2-1}{k/2} -2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1}\\
\end{align*}
Similarly, for $\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}$ we get:
\begin{align*}
\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}
%&= \Dnka{n-2}{k}{(0,0,0,1,\ldots,0,1)} + \Dnka{n-2}{k-2}{(0,0,0,1,\ldots,0,1)} \\
&=\sum_{i=0}^{n/2-1} \binom{n/2-1}{i} \Dnka{2}{k-2i}{(0,0)}\\
&=\binom{n/2-1}{k/2} \Dnka{2}{0}{(0,0)}+ \binom{n/2-1}{(k-1)/2} \Dnka{2}{1}{(0,0)}+ \binom{n/2-1}{k/2-1} \Dnka{2}{2}{(0,0)}\\
&=\binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1}\\
\end{align*}

%We can study the balancedness of $f$ using the $\Dnka{n}{k}{a}$ values.
Combining both we obtain:
\begin{align*}
\wt{f}(0_n)&=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}\\
&=\sum_{k=0}^{n/2} \left(\binom{n/2-1}{k/2} -2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1} \right)+ \sum_{k=\frac{n}{2}+1}^{n}   \left(  \binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1} \right)\\
&=\sum_{k=0}^{n}\left( \binom{n/2-1}{k/2} - \binom{n/2-1}{k/2-1}\right) 
+ 2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{n/2-1}{(k-1)/2} - \sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right)\\
&=2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{n/2-1}{(k-1)/2} - \sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right)\\
&=2 \left( \sum_{i=\lceil n/4 \rceil}^{n/2-1} \binom {n/2-1}{i} - \sum_{i=0}^{\lfloor(n-2)/4 \rfloor} \binom{n/2-1}{i}\right).\\
\end{align*}

Then, depending on the parity of $n/2$ we obtain the the value of $\wt{f}(0_n)$ (using that $\binom{n}{k}=\binom{n}{n-k}$):
	\[\wt{f}(0_n)= \left \{
\begin{array}{l l}
0 & \text{ if } n/2 \text{ is even, } \\
-2 \binom{n/2-1}{(n-2)/4} & \text{ if }  n/2 \text{ is odd.}
\end{array}\right.\]

Accordingly, $f$ is balanced when $n=0\mod 4$ and unbalanced when $n=2 \mod 4$.

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifnum\full=0
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{splncs04}
\bibliography{add}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\else
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{alpha}
\bibliography{add}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\fi

\end{document}

### 2024-07-23 hiddenweight.tex
Add files via upload

\def\anon{1} %% set to 1 for anonymous submissions, hides acknowledgements and author names
\def\full{1} %% set to 0 for springer proceedings

\ifnum\full=1
\documentclass[11pt]{llncs}

\addtolength{\parskip}{1pt}
\else
\documentclass[10pt, runningheads]{llncs}
\usepackage{times}
\fi

\input{header.tex}

\begin{document}
	\title{Weightwise (almost) perfectly balanced functions based on total orders}

	\titlerunning{Weightwise (almost) perfectly balanced functions based on total orders}
	\author{
		\mbox{Pierrick M\'eaux}\inst{1}
	}

	\authorrunning{ P. M\'eaux}

	\institute{
	Luxembourg university, Luxembourg\\
		\email{pierrick.meaux@uni.lu}		
	}

	%----------------------------------------------------------------
	\maketitle

\institute{
%	University of Luxembourg, Luxembourg\\
%	\email{pierrick.meaux@uni.lu}		
}

	\begin{abstract}

	\end{abstract}

\section{Introduction}

\subsection{Related works}

WPB constructions:
\cite{TOSC:CarMeaRot17}
\cite{DCC:LiuMes19,CC:TangLiu19,DAM:LiSu20,CC:MesSu21,AMC:ZhangSu21,BFA:MesSuLi21,DAM:GuoSu22,DAM:ZhuSu22,archiv:MPJDL22,DAM:GinMea22,INDO:GinMea22,ACI:ManKuLar22,CC:MSLZ22,eprint:GinMea22c}.

\section{Preliminaries}

For readability we use the notation $+$ instead of 
$\oplus$ to denote the addition in $\F_2$ and $\sum$ instead of $\bigoplus$. 
In addition to classic notations we denote $ [a,b] $ the subset of all integers between $a$ and $b$: $\{a, a+1, \ldots,b\}$. 
For a vector $v\in \F_2^n$ we use $\w(v)$ to denote its Hamming weight $\w(v)=|\{ i \in [1,n] \, | \, v_i=1 \}|$. For two vectors $v$ and $w$ of $\F_2^n$ we denote $\hd(v,w)$ the Hamming distance between $v$ and $w$, that is $\hd(v,w)=\w(v+w)$.

\subsection{Boolean functions and weightwise considerations}

In this part we recall general concepts on Boolean functions and their weightwise properties we use in this article. 
For a deeper introduction on Boolean functions and their cryptographic parameters we refer to the survey of \eg~\cite{Carlet20} and to~\cite{TOSC:CarMeaRot17} for the weightwise properties, also called properties on the slices.
For $k \in [0,n]$ we denote $\Ekn{k}{n}$ the set $\{x\in \F_2^n \, | \, \w(x)=k  \}$ and call it slice of the Boolean hypercube (of dimension $n$). 
Accordingly, the Boolean hypercube is partitioned into $n+1$ slices where the elements have the same Hamming weight.

\begin{definition}[Boolean Function]\label{def:bool_f}
	A Boolean function $f$ in $n$ variables is a function from $\F_2^n$ to $\F_2$. 
	The set of all Boolean functions in $n$ variables is denoted by $\BN$, and we denote $\BN^*$ the set without the null function.
\end{definition}

To denote when a property or a definition is restricted to a slice we use the subscript $k$. 
For example, for a $n$-variable Boolean function $f$ we denote its support $\supp(f)=\{x\in \F_2^n \, | \, f(x)=1  \}$ and we denote $\suppk{k}(f)$ its support restricted to a slice, that is $\supp(f)\cap \Ekn{k}{n}$.

\begin{definition}[Balancedness]\label{def:balancedness}
	A Boolean function $f\in \BN$ is called balanced if $|\supp(f)|=2^{n-1}=|\supp(f+1)|$.

	For $k\in [0,n]$ the function is said balanced on the slice $k$ if $||\suppk{k}(f)|-|\suppk{k}(f+1)| |\le 1$. In particular when $|\Ekn{k}{n}|$ is even $|\suppk{k}(f)|=|\suppk{k}(f+1)|=|\Ekn{k}{n}|/2$.
\end{definition}

\begin{definition}[Weightwise Perfectly Balanced Function (WPB)]\label{def:WPB}
	Let $m\in \N^*$ and $f$ be a Boolean function in $n=2^m$ variables. 
	The function $f$ is called weightwise perfectly balanced (WPB) if, for every $k\in[n-1]$, $f$ is balanced on the slice $k$, that is $\forall k \in [1,n-1], |\suppk{k}(f)|=\binom{n}{k}/2$, and:
	\[f(0,\dots,0)=0,\quad \text{ and } \quad f(1,\dots,1)=1.\]

	The set of WPB functions in $2^m$ variables is denoted $\WPB{m}$.

\end{definition}

\begin{definition}[Weightwise (Almost) Perfectly Balanced Function (WPB and WAPB)]\label{def:WAPB}
	Let $m\in \N^*$ and $f$ be a Boolean function in $n=2^m$ variables. It will be called weightwise perfectly balanced (WPB) if, for every $k\in[1,n-1]$, $f$ is balanced on the slice $k$, that is $\forall k \in [1,n-1], |\suppk{k}(f)|=\binom{n}{k}/2$, and:
	\[f(0,\cdots,0)=0,\quad \text{ and } f(1,\cdots,1)=1.\]	
	The set of WPB functions in $2^m$ variables is denoted $\WPB{m}$.

	When $n$ is not a power of $2$, other weights than $k=0$ and $n$ give slices of odd cardinality, we call $f\in \Bn{n}$ weightwise almost perfectly balanced (WAPB) if: 
	\[|\suppk{k}(f)|= \left \{
	\begin{array}{l l}
	|\Ekn{k}{n}|/2  & \text{ if } |\Ekn{k}{n}| \text{ is even, } \\
	(|\Ekn{k}{n}|\pm 1)/2  & \text{ if }  |\Ekn{k}{n}| \text{ is odd.}
	\end{array}\right.\]
	The set of WAPB functions in $n$ variables is denoted $\WAPB{n}$.		
\end{definition}

\begin{definition}[Walsh transform and restricted Walsh transform]\label{def:walsh_transform}
	Let $f\in \Bn{n}$ be a Boolean function, its Walsh transform $\wt{f}$ at $a \in \F_2^n$ is defined as:
	\[  \wt{f} (a) := \sum_{x \in \F_2^n} (-1)^{f(x) +  a \cdot x }.\]
	%	The Walsh support is the set $\Wsupp{f}:=\{ a\in \F_2^n\, | \, \wt{f} (a) \neq 0 \}$.
	Let $f\in \Bn{n}$, $S \subset \F_2^n$, its Walsh transform restricted to $S$ at $a \in \F_2^n$ is defined as:
	\[  \wt{f,S} (a) := \sum_{x\in S} (-1)^{f(x)+ax}.\]
	For $S=\Ekn{k}{n}$ we denote $\wt{f,\Ekn{k}{n}} (a)$ by $\wtk{f}{k}(a)$, and for $a= 0_{n}$ we denote $\wtk{f}{k}(a)$ as $\wtk{f}{k}(0)$.
\end{definition}

\begin{definition}[Algebraic Normal Form (ANF) and degree]\label{def:anf}
We call Algebraic Normal Form of a Boolean function $f$ its $n$-variable polynomial representation over $\F_2$ (\textit{i.e.} belonging to $\F_2[x_1,\dots,x_n]/(x_1^2+x_1,\dots,x_n^2+x_n)$):
	\[f(x_1,\dots,x_n)= \sum_{I \subseteq [1,n]} a_I \left( \prod_{i \in I} x_i \right) \]%x_1,\dots,x_n=\sum_{I \subseteq [1,n]} a_I x^I,\]
	where $a_I\in \F_2$. 
%The (algebraic) degree of $f$, denoted $\degg(f)$ is: \[\degg(f):=\left\{\begin{array}{l}
%	\max_{I\subseteq [1,n]}\{ |I|\, | \, a_I=1\}  \text{ if $f$ is not null}\\
%	0  \text{ otherwise}.
%	\end{array}\right.\]	
The (algebraic) degree of $f$, denoted $\degg(f)$ is: \[\degg(f)=\
\max_{I\subseteq [1,n]}\{ |I|\, | \, a_I=1\}  \text{ if $f$ is not null},0  \text{ otherwise}.\]
\end{definition}

\begin{definition}[Algebraic Immunity] \label{def:ai}
	The algebraic immunity of a Boolean function $f\in \Bfn{n}$, denoted as $\AI(f)$, is defined as:
	\[ \AI(f) = \min_{g \neq 0}\{ \degg(g) \; | \; fg = 0 \; \text{or} \; (f + 1)g = 0 \}{,} \]
	where $\degg(g)$ is the algebraic degree of $g$.
	The function $g$ is called an annihilator of $f$ (or $f + 1$). 
	Additionally we denote $\AN(f) = \min_{g \neq 0}\{ \degg(g) \; | \; fg = 0\}$.
\end{definition}

\begin{Prop}[Nonlinearity on the slice, adapted from~\cite{TOSC:CarMeaRot17}, Proposition 6]\label{prop:nlk}
	Let $n\in \N^*, k\in [0,n]$, for every $n$-variable Boolean function $f$ over $\Ekn{k}{n}$:
	\[ \NLk{k}(f)=\frac{|\Ekn{k}{n}|}{2} -\frac{\max_{a\in \F_2^n} |\wtk{f}{k}(a)|}{2}  .\]
\end{Prop}

\subsection{Families of WPB functions}

\begin{definition}[TL WPB construction (adapted from~\cite{CC:TangLiu19}, Construction $1$ )]\label{def:TL}
	Let $m \in \N^*$ and $n = 2^m \ge 4$ be an integer. A TL WPB Boolean function $f$ on $n$-variable is such that
	\begin{itemize}
	 \item $h(0_n)=0$ and $f(1_n)=1$ 
	 \item $h(x,y)=0$ if $\w(x)<\w(y)$.
	 \item $h(x,y)=1$ if $\w(x)>\w(y)$.
	 \item the cardinality of $U_i=\supp(f)\cap\set{(x,y)\in\F_2^{2^{m-1}}\times \F_2^{2^{m-1}}\colon \w(x)=\w(y)=j}$ is exactly $\binom{2^{m-1}}{j}^2/2$ for all $0<j<2^{m-1}$.
	\end{itemize}	
	% 	Let $(c_0,\dots,c_k)\in \set{0,1}^{k+1}$ such that $\sum c_j=0$
% 	\[
% 	 c_j=
% 	 \begin{cases}
% 	  0 & |\Ekn{j}{k}|\equiv 0 \pmod 2\\ 
% 	  \pm 1 & |\Ekn{j}{k}|\equiv 1 \pmod 2\\
% 	 \end{cases}
% 	\]
\end{definition}
\begin{remark}
 Despite Definition~\ref{def:TL} may appear quite different respect the original paper, it is equivalent when applying the constrains of our framework.
 Namely, here we consider only the case where $n$ is a power of two. Referring to Construction 1 of~\cite{CC:TangLiu19}, this implies that the coefficient $c_1,\dots,c_{k-1}$ must be zero. Moreover, in~\cite{CC:TangLiu19} $f(0_n)=0$ and $f(1_n)=1$ is not required for weightwise perfectly balancedness, differently from Definition~\ref{def:WPB}. This implies that in our context we can only instantiate their construction with $(-1,0,..,0,1)$ as input sequence, \ie as in Definition~\ref{def:TL}. 
\end{remark}

\begin{Prop}[TL WPB functions properties~\cite{CC:TangLiu19}]\label{Prop:TL}
	Let $m \in \N^*$ and $n=2^m$, a  $n$-variable TL function $h_n$ has optimal algebraic immunity $\AI(h_n)=\frac{n}{2}$.
\end{Prop}

\subsection{Symmetric Functions}

The $n$-variable \emph{Boolean symmetric functions} are those that are constant on each slice $\Ekn{k}{n}$ for $k\in [0,n]$. 
This class has been assiduously studied in the context of cryptography, see \eg \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,CCDS:Meaux21,IEEE:CarMea21}.
%  The set of $n$-variable symmetric functions is denoted $\SYM{n}$.and $|\SYM{n}|=2^{n+1}$. 
In this paper we mainly consider two families of symmetric functions, which are both bases of the symmetric functions:

\begin{definition}[Elementary symmetric functions]
Let $i\in [0,n]$, the elementary symmetric function of degree $i$ in $n$ variables, denoted $\sigma_{i,n}$, is the function which ANF contains all monomials of degree $i$ and no monomials of other degrees. 
\end{definition}
\begin{definition}[Slice indicator functions]
 Let $k\in [0,n]$, the indicator function of the slice of weight $k$ is defined as:
 \[\forall  x\in \mathbb{F}_2^{n}, \quad \phikn{k}{n}(x) = 1 \text{ if and only if } \w(x) = k.\]
\end{definition}
%We recall that bent functions are those Boolean functions achieving maximal nonlinearity.

\begin{Prop}[Nonlinearity of $\sigma_{2,n}$]\label{prop:sigmaTwoBent}
	Let $n\in \N^*$ even, the elementary symmetric function $\sigma_{2,n}=\sum_{1\le i<j\le n}x_ix_j$ is bent, \ie 
	$\NL(\sigma_{2,n})=2^{n-1}-2^{n/2-1}$.
\end{Prop}

\begin{Prop}[Weightwise restricted Walsh transform and addition of symmetric function (~\cite{INDO:GinMea22}, Proposition $4$)]\label{prop:AddSym}
	Let $n\in \N^*$, $k\in [0,n]$ and $f \in \Bn{n}$, the following holds on $f+\phikn{k}{n}$
	\[\forall a\in \F_2^n, \forall i\in [0,n]\setminus \{k\}, \wtk{f+\phikn{k}{n}}{i}(a)=\wtk{f}{i}(a),\text{ and } \wtk{f+\phikn{k}{n}}{k}(a)=-\wtk{f}{i}(a).\]	
\end{Prop}

\subsection{Orders}

\begin{definition}[Order]

A binary relation $\preceq$	on a set $X$ is called partial order if $\preceq$ is reflexive, transitive and antisymmetric. Moreover, $\preceq$ is a total order if for all $a,b\in X$ it holds $a\preceq b$ or $b \preceq a$.

\end{definition}

We give two examples of orders on $n$-length binary string, more examples can be found in \eg ~\cite{FUN:SteWil12} that also considers order on sets of fixed Hamming weight:
\begin{itemize}
	\item Lexicographic, given $a,b \in \F_2^n$ as $a=a_1,\ldots, a_n$ and $b=b_1,\ldots,b_n$, $a\preceq b$ if and only if  $a_i<b_i$ on the first index $i\in [1,n]$ such that $a_i\ne b_i$, or $a=b$.
%\item Gray 
\item Cool~\cite{DM:RukWil09}, a first element of $\F_2^n$ is chosen and a successor rule is used to determine the following element, allowing to generate the $2^n$ elements with no repetition. The successor rule for $a_1,a_2,\ldots,a_n$ is: Let $i$ be the minimum value such that $(a_i,a_{i+1})=(1,0)$ and $i>1$. If $i$ exists, then rotate $i+1$ bits, otherwise flip $a_1$ and then rotate $n$ bits.

\end{itemize}

\subsection{Krawtchouk polynomials}
For some proofs we will use Krawtchouk polynomials and some of their properties, we give the necessary preliminaries here and refer to \eg ~\cite{book:MacSlo78} for more details.

\begin{definition}[Krawtchouk Polynomials]\label{def:Kraw}
	The Krawtchouk polynomial of degree $k$, with $0\leq k\leq n$ is given by: $ \displaystyle \kraw{k}{\ell}{n}=\sum_{j=0}^{k} (-1)^j \binom{\ell}{j} \binom{n-\ell}{k-j}$. 
	%	Krawtchouk polynomials are characterized by the generating series: $ \displaystyle (1+z)^{n-x} (1-z)^x=\sum_{k=0}^\infty \kraw{k}{x}{n} z^k$.
\end{definition}

\begin{Prop}[Krawtchouk polynomials relations]\label{prop:Kr}
	Let $n\in \N^*$ and $k\in [0,n]$, the following hold:
	\begin{itemize}
		\item $\kraw{k}{\ell}{n}$ is the value of the restricted Walsh transform on $\Ekn{k}{n}$ of any $n$ variable linear function $a\cdot \ell$ such that $\w(a)=\ell$.
		%\item $\kraw{k}{n-x}{n}=(-1)^k \kraw{k}{x}{n}$,
		%\item $\kraw{n-k}{x}{n}=(-1)^x \kraw{k}{x}{n}$,
		%	\item if $n$ is even and $k$ is odd, $\kraw{k}{n/2}{n}=0$,
		%\item if $n$ is even, $\kraw{n/2}{1}{n}=0$.
		%	\item $\binom{n}{x}\kraw{k}{x}{n}=\binom{n}{k}\kraw{x}{k}{n}$.
	\end{itemize}	
\end{Prop}

\begin{Prop}[Vandermonde Convolution]\label{prop:Vandermonde}
	Let $a,b,c \in \N$. Then
	\begin{equation*}
	\binom{a+c}{b}=\sum_{j=0}^b\binom{c}{b-j}  \binom{a}{j}.
	\end{equation*}
\end{Prop}

\section{Constructions based on total orders}

\subsection{Recursive construction}

We denote $\prec_m$ an order on $2^m$-length binary strings.

\begin{definition}\label{def:orderWPB}
	Let $m\in \N^*$, and for $i \in [0,m-1]$ $\preceq_i$ be a total order on the set of $2^i$-length binary string.

	Let $f_m$ be the $2^m$ function defined as:
	\begin{itemize}
		\item $f_m(0_{2^m})=0$, $f_m(1_{2^m})=1$,
		\item 	\[f_m(x,y)= \left \{
		\begin{array}{l l}
		f_{m-1}(x) & \text{ if }  x= y, \\
		0   & \text{ if }  x \prec_{m-1} y,\\
		1   & \text{ if }  y \prec_{m-1} x,
		\end{array}
		\right. \]
		where $x,y\in \F_2^{m-1}$.
	\end{itemize}

\end{definition}

\begin{theorem}\label{thm:orderWPB}

	Let $f_m$ defined as in Definition~\ref{def:orderWPB}, $f_m$ is weightwise perfectly balanced.

\end{theorem}
\begin{proof}

We prove it by recursion. 
First, $f_1(x,y)$ takes the value $0$ in $(0,0)$ and $1$ in $(1,1)$ since by definition $f_m(0_{2^m})=0$ and $f_m(1_{2^m})=1$. 
For the two elements $(x,y)\in \F_2^m$ such that $x\ne y$, that is $\Ekn{1}{n}$, it holds $0 \prec_0 1$ or $1 \prec_0 0$, hence $f_1$ takes the value $1$ on exactly one of them. 
Consequently $f_1$ is WPB, which proves the basis of the recursion.

Then, if for $j\in [1,m-1]$ $f_j$ is WPB we show that $f_{j+1}$ is also WPB. We denote $n=2^{j+1}$, $f_{j+1}(x,y)$ takes the value $0$ in $(0_n)$ and $1$ in $(1_n)$ by definition. Then, for any weight $k\in [1,n-1]$ the set $\Ekn{k}{n}$ can be split in the two sets $A=\{(x,y)\in \Ekn{k}{n} \,  | \, x=y\}$ and $B=\{(x,y)\in \Ekn{k}{n} \,  | \, x\ne y\}$. 
On the set $A$, $f_{j+1}(x,y)$ takes the value of $f_{j}(x)$, and since $\{x\in \F_2^{n/2} \, | \, (x,y) \in A\}=\Ekn{k/2}{n/2}$, the weightwise perfect balancedness of $f_{j}$ implies the balancedness of $f_{j+1}$ on $A$. 
Finally, the set $B$ can be split in pairs $(x,y)$ and $(y,x)$ (since all elements of $B$ are such that $x \ne y$). For each pair, either $x \prec_j y$ or $y \prec_j x$ hence $f_{j+1}(x,y)=1+f_{j+1}(y,x)$. Accordingly, $f_{j+1}$ is balanced on each of these pairs, hence on $B$, and therefore on the full slice $\Ekn{k}{n}$.
It allows to conclude the proof by recursion, $f_m$ is WPB.

\end{proof}

\begin{proposition}\label{propo:const1count}
	Let $m\in \N^*$ and, the number $\mathcal{C}_m$ of $2^m$-variable WPB functions from the family of Definition~\ref{def:orderWPB} is:
	\[\mathcal{C}_m=\prod_{i=0}^{m-1} 2^{2^{i}}!.\]

\end{proposition}
\begin{proof}
First, we note that if two functions $f$ and $g$ from the family are defined with a different order for $i$ in $[0,m-1]$ there exist two elements $x$ and $y$ in $\F_2^{2^i}$ such that $x\prec_{f,i} y$ and $y\prec_{g,i} x$ (where the subscript $f$ or $g$ indicate the order used in the definition of $f$ or $g$ respectively). 
Then, by Definition~\ref{def:orderWPB} $f(x,y)=0$ and $g(x,y)=1$, hence $f$ and $g$ are different functions. 
Therefore, the number of different WPB functions from this family if the product over $m$ of the number of total orders over binary strings of length $2^{i-1}$. Since there are $n!$ possible total orders on a set of size $n$, it gives the final result: $\prod_{i=0}^{m-1} 2^{2^{i}}!$.

\end{proof}

\subsection{Construction based on an unique order}

\begin{definition}\label{def:orderWPB2}
	Let $m\in \N^*$, and $\preceq$ be a total order on the set of $2^{m-1}$-length binary string. 
	%We denote $u$ and $v$ the $2^{m-1}$-th and $2^{m-1}+1$-th elements in this order.
	Let $\preceq'$ be a total order on the set of $2^{m-1}$-length binary string such that for all $k\in [1,2^{m-1}-1]$ exactly half of the elements of Hamming weight $k$ are in the smallest half. 
	We denote $u$ the $2^{m-2}$-th element in the order $\preceq'$.

	Let $g_m$ be the $2^m$ function defined as:
	\begin{itemize}
		\item $g_m(0_{2^m})=0$, $g_m(1_{2^m})=1$,
		\item 	\[g_m(x,y)= \left \{
		\begin{array}{l l}
		0   & \text{ if }  x \prec y,\\
		1   & \text{ if }  y \prec x,\\
		0 \text{ if } x\preceq' u, 1 \text{ otherwise } & \text{ if }  x= y, \\
		\end{array}
		\right. \]
		where $x,y\in \F_2^{m-1}$.
	\end{itemize}

\end{definition}

\begin{theorem}\label{thm:orderWPB2}

	Let $f_m$ as defined in Definition~\ref{def:orderWPB2}, $f_m$ is weightwise perfectly balanced.

\end{theorem}
\begin{proof}
We denote $n=2^m$. 
By definition $g_m(0_{2^m})=0$ and $g_m(1_{2^m})=1$, so we focus on the balancedness of $g_m$ on the slices $\Ekn{k}{n}$ for $k\in [1,n-1]$. Each slice $\Ekn{k}{n}$ can be written as $A \cup B$ where $A$ is the set of elements such that $x=y$, that is $A=\{(x,x) \, | \, x \in \F_2^{n/2} \} \cap \Ekn{k}{n}$, and $B$ is the set of elements such that $x\ne y$, that is $B=\{(x,y) \, | \, x,y \in \F_2^{n/2}, x \ne y \}\cap \Ekn{k}{n}$. 
By construction $A \cap B =\emptyset$.

First, we show that $g_m$ is balanced over $A$. 
We remark that $|A|=|\Ekn{k/2}{n/2}|$ and more precisely $\{x\, | \, (x,x) \in A\}=\Ekn{k/2}{n/2}$. 
By definition of $\preceq'$ we have $|\{x \in \Ekn{k/2}{n/2}\, | \, x \preceq' u\}|= |\Ekn{k/2}{n/2}|/2$, hence $g_m$ is balanced on $A$.

Then, we prove the balancedness on $B$. $B$ can be partitioned into set of pairs $(x,y)$ and$ (y,x)$ and since $x \prec y$ or $y \prec x$ since $x\ne y$, $g_m$ is balanced on all the pairs and therefore on all $B$. 
Finally, $g_m$ is balanced on $A \cup B =\Ekn{k}{n}$ for all $k\in [1,n-1]$ which allows to conclude $g_m$ is WPB.
%\pmnote{It does not work without restriction on the "u order"

%if we use a second order where half of the elements of Hamming weight in $[1,n-1]$ are before the first half it is ok.
%}

\end{proof}

\begin{proposition}\label{const2count}
	Let $m\in \N^*$, the number $\mathcal{D}_m$ of $2^m$-variable WPB functions from the family of Definition~\ref{def:orderWPB2} is: \[\mathcal{D}_m=2^{2^{m-1}}!  \times \prod_{k=1}^{2^{m-1}-1} \binom{\binom{2^{m-1}}{k}}{\frac{ 1}{2} \binom{2^{m-1}}{k}}.\]

\end{proposition}
\begin{proof}
First, using the same argument as for Proposition~\ref{propo:const1count}, a different order for $\preceq$ gives a different function. 
Then, two functions $f$ and $g$ with only $\preceq'$ different can still be the same function if and only if for each $k\in [1,n/2-1]$ (where $n=2^m$) the same half of $\Ekn{k}{n/2}$ is in the smallest half. 
Indeed, if for all $k\in [1,n/2-1]$, the sets $\{x \in \Ekn{k}{n/2}\, | \, x\preceq_f' u_f\}$ and $\{x \in \Ekn{k}{n/2}\, | \, x\preceq_g' u_g\}$ are equal then $f(x,x)=g(x,x)$ for all $x\in \F_2^{n/2}$. 
And since we assumed $\preceq_f=\preceq_g$, for all $(x,y)\in \F_2^n \, | \, x\ne y$ we have $f(x,y)=g(x,y)$ therefore $f=g$. 
Conversely, if there exists $k\in [1,n/2-1]$ such that $x\in \Ekn{k}{n}$ satisfies $x\preceq'_f u_f$ and $x \not \preceq'_g u_g$ (without loss of generality) then $f(x,x)=0$ and $g(x,x)=1$, proving that $f \ne g$.

Finally, we derive the number of different functions, combining the number of different total order on binary strings of length $2^{m-1}$ and the number of partitions of $\Ekn{k}{2^{m-1}}$ in two parts of same size:
\[\mathcal{D}_m=2^{2^{m-1}}!  \times \prod_{k=1}^{2^{m-1}-1} \binom{\binom{2^{m-1}}{k}}{\frac{ 1}{2} \binom{2^{m-1}}{k}}.\]

\end{proof}

We study the nonlinearity and algebraic immunity of these families. First, we show a lower bound on the nonlinearity of any function from the two constructions. Then we give a lower bound on the weightwise nonlinearity of the WPB constructions in terms of Krawtchouk polynomials. 
Finally we address the algebraic immunity of the first construction in Section~\ref{sec:concrete}, exhibiting WPB functions with minimal and maximal AI.

\subsection{A nonlinearity lower bound}

\begin{theorem}\label{th:NLbound}
Let $m\in \N^*$, $n=2^m$ and $f$ be a function from the constructions of Definition~\ref{def:orderWPB} or Definition~\ref{def:orderWPB2}, then:
%\[\NL(f)\ge 2^{n-2}+2^{n-3}-2^{n/2-1}.\]
\[\NL(f)\ge 2^{n-2}.\]
\end{theorem}

\begin{proof}
We compute the Walsh transform of $f$. For all $c\in \F_2^n$:
\begin{align*}
\wt{f}(c)&=\sum_{z\in \F_2^n} (-1)^{f(z)+c z}\\
&=\sum_{x \in \F_2^{n/2}} (-1)^{f(x,x)+a x} + \sum_{x,y \in \F_2^{n/2} \times \F_2^{n/2} \atop {x \ne y}} (-1)^{f(x,y)+a x+ by},
\end{align*}
where $(a,b)=c$, that is $a$ denotes the first $n/2$ bits of $c$ and $b$ denotes the second half.

First, we can bound the absolute value of the first term: $|\sum_{x \in \F_2^{n/2}} (-1)^{f(x,x)+a x}|\le 2^{n/2}$. 
Then, we rewrite the second term:
\begin{align*}
A=\sum_{x,y \in \F_2^{n/2} \times \F_2^{n/2} \atop {x \ne y}} (-1)^{f(x,y)+a x+ by}&=   \frac{1}{2} \left( \sum_{x,y \in \F_2^{n/2} \times \F_2^{n/2} \atop {x \ne y}} (-1)^{f(x,y)+a x+ by}+ \sum_{x,y \in \F_2^{n/2} \times \F_2^{n/2} \atop {x \ne y}} (-1)^{f(x,y)+a x+ by}\right)\\
&= \frac{1}{2} \sum_{x,y \in \F_2^{n/2} \times \F_2^{n/2} \atop {x \ne y}} \left((-1)^{f(x,y)+a x+ by} + (-1)^{f(y,x)+a y+ bx} \right)\\
&= \frac{1}{2} \sum_{x,y \in \F_2^{n/2} \times \F_2^{n/2} \atop {x \ne y}} (-1)^{f(x,y)} \left( (-1)^{a x+ by} - (-1)^{a y+ bx} \right).
\end{align*}

Then, to bound $|A|$, we determine the cardinal of the set $S=\{x,y\in \F_2^{n/2} \times \F_2^{n/2}, \, x \ne y, \, | \, (-1)^{ax+by}- (-1)^{ay+bx}=0\}$. The condition $(-1)^{ax+by}- (-1)^{ay+bx}=0$ is equivalent to $ax+by=ay+bx \mod 2$, that is $(a+b)(x+y)=0 \mod 2$. 
First, note that if $a=b$ then $|S|=|\{x,y\in \F_2^{n/2} \times \F_2^{n/2}, \, x \ne y\}|=
%\binom{2^{n/2}}{2}=2^{n/2-1} (2^{n/2}-1)$. Hence we focus on the case $d=a+b\ne 0_{n/2}$. 
2^{n/2} \cdot (2^{n/2}-1)$. Hence we focus on the case $d=a+b\ne 0_{n/2}$.

The addition by a constant $y\in \F_2^{\ell}$, $\psi_y$, defined by $\psi_y(x)=x + y$ (for $x\in \F_2^{\ell})$ is a bijection over $ \F_2^{\ell}$. Then, the image of $\psi_y(x)$ for $x\in \F_2^{\ell}\setminus \{y\}$ is $\F_2^{\ell}\setminus \{0_\ell\}$. 
Accordingly, the sum  $(x+y)$ such that $x\in \F_2^\ell, y \in \F_2^\ell\setminus \{x\} $ takes each element of $\F_2^\ell \setminus \{0_\ell\}$ exactly $2^\ell$ times. 
%Taking $x\in \F_2^\ell$ and then $y\in \F_2^\ell \setminus \{x\}$ corresponds to take exactly twice each pair $(x,y)$ such that $x\ne y$ (more precisely, the each pair is obtained as $(x,y)$ and $(y,x)$).
%\pmnote{Verify here why we need count only half the elements}
Since for $d\ne 0_\ell$ we have $|\{x \in \F_2^\ell \, | \, d \cdot x=0\}|=2^{\ell-1}$ and $d \cdot 0_\ell =0$ we obtain 
$|S|= 2^{n/2} (2^{n/2-1}-1)=2^{n-1}-2^{n/2}$. 
It allows to bound $|A|$:
\begin{align*}
|A|&=|\frac{1}{2} \sum_{x,y \in \F_2^{n/2} \times \F_2^{n/2} \atop {x \ne y}} (-1)^{f(x,y)} \left( (-1)^{a x+ by} - (-1)^{a y+ bx} \right)|\\
&=\frac{1}{2}| \sum_{x,y \in \F_2^{n/2} \times \F_2^{n/2} \atop {x \ne y \text{ and } (x,y)\not \in S}} 2(-1)^{f(x,y)+a x+ by} + 
\sum_{x,y \in \F_2^{n/2} \times \F_2^{n/2} \atop {x \ne y \text{ and } (x,y) \in S}} 0|\\
%&\le \frac{1}{2}| 2 \left(\binom{2^{n/2}}{2} - %2^{n-2}+2^{n/2-1}\right) |
%= 2^{n/2-1} (2^{n/2}-1) -2^{n-2} + 2^{n/2-1}
%=2^{n-2}
&\le \frac{1}{2}| 2 \left(2^{n/2}(2^{n/2}-1) - 2^{n-1}+2^{n/2}\right) |
= |2^{n} - 2^{n/2}-2^{n-1} + 2^{n/2}|
=2^{n-1}
\end{align*}

Finally, using the relation between nonlinearity and Walsh transform we obtain:
%\[\NL(f)= 2^{n-1}-\frac{1}{2} \max_{c \in \F_2^n}|\wt{f}(c)|\ge 2^{n-1}-\frac{1}{2} \left(2^{n/2}+ 2^{n-2}\right)=2^{n-2}+2^{n-3}-2^{n/2-1}.\]
\[\NL(f)= 2^{n-1}-\frac{1}{2} \max_{c \in \F_2^n}|\wt{f}(c)|\ge 2^{n-1}-\frac{1}{2} \left(2^{n-1}\right)=2^{n-2}.\]

\end{proof}

\begin{theorem}\label{th:NLkbound}
	Let $m\in \N^*$, $n=2^m$ and $f$ be a function from the constructions of Definition~\ref{def:orderWPB} or Definition~\ref{def:orderWPB2}, then, for all $k\in [0,n]$:
	\[\NLk{k}(f) \ge \frac{1}{4} \binom{n}{k} - \binom{\frac{n}{2}}{\frac{k}{2}} - \frac{1}{2}   \max_{\ell \in [1,n]} |\sum_{t=0}^{k} \kraw{t}{\ell}{\frac{n}{2}} \kraw{k-t}{\ell}{\frac{n}{2}} |.\]
\end{theorem}

\begin{proof}

We compute the restricted Walsh transform of $f$ on $\Ekn{k}{n}$. For all $c\in \F_2^n$:
\begin{align*}
\wtk{f}{k}(c)&=\sum_{z\in \Ekn{k}{n}} (-1)^{f(z)+c z}\\
&=\sum_{x\in \Ekn{k/2}{n/2}} (-1)^{f(x,x)+(a+b)x} + \sum_{(x,y)\in \Ekn{k}{n},\, x \ne y} (-1)^{f(x,y)+ax+by}\\
&=\sum_{x\in \Ekn{k/2}{n/2}} (-1)^{f(x,x)+(a+b)x} + 
\sum_{t=0}^{k} \sum_{x\in \Ekn{t}{n/2}, \,y\in \Ekn{k-t}{n/2}\atop {x \ne y} } (-1)^{f(x,y)+ax+by}\\
&=\sum_{x\in \Ekn{k/2}{n/2}} (-1)^{f(x,x)+(a+b)x} + \frac{1}{2}
\sum_{t=0}^{k} \sum_{x\in \Ekn{t}{n/2}, \,y\in \Ekn{k-t}{n/2}\atop {x \ne y} }  (-1)^{f(x,y)} \left( (-1)^{a x+ by} - (-1)^{a y+ bx} \right)
\end{align*}
where $(a,b)=c$, that is $a$ denotes the first $n/2$ bits of $c$ and $b$ denotes the second half.

Similarly to the proof of Theorem~\ref{th:NLbound}, we are looking for the number of elements $(x,y)$ such that $(-1)^{a x+ by} - (-1)^{a y+ bx} =0$. This is equivalent to the number of elements $(x,y)$ such that $(a+b)(x+y)=0 \mod 2$ where this time $x \in \Ekn{t}{n/2}$ and $y\in \Ekn{k-t}{n/2}$. 
Denoting $a+b$ as $d$ we have that all elements lead to $0$ if $d=0_{n/2}$, for the other values of $d$ we determine it in function of $\ell=\w(d)$:
%\begin{align*}
%|S_d|&=|\{x\in \Ekn{t}{n/2}, y \in \Ekn{k-t}{n/2}\, | \, (x+y)d=0\}|\\
%&=|\{x\in \Ekn{t}{n/2}, y \in \Ekn{k-t}{n/2}\, | \, xd=yd=0\}| +|\{x\in \Ekn{t}{n/2}, y \in \Ekn{k-t}{n/2}\, | \, xd=yd=1\}|
%\\
%&=|\{x\in \Ekn{t}{n/2}\, | \, xd=0\}| \cdot  |\{y\in \Ekn{k-t}{n/2}\, | \, yd=0\}| +|\{x\in \Ekn{t}{n/2}\, | \, xd=1\}|  \cdot |\{y\in \Ekn{k-t}{n/2}\, | \, yd=1\}|
%\\
%&=\frac{1}{2}\left( \binom{n/2}{t} - \kraw{t}{\ell}{\frac{n}{2}} \right)\frac{1}{2}\left( \binom{n/2}{k-t} - \kraw{k-t}{\ell}{\frac{n}{2}} \right)
%+ \frac{1}{2}\left( \binom{n/2}{t} + \kraw{t}{\ell}{\frac{n}{2}} \right)\frac{1}{2}\left( \binom{n/2}{k-t} + \kraw{k-t}{\ell}{\frac{n}{2}} \right)\\
%&=\frac{1}{4} \left(2 \binom{n/2}{t} \binom{n/2}{k-t} + 2 \kraw{t}{\ell}{n/2} \kraw{k-t}{\ell}{n/2}\right)
%\end{align*}
\begin{align*}
|S_d|&=|\{x\in \Ekn{t}{n/2}, y \in \Ekn{k-t}{n/2}\, | \, (x+y)d=0\}|\\
&=|\{x\in \Ekn{t}{n/2}, y \in \Ekn{k-t}{n/2}\, | \, xd=yd=0\}| +|\{x\in \Ekn{t}{n/2}, y \in \Ekn{k-t}{n/2}\, | \, xd=yd=1\}|
\\
&=|\{x\in \Ekn{t}{n/2}\, | \, xd=0\}|   |\{y\in \Ekn{k-t}{n/2}\, | \, yd=0\}| +|\{x\in \Ekn{t}{n/2}\, | \, xd=1\}|   |\{y\in \Ekn{k-t}{n/2}\, | \, yd=1\}|
\end{align*}
Then, we determine $|\{x\in \Ekn{t}{n/2}\, | \, xd=0\}|$ using the definition of Krawtchouk polynomials (Definition~\ref{def:Kraw}): %and Property~\ref{prop:Kr} we have:
\begin{align*}
|\{x\in \Ekn{t}{n/2}\, | \, xd=0\}|&= \sum_{j=0 \atop j \text{ even }}^{t} \binom{\ell}{j} \binom{n/2-\ell}{t-j}\\
&= \frac{1}{2}\left( \sum_{j=0 \atop j \text{ even }}^{t} \binom{\ell}{j} \binom{n/2-\ell}{t-j} + \sum_{j=0}^{t} \binom{\ell}{j} \binom{n/2-\ell}{t-j} - \sum_{j=0 \atop j \text{ odd }}^{t} \binom{\ell}{j} \binom{n/2-\ell}{t-j} \right)\\
&=\frac{1}{2}\left( \kraw{t}{\ell}{n/2} + \sum_{j=0}^{t} \binom{\ell}{j} \binom{n/2-\ell}{t-j} \right)\\
&=\frac{1}{2}\left( \kraw{t}{\ell}{n/2} + \binom{n/2}{t} \right),
\end{align*}
where the last equation comes from the Vandermonde convolution (Property~\ref{prop:Vandermonde}). Using similar formulas for the other sets we obtain:
\begin{align*}
|S_d|&=\frac{1}{4}\left( \binom{\frac{n}{2}}{t} + \kraw{t}{\ell}{\frac{n}{2}} \right)\left( \binom{\frac{n}{2}}{k-t} + \kraw{k-t}{\ell}{\frac{n}{2}} \right)
+ \frac{1}{4}\left( \binom{\frac{n}{2}}{t} - \kraw{t}{\ell}{\frac{n}{2}} \right)\left( \binom{\frac{n}{2}}{k-t} - \kraw{k-t}{\ell}{\frac{n}{2}} \right)\\
&=\frac{1}{4} \left(2 \binom{\frac{n}{2}}{t} \binom{\frac{n}{2}}{k-t} + 2 \kraw{t}{\ell}{\frac{n}{2}} \kraw{k-t}{\ell}{\frac{n}{2}}\right).
\end{align*}

Using the value of $|S_d|$ we can derive an lower bound on $|\wtk{f}{k}(c)|$:
\begin{align*}
|\wtk{f}{k}(c)|&=|\sum_{x\in \Ekn{k/2}{n/2}} (-1)^{f(x,x)+(a+b)x} + \frac{1}{2}
\sum_{t=0}^{k} \sum_{x\in \Ekn{t}{n/2}, \,y\in \Ekn{k-t}{n/2}\atop {x \ne y} }  (-1)^{f(x,y)} \left( (-1)^{a x+ by} - (-1)^{a y+ bx} \right)|\\
&\le \binom{n/2}{k/2} + |\frac{1}{2} 
\sum_{t=0}^{k} \sum_{x\in \Ekn{t}{n/2}, \,y\in \Ekn{k-t}{n/2}\atop {x \ne y} }  (-1)^{f(x,y)} \left( (-1)^{a x+ by} - (-1)^{a y+ bx} \right)|\\
%&\ge \binom{n/2}{k/2} + |\frac{1}{2}
%\sum_{t=0}^{k} \left(\sum_{x\in \Ekn{t}{\frac{n}{2}}, \,y\in \Ekn{k-t}{\frac{n}{2}}\atop {x \ne y, \, (x,y) \in S_d}  }  (-1)^{f(x,y)} \left( (-1)^{a x+ by} - (-1)^{a y+ bx}\right) 
%+  \sum_{x\in \Ekn{t}{\frac{n}{2}}, \,y\in \Ekn{k-t}{\frac{n}{2}}\atop {x \ne y, \, (x,y) \not \in S_d} }  (-1)^{f(x,y)} \left( (-1)^{a x+ by} - (-1)^{a y+ bx} \right) \right)|
&\le \binom{n/2}{k/2} + |\frac{1}{2}
\sum_{t=0}^{k} \left(\sum_{x\in \Ekn{t}{\frac{n}{2}}, \,y\in \Ekn{k-t}{\frac{n}{2}}\atop {x \ne y, \, (x,y) \in S_d}  }  (-1)^{f(x,y)} (0) 
+  \sum_{x\in \Ekn{t}{\frac{n}{2}}, \,y\in \Ekn{k-t}{\frac{n}{2}}\atop {x \ne y, \, (x,y) \not \in S_d} }  2(-1)^{f(x,y)+a x+ by}   \right)|\\
%&\le \binom{\frac{n}{2}}{\frac{k}{2}}+ |\frac{1}{2}\left(
%\sum_{t\in [0,k] \setminus \{k/2\}} 2 \left( \binom{\frac{n}{2}}{t} \binom{\frac{n}{2}}{k-t}  - \frac{1}{2} \binom{\frac{n}{2}}{t} \binom{\frac{n}{2}}{k-t}    -   \kraw{t}{\ell}{\frac{n}{2}} \kraw{k-t}{\ell}{\frac{n}{2}}\right) \right) |
&\le \binom{\frac{n}{2}}{\frac{k}{2}}+ |\frac{1}{2}\left(
\left(\sum_{t=0}^{k} 2 \left( \binom{\frac{n}{2}}{t} \binom{\frac{n}{2}}{k-t}  - \frac{1}{2} \binom{\frac{n}{2}}{t} \binom{\frac{n}{2}}{k-t}    -   \kraw{t}{\ell}{\frac{n}{2}} \kraw{k-t}{\ell}{\frac{n}{2}}\right)  \right) - 2\binom{\frac{n}{2}}{\frac{k}{2}} \right) |\\
& \le 2\binom{\frac{n}{2}}{\frac{k}{2}}+ 
|\sum_{t=0}^{k} \left( \frac{1}{2} \binom{\frac{n}{2}}{t} \binom{\frac{n}{2}}{k-t}    -   \kraw{t}{\ell}{\frac{n}{2}} \kraw{k-t}{\ell}{\frac{n}{2}}\right)|\\
& \le 2\binom{\frac{n}{2}}{\frac{k}{2}}+ \frac{1}{2} \binom{n}{k}+ |\sum_{t=0}^{k} \kraw{t}{\ell}{\frac{n}{2}} \kraw{k-t}{\ell}{\frac{n}{2}}|,
\end{align*}
where the last equation comes from the Vandermonde convolution (Property~\ref{prop:Vandermonde}).

Finally, we can give the bound on the $\NLk{k}$ using the relation with the restricted Walsh transform:
\begin{align*}
\NLk{k}(f)&= \frac{1}{2} \binom{n}{k} - \frac{1}{2}\max_{c \in \F_2^n} |\wtk{f}{k}|\\
&\ge \frac{1}{2} \binom{n}{k} - \frac{1}{2}\max_{\ell \in [1,n]} \left( 2\binom{\frac{n}{2}}{\frac{k}{2}}+ \frac{1}{2} \binom{n}{k}+ |\sum_{t=0}^{k} \kraw{t}{\ell}{\frac{n}{2}} \kraw{k-t}{\ell}{\frac{n}{2}}| \right)\\
&\ge \frac{1}{4} \binom{n}{k} - \binom{\frac{n}{2}}{\frac{k}{2}} - \frac{1}{2}   \max_{\ell \in [1,n]} |\sum_{t=0}^{k} \kraw{t}{\ell}{\frac{n}{2}} \kraw{k-t}{\ell}{\frac{n}{2}} |.
\end{align*}

\end{proof}
\pmnote{re-read the proof}

\pmnote{Verify consistency with Property~\ref{prop:Kr}}

\section{Concrete constructions and parameters}\label{sec:concrete}

\subsection{WPB from popular orders}

We can take different orders to compare the properties reached in practice by the construction of Definition~\ref{def:orderWPB}. For example we will consider the orders lexicographic and cool~\cite{FUN:SteWil12}. 
For these two cases we use the lexicographic order (respectively cool order) to define the orders on the $2^i$-length binary strings for $i\in [1,m]$. We give the properties of the produced WPB functions in $8$ and $16$ variables in Table~\ref{tab:lexcool8} and Table~\ref{tab:lexcool16}.

\pmnote{we observe that...}

The algebraic immunity of the construction from the lexicographic order is the minimal possible for a WPB function in more than $2$ variables (see~\cite{Latin:GinMea23}, Theorem $1$). In the following proposition we show that any WPB function $f$ built from Definition~\ref{def:orderWPB} or Definition~\ref{def:orderWPB2} with the lexicographic order as $\prec_{m-1}$ has AI only $2$.

\begin{proposition}

\end{proposition}

\begin{proof}

\end{proof}

%\pmnote{Other construction, an order on length $2^{m-1}$ elements and a $2$-partition for all slice $\Ekn{k}{2^{m-1}}$. }

\pmnote{definitions, parameters, proofs for lexical order and AI}

\subsection{Weightwise order}

\pmnote{Verify if TL is a subcase,

	verify how many TL functions, compared to order function

	generalize which one can be of optimal AI as TL functions.
}

\pmnote{Order orbits in lexicographic order}

\pmnote{Look at "weightwise order"}

\subsection{orders from a field representation}

\pmnote{definition, then parameters}

\section{Generalizations to WAPB constructions}
\pmnote{Generalize the order idea to WAPB function in $2n$ variables.
}

\section{Conclusion}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifnum\full=0
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{splncs04}
\bibliography{add}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\else
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{alpha}
\bibliography{add}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\fi

\end{document}

### 2024-07-26 RevisedHiddenWeight.tex
Added some results for D_{n,k,a} based on generating functions.

@@
 \begin{definition}
-Let $n\in \N^*$ be an even number, and $a\in \F_2^n$. We denote $d_n$ the function given by: $d_n(x)=\sum_{i \text{ odd}}^n x_i x_{i+1}$, 
+Let $n\in \N$ be an even number, and $a\in \F_2^n$. We denote $d_n$ the function given by: $d_n(x)=\sum_{i \text{ odd}}^n x_i x_{i+1}$, 
 and we denote by $\Dnka{n}{k}{a}$:
@@
 \end{definition}
+The limit case of $n=0$ yields that $\Dnka 0ka=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise.
 
-With these notations we obtain a recursive relation for $\Dnka{n}{k}{a}$, and therefore for $\wtk{f}{k}(a)$, denoting $b=(a_1,\cdots,a_{n-2})$ and $y=(x_1,\cdots,x_{n-2})$:
+With these notations we obtain a recursive relation for $\Dnka{n}{k}{a}$, and therefore for $\wtk{f}{k}(a)$, denoting $b=(a_1,\cdots,a_{n-2})$ and $y=(x_1,\cdots,x_{n-2})$, we get for any even $n\geq 2$:
 
@@
 +\sum_{x\in \Ekn{k-2}{n-2}} (-1)^{d_{n-2}(y) +b y +1 + a_{n-1}+ a_{n}}\\
-&=\Dnka{n}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n}{k-2}{b}.
+&=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.
 \end{align*}
@@
 
+\subsection{Study of $\Dnka nka$ through Generating Functions}
+For $a\in\F_2^n$, denote by $p=p(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(0,0)$, by $q=q(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(1,1)$, and by $r=r(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})\in\{(0,1),(1,0)\}$.
+We then have $p+q+r=n/2$.
+Consider further the integer polynomial $P_a(z)$ given by the following expression:
+\[
+    P_a(z)=(-z^2+2z+1)^{p}\cdot(-z^2-2z+1)^{q}\cdot(z^2+1)^{r}.
+\]
+
+\begin{Prop}\label{prop:generating_fct}
+    It holds that $\sum_{k\in\Z}\Dnka nka z^k= P_a(z)$.
+\end{Prop}
+
+\begin{proof}
+    Proceed by induction on even $n\geq 0$.
+The base case $n=0$ is obvious because for $a\in\F_2^0$, we have $P_a(z)=1$, while $\Dnka 0ka=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise.
+For the inductive step, let $n\geq 2$ be even, and assume that the corresponding formula holds for $n-2$.
+Using the recursive formula for $\Dnka nka$ with the notation $a=(b,a_{n-1},a_n)$, we have:
+    \begin{align*}
+        \begin{split}
+        \sum_{k\in\Z}\Dnka nka z^k&=\sum_{k\in\Z}\Dnka{n-2}kbz^k+\big((-1)^{a_{n-1}}+(-1)^{a_{n}}\big)\sum_{k\in\Z}\Dnka{n-2}{k-1}{b}z^k\\
+        &\quad+(-1)^{1+a_{n-1}+a_n}\sum_{k\in\Z}\Dnka{n-2}{k-2}{b}z^k\\
+        &=P_b(z)+\big((-1)^{a_{n-1}}+(-1)^{a_{n}}\big)zP_b(z)+(-1)^{1+a_{n-1}+a_n}z^2P_b(z)\\
+        &=P_b(z)\cdot\Big(z^2(-1)^{1+a_{n-1}+a_n}+z\big((-1)^{a_{n-1}}+(-1)^{a_{n}}\big)+1\Big)\\
+        &=P_a(z).\qedhere
+        \end{split}
+    \end{align*}
+\end{proof}
+
+We can use this result to express $\Dnka n{n-k}a$  in terms of $\Dnka nka$:
+
+\begin{Prop}\label{prop:symmetry}
+    For every integer $k$, we have:
+    \[
+        \Dnka n{n-k}a=(-1)^{p+q+k}\Dnka nka.
+    \]
+\end{Prop}
+
+\begin{proof}
+    Define the degree $n$ polynomial $Q_a(z)$ in such a way that the coefficient of $z^k$ in $Q_a(z)$ is equal to the coefficient of $z^{n-k}$ in $P_a(z)$. Then we have:
+    \begin{align*}
+        Q_a(z)&=z^nP_a(1/z)\\
+        &=(z^2+2z-1)^p\cdot(z^2-2z-1)^q\cdot(z^2+1)^r\\
+        &=(-1)^{p+q}(-z^2-2z+1)^p\cdot(-z^2+2z+1)^q\cdot(z^2+1)^r\\
+        &=(-1)^{p+q}P_a(-z).
+    \end{align*}
+    Thus the coefficient of $z^k$ in $Q_a(z)$, which is $\Dnka n{n-k}a$, is equal to the coefficient of $z^k$ in $(-1)^{p+q}P_a(-z)$, which is $(-1)^{p+q+k}\Dnka nka$.
+\end{proof}
+
+\begin{Corollary}
+    If $r$ is odd, then for $k=n/2$, we have: $\Dnka n{n/2}a=0.$
+\end{Corollary}
+
+\begin{proof}
+    By Property \ref{prop:symmetry}, we have $\Dnka n{n/2}a=(-1)^{p+q+n/2}\Dnka n{n/2}a=-\Dnka n{n/2}a$ because $p+q+n/2\equiv n/2-p-q\equiv r\equiv 1\bmod 2$.
+\end{proof}
+
+Another immediate case for zero coefficients is the following:
+\begin{Prop}
+    If $p=q$ and $k$ is odd, then $\Dnka nka=0$.
+\end{Prop}
+
+\begin{proof}
+    If $p=q$, we have $P_a(z)=(z^4-6z^2+1)^p(z^2+1)^r$, which can be seen as a polynomial in $z^2$. Thus, the coefficient $\Dnka nka$ of $z^k$ for odd $k$ must be zero in $P_a(z)$.
+\end{proof}
+
+We can also use Property \ref{prop:generating_fct} to obtain $\Dnka nka$ through differentiation:
+\[
+    k!\cdot\Dnka nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}.
+\]
+Using this formula, we can for instance use a computer algebra system to deduce $\Dnka nka$ for small values of $k$, see Table \ref{tab:Dnka_small_k}.
+Note that even though the expression for $\Dnka n3a$ involves a division by $3$, its evaluation at specific values for $(p,q,r)$ will always yield integers.
+Indeed, either $p-q\equiv 0\bmod 3$, or $(p-q)^2\equiv 1\bmod 3$, in which case $2(p-q)^2+7\equiv 0\bmod 3$.
+
+\begin{table}
+	\centering
+	\begin{tabular}{|c|c|}
+		\hline
+		$k$ & $\Dnka nka$\\ \hline
+		$0$&$1$\\ \hline
+        $1$&$2(p-q)$\\ \hline
+        $2$&$2(p-q)^2-3(p+q)+r$\\ \hline
+        $3$&$\frac 23(p-q)\left(2(p-q)^2-9(p+q)+3r+7\right)$\\ \hline
+	\end{tabular}
+	\caption{Values of $\Dnka{n}{k}{a}$ for small $k$}\label{tab:Dnka_small_k}
+\end{table}
+
+Using Property \ref{prop:generating_fct}, we can also deduce some sums involving the $\Dnka nka$:
+
+\begin{Prop}\mbox{}
+    \begin{enumerate}
+        \item The sum and alternating sum over $k$ of the $\Dnka nka$ are, respectively:
+        \[
+            \sum_{k=0}^n\Dnka nka=(-1)^{q}2^{n/2},\quad\sum_{k=0}^n(-1)^k\Dnka nka=(-1)^{p}2^{n/2}.
+        \]
+        \item The sum over the even and the odd $k$ of the the $\Dnka nka$ are, respectively:
+        \[
+            \sum_{k=0}^{n/2}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big),
+        \]
+        \[
+            \sum_{k=0}^{n/2-1}\Dnka n{2k+1}a=2^{n/2-1}\big((-1)^{q}-(-1)^{p}\big).
+        \]
+    \end{enumerate}
+\end{Prop}
+
+\begin{proof}
+    For the sum and the alternating sum, it is enough to compute $P_a(1)$ and $P_a(-1)$, respectively.
+The sum of the $\Dnka nka$ over the even (respectively, odd) $k$ is obtained by adding (respectively, subtracting) these two sums and dividing by $2$.
+\end{proof}
+
 \newpage

### 2024-07-31 RevisedHiddenWeight.tex
Added small remark
Updates from Overleaf

@@
 
+\begin{remark}
     We can also use Property \ref{prop:generating_fct} to obtain $\Dnka nka$ through differentiation:
@@
     \end{table}
+\end{remark}
 
@@
 
+One can also prove the following:
+
+\begin{Prop}
+    For a fixed integer $k\geq 1$ and sufficiently large $n\geq b(k)$, it holds that:
+    \[
+        \max_{a\in\F_2^n}|\Dnka nka|=|\Dnka nk{0_n}|=\left(-\frac12\right)^k\sum_{i=\lceil k/2\rceil}^{n/2}(-4)^i\binom{n/2}{i}\binom{i}{k-i}.
+    \]
+\end{Prop}
+
+\begin{remark}
+    In general, it also appears that the vector $a\in\F_2^n$ for which $|\Dnka nka|$ is maximal always satisfies $r(a)=0$.
+\end{remark}
+
+Also, using the Cauchy estimate on holomorphic functions, we can prove:
+
+\begin{Prop}
+    For any real number $R>0$, we have the following bound:
+    \[
+        |\Dnka nka|\leq\frac{(M_R)^{n/2}}{R^k},
+    \]
+    where $B_R$ is the maximum of $\left|z^2-2z-1\right|$ on the complex disk $|z|=R$. Explicitly, $M_R$ can be expressed as follows:
+    \[
+        M_R=
+        \begin{cases}
+            -R^2+2R+1&\text{if $R\leq\sqrt 2-1$}\\
+            \sqrt 2\left(R^2+1\right)&\text{if $\sqrt 2-1\leq R\leq\sqrt 2+1$}\\
+            R^2+2R-1&\text{if $R\geq\sqrt 2+1$}\\
+        \end{cases}.
+    \]
+\end{Prop}
+
+\begin{remark}
+Here are some interesting choices for $R$:
+\begin{itemize}
+    \item Choosing $R=1/\sqrt 2$ yields that $|\Dnka nka|\leq\left(3/\sqrt 2\right)^{n/2}\cdot \sqrt 2^k$.
+    \item Choosing $R=1/2$ gives $|\Dnka nka|\leq (5\sqrt 2/4)^{n/2}\cdot 2^k$.
+\end{itemize}
+\end{remark}
+
 \newpage

### 2024-08-01 RevisedHiddenWeight.tex
Tighter bounds on |D_{n,k,a}| using Cauchy estimate

@@
     \]
-    where $B_R$ is the maximum of $\left|z^2-2z-1\right|$ on the complex disk $|z|=R$. Explicitly, $M_R$ can be expressed as follows:
+    where $M_R$ is the maximum of $\left|z^2-2z-1\right|$ on the complex disk $|z|=R$. Explicitly, $M_R$ can be expressed as follows:
     \[
@@
         \item Choosing $R=1/2$ gives $|\Dnka nka|\leq (5\sqrt 2/4)^{n/2}\cdot 2^k$.
+        \item Choosing $R=1$ yields $|\Dnka nka|\leq (2\sqrt 2)^{n/2}$. This is particularly useful if $k$ is close to $n/2$.
     \end{itemize}
+\end{remark}
+
+\begin{remark}
+    We can even go ahead and choose $R=R_{n,k}$ in terms of $n$ and $k$, in such a way that the upper bound of $B_{R,n,k}=(M_R)^{n/2}/R^k$ is minimized.
+To do this, consider any $1\leq k\leq n-1$.
+We can actually assume that $k\leq n/2$: if $k>n/2$, replace it by $n-k$ (recall that $|\Dnka nka|=|\Dnka n{n-k}a|$ by Property \ref{prop:symmetry}).
+One can show that $B_{R,n,k}$ is minimal for the following choice of $R=R_{n,k}$:
+    \[
+        R_{n,k}=\begin{cases}
+            \frac{n-2k-\sqrt{2(n-2k)^2-n^2}}{2(n-k)}&\text{if $k\leq\frac{2-\sqrt 2}{4}\cdot n$}\\
+            \sqrt{\frac{k}{n-k}}&\text{if $k\geq\frac{2-\sqrt 2}{4}\cdot n$}
+        \end{cases}.
+    \]
+    Figure \ref{fig:cauchy_estimate} compares for $n=1\,000$ the two upper bounds we have for $|\Dnka nka|$ on a logarithmic scale: the binomial coefficient $\binom nk$ in red, and the bound $B_{R,n,k}$ with the optimally chosen $R=R_{n,k}$ in blue.
+The $x$-axis represents the values for $k$, while the $y$-axis represents the binary logarithm of the two bounds.
+In case $|k-n/2|\leq\sqrt{2}/4\cdot n$, it can be observed that the Cauchy estimate yields particularly good bounds compared to the binomial coefficients.
+In fact, in this case, we get:
+    \[
+        \Dnka nka\leq\left(\frac{\sqrt 2 n}{n-k}\right)^{n/2}\cdot\left(\frac{n-k}{k}\right)^{k/2}.
+    \]
+
+    \begin{figure}
+        \centering
+        \includegraphics[width=7cm]{cauchy_estimate.pdf}
+        \caption{Cauchy estimate in blue vs.\ binomial coefficients in red}
+        \label{fig:cauchy_estimate}
+    \end{figure}
 \end{remark}

### 2024-08-02 RevisedHiddenWeight.tex

@@
 \begin{Prop}
-    If $p=q$ and $k$ is odd, then $\Dnka nka=0$.
+    If $p=q$ and $k$ is odd, then $\Dnka nka=0=\Dnka n{n-k}a$.
 \end{Prop}
@@
 \begin{proof}
-    If $p=q$, we have $P_a(z)=(z^4-6z^2+1)^p(z^2+1)^r$, which can be seen as a polynomial in $z^2$. Thus, the coefficient $\Dnka nka$ of $z^k$ for odd $k$ must be zero in $P_a(z)$.
+    If $p=q$, we have $P_a(z)=(z^4-6z^2+1)^p\cdot(z^2+1)^r$, which can be seen as a polynomial in $z^2$.
+Thus, the coefficient $\Dnka nka$ of $z^k$ for odd $k$ must be zero in $P_a(z)$.
+It follows that also $\Dnka n{n-k}a=0$ by Property \ref{prop:symmetry}.
 \end{proof}
@@
     \end{table}
+\end{remark}
+
+With this, we can get more cases in which $\Dnka nka=0$:
+
+\begin{Prop}\mbox{}
+    \begin{enumerate}
+        \item If $n=16m$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, where $\ell_s=s(s-1)$, then $\Dnka n2a=0=\Dnka n{k-2}a$.
+        \item If $n=16m+2$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, where $\ell_s=\left(6s^2+6s+(-1)^s(2s+1)-1\right)/8$, then $\Dnka n3a=0=\Dnka n{k-3}a$.
+        \item If $n=16m+4$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, where $\ell_s=s^2$, then $\Dnka n2a=0=\Dnka n{k-2}a$.
+        \item If $n=16m+6$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, where $\ell_s=\left(6s^2+6s-(-1)^s(2s+1)+1\right)/8$, then $\Dnka n3a=0=\Dnka n{k-3}a$.
+    \end{enumerate}
+\end{Prop}
+
+\begin{proof}
+    It is enough to use the expressions from Table \ref{tab:Dnka_small_k}, and replace $p$, $q$ and $r$ by their respective values.
+For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$ in the expression $\Dnka n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dnka n2a=0$.
+\end{proof}
+
+\begin{remark}
+    There are still instances where $\Dnka nka=0$ which have not been described by the above. For instance, we have $\Dnka{34}4a=0$ if $\{p,q\}=\{1,2\}$.
 \end{remark}
@@
     \[
-        \Dnka nka\leq\left(\frac{\sqrt 2 n}{n-k}\right)^{n/2}\cdot\left(\frac{n-k}{k}\right)^{k/2}.
+        |\Dnka nka|\leq\left(\frac{\sqrt 2 n}{n-k}\right)^{n/2}\cdot\left(\frac{n-k}{k}\right)^{k/2}.
     \]

### 2024-08-29 RevisedHiddenWeight.tex
Added bound on the sum of the absolute values of the D_{n,k,a}.
Updates from Overleaf

@@
 Denoting by $b$ the vector $\pi(a)+(0,1,0,1,\ldots,0,1)$, we can write the Walsh transform of $f$ in $a$ as:
-\[\wt{f}(a)=\sum_{k=0}^n\Dnka{n}{k}{b+\pi(e_k)}.\]
+\begin{equation}\label{eqn:walsh_from_D}
+    \wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}.
+\end{equation}
 
@@
 \wt{f}(0_n)&=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}\\
-&=\sum_{k=0}^{n/2} \left(\binom{n/2-1}{k/2} -2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1} \right)+ \sum_{k=\frac{n}{2}+1}^{n}   \left(  \binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1} \right)\\
+&=\sum_{k=0}^{n/2} \left(\binom{n/2-1}{k/2} -2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1} \right)\\
+&\qquad+ \sum_{k=\frac{n}{2}+1}^{n}   \left(  \binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1} \right)\\
 &=\sum_{k=0}^{n}\left( \binom{n/2-1}{k/2} - \binom{n/2-1}{k/2-1}\right) 
@@
 
-Then, depending on the parity of $n/2$ we obtain the the value of $\wt{f}(0_n)$ (using that $\binom{n}{k}=\binom{n}{n-k}$):
+Then, depending on the parity of $n/2$ we obtain the value of $\wt{f}(0_n)$ (using that $\binom{n}{k}=\binom{n}{n-k}$):
 	\[\wt{f}(0_n)= \left \{
@@
 
-We can use this result to express $\Dnka n{n-k}a$  in terms of $\Dnka nka$:
+\begin{remark}
+    In particular, since $P_a(z)$ only depends on the triplet $(p,q,r)$, we deduce that also $\Dnka nka$ only depends on the triplet $(p,q,r)$; therefore, it makes sense to introduce the notation $\mathsf D_{n,k}^{p,q,r}=\Dnka nka$, where $a\in\mathbb F_2^n$ is any vector with $(p(a),q(a),r(a))=(p,q,r)$.
+We will make use of this notation later on.
+\end{remark}
 
@@
         \item The sum and alternating sum over $k$ of the $\Dnka nka$ are, respectively:
-        \[
-            \sum_{k=0}^n\Dnka nka=(-1)^{q}2^{n/2},\quad\sum_{k=0}^n(-1)^k\Dnka nka=(-1)^{p}2^{n/2}.
-        \]
+        \begin{gather*}
+            \sum_{k=0}^n\Dnka nka=(-1)^{q}2^{n/2},\\
+            \sum_{k=0}^n(-1)^k\Dnka nka=(-1)^{p}2^{n/2}.
+        \end{gather*}
         \item The sum over the even and the odd $k$ of the the $\Dnka nka$ are, respectively:
-        \[
-            \sum_{k=0}^{n/2}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big),
-        \]
-        \[
+        \begin{gather*}
+            \sum_{k=0}^{n/2}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big),\\
             \sum_{k=0}^{n/2-1}\Dnka n{2k+1}a=2^{n/2-1}\big((-1)^{q}-(-1)^{p}\big).
-        \]
+        \end{gather*}
     \end{enumerate}
@@
     \[
-        |\Dnka nka|\leq\left(\frac{\sqrt 2 n}{n-k}\right)^{n/2}\cdot\left(\frac{n-k}{k}\right)^{k/2}.
+        |\Dnka nka|\leq 2^{n/4}\sqrt{\frac{n^n}{(n-k)^{n-k}\cdot k^k}}.
     \]
-
     \begin{figure}
@@
 
+\begin{Prop}\label{prop:bound_sum_D_nka}
+    For every $1\leq k\leq n$, fix a Boolean vector $a\ui k\in\F_2^n$. Then we have the following bound:
+    \[
+        \sum_{k=1}^n\left|\Dnka nk{a\ui k}\right|\leq n\cdot 2^{3n/4}.
+    \]
+\end{Prop}
+
+\begin{proof}
+    Simply observe that $2^{n/4}\sqrt{\frac{n^n}{(n-k)^{n-k}\cdot k^k}}$ is maximal for $k=n/2$, in which case the expression reduces to $2^{3n/4}$.
+\end{proof}
+
+\subsection{Bounding the Walsh transform of $f$}
+
+From Property \ref{prop:bound_sum_D_nka}, we can in particular deduce that $|\wt f(a)|\leq n\cdot 2^{3n/4}+1$ for every Boolean vector $a\in\F_2^n$.
+This is a very pessimistic bound.
+In this section, we will discuss how a tighter bound on $|\wt f(a)|$ can be obtained in polynomial time in $n$.
+
+This method is based on the identity (\ref{eqn:walsh_from_D}).
+For this, consider a vector $b\in\mathbb F_2^n$; we write $(p,q,r)=(p(b),q(b),r(b))$.
+Also, for $1\leq k\leq n$, let $b_k=b+\pi(e_k)$ and $(p_k,q_k,r_k)=(p(b_k),q(b_k),r(b_k))$.
+Observe that for every $1\leq k\leq n$, we have $(p_k,q_k,r_k)\in\{(p\pm1,q,r\mp 1),(p,q\pm 1,r\mp 1)\}$.
+Furthermore, observe that if $k\leq n/2$ and $(p_k,q_k,r_k)=(p+\alpha,q+\beta,r+\gamma)$ for $\{\alpha,\beta,\gamma\}=\{0,\pm 1\}$ with $\gamma\neq 0$, then we have $(p_{k+n/2},q_{k+n/2},r_{k+n/2})=(p+\alpha',q+\beta',r+\gamma')$ for some $\{\alpha',\beta',\gamma'\}=\{0,\pm 1\}$ with $\gamma'\neq 0$ which only depend on $\alpha$, $\beta$ and $\gamma$.
+Explicitly, we have $(\alpha',\beta',\gamma')=(\alpha,\beta,\gamma)$ if $\gamma=1$ and $(\alpha',\beta',\gamma')=(\beta,\alpha,\gamma)$ if $\gamma=-1$.
+
+In the following discussion, we outline a method to determine an upper bound on $\max_{a\in\F_2^n}\wt f(a)$.
+A similar approach can be applied to find a lower bound on $\min_{a\in\F_2^n}\wt f(a)$, and by utilizing both, we can also obtain an upper bound on $\max_{a\in\F_2^n}|\wt f(a)|$ by making use of the following identity:
+\[
+    \max_{a\in\F_2^n}|\wt f(a)|=\max\Big(\max_{a\in\F_2^n}\wt f(a),-\min_{a\in\F_2^n}\wt f(a)\Big).
+\]
+For each $1\leq k\leq n/2$, select $\{\alpha_k,\beta_k,\gamma_k\}=\{0,\pm 1\}$ with $\gamma_k\neq 0$ such that the following expression is defined and maximized:
+\[
+    B_k^{p,q,r}=\mathsf D_{n,k}^{p+\alpha_k,q+\beta_k,r+\gamma_k}+\mathsf D_{n,k+n/2}^{p+\alpha_k',q+\beta_k',r+\gamma_k'}.
+\]
+This implies that $\Dnka{n}{k}{b_k}+\Dnka{n}{k+n/2}{b_{k+n/2}}\leq B_k^{p,q,r}$ for every $1\leq k\leq n/2$, leading to the conclusion that $\sum_{k=1}^n\Dnka nk{b_k}\leq\sum_{k=1}^{n/2} B_k^{p,q,r}$.
+As a result, we derive the following upper bound:
+\begin{equation}\label{eqn:bound_walsh}
+\max_{a\in\F_2^n}\wt f(a)\leq\max_{p+q+r=n/2}\sum_{k=1}^{n/2} B_k^{p,q,r}.
+\end{equation}
+Under the assumption that the values of $\mathsf{D}_{n,k}^{p,q,r}$ have already been computed for all triplets $(p,q,r)$ satisfying $p+q+r=n/2$, the bound in equation (\ref{eqn:bound_walsh}) can be determined with a computational complexity of $\mathcal{O}(n^3)$.
+This is because there are $\mathcal{O}(n^2)$ possible triplets $(p,q,r)$ that meet the condition $p+q+r=n/2$, and the summation itself can be computed in $\mathcal{O}(n)$.
+
+Consider now the complexity involved in computing the values of $\mathsf{D}_{n,k}^{p,q,r}$ for all $0 \leq k \leq n$ and for all triplets $(p,q,r)$ where $p+q+r=n/2$.
+We claim that this computation has a complexity of $\mathcal{O}(n^3 \log n)$.
+Towards this, according to Property \ref{prop:generating_fct}, it is sufficient to expand the polynomials $(-z^2 + 2z + 1)^p \cdot (-z^2 - 2z + 1)^q \cdot (z^2 + 1)^r$ for all triplets $(p,q,r)$ such that $p+q+r=n/2$.
+
+To achieve this, we first precompute the expanded polynomials $(-z^2 + 2z + 1)^p$ for each $1 \leq p \leq n/2$.
+This can be done recursively using the formula $(-z^2 + 2z + 1)^{p+1} = (-z^2 + 2z + 1) \cdot (-z^2 + 2z + 1)^p$.
+For each $p$, we need to compute the product of two expanded polynomials of degree at most $n/2$, which requires $\mathcal{O}(n \log n)$ computations .
+Performing this for every $p$ results in a total complexity of $\mathcal{O}(n^2 \log n)$.
+The same approach is used to expand the polynomials $(-z^2 - 2z + 1)^q$ and $(z^2 + 1)^r$, resulting in an overall complexity of $\mathcal{O}(n^2 \log n)$ for this precomputational step.
+
+Finally, for each triplet $(p,q,r)$ where $p+q+r=n/2$, we multiply the expanded polynomials $(-z^2 + 2z + 1)^p$, $(-z^2 - 2z + 1)^q$, and $(z^2 + 1)^r$.
+These two multiplications are once more performed in $\mathcal{O}(n \log n)$.
+Given that there are $\mathcal{O}(n^2)$ such triplets $(p,q,r)$, the complexity of this step totals $\mathcal{O}(n^3 \log n)$.
+Therefore, this final step is the primary computational bottleneck, making the overall complexity of the procedure also $\mathcal{O}(n^3 \log n)$.
+
+Table \ref{table:max_walsh_vs_bound} compares $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ to the upper bound $B_n$ we find using the above method.
+Table \ref{table:walsh_bounds} gives all values of this bound $B_n$ for all even $1\leq n\leq 80$.
+As we can see from Figure \ref{fig:walsh_bound}, our bound $B_n$ is exponential in $n$.
+
+\begin{table}
+    \centering
+    \begin{tabular}{|c|c|c|}
+    \hline
+    $n$ & $\max_{a\in\F_2^n}|W_f(a)|$ & $B_n$ \\ \hline
+    $2$  & $2$     & $2$     \\
+    $4$  & $8$     & $8$     \\
+    $6$  & $20$    & $28$    \\
+    $8$  & $52$    & $76$    \\
+    $10$ & $108$   & $212$   \\
+    $12$ & $292$   & $596$   \\
+    $14$ & $700$   & $1\,828$  \\
+    $16$ & $2\,176$  & $5\,196$  \\
+    $18$ & $4\,964$  & $14\,668$  \\
+    $20$ & $14\,032$ & $41\,468$ \\
+    $22$ & $34\,232$ & $118\,544$ \\
+    $24$ & $109\,648$ & $325\,188$ \\ \hline
+    \end{tabular}
+    \caption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ vs.\ our bound $B_n$}
+    \label{table:max_walsh_vs_bound}
+\end{table}
+
+\begin{table}
+    \centering
+    \begin{minipage}{0.19\textwidth}
+        \centering
+        \begin{tabular}{|c|c|}
+            \hline
+            $n$ & $B_n$ \\
+            \hline
+            $2$  & $2.00 \cdot 10^{0}$  \\
+            $4$  & $8.00 \cdot 10^{0}$  \\
+            $6$  & $2.80 \cdot 10^{1}$  \\
+            $8$  & $7.60 \cdot 10^{1}$  \\
+            $10$ & $2.12 \cdot 10^{2}$ \\
+            $12$ & $5.96 \cdot 10^{2}$ \\
+            $14$ & $1.83 \cdot 10^{3}$ \\
+            $16$ & $5.20 \cdot 10^{3}$ \\
+            $18$ & $1.47 \cdot 10^{4}$ \\
+            $20$ & $4.15 \cdot 10^{4}$ \\
+            \hline
+        \end{tabular}
+    \end{minipage}%
+    \begin{minipage}{0.19\textwidth}
+        \centering
+        \begin{tabular}{|c|c|}
+            \hline
+            $n$ & $B_n$ \\
+            \hline
+            $22$ & $1.19 \cdot 10^{5}$ \\
+            $24$ & $3.25 \cdot 10^{5}$ \\
+            $26$ & $9.59 \cdot 10^{5}$ \\
+            $28$ & $2.68 \cdot 10^{6}$ \\
+            $30$ & $7.65 \cdot 10^{6}$ \\
+            $32$ & $2.14 \cdot 10^{7}$ \\
+            $34$ & $6.25 \cdot 10^{7}$ \\
+            $36$ & $1.76 \cdot 10^{8}$ \\
+            $38$ & $5.03 \cdot 10^{8}$ \\
+            $40$ & $1.40 \cdot 10^{9}$ \\
+            \hline
+        \end{tabular}
+    \end{minipage}%
+    \begin{minipage}{0.19\textwidth}
+        \centering
+        \begin{tabular}{|c|c|}
+            \hline
+            $n$ & $B_n$ \\
+            \hline
+            $42$ & $4.01 \cdot 10^{9}$ \\
+            $44$ & $1.12 \cdot 10^{10}$ \\
+            $46$ & $3.21 \cdot 10^{10}$ \\
+            $48$ & $8.91 \cdot 10^{10}$ \\
+            $50$ & $2.56 \cdot 10^{11}$ \\
+            $52$ & $7.12 \cdot 10^{11}$ \\
+            $54$ & $2.05 \cdot 10^{12}$ \\
+            $56$ & $5.73 \cdot 10^{12}$ \\
+            $58$ & $1.65 \cdot 10^{13}$ \\
+            $60$ & $4.59 \cdot 10^{13}$ \\
+            \hline
+        \end{tabular}
+    \end{minipage}%
+    \begin{minipage}{0.19\textwidth}
+        \centering
+        \begin{tabular}{|c|c|}
+            \hline
+            $n$ & $B_n$ \\
+            \hline
+            $62$ & $1.32 \cdot 10^{14}$ \\
+            $64$ & $3.66 \cdot 10^{14}$ \\
+            $66$ & $1.05 \cdot 10^{15}$ \\
+            $68$ & $2.93 \cdot 10^{15}$ \\
+            $70$ & $8.40 \cdot 10^{15}$ \\
+            $72$ & $2.33 \cdot 10^{16}$ \\
+            $74$ & $6.71 \cdot 10^{16}$ \\
+            $76$ & $1.87 \cdot 10^{17}$ \\
+            $78$ & $5.39 \cdot 10^{17}$ \\
+            $80$ & $1.51 \cdot 10^{18}$ \\
+            \hline
+        \end{tabular}
+    \end{minipage}
+    \caption{Values of $B_n$ for various $n$.}
+    \label{table:walsh_bounds}
+\end{table}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=10cm]{walsh_bound}
+    \caption{Our bounds $B_n$ in terms of $n$, on a logarithmic scale}
+    \label{fig:walsh_bound}
+\end{figure}
 \newpage

### 2024-09-23 RevisedHiddenWeight.tex
Minor corrections
def of the generalization

--- 2024-08-01 RevisedHiddenWeight.tex
@@
 	\author{
-		\mbox{Pierrick M\'eaux}\inst{1}
+%		\mbox{Pierrick M\'eaux}\inst{1}
 	}
@@
 	Luxembourg university, Luxembourg\\
-		\email{pierrick.meaux@uni.lu}		
+%		\email{pierrick.meaux@uni.lu}		
 	}
@@
 
+\subsection{Krawtchouk polynomials}
+We use Krawtchouk polynomials and some of their properties to prove one of our results, we give the necessary preliminaries here and refer to \eg ~\cite{book:MacSlo78} for more details.
+
+\begin{definition}[Krawtchouk Polynomials]\label{def:Kraw}
+	The Krawtchouk polynomial of degree $k$, with $0\leq k\leq n$ is given by: $ \displaystyle \kraw{k}{\ell}{n}=\sum_{j=0}^{k} (-1)^j \binom{\ell}{j} \binom{n-\ell}{k-j}$.
+
+	Krawtchouk polynomials are characterized by the generating series: $ \displaystyle (1+z)^{n-x} (1-z)^x=\sum_{k=0}^\infty \kraw{k}{x}{n} z^k$.
+\end{definition}
+
 \section{Main section}
@@
 We study the function $f$ in an even number of variables $n$ defined as the following:
-\[f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=0}^n \phikn{k}{n} x_k.\]
+\[f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k.\]
 
@@
 	Proceed by induction on even $n\geq 0$. 
-The base case $n=0$ is obvious because for $a\in\F_2^0$, we have $P_a(z)=1$, while $\Dnka 0ka=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise.
-For the inductive step, let $n\geq 2$ be even, and assume that the corresponding formula holds for $n-2$.
-Using the recursive formula for $\Dnka nka$ with the notation $a=(b,a_{n-1},a_n)$, we have:
+	For the base case $n=0$, for $a\in\F_2^0$, we have $P_a(z)=1$, while $\Dnka 0ka=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise. 
+	For the inductive step, let $n\geq 2$ be even, and assume that the corresponding formula holds for $n-2$. Using the recursive formula for $\Dnka nka$ with the notation $a=(b,a_{n-1},a_n)$, we have:
 	\begin{align*}
@@
 
-\begin{remark}
 We can also use Property \ref{prop:generating_fct} to obtain $\Dnka nka$ through differentiation:
@@
 \end{table}
-\end{remark}
 
@@
 
-One can also prove the following:
+\pmnote{Bounds on Dnk from complex analysis}
 
-\begin{Prop}
-    For a fixed integer $k\geq 1$ and sufficiently large $n\geq b(k)$, it holds that:
-    \[
-        \max_{a\in\F_2^n}|\Dnka nka|=|\Dnka nk{0_n}|=\left(-\frac12\right)^k\sum_{i=\lceil k/2\rceil}^{n/2}(-4)^i\binom{n/2}{i}\binom{i}{k-i}.
-    \]
-\end{Prop}
+\pmnote{practical experiments for the function.}
 
-\begin{remark}
-    In general, it also appears that the vector $a\in\F_2^n$ for which $|\Dnka nka|$ is maximal always satisfies $r(a)=0$.
-\end{remark}
+\subsection{Generalization}
 
-Also, using the Cauchy estimate on holomorphic functions, we can prove:
+\begin{definition}
+	Let $n\in \N$ be an even number and $t \in \N $ no greater than $n/2$, we denote by $d_{t,n}$ the function given by: $d_{t,n}(x)=\sum_{i=1}^t x_{2i-1} x_{2i}$.
 
-\begin{Prop}
-    For any real number $R>0$, we have the following bound:
-    \[
-        |\Dnka nka|\leq\frac{(M_R)^{n/2}}{R^k},
-    \]
-    where $M_R$ is the maximum of $\left|z^2-2z-1\right|$ on the complex disk $|z|=R$. Explicitly, $M_R$ can be expressed as follows:
-    \[
-        M_R=
-        \begin{cases}
-            -R^2+2R+1&\text{if $R\leq\sqrt 2-1$}\\
-            \sqrt 2\left(R^2+1\right)&\text{if $\sqrt 2-1\leq R\leq\sqrt 2+1$}\\
-            R^2+2R-1&\text{if $R\geq\sqrt 2+1$}\\
-        \end{cases}.
-    \]
-\end{Prop}
+%	by $\Dnka{n}{k}{a}$:
+%	\[\Dnka{n}{k}{a}= \sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a x}\]
+\end{definition}
 
-\begin{remark}
-    Here are some interesting choices for $R$:
-    \begin{itemize}
-        \item Choosing $R=1/\sqrt 2$ yields that $|\Dnka nka|\leq\left(3/\sqrt 2\right)^{n/2}\cdot \sqrt 2^k$.
-        \item Choosing $R=1/2$ gives $|\Dnka nka|\leq (5\sqrt 2/4)^{n/2}\cdot 2^k$.
-        \item Choosing $R=1$ yields $|\Dnka nka|\leq (2\sqrt 2)^{n/2}$. This is particularly useful if $k$ is close to $n/2$.
-    \end{itemize}
-\end{remark}
+In particular, $d_{n,n}(x)=d_n(x)$.
 
-\begin{remark}
-    We can even go ahead and choose $R=R_{n,k}$ in terms of $n$ and $k$, in such a way that the upper bound of $B_{R,n,k}=(M_R)^{n/2}/R^k$ is minimized.
-To do this, consider any $1\leq k\leq n-1$.
-We can actually assume that $k\leq n/2$: if $k>n/2$, replace it by $n-k$ (recall that $|\Dnka nka|=|\Dnka n{n-k}a|$ by Property \ref{prop:symmetry}).
-One can show that $B_{R,n,k}$ is minimal for the following choice of $R=R_{n,k}$:
-    \[
-        R_{n,k}=\begin{cases}
-            \frac{n-2k-\sqrt{2(n-2k)^2-n^2}}{2(n-k)}&\text{if $k\leq\frac{2-\sqrt 2}{4}\cdot n$}\\
-            \sqrt{\frac{k}{n-k}}&\text{if $k\geq\frac{2-\sqrt 2}{4}\cdot n$}
-        \end{cases}.
-    \]
-    Figure \ref{fig:cauchy_estimate} compares for $n=1\,000$ the two upper bounds we have for $|\Dnka nka|$ on a logarithmic scale: the binomial coefficient $\binom nk$ in red, and the bound $B_{R,n,k}$ with the optimally chosen $R=R_{n,k}$ in blue.
-The $x$-axis represents the values for $k$, while the $y$-axis represents the binary logarithm of the two bounds.
-In case $|k-n/2|\leq\sqrt{2}/4\cdot n$, it can be observed that the Cauchy estimate yields particularly good bounds compared to the binomial coefficients.
-In fact, in this case, we get:
-    \[
-        \Dnka nka\leq\left(\frac{\sqrt 2 n}{n-k}\right)^{n/2}\cdot\left(\frac{n-k}{k}\right)^{k/2}.
-    \]
+We focus on the Walsh spectrum restricted to the slices of any function $d_{t,n}$
 
-    \begin{figure}
-        \centering
-        \includegraphics[width=7cm]{cauchy_estimate.pdf}
-        \caption{Cauchy estimate in blue vs.\ binomial coefficients in red}
-        \label{fig:cauchy_estimate}
-    \end{figure}
-\end{remark}
+\begin{proposition}\label{prop:dtn}
+Let $t, n\in \N$ with $n$ even and $t\le n/2$, the following holds on $d_{t,n}$ for all $k\in [0,n]$:
+\[\wtk{d_{t,n}}{k}(a)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t},\]
+where $b$ denotes the first $2t$ elements of $a$ and $c$ the last $n-2t$ elements.
+
+\end{proposition}
+\begin{proof}
+We rewrite the restricted Walsh transform, denoting $x\in \F_2^n$ by $(y,z)$ where $y\in \F_2^{2t}$ and $z \in \F_2^{n-2t}$, and similarly denoting $a$ by $(b,c)$:
+
+\begin{align*}
+\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,t}(y)+by +cz}\\
+&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t} \atop z \in \Ekn{k-\ell}{n-2t}} (-1)^{d_{t,t}(y)+by +cz}\\
+	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,t}(y)+by} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{cz}\right)\\
+	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.
+\end{align*}
+
+\end{proof}
 

### 2024-09-23 RevisedHiddenWeight.tex

--- 2024-08-29 RevisedHiddenWeight.tex
@@
 \begin{Prop}
+
     If $p=q$ and $k$ is odd, then $\Dnka nka=0=\Dnka n{n-k}a$.
@@
 \end{remark}
+>>>>>>> 927bf10bd354d63e33833a2cff7df1af6d3d3523
 
@@
     \end{enumerate}
+
 \end{Prop}
@@
     $n$ & $\max_{a\in\F_2^n}|W_f(a)|$ & $B_n$ \\ \hline
-    $2$  & $2$     & $2$     \\
-    $4$  & $8$     & $8$     \\
-    $6$  & $20$    & $28$    \\
-    $8$  & $52$    & $76$    \\
-    $10$ & $108$   & $212$   \\
-    $12$ & $292$   & $596$   \\
-    $14$ & $700$   & $1\,828$  \\
-    $16$ & $2\,176$  & $5\,196$  \\
-    $18$ & $4\,964$  & $14\,668$  \\
-    $20$ & $14\,032$ & $41\,468$ \\
-    $22$ & $34\,232$ & $118\,544$ \\
-    $24$ & $109\,648$ & $325\,188$ \\ \hline
+    $2$  & $2$     & $4$     \\
+    $4$  & $8$     & $14$     \\
+    $6$  & $20$    & $36$    \\
+    $8$  & $52$    & $114$    \\
+    $10$ & $108$   & $288$   \\
+    $12$ & $292$   & $820$   \\
+    $14$ & $700$   & $2\,316$  \\
+    $16$ & $2\,176$  & $6\,006$  \\
+    $18$ & $4\,964$  & $18\,192$  \\
+    $20$ & $14\,968$ & $48\,480$ \\
+    $22$ & $34\,232$ & $140\,392$ \\
+    $24$ & $109\,648$ & $392\,168$ \\ \hline
     \end{tabular}
@@
 
+Here is the updated table with the new values for \( B_n \) corresponding to each \( n \):
+
 \begin{table}
     \centering
-    \begin{minipage}{0.19\textwidth}
+    \begin{minipage}{0.24\textwidth}
         \centering
@@
             \hline
-            $2$  & $2.00 \cdot 10^{0}$  \\
-            $4$  & $8.00 \cdot 10^{0}$  \\
-            $6$  & $2.80 \cdot 10^{1}$  \\
-            $8$  & $7.60 \cdot 10^{1}$  \\
-            $10$ & $2.12 \cdot 10^{2}$ \\
-            $12$ & $5.96 \cdot 10^{2}$ \\
-            $14$ & $1.83 \cdot 10^{3}$ \\
-            $16$ & $5.20 \cdot 10^{3}$ \\
-            $18$ & $1.47 \cdot 10^{4}$ \\
-            $20$ & $4.15 \cdot 10^{4}$ \\
+            $2$  & $4.00 \cdot 10^{0}$  \\
+            $4$  & $1.40 \cdot 10^{1}$  \\
+            $6$  & $3.60 \cdot 10^{1}$  \\
+            $8$  & $1.14 \cdot 10^{2}$  \\
+            $10$ & $2.88 \cdot 10^{2}$  \\
+            $12$ & $8.20 \cdot 10^{2}$  \\
+            $14$ & $2.32 \cdot 10^{3}$  \\
+            $16$ & $6.01 \cdot 10^{3}$  \\
+            $18$ & $1.82 \cdot 10^{4}$  \\
+            $20$ & $4.85 \cdot 10^{4}$  \\
             \hline
@@
     \end{minipage}%
-    \begin{minipage}{0.19\textwidth}
+    \begin{minipage}{0.24\textwidth}
         \centering
@@
             \hline
-            $22$ & $1.19 \cdot 10^{5}$ \\
-            $24$ & $3.25 \cdot 10^{5}$ \\
-            $26$ & $9.59 \cdot 10^{5}$ \\
-            $28$ & $2.68 \cdot 10^{6}$ \\
-            $30$ & $7.65 \cdot 10^{6}$ \\
-            $32$ & $2.14 \cdot 10^{7}$ \\
-            $34$ & $6.25 \cdot 10^{7}$ \\
-            $36$ & $1.76 \cdot 10^{8}$ \\
-            $38$ & $5.03 \cdot 10^{8}$ \\
-            $40$ & $1.40 \cdot 10^{9}$ \\
+            $22$ & $1.40 \cdot 10^{5}$  \\
+            $24$ & $3.92 \cdot 10^{5}$  \\
+            $26$ & $1.14 \cdot 10^{6}$  \\
+            $28$ & $3.12 \cdot 10^{6}$  \\
+            $30$ & $8.90 \cdot 10^{6}$  \\
+            $32$ & $2.50 \cdot 10^{7}$  \\
+            $34$ & $7.14 \cdot 10^{7}$  \\
+            $36$ & $2.04 \cdot 10^{8}$  \\
+            $38$ & $5.75 \cdot 10^{8}$  \\
+            $40$ & $1.62 \cdot 10^{9}$  \\
             \hline
@@
             \hline
-            $42$ & $4.01 \cdot 10^{9}$ \\
-            $44$ & $1.12 \cdot 10^{10}$ \\
-            $46$ & $3.21 \cdot 10^{10}$ \\
-            $48$ & $8.91 \cdot 10^{10}$ \\
-            $50$ & $2.56 \cdot 10^{11}$ \\
-            $52$ & $7.12 \cdot 10^{11}$ \\
-            $54$ & $2.05 \cdot 10^{12}$ \\
-            $56$ & $5.73 \cdot 10^{12}$ \\
-            $58$ & $1.65 \cdot 10^{13}$ \\
-            $60$ & $4.59 \cdot 10^{13}$ \\
+            $42$ & $4.59 \cdot 10^{9}$  \\
+            $44$ & $1.29 \cdot 10^{10}$ \\
+            $46$ & $3.63 \cdot 10^{10}$ \\
+            $48$ & $1.02 \cdot 10^{11}$ \\
+            $50$ & $2.88 \cdot 10^{11}$ \\
+            $52$ & $8.06 \cdot 10^{11}$ \\
+            $54$ & $2.30 \cdot 10^{12}$ \\
+            $56$ & $6.45 \cdot 10^{12}$ \\
+            $58$ & $1.83 \cdot 10^{13}$ \\
+            $60$ & $5.14 \cdot 10^{13}$ \\
             \hline
@@
             \hline
-            $62$ & $1.32 \cdot 10^{14}$ \\
-            $64$ & $3.66 \cdot 10^{14}$ \\
-            $66$ & $1.05 \cdot 10^{15}$ \\
-            $68$ & $2.93 \cdot 10^{15}$ \\
-            $70$ & $8.40 \cdot 10^{15}$ \\
-            $72$ & $2.33 \cdot 10^{16}$ \\
-            $74$ & $6.71 \cdot 10^{16}$ \\
-            $76$ & $1.87 \cdot 10^{17}$ \\
-            $78$ & $5.39 \cdot 10^{17}$ \\
-            $80$ & $1.51 \cdot 10^{18}$ \\
+            $62$ & $1.47 \cdot 10^{14}$ \\
+            $64$ & $4.09 \cdot 10^{14}$ \\
+            $66$ & $1.17 \cdot 10^{15}$ \\
+            $68$ & $3.25 \cdot 10^{15}$ \\
+            $70$ & $9.34 \cdot 10^{15}$ \\
+            $72$ & $2.60 \cdot 10^{16}$ \\
+            $74$ & $7.44 \cdot 10^{16}$ \\
+            $76$ & $2.08 \cdot 10^{17}$ \\
+            $78$ & $5.97 \cdot 10^{17}$ \\
+            $80$ & $1.65 \cdot 10^{18}$ \\
             \hline
@@
     \end{minipage}
-    \caption{Values of $B_n$ for various $n$.}
+    \caption{Values of $B_n$ for various $n$}
     \label{table:walsh_bounds}
@@
 \end{figure}
+
+\pmnote{Bounds on Dnk from complex analysis}
+
+\pmnote{practical experiments for the function.}
+
+\subsection{Generalization}
+
+\begin{definition}
+	Let $n\in \N$ be an even number and $t \in \N $ no greater than $n/2$, we denote by $d_{t,n}$ the function given by: $d_{t,n}(x)=\sum_{i=1}^t x_{2i-1} x_{2i}$.
+
+	%	by $\Dnka{n}{k}{a}$:
+	%	\[\Dnka{n}{k}{a}= \sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a x}\]
+\end{definition}
+
+In particular, $d_{n,n}(x)=d_n(x)$.
+
+We focus on the Walsh spectrum restricted to the slices of any function $d_{t,n}$
+
+\begin{proposition}\label{prop:dtn}
+	Let $t, n\in \N$ with $n$ even and $t\le n/2$, the following holds on $d_{t,n}$ for all $k\in [0,n]$:
+	\[\wtk{d_{t,n}}{k}(a)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t},\]
+	where $b$ denotes the first $2t$ elements of $a$ and $c$ the last $n-2t$ elements.
+
+\end{proposition}
+\begin{proof}
+	We rewrite the restricted Walsh transform, denoting $x\in \F_2^n$ by $(y,z)$ where $y\in \F_2^{2t}$ and $z \in \F_2^{n-2t}$, and similarly denoting $a$ by $(b,c)$:
+
+	\begin{align*}
+	\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,t}(y)+by +cz}\\
+	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t} \atop z \in \Ekn{k-\ell}{n-2t}} (-1)^{d_{t,t}(y)+by +cz}\\
+	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,t}(y)+by} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{cz}\right)\\
+	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.
+	\end{align*}
+
+\end{proof}
+
 \newpage

### 2024-09-25 RevisedHiddenWeight.tex
bit on AI

@@
 
-\begin{Prop}[Nonlinearity on the slice, adapted from~\cite{TOSC:CarMeaRot17}, Proposition 6]\label{prop:nlk}
-	Let $n\in \N^*, k\in [0,n]$, for every $n$-variable Boolean function $f$ over $\Ekn{k}{n}$:
-	\[ \NLk{k}(f)=\frac{|\Ekn{k}{n}|}{2} -\frac{\max_{a\in \F_2^n} |\wtk{f}{k}(a)|}{2}  .\]
-\end{Prop}
-
 \subsection{Symmetric Functions}
@@
 We recall that bent functions are those Boolean functions achieving maximal nonlinearity.
-
-\begin{Prop}[Weightwise restricted Walsh transform and addition of symmetric function (~\cite{INDO:GinMea22}, Proposition $4$)]\label{prop:AddSym}
-	Let $n\in \N^*$, $k\in [0,n]$ and $f \in \Bn{n}$, the following holds on $f+\phikn{k}{n}$
-	\[\forall a\in \F_2^n, \forall i\in [0,n]\setminus \{k\}, \wtk{f+\phikn{k}{n}}{i}(a)=\wtk{f}{i}(a),\text{ and } \wtk{f+\phikn{k}{n}}{k}(a)=-\wtk{f}{i}(a).\]	
-\end{Prop}
 
@@
 
-\pmnote{Bounds on Dnk from complex analysis}
-
-\pmnote{practical experiments for the function.}
-
 \subsection{Generalization}
@@
 
+\subsection{Algebraic immunity of $f$}
+
+\begin{proposition}[Algebraic immunity of $f$]
+	Let $n\in \N$ be even, $f$ defined as
+	$f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k$ and $h$ denote the $n$-variable HWBF, the following holds:
+	\[\AI(f)\ge \AI(h)-2.\]
+\end{proposition}
+\begin{proof}
+	content...
+\end{proof}
+
 \newpage

### 2024-09-25 RevisedHiddenWeight.tex
ok

@@
 %\end{definition}
+\begin{definition}[Nonlinearity and weightwise nonlinearity] \label{def:nl}
+	The nonlinearity $\NL(f)$ of a Boolean function $f\in \BN$, where $n$ is a positive integer, is the minimum Hamming distance between $f$ and all the affine functions in $\BN$:
+	\[ \NL(f) = \min_{g,\, \degg(g)\leq 1} \{ \hd(f,g) \}{,} \]
+	where $g(x)=a\cdot x+\varepsilon$, $a\in \F_2^n, \varepsilon\in \F_2$. 	
+	The nonlinearity can also be defined from the Walsh transform:
+	\[ \NL(f) = 2^{n-1}- \frac{1}{2} \max_{a\in \F_2^n}{|\wt{f}(a)|}. \]
+\end{definition}
+
+\begin{definition}[Algebraic immunity] \label{def:ai}
+	The algebraic immunity of a Boolean function $f\in \Bfn{n}$, denoted as $\AI(f)$, is defined as:
+	\[ \AI(f) = \min_{g \neq 0}\{ \degg(g) \; | \; fg = 0 \; \text{or} \; (f + 1)g = 0 \}{,} \]
+	where $\degg(g)$ is the algebraic degree of $g$.
+	The function $g$ is called an annihilator of $f$ (or $f + 1$). 
+\end{definition}
 
@@
 The $n$-variable \emph{Boolean symmetric functions} are those that are constant on each slice $\Ekn{k}{n}$ for $k\in [0,n]$. 
-This class has been assiduously studied in the context of cryptography, see \eg \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,CCDS:Meaux21,IEEE:CarMea21}.
+This class has been assiduously studied in the context of cryptography, see \eg \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
 In this paper we mainly consider two families of symmetric functions, which are both bases of the symmetric functions:
@@
 \end{definition}
+
+\pmnote{Introduce formally HWBF, and weightwise degree d functions}
 
@@
 
-Accordingly, $f$ is balanced when $n=0\mod 4$ and unbalanced when $n=2 \mod 4$.
+Accordingly, $f$ is balanced when $n \equiv 0\mod 4$ and unbalanced when $n\equiv 2 \mod 4$.
 
@@
 
+\pmnote{@Tim, could you do a (summary) graph with the bound it gives for the nonlinearity? (Definition from the Walsh transform in the preliminaries)
+
+Could you add curves for the majority function, $n$ even $\NL=2^{n-1}- 1/2 \binom{n}{n/2}$ , and HWBF  $n$ even $\NL=2^{n-1}- 2 \binom{n-2}{(n-2)/2}$ \cite{DAM:WCST14} Theorem 3.
+
+}
+
 Here is the updated table with the new values for \( B_n \) corresponding to each \( n \):
@@
 \begin{proof}
-	content...
+	Let denote by $q$ the quadratic function $\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}$, it allows to write $h=f+q$. 
+	Let $g\neq 0$ be an annihilator of $f+ \varepsilon$ of minimum degree (where $\varepsilon \in \{0,1\}$), then the following holds:
+	\[g (1+q) (h+\varepsilon) = g(1+q) (f+\varepsilon + q)=0, \]
+	hence $g (1+q)$ is an annihilator of $h+ \varepsilon$. 
+	If $g (1+q)\ne 0$ then $\degg(g(1+q)) \le \degg(g)+2$ and we obtain $\degg(g)\ge \AI(h) -2$. 
+	Otherwise, $g (1+q)= 0$ implies that $g$ annihilates $1+q$ and therefore $0=g (f+\varepsilon + 1 +q)=g(h+ \varepsilon +1)$ that is $\degg(g)\ge \AI(h)$. 
+	Summarizing, for any non null annihilator $g$ of $f$ or $f+1$ we get $\degg(g)\ge \AI(h)-2$, it allows to conclude $\AI(f)\ge \AI(h)-2$.
+
 \end{proof}
+
+From~\cite{DAM:WCST14} Theorem 4, the algebraic immunity of the HWBF is at least $\lfloor n/3\rfloor +1$, which leads to $\lfloor n/3\rfloor -1$ for $f$.
 

### 2024-09-26 RevisedHiddenWeight.tex
Added Walsh bound comparison

@@
 \end{remark}
->>>>>>> 927bf10bd354d63e33833a2cff7df1af6d3d3523
 
@@
 Table \ref{table:walsh_bounds} gives all values of this bound $B_n$ for all even $1\leq n\leq 80$.
-As we can see from Figure \ref{fig:walsh_bound}, our bound $B_n$ is exponential in $n$.
 
@@
 
-\pmnote{@Tim, could you do a (summary) graph with the bound it gives for the nonlinearity? (Definition from the Walsh transform in the preliminaries)
+Figure \ref{fig:walsh_bound_comparison} compares our experimental bound $B_n$ to the theoretical bound $n\cdot 2^{3n/4}+1$ and the binomial coefficient $\binom{n}{n/2}$, on a logarithmic scale.
+The first two and the last one have an asymptotic slope of $3/4$ and $1$, respectively.
 
-Could you add curves for the majority function, $n$ even $\NL=2^{n-1}- 1/2 \binom{n}{n/2}$ , and HWBF  $n$ even $\NL=2^{n-1}- 2 \binom{n-2}{(n-2)/2}$ \cite{DAM:WCST14} Theorem 3.
-
-}
-
-Here is the updated table with the new values for \( B_n \) corresponding to each \( n \):
+\begin{figure}
+    \centering
+    \includegraphics[width=9cm]{comparison_walsh_bound.pdf}
+    \caption{On a logarithmic scale, our experimental bound $B_n$ in terms of $n$ in red, our theoretical bound $n\cdot 2^{3n/4}+1$ from Property \ref{prop:bound_sum_D_nka} in green, and the bound $\binom{n}{n/2}$ in blue.}
+    \label{fig:walsh_bound_comparison}
+\end{figure}
 
@@
             \hline
-            $n$ & $B_n$ \\
+            $n$ & $\approx B_n$ \\
             \hline
@@
     \end{minipage}
-    \caption{Values of $B_n$ for various $n$}
+    \caption{Approximate values of $B_n$ for various $n$}
     \label{table:walsh_bounds}
 \end{table}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=10cm]{walsh_bound}
-    \caption{Our bounds $B_n$ in terms of $n$, on a logarithmic scale}
-    \label{fig:walsh_bound}
-\end{figure}
 
@@
 	\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,t}(y)+by +cz}\\
-	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t} \atop z \in \Ekn{k-\ell}{n-2t}} (-1)^{d_{t,t}(y)+by +cz}\\
+	&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,t}(y)+by +cz}\\
 	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,t}(y)+by} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{cz}\right)\\
-	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.
+	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
 	\end{align*}
@@
 	Summarizing, for any non null annihilator $g$ of $f$ or $f+1$ we get $\degg(g)\ge \AI(h)-2$, it allows to conclude $\AI(f)\ge \AI(h)-2$.
-
 \end{proof}

### 2024-10-02 RevisedHiddenWeight.tex
ok

@@
 
-\subsection{Boolean functions and weightwise considerations}
+For $v$ a binary vector of length $n$ we denote by $\w(v)$ its Hamming weight: $\w(v)=|\{i\in [1,n] \, | \, x_i=1\}|$.
 
-In this part we recall general concepts on Boolean functions and their weightwise properties we use in this article. 
-For a deeper introduction on Boolean functions and their cryptographic parameters we refer to the survey of \eg~\cite{Carlet20} and to~\cite{TOSC:CarMeaRot17} for the weightwise properties, also called properties on the slices.
+\pmnote{Preliminaries to adapt}
+
+\subsection{Boolean functions and cryptographic parameters}
+
+In this part we recall general concepts on Boolean functions and their cryptographic properties we use in this article. 
+For a deeper introduction on Boolean functions and their cryptographic parameters we refer to the book~\cite{Carlet20} and to~\cite{TOSC:CarMeaRot17} for the weightwise properties, also called properties on the slices.
 For $k \in [0,n]$ we denote $\Ekn{k}{n}$ the set $\{x\in \F_2^n \, | \, \w(x)=k  \}$ and call it slice of the Boolean hypercube (of dimension $n$).
-Accordingly, the Boolean hypercube is partitioned into $n+1$ slices where the elements have the same Hamming weight.
+
+%Accordingly, the Boolean hypercube is partitioned into $n+1$ slices where the elements have the same Hamming weight.
 
@@
 
-To denote when a property or a definition is restricted to a slice we use the subscript $k$. 
-For example, for a $n$-variable Boolean function $f$ we denote its support $\supp(f)=\{x\in \F_2^n \, | \, f(x)=1  \}$ and we denote $\suppk{k}(f)$ its support restricted to a slice, that is $\supp(f)\cap \Ekn{k}{n}$.
-
 \begin{definition}[Balancedness]\label{def:balancedness}
@@
 
-	For $k\in [0,n]$ the function is said balanced on the slice $k$ if $||\suppk{k}(f)|-|\suppk{k}(f+1)| |\le 1$.
+%	For $k\in [0,n]$ the function is said balanced on the slice $k$ if $||\suppk{k}(f)|-|\suppk{k}(f+1)| |\le 1$.
 In particular when $|\Ekn{k}{n}|$ is even $|\suppk{k}(f)|=|\suppk{k}(f+1)|=|\Ekn{k}{n}|/2$.
@@
 
-\subsection{Symmetric Functions}
+\subsection{Symmetric Functions, HWBF and weightwise degree-d functions}
 
@@
 This class has been assiduously studied in the context of cryptography, see \eg \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
-In this paper we mainly consider two families of symmetric functions, which are both bases of the symmetric functions:
+In this paper we mainly consider the slice indicator functions.
 
-\begin{definition}[Elementary symmetric functions]
-Let $i\in [0,n]$, the elementary symmetric function of degree $i$ in $n$ variables, denoted $\sigma_{i,n}$, is the function which ANF contains all monomials of degree $i$ and no monomials of other degrees.
-\end{definition}
-\begin{definition}[Slice indicator functions]
+%\begin{definition}[Elementary symmetric functions]
+%Let $i\in [0,n]$, the elementary symmetric function of degree $i$ in $n$ variables, denoted $\sigma_{i,n}$, is the function which ANF contains all monomials of degree $i$ and no monomials of other degrees.
+%\end{definition}
+\begin{definition}[Slice indicator functions]\label{def:slice}
  Let $k\in [0,n]$, the indicator function of the slice of weight $k$ is defined as:
@@
 \end{definition}
-We recall that bent functions are those Boolean functions achieving maximal nonlinearity.
+
+%We recall that bent functions are those Boolean functions achieving maximal nonlinearity.
+
+\pmnote{adapt usefull parts:
+
+In~\cite{DAM:GinMea22} the authors study the relationship between weightwise perfectly balanced functions (functions balanced on all the slices, see for example~\cite{TOSC:CarMeaRot17,DCC:LiuMes19,CC:TangLiu19,BFA:MesSuLi21,ACI:ManKuLar22,SSRN:ZLCQZ23,ASIACCS:YCL+23,LATIN:GinMea23}) and weightwise affine functions \ie weightwise degree-$1$ functions.
+In fact weightwise degree-$1$ and degree-$0$ functions have been studied for their cryptographic properties in many works, without the same formalism. 
+The weightwise constant functions ($\WD{0}{n}$) are the symmetric functions that have been extensively studied (\eg \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:CheLu11,A2C:CarMea19,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}).
+Thereafter, the hidden weight bit function introduced in~\cite{IEEE:Bryant91} is a weightwise degree-$1$ function, the one obtained by fixing $f_0=0$ and $f_k=x_k$ for $k \in [n]$. 
+The cryptographic properties of this function have been studied in~\cite{DAM:WCST14}, showing good algebraic properties for this function. 
+In~\cite{TOSC:CarMeaRot17}, the bent functions in Propositions $1$ and $2$ are weightwise affine.}
+
+\pmnote{Introduce formally HWBF, and weightwise degree d functions}
+\begin{definition}[Hidden Weight Bit Function (HWBF)]\label{def:hwbf}
+	Let $n\in \N^*$we call Hidden Weight Bit Function (HWBF) the $n$-variable Boolean function defined by:
+	\[h(x)= \left\{ 
+	\begin{array}{l l}
+	0 & \quad \text{ if } \w(x) =0, \\
+	x_k & \quad \text{ if } \w(x)=k.
+	\end{array} \right. \]
+
+\end{definition}
+
+\begin{definition}[Weightwise degree-$d$ functions]\label{def:WdegD}
+	Let $n\in \N^*$ and for $k\in[0,n]$ $\phikn{k}{n}$ denotes the indicator function of $\Ekn{k}{n}$. 
+	An $n$-variable Boolean function $f$, written as $f=\sum_{k=0}^n f_k \phikn{k}{n}$, is called weightwise degree-$d$ if and only if for each $k\in [0,n]$ $f_k$ coincide with a function of degree at most $d$ over $\Ekn{k}{n}$.
+	%	Equivalently, $f$ is weightwise affine if and only if for each $k\in [0,n]$ $\NLk{k}(f)=0$.
+
+	The set of weightwise degree-$d$ functions is denoted by $\WD{d}{n}$.
+
+	%	$f=\sum_{k=0}^n f_k \phikn{k}{n}$ is called weightwise affine if and only if for each $k\in [0,n]$ $f_k$ coincide with an affine function over $\Ekn{k}{n}$.
+
+\end{definition}
+
+\pmnote{add: properties of maj function, HWPF, and some WWL and WWQ}
+
+\pmnote{add the nonlinearity of Dickson's function}
 
@@
 \end{definition}
-
-\pmnote{Introduce formally HWBF, and weightwise degree d functions}
 

### 2024-10-07 RevisedHiddenWeight.tex
Proving bound 1 + n * 2^{3n/4} for |W_f(a)|.

@@
 
-\begin{Prop}\label{prop:generating_fct}
+\begin{proposition}\label{proposition:generating_fct}
 	It holds that $\sum_{k\in\Z}\Dnka nka z^k= P_a(z)$.
-\end{Prop}
+\end{proposition}
 
@@
 
-\begin{Prop}\label{prop:symmetry}
+\begin{proposition}\label{proposition:symmetry}
 	For every integer $k$, we have:
@@
 	\]
-\end{Prop}
+\end{proposition}
 
@@
 \begin{proof}
-	By Property \ref{prop:symmetry}, we have $\Dnka n{n/2}a=(-1)^{p+q+n/2}\Dnka n{n/2}a=-\Dnka n{n/2}a$ because $p+q+n/2\equiv n/2-p-q\equiv r\equiv 1\bmod 2$.
+	By Proposition \ref{proposition:symmetry}, we have $\Dnka n{n/2}a=(-1)^{p+q+n/2}\Dnka n{n/2}a=-\Dnka n{n/2}a$ because $p+q+n/2\equiv n/2-p-q\equiv r\equiv 1\bmod 2$.
 \end{proof}
@@
 Another immediate case for zero coefficients is the following:
-\begin{Prop}
-
+\begin{proposition}
     If $p=q$ and $k$ is odd, then $\Dnka nka=0=\Dnka n{n-k}a$.
-\end{Prop}
+\end{proposition}
 
@@
 Thus, the coefficient $\Dnka nka$ of $z^k$ for odd $k$ must be zero in $P_a(z)$.
-It follows that also $\Dnka n{n-k}a=0$ by Property \ref{prop:symmetry}.
+It follows that also $\Dnka n{n-k}a=0$ by Proposition \ref{proposition:symmetry}.
 \end{proof}
 
-\begin{remark}
-    We can also use Property \ref{prop:generating_fct} to obtain $\Dnka nka$ through differentiation:
+\begin{remark}\label{remark:D_nka_differentiation}
+    We can also use Proposition \ref{proposition:generating_fct} to obtain $\Dnka nka$ through differentiation:
     \[
@@
 
-\begin{Prop}\mbox{}
+\begin{proposition}\mbox{}
     \begin{enumerate}
@@
     \end{enumerate}
-\end{Prop}
+\end{proposition}
 
@@
 
-Using Property \ref{prop:generating_fct}, we can also deduce some sums involving the $\Dnka nka$:
+Using Proposition \ref{proposition:generating_fct}, we can also deduce some sums involving the $\Dnka nka$:
 
-\begin{Prop}\mbox{}
+\begin{proposition}\mbox{}
     \begin{enumerate}
@@
 
-\end{Prop}
+\end{proposition}
 
@@
 
-One can also prove the following:
+\subsection{Bounding the Walsh transform of $f$ using the Cauchy estimate}
 
-\begin{Prop}
+Recall the Cauchy estimate on holomorphic functions:
+
+\begin{Prop}[\cite{rudin1987}, Theorem 10.26]\label{property:cauchy_estimate}
+    Let $w$ be a complex number, and let $R>0$ be some radius.
+If $f$ is a holomorphic function defined on an open set containing every complex number $z$ satisfying $|z-w|<R$, then for every integer $k\geq 0$, the $k$-th derivative of $f$ evaluated at $w$ can be bounded, in absolute value, as follows:
+    \[
+        \left|\frac{\dd^k}{\dd^k z}f(w)\right|\leq\frac{k!\cdot M_R}{R^k},
+    \]
+    where $M_R$ is the maximum of $|f(z)|$ on the circle $|z-w|=R$.
+\end{Prop}
+
+Applying this, we get:
+
+\begin{theorem}\label{theorem:bound_D_nka}
+    For every $a\in\F_2^n$ and every integer $k\geq 0$, it holds that:
+    \[
+        |\Dnka nka|\leq 2^{3n/4}.
+    \]
+\end{theorem}
+
+\begin{proof}
+    Recall from Remark \ref{remark:D_nka_differentiation} that $k!\cdot\Dnka nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}$.
+Choosing $f=P_a$, $w=0$ and $R=1$ in Property \ref{property:cauchy_estimate} then gives:
+    \[
+        |\Dnka nka|=\frac{1}{k!}\left|\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}\right|\leq M,
+    \]
+    where $M$ is the maximum of $|P_a(z)|$ on the circle $|z|=1$.
+We claim, and prove below, that the maximum of $\left|-z^2+2z+1\right|$ on $|z|=1$ is $2\sqrt 2$.
+This implies that the maximum of $\left|-z^2-2z+1\right|$ on $|z|=1$ is $2\sqrt 2$ as well.
+Since the maximum of $\left|z^2+1\right|$ on $|z|=1$ is $2<2\sqrt 2$, it follows that $|\Dnka nka|\leq M\leq (2\sqrt 2)^{p+q}2^r\leq (2\sqrt 2)^{n/2}$.
+
+    It remains to prove that the maximum of $\left|-z^2+2z+1\right|^2$ on $|z|=1$ equals $8$. Using that $|w|^2=w\overline w$ for every complex number $w$, we obtain for $|z|=1$:
+    \[
+        \left|-z^2+2z+1\right|^2=\left(z^2-2z-1\right)\left(\overline z^2-2\overline z-1\right)=6-\left(z^2+\overline z^2\right)=6-2\mathrm{Re}\left(z^2\right),
+    \]
+    where $\mathrm{Re}\left(z^2\right)$ denotes the real part of $z^2$.
+Since the minimum of $\mathrm{Re}\left(z^2\right)$ on $|z|=1$ is $-1$, we conclude that the maximum of $\left|-z^2+2z+1\right|^2$ on $|z|=1$ is $6-2(-1)=8$.
+\end{proof}
+
+As a consequence, we have:
+
+\begin{Corollary}\label{cor:bound_walsh_cauchy}
+    For every $a\in\F_2^n$, it holds that:
+    \[
+        |\wt f(a)|\leq 1+n\cdot 2^{3n/4}.
+    \]
+\end{Corollary}
+
+\begin{proof}
+    We have previously established that $\wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}$. Then, applying Proposition \ref{theorem:bound_D_nka} yields:
+    \[
+        |\wt{f}(a)|\leq 1+\sum_{k=1}^n\left|\Dnka{n}{k}{b+\pi(e_k)}\right|\leq 1+ n\cdot 2^{3n/4}.\qedhere
+    \]
+\end{proof}
+
+\mycomment{One can also prove the following:
+
+\begin{proposition}
     For a fixed integer $k\geq 1$ and sufficiently large $n\geq b(k)$, it holds that:
@@
     \]
-\end{Prop}
-
-\begin{remark}
-    In general, it also appears that the vector $a\in\F_2^n$ for which $|\Dnka nka|$ is maximal always satisfies $r(a)=0$.
-\end{remark}
+\end{proposition}
 
@@
 
-\begin{Prop}
+\begin{proposition}
     For any real number $R>0$, we have the following bound:
@@
     \]
-\end{Prop}
+\end{proposition}
 
@@
 To do this, consider any $1\leq k\leq n-1$.
-We can actually assume that $k\leq n/2$: if $k>n/2$, replace it by $n-k$ (recall that $|\Dnka nka|=|\Dnka n{n-k}a|$ by Property \ref{prop:symmetry}).
+We can actually assume that $k\leq n/2$: if $k>n/2$, replace it by $n-k$ (recall that $|\Dnka nka|=|\Dnka n{n-k}a|$ by Proposition \ref{proposition:symmetry}).
 One can show that $B_{R,n,k}$ is minimal for the following choice of $R=R_{n,k}$:
@@
     \end{figure}
-\end{remark}
+\end{remark}}
 
-\begin{Prop}\label{prop:bound_sum_D_nka}
-    For every $1\leq k\leq n$, fix a Boolean vector $a\ui k\in\F_2^n$. Then we have the following bound:
-    \[
-        \sum_{k=1}^n\left|\Dnka nk{a\ui k}\right|\leq n\cdot 2^{3n/4}.
-    \]
-\end{Prop}
+\subsection{Bounding the Walsh transform of $f$ experimentally}
 
-\begin{proof}
-    Simply observe that $2^{n/4}\sqrt{\frac{n^n}{(n-k)^{n-k}\cdot k^k}}$ is maximal for $k=n/2$, in which case the expression reduces to $2^{3n/4}$.
-\end{proof}
-
-\subsection{Bounding the Walsh transform of $f$}
-
-From Property \ref{prop:bound_sum_D_nka}, we can in particular deduce that $|\wt f(a)|\leq n\cdot 2^{3n/4}+1$ for every Boolean vector $a\in\F_2^n$.
-This is a very pessimistic bound.
+We have just deduced that $|\wt f(a)|\leq 1+n\cdot 2^{3n/4}$ for every Boolean vector $a\in\F_2^n$.
+This is a pessimistic bound.
 In this section, we will discuss how a tighter bound on $|\wt f(a)|$ can be obtained in polynomial time in $n$.
@@
 We claim that this computation has a complexity of $\mathcal{O}(n^3 \log n)$.
-Towards this, according to Property \ref{prop:generating_fct}, it is sufficient to expand the polynomials $(-z^2 + 2z + 1)^p \cdot (-z^2 - 2z + 1)^q \cdot (z^2 + 1)^r$ for all triplets $(p,q,r)$ such that $p+q+r=n/2$.
+Towards this, according to Proposition \ref{proposition:generating_fct}, it is sufficient to expand the polynomials $(-z^2 + 2z + 1)^p \cdot (-z^2 - 2z + 1)^q \cdot (z^2 + 1)^r$ for all triplets $(p,q,r)$ such that $p+q+r=n/2$.
 
@@
 
-Figure \ref{fig:walsh_bound_comparison} compares our experimental bound $B_n$ to the theoretical bound $n\cdot 2^{3n/4}+1$ and the binomial coefficient $\binom{n}{n/2}$, on a logarithmic scale.
+Figure \ref{fig:walsh_bound_comparison} compares our experimental bound $B_n$ to the theoretical bound $1+n\cdot 2^{3n/4}$ and the binomial coefficient $\binom{n}{n/2}$, on a logarithmic scale.
 The first two and the last one have an asymptotic slope of $3/4$ and $1$, respectively.
@@
     \includegraphics[width=9cm]{comparison_walsh_bound.pdf}
-    \caption{On a logarithmic scale, our experimental bound $B_n$ in terms of $n$ in red, our theoretical bound $n\cdot 2^{3n/4}+1$ from Property \ref{prop:bound_sum_D_nka} in green, and the bound $\binom{n}{n/2}$ in blue.}
+    \caption{On a logarithmic scale, our experimental bound $B_n$ in terms of $n$ in red, our theoretical bound $1+n\cdot 2^{3n/4}$ from Proposition \ref{cor:bound_walsh_cauchy} in green, and the bound $\binom{n}{n/2}$ in blue.}
     \label{fig:walsh_bound_comparison}
@@
 
-\begin{proposition}\label{prop:dtn}
+\begin{proposition}\label{proposition:dtn}
 	Let $t, n\in \N$ with $n$ even and $t\le n/2$, the following holds on $d_{t,n}$ for all $k\in [0,n]$:

### 2024-10-08 RevisedHiddenWeight.tex
Proofs for generalizations (with parameter t)

@@
 
-As a consequence, we have:
-
 \begin{Corollary}\label{cor:bound_walsh_cauchy}
@@
 
-In particular, $d_{n,n}(x)=d_n(x)$.
+In particular, $d_{n/2,n}(x)=d_n(x)$.
 
@@
 	where $b$ denotes the first $2t$ elements of $a$ and $c$ the last $n-2t$ elements.
-
 \end{proposition}
@@
 	\end{align*}	
+\end{proof}
 
+This leads to the following generating function:
+
+\begin{proposition}
+    Let $t, n\in \N$ with $n$ even and $t\le n/2$. Let $a=(b,c)\in\F_2^n$ with $b\in\F_2^{2t}$. Denote $n-2t-\w(c)$ and $\w(c)$ by $u$ and $v$, respectively. Then the following holds:
+    \[
+        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.
+    \]
+\end{proposition}
+
+\begin{proof}
+    Applying Proposition \ref{proposition:dtn}, we get:
+    \begin{align*}
+        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k&=\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\sum_{k\in\Z}\kraw{k-\ell}{\w(c)}{n-2t}z^{k-\ell}\\
+        &=\left(\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\right)\cdot(1+z)^u\cdot(1-z)^v\\
+        &=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.\qedhere
+    \end{align*}
+\end{proof}
+
+Consequently, we get a generalization of Theorem \ref{theorem:bound_D_nka}:
+
+\begin{theorem}
+    Let $t, n\in \N$ with $n$ even and $t\le n/2$. For every $a\in\F_2^n$, it holds that:
+    \[
+        |\wtk{d_{t,n}}{k}(a)|\leq 2^{n-t/2}.
+    \]
+\end{theorem}
+
+\begin{proof}
+    By applying Property \ref{property:cauchy_estimate}, we get that a bound on $|\wtk{d_{t,n}}{k}(a)|$ is given by the maximum $M'$ on the circle $|z|=1$ of $|P_b(z)|\cdot|(1+z)^u\cdot(1-z)^v|$.
+As previously established, $|P_b(z)|$ is bounded on $|z|=1$ by $(2\sqrt 2)^t=2^{3t/2}$, and $|(1+z)^u\cdot(1-z)^v|$ is bounded on $|z|=1$ by $2^{u+v}=2^{n-2t}$.
+Therefore, we conclude that $M'$ is bounded by $2^{3t/2}2^{n-2t}=2^{n-t/2}$, and hence this is also a bound for $|\wtk{d_{t,n}}{k}(a)|$.
+\end{proof}
+
+\begin{Corollary}
+    For every $a\in\F_2^n$, the following holds:
+    \[
+        |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{n-t/2}.
+    \]
+\end{Corollary}
+
+\begin{proof}
+    Analogous to the proof of Corollary \ref{cor:bound_walsh_cauchy}.
 \end{proof}

### 2024-10-25 RevisedHiddenWeight.tex
start modif part 2

@@
 \section{Introduction}
+
+\pmnote{short intro:
+
+HWBF introduced in x, interesting for its cryptographic criteria and easy implementation. cryptographic properties studied in y such as balancedness, algebraic immunity and nonlinearity. 
+New potential uses in a stream cipher, or modifications. Use: transciphering and works aiming at finding Boolean functions easy to evaluate homomorphically, input oblivious algorithms. 
+Nonlinearity a bit low for direct use.
+
+Contributions: new function as addition of HWBF and quadratic bent function.
+We show when the function is balanced, formalize and study its nonlinearity.
+Bounds on the nonlinearity of $f$, generalization to a family of function, and an algorithm for estimating the nonlinearity for $n$ up to $80$.
+Comparisons with other functions and practical values of the parameters for $n$ up to $20$.
+
+}
 
@@
 %\end{definition}
-\begin{definition}[Nonlinearity and weightwise nonlinearity] \label{def:nl}
+\begin{definition}[Nonlinearity %and weightwise nonlinearity
+	] \label{def:nl}
 	The nonlinearity $\NL(f)$ of a Boolean function $f\in \BN$, where $n$ is a positive integer, is the minimum Hamming distance between $f$ and all the affine functions in $\BN$:
@@
 \end{definition}
+
+When $n$ is even, the nonlinearity of a function can reach at most $2^{n-1}-2^{n/2 -1}$.
+Functions reaching this maximum are called bent functions.
+The quadratic function $d_n$ given by: $d_n(x)=\sum_{i \text{ odd}}^n x_i x_{i+1}$ is an example of bent function.
 
@@
 The $n$-variable \emph{Boolean symmetric functions} are those that are constant on each slice $\Ekn{k}{n}$ for $k\in [0,n]$. 
-This class has been assiduously studied in the context of cryptography, see \eg \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
-In this paper we mainly consider the slice indicator functions.
-
+This class has been assiduously studied in the context of cryptography, see \eg \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,IEEE:CheLu11,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
+In this article we mainly consider the slice indicator functions.
 %\begin{definition}[Elementary symmetric functions]
@@
 
-%We recall that bent functions are those Boolean functions achieving maximal nonlinearity.
+Bigger families of function can be obtained by considering functions of bounded degree on each slice, it corresponds to the concept of weightwise degree-$d$ function introduced in~\cite{DAM:GinMea22} for $d=1$ and~\cite{DAM:MeaOza24} for the general case.
 
-\pmnote{adapt usefull parts:
+\begin{definition}[Weightwise degree-$d$ functions (~\cite{DAM:MeaOza24} Definition 12)]\label{def:WdegD}
+	Let $n\in \N^*$ and for $k\in[0,n]$ $\phikn{k}{n}$ denotes the indicator function of $\Ekn{k}{n}$. 
+	An $n$-variable Boolean function $f$, written as $f=\sum_{k=0}^n f_k \phikn{k}{n}$, is called weightwise degree-$d$ if and only if for each $k\in [0,n]$ $f_k$ coincide with a function of degree at most $d$ over $\Ekn{k}{n}$.
+		The set of weightwise degree-$d$ functions is denoted by $\WD{d}{n}$.
+\end{definition}
 
-In~\cite{DAM:GinMea22} the authors study the relationship between weightwise perfectly balanced functions (functions balanced on all the slices, see for example~\cite{TOSC:CarMeaRot17,DCC:LiuMes19,CC:TangLiu19,BFA:MesSuLi21,ACI:ManKuLar22,SSRN:ZLCQZ23,ASIACCS:YCL+23,LATIN:GinMea23}) and weightwise affine functions \ie weightwise degree-$1$ functions.
-In fact weightwise degree-$1$ and degree-$0$ functions have been studied for their cryptographic properties in many works, without the same formalism. 
-The weightwise constant functions ($\WD{0}{n}$) are the symmetric functions that have been extensively studied (\eg \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:CheLu11,A2C:CarMea19,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}).
-Thereafter, the hidden weight bit function introduced in~\cite{IEEE:Bryant91} is a weightwise degree-$1$ function, the one obtained by fixing $f_0=0$ and $f_k=x_k$ for $k \in [n]$. 
+Various weightwise affine functions (\ie belonging to $\WD{1}{n}$) have been exhibited such as in~\cite{TOSC:CarMeaRot17} where the bent functions in Propositions $1$ and $2$ are weightwise affine or in~\cite{DAM:GinMea22} to show than no weightwise perfectly balanced function is weightwise affine for $n\ge 8$.
+The most known example of weightwise affine function is the hidden weight bit function introduced in~\cite{IEEE:Bryant91}, the one obtained by fixing $f_0=0$ and $f_k=x_k$ for $k \in [n]$.
 The cryptographic properties of this function have been studied in~\cite{DAM:WCST14}, showing good algebraic properties for this function.
-In~\cite{TOSC:CarMeaRot17}, the bent functions in Propositions $1$ and $2$ are weightwise affine.}
 
-\pmnote{Introduce formally HWBF, and weightwise degree d functions}
 \begin{definition}[Hidden Weight Bit Function (HWBF)]\label{def:hwbf}
@@
 
-\begin{definition}[Weightwise degree-$d$ functions]\label{def:WdegD}
-	Let $n\in \N^*$ and for $k\in[0,n]$ $\phikn{k}{n}$ denotes the indicator function of $\Ekn{k}{n}$. 
-	An $n$-variable Boolean function $f$, written as $f=\sum_{k=0}^n f_k \phikn{k}{n}$, is called weightwise degree-$d$ if and only if for each $k\in [0,n]$ $f_k$ coincide with a function of degree at most $d$ over $\Ekn{k}{n}$.
-	%	Equivalently, $f$ is weightwise affine if and only if for each $k\in [0,n]$ $\NLk{k}(f)=0$.
+In~\cite{DAM:MeaOza24}, the parameters of different functions from $\WD{1}{n}$ and $\WD{2}{n}$ are studied experimentally for $n$ up to $20$ and lower bounds are given for the nonlinearity. 
+We summarize the known results on the cryptographic criteria of weightwise affine functions we will use in this article in the following property.
 
-	The set of weightwise degree-$d$ functions is denoted by $\WD{d}{n}$.
+\pmnote{complete the following prop, + references}
 
-	%	$f=\sum_{k=0}^n f_k \phikn{k}{n}$ is called weightwise affine if and only if for each $k\in [0,n]$ $f_k$ coincide with an affine function over $\Ekn{k}{n}$.
+\begin{property}[Cryptographic properties of functions from $\WD{1}{n}$ \label{prop:wwd1}]
+Let $n\in \N^*$, the following hold for functions in $\WD{1}{n}$.
+\begin{itemize}
+	\item Nonlinearity of majority functions.
+	\item Nonlinearity of HWBF.
+	\item Nonlinearity bound WWA.
+\end{itemize}
 
-\end{definition}
-
-\pmnote{add: properties of maj function, HWPF, and some WWL and WWQ}
-
-\pmnote{add the nonlinearity of Dickson's function}
+\end{property}
 
@@
 
-\section{Main section}
+\section{Revisited HWBF and balancedness}
 %\subsection{Restricted Walsh transform of $f$ in a recursive fashion}
 
-We study the function $f$ in an even number of variables $n$ defined as the following:
+In this part we formally define the revisited HWBF function $f$ and introduce a quantity that allows us to study its weightwise nonlinearity and balancedness.
+
+\begin{definition}[Revisited HWBF]\label{def:revHWBF}
+Let $n\in \N^*$, even, we call revisited HWBF and denote by $f$ the Boolean function defined as:
 \[f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k.\]
+\end{definition}
+
+%We study the function $f$ in an even number of variables $n$ defined as the following:
+%\[f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k.\]
 

### 2024-10-27 RevisedHiddenWeight.tex
modifications all Section 3

@@
-\def\anon{1} %% set to 1 for anonymous submissions, hides acknowledgements and author names
+\def\anon{0} %% set to 1 for anonymous submissions, hides acknowledgements and author names
 \def\full{1} %% set to 0 for springer proceedings
@@
 \begin{document}
-	\title{Draft: Notes on the revised Hidden weight function}
+	\title{Revisited hidden weight bit function}
 
-	\titlerunning{Notes on the revised Hidden weight function}
+	\titlerunning{Revisited Hidden weight bit function}
 \author{
-%		\mbox{Pierrick M\'eaux}\inst{1}
+	Pierrick M\'eaux\inst{1},
+	Tim Seuré\inst{1}, 
+	Deng Tang\inst{2}
+%	Pierrick M\'eaux\orcidID{0000-0001-5733-4341}\inst{1},
+%	Tim Seuré\inst{1}, 
+%	Deng Tang\orcidID{0000-0002-8373-9200}\inst{2}
 }
-
-	\authorrunning{ P. M\'eaux}
+\authorrunning{P. M\'eaux, T. Seuré, D. Tang}
 
 \institute{
-	Luxembourg university, Luxembourg\\
-%		\email{pierrick.meaux@uni.lu}		
+	University of Luxembourg, Luxembourg\\ \email{pierrick.meaux@uni.lu, tim.seure@uni.lu} 
+	%\and
+%		University of Luxembourg, Luxembourg\\ \email{pierrick.meaux@uni.lu}
+	\and
+	Shanghai Jiao Tong University, Shanghai, China.\\
+	\email{dengtang@sjtu.edu.cn}
 }
@@
 	Let $f\in \Bn{n}$, $S \subset \F_2^n$, its Walsh transform restricted to $S$ at $a \in \F_2^n$ is defined as:
-	\[  \wt{f,S} (a) := \sum_{x\in S} (-1)^{f(x)+ax}.\]
+	\[  \wt{f,S} (a) := \sum_{x\in S} (-1)^{f(x)+a \cdot x}.\]
 	For $S=\Ekn{k}{n}$ we denote $\wt{f,\Ekn{k}{n}} (a)$ by $\wtk{f}{k}(a)$.%, and for $a= 0_{n}$ we denote $\wtk{f}{k}(a)$ as $\wtk{f}{k}(0)$.
@@
 
-\begin{definition}[Weightwise degree-$d$ functions (~\cite{DAM:MeaOza24} Definition 12)]\label{def:WdegD}
+\begin{definition}[Weightwise degree-$d$ functions (~\cite{DAM:MeaOza24} Definition 12)]\label{def:wwdegd}
 	Let $n\in \N^*$ and for $k\in[0,n]$ $\phikn{k}{n}$ denotes the indicator function of $\Ekn{k}{n}$. 
@@
 
-In this part we formally define the revisited HWBF function $f$ and introduce a quantity that allows us to study its weightwise nonlinearity and balancedness.
+In this part we formally define the revisited HWBF function $f$ and introduce a quantity that allows us to study its balancedness and nonlinearity.
 
@@
 
-We study the restricted Walsh transform  of $f$ to bound its nonlinearity.
+Since $f$ is the sum of a quadratic function and a weightweise affine function, it is a weightwise quadratic function. 
+Using the formalism of Definition~\ref{def:wwdegd} $f$ is the WWQ function defined by:% $f_0=0$ and for $k\in [1,n]$ $f_k=x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$.
+\[f_0=0, \quad \text{ and } \quad \forall k \in [1,n], \, f_k= \sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}.\]
 
-\begin{align*}
-\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}\\
-&=\sum_{x \in \Ekn{k}{n}} (-1)^{x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}+ ax}\\
-&=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ (c)x},
-\end{align*}
-where $c$ is the $n$-length binary vector such that $c=a+e_k+\sum_{i=n/2+1}^n e_i$ where the $e_i$ denotes the canonical vector with "1" in position $i$.
+This form allows to derive the restricted Walsh transform of $f$, which can be a useful tool to study the balancedness and bound the nonlinearity of a function.
+%Maybe add examples, such as OM24, M24
+
+%We study the restricted Walsh transform  of $f$ to bound its nonlinearity.
+\begin{proposition}\label{prop:restrWT}
+Let $n \in \N^*$ even, and $f$ be the function from Definition~\ref{def:revHWBF}, for all $k\in [0,n]$ its restricted Walsh transform in $a\in \F_2^n$ is given by:
+\[\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x},\]
+where $c$ is the $n$-length binary vector such that $c=a+e_k+\sum_{i=n/2+1}^n e_i$ where the $e_i$ denotes the canonical vector with $1$ in position $i$.
+\end{proposition}
+\begin{proof}
+%\begin{align*}
+%	\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+a \cdot x}
+%	=\sum_{x \in \Ekn{k}{n}} (-1)^{x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}+ a \cdot x}\\
+%	&=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x},
+%\end{align*}
+%\begin{align*}
+\[	\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+a \cdot x}
+	=\sum_{x \in \Ekn{k}{n}} (-1)^{x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}+ a \cdot x}\\
+	=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x},\]
+where $c$ denotes the $n$-length binary vector such that $c=a+e_k+\sum_{i=n/2+1}^n e_i$ and $e_i$ denotes the $i$-th canonical vector.
+\end{proof}
+
+%\begin{align*}
+%\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}\\
+%&=\sum_{x \in \Ekn{k}{n}} (-1)^{x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}+ ax}\\
+%&=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ (c)x},
+%\end{align*}
+%where $c$ is the $n$-length binary vector such that $c=a+e_k+\sum_{i=n/2+1}^n e_i$ where the $e_i$ denotes the canonical vector with "1" in position $i$.
 
@@
 Let $n\in \N$ be an even number, and $a\in \F_2^n$. We denote $d_n$ the function given by: $d_n(x)=\sum_{i \text{ odd}}^n x_i x_{i+1}$, 
-and we denote by $\Dnka{n}{k}{a}$:
+and we denote by $\Dnka{n}{k}{a}$ the quantity:
 \[\Dnka{n}{k}{a}= \sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a x}\]
 \end{definition}
-The limit case of $n=0$ yields that $\Dnka 0ka=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise.
 
-With these notations we obtain a recursive relation for $\Dnka{n}{k}{a}$, and therefore for $\wtk{f}{k}(a)$, denoting $b=(a_1,\cdots,a_{n-2})$ and $y=(x_1,\cdots,x_{n-2})$, we get for any even $n\geq 2$:
+We can give a recursive relation for $\Dnka{n}{k}{a}$.
+
+\begin{proposition}\label{prop:recursiveDnka}
+Let $n\in \N$ be an even number, $k$ an integer in the range $[0,n]$ and $a\in \F_2^n$. the Following holds on $\Dnka{n}{k}{a}$:
+\begin{itemize}
+	\item For $n=0$, $\Dnka{0}{k}{a}=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise.
+	\item if $n\ge 2$, denoting  $b=(a_1,\cdots,a_{n-2})$ and $y=(x_1,\cdots,x_{n-2})$, we get:
+	\[\Dnka{n}{k}{a}=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.\]
+\end{itemize}
+
+\end{proposition}
+
+\begin{proof}
+For $n\ge 2$ we can rewrite $\Dnka{n}{k}{a}$:
 
@@
 
-Then it gives three cases:
+The limit cases $\Dnka 0ka=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise are obtained from the values of $\Dnka{2}{k}{a}$ given in Table~\ref{tab:Dnka}.
+\end{proof}
+
+%The limit case of $n=0$ yields that $\Dnka 0ka=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise.
+
+%With these notations we obtain a recursive relation for $\Dnka{n}{k}{a}$, and therefore for $\wtk{f}{k}(a)$, denoting $b=(a_1,\cdots,a_{n-2})$ and $y=(x_1,\cdots,x_{n-2})$, we get for any even $n\geq 2$:
+
+We remark that it gives three different cases depending on the values of the two last elements of $a$:%Then it gives three cases:
 \begin{itemize}
@@
 
-In this analysis we considered the different cases depending on the values of $a_{n-1}$ and $a_n$, but the same reasoning applies with any $a_i, a_{i+1}$ where $i$ is odd. 
-Thereafter, the value of $\Dnka{n}{k}{a}$ depends only on the number of pairs of $a$ being $(0,0)$, $(1,1)$ or $(0,1)$ or $(1,0)$, and the values $\Dnka{2}{k}{a}$ for $k \in [0,2]$ and $a\in \{ (0,0),(1,1),(0,1)\}$.
+%In this analysis we considered the different cases depending on the values of $a_{n-1}$ and $a_n$, but the same reasoning applies with any $a_i, a_{i+1}$ where $i$ is odd.
 
-The first values of $\Dnka{2}{k}{a}$ are listed in Table~\ref{tab:Dnka}
+The recursive formula of Proposition~\ref{prop:recursiveDnka} gives different cases depending on the values of $a_{n-1}$ and $a_n$, however the same reasoning applies with any $a_i, a_{i+1}$ where $i$ is odd.
+Thereafter, the value of $\Dnka{n}{k}{a}$ depends only on the number of pairs of $a$ being $(0,0)$, $(1,1)$ or $(0,1)$ or $(1,0)$, and the values $\Dnka{2}{k}{a}$ for $k \in [0,2]$ and $a \in \{ (0,0),(1,1),(0,1)\}$.
+We give the first values of $\Dnka{2}{k}{a}$ in Table~\ref{tab:Dnka},  these values and Proposition~\ref{prop:recursiveDnka} are sufficient to determine any $\Dnka{n}{k}{a}$. 
+In the following, we show how the Walsh transform of $f$ can be written in terms of $\Dnka{n}{k}{a}$.
+Then, in Section~\ref{sec:balancedness} we use Proposition~\ref{prop:recursiveDnka} to determine the balancedness of $f$, and in Section~\ref{sec:genfunc} we study the value of $\Dnka{n}{k}{a}$ using trough generating functions.
+
+%The first values of $\Dnka{2}{k}{a}$ are listed in Table~\ref{tab:Dnka}
 
@@
 
-The restricted Walsh transform of $f$ can the be written as \begin{align*}
-\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ (c)x}\\
-&=\Dnka{n}{k}{d},
-\end{align*}
+Then, we can express the restricted Walsh transform of $f$ in terms of $\Dnka{n}{k}{a}$:
+
+\begin{proposition}[Walsh transform of $f$]\label{prop:WT}
+	Let $n \in \N^*$ even, and $f$ be the function from Definition~\ref{def:revHWBF}, for all $a\in \F_2^n$ its Walsh transform is given by:
+	\[ \wt{f}(a)=1+\sum_{k=1}^n \Dnka{n}{k}{b+\pi(e_k)},\]
+where $\pi$ is the permutation sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions, and $b=\pi(a)+(0,1,0,1,\ldots,0,1)$.
+\end{proposition}
+
+\begin{proof}
+Using Proposition~\ref{prop:restrWT}, the restricted Walsh transform of $f$ can the be written as \[
+\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x}=\Dnka{n}{k}{d},\]
 where $d$ is the permutation of $c$ obtained by sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions.
-Calling $\pi$ this permutation we can write $d=\pi(a)+ \pi(e_k)+ (0,1,0,1,\ldots,0,1)$.
+
+Calling $\pi$ this permutation, since $c=a+e_k+\sum_{i=n/2+1}^n e_i$, we can write $d=\pi(c)=\pi(a)+ \pi(e_k)+ (0,1,0,1,\ldots,0,1)$. 
 Accordingly, if $k\le n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2+1$, with one couple of consecutive elements (the first one with an odd index) being $(1,1)$ and all the others $(0,1)$.
@@
 Denoting by $b$ the vector $\pi(a)+(0,1,0,1,\ldots,0,1)$, we can write the Walsh transform of $f$ in $a$ as:
-\begin{equation}\label{eqn:walsh_from_D}
-    \wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}.
-\end{equation}
+\[ \wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}.\]
+\end{proof}
 
-In particular, for $a=0_n$ we can study the balancedness of $f$:
-\begin{align*}
-\wt{f}(0_n)&=\sum_{k=0}^n\Dnka{n}{k}{(0,1,0,1,\ldots,0,1)+\pi(e_k)}\\
-&=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}
-\end{align*}
-Using the recursive relation we obtain:
+\subsection{Balancedness of $f$}\label{sec:balancedness}
+
+In this part we determine for which values of $n$ the function $f$ is balanced, using the expression of its Walsh transform in terms of $\Dnka{n}{k}{a}$ and the recursive relation of these quantities.
+
+\begin{theorem}[Balancedness of $f$]
+	Let $n \in \N^*$ even, and $f$ be the $n$-variable function from Definition~\ref{def:revHWBF}, the following holds on its Walsh transform in $0_n$:
+	\[\wt{f}(0_n)= \left \{
+	\begin{array}{l l}
+	0 & \text{ if } n/2 \text{ is even, } \\
+	-2 \binom{n/2-1}{(n-2)/4} & \text{ if }  n/2 \text{ is odd.}
+	\end{array}\right.\]
+
+	Accordingly, $f$ is balanced when $n \equiv 0\mod 4$ and unbalanced when $n\equiv 2 \mod 4$.
+
+\end{theorem}
+
+\begin{proof}
+We use the expression of the Walsh transform of $f$ from Proposition~\ref{prop:WT}:
+%In particular, for $a=0_n$ we can study the balancedness of $f$:
+%\begin{align*}
+%\wt{f}(0_n)&=\sum_{k=0}^n\Dnka{n}{k}{(0,1,0,1,\ldots,0,1)+\pi(e_k)}\\
+%&=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}
+%\end{align*}
+\[\wt{f}(0_n)=\sum_{k=0}^n\Dnka{n}{k}{(0,1,0,1,\ldots,0,1)+\pi(e_k)}=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}\]
+Using the recursive relation from Proposition~\ref{prop:recursiveDnka} we obtain:
 \begin{align*}
@@
 Combining both we obtain:
+%\begin{align*}
+%\wt{f}(0_n)&=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}\\
+%&=\sum_{k=0}^{n/2} \left(\binom{n/2-1}{k/2} -2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1} \right)\\
+%&\qquad+ \sum_{k=\frac{n}{2}+1}^{n}   \left(  \binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1} \right)\\
+%&=\sum_{k=0}^{n}\left( \binom{n/2-1}{k/2} - \binom{n/2-1}{k/2-1}\right) 
+%+ 2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{n/2-1}{(k-1)/2} - \sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right)\\
+%&=2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{n/2-1}{(k-1)/2} - \sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right)\\
+%&=2 \left( \sum_{i=\lceil n/4 \rceil}^{n/2-1} \binom {n/2-1}{i} - \sum_{i=0}^{\lfloor(n-2)/4 \rfloor} \binom{n/2-1}{i}\right).\\
+%\end{align*}
 \begin{align*}
 \wt{f}(0_n)&=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}\\
-&=\sum_{k=0}^{n/2} \left(\binom{n/2-1}{k/2} -2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1} \right)\\
-&\qquad+ \sum_{k=\frac{n}{2}+1}^{n}   \left(  \binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1} \right)\\
-&=\sum_{k=0}^{n}\left( \binom{n/2-1}{k/2} - \binom{n/2-1}{k/2-1}\right) 
-+ 2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{n/2-1}{(k-1)/2} - \sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right)\\
-&=2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{n/2-1}{(k-1)/2} - \sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right)\\
-&=2 \left( \sum_{i=\lceil n/4 \rceil}^{n/2-1} \binom {n/2-1}{i} - \sum_{i=0}^{\lfloor(n-2)/4 \rfloor} \binom{n/2-1}{i}\right).\\
+&=\sum_{k=0}^{\frac{n}{2}} \left(\binom{\frac{n}{2}-1}{\frac{k}{2}} -2 \binom{\frac{n}{2}-1}{\frac{k-1}{2}} - \binom{\frac{n}{2}-1}{\frac{k}{2}-1} \right)+ \sum_{k=\frac{n}{2}+1}^{n}   \left(  \binom{\frac{n}{2}-1}{\frac{k}{2}} +2 \binom{\frac{n}{2}-1}{\frac{k-1}{2}} - \binom{\frac{n}{2}-1}{\frac{k}{2}-1} \right)\\
+&=\sum_{k=0}^{n}\left( \binom{\frac{n}{2}-1}{\frac{k}{2}} - \binom{\frac{n}{2}-1}{\frac{k}{2}-1}\right) 
++ 2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{\frac{n}{2}-1}{\frac{k-1}{2}} - \sum_{k=0}^{\frac{n}{2}} \binom{\frac{n}{2}-1}{\frac{k-1}{2}}\right)\\
+&=2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{\frac{n}{2}-1}{\frac{k-1}{2}} - \sum_{k=0}^{n/2} \binom{\frac{n}{2}-1}{\frac{k-1}{2}}\right)
+=2 \left( \sum_{i=\lceil \frac{n}{4} \rceil}^{\frac{n}{2}-1} \binom {\frac{n}{2}-1}{i} - \sum_{i=0}^{\lfloor\frac{n-2}{4}\rfloor} \binom{\frac{n}{2}-1}{i}\right).\\
 \end{align*}
-
-Then, depending on the parity of $n/2$ we obtain the value of $\wt{f}(0_n)$ (using that $\binom{n}{k}=\binom{n}{n-k}$):
+Then, depending on the parity of $\frac{n}{2}$ we obtain the value of $\wt{f}(0_n)$ (using that $\binom{n}{k}=\binom{n}{n-k}$):
 	\[\wt{f}(0_n)= \left \{
 \begin{array}{l l}
-0 & \text{ if } n/2 \text{ is even, } \\
--2 \binom{n/2-1}{(n-2)/4} & \text{ if }  n/2 \text{ is odd.}
+0 & \text{ if } \frac{n}{2} \text{ is even, } \\
+-2 \binom{\frac{n}{2}-1}{\frac{n-2}{4}} & \text{ if }  \frac{n}{2} \text{ is odd.}
 \end{array}\right.\]
@@
 Accordingly, $f$ is balanced when $n \equiv 0\mod 4$ and unbalanced when $n\equiv 2 \mod 4$.
+\end{proof}
 
-\subsection{Study of $\Dnka nka$ through Generating Functions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Extensive study of $\Dnka nka$ and bounds on the Walsh spectrum of $f$}
+
+\subsection{Study of $\Dnka nka$ through Generating Functions}\label{sec:genfunc}
 For $a\in\F_2^n$, denote by $p=p(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(0,0)$, by $q=q(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(1,1)$, and by $r=r(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})\in\{(0,1),(1,0)\}$.
@@
 
+\subsection{Generalization}
+
+\begin{definition}
+	Let $n\in \N$ be an even number and $t \in \N $ no greater than $n/2$, we denote by $d_{t,n}$ the function given by: $d_{t,n}(x)=\sum_{i=1}^t x_{2i-1} x_{2i}$.
+
+	%	by $\Dnka{n}{k}{a}$:
+	%	\[\Dnka{n}{k}{a}= \sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a x}\]
+\end{definition}
+
+In particular, $d_{n/2,n}(x)=d_n(x)$.
+
+We focus on the Walsh spectrum restricted to the slices of any function $d_{t,n}$
+
+\begin{proposition}\label{proposition:dtn}
+	Let $t, n\in \N$ with $n$ even and $t\le n/2$, the following holds on $d_{t,n}$ for all $k\in [0,n]$:
+	\[\wtk{d_{t,n}}{k}(a)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t},\]
+	where $b$ denotes the first $2t$ elements of $a$ and $c$ the last $n-2t$ elements.
+\end{proposition}
+\begin{proof}
+	We rewrite the restricted Walsh transform, denoting $x\in \F_2^n$ by $(y,z)$ where $y\in \F_2^{2t}$ and $z \in \F_2^{n-2t}$, and similarly denoting $a$ by $(b,c)$:
+
+	\begin{align*}
+	\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,t}(y)+by +cz}\\
+	&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,t}(y)+by +cz}\\
+	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,t}(y)+by} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{cz}\right)\\
+	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
+	\end{align*}	
+\end{proof}
+
+This leads to the following generating function:
+
+\begin{proposition}
+    Let $t, n\in \N$ with $n$ even and $t\le n/2$. Let $a=(b,c)\in\F_2^n$ with $b\in\F_2^{2t}$. Denote $n-2t-\w(c)$ and $\w(c)$ by $u$ and $v$, respectively. Then the following holds:
+    \[
+        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.
+    \]
+\end{proposition}
+
+\begin{proof}
+    Applying Proposition \ref{proposition:dtn}, we get:
+    \begin{align*}
+        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k&=\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\sum_{k\in\Z}\kraw{k-\ell}{\w(c)}{n-2t}z^{k-\ell}\\
+        &=\left(\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\right)\cdot(1+z)^u\cdot(1-z)^v\\
+        &=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.\qedhere
+    \end{align*}
+\end{proof}
+
+Consequently, we get a generalization of Theorem \ref{theorem:bound_D_nka}:
+
+\begin{theorem}
+    Let $t, n\in \N$ with $n$ even and $t\le n/2$. For every $a\in\F_2^n$, it holds that:
+    \[
+        |\wtk{d_{t,n}}{k}(a)|\leq 2^{n-t/2}.
+    \]
+\end{theorem}
+
+\begin{proof}
+    By applying Property \ref{property:cauchy_estimate}, we get that a bound on $|\wtk{d_{t,n}}{k}(a)|$ is given by the maximum $M'$ on the circle $|z|=1$ of $|P_b(z)|\cdot|(1+z)^u\cdot(1-z)^v|$.
+As previously established, $|P_b(z)|$ is bounded on $|z|=1$ by $(2\sqrt 2)^t=2^{3t/2}$, and $|(1+z)^u\cdot(1-z)^v|$ is bounded on $|z|=1$ by $2^{u+v}=2^{n-2t}$.
+Therefore, we conclude that $M'$ is bounded by $2^{3t/2}2^{n-2t}=2^{n-t/2}$, and hence this is also a bound for $|\wtk{d_{t,n}}{k}(a)|$.
+\end{proof}
+
+\begin{Corollary}
+    For every $a\in\F_2^n$, the following holds:
+    \[
+        |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{n-t/2}.
+    \]
+\end{Corollary}
+
+\begin{proof}
+    Analogous to the proof of Corollary \ref{cor:bound_walsh_cauchy}.
+\end{proof}
+
+\section{Experiments and comparisons}
+
 \subsection{Bounding the Walsh transform of $f$ experimentally}
@@
 
-This method is based on the identity (\ref{eqn:walsh_from_D}).
+%This method is based on the identity (\ref{eqn:walsh_from_D}). 
+This method is based on the identity given in Proposition~\ref{prop:WT}.
 For this, consider a vector $b\in\mathbb F_2^n$; we write $(p,q,r)=(p(b),q(b),r(b))$.
@@
 
-\subsection{Generalization}
-
-\begin{definition}
-	Let $n\in \N$ be an even number and $t \in \N $ no greater than $n/2$, we denote by $d_{t,n}$ the function given by: $d_{t,n}(x)=\sum_{i=1}^t x_{2i-1} x_{2i}$.
-
-	%	by $\Dnka{n}{k}{a}$:
-	%	\[\Dnka{n}{k}{a}= \sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a x}\]
-\end{definition}
-
-In particular, $d_{n/2,n}(x)=d_n(x)$.
-
-We focus on the Walsh spectrum restricted to the slices of any function $d_{t,n}$
-
-\begin{proposition}\label{proposition:dtn}
-	Let $t, n\in \N$ with $n$ even and $t\le n/2$, the following holds on $d_{t,n}$ for all $k\in [0,n]$:
-	\[\wtk{d_{t,n}}{k}(a)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t},\]
-	where $b$ denotes the first $2t$ elements of $a$ and $c$ the last $n-2t$ elements.
-\end{proposition}
-\begin{proof}
-	We rewrite the restricted Walsh transform, denoting $x\in \F_2^n$ by $(y,z)$ where $y\in \F_2^{2t}$ and $z \in \F_2^{n-2t}$, and similarly denoting $a$ by $(b,c)$:
-
-	\begin{align*}
-	\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,t}(y)+by +cz}\\
-	&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,t}(y)+by +cz}\\
-	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,t}(y)+by} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{cz}\right)\\
-	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
-	\end{align*}	
-\end{proof}
-
-This leads to the following generating function:
-
-\begin{proposition}
-    Let $t, n\in \N$ with $n$ even and $t\le n/2$. Let $a=(b,c)\in\F_2^n$ with $b\in\F_2^{2t}$. Denote $n-2t-\w(c)$ and $\w(c)$ by $u$ and $v$, respectively. Then the following holds:
-    \[
-        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.
-    \]
-\end{proposition}
-
-\begin{proof}
-    Applying Proposition \ref{proposition:dtn}, we get:
-    \begin{align*}
-        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k&=\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\sum_{k\in\Z}\kraw{k-\ell}{\w(c)}{n-2t}z^{k-\ell}\\
-        &=\left(\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\right)\cdot(1+z)^u\cdot(1-z)^v\\
-        &=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.\qedhere
-    \end{align*}
-\end{proof}
-
-Consequently, we get a generalization of Theorem \ref{theorem:bound_D_nka}:
-
-\begin{theorem}
-    Let $t, n\in \N$ with $n$ even and $t\le n/2$. For every $a\in\F_2^n$, it holds that:
-    \[
-        |\wtk{d_{t,n}}{k}(a)|\leq 2^{n-t/2}.
-    \]
-\end{theorem}
-
-\begin{proof}
-    By applying Property \ref{property:cauchy_estimate}, we get that a bound on $|\wtk{d_{t,n}}{k}(a)|$ is given by the maximum $M'$ on the circle $|z|=1$ of $|P_b(z)|\cdot|(1+z)^u\cdot(1-z)^v|$.
-As previously established, $|P_b(z)|$ is bounded on $|z|=1$ by $(2\sqrt 2)^t=2^{3t/2}$, and $|(1+z)^u\cdot(1-z)^v|$ is bounded on $|z|=1$ by $2^{u+v}=2^{n-2t}$.
-Therefore, we conclude that $M'$ is bounded by $2^{3t/2}2^{n-2t}=2^{n-t/2}$, and hence this is also a bound for $|\wtk{d_{t,n}}{k}(a)|$.
-\end{proof}
-
-\begin{Corollary}
-    For every $a\in\F_2^n$, the following holds:
-    \[
-        |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{n-t/2}.
-    \]
-\end{Corollary}
-
-\begin{proof}
-    Analogous to the proof of Corollary \ref{cor:bound_walsh_cauchy}.
-\end{proof}
-
+\section{Other parameters}
 \subsection{Algebraic immunity of $f$}

### 2024-10-29 RevisedHiddenWeight.tex
Minor changes
Added special case t = n/3

@@
 Using the formalism of Definition~\ref{def:wwdegd} $f$ is the WWQ function defined by:% $f_0=0$ and for $k\in [1,n]$ $f_k=x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$.
-\[f_0=0, \quad \text{ and } \quad \forall k \in [1,n], \, f_k= \sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}.\]
+\[f_0=0, \quad \text{ and } \quad \forall k \in [1,n], \, f_k=x_k+\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}.\]
 
@@
 \begin{proof}
-Using Proposition~\ref{prop:restrWT}, the restricted Walsh transform of $f$ can the be written as \[
+Using Proposition~\ref{prop:restrWT}, the restricted Walsh transform of $f$ can then be written as \[
 \wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x}=\Dnka{n}{k}{d},\]
@@
 \subsection{Study of $\Dnka nka$ through Generating Functions}\label{sec:genfunc}
+
+\begin{definition}\label{defi:P_a}
     For $a\in\F_2^n$, denote by $p=p(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(0,0)$, by $q=q(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(1,1)$, and by $r=r(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})\in\{(0,1),(1,0)\}$.
@@
     \]
+\end{definition}
 
@@
 
-This leads to the following generating function:
+\begin{definition}\label{defi:P_a_t}
+    Let $t, n\in \N$ with $n$ even and $t\le n/2$.
+Given $a=(b,c)\in\F_2^n$ with $b\in\F_2^{2t}$, denote $n-2t-\w(c)$ and $\w(c)$ by $u$ and $v$, respectively.
+We  then introduce the following polynomial:
+    \[
+        P_{a,t}(z)=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.
+    \]
+\end{definition}
 
 \begin{proposition}
-    Let $t, n\in \N$ with $n$ even and $t\le n/2$. Let $a=(b,c)\in\F_2^n$ with $b\in\F_2^{2t}$. Denote $n-2t-\w(c)$ and $\w(c)$ by $u$ and $v$, respectively. Then the following holds:
+    Let $t, n\in \N$ with $n$ even and $t\le n/2$. Let $a\in\F_2^n$. The following holds true: 
     \[
-        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.
+        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k=P_{a,t}(z).
     \]
@@
         &=\left(\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\right)\cdot(1+z)^u\cdot(1-z)^v\\
-        &=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.\qedhere
+        &=P_b(z)\cdot(1+z)^u\cdot(1-z)^v\\
+        &=P_{a,t}(z).\qedhere
     \end{align*}
@@
 
-\begin{theorem}
-    Let $t, n\in \N$ with $n$ even and $t\le n/2$. For every $a\in\F_2^n$, it holds that:
+\begin{theorem}\label{theorem:bound_D_nka_generalized}
+    Let $t, n\in \N$ with $n$ even and $t\le n/2$. For every $a\in\F_2^n$ and every $k\in[0,n]$, it holds that:
     \[
@@
 \begin{Corollary}
-    For every $a\in\F_2^n$, the following holds:
+    Let $t, n\in \N$ with $n$ even and $t\le n/2$. For every $a\in\F_2^n$, the following holds:
     \[
@@
     Analogous to the proof of Corollary \ref{cor:bound_walsh_cauchy}.
+\end{proof}
+
+When one is given an explicit value for $t$ in terms of $n$, one can be more careful when employing the proof strategy of Theorem~\ref{theorem:bound_D_nka_generalized}.
+Let us for instance consider the case $t=n/3$:
+
+\begin{proposition}
+    Let $n\in\N$ be divisible by $6$. Then for every $a\in\F_2^n$ and every $k\in[0,n]$, it holds that:
+    \[
+        |\wtk{d_{n/3,n}}{k}(a)|\leq2^{3n/4},\quad|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}.
+    \]
+\end{proposition}
+
+\begin{proof}
+    As before, we want to bound the maximum of $|P_{a,t}(z)|$ on $|z|=1$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[0,n]$.
+Write $a=(b,c)$ with $b\in\F_2^{2t}$ and let $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}.
+Since we want to find a bound of $|P_{a,t}(z)|$ on $|z|=1$ which works for all $a\in\F_2^n$, it makes sense to only consider those $a$ which are actually candidates for maximizing $|P_{a,t}(z)|$, namely those for which only one among $(p,q,r)$ is non-zero, and for which only one among $(u,v)$ is non-zero.
+This leaves us with the following cases to consider for $(p,q,r;u,v)$:
+    \begin{gather*}
+        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0),\\
+         (t,0,0;0,n-2t),\quad(0,t,0;0,n-2t),\quad(0,0,t;0,n-2t).
+    \end{gather*}
+    Since swapping both $(p,q)$ and $(u,v)$ has the same effect as replacing $z$ by $-z$ in $P_{a,t}(z)$ and therefore does not change the maximum of $|P_{a,t}(z)|$ on $|z|=1$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
+    \[
+        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0).
+    \]
+    Let us for instance find an upper bound of $|P_{a,t}(z)|$ in case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $n-2t=t$ by assumption, we get:
+    \[
+        P_{a,t}(z)=[(-z^2+2z+1)(1+z)]^t.
+    \]
+    Writing $z=\cos\alpha+\mathrm i\sin\alpha$, we obtain:
+    \[
+        |P_{a,t}(z)|^2=[(6-2\cos2\alpha)(2+2\cos\alpha)]^t.
+    \]
+    Through calculus, one finds that $|(6-2\cos2\alpha)(2+2\cos\alpha)|<2^{9/2}$, and hence that $|P_{a,t}(z)|<2^{9t/4}=2^{3n/4}$.
+The same upper bound works for the remaining two candidates for $(p,q,r;u,v)$, and we can therefore conclude that $|\wtk{d_{n/3,n}}{k}(a)|\leq 2^{3n/4}$ and that $|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}$.
 \end{proof}

### 2024-10-29 RevisedHiddenWeight.tex
Added more bounds for different t

@@
 %\end{definition}
-\begin{definition}[Nonlinearity %and weightwise nonlinearity
-	] \label{def:nl}
+\begin{definition}[Nonlinearity]%and weightwise nonlinearity
+	\label{def:nl}
 	The nonlinearity $\NL(f)$ of a Boolean function $f\in \BN$, where $n$ is a positive integer, is the minimum Hamming distance between $f$ and all the affine functions in $\BN$:
@@
     \[
-        \left|\frac{\dd^k}{\dd^k z}f(w)\right|\leq\frac{k!\cdot M_R}{R^k},
+        \left|\frac{\dd^k}{\dd^k z}f(z)\vert_{z=w}\right|\leq\frac{k!\cdot M_R}{R^k},
     \]
@@
 
-\begin{proposition}
+\begin{proposition}\label{proposition:walsh_t_over_3}
     Let $n\in\N$ be divisible by $6$. Then for every $a\in\F_2^n$ and every $k\in[0,n]$, it holds that:
@@
 \end{proof}
+
+\begin{remark}
+    The proof of Proposition~\ref{proposition:walsh_t_over_3} can be redone for other values of $t$.
+In Figure~\ref{fig:walsh_bounds_generalization}, we provide bounds of the form $\max_{a\in\F_2^n}|\wt{d_{\alpha n/40,n}}(a)|\leq 1+n\cdot 2^{\beta n}$, where $\alpha\in[0,20]$ is represented on the $x$-axis and $\beta$ is represented on the $y$-axis.
+\end{remark}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=9cm]{walsh_bounds_generalization.pdf}
+	\caption{For each point $(\alpha,\beta)$, we have $\max_{a\in\F_2^n}|\wt{d_{\alpha n/40,n}}(a)|\leq 1+n\cdot 2^{\beta n}$.}
+    \label{fig:walsh_bounds_generalization}
+\end{figure}
 

### 2024-10-29 RevisedHiddenWeight.tex
part 4.2

--- 2024-10-27 RevisedHiddenWeight.tex
@@
 
-\subsection{Study of $\Dnka nka$ through Generating Functions}\label{sec:genfunc}
-For $a\in\F_2^n$, denote by $p=p(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(0,0)$, by $q=q(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(1,1)$, and by $r=r(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})\in\{(0,1),(1,0)\}$.
+In this section, we study the values of $\Dnka nka$ using generating functions.
+First, in Section~\ref{sec:genfunc} we establish key properties of these quantities.
+Then, in Section~\ref{sec:Cauchy}, we apply Cauchy's estimate to bound the absolute values of $\Dnka nka$, which enables us to bound the absolute values of the Walsh transform coefficients of $f$ and consequently, the nonlinearity.
+Finally, in Section~\ref{sec:general}, we demonstrate how this result can be extended to bound the nonlinearity of a family of weightwise quadratic functions.
+
+\subsection{Study of $\Dnka nka$ through generating functions}\label{sec:genfunc}
+For $a\in\F_2^n$, we denote by $p=p(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(0,0)$, by $q=q(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(1,1)$, and by $r=r(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})\in\{(0,1),(1,0)\}$.
 We then have $p+q+r=n/2$.
-Consider further the integer polynomial $P_a(z)$ given by the following expression:
+We consider further the integer polynomial $P_a(z)$ given by the following expression:
 \[
@@
 \begin{proof}
-	Proceed by induction on even $n\geq 0$. 
-	For the base case $n=0$, for $a\in\F_2^0$, we have $P_a(z)=1$, while $\Dnka 0ka=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise. 
+	We proceed by induction on even $n\geq 0$. 
+	For the base case $n=0$, for $a\in\F_2^0$, we have $P_a(z)=1$, while $\Dnka 0ka=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise (from Proposition~\ref{prop:recursiveDnka}). 
 	For the inductive step, let $n\geq 2$ be even, and assume that the corresponding formula holds for $n-2$. Using the recursive formula for $\Dnka nka$ with the notation $a=(b,a_{n-1},a_n)$, we have:
@@
 	For every integer $k$, we have:
-	\[
-	\Dnka n{n-k}a=(-1)^{p+q+k}\Dnka nka.
-	\]
+	\[	\Dnka n{n-k}a=(-1)^{p+q+k}\Dnka nka.	\]
 \end{proposition}
@@
 \begin{proof}
-	Define the degree $n$ polynomial $Q_a(z)$ in such a way that the coefficient of $z^k$ in $Q_a(z)$ is equal to the coefficient of $z^{n-k}$ in $P_a(z)$. Then we have:
+	We define the reverse polynomial  $Q_a(z)$ such as the degree $n$ polynomial where each coefficient of $z^k$ in $Q_a(z)$ is equal to the coefficient of $z^{n-k}$ in $P_a(z)$. 
+	Then we have:
 	\begin{align*}
@@
 Another immediate case for zero coefficients is the following:
+
 \begin{proposition}
@@
 Thus, the coefficient $\Dnka nka$ of $z^k$ for odd $k$ must be zero in $P_a(z)$.
-It follows that also $\Dnka n{n-k}a=0$ by Proposition \ref{proposition:symmetry}.
+It follows that also $\Dnka n{n-k}a=0$ by Proposition~\ref{proposition:symmetry}.
 \end{proof}
@@
 \begin{remark}\label{remark:D_nka_differentiation}
-    We can also use Proposition \ref{proposition:generating_fct} to obtain $\Dnka nka$ through differentiation:
+    We can also use Proposition \ref{proposition:generating_fct} to obtain $\Dnka nka$ through differentiation and evaluation in $0$:
     \[
@@
     	\end{tabular}
-    	\caption{Values of $\Dnka{n}{k}{a}$ for small $k$}\label{tab:Dnka_small_k}
+    	\caption{Values of $\Dnka{n}{k}{a}$ for small values of $k$}\label{tab:Dnka_small_k}
     \end{table}
@@
 
-With this, we can get more cases in which $\Dnka nka=0$:
+From differentiation, we can get more cases in which $\Dnka nka=0$:
 
@@
 \begin{remark}
-    There are still instances where $\Dnka nka=0$ which have not been described by the above. For instance, we have $\Dnka{34}4a=0$ if $\{p,q\}=\{1,2\}$.
+    There are other instances where $\Dnka nka=0$ which have not been described by the above. For instance, we have $\Dnka{34}4a=0$ if $\{p,q\}=\{1,2\}$.
 \end{remark}
@@
         \item The sum and alternating sum over $k$ of the $\Dnka nka$ are, respectively:
-        \begin{gather*}
-            \sum_{k=0}^n\Dnka nka=(-1)^{q}2^{n/2},\\
+ %       \begin{gather*}
+ %           \sum_{k=0}^n\Dnka nka=(-1)^{q}2^{n/2},\\
+ %           \sum_{k=0}^n(-1)^k\Dnka nka=(-1)^{p}2^{n/2}.
+ %       \end{gather*}
+\[
+ \sum_{k=0}^n\Dnka nka=(-1)^{q}2^{n/2}, \quad \text{and} \quad
  \sum_{k=0}^n(-1)^k\Dnka nka=(-1)^{p}2^{n/2}.
-        \end{gather*}
+\]
         \item The sum over the even and the odd $k$ of the the $\Dnka nka$ are, respectively:
-        \begin{gather*}
-            \sum_{k=0}^{n/2}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big),\\
+ %       \begin{gather*}
+  %          \sum_{k=0}^{n/2}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big),\\
+   %         \sum_{k=0}^{n/2-1}\Dnka n{2k+1}a=2^{n/2-1}\big((-1)^{q}-(-1)^{p}\big).
+    %    \end{gather*}   
+\[
+\sum_{k=0}^{n/2}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big), \quad \text{ and } \quad 
 \sum_{k=0}^{n/2-1}\Dnka n{2k+1}a=2^{n/2-1}\big((-1)^{q}-(-1)^{p}\big).
-        \end{gather*}
+\]
+
     \end{enumerate}
@@
 
-\subsection{Bounding the Walsh transform of $f$ using the Cauchy estimate}
+\subsection{Bounding the Walsh transform of $f$ using the Cauchy estimate}\label{sec:Cauchy}
 
-Recall the Cauchy estimate on holomorphic functions:
+We recall Cauchy's estimate on holomorphic functions:
 
-\begin{Prop}[\cite{rudin1987}, Theorem 10.26]\label{property:cauchy_estimate}
+\begin{Prop}[Cauchy's estimate \eg~\cite{rudin1987}, Theorem 10.26]\label{property:cauchy_estimate}
     Let $w$ be a complex number, and let $R>0$ be some radius.
@@
 \end{Prop}
+
+\pmnote{I would recall between parentheses somewhere that we denote by $|.|$ the complex norm here, which corresponds to the absolute value on $\R$
+
+verify if $w$ and $z$ are coherent.
+}
 
@@
 \begin{proof}
-    Recall from Remark \ref{remark:D_nka_differentiation} that $k!\cdot\Dnka nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}$.
+    From Remark~\ref{remark:D_nka_differentiation} we have: $k!\cdot\Dnka nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}$.
 Choosing $f=P_a$, $w=0$ and $R=1$ in Property \ref{property:cauchy_estimate} then gives:
@@
     \]
-    where $M$ is the maximum of $|P_a(z)|$ on the circle $|z|=1$.
-We claim, and prove below, that the maximum of $\left|-z^2+2z+1\right|$ on $|z|=1$ is $2\sqrt 2$.
-This implies that the maximum of $\left|-z^2-2z+1\right|$ on $|z|=1$ is $2\sqrt 2$ as well.
-Since the maximum of $\left|z^2+1\right|$ on $|z|=1$ is $2<2\sqrt 2$, it follows that $|\Dnka nka|\leq M\leq (2\sqrt 2)^{p+q}2^r\leq (2\sqrt 2)^{n/2}$.
+    where $M$ is the maximum of $|P_a(z)|$ on the circle %$|z|=1$. 
+    $\dis=\{ z \in \C,  |z|=1  \}$
+    We claim, and prove below, that the maximum of $\left|-z^2+2z+1\right|$ on $\dis$ is $2\sqrt 2$. 
+    This implies that the maximum of $\left|-z^2-2z+1\right|$ on $\dis$ is $2\sqrt 2$ as well. 
+    Since the maximum of $\left|z^2+1\right|$ on $\dis$ is $2<2\sqrt 2$, it follows that $|\Dnka nka|\leq M\leq (2\sqrt 2)^{p+q}2^r\leq (2\sqrt 2)^{n/2}$.
 
-    It remains to prove that the maximum of $\left|-z^2+2z+1\right|^2$ on $|z|=1$ equals $8$. Using that $|w|^2=w\overline w$ for every complex number $w$, we obtain for $|z|=1$:
+	We prove that the maximum of $\left|-z^2+2z+1\right|$ on $\dis$ is $2\sqrt 2$ by showing that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ equals $8$.
+    %It remains to prove that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ equals $8$. 
+    Using that $|w|^2=w\overline w$ for every complex number $w$, we obtain for all $z\in \dis$:
     \[
@@
     where $\mathrm{Re}\left(z^2\right)$ denotes the real part of $z^2$.
-Since the minimum of $\mathrm{Re}\left(z^2\right)$ on $|z|=1$ is $-1$, we conclude that the maximum of $\left|-z^2+2z+1\right|^2$ on $|z|=1$ is $6-2(-1)=8$.
+Since the minimum of $\mathrm{Re}\left(z^2\right)$ on $|z|=1$ is $-1$, we conclude that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ is $6-2(-1)=8$.
+
 \end{proof}
@@
     \]
+Equivalently, 
+%$\NL(f)\ge 2^{n-1} - \frac{1 + n 2^{\frac{3}{4}n}} {2}$.
+$\NL(f)\ge 2^{n-1} - \frac{1}{2} -2^{\frac{3n}{4} + \log n -1}$.
 \end{Corollary}
@@
 \begin{proof}
-    We have previously established that $\wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}$. Then, applying Proposition \ref{theorem:bound_D_nka} yields:
+    We have previously established in Proposition~\ref{prop:WT} that $\wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}$. Then, applying Theorem~\ref{theorem:bound_D_nka} yields:
     \[
-        |\wt{f}(a)|\leq 1+\sum_{k=1}^n\left|\Dnka{n}{k}{b+\pi(e_k)}\right|\leq 1+ n\cdot 2^{3n/4}.\qedhere
+        |\wt{f}(a)|\leq 1+\sum_{k=1}^n\left|\Dnka{n}{k}{b+\pi(e_k)}\right|\leq 1+ n\cdot 2^{3n/4}.%\qedhere
     \]
+The bound on the nonlinearity comes from the second expression of Definition~\ref{def:nl}.
 \end{proof}
@@
 
-\subsection{Generalization}
+\subsection{Generalization to a family of weightwise quadratic functions}\label{sec:general}
 

### 2024-10-29 RevisedHiddenWeight.tex

@@
 
-\subsection{Study of $\Dnka nka$ through generating functions}\label{sec:genfunc}
-For $a\in\F_2^n$, we denote by $p=p(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(0,0)$, by $q=q(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(1,1)$, and by $r=r(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})\in\{(0,1),(1,0)\}$.
+\subsection{Study of $\Dnka nka$ through Generating Functions}\label{sec:genfunc}
+
+\begin{definition}\label{defi:P_a}
+    For $a\in\F_2^n$, denote by $p=p(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(0,0)$, by $q=q(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(1,1)$, and by $r=r(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})\in\{(0,1),(1,0)\}$.
 We then have $p+q+r=n/2$.
-We consider further the integer polynomial $P_a(z)$ given by the following expression:
+Consider further the integer polynomial $P_a(z)$ given by the following expression:
     \[
@@
 \end{proof}
+
+When one is given an explicit value for $t$ in terms of $n$, one can be more careful when employing the proof strategy of Theorem~\ref{theorem:bound_D_nka_generalized}.
+Let us for instance consider the case $t=n/3$:
+
+\begin{proposition}\label{proposition:walsh_t_over_3}
+    Let $n\in\N$ be divisible by $6$. Then for every $a\in\F_2^n$ and every $k\in[0,n]$, it holds that:
+    \[
+        |\wtk{d_{n/3,n}}{k}(a)|\leq2^{3n/4},\quad|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}.
+    \]
+\end{proposition}
+
+\begin{proof}
+    As before, we want to bound the maximum of $|P_{a,t}(z)|$ on $|z|=1$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[0,n]$.
+Write $a=(b,c)$ with $b\in\F_2^{2t}$ and let $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}.
+Since we want to find a bound of $|P_{a,t}(z)|$ on $|z|=1$ which works for all $a\in\F_2^n$, it makes sense to only consider those $a$ which are actually candidates for maximizing $|P_{a,t}(z)|$, namely those for which only one among $(p,q,r)$ is non-zero, and for which only one among $(u,v)$ is non-zero.
+This leaves us with the following cases to consider for $(p,q,r;u,v)$:
+    \begin{gather*}
+        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0),\\
+         (t,0,0;0,n-2t),\quad(0,t,0;0,n-2t),\quad(0,0,t;0,n-2t).
+    \end{gather*}
+    Since swapping both $(p,q)$ and $(u,v)$ has the same effect as replacing $z$ by $-z$ in $P_{a,t}(z)$ and therefore does not change the maximum of $|P_{a,t}(z)|$ on $|z|=1$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
+    \[
+        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0).
+    \]
+    Let us for instance find an upper bound of $|P_{a,t}(z)|$ in case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $n-2t=t$ by assumption, we get:
+    \[
+        P_{a,t}(z)=[(-z^2+2z+1)(1+z)]^t.
+    \]
+    Writing $z=\cos\alpha+\mathrm i\sin\alpha$, we obtain:
+    \[
+        |P_{a,t}(z)|^2=[(6-2\cos2\alpha)(2+2\cos\alpha)]^t.
+    \]
+    Through calculus, one finds that $|(6-2\cos2\alpha)(2+2\cos\alpha)|<2^{9/2}$, and hence that $|P_{a,t}(z)|<2^{9t/4}=2^{3n/4}$.
+The same upper bound works for the remaining two candidates for $(p,q,r;u,v)$, and we can therefore conclude that $|\wtk{d_{n/3,n}}{k}(a)|\leq 2^{3n/4}$ and that $|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}$.
+\end{proof}
+
+\begin{remark}
+    The proof of Proposition~\ref{proposition:walsh_t_over_3} can be redone for other values of $t$.
+In Figure~\ref{fig:walsh_bounds_generalization}, we provide bounds of the form $\max_{a\in\F_2^n}|\wt{d_{\alpha n/40,n}}(a)|\leq 1+n\cdot 2^{\beta n}$, where $\alpha\in[0,20]$ is represented on the $x$-axis and $\beta$ is represented on the $y$-axis.
+\end{remark}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=9cm]{walsh_bounds_generalization.pdf}
+	\caption{For each point $(\alpha,\beta)$, we have $\max_{a\in\F_2^n}|\wt{d_{\alpha n/40,n}}(a)|\leq 1+n\cdot 2^{\beta n}$.}
+    \label{fig:walsh_bounds_generalization}
+\end{figure}
 

### 2024-10-29 RevisedHiddenWeight.tex
part 4.3 with comments.

@@
 
-\begin{property}[Cryptographic properties of functions from $\WD{1}{n}$ \label{prop:wwd1}]
+\begin{Prop}[Cryptographic properties of functions from $\WD{1}{n}$ \label{prop:wwd1}]
 Let $n\in \N^*$, the following hold for functions in $\WD{1}{n}$.
@@
 
-\end{property}
+\end{Prop}
 
@@
     where $\mathrm{Re}\left(z^2\right)$ denotes the real part of $z^2$.
-Since the minimum of $\mathrm{Re}\left(z^2\right)$ on $|z|=1$ is $-1$, we conclude that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ is $6-2(-1)=8$.
+Since the minimum of $\mathrm{Re}\left(z^2\right)$ on $\dis$ is $-1$, we conclude that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ is $6-2(-1)=8$.
 
@@
 \subsection{Generalization to a family of weightwise quadratic functions}\label{sec:general}
+In this part, we generalize the results of Section~\ref{sec:Cauchy} to all weightwise quadratic function such that for all $k\in [1,n]$ $f_k$ has exactly $t$ quadratic terms with no shared variables.
 
 \begin{definition}
-	Let $n\in \N$ be an even number and $t \in \N $ no greater than $n/2$, we denote by $d_{t,n}$ the function given by: $d_{t,n}(x)=\sum_{i=1}^t x_{2i-1} x_{2i}$.
+	Let $n\in \N^*$ be an even number and $t \in \N $ no greater than $n/2$, we denote by $d_{t,n}$ the function given by: $d_{t,n}(x)=\sum_{i=1}^t x_{2i-1} x_{2i}$.
 
@@
 In particular, $d_{n/2,n}(x)=d_n(x)$. 
-
-We focus on the Walsh spectrum restricted to the slices of any function $d_{t,n}$
+We focus on the Walsh spectrum restricted to the slices of any function $d_{t,n}$:
 
@@
 
+%	\begin{align*}
+%	\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,t}(y)+by +cz}\\
+%	&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,t}(y)+by +cz}\\
+%	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,t}(y)+by} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{cz}\right)\\
+%	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.%\qedhere
+%	\end{align*}
+
 	\begin{align*}
-	\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,t}(y)+by +cz}\\
-	&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,t}(y)+by +cz}\\
-	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,t}(y)+by} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{cz}\right)\\
-	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
+\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
+&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,2t}(y)+b \cdot y} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c \cdot z}\right)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.%\qedhere
 \end{align*}
+
 \end{proof}
@@
 
-Consequently, we get a generalization of Theorem \ref{theorem:bound_D_nka}:
+Consequently, we get a generalization of Theorem~\ref{theorem:bound_D_nka}:
 
@@
 \begin{proof}
-    By applying Property \ref{property:cauchy_estimate}, we get that a bound on $|\wtk{d_{t,n}}{k}(a)|$ is given by the maximum $M'$ on the circle $|z|=1$ of $|P_b(z)|\cdot|(1+z)^u\cdot(1-z)^v|$.
-As previously established, $|P_b(z)|$ is bounded on $|z|=1$ by $(2\sqrt 2)^t=2^{3t/2}$, and $|(1+z)^u\cdot(1-z)^v|$ is bounded on $|z|=1$ by $2^{u+v}=2^{n-2t}$.
+    By applying Property \ref{property:cauchy_estimate}, we get that a bound on $|\wtk{d_{t,n}}{k}(a)|$ is given by the maximum $M'$ on the circle $\dis$ of $|P_b(z)|\cdot|(1+z)^u\cdot(1-z)^v|$. 
+    As previously established in Theorem~\ref{theorem:bound_D_nka}, $|P_b(z)|$ is bounded on $\dis$ by $(2\sqrt 2)^t=2^{3t/2}$, and $|(1+z)^u\cdot(1-z)^v|$ is bounded on $\dis$ by $2^{u+v}=2^{n-2t}$. 
     Therefore, we conclude that $M'$ is bounded by $2^{3t/2}2^{n-2t}=2^{n-t/2}$, and hence this is also a bound for $|\wtk{d_{t,n}}{k}(a)|$. 
@@
 
-\begin{Corollary}
+\begin{Corollary}\label{cor:gen}
     Let $t, n\in \N$ with $n$ even and $t\le n/2$. For every $a\in\F_2^n$, the following holds:
@@
 
-When one is given an explicit value for $t$ in terms of $n$, one can be more careful when employing the proof strategy of Theorem~\ref{theorem:bound_D_nka_generalized}.
-Let us for instance consider the case $t=n/3$:
+When a specific value of $t$ is given in terms of $n$, the proof strategy for Theorem~\ref{theorem:bound_D_nka_generalized} can be applied more precisely.
+For instance, we consider the case where $t = n/3$:
 
 \begin{proposition}\label{proposition:walsh_t_over_3}
-    Let $n\in\N$ be divisible by $6$. Then for every $a\in\F_2^n$ and every $k\in[0,n]$, it holds that:
-    \[
-        |\wtk{d_{n/3,n}}{k}(a)|\leq2^{3n/4},\quad|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}.
-    \]
-\end{proposition}
-
-\begin{proof}
-    As before, we want to bound the maximum of $|P_{a,t}(z)|$ on $|z|=1$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[0,n]$.
-Write $a=(b,c)$ with $b\in\F_2^{2t}$ and let $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}.
-Since we want to find a bound of $|P_{a,t}(z)|$ on $|z|=1$ which works for all $a\in\F_2^n$, it makes sense to only consider those $a$ which are actually candidates for maximizing $|P_{a,t}(z)|$, namely those for which only one among $(p,q,r)$ is non-zero, and for which only one among $(u,v)$ is non-zero.
+    Let $n\in\N^*$ be divisible by $6$. 
+    Then, for every $a\in\F_2^n$ and every $k\in[0,n]$, it holds that:
+    \[
+        |\wtk{d_{n/3,n}}{k}(a)|\leq2^{3n/4},\quad \text{and }\quad|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}.
+    \]
+\end{proposition}
+
+\begin{proof}
+    As before, we want to bound the maximum of $|P_{a,t}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[1,n]$. 
+    We write $a=(b,c)$ with $b\in\F_2^{2t}$ and define $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}.
+
+   To find a bound for $|P_{a,t}(z)|$ on $\dis$ that applies to all $a\in\F_2^n$, we focus only on values of $a$ which are candidates for maximizing $|P_{a,t}(z)|$. 
+   Specifically, we consider cases where only one of $(p,q,r)$ is non-zero, and for which only and only one of $(u,v)$ is non-zero.
+
+\pmnote{What is the argument: "maximum implies only one is non-zero" }
+
    This leaves us with the following cases to consider for $(p,q,r;u,v)$:
@@
     \end{gather*}
-    Since swapping both $(p,q)$ and $(u,v)$ has the same effect as replacing $z$ by $-z$ in $P_{a,t}(z)$ and therefore does not change the maximum of $|P_{a,t}(z)|$ on $|z|=1$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
+    Since swapping both $(p,q)$ and $(u,v)$ has the same effect as replacing $z$ by $-z$ in $P_{a,t}(z)$ and therefore does not change the maximum of $|P_{a,t}(z)|$ on $\dis$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
     \[
@@
     Writing $z=\cos\alpha+\mathrm i\sin\alpha$, we obtain:
+
+    \pmnote{@Tim, add intermediate computation in the following:}
     \[
@@
     \]
+    \pmnote{@Tim, for the following, by calculus, you mean using some software? In this case we can add a footnote saying in practice we did it with xxx.
+
+    Can you give a plot of $(\alpha,(6-2\cos2\alpha)(2+2\cos\alpha))$ and add the line corresponding to $y=9/4$?
+    }
+
     Through calculus, one finds that $|(6-2\cos2\alpha)(2+2\cos\alpha)|<2^{9/2}$, and hence that $|P_{a,t}(z)|<2^{9t/4}=2^{3n/4}$.
-The same upper bound works for the remaining two candidates for $(p,q,r;u,v)$, and we can therefore conclude that $|\wtk{d_{n/3,n}}{k}(a)|\leq 2^{3n/4}$ and that $|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}$.
-\end{proof}
+The same upper bound works for the remaining two candidates for $(p,q,r;u,v)$, and we can therefore conclude  $|\wtk{d_{n/3,n}}{k}(a)|\leq 2^{3n/4}$, and $|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}$.
+\end{proof}
+
+\pmnote{for the remark, add how they are obtained (from a script in xxx). 
+We can give the scripts in supplementary material when submitting, of add the link of a github if you agree to have them public.
+
+}
 
 \begin{remark}
-    The proof of Proposition~\ref{proposition:walsh_t_over_3} can be redone for other values of $t$.
+    The proof of Proposition~\ref{proposition:walsh_t_over_3} can be extended to other values of $t$. 
     In Figure~\ref{fig:walsh_bounds_generalization}, we provide bounds of the form $\max_{a\in\F_2^n}|\wt{d_{\alpha n/40,n}}(a)|\leq 1+n\cdot 2^{\beta n}$, where $\alpha\in[0,20]$ is represented on the $x$-axis and $\beta$ is represented on the $y$-axis.
@@
 	\includegraphics[width=9cm]{walsh_bounds_generalization.pdf}
-	\caption{For each point $(\alpha,\beta)$, we have $\max_{a\in\F_2^n}|\wt{d_{\alpha n/40,n}}(a)|\leq 1+n\cdot 2^{\beta n}$.}
+	\caption{Improvements on Corollary~\ref{cor:gen}. For each point $(\alpha,\beta)$, we have $\max_{a\in\F_2^n}|\wt{d_{\alpha n/40,n}}(a)|\leq 1+n\cdot 2^{\beta n}$.}
     \label{fig:walsh_bounds_generalization}

### 2024-10-29 RevisedHiddenWeight.tex
start modif 5

@@
 
-\subsection{Bounding the Walsh transform of $f$ experimentally}
+\subsection{Bounding the Walsh transform of $f$ experimentally}\label{sec:expwt}
 
@@
 
-Table \ref{table:max_walsh_vs_bound} compares $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ to the upper bound $B_n$ we find using the above method.
-Table \ref{table:walsh_bounds} gives all values of this bound $B_n$ for all even $1\leq n\leq 80$.
+\subsection{Comparison of the nonlinearity}
+
+\pmnote{under construction}
+
+In this part we compare the nonlinearity of the function $f$ from Definition~\ref{def:revHWBF} to other weightwise quadratic functions considered for similar use-cases, such as majority, HWBF and the cyclic weightwise quadratic function $t$  from~\cite{DAM:MeaOza24}.
+More precisely, we compare the value $\max_{a\in\mathbb F_2^n}|\wt f(a)|$, the smaller the maximum the better the nonlinearity. 
+For majority and HWBF, we use the exact values recalled in Property~\ref{prop:wwd1}, for the function $t$ we use the upper bound proven in~\cite{DAM:MeaOza24}. 
+For the revisited HWBF, we consider the theoretical bound from Theorem~\ref{cor:bound_walsh_cauchy} and the experimental one from Section~\ref{sec:expwt}
+
+Table~\ref{table:max_walsh_vs_bound} compares $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ to the upper bound $B_n$ we find using the above method.
+Table~\ref{table:walsh_bounds} gives all values of this bound $B_n$ for all even $1\leq n\leq 80$.
 
@@
 	\end{tabular}
-	\caption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ vs.\ our bound $B_n$}
+	\caption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ compared to the bound $B_n$}
 	\label{table:max_walsh_vs_bound}

### 2024-10-29 RevisedHiddenWeight.tex
git

@@
 This class has been assiduously studied in the context of cryptography, see \eg \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,IEEE:CheLu11,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
-In this article we mainly consider the slice indicator functions.
+In this article we mainly consider the slice indicator functions and the majority functions.
 %\begin{definition}[Elementary symmetric functions]
@@
  \[\forall  x\in \mathbb{F}_2^{n}, \quad \phikn{k}{n}(x) = 1 \text{ if and only if } \w(x) = k.\]
+\end{definition}
+
+\pmnote{add}
+\begin{definition}[Majority functions]\label{def:maj}
 \end{definition}
@@
 
-\pmnote{complete the following prop, + references}
-
-\begin{Prop}[Cryptographic properties of functions from $\WD{1}{n}$ \label{prop:wwd1}]
-Let $n\in \N^*$, the following hold for functions in $\WD{1}{n}$.
+\pmnote{complete the following prop. Choose between nonlinearity or $\max_{a\in\mathbb F_2^n}|\wt f(a)|$}
+
+\begin{Prop}[Cryptographic properties of functions from $\WD{2}{n}$ \label{prop:wwd1}]
+Let $n\in \N^*$ even, the following hold for functions in $\WD{2}{n}$. 
 \begin{itemize}
-	\item Nonlinearity of majority functions.
-	\item Nonlinearity of HWBF.
-	\item Nonlinearity bound WWA.
+	\item For the majority function
+
+	$\max_{a\in\mathbb F_2^n}|\wt f(a)|$ (adapt from Theorem 3 \cite{DCC:DalMaiSar06})
+	\item value for HWBF. (from~\cite{DAM:WCST14}))
+
+	\item  bound for the cyclic weightwise linear (adapt Theorem 1 of \cite{DAM:MeaOza24})
+	\item  bound for the cyclic weightwise quadratic function $t$  (adapt Theorem 2 of \cite{DAM:MeaOza24})
 \end{itemize}

### 2024-10-30 RevisedHiddenWeight.tex
Addressed (most of) Pierrick's wishes

@@
 
-\pmnote{add}
-\begin{definition}[Majority functions]\label{def:maj}
-\end{definition}
-
-Bigger families of function can be obtained by considering functions of bounded degree on each slice, it corresponds to the concept of weightwise degree-$d$ function introduced in~\cite{DAM:GinMea22} for $d=1$ and~\cite{DAM:MeaOza24} for the general case.
+\pmnote{\color{blue} Tim: Check below}
+\begin{definition}[Majority function]\label{def:maj}
+    The \emph{majority function} in $n$ variables is the Boolean function $f\in\BN$ defined as:
+    \[
+        f(x)=0\iff\w(x)\leq\frac n2.
+    \]
+\end{definition}
+
+Bigger families of functions can be obtained by considering functions of bounded degree on each slice, it corresponds to the concept of weightwise degree-$d$ function introduced in~\cite{DAM:GinMea22} for $d=1$ and~\cite{DAM:MeaOza24} for the general case.
 
@@
 \begin{definition}[Hidden Weight Bit Function (HWBF)]\label{def:hwbf}
-	Let $n\in \N^*$we call Hidden Weight Bit Function (HWBF) the $n$-variable Boolean function defined by:
+	For $n\in \N^*$, we call Hidden Weight Bit Function (HWBF) the $n$-variable Boolean function defined by:
 	\[h(x)= \left\{ 
@@
 
-\pmnote{complete the following prop. Choose between nonlinearity or $\max_{a\in\mathbb F_2^n}|\wt f(a)|$}
-
-\begin{Prop}[Cryptographic properties of functions from $\WD{2}{n}$ \label{prop:wwd1}]
+\pmnote{complete the following prop. Choose between nonlinearity or $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ \color{blue} Tim: I started, but please do the remaining two items.}
+
+\begin{Prop}[Cryptographic properties of functions from $\WD{2}{n}$, \cite{DCC:DalMaiSar06,DAM:WCST14,DAM:MeaOza24,DAM:MeaOza24}\label{prop:wwd1}]
 Let $n\in \N^*$ even, the following hold for functions in $\WD{2}{n}$. 
 \begin{itemize}
-	\item For the majority function
-
-	$\max_{a\in\mathbb F_2^n}|\wt f(a)|$ (adapt from Theorem 3 \cite{DCC:DalMaiSar06})
-	\item value for HWBF. (from~\cite{DAM:WCST14}))
-
+    \item The majority function $f\in\WD{2}{n}$ introduced in Definition~\ref{def:maj} satisfies:
+    \[
+        \NL(f)=2^{n-1}-\binom{n-1}{\frac n2}.
+    \]
+    \item The HWBF $f\in\WD{2}{n}$ introduced in Definition~\ref{def:hwbf} satisfies:
+    \[
+        \NL(f)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}.
+    \]
 	\item  bound for the cyclic weightwise linear (adapt Theorem 1 of \cite{DAM:MeaOza24})
@@
 \end{itemize}
-
 \end{Prop}
@@
 
-\pmnote{I would recall between parentheses somewhere that we denote by $|.|$ the complex norm here, which corresponds to the absolute value on $\R$
+\begin{remark}
+    Property~\ref{property:cauchy_estimate} is typically employed to bound the absolute value of complex numbers.
+Naturally, the bound remains valid when the complex number is real, as will be the case in our application.
+\end{remark}
+
+\pmnote{I would recall between parentheses somewhere that we denote by $|.|$ the complex norm here, which corresponds to the absolute value on $\R${ \color{blue} Tim :OK, check above remark.}
 
@@
 
-When a specific value of $t$ is given in terms of $n$, the proof strategy for Theorem~\ref{theorem:bound_D_nka_generalized} can be applied more precisely.
-For instance, we consider the case where $t = n/3$:
+When a specific value of $t$ is given as a function of $n$, the proof strategy for Theorem~\ref{theorem:bound_D_nka_generalized} can be applied with greater precision.
+For example, we examine the case where $t=n/3$ in the below Proposition~\ref{proposition:walsh_t_over_3}.
+Before proceeding, we include a brief lemma that will clarify the proof of that proposition.
+
+\begin{lemma}\label{lemma:maximizing_args}
+    Let $N$ be a non-negative number and $D\subseteq\C$ a set of complex numbers.
+For every integer $1\leq i\leq N$, consider a non-negative integer $m_i$ as well as complex functions $f_{i,1},\dots,f_{i,k_i}$ defined on the set $D$.
+Assume that the following maximum exists (which holds for instance if the functions $f_{i,j}$ are continuous and $D$ is topologically compact):
+    \[
+        M=\max_{\substack{\forall 1\leq i\leq N:\,p_{i,1}+\cdots+p_{i,k_i}=m_i\\z\in D}}\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|.
+    \]
+    Then there exist integers $j_1,\dots,j_N$ with $1\leq j_i\leq k_i$ such that the following holds:
+    \[
+        M=\max_{z\in D}\left|\prod_{i=1}^Nf_{i,j_i}(z)^{m_i}\right|.
+    \]
+\end{lemma}
+
+\begin{proof}
+    Let us choose the integers $p_{i,j}$ and the complex number $z\in D$ to maximize the quantity $\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|$.
+Note that this in particular means that $\sum_{j=1}^{k_i}p_{i,j}=m_i$ for every $1\leq i\leq N$.
+Next, for every $1\leq i\leq N$, choose $1\leq j_i\leq k_i$ such that $|f_{i,j_i}(z)|\geq|f_{i,j}(z)|$ for every $1\leq j\leq k_i$.
+Then we have:
+    \[
+        M=\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|\leq\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j_i}(z)^{p_{i,j}}\right|=\left|\prod_{i=1}^Nf_{i,j_i}(z)^{\sum_{j=1}^{k_i}p_{i,j}}\right|=\left|\prod_{i=1}^Nf_{i,j}(z)^{m_i}\right|\leq M.\qedhere
+    \]
+\end{proof}
 
@@
 
-   To find a bound for $|P_{a,t}(z)|$ on $\dis$ that applies to all $a\in\F_2^n$, we focus only on values of $a$ which are candidates for maximizing $|P_{a,t}(z)|$. 
-   Specifically, we consider cases where only one of $(p,q,r)$ is non-zero, and for which only and only one of $(u,v)$ is non-zero.
-
-\pmnote{What is the argument: "maximum implies only one is non-zero" }
+   To find a bound for $|P_{a,t}(z)|$ on $\dis$ that applies to all $a\in\F_2^n$, we would like to bound the quantity $\max_{a\in\F_2^n,z\in\dis}|P_{a,t}(z)|$.
+Moving through all $a\in\F_2^n$ is equivalent to moving through all tuples $(p,q,r;u,v)$ of non-negative integers which satisfy $p+q+r=t$ and $u+v=n-2t$.
+It follows from Lemma~\ref{lemma:maximizing_args} that it is enough to consider only the cases for which only one of $p,q,r$ is non-zero, and for which only one of $u,v$ is non-zero.
+
+\pmnote{What is the argument: "maximum implies only one is non-zero" \color{blue} Tim: OK, check above lemma}
 
@@
     \]
-    Writing $z=\cos\alpha+\mathrm i\sin\alpha$, we obtain:
-
-    \pmnote{@Tim, add intermediate computation in the following:}
-    \[
-        |P_{a,t}(z)|^2=[(6-2\cos2\alpha)(2+2\cos\alpha)]^t.
-    \]
+    Writing $z=\cos\alpha+\mathrm i\sin\alpha$ and $z=\cos2\alpha+\mathrm i\sin2\alpha$, we have:
+    \begin{align*}
+        |-z^2+2z+1|^2&=|-z^2+2z+1|^2\\
+        &=|-\cos2\alpha-\mathrm i\sin2\alpha+2\cos\alpha+2\mathrm i\sin\alpha+1|^2\\
+        &=(-\cos2\alpha+2\cos\alpha+1)^2+(-\sin2\alpha+2\sin\alpha)^2\\
+        &=6-2\cos(2\alpha);
+    \end{align*}
+    the last equality can be obtained by expanding and applying classical trigonometric identities, or by making use of a computer algebra system such as \textsc{SageMath}.
+We similarly obtain that $|1+z|^2=2+2\cos\alpha$.
+Combining both, we get:
+
+    \pmnote{@Tim, add intermediate computation in the following: \color{blue} Tim: Done}
+
+    \[
+        |P_{a,t}(z)|^2=\left(|-z^2+2z+1|^2\cdot|1+z|^2\right)^t=[(6-2\cos2\alpha)(2+2\cos\alpha)]^t.
+    \]
+
     \pmnote{@Tim, for the following, by calculus, you mean using some software? In this case we can add a footnote saying in practice we did it with xxx.
@@
     Can you give a plot of $(\alpha,(6-2\cos2\alpha)(2+2\cos\alpha))$ and add the line corresponding to $y=9/4$?
-    }
-
-    Through calculus, one finds that $|(6-2\cos2\alpha)(2+2\cos\alpha)|<2^{9/2}$, and hence that $|P_{a,t}(z)|<2^{9t/4}=2^{3n/4}$.
+    \color{blue} Tim: Done}
+
+    Since $|(6-2\cos2\alpha)(2+2\cos\alpha)|<2^{9/2}$ as shown in Figure~\ref{fig:trigo_bound} (which can also be formally checked using classical tricks from calculus), we obtain that $|P_{a,t}(z)|<2^{9t/4}=2^{3n/4}$.
 The same upper bound works for the remaining two candidates for $(p,q,r;u,v)$, and we can therefore conclude  $|\wtk{d_{n/3,n}}{k}(a)|\leq 2^{3n/4}$, and $|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}$.
 \end{proof}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=9cm]{trigo_bound.pdf}
+	\caption{The function $\alpha\mapsto(6-2\cos2\alpha)(2+2\cos\alpha)$ in blue, and the line $y=2^{9/2}$ in red.}
+    \label{fig:trigo_bound}
+\end{figure}
 
@@
 We can give the scripts in supplementary material when submitting, of add the link of a github if you agree to have them public.
+\color{blue} Tim: I added the script to GitHub.
+You can decide what we do with it.
 

### 2024-10-30 RevisedHiddenWeight.tex
Easier proof in Prop 11

@@
     \]
-    Writing $z=\cos\alpha+\mathrm i\sin\alpha$ and $z=\cos2\alpha+\mathrm i\sin2\alpha$, we have:
+    Writing $z=\ee^{\ii\alpha}$ and using that $|w|^2=w\overline w$ for every complex number $w$, we have:
     \begin{align*}
-        |-z^2+2z+1|^2&=|-z^2+2z+1|^2\\
-        &=|-\cos2\alpha-\mathrm i\sin2\alpha+2\cos\alpha+2\mathrm i\sin\alpha+1|^2\\
-        &=(-\cos2\alpha+2\cos\alpha+1)^2+(-\sin2\alpha+2\sin\alpha)^2\\
-        &=6-2\cos(2\alpha);
+        |-z^2+2z+1|^2&=\left(-\ee^{2\ii\alpha}+2\ee^{\ii\alpha}+1\right)\left(-\ee^{-2\ii\alpha}+2\ee^{-\ii\alpha}+1\right)\\
+        &=6-\ee^{2\ii\alpha}-\ee^{-2\ii\alpha}\\
+        &=6-2\cos2\alpha;
     \end{align*}
-    the last equality can be obtained by expanding and applying classical trigonometric identities, or by making use of a computer algebra system such as \textsc{SageMath}.
-We similarly obtain that $|1+z|^2=2+2\cos\alpha$.
-Combining both, we get:
+    the last equality uses that $\ee^{2\ii\alpha}=\cos2\alpha+\ii\sin2\alpha$. We similarly obtain that $|1+z|^2=2+2\cos\alpha$. Combining both, we get:
 

### 2024-10-31 RevisedHiddenWeight.tex
minor 4.2

@@
     \]
-    where $M_R$ is the maximum of $|f(z)|$ on the circle $|z-w|=R$.
+%    where $M_R$ is the maximum of $|f(z)|$ on the circle $|z-w|=R$.
+where $M_R$ is the maximum of the absolute value of $f$, $|f(z)|$ on the circle defined by $|z-w|=R$.
 \end{Prop}
 
-\begin{remark}
-    Property~\ref{property:cauchy_estimate} is typically employed to bound the absolute value of complex numbers.
+%\pmnote{ The point for the remark was to recall that we use the notation "$| \cdot |$" for absolute value over the complex, since before we used it only to denote "cardinal" or absolute value over integers.}
+
+%\begin{remark}
+%    Property~\ref{property:cauchy_estimate} is typically employed to bound the absolute value of complex numbers.
 Naturally, the bound remains valid when the complex number is real, as will be the case in our application.
-\end{remark}
-
-\pmnote{I would recall between parentheses somewhere that we denote by $|.|$ the complex norm here, which corresponds to the absolute value on $\R${ \color{blue} Tim :OK, check above remark.}
-
-verify if $w$ and $z$ are coherent.
-}
-
-Applying this, we get:
+%\end{remark}
+
+Applying the property, we get:
 
@@
 
-In particular, $d_{n/2,n}(x)=d_n(x)$. 
-We focus on the Walsh spectrum restricted to the slices of any function $d_{t,n}$:
+In particular, $d_{\frac{n}{2},n}(x)=d_n(x)$. 
+%We focus on the Walsh spectrum restricted to the slices of any function $d_{t,n}$:
+We focus on the restricted Walsh spectrum of any function $d_{t,n}$:
 
@@
 
-\pmnote{What is the argument: "maximum implies only one is non-zero" \color{blue} Tim: OK, check above lemma}
+%\pmnote{What is the argument: "maximum implies only one is non-zero" \color{blue} Tim: OK, check above lemma}
+
+%\pmnote{perfect.}
 
@@
         &=6-\ee^{2\ii\alpha}-\ee^{-2\ii\alpha}\\
-        &=6-2\cos2\alpha;
+        &=6-2\cos (2\alpha),
     \end{align*}
-    the last equality uses that $\ee^{2\ii\alpha}=\cos2\alpha+\ii\sin2\alpha$. We similarly obtain that $|1+z|^2=2+2\cos\alpha$. Combining both, we get:
-
-    \pmnote{@Tim, add intermediate computation in the following: \color{blue} Tim: Done}
-
+    where the last equality uses that $\ee^{2\ii\alpha}=\cos(2\alpha)+\ii\sin(2\alpha)$. We similarly obtain that $|1+z|^2=2+2\cos\alpha$. Combining both, we get:   
     \[
@@
 
-    \pmnote{@Tim, for the following, by calculus, you mean using some software? In this case we can add a footnote saying in practice we did it with xxx.
-
-    Can you give a plot of $(\alpha,(6-2\cos2\alpha)(2+2\cos\alpha))$ and add the line corresponding to $y=9/4$?
-    \color{blue} Tim: Done}
-
-    Since $|(6-2\cos2\alpha)(2+2\cos\alpha)|<2^{9/2}$ as shown in Figure~\ref{fig:trigo_bound} (which can also be formally checked using classical tricks from calculus), we obtain that $|P_{a,t}(z)|<2^{9t/4}=2^{3n/4}$.
+    Since $|(6-2\cos2\alpha)(2+2\cos\alpha)|<2^{9/2}$ as shown in Figure~\ref{fig:trigo_bound} (which can also be formally proven using derivatives), we obtain that $|P_{a,t}(z)|<2^{9t/4}=2^{3n/4}$.
 The same upper bound works for the remaining two candidates for $(p,q,r;u,v)$, and we can therefore conclude  $|\wtk{d_{n/3,n}}{k}(a)|\leq 2^{3n/4}$, and $|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}$.
@@
 	\includegraphics[width=9cm]{trigo_bound.pdf}
-	\caption{The function $\alpha\mapsto(6-2\cos2\alpha)(2+2\cos\alpha)$ in blue, and the line $y=2^{9/2}$ in red.}
+	\caption{Graph of the function $\alpha\mapsto(6-2\cos)2\alpha))(2+2\cos\alpha)$ in blue, and the line $y=2^{9/2}$ in red.}
     \label{fig:trigo_bound}

### 2024-10-31 RevisedHiddenWeight.tex
5.1

@@
 	\includegraphics[width=9cm]{trigo_bound.pdf}
-	\caption{Graph of the function $\alpha\mapsto(6-2\cos)2\alpha))(2+2\cos\alpha)$ in blue, and the line $y=2^{9/2}$ in red.}
+	\caption{Graph of the function $\alpha\mapsto(6-2\cos(2\alpha))(2+2\cos\alpha)$ in blue, and the line $y=2^{9/2}$ in red.}
     \label{fig:trigo_bound}
@@
 
-\pmnote{for the remark, add how they are obtained (from a script in xxx). 
-We can give the scripts in supplementary material when submitting, of add the link of a github if you agree to have them public.
+%\pmnote{for the remark, add how they are obtained (from a script in xxx). 
+%We can give the scripts in supplementary material when submitting, of add the link of a github if you agree to have them public.
 \color{blue} Tim: I added the script to GitHub.
-You can decide what we do with it.
-
-}
+You can decide what we do with it.}
 
@@
     The proof of Proposition~\ref{proposition:walsh_t_over_3} can be extended to other values of $t$. 
-    In Figure~\ref{fig:walsh_bounds_generalization}, we provide bounds of the form $\max_{a\in\F_2^n}|\wt{d_{\alpha n/40,n}}(a)|\leq 1+n\cdot 2^{\beta n}$, where $\alpha\in[0,20]$ is represented on the $x$-axis and $\beta$ is represented on the $y$-axis.
+    In Figure~\ref{fig:walsh_bounds_generalization}, we provide bounds of the form $\max_{a\in\F_2^n}|\wt{d_{ r n/40,n}}(a)|\leq 1+n\cdot 2^{ s n}$ obtained with a script in \textsf{SageMath}, where the integer $r \in[0,20]$ is represented on the $x$-axis and $s$ is represented on the $y$-axis.
 \end{remark}
@@
 	\includegraphics[width=9cm]{walsh_bounds_generalization.pdf}
-	\caption{Improvements on Corollary~\ref{cor:gen}. For each point $(\alpha,\beta)$, we have $\max_{a\in\F_2^n}|\wt{d_{\alpha n/40,n}}(a)|\leq 1+n\cdot 2^{\beta n}$.}
+	\caption{Improvements on Corollary~\ref{cor:gen}. For each point $(r,s)$, we have $\max_{a\in\F_2^n}|\wt{d_{ r n/40,n}}(a)|\leq 1+n\cdot 2^{s n}$.}
     \label{fig:walsh_bounds_generalization}
@@
 
+In this section, we establish a tighter bound on the absolute value of the Walsh transform of the revised HWBF for values of $n$ up to $80$. 
+We then compare the nonlinearity of this function to that of other functions suited to similar use cases, such as the HWBF of weightwise cyclic functions from~\cite{DAM:MeaOza24}.
+
 \subsection{Bounding the Walsh transform of $f$ experimentally}\label{sec:expwt}
 
-We have just deduced that $|\wt f(a)|\leq 1+n\cdot 2^{3n/4}$ for every Boolean vector $a\in\F_2^n$.
+%We have just deduced that $|\wt f(a)|\leq 1+n\cdot 2^{3n/4}$ for every Boolean vector $a\in\F_2^n$.
 This is a pessimistic bound.
 In this section, we will discuss how a tighter bound on $|\wt f(a)|$ can be obtained in polynomial time in $n$.
+
+Following Corollary~\ref{cor:bound_walsh_cauchy} we deduce that $|\wt f(a)|\leq 1+n\cdot 2^{3n/4}$ for every Boolean vector $a\in\F_2^n$.
+This is a pessimistic bound.
+In this part, we discuss how a tighter bound on $|\wt f(a)|$ can be obtained in polynomial time in $n$.
 
@@
 \]
-For each $1\leq k\leq n/2$, select $\{\alpha_k,\beta_k,\gamma_k\}=\{0,\pm 1\}$ with $\gamma_k\neq 0$ such that the following expression is defined and maximized:
+For each $1\leq k\leq n/2$, we select $\{\alpha_k,\beta_k,\gamma_k\}=\{0,\pm 1\}$ with $\gamma_k\neq 0$ such that the following expression is defined and maximized:
 \[
@@
 
-Consider now the complexity involved in computing the values of $\mathsf{D}_{n,k}^{p,q,r}$ for all $0 \leq k \leq n$ and for all triplets $(p,q,r)$ where $p+q+r=n/2$.
+We consider now the complexity involved in computing the values of $\mathsf{D}_{n,k}^{p,q,r}$ for all $0 \leq k \leq n$ and for all triplets $(p,q,r)$ where $p+q+r=n/2$.
 We claim that this computation has a complexity of $\mathcal{O}(n^3 \log n)$.
@@
 
-\subsection{Comparison of the nonlinearity}
-
-\pmnote{under construction}
-
-In this part we compare the nonlinearity of the function $f$ from Definition~\ref{def:revHWBF} to other weightwise quadratic functions considered for similar use-cases, such as majority, HWBF and the cyclic weightwise quadratic function $t$  from~\cite{DAM:MeaOza24}.
-More precisely, we compare the value $\max_{a\in\mathbb F_2^n}|\wt f(a)|$, the smaller the maximum the better the nonlinearity. 
-For majority and HWBF, we use the exact values recalled in Property~\ref{prop:wwd1}, for the function $t$ we use the upper bound proven in~\cite{DAM:MeaOza24}. 
-For the revisited HWBF, we consider the theoretical bound from Theorem~\ref{cor:bound_walsh_cauchy} and the experimental one from Section~\ref{sec:expwt}
-
-Table~\ref{table:max_walsh_vs_bound} compares $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ to the upper bound $B_n$ we find using the above method.
+\pmnote{add a link to the public github or name of the name of this code in supplementary materials}
+
+%Table~\ref{table:max_walsh_vs_bound} compares $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ to the upper bound $B_n$ we find using the above method.
 Table~\ref{table:walsh_bounds} gives all values of this bound $B_n$ for all even $1\leq n\leq 80$.
 
+In Table~\ref{table:max_walsh_vs_bound}, we compare the exact values of $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ for small values of $n$ (calculated using \textsf{SageMath}) to the upper bound $B_n$ obtained through the above method and the one from Corollary~\ref{cor:bound_walsh_cauchy}.
+Additionally, Table~\ref{table:walsh_bounds} provides the values of the bound $B_n$ for all even values of $n$ from $1$ to $80$.
+We observe that the above method provides a much tighter bound than the one from Corollary~\ref{cor:bound_walsh_cauchy}, and its polynomial complexity enables us to extend the analysis far beyond what is feasible with a full computation of the Walsh spectrum (\( \mathcal{O}(n 2^n) \)).
+
+\iffalse
 \begin{table}
@@
 \end{table}
-
-Figure \ref{fig:walsh_bound_comparison} compares our experimental bound $B_n$ to the theoretical bound $1+n\cdot 2^{3n/4}$ and the binomial coefficient $\binom{n}{n/2}$, on a logarithmic scale.
-The first two and the last one have an asymptotic slope of $3/4$ and $1$, respectively.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=9cm]{comparison_walsh_bound.pdf}
-	\caption{On a logarithmic scale, our experimental bound $B_n$ in terms of $n$ in red, our theoretical bound $1+n\cdot 2^{3n/4}$ from Proposition \ref{cor:bound_walsh_cauchy} in green, and the bound $\binom{n}{n/2}$ in blue.}
-	\label{fig:walsh_bound_comparison}
-\end{figure}
+\fi
+
+\begin{table}
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		$n$ & $\max_{a\in\F_2^n}|W_f(a)|$ & $B_n$  & $\lfloor 1+n \cdot 2^{3n/4} \rfloor$\\ \hline
+		$2$  & $2$     & $4$  &  $6$ \\
+		$4$  & $8$     & $14$  & $33$  \\
+		$6$  & $20$    & $36$   & $136$\\
+		$8$  & $52$    & $114$  & $513$ \\
+		$10$ & $108$   & $288$  & $1\,811$\\
+		$12$ & $292$   & $820$  & $6\,145$ \\
+		$14$ & $700$   & $2\,316$ & $20\,275$ \\
+		$16$ & $2\,176$  & $6\,006$ & $65\,637$ \\
+		$18$ & $4\,964$  & $18\,192$ & $208\,535$ \\
+		$20$ & $14\,968$ & $48\,480$ & $655\,361$ \\
+		$22$ & $34\,232$ & $140\,392$ & $2\,039 \,002$ \\
+		$24$ & $109\,648$ & $392\,168$ & $6\,291 \,457$  \\ \hline
+	\end{tabular}
+	\caption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ compared to the bound $B_n$ and the one from Corollary~\ref{cor:bound_walsh_cauchy}.}
+	\label{table:max_walsh_vs_bound}
+\end{table}
 
@@
 \end{table}
+
+\subsection{Comparison of the nonlinearity}
+
+\pmnote{under construction}
+
+In this part we compare the nonlinearity of the function $f$ from Definition~\ref{def:revHWBF} to other weightwise quadratic functions considered for similar use-cases, such as majority, HWBF and the cyclic weightwise quadratic function $t$  from~\cite{DAM:MeaOza24}.
+More precisely, we compare the value $\max_{a\in\mathbb F_2^n}|\wt f(a)|$, the smaller the maximum the better the nonlinearity. 
+For majority and HWBF, we use the exact values recalled in Property~\ref{prop:wwd1}, for the function $t$ we use the upper bound proven in~\cite{DAM:MeaOza24}. 
+For the revisited HWBF, we consider the theoretical bound from Theorem~\ref{cor:bound_walsh_cauchy} and the experimental one from Section~\ref{sec:expwt}
+
+Figure~\ref{fig:walsh_bound_comparison} compares the experimental bound $B_n$ to the theoretical bound $1+n\cdot 2^{3n/4}$ and the binomial coefficient $\binom{n}{n/2}$, on a logarithmic scale.
+The first two and the last one have an asymptotic slope of $3/4$ and $1$, respectively.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=9cm]{comparison_walsh_bound.pdf}
+	\caption{On a logarithmic scale, our experimental bound $B_n$ in terms of $n$ in red, our theoretical bound $1+n\cdot 2^{3n/4}$ from Proposition \ref{cor:bound_walsh_cauchy} in green, and the bound $\binom{n}{n/2}$ in blue.}
+	\label{fig:walsh_bound_comparison}
+\end{figure}
 

### 2024-10-31 RevisedHiddenWeight.tex
prop 1

@@
 
-\pmnote{\color{blue} Tim: Check below}
 \begin{definition}[Majority function]\label{def:maj}
-    The \emph{majority function} in $n$ variables is the Boolean function $f\in\BN$ defined as:
-    \[
-        f(x)=0\iff\w(x)\leq\frac n2.
+    The \emph{majority function} in $n$ variables is the Boolean function $\textsf{Maj}\in\BN$ defined as:
+    \[
+        \textsf{Maj}(x)=0\iff\w(x)<n/2.
     \]
@@
 
-In~\cite{DAM:MeaOza24}, the parameters of different functions from $\WD{1}{n}$ and $\WD{2}{n}$ are studied experimentally for $n$ up to $20$ and lower bounds are given for the nonlinearity. 
-We summarize the known results on the cryptographic criteria of weightwise affine functions we will use in this article in the following property.
-
-\pmnote{complete the following prop. Choose between nonlinearity or $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ \color{blue} Tim: I started, but please do the remaining two items.}
-
-\begin{Prop}[Cryptographic properties of functions from $\WD{2}{n}$, \cite{DCC:DalMaiSar06,DAM:WCST14,DAM:MeaOza24,DAM:MeaOza24}\label{prop:wwd1}]
+In~\cite{DAM:MeaOza24}, the parameters of different functions from $\WD{1}{n}$ and $\WD{2}{n}$ are studied experimentally for $n$ up to $20$ and lower bounds are given for the nonlinearity for all $n$.
+These bounds involve sums of binomial coefficients.
+For simplicity, in the following we provide only the nonlinearity values of the majority function and HWBF, as these bounds will be used for comparison.
+
+%We summarize the known results on the cryptographic criteria of weightwise affine functions we will use in this article in the following property.
+
+%\pmnote{complete the following prop. Choose between nonlinearity or $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ \color{blue} Tim: I started, but please do the remaining two items.}
+\iffalse
+\begin{Prop}[Nonlinearity of some functions from $\WD{1}{n}$, \cite{DCC:DalMaiSar06,DAM:WCST14,DAM:MeaOza24}\label{prop:wwd1}]
 Let $n\in \N^*$ even, the following hold for functions in $\WD{2}{n}$. 
@@
 	\item  bound for the cyclic weightwise quadratic function $t$  (adapt Theorem 2 of \cite{DAM:MeaOza24})
+\end{itemize}
+\end{Prop}
+\fi
+
+\begin{Prop}[Nonlinearity of some functions from $\WD{1}{n}$\label{prop:wwd1}]
+Let $n\in \N^*$ even, the following hold for the following functions in $\WD{1}{n}$: 
+\begin{itemize}
+	\item (\eg ~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\textsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
+	\[
+	\NL(\textsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}.
+	\]
+	\item (\cite{DAM:WCST14}, Theorem $3$) The HWBF $h$ introduced in Definition~\ref{def:hwbf} satisfies:
+	\[
+	\NL(h)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}.
+	\]	
 \end{itemize}
@@
 	\end{minipage}
-	\caption{Approximate values of $B_n$ for various $n$}
+	\caption{Approximate values of $B_n$ for various values of $n$}
 	\label{table:walsh_bounds}
@@
 More precisely, we compare the value $\max_{a\in\mathbb F_2^n}|\wt f(a)|$, the smaller the maximum the better the nonlinearity.
+
 For majority and HWBF, we use the exact values recalled in Property~\ref{prop:wwd1}, for the function $t$ we use the upper bound proven in~\cite{DAM:MeaOza24}. 

### 2024-11-04 RevisedHiddenWeight.tex
Small typo
Updates from Overleaf
Replaced some results by Thm 3

@@
     where $M$ is the maximum of $|P_a(z)|$ on the circle %$|z|=1$. 
-    $\dis=\{ z \in \C,  |z|=1  \}$
+    $\dis=\{ z \in \C,  |z|=1  \}$.
     We claim, and prove below, that the maximum of $\left|-z^2+2z+1\right|$ on $\dis$ is $2\sqrt 2$. 
@@
 
-Consequently, we get a generalization of Theorem~\ref{theorem:bound_D_nka}:
-
-\begin{theorem}\label{theorem:bound_D_nka_generalized}
-    Let $t, n\in \N$ with $n$ even and $t\le n/2$. For every $a\in\F_2^n$ and every $k\in[0,n]$, it holds that:
-    \[
-        |\wtk{d_{t,n}}{k}(a)|\leq 2^{n-t/2}.
-    \]
-\end{theorem}
-
-\begin{proof}
-    By applying Property \ref{property:cauchy_estimate}, we get that a bound on $|\wtk{d_{t,n}}{k}(a)|$ is given by the maximum $M'$ on the circle $\dis$ of $|P_b(z)|\cdot|(1+z)^u\cdot(1-z)^v|$. 
-    As previously established in Theorem~\ref{theorem:bound_D_nka}, $|P_b(z)|$ is bounded on $\dis$ by $(2\sqrt 2)^t=2^{3t/2}$, and $|(1+z)^u\cdot(1-z)^v|$ is bounded on $\dis$ by $2^{u+v}=2^{n-2t}$. 
-    Therefore, we conclude that $M'$ is bounded by $2^{3t/2}2^{n-2t}=2^{n-t/2}$, and hence this is also a bound for $|\wtk{d_{t,n}}{k}(a)|$. 
-\end{proof}
-
-\begin{Corollary}\label{cor:gen}
-    Let $t, n\in \N$ with $n$ even and $t\le n/2$. For every $a\in\F_2^n$, the following holds:
-    \[
-        |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{n-t/2}.
-    \]
-\end{Corollary}
-
-\begin{proof}
-    Analogous to the proof of Corollary \ref{cor:bound_walsh_cauchy}.
-\end{proof}
-
-When a specific value of $t$ is given as a function of $n$, the proof strategy for Theorem~\ref{theorem:bound_D_nka_generalized} can be applied with greater precision.
-For example, we examine the case where $t=n/3$ in the below Proposition~\ref{proposition:walsh_t_over_3}.
-Before proceeding, we include a brief lemma that will clarify the proof of that proposition.
+With this, we prove a generalization of Theorem~\ref{theorem:bound_D_nka} below. Before that, we still require a preliminary result:
 
@@
 
-\begin{proposition}\label{proposition:walsh_t_over_3}
-    Let $n\in\N^*$ be divisible by $6$. 
-    Then, for every $a\in\F_2^n$ and every $k\in[0,n]$, it holds that:
-    \[
-        |\wtk{d_{n/3,n}}{k}(a)|\leq2^{3n/4},\quad \text{and }\quad|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}.
-    \]
-\end{proposition}
-
-\begin{proof}
+\begin{theorem}\label{theorem:bound_D_nka_generalized}
+    Let $t, n\in \N$ with $n$ even and $t\le n/2$. Define $\lambda:=t/n\in\left[0,\frac 12\right]$, as well as:
+    \[
+        \mu:=\mu(\lambda):=
+        \begin{cases}
+            \frac{\lambda+1}{2}+\frac12\log_2\left(\frac{\left(-\lambda^2+2\lambda+\lambda\sqrt{\lambda^2-4\lambda+2}\right)^\lambda}{\left(1-\lambda+\sqrt{\lambda^2-4\lambda+2}\right)^{2\lambda-1}}\right)&\text{if $\lambda>\frac 16$,}\\
+            1-\lambda&\text{if $\lambda\leq\frac 16$.}\\
+        \end{cases}
+    \]
+    Then for all $a\in\F_2^n$ and $k\in[0,n]$, the following hold true:
+    \[
+        |\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n},\quad |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}.
+    \]
+\end{theorem}
+
+\begin{proof}
+    To begin, observe that the inequality $|\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}$ will follow from the inequality $|\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n}$ using precisely the arguments of the proof of Corollary~\ref{cor:bound_walsh_cauchy}, so that we are only required to prove the first inequality.
+
     As before, we want to bound the maximum of $|P_{a,t}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[1,n]$. 
@@
     \]
-    Let us for instance find an upper bound of $|P_{a,t}(z)|$ in case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $n-2t=t$ by assumption, we get:
-    \[
-        P_{a,t}(z)=[(-z^2+2z+1)(1+z)]^t.
-    \]
-    Writing $z=\ee^{\ii\alpha}$ and using that $|w|^2=w\overline w$ for every complex number $w$, we have:
+    Let us start by bounding $|P_{a,t}(z)|$ on $\dis$ in case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $t=\lambda n$, we can write:
+    \[
+        P_{a,t}(z)=\left((-z^2+2z+1)^{\lambda}(1+z)^{1-2\lambda}\right)^n.
+    \]
+    Writing $z=\ee^{\ii\alpha}$ and $z^2=\ee^{2\ii\alpha}$ for $\alpha\in[-\pi,\pi]$, and using that $|w|^2=w\overline w$ for every complex number $w$, we get:
     \begin{align*}
@@
     \[
-        |P_{a,t}(z)|^2=\left(|-z^2+2z+1|^2\cdot|1+z|^2\right)^t=[(6-2\cos2\alpha)(2+2\cos\alpha)]^t.
-    \]
-
-    Since $|(6-2\cos2\alpha)(2+2\cos\alpha)|<2^{9/2}$ as shown in Figure~\ref{fig:trigo_bound} (which can also be formally proven using derivatives), we obtain that $|P_{a,t}(z)|<2^{9t/4}=2^{3n/4}$. 
-    The same upper bound works for the remaining two candidates for $(p,q,r;u,v)$, and we can therefore conclude $|\wtk{d_{n/3,n}}{k}(a)|\leq 2^{3n/4}$, and $|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}$.
-\end{proof}
+        |P_{a,t}(z)|^2=\left(\left|-z^2+2z+1\right|^{2\lambda}|1+z|^{2(1-2\lambda)}\right)^n=\left((6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}\right)^n.
+    \]
+    The goal will be to prove that the maximum of $g(\alpha):=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{a,t}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$.
+Since $g$ is an even function, it is enough to focus on the interval $\alpha\in[0,\pi]$.
+
+    To begin, computing the first derivative of $g$ and applying the \textit{double angle formulas} $\cos(2\alpha)=2\cos^2\alpha-1$ and $\sin(2\alpha)=2\cos\alpha\sin\alpha$ gives:
+    \[
+        \frac{\dd}{\dd\alpha}g(\alpha)=8(6-2\cos(2\alpha))^{\lambda-1}(2+2\cos\alpha)^{-2\lambda}\sin\alpha\left(\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2\right).
+    \]
+    The only interesting zeros of $\frac{\dd}{\dd\alpha}g(\alpha)$ are those of the last factor 
+    $\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2$: those of the factor $8(6-2\cos(2\alpha))^{\lambda-1}(2+2\cos\alpha)^{-2\lambda}$ will make $g(\alpha)$ vanish and will therefore not maximize $g(\alpha)$, and those for $\sin\alpha$ are $\alpha=0$ and $\alpha=\pi$.
+
+    Our first claim is that the equation $\mathcal E:\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2=0$ either has a unique solution $\cos\alpha=-\lambda+\sqrt{\lambda^2-4\lambda+2}$ if $\lambda\geq\frac 16$, and has no solution $\cos\alpha$ otherwise.
+To see this, we consider $\mathcal E$ as an equation of second degree in $\cos\alpha$, it leads to the two solutions $\cos\alpha=-\lambda\pm\sqrt{\lambda^2-4\lambda+2}$.
+We can exclude the solution $\cos\alpha=-\lambda-\sqrt{\lambda^2-4\lambda+2}$ since $\cos\alpha\in[-1,1]$.
+The other solution needs to be excluded for the same reason if $\lambda<\frac 16$.
+
+    Our next claim is that $\frac{\dd^2}{\dd^2\alpha}g(\alpha)\vert_{\alpha=0}$ has the same sign as $6\lambda -1$. Indeed, by definition of the second derivative, we have:
+    \begin{align*}
+        \frac{\dd^2}{\dd^2\alpha}g(\alpha)\vert_{\alpha=0}
+        &=\lim_{\alpha\to 0}\frac{\frac{\dd}{\dd\alpha}g(\alpha)}{\alpha}\\
+        &=\lim_{\alpha\to 0}8(6-2\cos(2\alpha))^{\lambda-1}(2+2\cos\alpha)^{-2\lambda}\cdot\frac{\sin\alpha}{\alpha}\cdot\left(\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2\right)\\
+        &=8\cdot4^{\lambda-1}\cdot 4^{-2\lambda}\cdot 1\cdot(6\lambda -1)\\
+        &=2^{1-2\lambda}(6\lambda -1).
+    \end{align*}
+
+    Therefore, in case $\lambda<\frac 16$, we can conclude from the two claims that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and this maximum is then equal to $2^{2-2\lambda}=2^{2\mu}$, as required.
+For $\lambda=\frac 16$, the solution to the equation $\mathcal E$ is $\cos\alpha=1$, again implying $\alpha_0=0$, and we obtain the same maximum of $2^{2\mu}$.
+In case $\lambda>\frac 16$, the two claims imply that $g(\alpha)$ reaches its maximum at the two values $\alpha_0\in[0,pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$.
+For such $\alpha$, the \textit{double angle formula} for the cosine implies that $\cos(2\alpha_0)=2\lambda^2-4\lambda+2-2\lambda\sqrt{\lambda^2-4\lambda+2}$.
+If we replace $\cos(\alpha_0)$ and $\cos(2\alpha_0)$ by their respective values, we obtain that the maximum of $g(\alpha)$ on $\alpha\in[0,\pi]$ is given by the following value:
+    \[
+        g(\alpha_0)=\frac{\left(-8\lambda^2+16\lambda+8\lambda\sqrt{\lambda^2-4\lambda+2}\right)^{\lambda}}{\left(2-2\lambda+2\sqrt{\lambda^2-4\lambda+2}\right)^{2\lambda-1}}=2^{2\mu}.
+    \]
+    This is exactly what we wanted to prove, and we have therefore covered the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$ entirely.
+In a similar fashion, it can be proven that $|P_{a,t}(z)|$ is also bounded by $2^{\mu n}$ on $\dis$  for the remaining two cases of $(p,q,r;u,v)$.
+\end{proof}
+
+The curve $\lambda\mapsto\mu(\lambda)$ defined in the above Theorem~\ref{theorem:bound_D_nka_generalized} is represented in Figure~\ref{fig:curve_exponents_lambda_mu}.
 
@@
 	\centering
-	\includegraphics[width=9cm]{trigo_bound.pdf}
-	\caption{Graph of the function $\alpha\mapsto(6-2\cos(2\alpha))(2+2\cos\alpha)$ in blue, and the line $y=2^{9/2}$ in red.}
-    \label{fig:trigo_bound}
+	\includegraphics[width=9cm]{curve_exponents_lambda_mu.pdf}
+	\caption{The curve $\lambda\mapsto\mu(\lambda)$ from Theorem~\ref{theorem:bound_D_nka_generalized}}
+	\label{fig:curve_exponents_lambda_mu}
 \end{figure}
@@
 You can decide what we do with it.}
-
-\begin{remark}
-    The proof of Proposition~\ref{proposition:walsh_t_over_3} can be extended to other values of $t$. 
-    In Figure~\ref{fig:walsh_bounds_generalization}, we provide bounds of the form $\max_{a\in\F_2^n}|\wt{d_{ r n/40,n}}(a)|\leq 1+n\cdot 2^{ s n}$ obtained with a script in \textsf{SageMath}, where the integer $r \in[0,20]$ is represented on the $x$-axis and $s$ is represented on the $y$-axis.
-\end{remark}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=9cm]{walsh_bounds_generalization.pdf}
-	\caption{Improvements on Corollary~\ref{cor:gen}. For each point $(r,s)$, we have $\max_{a\in\F_2^n}|\wt{d_{ r n/40,n}}(a)|\leq 1+n\cdot 2^{s n}$.}
-    \label{fig:walsh_bounds_generalization}
-\end{figure}
 
@@
 
-\pmnote{add a link to the public github or name of the name of this code in supplementary materials}
+\pmnote{add a link to the public github or name of the name of this code in supplementary materials \color{blue} Tim: Is on GitHub now: \texttt{Bounding\_Walsh.ipynb}}
 

### 2024-11-04 RevisedHiddenWeight.tex
Clarifications and typo corrections in Thm. 3 proof

@@
     \]
-    Then for all $a\in\F_2^n$ and $k\in[0,n]$, the following hold true:
+    Then for all $a\in\F_2^n$ and $k\in[1,n]$, the following hold true:
     \[
@@
     To begin, observe that the inequality $|\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}$ will follow from the inequality $|\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n}$ using precisely the arguments of the proof of Corollary~\ref{cor:bound_walsh_cauchy}, so that we are only required to prove the first inequality.
+Also, since the case $\lambda=\frac 12$ corresponds to Theorem~\ref{theorem:bound_D_nka}, we will henceforth assume $\lambda<\frac 12$.
 
@@
     \]
-    Writing $z=\ee^{\ii\alpha}$ and $z^2=\ee^{2\ii\alpha}$ for $\alpha\in[-\pi,\pi]$, and using that $|w|^2=w\overline w$ for every complex number $w$, we get:
+    Further writing $z=\ee^{\ii\alpha}$ and $z^2=\ee^{2\ii\alpha}$ for $\alpha\in[-\pi,\pi]$, and using that $|w|^2=w\overline w$ for every complex number $w$, we get:
     \begin{align*}
@@
 
-    To begin, computing the first derivative of $g$ and applying the \textit{double angle formulas} $\cos(2\alpha)=2\cos^2\alpha-1$ and $\sin(2\alpha)=2\cos\alpha\sin\alpha$ gives:
+    To begin, computing the first derivative of $g$ and applying the double angle formulas $\cos(2\alpha)=2\cos^2\alpha-1$ and $\sin(2\alpha)=2\cos\alpha\sin\alpha$ gives:
     \[
@@
     The only interesting zeros of $\frac{\dd}{\dd\alpha}g(\alpha)$ are those of the last factor 
-    $\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2$: those of the factor $8(6-2\cos(2\alpha))^{\lambda-1}(2+2\cos\alpha)^{-2\lambda}$ will make $g(\alpha)$ vanish and will therefore not maximize $g(\alpha)$, and those for $\sin\alpha$ are $\alpha=0$ and $\alpha=\pi$.
-
-    Our first claim is that the equation $\mathcal E:\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2=0$ either has a unique solution $\cos\alpha=-\lambda+\sqrt{\lambda^2-4\lambda+2}$ if $\lambda\geq\frac 16$, and has no solution $\cos\alpha$ otherwise.
-To see this, we consider $\mathcal E$ as an equation of second degree in $\cos\alpha$, it leads to the two solutions $\cos\alpha=-\lambda\pm\sqrt{\lambda^2-4\lambda+2}$.
+    $\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2$: those of the factor $8(6-2\cos(2\alpha))^{\lambda-1}(2+2\cos\alpha)^{-2\lambda}$ will make $g(\alpha)$ vanish and will therefore not maximize $g(\alpha)$, and those for $\sin\alpha$ are $\alpha=0$ and $\alpha=\pi$, with corresponding values $g(0)=2^{2-2\lambda}$ and $g(\pi)=0$.
+
+    Our first claim is that the equation $\mathcal E:\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2=0$ has a unique solution $\cos\alpha=-\lambda+\sqrt{\lambda^2-4\lambda+2}$ if $\lambda\geq\frac 16$ and has no solution $\cos\alpha$ otherwise.
+To see this, we consider $\mathcal E$ as an equation of second degree in $\cos\alpha$, which leads to the two solution candidates $\cos\alpha=-\lambda\pm\sqrt{\lambda^2-4\lambda+2}$.
 We can exclude the solution $\cos\alpha=-\lambda-\sqrt{\lambda^2-4\lambda+2}$ since $\cos\alpha\in[-1,1]$.
@@
 
-    Our next claim is that $\frac{\dd^2}{\dd^2\alpha}g(\alpha)\vert_{\alpha=0}$ has the same sign as $6\lambda -1$. Indeed, by definition of the second derivative, we have:
+    Our next claim is that $\frac{\dd^2}{\dd^2\alpha}g(\alpha)\vert_{\alpha=0}$ has the same sign as $6\lambda -1$. To see why, we apply the definition of the second derivative:
     \begin{align*}
@@
     Therefore, in case $\lambda<\frac 16$, we can conclude from the two claims that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and this maximum is then equal to $2^{2-2\lambda}=2^{2\mu}$, as required.
-For $\lambda=\frac 16$, the solution to the equation $\mathcal E$ is $\cos\alpha=1$, again implying $\alpha_0=0$, and we obtain the same maximum of $2^{2\mu}$.
-In case $\lambda>\frac 16$, the two claims imply that $g(\alpha)$ reaches its maximum at the two values $\alpha_0\in[0,pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$.
-For such $\alpha$, the \textit{double angle formula} for the cosine implies that $\cos(2\alpha_0)=2\lambda^2-4\lambda+2-2\lambda\sqrt{\lambda^2-4\lambda+2}$.
-If we replace $\cos(\alpha_0)$ and $\cos(2\alpha_0)$ by their respective values, we obtain that the maximum of $g(\alpha)$ on $\alpha\in[0,\pi]$ is given by the following value:
+For $\lambda=\frac 16$, the solution to the equation $\mathcal E$ is $\cos\alpha=1$, again implying that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and we obtain the same maximum of $2^{2\mu}$.
+In case $\lambda>\frac 16$, the two claims imply that $g(\alpha)$ reaches its maximum at the two values $\alpha_0\in[0,\pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$.
+For such $\alpha$, the double angle formula for the cosine implies that $\cos(2\alpha_0)=2\lambda^2-4\lambda+2-2\lambda\sqrt{\lambda^2-4\lambda+2}$.
+If we replace $\cos\alpha_0$ and $\cos(2\alpha_0)$ by their respective values, we obtain that the maximum of $g(\alpha)$ for $\alpha\in[0,\pi]$ is given by the following value:
     \[
@@
 In a similar fashion, it can be proven that $|P_{a,t}(z)|$ is also bounded by $2^{\mu n}$ on $\dis$ for the remaining two cases of $(p,q,r;u,v)$.
-\end{proof}
-
-The curve $\lambda\mapsto\mu(\lambda)$ defined in the above Theorem~\ref{theorem:bound_D_nka_generalized} is represented in Figure~\ref{fig:curve_exponents_lambda_mu}.
+In fact, for $(p,q,r;u,v)=(0,t,0;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h_1(\alpha):=(6-2\cos(2\alpha))^\lambda(2-2\cos\alpha)^{1-2\lambda}$, which has the same maximum as $g(\alpha)$ because $h_1\left(\frac{\pi}{2}+\alpha\right)=g\left(\frac{\pi}{2}-\alpha\right)$; for $(p,q,r;u,v)=(0,0,t;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h_2(\alpha):=(2+2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$, whose maximum is bounded by the maximum of $g(\alpha)$ because $h_2(\alpha)\leq g(\alpha)$.
+\end{proof}
+
+The curve of $\lambda\mapsto\mu(\lambda)$ defined in the above Theorem~\ref{theorem:bound_D_nka_generalized} is represented in Figure~\ref{fig:curve_exponents_lambda_mu}.
 
@@
 	\centering
-	\includegraphics[width=9cm]{curve_exponents_lambda_mu.pdf}
-	\caption{The curve $\lambda\mapsto\mu(\lambda)$ from Theorem~\ref{theorem:bound_D_nka_generalized}}
+	\includegraphics[width=10cm]{curve_exponents_lambda_mu.pdf}
+	\caption{The curve of $\lambda\mapsto\mu(\lambda)$ with $0\leq\lambda\leq\frac 12$ from Theorem~\ref{theorem:bound_D_nka_generalized}}
 	\label{fig:curve_exponents_lambda_mu}

### 2024-11-04 RevisedHiddenWeight.tex
comments new version4.3

--- 2024-11-04 RevisedHiddenWeight.tex
@@
 	Let $f\in \Bn{n}$ be a Boolean function, its Walsh transform $\wt{f}$ at $a \in \F_2^n$ is defined as:
-	\[  \wt{f} (a) := \sum_{x \in \F_2^n} (-1)^{f(x) +  a \cdot x }.\]
-	%	The Walsh support is the set $\Wsupp{f}:=\{ a\in \F_2^n\, | \, \wt{f} (a) \neq 0 \}$.
+	\[  \wt{f} (a) = \sum_{x \in \F_2^n} (-1)^{f(x) +  a \cdot x }.\]
+	%	The Walsh support is the set $\Wsupp{f}=\{ a\in \F_2^n\, | \, \wt{f} (a) \neq 0 \}$.
 	Let $f\in \Bn{n}$, $S \subset \F_2^n$, its Walsh transform restricted to $S$ at $a \in \F_2^n$ is defined as:
-	\[  \wt{f,S} (a) := \sum_{x\in S} (-1)^{f(x)+a \cdot x}.\]
+	\[  \wt{f,S} (a) = \sum_{x\in S} (-1)^{f(x)+a \cdot x}.\]
 	For $S=\Ekn{k}{n}$ we denote $\wt{f,\Ekn{k}{n}} (a)$ by $\wtk{f}{k}(a)$.%, and for $a= 0_{n}$ we denote $\wtk{f}{k}(a)$ as $\wtk{f}{k}(0)$.
@@
 \begin{theorem}\label{theorem:bound_D_nka_generalized}
-    Let $t, n\in \N$ with $n$ even and $t\le n/2$. Define $\lambda:=t/n\in\left[0,\frac 12\right]$, as well as:
-    \[
-        \mu:=\mu(\lambda):=
+    Let $t, n\in \N$ with $n$ even and $t\le n/2$. 
+    We define $\lambda=t/n\in\left[0,\frac 12\right]$, as well as:
+    \[
+        \mu(\lambda)=
         \begin{cases}
@@
     \]
-    Then for all $a\in\F_2^n$ and $k\in[0,n]$, the following hold true:
-    \[
-        |\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n},\quad |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}.
+    Then, for all $a\in\F_2^n$ and $k\in[0,n]$, the following hold true:
+    \[
+        |\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n},\quad \text{and} \quad  |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}.
     \]
@@
 \begin{proof}
-    To begin, observe that the inequality $|\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}$ will follow from the inequality $|\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n}$ using precisely the arguments of the proof of Corollary~\ref{cor:bound_walsh_cauchy}, so that we are only required to prove the first inequality.
-
-    As before, we want to bound the maximum of $|P_{a,t}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[1,n]$. 
+    To begin, we observe that the inequality $|\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}$ will follow from the inequality $|\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n}$ using precisely the arguments of the proof of Corollary~\ref{cor:bound_walsh_cauchy}, so that we are only required to prove the first inequality.
+
+    As before (in the proof of Theorem~\ref{theorem:bound_D_nka}, we want to bound the maximum of $|P_{a,t}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[1,n]$.
     We write $a=(b,c)$ with $b\in\F_2^{2t}$ and define $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}.    
-
    To find a bound for $|P_{a,t}(z)|$ on $\dis$ that applies to all $a\in\F_2^n$, we would like to bound the quantity $\max_{a\in\F_2^n,z\in\dis}|P_{a,t}(z)|$.
@@
 It follows from Lemma~\ref{lemma:maximizing_args} that it is enough to consider only the cases for which only one of $p,q,r$ is non-zero, and for which only one of $u,v$ is non-zero.
-
-%\pmnote{What is the argument: "maximum implies only one is non-zero" \color{blue} Tim: OK, check above lemma}
-
-%\pmnote{perfect.}
-
    This leaves us with the following cases to consider for $(p,q,r;u,v)$:
@@
     \]
-    The goal will be to prove that the maximum of $g(\alpha):=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{a,t}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$.
+    The goal will be to prove that the maximum of $g(\alpha)=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{a,t}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$.
 Since $g$ is an even function, it is enough to focus on the interval $\alpha\in[0,\pi]$.
@@
     To begin, computing the first derivative of $g$ and applying the \textit{double angle formulas} $\cos(2\alpha)=2\cos^2\alpha-1$ and $\sin(2\alpha)=2\cos\alpha\sin\alpha$ gives:
+
+    \pmnote{Add intermediate computations for the derivative for verifiability}
+
     \[
@@
 To see this, we consider $\mathcal E$ as an equation of second degree in $\cos\alpha$, it leads to the two solutions $\cos\alpha=-\lambda\pm\sqrt{\lambda^2-4\lambda+2}$.
-We can exclude the solution $\cos\alpha=-\lambda-\sqrt{\lambda^2-4\lambda+2}$ since $\cos\alpha\in[-1,1]$.
-The other solution needs to be excluded for the same reason if $\lambda<\frac 16$.
+
+    \pmnote{factor 2 missing?}
+
+    \pmnote{why do you exclude, for $\lambda=0.5$ it is in the range isn't it?}
+
+     We can exclude the solution $\cos\alpha=-\lambda-\sqrt{\lambda^2-4\lambda+2}$ since $\cos\alpha\in[-1,1]$. The other solution needs to be excluded for the same reason if $\lambda<\frac 16$.
 
@@
 For $\lambda=\frac 16$, the solution to the equation $\mathcal E$ is $\cos\alpha=1$, again implying $\alpha_0=0$, and we obtain the same maximum of $2^{2\mu}$.
-In case $\lambda>\frac 16$, the two claims imply that $g(\alpha)$ reaches its maximum at the two values $\alpha_0\in[0,pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$.
+    In case $\lambda>\frac 16$, the two claims imply that $g(\alpha)$ reaches its maximum at the two values $\alpha_0\in[0,\pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$.
 For such $\alpha$, the \textit{double angle formula} for the cosine implies that $\cos(2\alpha_0)=2\lambda^2-4\lambda+2-2\lambda\sqrt{\lambda^2-4\lambda+2}$.

### 2024-11-04 RevisedHiddenWeight.tex

--- 2024-11-04 RevisedHiddenWeight.tex
@@
     \]
-    Then for all $a\in\F_2^n$ and $k\in[1,n]$, the following hold true:
-    \[
-        |\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n},\quad |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}.
+
+    Then, for all $a\in\F_2^n$ and $k\in[0,n]$, the following hold true:
+
+    \[
+        |\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n},\quad \text{and} \quad  |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}.
     \]
@@
 \begin{proof}
-    To begin, observe that the inequality $|\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}$ will follow from the inequality $|\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n}$ using precisely the arguments of the proof of Corollary~\ref{cor:bound_walsh_cauchy}, so that we are only required to prove the first inequality.
+    To begin, we observe that the inequality $|\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}$ will follow from the inequality $|\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n}$ using precisely the arguments of the proof of Corollary~\ref{cor:bound_walsh_cauchy}, so that we are only required to prove the first inequality.
 Also, since the case $\lambda=\frac 12$ corresponds to Theorem~\ref{theorem:bound_D_nka}, we will henceforth assume $\lambda<\frac 12$.
 
-    As before, we want to bound the maximum of $|P_{a,t}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[1,n]$. 
+    As before (in the proof of Theorem~\ref{theorem:bound_D_nka}, we want to bound the maximum of $|P_{a,t}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[1,n]$.
     We write $a=(b,c)$ with $b\in\F_2^{2t}$ and define $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}.    
-
    To find a bound for $|P_{a,t}(z)|$ on $\dis$ that applies to all $a\in\F_2^n$, we would like to bound the quantity $\max_{a\in\F_2^n,z\in\dis}|P_{a,t}(z)|$.
@@
     To begin, computing the first derivative of $g$ and applying the double angle formulas $\cos(2\alpha)=2\cos^2\alpha-1$ and $\sin(2\alpha)=2\cos\alpha\sin\alpha$ gives:
+
+        \pmnote{Add intermediate computations for the derivative for verifiability}
+
     \[
@@
 To see this, we consider $\mathcal E$ as an equation of second degree in $\cos\alpha$, which leads to the two solution candidates $\cos\alpha=-\lambda\pm\sqrt{\lambda^2-4\lambda+2}$.
-We can exclude the solution $\cos\alpha=-\lambda-\sqrt{\lambda^2-4\lambda+2}$ since $\cos\alpha\in[-1,1]$.
-The other solution needs to be excluded for the same reason if $\lambda<\frac 16$.
+
+        \pmnote{factor 2 missing?}
+
+    \pmnote{why do you exclude, for $\lambda=0.5$ it is in the range isn't it?}
+
+    We can exclude the solution $\cos\alpha=-\lambda-\sqrt{\lambda^2-4\lambda+2}$ since $\cos\alpha\in[-1,1]$. The other solution needs to be excluded for the same reason if $\lambda<\frac 16$.
 
@@
 If we replace $\cos\alpha_0$ and $\cos(2\alpha_0)$ by their respective values, we obtain that the maximum of $g(\alpha)$ for $\alpha\in[0,\pi]$ is given by the following value:
+
     \[

### 2024-11-04 RevisedHiddenWeight.tex
Added colorful curve, addressed PM's remarks, changed notation D_{n,k,a} to D_k(a), updated plot of "lines"

@@
 \begin{Corollary}
-	If $r$ is odd, then for $k=n/2$, we have: $\Dnka n{n/2}a=0.$
+	If $r$ is odd, then for $k=n/2$, we have $\Dnka n{n/2}a=0.$
 \end{Corollary}
@@
         \includegraphics[width=7cm]{cauchy_estimate.pdf}
-        \caption{Cauchy estimate in blue vs.\ binomial coefficients in red}
+        \caption{Cauchy estimate in blue vs.\ binomial coefficients in red.}
         \label{fig:cauchy_estimate}
@@
 \subsection{Generalization to a family of weightwise quadratic functions}\label{sec:general}
-In this part, we generalize the results of Section~\ref{sec:Cauchy} to all weightwise quadratic function such that for all $k\in [1,n]$ $f_k$ has exactly $t$ quadratic terms with no shared variables.
+In this part, we generalize the results of Section~\ref{sec:Cauchy} to all weightwise quadratic function such that for all $k\in [1,n]$, the function $f_k$ has exactly $t$ quadratic terms with no shared variables.
 
@@
     \[
-        \mu(\lambda)=
+        \mu(\lambda)=\mu=
         \begin{cases}
@@
     \]
-    The goal will be to prove that the maximum of $g(\alpha)=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{a,t}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$.
-Since $g$ is an even function, it is enough to focus on the interval $\alpha\in[0,\pi]$.
-
-    To begin, computing the first derivative of $g$ and applying the double angle formulas $\cos(2\alpha)=2\cos^2\alpha-1$ and $\sin(2\alpha)=2\cos\alpha\sin\alpha$ gives:
-
-        \pmnote{Add intermediate computations for the derivative for verifiability}
-
-    \[
-        \frac{\dd}{\dd\alpha}g(\alpha)=8(6-2\cos(2\alpha))^{\lambda-1}(2+2\cos\alpha)^{-2\lambda}\sin\alpha\left(\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2\right).
-    \]
+
+    The goal will be to prove that the maximum of $g_\lambda(\alpha)=g(\alpha)=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{a,t}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$.
+Since $g$ is an even function, it is enough to focus on the interval $\alpha\in[0,\pi]$; the function $g$ is represented for several different values of $0\leq\lambda<\frac 12$ in Figure~\ref{fig:family_curves_g}.
+
+    \begin{figure}
+    	\centering
+    	\includegraphics[width=9cm]{family_curves_g.pdf}
+    	\caption{The curves of $\alpha\mapsto g_\lambda(\alpha)$ for the values $\lambda=\frac{i}{25}$ from $i=0$ (blue) to $i=24$ (red).}
+    	\label{fig:family_curves_g}
+    \end{figure}
+
+    Writing $g(\alpha)=g_1(\alpha)^{\lambda}g_2(\alpha)^{1-2\lambda}$ for $g_1(\alpha)=6-2\cos(2\alpha)$ and $g_2(\alpha)=2+2\cos\alpha$, we compute the first derivative of $g$, and apply the double angle formulas $\cos(2\alpha)=2\cos^2\alpha-1$ and $\sin(2\alpha)=2\cos\alpha\sin\alpha$:
+    \begin{align*}
+         \frac{\dd}{\dd\alpha}g(\alpha)&=g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}\left(\lambda g_2(\alpha)\frac{\dd}{\dd\alpha}g_1(\alpha)+(1-2\lambda)g_1(\alpha)\frac{\dd}{\dd\alpha}g_2(\alpha)\right)\\
+         &=g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}\left(\lambda(2+2\cos\alpha)\cdot4\sin(2\alpha)+(1-2\lambda)(6-2\cos(2\alpha))(-2\sin\alpha)\right)\\
+         &=g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}\left(\lambda(2+2\cos\alpha)\cdot4\cdot2\cos\alpha\sin\alpha+(1-2\lambda)\left(8-4\cos^2\alpha\right)(-2\sin\alpha)\right)\\
+         &=8g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}\sin\alpha\left(2\lambda \cos\alpha(1+\cos\alpha)-(1-2\lambda)\left(2-\cos^2\alpha\right)\right)\\
+         &=8g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}\sin\alpha\left(\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2\right).
+    \end{align*}
+
     The only interesting zeros of $\frac{\dd}{\dd\alpha}g(\alpha)$ are those of the last factor 
@@
 To see this, we consider $\mathcal E$ as an equation of second degree in $\cos\alpha$, which leads to the two solution candidates $\cos\alpha=-\lambda\pm\sqrt{\lambda^2-4\lambda+2}$.
-
-        \pmnote{factor 2 missing?}
-
-    \pmnote{why do you exclude, for $\lambda=0.5$ it is in the range isn't it?}
 
@@
 In a similar fashion, it can be proven that $|P_{a,t}(z)|$ is also bounded by $2^{\mu n}$ on $\dis$ for the remaining two cases of $(p,q,r;u,v)$.
-In fact, for $(p,q,r;u,v)=(0,t,0;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h_1(\alpha):=(6-2\cos(2\alpha))^\lambda(2-2\cos\alpha)^{1-2\lambda}$, which has the same maximum as $g(\alpha)$ because $h_1\left(\frac{\pi}{2}+\alpha\right)=g\left(\frac{\pi}{2}-\alpha\right)$; for $(p,q,r;u,v)=(0,0,t;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h_2(\alpha):=(2+2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$, whose maximum is bounded by the maximum of $g(\alpha)$ because $h_2(\alpha)\leq g(\alpha)$.
+In fact, for $(p,q,r;u,v)=(0,t,0;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h_1(\alpha)=(6-2\cos(2\alpha))^\lambda(2-2\cos\alpha)^{1-2\lambda}$, which has the same maximum as $g(\alpha)$ because $h_1\left(\frac{\pi}{2}+\alpha\right)=g\left(\frac{\pi}{2}-\alpha\right)$; for $(p,q,r;u,v)=(0,0,t;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h_2(\alpha)=(2+2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$, whose maximum is bounded by the maximum of $g(\alpha)$ because $h_2(\alpha)\leq g(\alpha)$.
 \end{proof}
@@
 	\includegraphics[width=10cm]{curve_exponents_lambda_mu.pdf}
-	\caption{The curve of $\lambda\mapsto\mu(\lambda)$ with $0\leq\lambda\leq\frac 12$ from Theorem~\ref{theorem:bound_D_nka_generalized}}
+	\caption{The curve of $\lambda\mapsto\mu(\lambda)$ with $0\leq\lambda\leq\frac 12$ from Theorem~\ref{theorem:bound_D_nka_generalized}.}
 	\label{fig:curve_exponents_lambda_mu}
@@
 
-\pmnote{add a link to the public github or name of the name of this code in supplementary materials \color{blue} Tim: Is on GitHub now: \texttt{Bounding\_Walsh.ipynb}}
+\pmnote{add a link to the public github or name of the name of this code in supplementary materials.}
+
+\tsnote{Is on GitHub now: \texttt{Bounding\_Walsh.ipynb}}
 
@@
 	\includegraphics[width=9cm]{comparison_walsh_bound.pdf}
-	\caption{On a logarithmic scale, our experimental bound $B_n$ in terms of $n$ in red, our theoretical bound $1+n\cdot 2^{3n/4}$ from Proposition \ref{cor:bound_walsh_cauchy} in green, and the bound $\binom{n}{n/2}$ in blue.}
+	\caption{On a logarithmic scale, our experimental bound $B_n$ in terms of $n$ in red, our theoretical bound $1+n\cdot 2^{3n/4}$ from Proposition \ref{cor:bound_walsh_cauchy} in green, and the bound $\binom{n}{n/2}$ in blue.
+\tsnote{Updated plot, but the description now needs to be changed.}}
 	\label{fig:walsh_bound_comparison}

### 2024-11-05 RevisedHiddenWeight.tex
Minors

@@
 	\end{tabular}
-	\caption{Values of $\Dnka{2}{k}{a}$}\label{tab:Dnka}
+	\tablecaption{Values of $\Dnka{2}{k}{a}$}\label{tab:Dnka}
 \end{table}
@@
 Denoting by $b$ the vector $\pi(a)+(0,1,0,1,\ldots,0,1)$, we can write the Walsh transform of $f$ in $a$ as:
-\[ \wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}.\]
+\[ \wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}.\qedhere\]
 \end{proof}
@@
     	\end{tabular}
-    	\caption{Values of $\Dnka{n}{k}{a}$ for small values of $k$}\label{tab:Dnka_small_k}
+    	\tablecaption{Values of $\Dnka{n}{k}{a}$ for small values of $k$}\label{tab:Dnka_small_k}
     \end{table}
@@
 Since the minimum of $\mathrm{Re}\left(z^2\right)$ on $\dis$ is $-1$, we conclude that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ is $6-2(-1)=8$.
-
 \end{proof}
@@
 \wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
-&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,2t}(y)+b \cdot y} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c \cdot z}\right)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.%\qedhere
+&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,2t}(y)+b \cdot y} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c \cdot z}\right)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
 \end{align*}
@@
     	\centering
-    	\includegraphics[width=9cm]{family_curves_g.pdf}
+    	\includegraphics[width=11cm]{family_curves_g.pdf}
     	\caption{The curves of $\alpha\mapsto g_\lambda(\alpha)$ for the values $\lambda=\frac{i}{25}$ from $i=0$ (blue) to $i=24$ (red).}
@@
 	\end{tabular}
-	\caption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ compared to the bound $B_n$}
+	\tablecaption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ compared to the bound $B_n$}
 	\label{table:max_walsh_vs_bound}
@@
 	\end{tabular}
-	\caption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ compared to the bound $B_n$ and the one from Corollary~\ref{cor:bound_walsh_cauchy}.}
+	\tablecaption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ compared to the bound $B_n$ and the one from Corollary~\ref{cor:bound_walsh_cauchy}.}
 	\label{table:max_walsh_vs_bound}
@@
 	\end{minipage}
-	\caption{Approximate values of $B_n$ for various values of $n$}
+	\tablecaption{Approximate values of $B_n$ for various values of $n$}
 	\label{table:walsh_bounds}

### 2024-11-05 RevisedHiddenWeight.tex
5.2

--- 2024-11-04 RevisedHiddenWeight.tex
@@
 		The set of weightwise degree-$d$ functions is denoted by $\WD{d}{n}$.
+
+Additionally, a weightwise degree-$d$ function is called cyclic weightwise degree-$d$ function if for all $i\in [1,n]$ it holds $f_i(x)=f_0(O^i(x))$, where $O^i$ denotes the cyclic shift by $i$ positions, $O^i(x_1,\dots,x_n)=(x_{1+i \mod n},\dots,x_{n+i \mod n})$, the representative modulo being taken as an integer between $1$ and $n$.
 \end{definition}
@@
 In~\cite{DAM:MeaOza24}, the parameters of different functions from $\WD{1}{n}$ and $\WD{2}{n}$ are studied experimentally for $n$ up to $20$ and lower bounds are given for the nonlinearity for all $n$.
-These bounds involve sums of binomial coefficients.
+These bounds focus on cyclic weightwise quadratic functions and involve sums of binomial coefficients.
 For simplicity, in the following we provide only the nonlinearity values of the majority function and HWBF, as these bounds will be used for comparison.
@@
 
-In this part we compare the nonlinearity of the function $f$ from Definition~\ref{def:revHWBF} to other weightwise quadratic functions considered for similar use-cases, such as majority, HWBF and the cyclic weightwise quadratic function $t$  from~\cite{DAM:MeaOza24}.
-More precisely, we compare the value $\max_{a\in\mathbb F_2^n}|\wt f(a)|$, the smaller the maximum the better the nonlinearity.
-
-For majority and HWBF, we use the exact values recalled in Property~\ref{prop:wwd1}, for the function $t$ we use the upper bound proven in~\cite{DAM:MeaOza24}. 
-For the revisited HWBF, we consider the theoretical bound from Theorem~\ref{cor:bound_walsh_cauchy} and the experimental one from Section~\ref{sec:expwt}
-
-Figure~\ref{fig:walsh_bound_comparison} compares the experimental bound $B_n$ to the theoretical bound $1+n\cdot 2^{3n/4}$ and the binomial coefficient $\binom{n}{n/2}$, on a logarithmic scale.
-The first two and the last one have an asymptotic slope of $3/4$ and $1$, respectively.
+In this part we compare the nonlinearity of the function $f$ from Definition~\ref{def:revHWBF} to other weightwise quadratic functions considered for similar use-cases, such as majority, HWBF and the cyclic weighwise functions studied in~\cite{DAM:MeaOza24}.
+
+%In Figure~\ref{fig:walsh_bound_comparison} we compare the value $\max_{a\in\mathbb F_2^n}|\wt f(a)|$, the smaller the maximum the better the nonlinearity.
+We display the values for $n$ up to $80$, which is sufficient to compare the asymptotic behavior of the different bounds.
+%The violet and orange curves correspond to the upper bounds proven in~\cite{DAM:MeaOza24}.
+The violet one corresponds to the bound holding for all cyclic weightwise linear function such that $f_0(x)=b\cdot x$ with $\w(b)$ odd.
+It gives for example an upper bound for the HWBF.
+The orange one corresponds to the bound holding the cyclic weightwise quadratic function given by $f_0(x)=x_1+x_2x_3$.
+%The blue curve corresponds to both the majority and HWBF function, whose exact nonlinearity are recalled in Property~\ref{prop:wwd1}.
+We use only one curve since on a logarithmic scale the difference of nonlinearity between these two functions is too small to differentiate the curves.
+%Regarding the revisited HWBF introduced in Definition~\ref{def:revHWBF}, the red curve corresponds to the theoretical bound from Corollary~\ref{cor:bound_walsh_cauchy}, and the green one the experimental approach of Section~\ref{sec:expwt}.
+
+In Figure~\ref{fig:walsh_bound_comparison}, we compare the values of $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$, where a smaller maximum indicates better nonlinearity (see Definition~\ref{def:nl}). 
+We present values for $n$ up to $80$, which is sufficient for examining the asymptotic behavior of the different bounds.
+The violet and orange curves represent the upper bounds  in~\cite{DAM:MeaOza24}.
+The violet curve corresponds to the bound that holds for all cyclic weightwise linear functions where $ f_0(x) = b \cdot x $ with $\w(b)$ odd, providing, for example, an upper bound for the HWBF.
+The orange curve corresponds to the bound for the cyclic weightwise quadratic function defined by $f_0(x) = x_1 + x_2 x_3$.
+The blue curve represents both the majority and HWBF functions, whose exact nonlinearities are given in Property~\ref{prop:wwd1}.
+We use a single curve here because, on a logarithmic scale, the nonlinearity difference between these two functions is too small to distinguish between them.
+For the revisited HWBF introduced in Definition~\ref{def:revHWBF}, the red curve corresponds to the theoretical bound from Corollary~\ref{cor:bound_walsh_cauchy}, while the green curve represents the experimental results from Section~\ref{sec:expwt}.
 
@@
 	\includegraphics[width=9cm]{comparison_walsh_bound.pdf}
-	\caption{On a logarithmic scale, our experimental bound $B_n$ in terms of $n$ in red, our theoretical bound $1+n\cdot 2^{3n/4}$ from Proposition \ref{cor:bound_walsh_cauchy} in green, and the bound $\binom{n}{n/2}$ in blue.
+	\caption{
+		%Maximum of the absolute value of the Walsh spectrum of different functions, in logarithmic scale, for even values of $n$.
+In violet and orange are the bounds for the cyclic weigtwise linear functions and one cyclic weightwise quadratic function from~\cite{DAM:MeaOza24}.
+In blue is the value for the majority function and HWBF.
+The theoretical bound (Corollary~\ref{cor:bound_walsh_cauchy}) for the function $f$ is in red and the experimental one $B_n$ (Section~\ref{sec:expwt}) is in green.}
+		%On a logarithmic scale, our experimental bound $B_n$ in terms of $n$ in red, our theoretical bound $1+n\cdot 2^{3n/4}$ from Proposition \ref{cor:bound_walsh_cauchy} in green, and the bound $\binom{n}{n/2}$ in blue.
 \tsnote{Updated plot, but the description now needs to be changed.}}
+		Maximum absolute values of the Walsh spectrum for various functions, shown on a logarithmic scale for even values of $n$. 
+		The violet and orange curves represent bounds for cyclic weightwise linear functions and a cyclic weightwise quadratic function from~\cite{DAM:MeaOza24}.
+The blue curve shows values for the majority function and HWBF.
+The theoretical bound for the function $f$ (from Corollary~\ref{cor:bound_walsh_cauchy}) is in red, and the experimental bound $B_n$ (Section~\ref{sec:expwt}) is in green.}
 	\label{fig:walsh_bound_comparison}
 \end{figure}
+
+We observe significantly better performance for the newly introduced function $f$ compared to the majority function and HWBF, with the proven bound exhibiting an asymptotic slope of $ 3/4$ as opposed to $1$.
+The two bounds proven in~\cite{DAM:MeaOza24} also have an asymptotic slope of $1$.
+The gap between the red and green curves, both representing upper bounds on $ \max_{a \in \mathbb{F}_2^n} |\wt f(a)| $ (with only the formula for the red curve proven for all even $n$), suggests that the true values may follow an even better slope than $ 3/4$.
+
+In Table~\ref{table:comparisonsNL}, we compare the specific nonlinearity values of the functions under consideration.
+Among the various weightwise quadratic functions studied so far, we observe that $f$ has the highest nonlinearity from $n=10$ onward.
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|c| c|c|c|c| c|c|c|}
+		\hline
+		$n$ & $4$  & $6$  & $8$  &  $10$ & $12$ & $14$ & $16$  \\
+	\hline	
+    	HWBF   & $4$  & $20$  & $88$  &  $372$ & $1544$ & $6344$ & $25904$  \\  	
+   %4 10 20 44 88 186 372 772 1544 3172 6344 12952 25904
+		\hline
+Majority   & $5$  & $22$  & $93$  &  $386$ & $1586$ & $6476$ & $26333$  \\
+\hline
+		%cyclic $f_0=x_1+x_2x_3$
+    	t~\cite{DAM:MeaOza24}   & $4$  & $22$  & $96$  &  $404$ & $1672$ & $6854$ & $27884$\\
+    	%4 10 22 46 96 196 404 816 1672 3358 6854 13722 27884
+\hline	
+%$f_0= x_1 + \sum_{i=1}^{n/2-1}x_{2i}x_{2i+1}$	
+    	u~\cite{DAM:MeaOza24}   & $4$  & $24$  & $104$  &  $456$ & $1888$ & $7816$ & $31616$ \\
+    	%4 10 24 48 104 220 456 924 1888 3862 7816 15748 31616
+\hline
+
+		$f$  & $4$  & $22$  & $102$  &  $458$ & $1902$ & $7842$ & $31680$\\
+\hline
+	\end{tabular}
+	\caption{Comparison of the nonlinearity.}
+	\label{table:comparisonsNL}
+\end{table}
 

### 2024-11-06 RevisedHiddenWeight.tex
Minor corrections

@@
 Indeed, either $p-q\equiv 0\bmod 3$, or $(p-q)^2\equiv 1\bmod 3$, in which case $2(p-q)^2+7\equiv 0\bmod 3$.
+\end{remark}
 
@@
 %    where $M_R$ is the maximum of $|f(z)|$ on the circle $|z-w|=R$.
-where $M_R$ is the maximum of the absolute value of $f$, $|f(z)|$ on the circle defined by $|z-w|=R$.
+where$M_R=\max\{|f(z)|:z\in\C\text{ and } |z-w|=R\}$, the maximum of the absolute value of $f$ on the circle defined by the equation $|z-w|=R$.
 \end{Prop}
@@
     \[
-        |\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n},\quad \text{and} \quad  |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}.
+        |\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n}\quad \text{and} \quad  |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}.
     \]
@@
 
-    As before (in the proof of Theorem~\ref{theorem:bound_D_nka}, we want to bound the maximum of $|P_{a,t}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[1,n]$.
+    As before in the proof of Theorem~\ref{theorem:bound_D_nka}, we want to bound the maximum of $|P_{a,t}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[1,n]$.
     We write $a=(b,c)$ with $b\in\F_2^{2t}$ and define $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}.    
@@
 In case $\lambda>\frac 16$, the two claims imply that $g(\alpha)$ reaches its maximum at the two values $\alpha_0\in[0,\pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$.
-For such $\alpha$, the double angle formula for the cosine implies that $\cos(2\alpha_0)=2\lambda^2-4\lambda+2-2\lambda\sqrt{\lambda^2-4\lambda+2}$.
+For such $\alpha_0$, the double angle formula for the cosine implies that $\cos(2\alpha_0)=2\lambda^2-4\lambda+2-2\lambda\sqrt{\lambda^2-4\lambda+2}$.
 If we replace $\cos\alpha_0$ and $\cos(2\alpha_0)$ by their respective values, we obtain that the maximum of $g(\alpha)$ for $\alpha\in[0,\pi]$ is given by the following value:

### 2024-11-06 RevisedHiddenWeight.tex
More typos

@@
 \begin{definition}[Majority function]\label{def:maj}
-    The \emph{majority function} in $n$ variables is the Boolean function $\textsf{Maj}\in\BN$ defined as:
-    \[
-        \textsf{Maj}(x)=0\iff\w(x)<n/2.
+    The \emph{majority function} in $n$ variables is the Boolean function $\mathsf{Maj}\in\BN$ defined as:
+    \[
+        \mathsf{Maj}(x)=0\iff\w(x)<n/2.
     \]
@@
 \begin{itemize}
-	\item (\eg ~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\textsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
-	\[
-	\NL(\textsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}.
+	\item (\eg ~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\mathsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
+	\[
+	\NL(\mathsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}.
 	\]
@@
 	\end{tabular}
-	\caption{Comparison of the nonlinearity.}
+	\tablecaption{Comparison of the nonlinearity.}
 	\label{table:comparisonsNL}

### 2024-11-06 RevisedHiddenWeight.tex
more 6

--- 2024-11-05 RevisedHiddenWeight.tex
@@
 
-\begin{Prop}[Nonlinearity of some functions from $\WD{1}{n}$\label{prop:wwd1}]
+%\begin{Prop}[Nonlinearity of some functions from $\WD{1}{n}$\label{prop:wwd1}]
+%Let $n\in \N^*$ even, the following hold for the following functions in $\WD{1}{n}$: 
+%\begin{itemize}
+%	\item (\eg ~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\textsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
+%	\[
+%	\NL(\textsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}.
+%	\]
+%	\item (\cite{DAM:WCST14}, Theorem $3$) The HWBF $h$ introduced in Definition~\ref{def:hwbf} satisfies:
+%	\[
+%	\NL(h)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}.
+%	\]	
+%\end{itemize}
+%\end{Prop}
+
+\begin{Prop}[Properties of some functions from $\WD{1}{n}$\label{prop:wwd1}]
 	Let $n\in \N^*$ even, the following hold for the following functions in $\WD{1}{n}$: 
@@
 		\]	
+		\item (\cite{DAM:WCST14}, Theorem $1$) The HWBF $h$ introduced in Definition~\ref{def:hwbf} satisfies $\forall n \ge 3$, $\degg(h)=n-1$. 	
 	\end{itemize}
@@
 \section{Other parameters}
+
+\pmnote{under construction}
+
+\begin{proposition}[Algebraic degree of $f$]
+	Let $n\in \N$ be even, greater than $4$, and $f$ defined as in Definition~\ref{def:revHWBF}, the following holds: $\degg(f)= n-1$.
+\end{proposition}
+\begin{proof}
+	We write $f$ as $q+h$ where $q$ is the quadratic function $\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}$ and $h$ is the HWBF.
+	Using Property~\ref{prop:wwd1} Item $3$, $h$ has degree $n-1\ge 3$, and the function $q$ has no monomial of degree higher than $2$, therefore $\degg(f)=\degg(h)=n+1$.
+
+\end{proof}
+
 \subsection{Algebraic immunity of $f$}
@@
 \begin{proposition}[Algebraic immunity of $f$]
-	Let $n\in \N$ be even, $f$ defined as
+	Let $n\in \N$ be even, $f$ defined (as in Definition~\ref{def:revHWBF}) as
 	$f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k$ and $h$ denote the $n$-variable HWBF, the following holds:
@@
 From~\cite{DAM:WCST14} Theorem 4, the algebraic immunity of the HWBF is at least $\lfloor n/3\rfloor +1$, which leads to $\lfloor n/3\rfloor -1$ for $f$.
+
+ \begin{table}[h!]
+	 \centering
+	 \begin{tabular}{|c|c|c|c|c|}
+		 \hline
+		 $n$ & Nonlinearity & Is Balanced & Algebraic Degree & Algebraic Immunity \\
+		 \hline
+		 2   & 1             & False       & 2               & 1                   \\
+		 4   & 4             & True        & 3               & 2                   \\
+		 6   & 22            & False       & 5               & 3                   \\
+		 8   & 102           & True        & 7               & 4                   \\
+		 10  & 458           & False       & 9               & 5                   \\
+		 12  & 1902          & True        & 11              & 6                   \\
+		 14  & 7842          & False       & 13              & 6                   \\
+		 16  & 31680         & True        & 15              & —                   \\
+		 \hline
+		 \end{tabular}
+	 \tablecaption{Characteristics of Boolean Functions for Different $n$ Values}
+	 \end{table}
 

### 2024-11-06 RevisedHiddenWeight.tex
a bit of section 6

@@
 
-\pmnote{under construction}
+\pmnote{under construction, waiting for the parameters for the FAI}
+
+\subsection{Degree}
 
@@
 
-\subsection{Algebraic immunity of $f$}
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|c| c|c|c|c| c|c|c|}
+		\hline
+		$n$ & $4$  & $6$  & $8$  &  $10$ & $12$ & $14$ & $16$  \\
+		\hline	
+		HWBF   & $3$  & $5$  & $7$  &  $9$ & $11$ & $13$ & $15$  \\  	
+		\hline
+		Majority   & $4$  & $4$  & $8$  &  $8$ & $8$ & $8$ & $16$  \\
+		\hline
+		%cyclic $f_0=x_1+x_2x_3$
+		t~\cite{DAM:MeaOza24}   & $2$  & $5$  & $6$  &  $9$ & $11$ & $13$ & $14$\\
+		\hline	
+		%$f_0= x_1 + \sum_{i=1}^{n/2-1}x_{2i}x_{2i+1}$	
+		u~\cite{DAM:MeaOza24}   & $2$  & $4$  & $6$  &  $8$ & $10$ & $12$ & $14$ \\
+		\hline
+
+		$f$  & $3$  & $5$  & $7$  &  $9$ & $11$ & $13$ & $15$\\
+		\hline
+	\end{tabular}
+	\tablecaption{Comparison of the degree.}
+	\label{table:comparisonsDeg}
+\end{table}
+
+\subsection{Algebraic immunity}
 
@@
 
+\iffalse
  \begin{table}[h!]
@@
 		 14  & 7842          & False       & 13              & 6                   \\
-		 16  & 31680         & True        & 15              & —                   \\
+		 16  & 31680         & True        & 15              & 7                   \\
 		 \hline
@@
 	 \end{table}
+\fi
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|c| c|c|c|c| c|c|c|}
+		\hline
+		$n$ & $4$  & $6$  & $8$  &  $10$ & $12$ & $14$ & $16$  \\
+		\hline	
+		HWBF   & $2$  & $3$  & $4$  &  $4$ & $5$ & $5$ & $6$  \\  	
+		\hline
+		Majority   & $2$  & $3$  & $4$  &  $5$ & $6$ & $7$ & $8$  \\
+		\hline
+		%cyclic $f_0=x_1+x_2x_3$
+		t~\cite{DAM:MeaOza24}   & $2$  & $3$  & $4$  &  $5$ & $5$ & $6$ & $7$\\
+		\hline	
+		%$f_0= x_1 + \sum_{i=1}^{n/2-1}x_{2i}x_{2i+1}$	
+		u~\cite{DAM:MeaOza24}   & $2$  & $3$  & $4$  &  $5$ & $6$ & $6$ & $7$ \\
+		\hline						
+		$f$  & $2$  & $3$  & $4$  &  $5$ & $6$ & $6$ & $7$\\
+		\hline
+	\end{tabular}
+	\tablecaption{Comparison of the algebraic immunity.}
+	\label{table:comparisonsAI}
+\end{table}
+
+\section{Conclusion and open questions}
+\pmnote{TODO or remove}
 

### 2024-11-07 RevisedHiddenWeight.tex
minor 4.3

@@
 
-    As before (in the proof of Theorem~\ref{theorem:bound_D_nka}, we want to bound the maximum of $|P_{a,t}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[1,n]$.
+    As before (in the proof of Theorem~\ref{theorem:bound_D_nka}), we want to bound the maximum of $|P_{a,t}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[1,n]$.
     We write $a=(b,c)$ with $b\in\F_2^{2t}$ and define $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}.    
@@
     \]
-    Let us start by bounding $|P_{a,t}(z)|$ on $\dis$ in case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $t=\lambda n$, we can write:
+    Let us start by bounding $|P_{a,t}(z)|$ on $\dis$ in the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $t=\lambda n$, we can write:
     \[
@@
 
-    We can exclude the solution $\cos\alpha=-\lambda-\sqrt{\lambda^2-4\lambda+2}$ since $\cos\alpha\in[-1,1]$. The other solution needs to be excluded for the same reason if $\lambda<\frac 16$.
+    We can exclude the solution $\cos\alpha=-\lambda-\sqrt{\lambda^2-4\lambda+2}$ since $\cos\alpha\in[-1,1]$ (and $\lambda\in [0,1/2[$). 
+    The other solution needs to be excluded for the same reason if $\lambda<\frac 16$.
 
@@
 In case $\lambda>\frac 16$, the two claims imply that $g(\alpha)$ reaches its maximum at the two values $\alpha_0\in[0,\pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$.
+
+    \pmnote{@Tim, is the expression of $\cos(2\alpha_0)$ correct in the following?
+I think it should be $4\lambda^2-4 \lambda \sqrt{bla} - 8\lambda +3$ instead, which is coherent with the next expression}
+
      For such $\alpha$, the double angle formula for the cosine implies that $\cos(2\alpha_0)=2\lambda^2-4\lambda+2-2\lambda\sqrt{\lambda^2-4\lambda+2}$.
@@
     \]
-    This is exactly what we wanted to prove, and we have therefore covered the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$ entirely.
+    %This is exactly what we wanted to prove, 
+    This is equivalent to the first equation in the theorem statement, 
+    and we have therefore covered the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$ entirely.
 In a similar fashion, it can be proven that $|P_{a,t}(z)|$ is also bounded by $2^{\mu n}$ on $\dis$ for the remaining two cases of $(p,q,r;u,v)$.

### 2024-11-07 RevisedHiddenWeight.tex
Typos in proof of Theorem 3

@@
 For $\lambda=\frac 16$, the solution to the equation $\mathcal E$ is $\cos\alpha=1$, again implying that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and we obtain the same maximum of $2^{2\mu}$.
-In case $\lambda>\frac 16$, the two claims imply that $g(\alpha)$ reaches its maximum at the two values $\alpha_0\in[0,\pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$.
-
-    \pmnote{@Tim, is the expression of $\cos(2\alpha_0)$ correct in the following?
-I think it should be $4\lambda^2-4 \lambda \sqrt{bla} - 8\lambda +3$ instead, which is coherent with the next expression}
-
-     For such $\alpha$, the double angle formula for the cosine implies that $\cos(2\alpha_0)=2\lambda^2-4\lambda+2-2\lambda\sqrt{\lambda^2-4\lambda+2}$.
+In case $\lambda>\frac 16$, the two claims imply that $g(\alpha)$ reaches its maximum at the unique $\alpha_0\in[0,\pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$.
+For this $\alpha_0$, the double angle formula for the cosine implies that $\cos(2\alpha_0)=4\lambda^2-8\lambda+3-4\lambda\sqrt{\lambda^2-4\lambda+2}$.
 If we replace $\cos\alpha_0$ and $\cos(2\alpha_0)$ by their respective values, we obtain that the maximum of $g(\alpha)$ for $\alpha\in[0,\pi]$ is given by the following value:
-
     \[

### 2024-11-12 RevisedHiddenWeight.tex
ok

--- 2024-11-07 RevisedHiddenWeight.tex
@@
 
-\begin{definition}[Algebraic immunity] \label{def:ai}
+\begin{definition}[Algebraic immunity~\cite{EC:MeiPasCar04}] \label{def:ai}
 	The algebraic immunity of a Boolean function $f\in \Bfn{n}$, denoted as $\AI(f)$, is defined as:

### 2024-11-16 RevisedHiddenWeight.tex
Updates from Overleaf
some part 6, bib, and pre-intro

@@
 }
+
+recent developpement stream ciphers
+
+\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24}
+
+HHE \cite{CCS:NaeLauVai11}
+
+FLIP~\cite{EC:MJSC16}
+
+RASTA~\cite{C:Rasta}
+
+FiLIP~\cite{INDO:MCJS19}
+
+HWBF:
+
+\cite{IEEE:Bryant91}
+
+\cite{IEEE:Carlet22}
+
+\cite{eprint:CarPar23}
+
+\cite{DAM:MeaOza24}
 
@@
 When $n$ is even, the nonlinearity of a function can reach at most $2^{n-1}-2^{n/2 -1}$.
-Functions reaching this maximum are called bent functions.
+Functions reaching this maximum are called bent functions, due to their multiple applications and importance they have been the focus of multiple works \eg \cite{Rothaus76,FSE:Dobbertin95,DBLP:conf/itw/BudaghyanCH11,Tokareva15,Mesnager16}.
 The quadratic function $d_n$ given by: $d_n(x)=\sum_{i \text{ odd}}^n x_i x_{i+1}$ is an example of bent function.
+
+The algebraic degree of multiples of a Boolean function is a crucial criterion for various attacks on stream ciphers that utilize a Boolean function as a filter.
+The well-known algebraic attack~\cite{EC:CouMei03} and fast algebraic attack~\cite{C:Courtois03} on filtered LFSRs have motivated the study of cryptographic properties such as algebraic immunity and fast algebraic immunity, investigated in numerous works (\eg \cite{C:HawRos04,ISC:JiaZhaWan13})).
+
+Nowadays, these parameters are systematically determined for any function considered as a filter.
 
@@
 	The function $g$ is called an annihilator of $f$ (or $f + 1$). 
+\end{definition}
+
+\begin{definition}[Fast algebraic immunity, \eg \cite{EC:ACGKMR06}]\label{def:fai} The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined as $\FAI(f)=\min \{ 2 \AI(f), \min _{1 \le \degg(g)<\AI(f)} (\degg(g)+ \degg(fg))\}$.
 \end{definition}
@@
 
-\begin{theorem}[Balancedness of $f$]
+\begin{theorem}[Balancedness of $f$]\label{th:bal}
 	Let $n \in \N^*$ even, and $f$ be the $n$-variable function from Definition~\ref{def:revHWBF}, the following holds on its Walsh transform in $0_n$:
@@
 
-\section{Experiments and comparisons}
+\section{Experiments and comparisons}\label{sec:expAndComp}
 
@@
 
-\pmnote{under construction}
-
 In this part we compare the nonlinearity of the function $f$ from Definition~\ref{def:revHWBF} to other weightwise quadratic functions considered for similar use-cases, such as majority, HWBF and the cyclic weighwise functions studied in~\cite{DAM:MeaOza24}.
@@
 
-\pmnote{under construction, waiting for the parameters for the FAI}
-
-\subsection{Degree}
+In this part we give the other cryptographic parameters of the function $f$.
+Since its balancedness is characterized by Theorem~\ref{th:bal} and its nonlinearity deeply analyzed in Section~\ref{sec:Cauchy} and Section~\ref{sec:expAndComp}, in the following we focus on the algebraic properties.
+More precisely we analyze the degree, algebraic immunity and fast algebraic immunity of $f$, providing comparisons with other weightwise quadratic functions.
+
+%\pmnote{under construction, waiting for the parameters for the FAI}
+
+%\subsection{Degree}
 
@@
 \end{proof}
+
+In Table~\ref{table:comparisonsDeg}, we display the algebraic degree of different weightwise quadratic function. We observe that $f$ is the function with higher degree, jointly with the HWBF.
 
@@
 
-\subsection{Algebraic immunity}
+%\subsection{Algebraic immunity}
 
@@
 From~\cite{DAM:WCST14} Theorem 4, the algebraic immunity of the HWBF is at least $\lfloor n/3\rfloor +1$, which leads to $\lfloor n/3\rfloor -1$ for $f$. 
+In Table~\ref{table:comparisonsAI}, we present the algebraic immunity of various weightwise quadratic functions.
+We observe that the function $f$ demonstrates the best performance after the majority function, which is known to achieve optimal algebraic immunity.
 
@@
 	\label{table:comparisonsAI}
+\end{table}
+
+Additionally, we considered the fast algebraic immunity of $f$ (see Definition~\ref{def:FAI}).
+In Table~\ref{table:FAI} we give the best couples $(d,e)$ encountered for the function $f$, where $fg=h$, $\degg(g)=d, \degg(h)=e$.
+
+These various results on the algebraic properties of $f$ suggest that it possesses strong resistance against standard attacks.
+Additionally, its high nonlinearity makes it a well-suited candidate for use as a filter function in contexts such as filtered LFSRs or in homomorphically-friendly schemes like FLIP and FiLIP.
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+		\hline
+		$ n $      & $4$     & $6$     & $8$     & $10$    & $12$    & $14$    & $16$    & $18$    \\ \hline
+		$(d, e)$ & $(1,2)$ & $(1,3)$ & $(1,5)$  & $(1,7)$ & $(1,9)$ & $(1,11)$ & $(1,13)$ & $(1,15)$ \\ 
+		 &     &    & $(2,4)$  & $(2,6)$ & $(2,8)$ & $(2,10)$ & $(2,12)$ & $(2,14)$\\ 
+		 &     &    &     & $(3,5)$ & $(3,6)$ & $(3,9)$ & $(3,11)$ & $(3,13)$\\ 
+		 &     &    &     &  &  &  & $(4,9)$ & $(4,11)$\\ 
+	 &     &    &     &  &  &  &  & $(5,10)$ \\ \hline
+	\end{tabular}
+	\caption{Lowest possible values of $(d, e)$ for different values of $ n$}
+	\label{table:FAI}
 \end{table}

### 2024-11-19 RevisedHiddenWeight.tex
intro first

@@
 \begin{document}
-	\title{Revisited hidden weight bit function}
-
-	\titlerunning{Revisited Hidden weight bit function}
+	\title{The revisited hidden weight bit function}
+
+	\titlerunning{The revisited Hidden weight bit function}
 \author{
@@
 
-\pmnote{short intro:
-
-HWBF introduced in x, interesting for its cryptographic criteria and easy implementation. cryptographic properties studied in y such as balancedness, algebraic immunity and nonlinearity. 
-New potential uses in a stream cipher, or modifications. Use: transciphering and works aiming at finding Boolean functions easy to evaluate homomorphically, input oblivious algorithms. 
-Nonlinearity a bit low for direct use.
-
-Contributions: new function as addition of HWBF and quadratic bent function.
+%\pmnote{short intro:
+
+%HWBF introduced in x, interesting for its cryptographic criteria and easy implementation. cryptographic properties studied in y such as balancedness, algebraic immunity and nonlinearity. 
+%New potential uses in a stream cipher, or modifications. Use: transciphering and works aiming at finding Boolean functions easy to evaluate homomorphically, input oblivious algorithms. 
+%Nonlinearity a bit low for direct use.
+
+%Contributions: new function as addition of HWBF and quadratic bent function.
 We show when the function is balanced, formalize and study its nonlinearity.
@@
 
-}
-
-recent developpement stream ciphers
-
-\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24}
-
-HHE \cite{CCS:NaeLauVai11}
-
-FLIP~\cite{EC:MJSC16}
-
-RASTA~\cite{C:Rasta}
-
-FiLIP~\cite{INDO:MCJS19}
-
-HWBF:
-
-\cite{IEEE:Bryant91}
-
-\cite{IEEE:Carlet22}
-
-\cite{eprint:CarPar23}
-
-\cite{DAM:MeaOza24}
+%}
+
+\iffalse
+%prompt
+
+The Hamming Weight Bit Function (HWBF) has received a lot of attention since its introduction by Bryant
+in $1991$~\cite{IEEE:Bryant91}, it has been considered as the simplest example of function with binary decision
+diagram of exponential size~\cite{IEEE:Bryant91,TIA:BoLSW99}. 
+The facility of implementing this function in different models of computation since it consists in computing the Hamming weight of the input and applying a simple linear function, and it relatively good cryptographic properties exhibited in~\cite{DAM:WCST14} (balancedness, nonlinearity, degree and algebraic immunity) made it an interesting starting point candidate to design the filter of some streamcipher constructions.
+
+Recently, new developpements in stream ciphers lead to reconsider this function.
+The new potential uses of stream ciphers with filter functions on a larger number number of variables such as Hybrid Homomorphic Encryption~\cite{CCS:NaeLauVai11} (HHE) gave a regain of interest in these functions.
+HHE aims at finding Boolean functions efficient to evaluate as an input oblivious algorithm.
+For example various new binary stream ciphers have been designed since $2016$ such as Kreyvium~\cite{JOC:CCFLNP18}, FLIP~\cite{EC:MJSC16}, Rasta~\cite{C:Rasta}, FiLIP~\cite{INDO:MCJS19} and Dasta~\cite{TOSC:BeiLea20}.
+Currently, the designs with Boolean functions with more than one hundred variables as a filter are the ones leading to the HHE with best latency~\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24}.
+%cite FHE for MPC?
+
+The nonlinearity of the HWBF being low for a direct use as filter function, several generalizations have been considered recently, aiming at strengthening this parameter and keeping or improving the others cryptographic relevent parameters such as balancedness, algebraic degree and and algebraic immunity.
+In these generalizations we count the functions introduced in~\cite{IEEE:Carlet22,eprint:CarPar23,DAM:MeaOza24}.
+The later article considers some functions obtained by computing the Hamming weight of the input and then simply applying a quadratic Boolean function.
+
+In this article we consider another function that is weightwise quadratic, obtained by xoring the HWBF and a bent quadratic function.
+Therefore, we exhibit a family of Boolean functions both easy to compute and with good parameters, improving over the ones exhibited in~\cite{DAM:MeaOza24}.
+Various of the techniques we introduce to determine the nonlinearity are of independent interest, and allow to bound the maximum of the absolute Walsh spectrum for a wider family of weightwise quadratic functions.
+Our contributions are the following:
+
+\begin{itemize}
+	\item In Section~\ref{sec:defAndBal}, we defined the revisited HWBF $f$, and study its balancedness.
+This part is done by studying the (restricted) Walsh transform of some quadratic functions over sets of fixed Hamming weight, called slices.
+A recursive relation between these values allows to determine for which values of $n$ the function is balanced.
+	\item In Section~\ref{sec:dnk}, we link the maximum Walsh coefficients of the revisited HWBF to the coefficients of generating functions and use techniques from complex analysis to prove lower bounds on the nonlinearity of $f$.
+	Differing from usual results in Boolean function used in cryptography, this allows us to determine a good enough bound on the nonlinearity for a larger family of functions, and for all even number of variables $n$.
+	\item In Section~\ref{sec:expAndComp}, we explain techniques to get a better bound for bounded values of $n$, giving a tighter bound for the nonlinearity of $f$ up to $n=80$.
+In this parts with experiments, we compare the bounds we obtain and the real value of the nonlinearity between $f$ and other weightwise quadratic functions such as the majority function, the HWBF, and the two main examples from~\cite{DAM:MeaOza24}.
+These results show a neat advantage for the revisited HWBF relatively the nonlinearity compared to function with similar computation costs.
+	\item In Section~\ref{sec:otherParameters} we analyze the other cryptographic relevant parameters of $f$, such as degree, algebraic immunity and fast algebraic immunity.
+Similarly to the comparison for the nonlinearity the revisited HWBF performs better or similarly to the function with similar computation costs.
+
+\end{itemize}
+
+\fi
+
+The Hamming Weight Bit Function (HWBF) has attracted significant attention since its introduction by Bryant in 1991~\cite{IEEE:Bryant91}.
+It has been regarded as the simplest example of a function whose binary decision diagram has exponential size~\cite{IEEE:Bryant91,TIA:BoLSW99}.
+The ease of implementing this function across various computational models—owing to its reliance on computing the Hamming weight of the input and applying a simple linear function—combined with its relatively strong cryptographic properties, as demonstrated in~\cite{DAM:WCST14} (e.g., balancedness, nonlinearity, degree, and algebraic immunity), has made it an intriguing candidate for use as a filter function in stream cipher constructions.
+
+Recent developments in stream ciphers have reignited interest in this function.
+The emergence of new applications for stream ciphers with filter functions on a larger number of variables—such as Hybrid Homomorphic Encryption (HHE)~\cite{CCS:NaeLauVai11}—has further emphasized the relevance of such functions.
+HHE requires Boolean functions that can be efficiently evaluated in an input-oblivious algorithm.
+For instance, several new binary stream ciphers have been proposed since 2016, including Kreyvium~\cite{JOC:CCFLNP18}, FLIP~\cite{EC:MJSC16}, Rasta~\cite{C:Rasta}, FiLIP~\cite{INDO:MCJS19}, and Dasta~\cite{TOSC:BeiLea20}.
+Currently, designs employing Boolean functions with more than one hundred variables as filters lead to HHE schemes with the best latency~\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24}.
+
+The HWBF, while efficient to compute, suffers from low nonlinearity, which limits its direct application as a filter function.
+Consequently, various generalizations have been explored to enhance this parameter while preserving or improving other cryptographically relevant properties, such as balancedness, algebraic degree, and algebraic immunity.
+Notable examples include functions introduced in~\cite{IEEE:Carlet22,eprint:CarPar23} and~\cite{DAM:MeaOza24}.
+The latter work considers functions obtained by computing the Hamming weight of the input and applying a quadratic Boolean function, called weightwise quadratic functions.
+
+In this article, we propose a new generalization of the HWBF, a weightwise quadratic function constructed by XORing the HWBF with a bent quadratic function.
+This leads to a family of Boolean functions that are computationally efficient and exhibit superior cryptographic properties compared to previous constructions.
+Additionally, the techniques we introduce to analyze nonlinearity have broader applicability and provide bounds on the maximum absolute Walsh spectrum for a wider class of weightwise quadratic functions.
+
+Our contributions are as follows:
+\begin{itemize}
+	\item Balancedness analysis (Section~\ref{sec:defAndBal}):
+We define the revisited HWBF, called $f$, and analyze its balancedness.
+This involves studying the (restricted) Walsh transform of specific quadratic functions over sets of fixed Hamming weights (called slices).
+By establishing recursive relations for these values, we determine for which values of $n$ the function is balanced.
+
+\item Nonlinearity bounds (Section~\ref{sec:dnk}):
+We relate the maximum Walsh coefficients of the revisited HWBF to the coefficients of generating functions and employ complex analysis techniques to prove lower bounds on the nonlinearity of $f$. 
+Unlike most studies on Boolean functions used in cryptography, this approach yields strong nonlinearity bounds for a broader class of functions and for all even numbers of variables $n$.
+
+\item Experimental results and comparisons (Section~\ref{sec:expAndComp}): 
+For bounded values of $n$, we employ specific techniques to refine the nonlinearity bounds of $f$, providing tighter estimates up to $n = 80$.
+Through experiments, we compare these bounds with actual nonlinearity values for $f$ and other weightwise quadratic functions, such as the majority function, HWBF, and the two main examples in~\cite{DAM:MeaOza24}.
+Our results highlight the revisited HWBF's superior nonlinearity relative to functions with similar computational costs.
+
+\item Analysis of other cryptographic parameters (Section~\ref{sec:otherParameters}):  
+We evaluate other cryptographically relevant parameters of $f$, including degree, algebraic immunity, and fast algebraic immunity.
+Similar to the nonlinearity analysis, the revisited HWBF outperforms or matches other functions with comparable computational costs.
+
+\end{itemize}
 
@@
 
-\section{Revisited HWBF and balancedness}
+\section{Revisited HWBF and balancedness}\label{sec:defAndBal}
 %\subsection{Restricted Walsh transform of $f$ in a recursive fashion}
@@
 
-\section{Extensive study of $\Dnka nka$ and bounds on the Walsh spectrum of $f$}
+\section{Extensive study of $\Dnka nka$ and bounds on the Walsh spectrum of $f$}\label{sec:dnk}
 
@@
 
-\section{Other parameters}
+\section{Other parameters}\label{sec:otherParameters}
 

### 2024-11-19 RevisedHiddenWeight.tex
modif comment, polish citations.

@@
 
+\pmnote{add a small abstract, usually summary of introduction}		
 	\end{abstract}
@@
 
+\pmnote{proofread and modify introduction}
+
 The Hamming Weight Bit Function (HWBF) has attracted significant attention since its introduction by Bryant in 1991~\cite{IEEE:Bryant91}.
@@
 HHE requires Boolean functions that can be efficiently evaluated in an input-oblivious algorithm.
-For instance, several new binary stream ciphers have been proposed since 2016, including Kreyvium~\cite{JOC:CCFLNP18}, FLIP~\cite{EC:MJSC16}, Rasta~\cite{C:Rasta}, FiLIP~\cite{INDO:MCJS19}, and Dasta~\cite{TOSC:BeiLea20}.
-Currently, designs employing Boolean functions with more than one hundred variables as filters lead to HHE schemes with the best latency~\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24}.
+For instance, several new binary stream ciphers have been proposed since 2016, including Kreyvium~\cite{JOC:CCFLNP18}, FLIP~\cite{EC:MJSC16}, Rasta~\cite{C:Rasta}, FiLIP~\cite{INDO:MCJS19}, Dasta~\cite{TOSC:BeiLea20} and Fasta~\cite{CTRSA:CidIndRad22}.
+Currently, designs employing Boolean functions with more than one hundred variables as filters lead to HHE schemes with the best latency~\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24,eprint:AGHM24}.
 
@@
 
+\pmnote{Add here the other notations we took if not explained locally or in the other parts of preliminaries}
+
 For $v$ a binary vector of length $n$ we denote by $\w(v)$ its Hamming weight: $\w(v)=|\{i\in [1,n] \, | \, x_i=1\}|$.
-
-\pmnote{Preliminaries to adapt}
 
@@
 The algebraic degree of multiples of a Boolean function is a crucial criterion for various attacks on stream ciphers that utilize a Boolean function as a filter.
-The well-known algebraic attack~\cite{EC:CouMei03} and fast algebraic attack~\cite{C:Courtois03} on filtered LFSRs have motivated the study of cryptographic properties such as algebraic immunity and fast algebraic immunity, investigated in numerous works (\eg \cite{C:HawRos04,ISC:JiaZhaWan13})).
+The well-known algebraic attack~\cite{EC:CouMei03} and fast algebraic attack~\cite{C:Courtois03} on filtered LFSRs have motivated the study of cryptographic properties such as algebraic immunity and fast algebraic immunity, investigated in numerous works (\eg \cite{FSE:Armknecht04,C:HawRos04,ISC:JiaZhaWan13})).
 
@@
 
-\begin{definition}[Fast algebraic immunity, \eg \cite{EC:ACGKMR06}]\label{def:fai} The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined as $\FAI(f)=\min \{ 2 \AI(f), \min _{1 \le \degg(g)<\AI(f)} (\degg(g)+ \degg(fg))\}$.
+\begin{definition}[Fast algebraic immunity, \eg \cite{EC:ACGKMR06}]\label{def:FAI} The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined as $\FAI(f)=\min \{ 2 \AI(f), \min _{1 \le \degg(g)<\AI(f)} (\degg(g)+ \degg(fg))\}$.
 \end{definition}
@@
 
+\pmnote{Show me screenshots proving that 2 and 4 are correct}
+
 Using Proposition \ref{proposition:generating_fct}, we can also deduce some sums involving the $\Dnka nka$:
@@
 
-\pmnote{add a link to the public github or name of the name of this code in supplementary materials.}
-
-\tsnote{Is on GitHub now: \texttt{Bounding\_Walsh.ipynb}}
+\pmnote{Create a public github with all the code (not the .tex) used relatively to the article.
+We will give this link for the public version.
+Fot the anonymous one we will not mention the git, and only add the files in supplementary material.}
+
+%\pmnote{add a link to the public github or name of the name of this code in supplementary materials.}
+
+%\tsnote{Is on GitHub now: \texttt{Bounding\_Walsh.ipynb}}
 
@@
 \section{Conclusion and open questions}
-\pmnote{TODO or remove}
+\pmnote{add a small conclusion (summary of contributions), and elaborate on an opean question, for example on how the Cauchy estimate could be used for more families, other quadratic functions or more easily higher degree ones.}
+
+\ifnum\anon=0
+\section{Acknowledgments}
+Pierrick Méaux was supported by the ERC Advanced Grant no. 787390.
+\fi
 

### 2024-11-21 RevisedHiddenWeight.tex
Added Abstract, checked 1 (Intro) and 2 (Prelim)

@@
 \begin{document}
-	\title{The revisited hidden weight bit function}
-
-	\titlerunning{The revisited Hidden weight bit function}
+    \setcounter{page}{1} 
+	\title{The Revisited Hidden Weight Bit Function}
+
+	\titlerunning{The Revisited Hidden Weight Bit Function}
 \author{
@@
 	\and
-	Shanghai Jiao Tong University, Shanghai, China.\\
+	Shanghai Jiao Tong University, Shanghai, China\\
 	\email{dengtang@sjtu.edu.cn}
@@
 	\begin{abstract}
-
-\pmnote{add a small abstract, usually summary of introduction}		
+	The Hidden Weight Bit Function (\hwbf{}) has drawn considerable attention for its simplicity and cryptographic potential.
+Despite its ease of implementation and favorable algebraic properties, its low nonlinearity limits its direct application in modern cryptographic designs.
+In this work, we revisit the \hwbf{} and propose a new weightwise quadratic variant obtained by combining the \hwbf{} with a bent function.
+This construction offers improved cryptographic properties while remaining computationally efficient.
+We analyze the balancedness, nonlinearity, and other criteria of this function, presenting theoretical bounds and experimental results to highlight its advantages over existing functions in similar use cases.
+%Tim: Check abstract
 	\end{abstract}
@@
 
-The Hamming Weight Bit Function (HWBF) has received a lot of attention since its introduction by Bryant
+The Hidden Weight Bit Function (\hwbf{}) has received a lot of attention since its introduction by Bryant
 in $1991$~\cite{IEEE:Bryant91}, it has been considered as the simplest example of function with binary decision
 diagram of exponential size~\cite{IEEE:Bryant91,TIA:BoLSW99}. 
-The facility of implementing this function in different models of computation since it consists in computing the Hamming weight of the input and applying a simple linear function, and it relatively good cryptographic properties exhibited in~\cite{DAM:WCST14} (balancedness, nonlinearity, degree and algebraic immunity) made it an interesting starting point candidate to design the filter of some streamcipher constructions.
-
-Recently, new developpements in stream ciphers lead to reconsider this function.
-The new potential uses of stream ciphers with filter functions on a larger number number of variables such as Hybrid Homomorphic Encryption~\cite{CCS:NaeLauVai11} (HHE) gave a regain of interest in these functions.
-HHE aims at finding Boolean functions efficient to evaluate as an input oblivious algorithm.
+The facility of implementing this function in different models of computation since it consists in computing the Hamming weight of the input and applying a simple linear function, and it relatively good cryptographic properties exhibited in~\cite{DAM:WCST14} (balancedness, nonlinearity, degree and algebraic immunity) made it an interesting starting point candidate to design the filter of some stream cipher constructions.
+
+Recently, new developments in stream ciphers lead to reconsider this function.
+The new potential uses of stream ciphers with filter functions on a larger number number of variables such as Hybrid Homomorphic Encryption~\cite{CCS:NaeLauVai11} (\textsf{HHE}) gave a regain of interest in these functions.
+\textsf{HHE} aims at finding Boolean functions efficient to evaluate as an input oblivious algorithm.
 For example various new binary stream ciphers have been designed since $2016$ such as Kreyvium~\cite{JOC:CCFLNP18}, FLIP~\cite{EC:MJSC16}, Rasta~\cite{C:Rasta}, FiLIP~\cite{INDO:MCJS19} and Dasta~\cite{TOSC:BeiLea20}.
-Currently, the designs with Boolean functions with more than one hundred variables as a filter are the ones leading to the HHE with best latency~\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24}.
+Currently, the designs with Boolean functions with more than one hundred variables as a filter are the ones leading to the \textsf{HHE} with best latency~\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24}.
 %cite FHE for MPC?
 
-The nonlinearity of the HWBF being low for a direct use as filter function, several generalizations have been considered recently, aiming at strengthening this parameter and keeping or improving the others cryptographic relevent parameters such as balancedness, algebraic degree and and algebraic immunity.
+The nonlinearity of the \hwbf{} being low for a direct use as filter function, several generalizations have been considered recently, aiming at strengthening this parameter and keeping or improving the others cryptographic relevant parameters such as balancedness, algebraic degree and and algebraic immunity.
 In these generalizations we count the functions introduced in~\cite{IEEE:Carlet22,eprint:CarPar23,DAM:MeaOza24}.
@@
 
-In this article we consider another function that is weightwise quadratic, obtained by xoring the HWBF and a bent quadratic function.
+In this article we consider another function that is weightwise quadratic, obtained by \textsf{XOR}-ing the \hwbf{} and a bent quadratic function.
 Therefore, we exhibit a family of Boolean functions both easy to compute and with good parameters, improving over the ones exhibited in~\cite{DAM:MeaOza24}.
@@
 \begin{itemize}
-	\item In Section~\ref{sec:defAndBal}, we defined the revisited HWBF $f$, and study its balancedness.
+	\item In Section~\ref{sec:defAndBal}, we defined the revisited \hwbf{} $f$, and study its balancedness.
 This part is done by studying the (restricted) Walsh transform of some quadratic functions over sets of fixed Hamming weight, called slices.
 A recursive relation between these values allows to determine for which values of $n$ the function is balanced.
-	\item In Section~\ref{sec:dnk}, we link the maximum Walsh coefficients of the revisited HWBF to the coefficients of generating functions and use techniques from complex analysis to prove lower bounds on the nonlinearity of $f$.
+	\item In Section~\ref{sec:dnk}, we link the maximum Walsh coefficients of the revisited \hwbf{} to the coefficients of generating functions and use techniques from complex analysis to prove lower bounds on the nonlinearity of $f$.
 	Differing from usual results in Boolean function used in cryptography, this allows us to determine a good enough bound on the nonlinearity for a larger family of functions, and for all even number of variables $n$.
 	\item In Section~\ref{sec:expAndComp}, we explain techniques to get a better bound for bounded values of $n$, giving a tighter bound for the nonlinearity of $f$ up to $n=80$.
-In this parts with experiments, we compare the bounds we obtain and the real value of the nonlinearity between $f$ and other weightwise quadratic functions such as the majority function, the HWBF, and the two main examples from~\cite{DAM:MeaOza24}.
-These results show a neat advantage for the revisited HWBF relatively the nonlinearity compared to function with similar computation costs.
+In this parts with experiments, we compare the bounds we obtain and the real value of the nonlinearity between $f$ and other weightwise quadratic functions such as the majority function, the \hwbf{}, and the two main examples from~\cite{DAM:MeaOza24}.
+These results show a neat advantage for the revisited \hwbf{} relatively the nonlinearity compared to function with similar computation costs.
 	\item In Section~\ref{sec:otherParameters} we analyze the other cryptographic relevant parameters of $f$, such as degree, algebraic immunity and fast algebraic immunity.
-Similarly to the comparison for the nonlinearity the revisited HWBF performs better or similarly to the function with similar computation costs.
+Similarly to the comparison for the nonlinearity the revisited \hwbf{} performs better or similarly to the function with similar computation costs.
 
@@
 
-\pmnote{proofread and modify introduction}
-
-The Hamming Weight Bit Function (HWBF) has attracted significant attention since its introduction by Bryant in 1991~\cite{IEEE:Bryant91}.
+The Hidden Weight Bit Function (\hwbf{}) has attracted significant attention since its introduction by Bryant in 1991~\cite{IEEE:Bryant91}.
 It has been regarded as the simplest example of a function whose binary decision diagram has exponential size~\cite{IEEE:Bryant91,TIA:BoLSW99}.
-The ease of implementing this function across various computational models—owing to its reliance on computing the Hamming weight of the input and applying a simple linear function—combined with its relatively strong cryptographic properties, as demonstrated in~\cite{DAM:WCST14} (e.g., balancedness, nonlinearity, degree, and algebraic immunity), has made it an intriguing candidate for use as a filter function in stream cipher constructions.
+The ease of implementing this function across various computational models—owing to its reliance on computing the Hamming weight of the input and applying a simple linear function—combined with its relatively strong cryptographic properties as demonstrated in~\cite{DAM:WCST14} (\eg, balancedness, nonlinearity, degree, and algebraic immunity), has made it a noteworthy candidate for use as a filter function in stream cipher constructions.
 
 Recent developments in stream ciphers have reignited interest in this function.
-The emergence of new applications for stream ciphers with filter functions on a larger number of variables—such as Hybrid Homomorphic Encryption (HHE)~\cite{CCS:NaeLauVai11}—has further emphasized the relevance of such functions.
-HHE requires Boolean functions that can be efficiently evaluated in an input-oblivious algorithm.
+The emergence of new applications for stream ciphers with filter functions on a larger number of variables—such as Hybrid Homomorphic Encryption (\textsf{HHE})~\cite{CCS:NaeLauVai11}—has further emphasized the relevance of such functions.
+\textsf{HHE} requires Boolean functions that can be efficiently evaluated in an input-oblivious algorithm.
 For instance, several new binary stream ciphers have been proposed since 2016, including Kreyvium~\cite{JOC:CCFLNP18}, FLIP~\cite{EC:MJSC16}, Rasta~\cite{C:Rasta}, FiLIP~\cite{INDO:MCJS19}, Dasta~\cite{TOSC:BeiLea20} and Fasta~\cite{CTRSA:CidIndRad22}.
-Currently, designs employing Boolean functions with more than one hundred variables as filters lead to HHE schemes with the best latency~\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24,eprint:AGHM24}.
-
-The HWBF, while efficient to compute, suffers from low nonlinearity, which limits its direct application as a filter function.
+Currently, designs employing Boolean functions with more than one hundred variables as filters lead to \textsf{HHE} schemes with the best latency~\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24,eprint:AGHM24}.
+
+The \hwbf{}, while efficient to compute, suffers from low nonlinearity, which limits its direct application as a filter function.
 Consequently, various generalizations have been explored to enhance this parameter while preserving or improving other cryptographically relevant properties, such as balancedness, algebraic degree, and algebraic immunity.
 Notable examples include functions introduced in~\cite{IEEE:Carlet22,eprint:CarPar23} and~\cite{DAM:MeaOza24}.
-The latter work considers functions obtained by computing the Hamming weight of the input and applying a quadratic Boolean function, called weightwise quadratic functions.
-
-In this article, we propose a new generalization of the HWBF, a weightwise quadratic function constructed by XORing the HWBF with a bent quadratic function.
-This leads to a family of Boolean functions that are computationally efficient and exhibit superior cryptographic properties compared to previous constructions.
+The latter work considers functions obtained by computing the Hamming weight of the input and applying a quadratic Boolean function, so-called weightwise quadratic functions.
+
+\bigskip
+In this article, we propose a new generalization of the \hwbf{}, a weightwise quadratic function constructed by \textsf{XOR}-ing the \hwbf{} with a bent quadratic function.
+This leads to a family of Boolean functions that are computationally efficient and feature superior cryptographic properties compared to previous constructions.
 Additionally, the techniques we introduce to analyze nonlinearity have broader applicability and provide bounds on the maximum absolute Walsh spectrum for a wider class of weightwise quadratic functions.
-
 Our contributions are as follows:
 \begin{itemize}
-	\item Balancedness analysis (Section~\ref{sec:defAndBal}):
-We define the revisited HWBF, called $f$, and analyze its balancedness.
+	\item\emph{Balancedness analysis} (Section~\ref{sec:defAndBal}): We define the revisited \hwbf{} in $n$ variables, hereafter denoted by $f$, and analyze its balancedness.
 This involves studying the (restricted) Walsh transform of specific quadratic functions over sets of fixed Hamming weights (called slices).
@@
 
-\item Nonlinearity bounds (Section~\ref{sec:dnk}):
-We relate the maximum Walsh coefficients of the revisited HWBF to the coefficients of generating functions and employ complex analysis techniques to prove lower bounds on the nonlinearity of $f$. 
-Unlike most studies on Boolean functions used in cryptography, this approach yields strong nonlinearity bounds for a broader class of functions and for all even numbers of variables $n$.
-
-\item Experimental results and comparisons (Section~\ref{sec:expAndComp}): 
+    \item \emph{Nonlinearity bounds} (Section~\ref{sec:dnk}):
+    We relate the maximum Walsh coefficients of the revisited \hwbf{} to the coefficients of generating functions and employ complex analysis techniques to prove lower bounds on the nonlinearity of $f$.
+    Unlike most studies on Boolean functions used in cryptography, this approach yields strong nonlinearity bounds for a broader class of functions and for all even $n$.
+
+    \item \emph{Experimental results and comparisons} (Section~\ref{sec:expAndComp}): 
     For bounded values of $n$, we employ specific techniques to refine the nonlinearity bounds of $f$, providing tighter estimates up to $n = 80$.
-Through experiments, we compare these bounds with actual nonlinearity values for $f$ and other weightwise quadratic functions, such as the majority function, HWBF, and the two main examples in~\cite{DAM:MeaOza24}.
-Our results highlight the revisited HWBF's superior nonlinearity relative to functions with similar computational costs.
-
-\item Analysis of other cryptographic parameters (Section~\ref{sec:otherParameters}):  
+Through experiments, we compare these bounds with actual nonlinearity values for $f$ and other weightwise quadratic functions, such as the majority function, the \hwbf{}, and the two main examples in~\cite{DAM:MeaOza24}.
+    Our results highlight the revisited \hwbf{}'s superior nonlinearity relative to functions with similar computational costs.
+
+    \item \emph{Analysis of other cryptographic parameters} (Section~\ref{sec:otherParameters}):  
     We evaluate other cryptographically relevant parameters of $f$, including degree, algebraic immunity, and fast algebraic immunity.
-Similar to the nonlinearity analysis, the revisited HWBF outperforms or matches other functions with comparable computational costs.
-
+Similar to the nonlinearity analysis, the revisited \hwbf{} outperforms or matches other functions with comparable computational costs.
 \end{itemize}
@@
 
-\pmnote{Add here the other notations we took if not explained locally or in the other parts of preliminaries}
-
-For $v$ a binary vector of length $n$ we denote by $\w(v)$ its Hamming weight: $\w(v)=|\{i\in [1,n] \, | \, x_i=1\}|$.
+Throughout this paper, $n$ will always denote a positive integer.
+Further, our intervals will only contain integers, so that for instance $[0,n]=\{0,1,\dots,n\}$.
+The set of binary vectors of length $n$ will be denoted by $\F_2^n$.
+The entries of a binary vector $x\in\F_2^n$ will always be denoted by $x_1,\dots,x_n$.
+We denote the scalar product of two binary vectors $x,y\in\F_2^n$ by $x\cdot y=\sum_{i=1}^nx_iy_i\in\F_2$.
+The Hamming weight of a binary vector $x\in\F_2^n$ is denoted by $\w(x)=|\{i\in [1,n]:x_i=1\}|$.%Tim: Check
 
@@
 In this part we recall general concepts on Boolean functions and their cryptographic properties we use in this article. 
-For a deeper introduction on Boolean functions and their cryptographic parameters we refer to the book~\cite{Carlet20} and to~\cite{TOSC:CarMeaRot17} for the weightwise properties, also called properties on the slices.
-For $k \in [0,n]$ we denote $\Ekn{k}{n}$ the set $\{x\in \F_2^n \, | \, \w(x)=k  \}$ and call it slice of the Boolean hypercube (of dimension $n$).
+For a deeper introduction on Boolean functions and their cryptographic parameters, we refer to the book~\cite{Carlet20}, and to~\cite{TOSC:CarMeaRot17} for properties on slices, so-called weightwise properties.
 
@@
 
-\begin{definition}[Boolean Function]\label{def:bool_f}
-	A Boolean function $f$ in $n$ variables is a function from $\F_2^n$ to $\F_2$. 
-	The set of all Boolean functions in $n$ variables is denoted by $\BN$, and we denote $\BN^*$ the set without the null function.
-\end{definition}
-
-\begin{definition}[Balancedness]\label{def:balancedness}
-	A Boolean function $f\in \BN$ is called balanced if $|\supp(f)|=2^{n-1}=|\supp(f+1)|$.
-
-%	For $k\in [0,n]$ the function is said balanced on the slice $k$ if $||\suppk{k}(f)|-|\suppk{k}(f+1)| |\le 1$.
+\begin{definition}[Slice]
+    For $k \in [0,n]$, we introduce the set $\Ekn{k}{n}=\{x\in \F_2^n:\w(x)=k\}$, and call it the $k$-th slice of the Boolean hypercube (of dimension $n$). 
+\end{definition}
+
+\begin{definition}[Boolean function, support]\label{def:bool_f}
+	A Boolean function in $n$ variables is a function from $\F_2^n$ to $\F_2$.
+The set of all Boolean functions in $n$ variables is denoted by $\BN$, and we denote this set without the null function by $\BN^*$.
+\end{definition}
+
+Below, for a Boolean function $f\in\BN$, we write $f+1$ for the Boolean function $g\in\BN$ which satisfies $g(x)=f(x)+1$ for every $x\in\F_2^n$.
+
+\begin{definition}[Support, balancedness]\label{def:balancedness}
+	Consider a Boolean function $f\in\BN$.
+Then the support of $f$ is defined as $\supp(f)=\{x\in\F_2^n:f(x)\neq 0\}$.
+The function $f$ is called balanced if it satisfies the equalities $|\supp(f)|=2^{n-1}=|\supp(f+1)|$.
+
+%	For $k\in [0,n]$ the function is said balanced on the slice $k$ if $||\suppk{k}(f)|-|\suppk{k}(f+1)| |\leq 1$.
 In particular when $|\Ekn{k}{n}|$ is even $|\suppk{k}(f)|=|\suppk{k}(f+1)|=|\Ekn{k}{n}|/2$.
@@
 \begin{definition}[Algebraic Normal Form (ANF) and degree]\label{def:anf}
-	We call Algebraic Normal Form of a Boolean function $f$ its $n$-variable polynomial representation over $\F_2$ (\textit{i.e.} belonging to $\F_2[x_1,\dots,x_n]/(x_1^2+x_1,\dots,x_n^2+x_n)$):
-	\[f(x_1,\dots,x_n)= \sum_{I \subseteq [1,n]} a_I \left( \prod_{i \in I} x_i \right) \]%x_1,\dots,x_n=\sum_{I \subseteq [1,n]} a_I x^I,\]
-	where $a_I\in \F_2$. 	
-	The (algebraic) degree of $f$, denoted $\degg(f)$ is: \[\degg(f)=\
-	\max_{I\subseteq [1,n]}\{ |I|\, | \, a_I=1\}  \text{ if $f$ is not null},0  \text{ otherwise}.\]
+	We call Algebraic Normal Form of a Boolean function $f\in\BN$ its unique representation as an element of the ring $\F_2[x_1,\dots,x_n]/(x_1^2+x_1,\dots,x_n^2+x_n)$, and we represent it as follows:
+	\[f(x_1,\dots,x_n)= \sum_{I \subseteq [1,n]} a_I \left( \prod_{i \in I} x_i \right), \]%x_1,\dots,x_n=\sum_{I \subseteq [1,n]} a_I x^I,\]
+	where $a_I\in \F_2$. The (algebraic) degree of $f$ is defined by $\degg(f)=0$ in case $f$ is the null function, and $\degg(f)=\max\{ |I|:I\subseteq[1,n],a_I=1\}$ otherwise.
 \end{definition}
@@
 \begin{definition}[Walsh transform and restricted Walsh transform]\label{def:walsh_transform}
-	Let $f\in \Bn{n}$ be a Boolean function, its Walsh transform $\wt{f}$ at $a \in \F_2^n$ is defined as:
-	\[  \wt{f} (a) = \sum_{x \in \F_2^n} (-1)^{f(x) +  a \cdot x }.\]
-	%	The Walsh support is the set $\Wsupp{f}=\{ a\in \F_2^n\, | \, \wt{f} (a) \neq 0 \}$.
-	Let $f\in \Bn{n}$, $S \subset \F_2^n$, its Walsh transform restricted to $S$ at $a \in \F_2^n$ is defined as:
+	The Walsh transform at $a \in \F_2^n$ of a Boolean function $f\in\BN$ restricted to a subset $S\subseteq \F_2^n$ is defined as:
     \[  \wt{f,S} (a) = \sum_{x\in S} (-1)^{f(x)+a \cdot x}.\]
-	For $S=\Ekn{k}{n}$ we denote $\wt{f,\Ekn{k}{n}} (a)$ by $\wtk{f}{k}(a)$.%, and for $a= 0_{n}$ we denote $\wtk{f}{k}(a)$ as $\wtk{f}{k}(0)$.
+    The Walsh transform of $f$ is then defined as $\wt{f}=\wt{f,\F_2^n}$. For $k\in[0,n]$, we also set $\wt{f,k}=\wt{f,\Ekn{k}{n}}$.
 \end{definition}
@@
 %\end{definition}
+
 \begin{definition}[Nonlinearity]%and weightwise nonlinearity
 	\label{def:nl}
-	The nonlinearity $\NL(f)$ of a Boolean function $f\in \BN$, where $n$ is a positive integer, is the minimum Hamming distance between $f$ and all the affine functions in $\BN$:
-	\[ \NL(f) = \min_{g,\, \degg(g)\leq 1} \{ \hd(f,g) \}{,} \]
-	where $g(x)=a\cdot x+\varepsilon$, $a\in \F_2^n, \varepsilon\in \F_2$. 	
-	The nonlinearity can also be defined from the Walsh transform:
+	The nonlinearity $\NL(f)$ of a Boolean function $f\in \BN$ is the minimum Hamming distance between $f$ and all the affine functions in $\BN$:
+	\[ \NL(f) = \min\{ \hd(f,g):g\in\BN,\degg(g)\leq 1\}{,} \]
+	where the Hamming distance between $f$ and $g$ is defined as $\hd(f,g)=|\{x\in\F_2^n:f(x)\neq g(x)\}|$.
+Alternatively, the nonlinearity of $f\in\BN$ can also be defined in terms of its Walsh transform:
 	\[ \NL(f) = 2^{n-1}- \frac{1}{2} \max_{a\in \F_2^n}{|\wt{f}(a)|}. \]
@@
 
-When $n$ is even, the nonlinearity of a function can reach at most $2^{n-1}-2^{n/2 -1}$.
-Functions reaching this maximum are called bent functions, due to their multiple applications and importance they have been the focus of multiple works \eg \cite{Rothaus76,FSE:Dobbertin95,DBLP:conf/itw/BudaghyanCH11,Tokareva15,Mesnager16}.
-The quadratic function $d_n$ given by: $d_n(x)=\sum_{i \text{ odd}}^n x_i x_{i+1}$ is an example of bent function.
-
-The algebraic degree of multiples of a Boolean function is a crucial criterion for various attacks on stream ciphers that utilize a Boolean function as a filter.
-The well-known algebraic attack~\cite{EC:CouMei03} and fast algebraic attack~\cite{C:Courtois03} on filtered LFSRs have motivated the study of cryptographic properties such as algebraic immunity and fast algebraic immunity, investigated in numerous works (\eg \cite{FSE:Armknecht04,C:HawRos04,ISC:JiaZhaWan13})).
-
+When $n$ is even, the nonlinearity of a Boolean function in $n$ variables can reach at most $2^{n-1}-2^{n/2 -1}$.
+Functions reaching this maximum are called bent functions.
+Due to their broad applications and importance, they have been the focus of multiple works, \eg{} \cite{Rothaus76,FSE:Dobbertin95,DBLP:conf/itw/BudaghyanCH11,Tokareva15,Mesnager16}.
+The quadratic function $d_n\in\BN$ given by $d_n(x)=\sum_{i=1}^{n/2}x_{2i-1}x_{2i}$ is an example for such a bent function.
+
+\bigskip
+The algebraic degree of multiples of a Boolean function is a crucial quantity for various attacks on stream ciphers that utilize a Boolean function as a filter. %Tim: Check previous sentence
+The well-known algebraic attack~\cite{EC:CouMei03} and fast algebraic attack~\cite{C:Courtois03} on filtered \textsf{LFSR}s have motivated the study of cryptographic properties such as algebraic immunity and fast algebraic immunity, investigated in numerous works, \eg{} \cite{FSE:Armknecht04,C:HawRos04,ISC:JiaZhaWan13})).
 Nowadays, these parameters are systematically determined for any function considered as a filter.
 
-\begin{definition}[Algebraic immunity~\cite{EC:MeiPasCar04}] \label{def:ai}
-	The algebraic immunity of a Boolean function $f\in \Bfn{n}$, denoted as $\AI(f)$, is defined as:
-	\[ \AI(f) = \min_{g \neq 0}\{ \degg(g) \; | \; fg = 0 \; \text{or} \; (f + 1)g = 0 \}{,} \]
-	where $\degg(g)$ is the algebraic degree of $g$.
-	The function $g$ is called an annihilator of $f$ (or $f + 1$). 
-\end{definition}
-
-\begin{definition}[Fast algebraic immunity, \eg \cite{EC:ACGKMR06}]\label{def:FAI} The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined as $\FAI(f)=\min \{ 2 \AI(f), \min _{1 \le \degg(g)<\AI(f)} (\degg(g)+ \degg(fg))\}$.
-\end{definition}
-
-\subsection{Symmetric Functions, HWBF and weightwise degree-d functions}
-
-The $n$-variable \emph{Boolean symmetric functions} are those that are constant on each slice $\Ekn{k}{n}$ for $k\in [0,n]$. 
-This class has been assiduously studied in the context of cryptography, see \eg \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,IEEE:CheLu11,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
-In this article we mainly consider the slice indicator functions and the majority functions.
+\begin{definition}[Annihilator, algebraic immunity~\cite{EC:MeiPasCar04}] \label{def:ai}
+	Let $f\in\BN$ be a Boolean function. Then a function $g\in\BN^*$ is called an annihilator of $f$ if it satisfies $fg=0$. The algebraic immunity of $f$ is then defined as:
+	\[ \AI(f) = \min\{ \degg(g):\text{$g\in\BN^*$ is an annihilator of $f$ or $f+1$}\}.\]
+\end{definition}
+
+\begin{definition}[Fast algebraic immunity, \eg{} \cite{EC:ACGKMR06}]\label{def:FAI} The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined as:
+\[
+    \FAI(f)=\min \{ 2 \AI(f), \min\{\degg(g)+ \degg(fg):g\in\BN,1\leq\degg(g)<\AI(f)\}\}
+\]
+
+\end{definition}
+
+\subsection{Symmetric Functions, \hwbf{} and weightwise degree-d functions}
+
+The Boolean symmetric functions in $n$ variables are those that are constant on each slice $\Ekn{k}{n}$ for $k\in [0,n]$. 
+This class has been thoroughly studied in the context of cryptography, see \eg{} \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,IEEE:CheLu11,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
+In this article, the symmetric functions that we consider will mainly be the slice indicator function and the majority function.
 %\begin{definition}[Elementary symmetric functions]
@@
 %\end{definition}
-\begin{definition}[Slice indicator functions]\label{def:slice}
- Let $k\in [0,n]$, the indicator function of the slice of weight $k$ is defined as:
- \[\forall  x\in \mathbb{F}_2^{n}, \quad \phikn{k}{n}(x) = 1 \text{ if and only if } \w(x) = k.\]
+\begin{definition}[Slice indicator functions]\label{def:slice} The indicator function of the slice of weight $k\in[0,n]$ is the function $\phikn kn\in\BN$ defined by $\phikn kn(x)=1$ if and only if $\w(x)=k$.
 \end{definition}
@@
 \begin{definition}[Majority function]\label{def:maj}
-    The \emph{majority function} in $n$ variables is the Boolean function $\textsf{Maj}\in\BN$ defined as:
-    \[
-        \textsf{Maj}(x)=0\iff\w(x)<n/2.
-    \]
-\end{definition}
-
-Bigger families of functions can be obtained by considering functions of bounded degree on each slice, it corresponds to the concept of weightwise degree-$d$ function introduced in~\cite{DAM:GinMea22} for $d=1$ and~\cite{DAM:MeaOza24} for the general case.
-
-\begin{definition}[Weightwise degree-$d$ functions (~\cite{DAM:MeaOza24} Definition 12)]\label{def:wwdegd}
-	Let $n\in \N^*$ and for $k\in[0,n]$ $\phikn{k}{n}$ denotes the indicator function of $\Ekn{k}{n}$. 
-	An $n$-variable Boolean function $f$, written as $f=\sum_{k=0}^n f_k \phikn{k}{n}$, is called weightwise degree-$d$ if and only if for each $k\in [0,n]$ $f_k$ coincide with a function of degree at most $d$ over $\Ekn{k}{n}$.
+    The majority function in $n$ variables is the Boolean function $\mathsf{Maj}_n\in\BN$ defined by $\mathsf{Maj}_n(x)=1$ if and only if $\w(x)\geq n/2$.
+\end{definition}
+
+Bigger families of functions can be obtained by considering functions of bounded degree on each slice.
+This corresponds to the concept of weightwise degree-$d$ functions introduced in~\cite{DAM:GinMea22} for $d=1$ and~\cite{DAM:MeaOza24} for the general case.
+
+\begin{definition}[Weightwise degree-\textit{d} functions (~\cite{DAM:MeaOza24} Definition 12)]\label{def:wwdegd}
+    A Boolean function $f\in\BN^*$ is called weightwise degree-$d$ if it can be written under the form $f=\sum_{k=0}^n f_k \phikn{k}{n}$ with $f_k\in\BN$ of degree at most $d$.
 The set of weightwise degree-$d$ functions is denoted by $\WD{d}{n}$.
-
-Additionally, a weightwise degree-$d$ function is called cyclic weightwise degree-$d$ function if for all $i\in [1,n]$ it holds $f_i(x)=f_0(O^i(x))$, where $O^i$ denotes the cyclic shift by $i$ positions, $O^i(x_1,\dots,x_n)=(x_{1+i \mod n},\dots,x_{n+i \mod n})$, the representative modulo being taken as an integer between $1$ and $n$.
-\end{definition}
-
-Various weightwise affine functions (\ie belonging to $\WD{1}{n}$) have been exhibited such as in~\cite{TOSC:CarMeaRot17} where the bent functions in Propositions $1$ and $2$ are weightwise affine or in~\cite{DAM:GinMea22} to show than no weightwise perfectly balanced function is weightwise affine for $n\ge 8$.
-The most known example of weightwise affine function is the hidden weight bit function introduced in~\cite{IEEE:Bryant91}, the one obtained by fixing $f_0=0$ and $f_k=x_k$ for $k \in [n]$.
+	Additionally, a weightwise degree-$d$ function $f=\sum_{k=0}^n f_k \phikn{k}{n}$ is called a cyclic weightwise degree-$d$ function if for all $k\in [0,n]$ and all $x\in\F_2^n$, it holds that $f_k(x)=f_0(O^k(x))$, where $O^k:\F_2^n\to\F_2^n$ is the cyclic shift by $k$ positions, defined by $O^k(x_1,\dots,x_n)=(x_{(1+k)\bmod n},\dots,x_{(n+k)\bmod n})$, the representatives modulo $n$ being taken as integers in $[1,n]$.
+\end{definition}
+
+Various weightwise affine functions (\ie{} belonging to $\WD{1}{n}$) have been exhibited, such as in~\cite{TOSC:CarMeaRot17} where the bent functions in Propositions $1$ and $2$ are weightwise affine, or in~\cite{DAM:GinMea22} to show than no weightwise perfectly balanced function is weightwise affine for $n\geq 8$.
+The arguably best known example of weightwise affine function is the hidden weight bit function introduced in~\cite{IEEE:Bryant91}, the one obtained by fixing $f_0=0$ and $f_k=x_k$ for $k \in [1,n]$.
 The cryptographic properties of this function have been studied in~\cite{DAM:WCST14}, showing good algebraic properties for this function.
 
-\begin{definition}[Hidden Weight Bit Function (HWBF)]\label{def:hwbf}
-	For $n\in \N^*$, we call Hidden Weight Bit Function (HWBF) the $n$-variable Boolean function defined by:
+\begin{definition}[Hidden Weight Bit Function (\hwbf{})]\label{def:hwbf}
+    We call Hidden Weight Bit Function (\hwbf{}) the Boolean function $h\in\BN$ defined by:
 	\[h(x)= \left\{ 
@@
 
-In~\cite{DAM:MeaOza24}, the parameters of different functions from $\WD{1}{n}$ and $\WD{2}{n}$ are studied experimentally for $n$ up to $20$ and lower bounds are given for the nonlinearity for all $n$.
+In~\cite{DAM:MeaOza24}, the parameters of different functions from $\WD{1}{n}$ and $\WD{2}{n}$ are studied experimentally for $n$ up to $20$, and lower bounds are given for the nonlinearity for all $n$.
 These bounds focus on cyclic weightwise quadratic functions and involve sums of binomial coefficients.
-For simplicity, in the following we provide only the nonlinearity values of the majority function and HWBF, as these bounds will be used for comparison.
+For simplicity, in the following we provide only the nonlinearity values of the majority function and \hwbf{}, as these bounds will be used for comparison.
 
@@
     \]
-    \item The HWBF $f\in\WD{2}{n}$ introduced in Definition~\ref{def:hwbf} satisfies:
+    \item The \hwbf{} $f\in\WD{2}{n}$ introduced in Definition~\ref{def:hwbf} satisfies:
     \[
@@
 %\begin{itemize}
-%	\item (\eg ~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\textsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
+%	\item (\eg{} ~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\textsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
 %	\[
@@
 \begin{Prop}[Properties of some functions from $\WD{1}{n}$\label{prop:wwd1}]
-	Let $n\in \N^*$ even, the following hold for the following functions in $\WD{1}{n}$: 
+	Let $n\geq 2$ be an even integer.
 	\begin{itemize}
-		\item (\eg ~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\textsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
-		\[
-		\NL(\textsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}.
-		\]
-		\item (\cite{DAM:WCST14}, Theorem $3$) The HWBF $h$ introduced in Definition~\ref{def:hwbf} satisfies:
+		\item (\eg{}~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\mathsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
+		\[
+		\NL(\mathsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}.
+		\]
+		\item (\cite{DAM:WCST14}, Theorem $3$) The \hwbf{} $h$ introduced in Definition~\ref{def:hwbf} satisfies:
 		\[
@@
 		\]	
-		\item (\cite{DAM:WCST14}, Theorem $1$) The HWBF $h$ introduced in Definition~\ref{def:hwbf} satisfies $\forall n \ge 3$, $\degg(h)=n-1$. 	
+		\item (\cite{DAM:WCST14}, Theorem $1$) The \hwbf{} $h$ introduced in Definition~\ref{def:hwbf} satisfies $\degg(h)=n-1$ for all $n\geq 4$.
 	\end{itemize}
@@
 \subsection{Krawtchouk polynomials}
-We use Krawtchouk polynomials and some of their properties to prove one of our results, we give the necessary preliminaries here and refer to \eg ~\cite{book:MacSlo78} for more details.
+We use Krawtchouk polynomials and some of their properties to prove one of our main results. We give the necessary preliminaries here and refer to \eg{}~\cite{book:MacSlo78} for more details.
 
 \begin{definition}[Krawtchouk Polynomials]\label{def:Kraw}
-	The Krawtchouk polynomial of degree $k$, with $0\leq k\leq n$ is given by: $ \displaystyle \kraw{k}{\ell}{n}=\sum_{j=0}^{k} (-1)^j \binom{\ell}{j} \binom{n-\ell}{k-j}$.
-
-	Krawtchouk polynomials are characterized by the generating series: $ \displaystyle (1+z)^{n-x} (1-z)^x=\sum_{k=0}^\infty \kraw{k}{x}{n} z^k$.
-\end{definition}
-
-\section{Revisited HWBF and balancedness}\label{sec:defAndBal}
+	The $n$-th Krawtchouk polynomial of degree $k\in[0,n]$ is given by:
+    \[
+        \displaystyle \kraw{k}{x}{n}=\sum_{j=0}^{k} (-1)^j \binom{x}{j} \binom{n-x}{k-j}.
+    \]
+    Alternatively, the Krawtchouk polynomials can be implicitly defined as the coefficients of the generating series for $(1+z)^{n-x} (1-z)^x$:
+    \[
+        (1+z)^{n-x} (1-z)^x=\sum_{k=0}^\infty \kraw{k}{x}{n} z^k.
+    \]
+\end{definition} %Tim: This is different from the Wiki
+
+\section{Revisited \hwbf{} and balancedness}\label{sec:defAndBal}
 %\subsection{Restricted Walsh transform of $f$ in a recursive fashion}
 
-In this part we formally define the revisited HWBF function $f$ and introduce a quantity that allows us to study its balancedness and nonlinearity.
-
-\begin{definition}[Revisited HWBF]\label{def:revHWBF}
-Let $n\in \N^*$, even, we call revisited HWBF and denote by $f$ the Boolean function defined as:
+In this part, we will formally define the revisited \hwbf{} function and introduce a quantity that allows us to study its balancedness and nonlinearity.
+
+\begin{definition}[Revisited \hwbf{}]\label{def:revHWBF}
+Let $n\in \N^*$, even, we call revisited \hwbf{} and denote by $f$ the Boolean function defined as:
 \[f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k.\]
@@
 
-Since $f$ is the sum of a quadratic function and a weightweise affine function, it is a weightwise quadratic function. 
-Using the formalism of Definition~\ref{def:wwdegd} $f$ is the WWQ function defined by:% $f_0=0$ and for $k\in [1,n]$ $f_k=x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$.
+Since $f$ is the sum of a quadratic function and a weightwise affine function, it is a weightwise quadratic function. 
+Using the formalism of Definition~\ref{def:wwdegd}, $f$ is the weightwise quadratic function defined by:% $f_0=0$ and for $k\in [1,n]$ $f_k=x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$.
 \[f_0=0, \quad \text{ and } \quad \forall k \in [1,n], \, f_k=x_k+\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}.\]
@@
 	\item For $n=0$, $\Dnka{0}{k}{a}=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise.
-	\item if $n\ge 2$, denoting  $b=(a_1,\cdots,a_{n-2})$ and $y=(x_1,\cdots,x_{n-2})$, we get:
+	\item if $n\geq 2$, denoting  $b=(a_1,\cdots,a_{n-2})$ and $y=(x_1,\cdots,x_{n-2})$, we get:
 	\[\Dnka{n}{k}{a}=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.\]
@@
 \begin{proof}
-For $n\ge 2$ we can rewrite $\Dnka{n}{k}{a}$:
+For $n\geq 2$ we can rewrite $\Dnka{n}{k}{a}$:
 
@@
 Calling $\pi$ this permutation, since $c=a+e_k+\sum_{i=n/2+1}^n e_i$, we can write $d=\pi(c)=\pi(a)+ \pi(e_k)+ (0,1,0,1,\ldots,0,1)$. 
-Accordingly, if $k\le n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2+1$, with one couple of consecutive elements (the first one with an odd index) being $(1,1)$ and all the others $(0,1)$.
+Accordingly, if $k\leq n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2+1$, with one couple of consecutive elements (the first one with an odd index) being $(1,1)$ and all the others $(0,1)$.
 Otherwise,  when $k> n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2-1$, with one couple of consecutive elements (the first one with an odd index) being $(0,0)$ and all the others $(0,1)$.
@@
 Equivalently, 
-%$\NL(f)\ge 2^{n-1} - \frac{1 + n 2^{\frac{3}{4}n}} {2}$.
-$\NL(f)\ge 2^{n-1} - \frac{1}{2} -2^{\frac{3n}{4} + \log n -1}$.
+%$\NL(f)\geq 2^{n-1} - \frac{1 + n 2^{\frac{3}{4}n}} {2}$.
+$\NL(f)\geq 2^{n-1} - \frac{1}{2} -2^{\frac{3n}{4} + \log n -1}$.
 \end{Corollary}
@@
 \begin{proposition}\label{proposition:dtn}
-	Let $t, n\in \N$ with $n$ even and $t\le n/2$, the following holds on $d_{t,n}$ for all $k\in [0,n]$:
+	Let $t, n\in \N$ with $n$ even and $t\leq n/2$, the following holds on $d_{t,n}$ for all $k\in [0,n]$:
 	\[\wtk{d_{t,n}}{k}(a)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t},\]
@@
 \begin{definition}\label{defi:P_a_t}
-    Let $t, n\in \N$ with $n$ even and $t\le n/2$.
+    Let $t, n\in \N$ with $n$ even and $t\leq n/2$.
 Given $a=(b,c)\in\F_2^n$ with $b\in\F_2^{2t}$, denote $n-2t-\w(c)$ and $\w(c)$ by $u$ and $v$, respectively.
@@
 \begin{proposition}
-    Let $t, n\in \N$ with $n$ even and $t\le n/2$. Let $a\in\F_2^n$. The following holds true: 
+    Let $t, n\in \N$ with $n$ even and $t\leq n/2$. Let $a\in\F_2^n$. The following holds true: 
     \[
@@
 \begin{theorem}\label{theorem:bound_D_nka_generalized}
-    Let $t, n\in \N$ with $n$ even and $t\le n/2$. 
+    Let $t, n\in \N$ with $n$ even and $t\leq n/2$. 
     We define $\lambda=t/n\in\left[0,\frac 12\right]$, as well as:
@@
 
-In this section, we establish a tighter bound on the absolute value of the Walsh transform of the revised HWBF for values of $n$ up to $80$. 
-We then compare the nonlinearity of this function to that of other functions suited to similar use cases, such as the HWBF of weightwise cyclic functions from~\cite{DAM:MeaOza24}.
+In this section, we establish a tighter bound on the absolute value of the Walsh transform of the revised \hwbf{} for values of $n$ up to $80$. 
+We then compare the nonlinearity of this function to that of other functions suited to similar use cases, such as the \hwbf{} of weightwise cyclic functions from~\cite{DAM:MeaOza24}.
 
@@
 
-In this part we compare the nonlinearity of the function $f$ from Definition~\ref{def:revHWBF} to other weightwise quadratic functions considered for similar use-cases, such as majority, HWBF and the cyclic weighwise functions studied in~\cite{DAM:MeaOza24}.
+In this part we compare the nonlinearity of the function $f$ from Definition~\ref{def:revHWBF} to other weightwise quadratic functions considered for similar use-cases, such as majority, \hwbf{} and the cyclic weighwise functions studied in~\cite{DAM:MeaOza24}.
 
@@
 The violet and orange curves represent the upper bounds  in~\cite{DAM:MeaOza24}.
-The violet curve corresponds to the bound that holds for all cyclic weightwise linear functions where $ f_0(x) = b \cdot x $ with $\w(b)$ odd, providing, for example, an upper bound for the HWBF.
+The violet curve corresponds to the bound that holds for all cyclic weightwise linear functions where $ f_0(x) = b \cdot x $ with $\w(b)$ odd, providing, for example, an upper bound for the \hwbf{}.
 The orange curve corresponds to the bound for the cyclic weightwise quadratic function defined by $f_0(x) = x_1 + x_2 x_3$.
-The blue curve represents both the majority and HWBF functions, whose exact nonlinearities are given in Property~\ref{prop:wwd1}.
+The blue curve represents both the majority and \hwbf{} functions, whose exact nonlinearities are given in Property~\ref{prop:wwd1}.
 We use a single curve here because, on a logarithmic scale, the nonlinearity difference between these two functions is too small to distinguish between them.
-For the revisited HWBF introduced in Definition~\ref{def:revHWBF}, the red curve corresponds to the theoretical bound from Corollary~\ref{cor:bound_walsh_cauchy}, while the green curve represents the experimental results from Section~\ref{sec:expwt}.
+For the revisited \hwbf{} introduced in Definition~\ref{def:revHWBF}, the red curve corresponds to the theoretical bound from Corollary~\ref{cor:bound_walsh_cauchy}, while the green curve represents the experimental results from Section~\ref{sec:expwt}.
 
@@
 		The violet and orange curves represent bounds for cyclic weightwise linear functions and a cyclic weightwise quadratic function from~\cite{DAM:MeaOza24}.
-The blue curve shows values for the majority function and HWBF.
+The blue curve shows values for the majority function and \hwbf{}.
 The theoretical bound for the function $f$ (from Corollary~\ref{cor:bound_walsh_cauchy}) is in red, and the experimental bound $B_n$ (Section~\ref{sec:expwt}) is in green.}
@@
 
-We observe significantly better performance for the newly introduced function $f$ compared to the majority function and HWBF, with the proven bound exhibiting an asymptotic slope of $ 3/4$ as opposed to $1$.
+We observe significantly better performance for the newly introduced function $f$ compared to the majority function and \hwbf{}, with the proven bound exhibiting an asymptotic slope of $ 3/4$ as opposed to $1$.
 The two bounds proven in~\cite{DAM:MeaOza24} also have an asymptotic slope of $1$.
@@
 	\hline	
-    	HWBF   & $4$  & $20$  & $88$  &  $372$ & $1544$ & $6344$ & $25904$  \\  	
+    	\hwbf{}   & $4$  & $20$  & $88$  &  $372$ & $1544$ & $6344$ & $25904$  \\  	
    %4 10 20 44 88 186 372 772 1544 3172 6344 12952 25904
@@
 \begin{proof}
-	We write $f$ as $q+h$ where $q$ is the quadratic function $\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}$ and $h$ is the HWBF.
-	Using Property~\ref{prop:wwd1} Item $3$, $h$ has degree $n-1\ge 3$, and the function $q$ has no monomial of degree higher than $2$, therefore $\degg(f)=\degg(h)=n+1$.
-
-\end{proof}
-
-In Table~\ref{table:comparisonsDeg}, we display the algebraic degree of different weightwise quadratic function. We observe that $f$ is the function with higher degree, jointly with the HWBF.
+	We write $f$ as $q+h$ where $q$ is the quadratic function $\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}$ and $h$ is the \hwbf{}.
+	Using Property~\ref{prop:wwd1} Item $3$, $h$ has degree $n-1\geq 3$, and the function $q$ has no monomial of degree higher than $2$, therefore $\degg(f)=\degg(h)=n+1$.
+
+\end{proof}
+
+In Table~\ref{table:comparisonsDeg}, we display the algebraic degree of different weightwise quadratic function. We observe that $f$ is the function with higher degree, jointly with the \hwbf{}.
 
@@
 		\hline	
-		HWBF   & $3$  & $5$  & $7$  &  $9$ & $11$ & $13$ & $15$  \\  	
+		\hwbf{}   & $3$  & $5$  & $7$  &  $9$ & $11$ & $13$ & $15$  \\  	
 		\hline
@@
 	Let $n\in \N$ be even, $f$ defined (as in Definition~\ref{def:revHWBF}) as
-	$f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k$ and $h$ denote the $n$-variable HWBF, the following holds:
-	\[\AI(f)\ge \AI(h)-2.\]
+	$f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k$ and $h$ denote the $n$-variable \hwbf{}, the following holds:
+	\[\AI(f)\geq \AI(h)-2.\]
 \end{proposition}
@@
 	hence $g (1+q)$ is an annihilator of $h+ \varepsilon$. 
-	If $g (1+q)\ne 0$ then $\degg(g(1+q)) \le \degg(g)+2$ and we obtain $\degg(g)\ge \AI(h) -2$. 
-	Otherwise, $g (1+q)= 0$ implies that $g$ annihilates $1+q$ and therefore $0=g (f+\varepsilon + 1 +q)=g(h+ \varepsilon +1)$ that is $\degg(g)\ge \AI(h)$. 
-	Summarizing, for any non null annihilator $g$ of $f$ or $f+1$ we get $\degg(g)\ge \AI(h)-2$, it allows to conclude $\AI(f)\ge \AI(h)-2$.
-\end{proof}
-
-From~\cite{DAM:WCST14} Theorem 4, the algebraic immunity of the HWBF is at least $\lfloor n/3\rfloor +1$, which leads to $\lfloor n/3\rfloor -1$ for $f$. 
+	If $g (1+q)\ne 0$ then $\degg(g(1+q)) \leq \degg(g)+2$ and we obtain $\degg(g)\geq \AI(h) -2$. 
+	Otherwise, $g (1+q)= 0$ implies that $g$ annihilates $1+q$ and therefore $0=g (f+\varepsilon + 1 +q)=g(h+ \varepsilon +1)$ that is $\degg(g)\geq \AI(h)$. 
+	Summarizing, for any non null annihilator $g$ of $f$ or $f+1$ we get $\degg(g)\geq \AI(h)-2$, it allows to conclude $\AI(f)\geq \AI(h)-2$.
+\end{proof}
+
+From~\cite{DAM:WCST14} Theorem 4, the algebraic immunity of the \hwbf{} is at least $\lfloor n/3\rfloor +1$, which leads to $\lfloor n/3\rfloor -1$ for $f$. 
 In Table~\ref{table:comparisonsAI}, we present the algebraic immunity of various weightwise quadratic functions.
@@
 		\hline	
-		HWBF   & $2$  & $3$  & $4$  &  $4$ & $5$ & $5$ & $6$  \\  	
+		\hwbf{}   & $2$  & $3$  & $4$  &  $4$ & $5$ & $5$ & $6$  \\  	
 		\hline

### 2024-11-21 RevisedHiddenWeight.tex
ok

@@
 We analyze the balancedness, nonlinearity, and other criteria of this function, presenting theoretical bounds and experimental results to highlight its advantages over existing functions in similar use cases.
-%Tim: Check abstract
 	\end{abstract}
@@
 \begin{itemize}
-	\item In Section~\ref{sec:defAndBal}, we defined the revisited \hwbf{} $f$, and study its balancedness.
+	\item In Section~\ref{sec:defAndBal}, we define the revisited \hwbf{} $f$, and study its balancedness.
 This part is done by studying the (restricted) Walsh transform of some quadratic functions over sets of fixed Hamming weight, called slices.
@@
 We denote the scalar product of two binary vectors $x,y\in\F_2^n$ by $x\cdot y=\sum_{i=1}^nx_iy_i\in\F_2$.
-The Hamming weight of a binary vector $x\in\F_2^n$ is denoted by $\w(x)=|\{i\in [1,n]:x_i=1\}|$.%Tim: Check
+The Hamming weight of a binary vector $x\in\F_2^n$ is denoted by $\w(x)=|\{i\in [1,n]:x_i=1\}|$.
 
@@
 
-\begin{definition}[Nonlinearity]%and weightwise nonlinearity
+\begin{definition}[Nonlinearity \eg{}~\cite{Carlet20} Page 79]%and weightwise nonlinearity
 	\label{def:nl}
@@
 \bigskip
-The algebraic degree of multiples of a Boolean function is a crucial quantity for various attacks on stream ciphers that utilize a Boolean function as a filter. %Tim: Check previous sentence
+The algebraic degree of multiples of a Boolean function is a crucial quantity for various attacks on stream ciphers that utilize a Boolean function as a filter. 
 The well-known algebraic attack~\cite{EC:CouMei03} and fast algebraic attack~\cite{C:Courtois03} on filtered \textsf{LFSR}s have motivated the study of cryptographic properties such as algebraic immunity and fast algebraic immunity, investigated in numerous works, \eg{} \cite{FSE:Armknecht04,C:HawRos04,ISC:JiaZhaWan13})).
@@
 
-%\pmnote{complete the following prop. Choose between nonlinearity or $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ \color{blue} Tim: I started, but please do the remaining two items.}
 \iffalse
@@
 
-\begin{definition}[Krawtchouk Polynomials]\label{def:Kraw}
+\begin{definition}[Krawtchouk polynomials]\label{def:Kraw}
 	The $n$-th Krawtchouk polynomial of degree $k\in[0,n]$ is given by:
@@
     \]
-\end{definition} %Tim: This is different from the Wiki
+\end{definition}
 
@@
 
-%\pmnote{for the remark, add how they are obtained (from a script in xxx). 
-%We can give the scripts in supplementary material when submitting, of add the link of a github if you agree to have them public.
-\color{blue} Tim: I added the script to GitHub.
-You can decide what we do with it.}
-
 \section{Experiments and comparisons}\label{sec:expAndComp}

### 2024-11-26 RevisedHiddenWeight.tex
Updates from Overleaf

--- 2024-11-21 RevisedHiddenWeight.tex
@@
 
-The Boolean symmetric functions in $n$ variables are those that are constant on each slice $\Ekn{k}{n}$ for $k\in [0,n]$. 
-This class has been thoroughly studied in the context of cryptography, see \eg{} \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,IEEE:CheLu11,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
+Recall that the Boolean symmetric functions in $n$ variables are those that are constant on the slice $\Ekn{k}{n}$ for every $k\in [0,n]$. 
+This class of functions has been thoroughly studied in the context of cryptography, see \eg{} \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,IEEE:CheLu11,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
 In this article, the symmetric functions that we consider will mainly be the slice indicator function and the majority function.
@@
 
-\begin{definition}[Weightwise degree-\textit{d} functions (~\cite{DAM:MeaOza24} Definition 12)]\label{def:wwdegd}
+\begin{definition}[Weightwise degree-\textit{d} functions, \cite{DAM:MeaOza24} Definition 12]\label{def:wwdegd}
     A Boolean function $f\in\BN^*$ is called weightwise degree-$d$ if it can be written under the form $f=\sum_{k=0}^n f_k \phikn{k}{n}$ with $f_k\in\BN$ of degree at most $d$.
@@
     \]
-    Alternatively, the Krawtchouk polynomials can be implicitly defined as the coefficients of the generating series for $(1+z)^{n-x} (1-z)^x$:
+    Alternatively, the Krawtchouk polynomials can be characterized as the coefficients in the generating function for $(1+z)^{n-x} (1-z)^x$ in the variable $z$:
     \[
@@
 
-In this section, we establish a tighter bound on the absolute value of the Walsh transform of the revised \hwbf{} for values of $n$ up to $80$. 
+In this section, we establish a tighter bound on the absolute value of the Walsh transform of the revisited \hwbf{} for values of $n$ up to $80$. 
 We then compare the nonlinearity of this function to that of other functions suited to similar use cases, such as the \hwbf{} of weightwise cyclic functions from~\cite{DAM:MeaOza24}.

### 2024-11-26 old.tex
Please check Proposition 3 and Theorem 1

--- 2024-11-26 RevisedHiddenWeight.tex
@@
 
-Throughout this paper, $n$ will always denote a positive integer.
+Throughout this paper, $n\geq 0$ will always denote a non-negative integer.
 Further, our intervals will only contain integers, so that for instance $[0,n]=\{0,1,\dots,n\}$.
-The set of binary vectors of length $n$ will be denoted by $\F_2^n$.
+The set of binary vectors of length $n$ will be denoted by $\F_2^n$, with zero vector written as $0_n$.
+The canonical basis of $\F_2^n$ will be written as $\{e_1,\dots,e_n\}$; therefore, $e_i\in\F_2^n$ is the vector which is zero everywhere, except at position $i$.
 The entries of a binary vector $x\in\F_2^n$ will always be denoted by $x_1,\dots,x_n$.
-We denote the scalar product of two binary vectors $x,y\in\F_2^n$ by $x\cdot y=\sum_{i=1}^nx_iy_i\in\F_2$.
+We write the scalar product of two binary vectors $x,y\in\F_2^n$ as $x\cdot y=\sum_{i=1}^nx_iy_i\in\F_2$.
 The Hamming weight of a binary vector $x\in\F_2^n$ is denoted by $\w(x)=|\{i\in [1,n]:x_i=1\}|$.
@@
 
-\begin{definition}[Boolean function, support]\label{def:bool_f}
+\begin{definition}[Boolean function]\label{def:bool_f}
 	A Boolean function in $n$ variables is a function from $\F_2^n$ to $\F_2$.
@@
 
-\begin{definition}[Support, balancedness]\label{def:balancedness}
-	Consider a Boolean function $f\in\BN$.
-Then the support of $f$ is defined as $\supp(f)=\{x\in\F_2^n:f(x)\neq 0\}$.
-The function $f$ is called balanced if it satisfies the equalities $|\supp(f)|=2^{n-1}=|\supp(f+1)|$.
-
-%	For $k\in [0,n]$ the function is said balanced on the slice $k$ if $||\suppk{k}(f)|-|\suppk{k}(f+1)| |\leq 1$.
-In particular when $|\Ekn{k}{n}|$ is even $|\suppk{k}(f)|=|\suppk{k}(f+1)|=|\Ekn{k}{n}|/2$.
-\end{definition}
-
-\begin{definition}[Algebraic Normal Form (ANF) and degree]\label{def:anf}
+\begin{definition}[Algebraic Normal Form, degree]\label{def:anf}
 	We call Algebraic Normal Form of a Boolean function $f\in\BN$ its unique representation as an element of the ring $\F_2[x_1,\dots,x_n]/(x_1^2+x_1,\dots,x_n^2+x_n)$, and we represent it as follows:
@@
 
-\begin{definition}[Walsh transform and restricted Walsh transform]\label{def:walsh_transform}
+\begin{definition}[Walsh transform, restricted Walsh transform]\label{def:walsh_transform}
 	The Walsh transform at $a \in \F_2^n$ of a Boolean function $f\in\BN$ restricted to a subset $S\subseteq \F_2^n$ is defined as:
@@
 
-\begin{definition}[Nonlinearity \eg{}~\cite{Carlet20} Page 79]%and weightwise nonlinearity
+\begin{definition}[Balancedness]
+    A Boolean function $f\in\BN$ is called balanced if $\wt f(0_n)=0$.
+\end{definition}
+
+\begin{definition}[Nonlinearity, \eg{} page 79 in \cite{Carlet20}]%and weightwise nonlinearity
 	\label{def:nl}
@@
 
-\begin{definition}[Weightwise degree-\textit{d} functions, \cite{DAM:MeaOza24} Definition 12]\label{def:wwdegd}
+\begin{definition}[Weightwise degree-\textit{d} functions, Definition 12 in \cite{DAM:MeaOza24}]\label{def:wwdegd}
     A Boolean function $f\in\BN^*$ is called weightwise degree-$d$ if it can be written under the form $f=\sum_{k=0}^n f_k \phikn{k}{n}$ with $f_k\in\BN$ of degree at most $d$.
@@
 
-\begin{definition}[Hidden Weight Bit Function (\hwbf{})]\label{def:hwbf}
+\begin{definition}[Hidden Weight Bit Function]\label{def:hwbf}
     We call Hidden Weight Bit Function (\hwbf{}) the Boolean function $h\in\BN$ defined by:
@@
 
-\begin{Prop}[Properties of some functions from $\WD{1}{n}$\label{prop:wwd1}]
+\begin{Prop}\label{prop:wwd1}
 	Let $n\geq 2$ be an even integer.
@@
 \subsection{Krawtchouk polynomials}
-We use Krawtchouk polynomials and some of their properties to prove one of our main results. We give the necessary preliminaries here and refer to \eg{}~\cite{book:MacSlo78} for more details.
+We use Krawtchouk polynomials and some of their properties to prove one of our main results. We give the necessary definition here and refer to \eg{}~\cite{book:MacSlo78} for more details.
 
@@
 \begin{definition}[Revisited \hwbf{}]\label{def:revHWBF}
-Let $n\in \N^*$, even, we call revisited \hwbf{} and denote by $f$ the Boolean function defined as:
-\[f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k.\]
+For an even integer $n\geq 0$, we call revisited \hwbf{} the Boolean function $f\in\BN$ defined as:
+\[f(x)=\sum_{i=1}^{n/2}(x_{2i-1}+1)x_{2i}+ \sum_{k=1}^n x_k\phikn{k}{n}(x).\]
 \end{definition}
@@
 Since $f$ is the sum of a quadratic function and a weightwise affine function, it is a weightwise quadratic function. 
-Using the formalism of Definition~\ref{def:wwdegd}, $f$ is the weightwise quadratic function defined by:% $f_0=0$ and for $k\in [1,n]$ $f_k=x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$.
-\[f_0=0, \quad \text{ and } \quad \forall k \in [1,n], \, f_k=x_k+\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}.\]
-
+Using the formalism of Definition~\ref{def:wwdegd}, $f$ is the weightwise quadratic function defined by $f_0(x)=0$ and $f_k(x)=\sum_{i=1}^{n/2}(x_{2i-1}+1)x_{2i}+x_k$ for all $k\in[1,n]$.
 This form allows to derive the restricted Walsh transform of $f$, which can be a useful tool to study the balancedness and bound the nonlinearity of a function.
@@
 
+\begin{definition}
+    For an even integer $n\geq 0$, we introduce the Boolean function $d_n\in\BN$ given by:
+    \[
+        d_n(x)=\sum_{i=1}^{n/2}x_{2i-1}x_{2i}.
+    \]
+\end{definition}
+
 %We study the restricted Walsh transform  of $f$ to bound its nonlinearity.
 \begin{proposition}\label{prop:restrWT}
-Let $n \in \N^*$ even, and $f$ be the function from Definition~\ref{def:revHWBF}, for all $k\in [0,n]$ its restricted Walsh transform in $a\in \F_2^n$ is given by:
-\[\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x},\]
-where $c$ is the $n$-length binary vector such that $c=a+e_k+\sum_{i=n/2+1}^n e_i$ where the $e_i$ denotes the canonical vector with $1$ in position $i$.
+Let $n\geq 2$ be an even integer. Let $a\in\F_2^n$ and let $k\in[1,n]$. If we put $c=a+e_k+\sum_{i=1}^{n/2}e_{2i}$, then the restricted Walsh transform of the revisited \hwbf{} $f\in\BN$ satisfies:
+\[
+    \wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{d_n(x)+c\cdot x}=\wtk{d_n}{k}(c).
+\]
 \end{proposition}
+
 \begin{proof}
@@
 %\begin{align*}
-\[	\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+a \cdot x}
-	=\sum_{x \in \Ekn{k}{n}} (-1)^{x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}+ a \cdot x}\\
-	=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x},\]
-where $c$ denotes the $n$-length binary vector such that $c=a+e_k+\sum_{i=n/2+1}^n e_i$ and $e_i$ denotes the $i$-th canonical vector.
+We compute:
+\begin{align*}
+    \wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+a \cdot x}\\
+    &=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2}(x_{2i-1}+1)x_{2i}+x_k+a \cdot x}\\
+    &=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2}x_{2i-1}x_{2i}+\left(x_k+\sum_{i=1}^{n/2}x_{2i}+a \cdot x\right)}\\
+    &=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2}x_{2i-1}x_{2i}+c\cdot x}.\qedhere
+\end{align*}
 \end{proof}
@@
 
-Accordingly, we can study the restricted Walsh transform of this function by analyzing the one of $\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}$, for all $a$. We introduce the following notations.
+Accordingly, we can study the restricted Walsh transform of the \hwbf{} by analyzing the one of $d_n$. We introduce the following notations:
 
 \begin{definition}
-Let $n\in \N$ be an even number, and $a\in \F_2^n$. We denote $d_n$ the function given by: $d_n(x)=\sum_{i \text{ odd}}^n x_i x_{i+1}$, 
-and we denote by $\Dnka{n}{k}{a}$ the quantity:
-\[\Dnka{n}{k}{a}= \sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a x}\]
-\end{definition}
-
-We can give a recursive relation for $\Dnka{n}{k}{a}$.
+Let $n\geq 0$ be an even integer and $a\in\F_2^n$ a vector. Then for every integer $k$, we define $\Dnka{n}{k}{a}=0$ if $n\not\in[0,n]$, and otherwise:
+\[
+    \Dnka{n}{k}{a}= \sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a\cdot x}.
+\]
+\end{definition}
+
+The $\Dnka{n}{k}{a}$ satisfy a recursive relation:
 
 \begin{proposition}\label{prop:recursiveDnka}
-Let $n\in \N$ be an even number, $k$ an integer in the range $[0,n]$ and $a\in \F_2^n$. the Following holds on $\Dnka{n}{k}{a}$:
+Let $n\geq 0$ be an even integer. Then for all $k\in[0,n]$ and $a\in\F_2^n$, the following hold true:
 \begin{itemize}
-	\item For $n=0$, $\Dnka{0}{k}{a}=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise.
-	\item if $n\geq 2$, denoting  $b=(a_1,\cdots,a_{n-2})$ and $y=(x_1,\cdots,x_{n-2})$, we get:
+    \item We have $\Dnka 00a=1$ and $\Dnka 0ka=0$ if $k\neq 0$.
+    \item If $n\geq 2$, then for $b=(a_1,\dots,a_{n-2})$, we have:
     \[\Dnka{n}{k}{a}=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.\]
 \end{itemize}
-
 \end{proposition}
@@
 \begin{proof}
-For $n\geq 2$ we can rewrite $\Dnka{n}{k}{a}$:
-
+    We have that $\Dnka 00a=(-1)^0=0$ since $\Ekn 00=\{\epsilon\}$ for the empty vector $\epsilon\in\F_2^0$.
+That $\Dnka 0ka=0$ if $k\neq 0$ follows directly from the definition.
+Assume now that $n\geq 2$.
+By considering binary vectors $x\in\F_2^n$ as $x=(y,x_{n-1},x_n)$ for $y\in\F_2^{n-2}$, we get:
     \begin{align*}
     \Dnka{n}{k}{a}&=\sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a x}\\
-&=\sum_{x\in \Ekn{k}{n-2}} (-1)^{d_{n-2}(y) +b y}+
-\sum_{x\in \Ekn{k-1}{n-2}} (-1)^{d_{n-2}(y) +b y + a_{n-1}}\\
-&+\sum_{x\in \Ekn{k-1}{n-2}} (-1)^{d_{n-2}(y) +b y + a_{n}}
-+\sum_{x\in \Ekn{k-2}{n-2}} (-1)^{d_{n-2}(y) +b y +1 + a_{n-1}+ a_{n}}\\
-&=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.
+    &=\sum_{y\in \Ekn{k}{n-2}} (-1)^{d_{n-2}(y) +b y}+
+    \sum_{y\in \Ekn{k-1}{n-2}} (-1)^{d_{n-2}(y) +b y + a_{n-1}}\\
+    &\qquad+\sum_{y\in \Ekn{k-1}{n-2}} (-1)^{d_{n-2}(y) +b y + a_{n}}
+    +\sum_{y\in \Ekn{k-2}{n-2}} (-1)^{d_{n-2}(y) +b y +1 + a_{n-1}+ a_{n}}\\
+    &=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.\qedhere
     \end{align*}
-
-The limit cases $\Dnka 0ka=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise are obtained from the values of $\Dnka{2}{k}{a}$ given in Table~\ref{tab:Dnka}.
 \end{proof}
@@
 
-We remark that it gives three different cases depending on the values of the two last elements of $a$:%Then it gives three cases:
+\begin{remark}
+    We note that Proposition~\ref{prop:recursiveDnka} gives three different cases depending on the values of the two last elements of $a$:%Then it gives three cases:
 \begin{itemize}
-	\item if $a_{n-1}=a_n=0$, then $\Dnka{n}{k}{a}=\Dnka{n}{k}{b}+2\Dnka{n}{k-1}{b}-\Dnka{n}{k-2}{b}$,
+	\item if $a_{n-1}=0=a_n$, then $\Dnka{n}{k}{a}=\Dnka{n}{k}{b}+2\Dnka{n}{k-1}{b}-\Dnka{n}{k-2}{b}$,
 	\item if $a_{n-1} \ne a_n$, then $\Dnka{n}{k}{a}=\Dnka{n}{k}{b}+\Dnka{n}{k-2}{b}$,
-	\item if $a_{n-1}=a_n=1$, then $\Dnka{n}{k}{a}=\Dnka{n}{k}{b}-2\Dnka{n}{k-1}{b}-\Dnka{n}{k-2}{b}$.
+	\item if $a_{n-1}=1=a_n$, then $\Dnka{n}{k}{a}=\Dnka{n}{k}{b}-2\Dnka{n}{k-1}{b}-\Dnka{n}{k-2}{b}$.
 \end{itemize}
+\end{remark}
 
@@
 
-The recursive formula of Proposition~\ref{prop:recursiveDnka} gives different cases depending on the values of $a_{n-1}$ and $a_n$, however the same reasoning applies with any $a_i, a_{i+1}$ where $i$ is odd.
-Thereafter, the value of $\Dnka{n}{k}{a}$ depends only on the number of pairs of $a$ being $(0,0)$, $(1,1)$ or $(0,1)$ or $(1,0)$, and the values $\Dnka{2}{k}{a}$ for $k \in [0,2]$ and $a \in \{ (0,0),(1,1),(0,1)\}$.
-We give the first values of $\Dnka{2}{k}{a}$ in Table~\ref{tab:Dnka},  these values and Proposition~\ref{prop:recursiveDnka} are sufficient to determine any $\Dnka{n}{k}{a}$. 
-In the following, we show how the Walsh transform of $f$ can be written in terms of $\Dnka{n}{k}{a}$.
-Then, in Section~\ref{sec:balancedness} we use Proposition~\ref{prop:recursiveDnka} to determine the balancedness of $f$, and in Section~\ref{sec:genfunc} we study the value of $\Dnka{n}{k}{a}$ using trough generating functions.
-
-%The first values of $\Dnka{2}{k}{a}$ are listed in Table~\ref{tab:Dnka}
+The recursive formula of Proposition~\ref{prop:recursiveDnka} gives different cases depending on the values of the pair $(a_{n-1},a_n)$.
+However, the same reasoning applies with any pair of the form $(a_{2i-1}, a_{2i})$ for $i\in[0,n/2]$.
+Therefore, the value of $\Dnka{n}{k}{a}$ depends only on the number of pairs $(a_{2i-1}, a_{2i})$ in $a$ being $(0,0)$, $(1,1)$, $(0,1)$ or $(1,0)$.
+We give the values of $\Dnka{2}{k}{a}$ for $n=2$ in Table~\ref{tab:Dnka}. These values together with Proposition~\ref{prop:recursiveDnka} are sufficient to determine any $\Dnka{n}{k}{a}$.
 
@@
 	\end{tabular}
-	\tablecaption{Values of $\Dnka{2}{k}{a}$}\label{tab:Dnka}
+	\tablecaption{Values of $\Dnka{2}{k}{a}$ for $n=2$.}\label{tab:Dnka}
 \end{table}
 
-Then, we can express the restricted Walsh transform of $f$ in terms of $\Dnka{n}{k}{a}$:
-
-\begin{proposition}[Walsh transform of $f$]\label{prop:WT}
-	Let $n \in \N^*$ even, and $f$ be the function from Definition~\ref{def:revHWBF}, for all $a\in \F_2^n$ its Walsh transform is given by:
-	\[ \wt{f}(a)=1+\sum_{k=1}^n \Dnka{n}{k}{b+\pi(e_k)},\]
-where $\pi$ is the permutation sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions, and $b=\pi(a)+(0,1,0,1,\ldots,0,1)$.
+In the following, we show how the Walsh transform of $f$ can be written in terms of the $\Dnka{n}{k}{a}$.
+Then, in Section~\ref{sec:balancedness} we use Proposition~\ref{prop:recursiveDnka} to determine the balancedness of $f$, and in Section~\ref{sec:genfunc} we study the value of $\Dnka{n}{k}{a}$ using generating functions.
+
+\begin{proposition}\label{prop:WT}
+    Let $n\geq 0$ be even, and let $a\in\F_2^n$. Put $b=a+\sum_{i=1}^{n/2}e_{2i}$. Then the Walsh transform of the revisited \hwbf{} $f\in\BN$ at $a$ is given by:
+    \[ \wt{f}(a)=1+\sum_{k=1}^n \Dnka{n}{k}{b+e_k}.\]
 \end{proposition}
@@
 \begin{proof}
-Using Proposition~\ref{prop:restrWT}, the restricted Walsh transform of $f$ can then be written as \[
-\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x}=\Dnka{n}{k}{d},\]
-where $d$ is the permutation of $c$ obtained by sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions.
-
-Calling $\pi$ this permutation, since $c=a+e_k+\sum_{i=n/2+1}^n e_i$, we can write $d=\pi(c)=\pi(a)+ \pi(e_k)+ (0,1,0,1,\ldots,0,1)$. 
-Accordingly, if $k\leq n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2+1$, with one couple of consecutive elements (the first one with an odd index) being $(1,1)$ and all the others $(0,1)$.
-Otherwise,  when $k> n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2-1$, with one couple of consecutive elements (the first one with an odd index) being $(0,0)$ and all the others $(0,1)$.
-
-Denoting by $b$ the vector $\pi(a)+(0,1,0,1,\ldots,0,1)$, we can write the Walsh transform of $f$ in $a$ as:
-\[ \wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}.\qedhere\]
+For every $k\in[1,n]$, define $c_k=a+e_k+\sum_{i=1}^{n/2}e_{2i}=b+e_k$. Then, using Proposition~\ref{prop:restrWT}, we get:
+\[
+    \wt{f}(a)=1+\sum_{k=1}^n\wtk fk(a)=1+\sum_{k=1}^n\wtk{d_n}k(c_k)=1+\sum_{k=1}^n\Dnka nk{c_k}=1+\sum_{k=1}^n\Dnka nk{b+e_k}.\qedhere
+\]
 \end{proof}
@@
 
-In this part we determine for which values of $n$ the function $f$ is balanced, using the expression of its Walsh transform in terms of $\Dnka{n}{k}{a}$ and the recursive relation of these quantities.
-
-\begin{theorem}[Balancedness of $f$]\label{th:bal}
-	Let $n \in \N^*$ even, and $f$ be the $n$-variable function from Definition~\ref{def:revHWBF}, the following holds on its Walsh transform in $0_n$:
+In this part, we determine for which values of $n$ the revisited \hwbf{} $f\in\BN$ is balanced by using the expression of its Walsh transform in terms of the $\Dnka{n}{k}{a}$ together with the recursive relation of these quantities.
+
+\begin{theorem}\label{th:bal}
+    For an even integer $n\geq 2$, the following holds true for the Walsh transform of the revisited \hwbf{} $f\in\BN$ at $0_n$:
 	\[\wt{f}(0_n)= \left \{
@@
 	\end{array}\right.\]
-
-	Accordingly, $f$ is balanced when $n \equiv 0\mod 4$ and unbalanced when $n\equiv 2 \mod 4$.
-
+	Accordingly, $f$ is balanced when $n \equiv 0\bmod 4$ and unbalanced when $n\equiv 2 \bmod 4$.
 \end{theorem}
@@
 
-\subsection{Study of $\Dnka nka$ through Generating Functions}\label{sec:genfunc}
+\subsection{Study of $\Dnka nka$ through generating functions}\label{sec:genfunc}
 
 \begin{definition}\label{defi:P_a}
+    Let $n\geq 2$ be an even integer.
 For $a\in\F_2^n$, denote by $p=p(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(0,0)$, by $q=q(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(1,1)$, and by $r=r(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})\in\{(0,1),(1,0)\}$.
@@
 \]
-        \item The sum over the even and the odd $k$ of the the $\Dnka nka$ are, respectively:
+        \item The sum over the even and the odd $k$ of the $\Dnka nka$ are, respectively:
  %       \begin{gather*}
@@
 	\end{minipage}
-	\tablecaption{Approximate values of $B_n$ for various values of $n$}
+	\tablecaption{Approximate values of $B_n$ for various values of $n$.}
 	\label{table:walsh_bounds}
@@
 	\end{tabular}
-	\caption{Lowest possible values of $(d, e)$ for different values of $ n$}
+	\tablecaption{Lowest possible values of $(d, e)$ for different values of $n$.}
 	\label{table:FAI}

### 2024-11-28 RevisedHiddenWeight.tex
- Corrections, plus indications for parts which need to be addressed.

@@
 }
-\authorrunning{P. M\'eaux, T. Seuré, D. Tang}
+\authorrunning{P.\ M\'eaux, T.\ Seur\'e, D.\ Tang}
 
@@
 	\end{abstract}
+
+\tsnote{@Self, check entire document.}
 
@@
 \textsf{HHE} requires Boolean functions that can be efficiently evaluated in an input-oblivious algorithm.
-For instance, several new binary stream ciphers have been proposed since 2016, including Kreyvium~\cite{JOC:CCFLNP18}, FLIP~\cite{EC:MJSC16}, Rasta~\cite{C:Rasta}, FiLIP~\cite{INDO:MCJS19}, Dasta~\cite{TOSC:BeiLea20} and Fasta~\cite{CTRSA:CidIndRad22}.
+For instance, several new binary stream ciphers have been proposed since 2016, including Kreyvium~\cite{JOC:CCFLNP18}, \textsf{FLIP}~\cite{EC:MJSC16}, Rasta~\cite{C:Rasta}, \textsf{FiLIP}~\cite{INDO:MCJS19}, Dasta~\cite{TOSC:BeiLea20} and Fasta~\cite{CTRSA:CidIndRad22}.
 Currently, designs employing Boolean functions with more than one hundred variables as filters lead to \textsf{HHE} schemes with the best latency~\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24,eprint:AGHM24}.
@@
 
-Throughout this paper, $n$ will always denote a positive integer.
+Throughout this paper, $n\geq 0$ will always denote a non-negative integer.
 Further, our intervals will only contain integers, so that for instance $[0,n]=\{0,1,\dots,n\}$.
-The set of binary vectors of length $n$ will be denoted by $\F_2^n$.
+The set of binary vectors of length $n$ will be denoted by $\F_2^n$, with zero vector written as $0_n$.
+The canonical basis of $\F_2^n$ will be written as $\{e_1,\dots,e_n\}$; therefore, $e_i\in\F_2^n$ is the vector which is zero everywhere, except at position $i$.
 The entries of a binary vector $x\in\F_2^n$ will always be denoted by $x_1,\dots,x_n$.
-We denote the scalar product of two binary vectors $x,y\in\F_2^n$ by $x\cdot y=\sum_{i=1}^nx_iy_i\in\F_2$.
+Given a permutation $\pi:[1,n]\to[1,n]$ and a vector $x\in\F_2^n$, we define $\pi(x)=(x_{\pi(i)})_{i\in[1,n]}\in\F_2^n$.
+We write the scalar product of two binary vectors $x,y\in\F_2^n$ as $x\cdot y=\sum_{i=1}^nx_iy_i\in\F_2$.
 The Hamming weight of a binary vector $x\in\F_2^n$ is denoted by $\w(x)=|\{i\in [1,n]:x_i=1\}|$.
@@
 
-\begin{Prop}[Properties of some functions from $\WD{1}{n}$\label{prop:wwd1}]
+\begin{Prop}\label{prop:wwd1}
 	Let $n\geq 2$ be an even integer.
 	\begin{itemize}
-		\item (\eg{}~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\mathsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
+		\item (\eg{} Theorem $3$ in~\cite{DCC:DalMaiSar06}) The majority function $\mathsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
 		\[
@@
 		\]
-		\item (\cite{DAM:WCST14}, Theorem $3$) The \hwbf{} $h$ introduced in Definition~\ref{def:hwbf} satisfies:
+		\item (Theorem $3$ in~\cite{DAM:WCST14}) The \hwbf{} $h$ introduced in Definition~\ref{def:hwbf} satisfies:
 		\[
@@
 		\]	
-		\item (\cite{DAM:WCST14}, Theorem $1$) The \hwbf{} $h$ introduced in Definition~\ref{def:hwbf} satisfies $\degg(h)=n-1$ for all $n\geq 4$.
+		\item (Theorem $1$ in \cite{DAM:WCST14}) The \hwbf{} $h$ introduced in Definition~\ref{def:hwbf} satisfies $\degg(h)=n-1$ for all $n\geq 4$.
 	\end{itemize}
@@
     \[
-        \displaystyle \kraw{k}{x}{n}=\sum_{j=0}^{k} (-1)^j \binom{x}{j} \binom{n-x}{k-j}.
-    \]
-    Alternatively, the Krawtchouk polynomials can be characterized as the coefficients in the generating function for $(1+z)^{n-x} (1-z)^x$ in the variable $z$:
-    \[
-        (1+z)^{n-x} (1-z)^x=\sum_{k=0}^\infty \kraw{k}{x}{n} z^k.
+        \kraw{k}{x}{n}=\sum_{j=0}^{k} (-1)^j \binom{x}{j} \binom{n-x}{k-j}.
+    \]
+    If $k<0$, we further define $\kraw{k}{x}{n}=0$.
+The Krawtchouk polynomials can alternatively be characterized as the coefficients in the generating function for $(1+z)^{n-x} (1-z)^x$ in the variable $z$:
+    \[
+        (1+z)^{n-x} (1-z)^x=\sum_{k\in\Z} \kraw{k}{x}{n} z^k.
     \]
@@
 \begin{definition}[Revisited \hwbf{}]\label{def:revHWBF}
-Let $n\in \N^*$, even, we call revisited \hwbf{} and denote by $f$ the Boolean function defined as:
-\[f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k.\]
-\end{definition}
-
-%We study the function $f$ in an even number of variables $n$ defined as the following:
-%\[f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k.\]
+For an even integer $n\geq 0$, we call revisited \hwbf{} the Boolean function $f\in\BN$ defined as:
+\[f(x)=\sum_{i=1}^{n/2}(x_i+1) x_{i+\frac{n}{2}} + \sum_{k=1}^nx_k\phikn{k}{n}(x).\]
+\end{definition}
 
 Since $f$ is the sum of a quadratic function and a weightwise affine function, it is a weightwise quadratic function.
-Using the formalism of Definition~\ref{def:wwdegd}, $f$ is the weightwise quadratic function defined by:% $f_0=0$ and for $k\in [1,n]$ $f_k=x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$.
-\[f_0=0, \quad \text{ and } \quad \forall k \in [1,n], \, f_k=x_k+\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}.\]
-
+Using the formalism of Definition~\ref{def:wwdegd}, $f$ is the weightwise quadratic function defined by $f_0(x)=0$ and $f_k(x)=x_k+\sum_{i=1}^{n/2}(x_i+1) x_{i+n/2}$ for $k\in[1,n]$.
 This form allows to derive the restricted Walsh transform of $f$, which can be a useful tool to study the balancedness and bound the nonlinearity of a function.
 %Maybe add examples, such as OM24, M24
-
 %We study the restricted Walsh transform  of $f$ to bound its nonlinearity.
 \begin{proposition}\label{prop:restrWT}
-Let $n \in \N^*$ even, and $f$ be the function from Definition~\ref{def:revHWBF}, for all $k\in [0,n]$ its restricted Walsh transform in $a\in \F_2^n$ is given by:
-\[\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x},\]
-where $c$ is the $n$-length binary vector such that $c=a+e_k+\sum_{i=n/2+1}^n e_i$ where the $e_i$ denotes the canonical vector with $1$ in position $i$.
+Let $n\geq 0$ be an even integer, and let $f\in\BN$ be the revisited \hwbf{}.
+Consider any binary vector $a\in\F_2^n$, and define $c=a+e_k+\sum_{i=n/2+1}^n e_i$.
+Then the restricted Walsh transform of $f$ satisfies:
+\[\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+n/2}+ c \cdot x}.\]
 \end{proposition}
 \begin{proof}
+We compute:
 %\begin{align*}
@@
 %\begin{align*}
-\[	\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+a \cdot x}
-	=\sum_{x \in \Ekn{k}{n}} (-1)^{x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}+ a \cdot x}\\
-	=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x},\]
-where $c$ denotes the $n$-length binary vector such that $c=a+e_k+\sum_{i=n/2+1}^n e_i$ and $e_i$ denotes the $i$-th canonical vector.
+\begin{align*}
+    \wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+a \cdot x}\\
+	&=\sum_{x \in \Ekn{k}{n}} (-1)^{x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}+ a \cdot x}\\
+	&=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+n/2}+\left(x_k+\sum_{i=n/2+1}^{n}x_i+a\cdot x\right)}\\
+    &=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+n/2}+ c \cdot x}.\qedhere
+\end{align*}
 \end{proof}
@@
 
-Accordingly, we can study the restricted Walsh transform of this function by analyzing the one of $\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}$, for all $a$. We introduce the following notations.
+Accordingly, we can study the restricted Walsh transform of the revisited \hwbf{} by analyzing the one of the following Boolean function $d_n\in\BN$:
 
 \begin{definition}
-Let $n\in \N$ be an even number, and $a\in \F_2^n$. We denote $d_n$ the function given by: $d_n(x)=\sum_{i \text{ odd}}^n x_i x_{i+1}$, 
-and we denote by $\Dnka{n}{k}{a}$ the quantity:
-\[\Dnka{n}{k}{a}= \sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a x}\]
-\end{definition}
-
-We can give a recursive relation for $\Dnka{n}{k}{a}$.
+Let $n\geq 0$ be an even integer.
+Then we define the Boolean function $d_n\in\BN$ by $d_n(x)=\sum_{i=1}^{n/2}x_{2i-1}x_{2i}$.
+Further, for an integer $k$ and a binary vector $a\in\F_2^n$, we define $\Dnka{n}{k}{a}=0$ if $n\not\in[0,n]$, and otherwise:
+\[
+    \Dnka{n}{k}{a}=\sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a\cdot x}.
+\]
+\end{definition}
+
+The $\Dnka{n}{k}{a}$ satisfy a recursive relation:
 
 \begin{proposition}\label{prop:recursiveDnka}
-Let $n\in \N$ be an even number, $k$ an integer in the range $[0,n]$ and $a\in \F_2^n$. the Following holds on $\Dnka{n}{k}{a}$:
+Let $n\geq 0$ be an even integer. Then for all $k\in[0,n]$ and $a\in\F_2^n$, the following hold true:
 \begin{itemize}
-	\item For $n=0$, $\Dnka{0}{k}{a}=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise.
-	\item if $n\geq 2$, denoting  $b=(a_1,\cdots,a_{n-2})$ and $y=(x_1,\cdots,x_{n-2})$, we get:
+    \item We have $\Dnka 00a=1$ and $\Dnka 0ka=0$ if $k\neq 0$.
+    \item If $n\geq 2$, then for $b=(a_1,\dots,a_{n-2})\in\F_2^{n-2}$, we have:
     \[\Dnka{n}{k}{a}=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.\]
 \end{itemize}
-
 \end{proposition}
@@
 \begin{proof}
-For $n\geq 2$ we can rewrite $\Dnka{n}{k}{a}$:
-
+    We have that $\Dnka 00a=(-1)^0=0$ since $\Ekn 00=\{\epsilon\}$ for the empty vector $\epsilon\in\F_2^0$.
+That $\Dnka 0ka=0$ if $k\neq 0$ follows directly from the definition.
+Assume now that $n\geq 2$.
+By considering binary vectors $x\in\F_2^n$ as $x=(y,x_{n-1},x_n)$ for $y\in\F_2^{n-2}$, we get:
     \begin{align*}
-\Dnka{n}{k}{a}&=\sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a x}\\
-&=\sum_{x\in \Ekn{k}{n-2}} (-1)^{d_{n-2}(y) +b y}+
-\sum_{x\in \Ekn{k-1}{n-2}} (-1)^{d_{n-2}(y) +b y + a_{n-1}}\\
-&+\sum_{x\in \Ekn{k-1}{n-2}} (-1)^{d_{n-2}(y) +b y + a_{n}}
-+\sum_{x\in \Ekn{k-2}{n-2}} (-1)^{d_{n-2}(y) +b y +1 + a_{n-1}+ a_{n}}\\
-&=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.
+    \Dnka{n}{k}{a}&=\sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a\cdot x}\\
+    &=\sum_{y\in \Ekn{k}{n-2}} (-1)^{d_{n-2}(y) +b\cdot y}+
+    \sum_{y\in \Ekn{k-1}{n-2}} (-1)^{d_{n-2}(y) +b\cdot y + a_{n-1}}\\
+    &\qquad+\sum_{y\in \Ekn{k-1}{n-2}} (-1)^{d_{n-2}(y) +b\cdot y + a_{n}}
+    +\sum_{y\in \Ekn{k-2}{n-2}} (-1)^{d_{n-2}(y) +b\cdot y +1 + a_{n-1}+ a_{n}}\\
+    &=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.\qedhere
     \end{align*}
-
-The limit cases $\Dnka 0ka=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise are obtained from the values of $\Dnka{2}{k}{a}$ given in Table~\ref{tab:Dnka}.
 \end{proof}
@@
 
-The recursive formula of Proposition~\ref{prop:recursiveDnka} gives different cases depending on the values of $a_{n-1}$ and $a_n$, however the same reasoning applies with any $a_i, a_{i+1}$ where $i$ is odd.
-Thereafter, the value of $\Dnka{n}{k}{a}$ depends only on the number of pairs of $a$ being $(0,0)$, $(1,1)$ or $(0,1)$ or $(1,0)$, and the values $\Dnka{2}{k}{a}$ for $k \in [0,2]$ and $a \in \{ (0,0),(1,1),(0,1)\}$.
-We give the first values of $\Dnka{2}{k}{a}$ in Table~\ref{tab:Dnka},  these values and Proposition~\ref{prop:recursiveDnka} are sufficient to determine any $\Dnka{n}{k}{a}$. 
-In the following, we show how the Walsh transform of $f$ can be written in terms of $\Dnka{n}{k}{a}$.
-Then, in Section~\ref{sec:balancedness} we use Proposition~\ref{prop:recursiveDnka} to determine the balancedness of $f$, and in Section~\ref{sec:genfunc} we study the value of $\Dnka{n}{k}{a}$ using trough generating functions.
-
-%The first values of $\Dnka{2}{k}{a}$ are listed in Table~\ref{tab:Dnka}
-
-\begin{table}[H]
+\begin{remark}\label{rmk:dependence_dnka}
+    The recursive formula of Proposition~\ref{prop:recursiveDnka} gives different cases depending on the values of the pair $(a_{n-1},a_n)$.
+However, the same reasoning applies with any pair of the form $(a_{2i-1}, a_{2i})$ for $i\in[0,n/2]$.
+Therefore, the value of $\Dnka{n}{k}{a}$ depends only on the number of pairs $(a_{2i-1}, a_{2i})$ in $a$ being $(0,0)$, $(1,1)$, $(0,1)$ or $(1,0)$.
+We give the values of $\Dnka{2}{k}{a}$ for $n=2$ in Table~\ref{tab:Dnka}.
+These values together with Proposition~\ref{prop:recursiveDnka} are sufficient to determine any $\Dnka{n}{k}{a}$.
+We will get back to this in Remark~\ref{rmk:Dnka_dep_pqr}.
+\end{remark}
+
+\begin{table}
 	\centering
@@
 	\end{tabular}
-	\tablecaption{Values of $\Dnka{2}{k}{a}$}\label{tab:Dnka}
+	\tablecaption{Values of $\Dnka{2}{k}{a}$ for $n=2$.}\label{tab:Dnka}
 \end{table}
 
-Then, we can express the restricted Walsh transform of $f$ in terms of $\Dnka{n}{k}{a}$:
-
-\begin{proposition}[Walsh transform of $f$]\label{prop:WT}
-	Let $n \in \N^*$ even, and $f$ be the function from Definition~\ref{def:revHWBF}, for all $a\in \F_2^n$ its Walsh transform is given by:
-	\[ \wt{f}(a)=1+\sum_{k=1}^n \Dnka{n}{k}{b+\pi(e_k)},\]
-where $\pi$ is the permutation sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions, and $b=\pi(a)+(0,1,0,1,\ldots,0,1)$.
+In the following, we show how the Walsh transform of $f$ can be written in terms of the $\Dnka{n}{k}{a}$.
+Then, in Section~\ref{sec:balancedness} we use Proposition~\ref{prop:recursiveDnka} to determine the balancedness of $f$, and in Section~\ref{sec:genfunc} we study the value of $\Dnka{n}{k}{a}$ using generating functions.
+
+\tsnote{@Pierrick, check the below proposition with its proof.}
+\begin{proposition}\label{prop:WT}
+    Let $n\geq 0$ be an even integer, and let $f\in\BN$ be the revisited \hwbf{}.
+Denote by $\pi:[1,n]\to[1,n]$ the permutation sending the first $n/2$ elements to the odd positions and the $n/2$ last ones to the even positions.
+Let $a\in\F_2^n$ be a binary vector, and let $b=\pi(a)+(0,1,0,1,\ldots,0,1)$.
+Then the following holds true:
+	\[ \wt{f}(a)=1+\sum_{k=1}^n \Dnka{n}{k}{b+\pi(e_k)}.\]
 \end{proposition}
@@
 \begin{proof}
-Using Proposition~\ref{prop:restrWT}, the restricted Walsh transform of $f$ can then be written as \[
+We have by Proposition~\ref{prop:restrWT} that:
+\[
 \wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x}=\Dnka{n}{k}{d},\]
@@
 \subsection{Balancedness of $f$}\label{sec:balancedness}
+\tsnote{@Pierrick, check entire section.}
 
@@
 
-\begin{theorem}[Balancedness of $f$]\label{th:bal}
+\begin{theorem}\label{th:bal}
 	Let $n \in \N^*$ even, and $f$ be the $n$-variable function from Definition~\ref{def:revHWBF}, the following holds on its Walsh transform in $0_n$:
@@
 
-In this section, we study the values of $\Dnka nka$ using generating functions.
-First, in Section~\ref{sec:genfunc} we establish key properties of these quantities.
-Then, in Section~\ref{sec:Cauchy}, we apply Cauchy's estimate to bound the absolute values of $\Dnka nka$, which enables us to bound the absolute values of the Walsh transform coefficients of $f$ and consequently, the nonlinearity.
-Finally, in Section~\ref{sec:general}, we demonstrate how this result can be extended to bound the nonlinearity of a family of weightwise quadratic functions.
-
-\subsection{Study of $\Dnka nka$ through Generating Functions}\label{sec:genfunc}
+This section examines the values of $\Dnka nka$ through the use of generating functions.
+To begin, in Section~\ref{sec:genfunc}, we determine essential characteristics of these values.
+Subsequently, in Section~\ref{sec:Cauchy}, we employ Cauchy's estimate to bound the absolute values of $\Dnka nka$.
+This approach allows us to also bound the absolute values of the Walsh transform coefficients of the revisited \hwbf{}, thereby constraining the nonlinearity.
+Lastly, in Section~\ref{sec:general}, we illustrate how this result can be extended to bound the nonlinearity of a family of weightwise quadratic functions.
+
+\subsection{Study of $\Dnka nka$ through generating functions}\label{sec:genfunc}
 
 \begin{definition}\label{defi:P_a}
-    For $a\in\F_2^n$, denote by $p=p(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(0,0)$, by $q=q(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(1,1)$, and by $r=r(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})\in\{(0,1),(1,0)\}$.
+    Let $n\geq 0$ be an even integer.
+For $a\in\F_2^n$, we denote by $p=p(a)$ the number of $i\geq 1$ for which $(a_{2i-1},a_{2i})=(0,0)$, by $q=q(a)$ the number of $i\geq 1$ for which $(a_{2i-1},a_{2i})=(1,1)$, and by $r=r(a)$ the number of $i\geq 1$ for which $(a_{2i-1},a_{2i})\in\{(0,1),(1,0)\}$.
 We then have $p+q+r=n/2$.
-Consider further the integer polynomial $P_a(z)$ given by the following expression:
+We further introduce the integer polynomial $P_a(z)$ given by the following expression:
     \[
@@
 \begin{proposition}\label{proposition:generating_fct}
-	It holds that $\sum_{k\in\Z}\Dnka nka z^k= P_a(z)$.
+	For every even integer $n\geq 0$ and every binary vector $a\in\F_2^n$, the following holds:
+    \[
+        \sum_{k\in\Z}\Dnka nka z^k= P_a(z).
+    \]
 \end{proposition}
@@
 	We proceed by induction on even $n\geq 0$. 
-	For the base case $n=0$, for $a\in\F_2^0$, we have $P_a(z)=1$, while $\Dnka 0ka=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise (from Proposition~\ref{prop:recursiveDnka}). 
+	For the base case $n=0$, for $a\in\F_2^0$ (the empty vector), we have $P_a(z)=1$, while $\Dnka 00a=1$ and $\Dnka 0ka=0$ if $k\neq 0$ (from Proposition~\ref{prop:recursiveDnka}). 
 	For the inductive step, let $n\geq 2$ be even, and assume that the corresponding formula holds for $n-2$. Using the recursive formula for $\Dnka nka$ with the notation $a=(b,a_{n-1},a_n)$, we have:
@@
 	\sum_{k\in\Z}\Dnka nka z^k&=\sum_{k\in\Z}\Dnka{n-2}kbz^k+\big((-1)^{a_{n-1}}+(-1)^{a_{n}}\big)\sum_{k\in\Z}\Dnka{n-2}{k-1}{b}z^k\\
-	&\quad+(-1)^{1+a_{n-1}+a_n}\sum_{k\in\Z}\Dnka{n-2}{k-2}{b}z^k\\
+	&\qquad+(-1)^{1+a_{n-1}+a_n}\sum_{k\in\Z}\Dnka{n-2}{k-2}{b}z^k\\
 	&=P_b(z)+\big((-1)^{a_{n-1}}+(-1)^{a_{n}}\big)zP_b(z)+(-1)^{1+a_{n-1}+a_n}z^2P_b(z)\\
@@
 
-\begin{remark}
-    In particular, since $P_a(z)$ only depends on the triplet $(p,q,r)$, we deduce that also $\Dnka nka$ only depends on the triplet $(p,q,r)$; therefore, it makes sense to introduce the notation $\mathsf D_{n,k}^{p,q,r}=\Dnka nka$, where $a\in\mathbb F_2^n$ is any vector with $(p(a),q(a),r(a))=(p,q,r)$.
+\begin{remark}\label{rmk:Dnka_dep_pqr}
+    We have already argued in Remark~\ref{rmk:dependence_dnka} that $\Dnka nka$ only depends on $p(a)$, $q(a)$ and $r(a)$.
+This observation can also be obtained from Proposition~\ref{proposition:generating_fct}: since $P_a(z)$ only depends on $p(a)$, $q(a)$ and $r(a)$ (by definition), we deduce that also $\Dnka nka$ only depends on $p(a)$, $q(a)$ and $r(a)$.
+Therefore, for any $p,q,r\geq0$ satisfying $p+q+r=n/2$, it makes sense to introduce the notation $\mathsf D_{n,k}^{p,q,r}=\Dnka nka$, where $a\in\mathbb F_2^n$ is any vector with $(p(a),q(a),r(a))=(p,q,r)$.
 We will make use of this notation later on.
@@
 \begin{proposition}\label{proposition:symmetry}
-	For every integer $k$, we have:
+	For every even integer $n\geq 0$, for every binary vector $a\in\F_2^n$, and for every integer $k$, the following holds:
 	\[	\Dnka n{n-k}a=(-1)^{p+q+k}\Dnka nka.	\]
@@
 \begin{proof}
-	We define the reverse polynomial  $Q_a(z)$ such as the degree $n$ polynomial where each coefficient of $z^k$ in $Q_a(z)$ is equal to the coefficient of $z^{n-k}$ in $P_a(z)$. 
+	We define the reverse polynomial  $Q_a(z)$ as the degree $n$ polynomial where each coefficient of $z^k$ in $Q_a(z)$ is equal to the coefficient of $z^{n-k}$ in $P_a(z)$. 
 	Then we have:
@@
 	\end{align*}
-	Thus the coefficient of $z^k$ in $Q_a(z)$, which is $\Dnka n{n-k}a$, is equal to the coefficient of $z^k$ in $(-1)^{p+q}P_a(-z)$, which is $(-1)^{p+q+k}\Dnka nka$.
+	Therefore, the coefficient of $z^k$ in $Q_a(z)$, which is $\Dnka n{n-k}a$, is equal to the coefficient of $z^k$ in $(-1)^{p+q}P_a(-z)$, which is $(-1)^{p+q+k}\Dnka nka$.
 \end{proof}
@@
 \begin{Corollary}
-	If $r$ is odd, then for $k=n/2$, we have $\Dnka n{n/2}a=0.$
+    Let $n\geq 0$ be an even integer, and let $a\in\F_2^n$ be a binary vector. If $r=r(a)$ is odd, then it holds that $\Dnka n{n/2}a=0$.
 \end{Corollary}
@@
 \begin{proof}
-	By Proposition \ref{proposition:symmetry}, we have $\Dnka n{n/2}a=(-1)^{p+q+n/2}\Dnka n{n/2}a=-\Dnka n{n/2}a$ because $p+q+n/2\equiv n/2-p-q\equiv r\equiv 1\bmod 2$.
+	By Proposition \ref{proposition:symmetry}, we have $\Dnka n{n/2}a=(-1)^{p+q+n/2}\Dnka n{n/2}a=-\Dnka n{n/2}a$ because $p+q+n/2$ is odd: $p+q+n/2\equiv n/2-p-q\equiv r\equiv 1\bmod 2$.
 \end{proof}
@@
 \begin{proposition}
-    If $p=q$ and $k$ is odd, then $\Dnka nka=0=\Dnka n{n-k}a$.
+    Let $n\geq 0$ be an even integer, and let $a\in\F_2^n$ be a binary vector. If $k$ is an odd integer and  $p=q$, then it holds that $\Dnka nka=0=\Dnka n{n-k}a$.
 \end{proposition}
@@
     If $p=q$, we have $P_a(z)=(z^4-6z^2+1)^p\cdot(z^2+1)^r$, which can be seen as a polynomial in $z^2$.
-Thus, the coefficient $\Dnka nka$ of $z^k$ for odd $k$ must be zero in $P_a(z)$.
+Thus, the coefficient $\Dnka nka$ in $P_a(z)$ of $z^k$ for odd $k$ must be zero.
 It follows that also $\Dnka n{n-k}a=0$ by Proposition~\ref{proposition:symmetry}.
@@
 \begin{remark}\label{remark:D_nka_differentiation}
-    We can also use Proposition \ref{proposition:generating_fct} to obtain $\Dnka nka$ through differentiation and evaluation in $0$:
+    We can also use Proposition \ref{proposition:generating_fct} to obtain $\Dnka nka$ through differentiation and evaluation at $z=0$:
     \[
@@
 Indeed, either $p-q\equiv 0\bmod 3$, or $(p-q)^2\equiv 1\bmod 3$, in which case $2(p-q)^2+7\equiv 0\bmod 3$.
-
+\end{remark}
 \begin{table}
@@
     		$k$ & $\Dnka nka$\\ \hline
-    		$0$&$1$\\ \hline
-            $1$&$2(p-q)$\\ \hline
-            $2$&$2(p-q)^2-3(p+q)+r$\\ \hline
+    		$0$&$1$\\
+            $1$&$2(p-q)$\\ 
+            $2$&$2(p-q)^2-3(p+q)+r$\\
             $3$&$\frac 23(p-q)\left(2(p-q)^2-9(p+q)+3r+7\right)$\\ \hline
     	\end{tabular}
-    	\tablecaption{Values of $\Dnka{n}{k}{a}$ for small values of $k$}\label{tab:Dnka_small_k}
+    	\tablecaption{Values of $\Dnka{n}{k}{a}$ for small values of $k$.}\label{tab:Dnka_small_k}
     \end{table}
-\end{remark}
 
@@
 
-\begin{proposition}\mbox{}
+\begin{proposition}
+    Let $n\geq 0$ be an even integer, and let $a\in\F_2^n$ be a binary vector.
     \begin{enumerate}
-        \item If $n=16m$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, where $\ell_s=s(s-1)$, then $\Dnka n2a=0=\Dnka n{k-2}a$.
-        \item If $n=16m+2$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, where $\ell_s=\left(6s^2+6s+(-1)^s(2s+1)-1\right)/8$, then $\Dnka n3a=0=\Dnka n{k-3}a$.
-        \item If $n=16m+4$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, where $\ell_s=s^2$, then $\Dnka n2a=0=\Dnka n{k-2}a$.
-        \item If $n=16m+6$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, where $\ell_s=\left(6s^2+6s-(-1)^s(2s+1)+1\right)/8$, then $\Dnka n3a=0=\Dnka n{k-3}a$.
+        \item For every integer $s\geq0$, define $\ell_s=s(s-1)$. If $n=16m$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, then $\Dnka n2a=0=\Dnka n{n-2}a$.
+        \item For every integer $s\geq 0$, define $\ell_s=\left(6s^2+6s+(-1)^s(2s+1)-1\right)/8$.
+If $n=16m+2$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+2}\}$ for integers $m,s\geq 0$, then $\Dnka n3a=0=\Dnka n{k-3}a$.
+        \item For every integer $s\geq 0$, define $\ell_s=s^2$. If $n=16m+4$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, then $\Dnka n2a=0=\Dnka n{n-2}a$.
+        \item For every integer $s\geq 0$, define $\ell_s=\left(6s^2+6s-(-1)^s(2s+1)+1\right)/8$.
+If $n=16m+6$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+2}\}$ for integers $m,s\geq 0$, then $\Dnka n3a=0=\Dnka n{n-3}a$.
     \end{enumerate}
@@
 For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$ in the expression $\Dnka n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dnka n2a=0$.
+This checking can be autotomized by a computer algebra system.
+For this, we refer to the corresponding \textsf{SageMath} implementation from \cite{githubseure24}.\tsnote{@Pierrick, OK like this?}
 \end{proof}
@@
 \begin{remark}
-    There are other instances where $\Dnka nka=0$ which have not been described by the above. For instance, we have $\Dnka{34}4a=0$ if $\{p,q\}=\{1,2\}$.
+    There are other instances where $\Dnka nka=0$ which have not been described by any of the previous results. For instance, we have $\Dnka{34}4a=0$ if $\{p,q\}=\{1,2\}$.
 \end{remark}
 
-\pmnote{Show me screenshots proving that 2 and 4 are correct}
-
 Using Proposition \ref{proposition:generating_fct}, we can also deduce some sums involving the $\Dnka nka$:
 
-\begin{proposition}\mbox{}
+\begin{proposition}
+    Let $n\geq 0$ be an even integer, and let $a\in\F_2^n$ be a binary vector.
     \begin{enumerate}
@@
 \[
- \sum_{k=0}^n\Dnka nka=(-1)^{q}2^{n/2}, \quad \text{and} \quad
- \sum_{k=0}^n(-1)^k\Dnka nka=(-1)^{p}2^{n/2}.
+ \sum_{k\in\Z}\Dnka nka=(-1)^{q}2^{n/2} \quad \text{and} \quad
+ \sum_{k\in\Z}(-1)^k\Dnka nka=(-1)^{p}2^{n/2}.
 \]
@@
 \[
-\sum_{k=0}^{n/2}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big), \quad \text{ and } \quad 
-\sum_{k=0}^{n/2-1}\Dnka n{2k+1}a=2^{n/2-1}\big((-1)^{q}-(-1)^{p}\big).
+\sum_{k\in\Z}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big) \quad \text{ and } \quad 
+\sum_{k\in\Z}\Dnka n{2k+1}a=2^{n/2-1}\big((-1)^{q}-(-1)^{p}\big).
 \]
@@
 
-\begin{Prop}[Cauchy's estimate \eg~\cite{rudin1987}, Theorem 10.26]\label{property:cauchy_estimate}
+\begin{Prop}[Cauchy's estimate, \eg{} Theorem 10.26 in~\cite{rudin1987}]\label{property:cauchy_estimate}
     Let $w$ be a complex number, and let $R>0$ be some radius.
-If $f$ is a holomorphic function defined on an open set containing every complex number $z$ satisfying $|z-w|<R$, then for every integer $k\geq 0$, the $k$-th derivative of $f$ evaluated at $w$ can be bounded, in absolute value, as follows:
-    \[
-        \left|\frac{\dd^k}{\dd^k z}f(z)\vert_{z=w}\right|\leq\frac{k!\cdot M_R}{R^k},
-    \]
-%    where $M_R$ is the maximum of $|f(z)|$ on the circle $|z-w|=R$.
-where $M_R$ is the maximum of the absolute value of $f$, $|f(z)|$ on the circle defined by $|z-w|=R$.
+Let $f$ be a holomorphic function defined on an open set containing every complex number $z$ satisfying $|z-w|\leq R$, and let $M_R$ be the maximum of the absolute value of $f$ on the circle defined by $|z-w|=R$.
+Then for every integer $k\geq 0$, the $k$-th derivative of $f$ evaluated at $w$ can be bounded, in absolute value, as follows:
+    \[
+        \left|\frac{\dd^k}{\dd^k z}f(z)\vert_{z=w}\right|\leq\frac{k!\cdot M_R}{R^k}.
+    \]
 \end{Prop}
@@
 \begin{theorem}\label{theorem:bound_D_nka}
-    For every $a\in\F_2^n$ and every integer $k\geq 0$, it holds that:
+    Let $n\geq 0$ be an even integer, and let $a\in\F_2^n$ be a binary vector. Then, for every integer $k\in[0,n]$, it holds that:
     \[
@@
 \begin{proof}
-    From Remark~\ref{remark:D_nka_differentiation} we have: $k!\cdot\Dnka nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}$.
+    From Remark~\ref{remark:D_nka_differentiation} we have $k!\cdot\Dnka nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}$.
 Choosing $f=P_a$, $w=0$ and $R=1$ in Property \ref{property:cauchy_estimate} then gives:
@@
     \]
-    where $M$ is the maximum of $|P_a(z)|$ on the circle %$|z|=1$. 
-    $\dis=\{ z \in \C,  |z|=1  \}$.
+    where $M$ is the maximum of $|P_a(z)|$ on the complex circle %$|z|=1$. 
+    $\dis=\{ z \in \C: |z|=1  \}$.
     We claim, and prove below, that the maximum of $\left|-z^2+2z+1\right|$ on $\dis$ is $2\sqrt 2$. 
-    This implies that the maximum of $\left|-z^2-2z+1\right|$ on $\dis$ is $2\sqrt 2$ as well. 
+    This implies that the maximum of $\left|-z^2-2z+1\right|$ on $\dis$ is $2\sqrt 2$ as well because $-z^2-2z+1=-(-z)^2+2(-z)+1$. 
     Since the maximum of $\left|z^2+1\right|$ on $\dis$ is $2<2\sqrt 2$, it follows that $|\Dnka nka|\leq M\leq (2\sqrt 2)^{p+q}2^r\leq (2\sqrt 2)^{n/2}$.
@@
     \[
-        \left|-z^2+2z+1\right|^2=\left(z^2-2z-1\right)\left(\overline z^2-2\overline z-1\right)=6-\left(z^2+\overline z^2\right)=6-2\mathrm{Re}\left(z^2\right),
-    \]
-    where $\mathrm{Re}\left(z^2\right)$ denotes the real part of $z^2$.
+        \left|-z^2+2z+1\right|^2=\left(z^2-2z-1\right)\left(\overline z^2-2\overline z-1\right)=6-\left(z^2+\overline z^2\right)=6-2\mathrm{Re}\left(z^2\right).
+    \]
     Since the minimum of $\mathrm{Re}\left(z^2\right)$ on $\dis$ is $-1$, we conclude that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ is $6-2(-1)=8$.
@@
 \begin{Corollary}\label{cor:bound_walsh_cauchy}
-    For every $a\in\F_2^n$, it holds that:
+    Let $n\geq 0$ be an even integer, and let $f\in\BN$ be the revisited \hwbf{}. Then for every binary vector $a\in\F_2^n$, it holds that:
     \[
@@
     \]
-Equivalently, 
+    Equivalently, it holds that
     %$\NL(f)\geq 2^{n-1} - \frac{1 + n 2^{\frac{3}{4}n}} {2}$.
-$\NL(f)\geq 2^{n-1} - \frac{1}{2} -2^{\frac{3n}{4} + \log n -1}$.
+    $\NL(f)\geq 2^{n-1} - \frac{1}{2} -2^{3n/4 + \log_2(n) -1}$.
 \end{Corollary}
@@
 \begin{proof}
-    We have previously established in Proposition~\ref{prop:WT} that $\wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}$. Then, applying Theorem~\ref{theorem:bound_D_nka} yields:
-    \[
-        |\wt{f}(a)|\leq 1+\sum_{k=1}^n\left|\Dnka{n}{k}{b+\pi(e_k)}\right|\leq 1+ n\cdot 2^{3n/4}.%\qedhere
-    \]
-The bound on the nonlinearity comes from the second expression of Definition~\ref{def:nl}.
+    It is enough to prove the bound on $|\wt f(a)|$; the bound on the nonlinearity of $f$ comes from the second expression of Definition~\ref{def:nl}.
+We have previously established in Proposition~\ref{prop:WT} that $\wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b_k}$ for some vectors $b_k\in\F_2^n$.
+Then, applying the triangle inequality together with Theorem~\ref{theorem:bound_D_nka} yields:
+    \[
+        |\wt{f}(a)|\leq 1+\sum_{k=1}^n\left|\Dnka{n}{k}{b_k}\right|\leq 1+ n\cdot 2^{3n/4}.\qedhere
+    \]
 \end{proof}
@@
 \subsection{Generalization to a family of weightwise quadratic functions}\label{sec:general}
-In this part, we generalize the results of Section~\ref{sec:Cauchy} to all weightwise quadratic function such that for all $k\in [1,n]$, the function $f_k$ has exactly $t$ quadratic terms with no shared variables.
+In this part, we generalize the results of Section~\ref{sec:Cauchy} to all weightwise quadratic functions $f$ such that for every $k\in [1,n]$, the function $f_k$ in Definition~\ref{def:wwdegd} has exactly $t$ quadratic terms with no shared variables.
 
 \begin{definition}
-	Let $n\in \N^*$ be an even number and $t \in \N $ no greater than $n/2$, we denote by $d_{t,n}$ the function given by: $d_{t,n}(x)=\sum_{i=1}^t x_{2i-1} x_{2i}$.
-
+	For an even integer $n\geq 0$ and any integer $t\in[0,n/2]$, we define the Boolean function $d_{t,n}\in\BN$ by $d_{t,n}(x)=\sum_{i=1}^t x_{2i-1} x_{2i}$.
 	%	by $\Dnka{n}{k}{a}$:
@@
 
-In particular, $d_{\frac{n}{2},n}(x)=d_n(x)$. 
+In particular, it holds that $d_{n/2,n}(x)=d_n(x)$. 
 %We focus on the Walsh spectrum restricted to the slices of any function $d_{t,n}$:
-We focus on the restricted Walsh spectrum of any function $d_{t,n}$:
+We now focus on the restricted Walsh transform of $d_{t,n}$:
 
 \begin{proposition}\label{proposition:dtn}
-	Let $t, n\in \N$ with $n$ even and $t\leq n/2$, the following holds on $d_{t,n}$ for all $k\in [0,n]$:
-	\[\wtk{d_{t,n}}{k}(a)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t},\]
-	where $b$ denotes the first $2t$ elements of $a$ and $c$ the last $n-2t$ elements.
+    Let $n\geq 0$ be an even integer, and let $t\in[0,n/2]$.
+Let $a\in\F_2^n$ be a binary vector, and write $a=(b,c)$ with $b\in\F_2^{2t}$ and $c\in\F_2^{n-2t}$.
+Then the following holds for all $k\in [0,n]$:
+	\[\wtk{d_{t,n}}{k}(a)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b}\cdot\kraw{k-\ell}{\w(c)}{n-2t}.\]
 \end{proposition}
 \begin{proof}
-	We rewrite the restricted Walsh transform, denoting $x\in \F_2^n$ by $(y,z)$ where $y\in \F_2^{2t}$ and $z \in \F_2^{n-2t}$, and similarly denoting $a$ by $(b,c)$:
+    By considering binary vectors $x\in\F_2^n$ as $x=(y,z)$ with $y\in\F_2^{2t}$ and $z\in\F_2^{n-2t}$, we get:
 
@@
 %	\end{align*}	
-
 	\begin{align*}
-\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
-&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,2t}(y)+b \cdot y} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c \cdot z}\right)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
+\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}\\&=\sum_{(y,z)\in\Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
+&=\sum_{\ell=0}^{2t}\left(\sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{2t}(y)+b \cdot y}\right)\left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c \cdot z}\right)\\&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b}\cdot\kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
 \end{align*}
@@
 \begin{definition}\label{defi:P_a_t}
-    Let $t, n\in \N$ with $n$ even and $t\leq n/2$.
-Given $a=(b,c)\in\F_2^n$ with $b\in\F_2^{2t}$, denote $n-2t-\w(c)$ and $\w(c)$ by $u$ and $v$, respectively.
-We  then introduce the following polynomial:
+    Let $n\geq 0$ be an even integer, and let $t\in[0,n/2]$.
+Let $a=(b,c)\in\F_2^n$ be a binary vector with $b\in\F_2^{2t}$ and $c\in\F_2^{n-2t}$.
+By letting $u=u_t(a)=n-2t-\w(c)$ and $v=v_t(a)=\w(c)$, we introduce the polynomial $P_{a,t}(z)$ given by the following expression:
     \[
@@
 \begin{proposition}
-    Let $t, n\in \N$ with $n$ even and $t\leq n/2$. Let $a\in\F_2^n$. The following holds true: 
+    For every even integer $n\geq 0$, every integer $t\in[0,n/2]$ and every binary vector $a\in\F_2^n$, the following holds:
     \[
@@
 
-With this, we prove a generalization of Theorem~\ref{theorem:bound_D_nka} below. Before that, we still require a preliminary result:
+With this, we prove a generalization of Theorem~\ref{theorem:bound_D_nka} below. Before that, we still require a technical preliminary result:
 
 \begin{lemma}\label{lemma:maximizing_args}
-    Let $N$ be a non-negative number and $D\subseteq\C$ a set of complex numbers.
-For every integer $1\leq i\leq N$, consider a non-negative integer $m_i$ as well as complex functions $f_{i,1},\dots,f_{i,k_i}$ defined on the set $D$.
+    Let $N\geq 1$ be an integer and $D\subseteq\C$ a set of complex numbers.
+For every $i\in[1,N]$, consider an integer $m_i\geq 0$ as well as complex functions $f_{i,1},\dots,f_{i,k_i}$ defined on the set $D$.
 Assume that the following maximum exists (which holds for instance if the functions $f_{i,j}$ are continuous and $D$ is topologically compact):
     \[
-        M=\max_{\substack{\forall 1\leq i\leq N:\,p_{i,1}+\cdots+p_{i,k_i}=m_i\\z\in D}}\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|.
-    \]
-    Then there exist integers $j_1,\dots,j_N$ with $1\leq j_i\leq k_i$ such that the following holds:
+        M=\max_{\substack{\forall i\in[1,N]:\,p_{i,1}+\cdots+p_{i,k_i}=m_i\\z\in D}}\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|.
+    \]
+    Then there exist integers $j_1,\dots,j_N$ with $j_i\in[1,k_i]$ such that the following holds:
     \[
@@
 \begin{proof}
-    Let us choose the integers $p_{i,j}$ and the complex number $z\in D$ to maximize the quantity $\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|$.
-Note that this in particular means that $\sum_{j=1}^{k_i}p_{i,j}=m_i$ for every $1\leq i\leq N$.
-Next, for every $1\leq i\leq N$, choose $1\leq j_i\leq k_i$ such that $|f_{i,j_i}(z)|\geq|f_{i,j}(z)|$ for every $1\leq j\leq k_i$.
+    Let us choose the integers $p_{i,j}\geq 0$ satisfying $\sum_{j=1}^{k_i}p_{i,j}=m_i$ for every $i\in[1,N]$ together with the complex number $z\in D$ to maximize the quantity $\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|$.
+Next, for every $i\in[1,N]$, choose $j_i\in[1,k_i]$ such that $|f_{i,j_i}(z)|\geq|f_{i,j}(z)|$ for every $j\in[1,k_i]$.
 Then we have:
     \[
-        M=\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|\leq\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j_i}(z)^{p_{i,j}}\right|=\left|\prod_{i=1}^Nf_{i,j_i}(z)^{\sum_{j=1}^{k_i}p_{i,j}}\right|=\left|\prod_{i=1}^Nf_{i,j}(z)^{m_i}\right|\leq M.\qedhere
+        M=\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|\leq\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j_i}(z)^{p_{i,j}}\right|=\left|\prod_{i=1}^Nf_{i,j_i}(z)^{\sum_{j=1}^{k_i}p_{i,j}}\right|=\left|\prod_{i=1}^Nf_{i,j_i}(z)^{m_i}\right|\leq M.\qedhere
     \]
@@
 \begin{theorem}\label{theorem:bound_D_nka_generalized}
-    Let $t, n\in \N$ with $n$ even and $t\leq n/2$. 
-    We define $\lambda=t/n\in\left[0,\frac 12\right]$, as well as:
-    \[
-        \mu(\lambda)=\mu=
+    Let $n\geq 0$ be an even integer, and let $t\in[0,n/2]$. We define $\lambda=t/n$, as well as:
+    \[
+        \mu=\mu(\lambda)=
         \begin{cases}
@@
     \]
-
-    Then, for all $a\in\F_2^n$ and $k\in[0,n]$, the following hold true:
-
-    \[
-        |\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n},\quad \text{and} \quad  |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}.
+    Then, for all $a\in\F_2^n$ and all $k\in[0,n]$, the following hold true:
+
+    \[
+        |\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n}\quad \text{and} \quad  |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}.
     \]
@@
     To begin, we observe that the inequality $|\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}$ will follow from the inequality $|\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n}$ using precisely the arguments of the proof of Corollary~\ref{cor:bound_walsh_cauchy}, so that we are only required to prove the first inequality.
-Also, since the case $\lambda=\frac 12$ corresponds to Theorem~\ref{theorem:bound_D_nka}, we will henceforth assume $\lambda<\frac 12$.
-
-    As before (in the proof of Theorem~\ref{theorem:bound_D_nka}), we want to bound the maximum of $|P_{a,t}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[1,n]$.
-    We write $a=(b,c)$ with $b\in\F_2^{2t}$ and define $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}.    
+Also, since the case $\lambda=1/2$ corresponds to Theorem~\ref{theorem:bound_D_nka}, we will henceforth assume $\lambda<1/2$.
+
+    As before (in the proof of Theorem~\ref{theorem:bound_D_nka}), we want to bound the maximum of $|P_{a,t}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[0,n]$.
+    We write $a=(b,c)$ with $b\in\F_2^{2t}$ and $c\in\F_2^{n-2t}$, and define $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}.    
    To find a bound for $|P_{a,t}(z)|$ on $\dis$ that applies to all $a\in\F_2^n$, we would like to bound the quantity $\max_{a\in\F_2^n,z\in\dis}|P_{a,t}(z)|$.
@@
     \end{gather*}
-    Since swapping both $(p,q)$ and $(u,v)$ has the same effect as replacing $z$ by $-z$ in $P_{a,t}(z)$ and therefore does not change the maximum of $|P_{a,t}(z)|$ on $\dis$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
+    Since replacing $(p,q)$ and $(u,v)$ by $(q,p)$ and $(v,u)$ has the same effect as replacing $z$ by $-z$ in $P_{a,t}(z)$ and therefore does not change the maximum of $|P_{a,t}(z)|$ on $\dis$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
     \[
@@
 
-    The goal will be to prove that the maximum of $g_\lambda(\alpha)=g(\alpha)=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{a,t}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$.
-Since $g$ is an even function, it is enough to focus on the interval $\alpha\in[0,\pi]$; the function $g$ is represented for several different values of $0\leq\lambda<\frac 12$ in Figure~\ref{fig:family_curves_g}.
+    The goal will be to prove that the maximum of $g^{(\lambda)}(\alpha)=g(\alpha)=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{a,t}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$.
+Since $g$ is an even function, it is enough to focus on the interval $\alpha\in[0,\pi]$; the function $g$ is represented for several different values of $0\leq\lambda<1/2$ in Figure~\ref{fig:family_curves_g}.
 
@@
     	\includegraphics[width=11cm]{family_curves_g.pdf}
-    	\caption{The curves of $\alpha\mapsto g_\lambda(\alpha)$ for the values $\lambda=\frac{i}{25}$ from $i=0$ (blue) to $i=24$ (red).}
+        \vspace{-4mm}
+    	\caption{The curves of $\alpha\mapsto g^{(\lambda)}(\alpha)$ for the values $\lambda=\frac{i}{50}$ from $i=0$ (red) to $i=24$ (blue).}
     	\label{fig:family_curves_g}
@@
     The only interesting zeros of $\frac{\dd}{\dd\alpha}g(\alpha)$ are those of the last factor 
-    $\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2$: those of the factor $8(6-2\cos(2\alpha))^{\lambda-1}(2+2\cos\alpha)^{-2\lambda}$ will make $g(\alpha)$ vanish and will therefore not maximize $g(\alpha)$, and those for $\sin\alpha$ are $\alpha=0$ and $\alpha=\pi$, with corresponding values $g(0)=2^{2-2\lambda}$ and $g(\pi)=0$.
-
-    Our first claim is that the equation $\mathcal E:\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2=0$ has a unique solution $\cos\alpha=-\lambda+\sqrt{\lambda^2-4\lambda+2}$ if $\lambda\geq\frac 16$ and has no solution $\cos\alpha$ otherwise.
+    $\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2$: those of the factor $8g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}$ will make $g(\alpha)$ vanish and will therefore not maximize $g(\alpha)$, and those for $\sin\alpha$ are $\alpha=0$ and $\alpha=\pi$, with corresponding values $g(0)=2^{2-2\lambda}$ and $g(\pi)=0$.
+
+    Our first claim is that the equation $\mathcal E:\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2=0$ has a unique solution $\cos\alpha=-\lambda+\sqrt{\lambda^2-4\lambda+2}$ if $\lambda\geq 1/6$ and has no solution $\cos\alpha$ otherwise.
 To see this, we consider $\mathcal E$ as an equation of second degree in $\cos\alpha$, which leads to the two solution candidates $\cos\alpha=-\lambda\pm\sqrt{\lambda^2-4\lambda+2}$.
 
-    We can exclude the solution $\cos\alpha=-\lambda-\sqrt{\lambda^2-4\lambda+2}$ since $\cos\alpha\in[-1,1]$ (and $\lambda\in [0,1/2[$). 
-    The other solution needs to be excluded for the same reason if $\lambda<\frac 16$.
-
-    Our next claim is that $\frac{\dd^2}{\dd^2\alpha}g(\alpha)\vert_{\alpha=0}$ has the same sign as $6\lambda -1$. To see why, we apply the definition of the second derivative:
+    We can exclude the solution $\cos\alpha=-\lambda-\sqrt{\lambda^2-4\lambda+2}$ since $\cos\alpha\in[-1,1]$ (and $\lambda\in [0,1/2)$). 
+    The other solution needs to be excluded for the same reason if $\lambda<1/6$.
+
+    Our second claim is that $\frac{\dd^2}{\dd^2\alpha}g(\alpha)\vert_{\alpha=0}$ has the same sign as $6\lambda -1$. To see why, we apply the definition of the second derivative:
     \begin{align*}
@@
 
-    Therefore, in case $\lambda<\frac 16$, we can conclude from the two claims that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and this maximum is then equal to $2^{2-2\lambda}=2^{2\mu}$, as required.
-For $\lambda=\frac 16$, the solution to the equation $\mathcal E$ is $\cos\alpha=1$, again implying that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and we obtain the same maximum of $2^{2\mu}$.
-In case $\lambda>\frac 16$, the two claims imply that $g(\alpha)$ reaches its maximum at the unique $\alpha_0\in[0,\pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$.
+    Therefore, in case $\lambda<1/6$, we can conclude from the two claims that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and this maximum is then equal to $2^{2-2\lambda}=2^{2\mu}$, as required.
+For $\lambda=1/6$, the solution to the equation $\mathcal E$ is $\cos\alpha=1$, again implying that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and we obtain the same maximum of $2^{2\mu}$.
+In case $\lambda>1/6$, the two claims imply that $g(\alpha)$ reaches its maximum at the unique $\alpha_0\in[0,\pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$.
 For this $\alpha_0$, the double angle formula for the cosine implies that $\cos(2\alpha_0)=4\lambda^2-8\lambda+3-4\lambda\sqrt{\lambda^2-4\lambda+2}$.
@@
     %This is exactly what we wanted to prove, 
-    This is equivalent to the first equation in the theorem statement, 
-    and we have therefore covered the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$ entirely.
+    With this, we have covered the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$ entirely.
 In a similar fashion, it can be proven that $|P_{a,t}(z)|$ is also bounded by $2^{\mu n}$ on $\dis$ for the remaining two cases of $(p,q,r;u,v)$.
-In fact, for $(p,q,r;u,v)=(0,t,0;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h_1(\alpha)=(6-2\cos(2\alpha))^\lambda(2-2\cos\alpha)^{1-2\lambda}$, which has the same maximum as $g(\alpha)$ because $h_1\left(\frac{\pi}{2}+\alpha\right)=g\left(\frac{\pi}{2}-\alpha\right)$; for $(p,q,r;u,v)=(0,0,t;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h_2(\alpha)=(2+2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$, whose maximum is bounded by the maximum of $g(\alpha)$ because $h_2(\alpha)\leq g(\alpha)$.
+In fact, for $(p,q,r;u,v)=(0,t,0;n-2t,0)$, one can proceed in exactly the same way, and for $(p,q,r;u,v)=(0,0,t;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h(\alpha)=(2+2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$, whose maximum is bounded by the maximum of $g(\alpha)$ because $0\leq h(\alpha)\leq g(\alpha)$.
 \end{proof}
@@
 	\includegraphics[width=10cm]{curve_exponents_lambda_mu.pdf}
+    \vspace{-5mm}
 	\caption{The curve of $\lambda\mapsto\mu(\lambda)$ with $0\leq\lambda\leq\frac 12$ from Theorem~\ref{theorem:bound_D_nka_generalized}.}
@@
 
-In this section, we establish a tighter bound on the absolute value of the Walsh transform of the revisited \hwbf{} for values of $n$ up to $80$. 
-We then compare the nonlinearity of this function to that of other functions suited to similar use cases, such as the \hwbf{} of weightwise cyclic functions from~\cite{DAM:MeaOza24}.
+\tsnote{@Pierrick, this entire section needs updating because of Proposition 3.}
+
+In this section, we establish a tighter bound on the absolute value of the Walsh transform of the revisited \hwbf{} for even $n\in[1,80]$. 
+We then compare the nonlinearity of this function to that of other functions suited to similar use cases, such as the \hwbf{} or weightwise cyclic functions from~\cite{DAM:MeaOza24}.
 
@@
 
-Following Corollary~\ref{cor:bound_walsh_cauchy} we deduce that $|\wt f(a)|\leq 1+n\cdot 2^{3n/4}$ for every Boolean vector $a\in\F_2^n$.
+Following Corollary~\ref{cor:bound_walsh_cauchy}, we deduce that $|\wt f(a)|\leq 1+n\cdot 2^{3n/4}$ for every even integer $n\geq 0$ and every Boolean vector $a\in\F_2^n$, where $f\in\BN$ denotes the revisited \hwbf{}.
 This is a pessimistic bound.
@@
 For this, consider a vector $b\in\mathbb F_2^n$; we write $(p,q,r)=(p(b),q(b),r(b))$.
-Also, for $1\leq k\leq n$, let $b_k=b+\pi(e_k)$ and $(p_k,q_k,r_k)=(p(b_k),q(b_k),r(b_k))$.
-Observe that for every $1\leq k\leq n$, we have $(p_k,q_k,r_k)\in\{(p\pm1,q,r\mp 1),(p,q\pm 1,r\mp 1)\}$.
-Furthermore, observe that if $k\leq n/2$ and $(p_k,q_k,r_k)=(p+\alpha,q+\beta,r+\gamma)$ for $\{\alpha,\beta,\gamma\}=\{0,\pm 1\}$ with $\gamma\neq 0$, then we have $(p_{k+n/2},q_{k+n/2},r_{k+n/2})=(p+\alpha',q+\beta',r+\gamma')$ for some $\{\alpha',\beta',\gamma'\}=\{0,\pm 1\}$ with $\gamma'\neq 0$ which only depend on $\alpha$, $\beta$ and $\gamma$.
+Also, for $k\in[1,n]$, let $b_k=b+\pi(e_k)$ and $(p_k,q_k,r_k)=(p(b_k),q(b_k),r(b_k))$.
+Observe that for every $k\in[1,n]$, we have $(p_k,q_k,r_k)\in\{(p\pm1,q,r\mp 1),(p,q\pm 1,r\mp 1)\}$.
+Furthermore, observe that if $k\in[0,n/2]$ and $(p_k,q_k,r_k)=(p+\alpha,q+\beta,r+\gamma)$ for $\{\alpha,\beta,\gamma\}=\{0,\pm 1\}$ with $\gamma\neq 0$, then we have $(p_{k+n/2},q_{k+n/2},r_{k+n/2})=(p+\alpha',q+\beta',r+\gamma')$ for some $\{\alpha',\beta',\gamma'\}=\{0,\pm 1\}$ with $\gamma'\neq 0$ which only depend on $\alpha$, $\beta$ and $\gamma$.
 Explicitly, we have $(\alpha',\beta',\gamma')=(\alpha,\beta,\gamma)$ if $\gamma=1$ and $(\alpha',\beta',\gamma')=(\beta,\alpha,\gamma)$ if $\gamma=-1$.
@@
 
-\begin{table}[h]
+\begin{table}
 	\centering
@@
 	\hline	
-    	\hwbf{}   & $4$  & $20$  & $88$  &  $372$ & $1544$ & $6344$ & $25904$  \\  	
+    	\hwbf{}   & $4$  & $20$  & $88$  &  $372$ & $1\,544$ & $6\,344$ & $25\,904$  \\  	
    %4 10 20 44 88 186 372 772 1544 3172 6344 12952 25904
-		\hline
-Majority   & $5$  & $22$  & $93$  &  $386$ & $1586$ & $6476$ & $26333$  \\
-\hline
+
+Majority   & $5$  & $22$  & $93$  &  $386$ & $1\,586$ & $6\,476$ & $26\,333$  \\
+
 		%cyclic $f_0=x_1+x_2x_3$
-    	t~\cite{DAM:MeaOza24}   & $4$  & $22$  & $96$  &  $404$ & $1672$ & $6854$ & $27884$\\
+    	$t$~\cite{DAM:MeaOza24}   & $4$  & $22$  & $96$  &  $404$ & $1\,672$ & $6\,854$ & $27\,884$\\
     	%4 10 22 46 96 196 404 816 1672 3358 6854 13722 27884
-\hline	
+
 %$f_0= x_1 + \sum_{i=1}^{n/2-1}x_{2i}x_{2i+1}$	
-    	u~\cite{DAM:MeaOza24}   & $4$  & $24$  & $104$  &  $456$ & $1888$ & $7816$ & $31616$ \\
+    	$u$~\cite{DAM:MeaOza24}   & $4$  & $24$  & $104$  &  $456$ & $1\,888$ & $7\,816$ & $31\,616$ \\
     	%4 10 24 48 104 220 456 924 1888 3862 7816 15748 31616
-\hline
-
-		$f$  & $4$  & $22$  & $102$  &  $458$ & $1902$ & $7842$ & $31680$\\
+
+		Revisited \hwbf{}  & $4$  & $22$  & $102$  &  $458$ & $1\,902$ & $7\,842$ & $31\,680$\\
 \hline
@@
 
-In this part we give the other cryptographic parameters of the function $f$.
-Since its balancedness is characterized by Theorem~\ref{th:bal} and its nonlinearity deeply analyzed in Section~\ref{sec:Cauchy} and Section~\ref{sec:expAndComp}, in the following we focus on the algebraic properties.
-More precisely we analyze the degree, algebraic immunity and fast algebraic immunity of $f$, providing comparisons with other weightwise quadratic functions.
+In this section, we present additional cryptographic parameters for the \hwbf{} $f\in\BN$.
+While Theorem~\ref{th:bal} describes its balancedness and Sections~\ref{sec:Cauchy} and \ref{sec:expAndComp} thoroughly explore its nonlinearity, our focus here will be on its algebraic characteristics.
+Specifically, we will examine the degree, the algebraic immunity, and the fast algebraic immunity of $f$, and offer comparisons with other weightwise quadratic functions.
 
@@
 
-\begin{proposition}[Algebraic degree of $f$]
-	Let $n\in \N$ be even, greater than $4$, and $f$ defined as in Definition~\ref{def:revHWBF}, the following holds: $\degg(f)= n-1$.
+\begin{proposition}
+	Let $n\geq 4$ be even, and let $f\in\BN$ be the revisited \hwbf{}. Then $\degg(f)=n-1$.
 \end{proposition}
 \begin{proof}
-	We write $f$ as $q+h$ where $q$ is the quadratic function $\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}$ and $h$ is the \hwbf{}.
-	Using Property~\ref{prop:wwd1} Item $3$, $h$ has degree $n-1\geq 3$, and the function $q$ has no monomial of degree higher than $2$, therefore $\degg(f)=\degg(h)=n+1$.
-
-\end{proof}
-
-In Table~\ref{table:comparisonsDeg}, we display the algebraic degree of different weightwise quadratic function. We observe that $f$ is the function with higher degree, jointly with the \hwbf{}.
-
-\begin{table}[h]
+	We write $f=q+h$, where $q\in\BN$ is given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}$ and $h\in\BN$ is the \hwbf{}.
+	The function $h$ has degree $n-1\geq 3$ by Property~\ref{prop:wwd1}, and the function $q$ has no monomial of degree higher than $2$, so that $\degg(f)=\degg(h)=n-1$.
+\end{proof}
+
+In Table~\ref{table:comparisonsDeg}, we display the algebraic degree of different weightwise quadratic function.
+We observe that the revisited \hwbf{} is the function with highest degree, together with the \hwbf{}.
+
+\begin{table}
 	\centering
@@
 		\hwbf{}   & $3$  & $5$  & $7$  &  $9$ & $11$ & $13$ & $15$  \\
-		\hline
+
 		Majority   & $4$  & $4$  & $8$  &  $8$ & $8$ & $8$ & $16$  \\
-		\hline
+
 		%cyclic $f_0=x_1+x_2x_3$
-		t~\cite{DAM:MeaOza24}   & $2$  & $5$  & $6$  &  $9$ & $11$ & $13$ & $14$\\
-		\hline	
+		$t$~\cite{DAM:MeaOza24}   & $2$  & $5$  & $6$  &  $9$ & $11$ & $13$ & $14$\\
+
 		%$f_0= x_1 + \sum_{i=1}^{n/2-1}x_{2i}x_{2i+1}$	
-		u~\cite{DAM:MeaOza24}   & $2$  & $4$  & $6$  &  $8$ & $10$ & $12$ & $14$ \\
-		\hline
-
-		$f$  & $3$  & $5$  & $7$  &  $9$ & $11$ & $13$ & $15$\\
+		$u$~\cite{DAM:MeaOza24}   & $2$  & $4$  & $6$  &  $8$ & $10$ & $12$ & $14$ \\
+
+		Revisited \hwbf{}  & $3$  & $5$  & $7$  &  $9$ & $11$ & $13$ & $15$\\
 		\hline
@@
 
-\begin{proposition}[Algebraic immunity of $f$]
-	Let $n\in \N$ be even, $f$ defined (as in Definition~\ref{def:revHWBF}) as
-	$f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k$ and $h$ denote the $n$-variable \hwbf{}, the following holds:
+\begin{proposition}
+    Let $n\geq 4$ be even, let $f\in\BN$ be the revisited \hwbf{}, and let $h\in\BN$ be the \hwbf{}. Then the following holds:
 	\[\AI(f)\geq \AI(h)-2.\]
 \end{proposition}
-\begin{proof}
-	Let denote by $q$ the quadratic function $\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}$, it allows to write $h=f+q$. 
-	Let $g\neq 0$ be an annihilator of $f+ \varepsilon$ of minimum degree (where $\varepsilon \in \{0,1\}$), then the following holds:
-	\[g (1+q) (h+\varepsilon) = g(1+q) (f+\varepsilon + q)=0, \]
-	hence $g (1+q)$ is an annihilator of $h+ \varepsilon$. 
-	If $g (1+q)\ne 0$ then $\degg(g(1+q)) \leq \degg(g)+2$ and we obtain $\degg(g)\geq \AI(h) -2$. 
-	Otherwise, $g (1+q)= 0$ implies that $g$ annihilates $1+q$ and therefore $0=g (f+\varepsilon + 1 +q)=g(h+ \varepsilon +1)$ that is $\degg(g)\geq \AI(h)$. 
-	Summarizing, for any non null annihilator $g$ of $f$ or $f+1$ we get $\degg(g)\geq \AI(h)-2$, it allows to conclude $\AI(f)\geq \AI(h)-2$.
-\end{proof}
-
-From~\cite{DAM:WCST14} Theorem 4, the algebraic immunity of the \hwbf{} is at least $\lfloor n/3\rfloor +1$, which leads to $\lfloor n/3\rfloor -1$ for $f$. 
+
+\begin{proof}
+	Denote by $q\in\BN$ the quadratic function given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$, allowing to write $h=f+q$.
+    Let $g\in\BN^*$ with $\degg(g)=\AI(f)$ be an annihilator of $f+ \varepsilon$ for some $\varepsilon\in\{0,1\}$. Then the following holds:
+	\[g\cdot(q+1) \cdot(h+\varepsilon) = g\cdot(q+1)\cdot(f+q+\varepsilon)=g\cdot(q+1)\cdot(f+\epsilon)+g\cdot(q+1)\cdot q=0+0=0.\]
+	Hence $g\cdot(q+1)$ is an annihilator of $h+ \varepsilon$. 
+	If $g\cdot(q+1)\ne 0$, it follows that $\AI(h)\leq\degg(g\cdot(q+1))\leq\degg(g)+\degg(q+1)$, and therefore that $\AI(f)=\degg(g)\geq\AI(h)-\degg(q+1)=\AI(h)-2$.
+If $g\cdot(q+1)=0$, then $0=g\cdot(f+\epsilon+q+1)=g\cdot(h+\epsilon+1)$, showing that $\AI(f)=\degg(g)\geq\AI(h)$.
+\end{proof}
+
+From Theorem 4 in~\cite{DAM:WCST14}, the algebraic immunity of the \hwbf{} is at least $\lfloor n/3\rfloor +1$, which leads to $\lfloor n/3\rfloor -1$ for the revisited \hwbf{}.
 In Table~\ref{table:comparisonsAI}, we present the algebraic immunity of various weightwise quadratic functions.
-We observe that the function $f$ demonstrates the best performance after the majority function, which is known to achieve optimal algebraic immunity.
+We observe that the revisited \hwbf{} demonstrates the best performance after the majority function; the latter is known to achieve optimal algebraic immunity.
 
@@
 		\hwbf{}   & $2$  & $3$  & $4$  &  $4$ & $5$ & $5$ & $6$  \\  	
-		\hline
 		Majority   & $2$  & $3$  & $4$  &  $5$ & $6$ & $7$ & $8$  \\
-		\hline
 		%cyclic $f_0=x_1+x_2x_3$
-		t~\cite{DAM:MeaOza24}   & $2$  & $3$  & $4$  &  $5$ & $5$ & $6$ & $7$\\
-		\hline	
+		$t$~\cite{DAM:MeaOza24}   & $2$  & $3$  & $4$  &  $5$ & $5$ & $6$ & $7$\\
 		%$f_0= x_1 + \sum_{i=1}^{n/2-1}x_{2i}x_{2i+1}$	
-		u~\cite{DAM:MeaOza24}   & $2$  & $3$  & $4$  &  $5$ & $6$ & $6$ & $7$ \\
-		\hline						
-		$f$  & $2$  & $3$  & $4$  &  $5$ & $6$ & $6$ & $7$\\
+		$u$~\cite{DAM:MeaOza24}   & $2$  & $3$  & $4$  &  $5$ & $6$ & $6$ & $7$ \\					
+		Revisited \hwbf{}   & $2$  & $3$  & $4$  &  $5$ & $6$ & $6$ & $7$\\
 		\hline
@@
 
-Additionally, we considered the fast algebraic immunity of $f$ (see Definition~\ref{def:FAI}).
-In Table~\ref{table:FAI} we give the best couples $(d,e)$ encountered for the function $f$, where $fg=h$, $\degg(g)=d, \degg(h)=e$.
-
+Lastly, we considered the fast algebraic immunity of the revisited \hwbf{} $f$.
+In Table~\ref{table:FAI}, we give the best couples $(d,e)$ encountered for the function $f$, where $\degg(g)=d$ and $\degg(h)=e$ for functions $g$ and $h$ satisfying $fg=h$.
+
+\bigskip
 These various results on the algebraic properties of $f$ suggest that it possesses strong resistance against standard attacks.
-Additionally, its high nonlinearity makes it a well-suited candidate for use as a filter function in contexts such as filtered LFSRs or in homomorphically-friendly schemes like FLIP and FiLIP.
-
-\begin{table}[h]
+Furthermore, its high nonlinearity makes it a well-suited candidate for use as a filter function in contexts such as filtered \textsf{LFSR}s or in homomorphically-friendly schemes like \textsf{FLIP} and \textsf{FiLIP}.
+
+\begin{table}
 	\centering
@@
 \section{Conclusion and open questions}
-\pmnote{add a small conclusion (summary of contributions), and elaborate on an opean question, for example on how the Cauchy estimate could be used for more families, other quadratic functions or more easily higher degree ones.}
+
+In this work, we introduced the revisited Hidden Weight Bit Function (\hwbf{}), a weightwise quadratic Boolean function with improved cryptographic properties over existing constructions.
+We analyzed its balancedness, and using generating functions in combination with complex analysis, we derived new lower bounds on its nonlinearity, demonstrating that the revisited \hwbf{} achieves superior nonlinearity compared to other functions with similar computational costs.
+We further examined other cryptographic parameters such as degree, algebraic immunity, and fast algebraic immunity, confirming that the revisited \hwbf{} matches or outperforms comparable functions in these aspects.
+
+Our approach makes use of generating functions and Cauchy’s estimate to bound the maximum absolute Walsh spectrum of weightwise quadratic functions.
+This naturally leads to the following question: do the employed techniques, particularly the use of Cauchy’s estimate, extend to different families of Boolean functions?
+Exploring this could potentially lead to the discovery of new functions with even better cryptographic properties.
 
@@
 \section{Acknowledgments}
-Pierrick Méaux was supported by the ERC Advanced Grant no. 787390.
+Pierrick Méaux was funded by the European Research Council (\textsf{ERC}) under the Advanced Grant program (reference number: 787390).
+Tim Seuré acknowledges the support of the Luxembourgish “Fonds National de la Recherche” (\textsf{FNR}) through an Individual Grant (reference number: 17936291).
 \fi

### 2024-11-28 RevisedHiddenWeight.tex
Some more typos

@@
 
-In this section, we present additional cryptographic parameters for the \hwbf{} $f\in\BN$.
+In this section, we present additional cryptographic parameters for the revisited \hwbf{} $f\in\BN$.
 While Theorem~\ref{th:bal} describes its balancedness and Sections~\ref{sec:Cauchy} and \ref{sec:expAndComp} thoroughly explore its nonlinearity, our focus here will be on its algebraic characteristics.
@@
 
-Lastly, we considered the fast algebraic immunity of the revisited \hwbf{} $f$.
+\bigskip
+Lastly, we also considered the fast algebraic immunity of the revisited \hwbf{} $f$.
 In Table~\ref{table:FAI}, we give the best couples $(d,e)$ encountered for the function $f$, where $\degg(g)=d$ and $\degg(h)=e$ for functions $g$ and $h$ satisfying $fg=h$.
@@
 	\end{tabular}
-	\tablecaption{Lowest possible values of $(d, e)$ for different values of $n$.}
+	\tablecaption{Lowest possible values of $(d, e)$ for different values of $n$.\tsnote{Aren't the roles of $d$ and $e$ reversed?}}
 	\label{table:FAI}

### 2024-11-28 RevisedHiddenWeight.tex
More typos (sorry)
propr 3 under repair

@@
 		$a$ & $(0,0)$ & $(0,1)$ & $(1,1)$ \\ \hline
-		$\Dnka{2}{0}{a}$ &$1$&$1$ & $1$\\ \hline
-		$\Dnka{2}{1}{a}$ &$2$& $0$ & $-2$\\ \hline
-		$\Dnka{2}{2}{a}$ &$-1$&$1$ & $-1$\\ \hline
+		$\Dnka{2}{0}{a}$ &$1$&$1$ & $1$\\
+		$\Dnka{2}{1}{a}$ &$2$& $0$ & $-2$\\
+		$\Dnka{2}{2}{a}$ &$-1$&$1$ & $-1$\\
 	\end{tabular}
@@
 \tsnote{@Pierrick, check the below proposition with its proof.}
+
+\pmnote{Part under repair}
+
 \begin{proposition}\label{prop:WT}
@@
 Denote by $\pi:[1,n]\to[1,n]$ the permutation sending the first $n/2$ elements to the odd positions and the $n/2$ last ones to the even positions.
-Let $a\in\F_2^n$ be a binary vector, and let $b=\pi(a)+(0,1,0,1,\ldots,0,1)$.
+Let $a\in\F_2^n$ be a binary vector, and let $b=\pi^{-1}(a)+(0,1,0,1,\ldots,0,1)$.
 Then the following holds true:
@@
 We have by Proposition~\ref{prop:restrWT} that:
-\[
-\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x}=\Dnka{n}{k}{d},\]
-where $d$ is the permutation of $c$ obtained by sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions.
-
-Calling $\pi$ this permutation, since $c=a+e_k+\sum_{i=n/2+1}^n e_i$, we can write $d=\pi(c)=\pi(a)+ \pi(e_k)+ (0,1,0,1,\ldots,0,1)$. 
-Accordingly, if $k\leq n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2+1$, with one couple of consecutive elements (the first one with an odd index) being $(1,1)$ and all the others $(0,1)$.
-Otherwise,  when $k> n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2-1$, with one couple of consecutive elements (the first one with an odd index) being $(0,0)$ and all the others $(0,1)$.
-
-Denoting by $b$ the vector $\pi(a)+(0,1,0,1,\ldots,0,1)$, we can write the Walsh transform of $f$ in $a$ as:
+%\[
+%\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x}=\Dnka{n}{k}{d},\]
+%where $d$ is the permutation of $c$ obtained by sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions.
+
+\begin{align*}
+\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ x_k +a \cdot x + \sum_{i=1}^{n/2} x_{n/2+i}}\\
+&= \sum_{\pi(x) \in \Ekn{k}{n}} (-1)^{f(\pi(x))+a \cdot \pi(x)} =\sum_{\pi(x) \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_{\pi(i)} x_{\pi(i+\frac{n}{2})}+ x_{\pi(k)}+a \cdot \pi(x) + \sum_{i=1}^{n/2} x_{\pi(n/2+i)}}
+\end{align*}
+where $\pi$ is a permutation of $[1,n]$. 
+We consider the permutation $\pi$ mapping the first half of $[1,n]$ to the odd positions and the second half to the even positions:
+\[\pi(i)= \left\{ 
+\begin{array}{l l}
+2i-1 & \quad \text{ if } i\in [1,\frac{n}{2}], \\
+2(i-\frac{n}{2}) & \quad \text{ if } i\in [\frac{n}{2}+1,n].
+\end{array} \right. \] 
+Regarding the restricted Walsh transform of $f$ it gives:
+\begin{align*}
+\wtk{f}{k}(a)&=\sum_{x\in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_{2i-1} x_{2i}+ x_{\pi(k)} + \pi^{-1}(a) \cdot x + \sum_{i=1}^{n/2} x_{2i}}\\
+&= \Dnka{n}{k}{d},
+\end{align*}
+where $d= \pi^{-1}(a) + e_{\pi(k)} +\sum_{i=1}^{n/2} e_{2i}$.
+
+%=\Dnka{n}{k}{d},\]
+%where $d$ is the permutation of $c$ obtained by sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions.
+
+%Calling $\pi$ this permutation, since $c=a+e_k+\sum_{i=n/2+1}^n e_i$, we can write $d=\pi(c)=\pi(a)+ \pi(e_k)+ (0,1,0,1,\ldots,0,1)$. 
+%Accordingly, if $k\leq n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2+1$, with one couple of consecutive elements (the first one with an odd index) being $(1,1)$ and all the others $(0,1)$.
+%Otherwise,  when $k> n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2-1$, with one couple of consecutive elements (the first one with an odd index) being $(0,0)$ and all the others $(0,1)$.
+
+Denoting by $b$ the vector $\pi^{-1}(a)+(0,1,0,1,\ldots,0,1)$, we can write the Walsh transform of $f$ in $a$ as:
 \[ \wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}.\qedhere\]
@@
 We use the expression of the Walsh transform of $f$ from Proposition~\ref{prop:WT}:
+\begin{align*}
+\wt{f}(0_n)&=1+\sum_{k=1}^n\Dnka{n}{k}{\pi^{-1}(0_n)+(0,1,0,1,\ldots,0,1)+\pi(e_k)}\\
+&=1+\sum_{k=1}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}
+\end{align*}
+
 %In particular, for $a=0_n$ we can study the balancedness of $f$:
@@
 %\end{align*}
-\[\wt{f}(0_n)=\sum_{k=0}^n\Dnka{n}{k}{(0,1,0,1,\ldots,0,1)+\pi(e_k)}=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}\]
+%\[\wt{f}(0_n)=\sum_{k=0}^n\Dnka{n}{k}{(0,1,0,1,\ldots,0,1)+\pi(e_k)}=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}\]
 Using the recursive relation from Proposition~\ref{prop:recursiveDnka} we obtain:
@@
 &=\binom{n/2-1}{k/2} \Dnka{2}{0}{(0,0)}+ \binom{n/2-1}{(k-1)/2} \Dnka{2}{1}{(0,0)}+ \binom{n/2-1}{k/2-1} \Dnka{2}{2}{(0,0)}\\
-&=\binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1}\\
+&=\binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1}.\\
 \end{align*}
-
 %We can study the balancedness of $f$ using the $\Dnka{n}{k}{a}$ values.
@@
 %\end{align*}
+\iffalse
 \begin{align*}
@@
 \end{align*}
+\fi
+\begin{align*}
+\wt{f}(0_n)&=1+\sum_{k=1}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}\\
+&=\sum_{k=0}^{\frac{n}{2}} \left(\binom{\frac{n}{2}-1}{\frac{k}{2}} -2 \binom{\frac{n}{2}-1}{\frac{k-1}{2}} - \binom{\frac{n}{2}-1}{\frac{k}{2}-1} \right)+ \sum_{k=\frac{n}{2}+1}^{n}   \left(  \binom{\frac{n}{2}-1}{\frac{k}{2}} +2 \binom{\frac{n}{2}-1}{\frac{k-1}{2}} - \binom{\frac{n}{2}-1}{\frac{k}{2}-1} \right)\\
+&=\sum_{k=0}^{n}\left( \binom{\frac{n}{2}-1}{\frac{k}{2}} - \binom{\frac{n}{2}-1}{\frac{k}{2}-1}\right) 
++ 2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{\frac{n}{2}-1}{\frac{k-1}{2}} - \sum_{k=0}^{\frac{n}{2}} \binom{\frac{n}{2}-1}{\frac{k-1}{2}}\right)\\
+&=2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{\frac{n}{2}-1}{\frac{k-1}{2}} - \sum_{k=0}^{n/2} \binom{\frac{n}{2}-1}{\frac{k-1}{2}}\right)
+=2 \left( \sum_{i=\lceil \frac{n}{4} \rceil}^{\frac{n}{2}-1} \binom {\frac{n}{2}-1}{i} - \sum_{i=0}^{\lfloor\frac{n-2}{4}\rfloor} \binom{\frac{n}{2}-1}{i}\right).\\
+\end{align*}
+
 Then, depending on the parity of $\frac{n}{2}$ we obtain the value of $\wt{f}(0_n)$ (using that $\binom{n}{k}=\binom{n}{n-k}$):

### 2024-11-28 RevisedHiddenWeight.tex
minor+answer comments

@@
 \end{align*}
-where $\pi$ is a permutation of $[1,n]$. 
-We consider the permutation $\pi$ mapping the first half of $[1,n]$ to the odd positions and the second half to the even positions:
+where $\pi$ can be any permutation over $[1,n]$. 
+In particular, we consider the permutation $\pi$ mapping the first half of $[1,n]$ to the odd positions and the second half to the even positions:
 \[\pi(i)= \left\{ 
@@
 \tsnote{@Pierrick, check entire section.}
+
+\pmnote{Under revision}
 
@@
 For this, we refer to the corresponding \textsf{SageMath} implementation from \cite{githubseure24}.\tsnote{@Pierrick, OK like this?}
+
+    \pmnote{I think it works for the eprint (use the "ifnum\anon=" to be sure we do not forget it in an anonymous submission.
+
+    I do not know if this will create a reference in your google scholar later one.
+Personally I would prevent that by just giving the link in the text, to avoid to have a reference that will have only 1 citation.
+
+    	)}
+
 \end{proof}
@@
 
+\pmnote{ degree of $h$, denoted by $e$ here is always greater than the AI, whereas $\degg(g)=d$ is smaller. It is consistent}
+
 \section{Conclusion and open questions}

### 2024-12-05 RevisedHiddenWeight.tex
Checked Prop. 3 and Theorem 1

--- 2024-11-28 RevisedHiddenWeight.tex
@@
 %We summarize the known results on the cryptographic criteria of weightwise affine functions we will use in this article in the following property.
-
-\iffalse
-\begin{Prop}[Nonlinearity of some functions from $\WD{1}{n}$, \cite{DCC:DalMaiSar06,DAM:WCST14,DAM:MeaOza24}\label{prop:wwd1}]
-Let $n\in \N^*$ even, the following hold for functions in $\WD{2}{n}$. 
-\begin{itemize}
-    \item The majority function $f\in\WD{2}{n}$ introduced in Definition~\ref{def:maj} satisfies:
-    \[
-        \NL(f)=2^{n-1}-\binom{n-1}{\frac n2}.
-    \]
-    \item The \hwbf{} $f\in\WD{2}{n}$ introduced in Definition~\ref{def:hwbf} satisfies:
-    \[
-        \NL(f)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}.
-    \]
-	\item  bound for the cyclic weightwise linear (adapt Theorem 1 of \cite{DAM:MeaOza24})
-	\item  bound for the cyclic weightwise quadratic function $t$  (adapt Theorem 2 of \cite{DAM:MeaOza24})
-\end{itemize}
-\end{Prop}
-\fi
-
-%\begin{Prop}[Nonlinearity of some functions from $\WD{1}{n}$\label{prop:wwd1}]
-%Let $n\in \N^*$ even, the following hold for the following functions in $\WD{1}{n}$: 
-%\begin{itemize}
-%	\item (\eg{} ~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\textsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
-%	\[
-%	\NL(\textsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}.
-%	\]
-%	\item (\cite{DAM:WCST14}, Theorem $3$) The HWBF $h$ introduced in Definition~\ref{def:hwbf} satisfies:
-%	\[
-%	\NL(h)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}.
-%	\]	
-%\end{itemize}
-%\end{Prop}
 
@@
 		$a$ & $(0,0)$ & $(0,1)$ & $(1,1)$ \\ \hline
-		$\Dnka{2}{0}{a}$ &$1$&$1$ & $1$\\ \hline
-		$\Dnka{2}{1}{a}$ &$2$& $0$ & $-2$\\ \hline
+		$\Dnka{2}{0}{a}$ &$1$&$1$ & $1$\\
+		$\Dnka{2}{1}{a}$ &$2$& $0$ & $-2$\\
 		$\Dnka{2}{2}{a}$ &$-1$&$1$ & $-1$\\ \hline
@@
 
-\tsnote{@Pierrick, check the below proposition with its proof.}
 \begin{proposition}\label{prop:WT}
@@
 \begin{proof}
-We have by Proposition~\ref{prop:restrWT} that:
-\[
-\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x}=\Dnka{n}{k}{d},\]
-where $d$ is the permutation of $c$ obtained by sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions.
-
-Calling $\pi$ this permutation, since $c=a+e_k+\sum_{i=n/2+1}^n e_i$, we can write $d=\pi(c)=\pi(a)+ \pi(e_k)+ (0,1,0,1,\ldots,0,1)$. 
-Accordingly, if $k\leq n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2+1$, with one couple of consecutive elements (the first one with an odd index) being $(1,1)$ and all the others $(0,1)$.
-Otherwise,  when $k> n/2$, the vector $(\pi(e_k)+ (0,1,0,1,\ldots,0,1))$ has weight $n/2-1$, with one couple of consecutive elements (the first one with an odd index) being $(0,0)$ and all the others $(0,1)$.
-
-Denoting by $b$ the vector $\pi(a)+(0,1,0,1,\ldots,0,1)$, we can write the Walsh transform of $f$ in $a$ as:
-\[ \wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}.\qedhere\]
+	For every $k\in[1,n]$, we have by Proposition~\ref{prop:restrWT} that:
+	%\[
+	%\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x}=\Dnka{n}{k}{d},\]
+	%where $d$ is the permutation of $c$ obtained by sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions. 
+	\begin{align*}
+		\wt{f}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+a\cdot x}\\
+		&=\sum_{\pi(x) \in \Ekn{k}{n}} (-1)^{f(\pi(x))+a \cdot \pi(x)}\\
+		&=\sum_{\pi(x) \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_{\pi(i)} x_{\pi(i+n/2)}+ x_{\pi(k)}+a \cdot \pi(x)+ \sum_{i=1}^{n/2} x_{\pi(i+n/2)}}\\
+		&=\sum_{\pi(x) \in \Ekn{k}{n}}(-1)^{d_n(x)+x_{\pi(k)}+\pi^{-1}(a)\cdot x+\sum_{i=1}^{n/2}x_{2i}}\\
+		&=\sum_{x\in \Ekn{k}{n}}(-1)^{d_n(x)+(b+\pi(e_k))\cdot x}\\
+		&=\Dnka{n}{k}{b+\pi(e_k)}.
+	\end{align*}
+	We conclude by applying $\wtk{f}{k}(a)=1+\sum_{k=1}^n\wtk{f}{k}(a)$.
 \end{proof}
@@
 \subsection{Balancedness of $f$}\label{sec:balancedness}
-\tsnote{@Pierrick, check entire section.}
-
-In this part we determine for which values of $n$ the function $f$ is balanced, using the expression of its Walsh transform in terms of $\Dnka{n}{k}{a}$ and the recursive relation of these quantities.
+
+In this part, we determine for which values of $n$ the function $f$ is balanced, using the expression of its Walsh transform in terms of $\Dnka{n}{k}{a}$ and the recursive relation of these quantities.
 
 \begin{theorem}\label{th:bal}
-	Let $n \in \N^*$ even, and $f$ be the $n$-variable function from Definition~\ref{def:revHWBF}, the following holds on its Walsh transform in $0_n$:
-	\[\wt{f}(0_n)= \left \{
-	\begin{array}{l l}
-	0 & \text{ if } n/2 \text{ is even, } \\
-	-2 \binom{n/2-1}{(n-2)/4} & \text{ if }  n/2 \text{ is odd.}
-	\end{array}\right.\]
-
-	Accordingly, $f$ is balanced when $n \equiv 0\mod 4$ and unbalanced when $n\equiv 2 \mod 4$.
-
+	Let $n\geq 2$ be an even integer.
+	Then the Walsh transform of the revisited \hwbf{} $f\in\BN$ at $0_n$ satisfies:
+	\[
+		\wt{f}(0_n)=\left\{\begin{array}{l l}
+			0&\text{ if }n\equiv 0\bmod 4\\
+			-2\binom{(n-2)/2}{(n-2)/4}&\text{ if }n\equiv 2\bmod 4.\\
+		\end{array}\right.
+	\]
+	Accordingly, $f$ is balanced if and only if $n \equiv 0\bmod 4$.
 \end{theorem}
@@
 \begin{proof}
-We use the expression of the Walsh transform of $f$ from Proposition~\ref{prop:WT}:
-%In particular, for $a=0_n$ we can study the balancedness of $f$:
-%\begin{align*}
-%\wt{f}(0_n)&=\sum_{k=0}^n\Dnka{n}{k}{(0,1,0,1,\ldots,0,1)+\pi(e_k)}\\
-%&=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}
-%\end{align*}
-\[\wt{f}(0_n)=\sum_{k=0}^n\Dnka{n}{k}{(0,1,0,1,\ldots,0,1)+\pi(e_k)}=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}\]
-Using the recursive relation from Proposition~\ref{prop:recursiveDnka} we obtain:
+	Applying Remark~\ref{rmk:dependence_dnka} and that $\pi^{-1}(0_n)=0_n$,
+	Proposition~\ref{prop:WT} gives:
 	\begin{align*}
-\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}&= \Dnka{n-2}{k}{(1,1,0,1,\ldots,0,1)} + \Dnka{n-2}{k-2}{(1,1,0,1,\ldots,0,1)} \\
-&=\sum_{i=0}^{n/2-1} \binom{n/2-1}{i} \Dnka{2}{k-2i}{(1,1)}\\
-&=\binom{n/2-1}{k/2} \Dnka{2}{0}{(1,1)}+ \binom{n/2-1}{(k-1)/2} \Dnka{2}{1}{(1,1)}+ \binom{n/2-1}{k/2-1} \Dnka{2}{2}{(1,1)}\\
-&=\binom{n/2-1}{k/2} -2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1}\\
+		\wt{f}(0_n)&=1+\sum_{k=1}^n\Dnka{n}{k}{\pi^{-1}(0_n)+(0,1,0,1,\ldots,0,1)+\pi(e_k)}\\
+		&=1+\sum_{k=1}^{n/2}\Dnka{n}{k}{1,1,0,1,\ldots,0,1}+\sum_{k=n/2+1}^{n}\Dnka{n}{k}{0,0,0,1,\ldots,0,1}.
 	\end{align*}
-Similarly, for $\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}$ we get:
+	Using the recursive relation from Proposition~\ref{prop:recursiveDnka}, we obtain:
+	\[
+		\Dnka{n}{k}{1,1,0,1,\ldots,0,1}=\Dnka{n-2}{k}{1,1,0,1,\ldots,0,1} +\Dnka{n-2}{k-2}{1,1,0,1,\ldots,0,1}.
+	\]
+	By reapplying this $n/2-1$ times, we obtain:
 	\begin{align*}
-\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}
-%&= \Dnka{n-2}{k}{(0,0,0,1,\ldots,0,1)} + \Dnka{n-2}{k-2}{(0,0,0,1,\ldots,0,1)} \\
-&=\sum_{i=0}^{n/2-1} \binom{n/2-1}{i} \Dnka{2}{k-2i}{(0,0)}\\
-&=\binom{n/2-1}{k/2} \Dnka{2}{0}{(0,0)}+ \binom{n/2-1}{(k-1)/2} \Dnka{2}{1}{(0,0)}+ \binom{n/2-1}{k/2-1} \Dnka{2}{2}{(0,0)}\\
-&=\binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1}\\
+		\Dnka{n}{k}{1,1,0,1,\ldots,0,1}&=\sum_{i=0}^{n/2-1} \binom{n/2-1}{i} \Dnka{2}{k-2i}{1,1}\\
+		&=\binom{n/2-1}{k/2} \Dnka{2}{0}{1,1}+ \binom{n/2-1}{(k-1)/2} \Dnka{2}{1}{1,1}\\
+		&\qquad+ \binom{n/2-1}{k/2-1} \Dnka{2}{2}{1,1}\\
+		&=\binom{n/2-1}{k/2}-2\binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}.
 	\end{align*}
-
-%We can study the balancedness of $f$ using the $\Dnka{n}{k}{a}$ values.
-Combining both we obtain:
-%\begin{align*}
-%\wt{f}(0_n)&=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}\\
-%&=\sum_{k=0}^{n/2} \left(\binom{n/2-1}{k/2} -2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1} \right)\\
-%&\qquad+ \sum_{k=\frac{n}{2}+1}^{n}   \left(  \binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2} - \binom{n/2-1}{k/2-1} \right)\\
-%&=\sum_{k=0}^{n}\left( \binom{n/2-1}{k/2} - \binom{n/2-1}{k/2-1}\right) 
-%+ 2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{n/2-1}{(k-1)/2} - \sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right)\\
-%&=2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{n/2-1}{(k-1)/2} - \sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right)\\
-%&=2 \left( \sum_{i=\lceil n/4 \rceil}^{n/2-1} \binom {n/2-1}{i} - \sum_{i=0}^{\lfloor(n-2)/4 \rfloor} \binom{n/2-1}{i}\right).\\
-%\end{align*}
+	Similarly, we get:
+	\[
+		\Dnka{n}{k}{0,0,0,1,\ldots,0,1}=\binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}.\\
+	\]
+	Combining both, we obtain:
 	\begin{align*}
-\wt{f}(0_n)&=\sum_{k=0}^{n/2}\Dnka{n}{k}{(1,1,0,1,\ldots,0,1)}+ \sum_{k=\frac{n}{2}+1}^{n}\Dnka{n}{k}{(0,0,0,1,\ldots,0,1)}\\
-&=\sum_{k=0}^{\frac{n}{2}} \left(\binom{\frac{n}{2}-1}{\frac{k}{2}} -2 \binom{\frac{n}{2}-1}{\frac{k-1}{2}} - \binom{\frac{n}{2}-1}{\frac{k}{2}-1} \right)+ \sum_{k=\frac{n}{2}+1}^{n}   \left(  \binom{\frac{n}{2}-1}{\frac{k}{2}} +2 \binom{\frac{n}{2}-1}{\frac{k-1}{2}} - \binom{\frac{n}{2}-1}{\frac{k}{2}-1} \right)\\
-&=\sum_{k=0}^{n}\left( \binom{\frac{n}{2}-1}{\frac{k}{2}} - \binom{\frac{n}{2}-1}{\frac{k}{2}-1}\right) 
-+ 2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{\frac{n}{2}-1}{\frac{k-1}{2}} - \sum_{k=0}^{\frac{n}{2}} \binom{\frac{n}{2}-1}{\frac{k-1}{2}}\right)\\
-&=2 \left( \sum_{k=\frac{n}{2}+1}^{n} \binom{\frac{n}{2}-1}{\frac{k-1}{2}} - \sum_{k=0}^{n/2} \binom{\frac{n}{2}-1}{\frac{k-1}{2}}\right)
-=2 \left( \sum_{i=\lceil \frac{n}{4} \rceil}^{\frac{n}{2}-1} \binom {\frac{n}{2}-1}{i} - \sum_{i=0}^{\lfloor\frac{n-2}{4}\rfloor} \binom{\frac{n}{2}-1}{i}\right).\\
+		\wt{f}(0_n)&=1+\sum_{k=1}^{n/2}\Dnka{n}{k}{1,1,0,1,\ldots,0,1}+ \sum_{k=n/2+1}^{n}\Dnka{n}{k}{0,0,0,1,\ldots,0,1}\\
+		&=\sum_{k=0}^{n/2} \left(\binom{n/2-1}{k/2} -2 \binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}\right)\\
+		&\qquad+\sum_{k=n/2+1}^{n}\left(\binom{n/2-1}{k/2}+2\binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}\right)\\
+		&=\sum_{k=0}^{n}\left( \binom{n/2-1}{k/2}-\binom{n/2-1}{k/2-1}\right)+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2}\binom{n/2-1}{(k-1)/2}\right)\\
+		&=0+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right)\\
+		&=2\left(\sum_{i=\lceil n/4\rceil}^{n/2-1} \binom {n/2-1}{i} - \sum_{i=0}^{\lfloor(n-2)/4\rfloor} \binom{n/2-1}{i}\right).
 	\end{align*}
-Then, depending on the parity of $\frac{n}{2}$ we obtain the value of $\wt{f}(0_n)$ (using that $\binom{n}{k}=\binom{n}{n-k}$):
-	\[\wt{f}(0_n)= \left \{
-\begin{array}{l l}
-0 & \text{ if } \frac{n}{2} \text{ is even, } \\
--2 \binom{\frac{n}{2}-1}{\frac{n-2}{4}} & \text{ if }  \frac{n}{2} \text{ is odd.}
-\end{array}\right.\]
-
-Accordingly, $f$ is balanced when $n \equiv 0\mod 4$ and unbalanced when $n\equiv 2 \mod 4$.
+	The announced result follows by applying that $\binom{m}{k}=\binom{m}{m-k}$ for all integers $m\geq 0$ and $k$.
 \end{proof}
@@
 We observe that the above method provides a much tighter bound than the one from Corollary~\ref{cor:bound_walsh_cauchy}, and its polynomial complexity enables us to extend the analysis far beyond what is feasible with a full computation of the Walsh spectrum (\( \mathcal{O}(n 2^n) \)).
-
-\iffalse
-\begin{table}
-	\centering
-	\begin{tabular}{|c|c|c|}
-		\hline
-		$n$ & $\max_{a\in\F_2^n}|W_f(a)|$ & $B_n$ \\ \hline
-		$2$  & $2$     & $4$     \\
-		$4$  & $8$     & $14$     \\
-		$6$  & $20$    & $36$    \\
-		$8$  & $52$    & $114$    \\
-		$10$ & $108$   & $288$   \\
-		$12$ & $292$   & $820$   \\
-		$14$ & $700$   & $2\,316$  \\
-		$16$ & $2\,176$  & $6\,006$  \\
-		$18$ & $4\,964$  & $18\,192$  \\
-		$20$ & $14\,968$ & $48\,480$ \\
-		$22$ & $34\,232$ & $140\,392$ \\
-		$24$ & $109\,648$ & $392\,168$ \\ \hline
-	\end{tabular}
-	\tablecaption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ compared to the bound $B_n$}
-	\label{table:max_walsh_vs_bound}
-\end{table}
-\fi
 

### 2024-12-05 RevisedHiddenWeight.tex
Removed some comments

@@
 	\end{tabular}
-	\tablecaption{Lowest possible values of $(d, e)$ for different values of $n$.\tsnote{Aren't the roles of $d$ and $e$ reversed?}}
+	\tablecaption{Lowest possible values of $(d, e)$ for different values of $n$.}
 	\label{table:FAI}
 \end{table}
-
-\pmnote{ degree of $h$, denoted by $e$ here is always greater than the AI, whereas $\degg(g)=d$ is smaller. It is consistent}
 

### 2024-12-06 RevisedHiddenWeight.tex
Checked Section 5 (not yet final check)

@@
 	\end{abstract}
-
-\tsnote{@Self, check entire document.}
 
@@
 %\end{align*}
-%where $c$ is the $n$-length binary vector such that $c=a+e_k+\sum_{i=n/2+1}^n e_i$ where the $e_i$ denotes the canonical vector with "1" in position $i$.
+%where $c$ is the $n$-length binary vector such that $c=a+e_k+\sum_{i=n/2+1}^n e_i$ where the $e_i$ denotes the canonical vector with “1” in position $i$.
 
@@
 \begin{table}
+	\small
 	\centering
@@
 	\end{tabular}
-	\tablecaption{Values of $\Dnka{2}{k}{a}$ for $n=2$.}\label{tab:Dnka}
+
+	\mycaption{Values of $\Dnka{2}{k}{a}$ for $n=2$.}\label{tab:Dnka}
 \end{table}
@@
 \begin{table}
+	\small
     	\centering
@@
     	\end{tabular}
-    	\tablecaption{Values of $\Dnka{n}{k}{a}$ for small values of $k$.}\label{tab:Dnka_small_k}
+
+    	\mycaption{Values of $\Dnka{n}{k}{a}$ for small values of $k$.}\label{tab:Dnka_small_k}
     \end{table}
@@
 This checking can be autotomized by a computer algebra system.
-For this, we refer to the corresponding \textsf{SageMath} implementation from \cite{githubseure24}.\tsnote{@Pierrick, OK like this?}
-
-    \pmnote{I think it works for the eprint (use the "ifnum\anon=" to be sure we do not forget it in an anonymous submission.
-
-    I do not know if this will create a reference in your google scholar later one.
-Personally I would prevent that by just giving the link in the text, to avoid to have a reference that will have only 1 citation.
-
-    	)}
-
+For this, we refer to the corresponding \textsf{SageMath} implementation, accessible via this link: \url{https://github.com/se-tim/Revisited-HWBF.git}.
 \end{proof}
@@
         \includegraphics[width=7cm]{cauchy_estimate.pdf}
-        \caption{Cauchy estimate in blue vs.\ binomial coefficients in red.}
+
+        \mycaption{Cauchy estimate in blue vs.\ binomial coefficients in red.}
         \label{fig:cauchy_estimate}
@@
     The goal will be to prove that the maximum of $g^{(\lambda)}(\alpha)=g(\alpha)=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{a,t}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$.
-Since $g$ is an even function, it is enough to focus on the interval $\alpha\in[0,\pi]$; the function $g$ is represented for several different values of $0\leq\lambda<1/2$ in Figure~\ref{fig:family_curves_g}.
+Since $g$ is an even function, it is enough to focus on the interval $\alpha\in[0,\pi]$; the function $g$ is represented for several values of $0\leq\lambda<1/2$ in Figure~\ref{fig:family_curves_g}.
 
@@
         \vspace{-4mm}
-    	\caption{The curves of $\alpha\mapsto g^{(\lambda)}(\alpha)$ for the values $\lambda=\frac{i}{50}$ from $i=0$ (red) to $i=24$ (blue).}
+
+    	\mycaption{The curves of $\alpha\mapsto g^{(\lambda)}(\alpha)$ for the values $\lambda=\frac{i}{50}$ from $i=0$ (red) to $i=24$ (blue).}
     	\label{fig:family_curves_g}
@@
 	\centering
-	\includegraphics[width=10cm]{curve_exponents_lambda_mu.pdf}
+	\includegraphics[width=9.5cm]{curve_exponents_lambda_mu.pdf}
     \vspace{-5mm}
-	\caption{The curve of $\lambda\mapsto\mu(\lambda)$ with $0\leq\lambda\leq\frac 12$ from Theorem~\ref{theorem:bound_D_nka_generalized}.}
+
+	\mycaption{The curve of $\lambda\mapsto\mu(\lambda)$ with $0\leq\lambda\leq\frac 12$ from Theorem~\ref{theorem:bound_D_nka_generalized}.}
 	\label{fig:curve_exponents_lambda_mu}
@@
 \section{Experiments and comparisons}\label{sec:expAndComp}
-
-\tsnote{@Pierrick, this entire section needs updating because of Proposition 3.}
 
@@
 For this, consider a vector $b\in\mathbb F_2^n$; we write $(p,q,r)=(p(b),q(b),r(b))$.
-Also, for $k\in[1,n]$, let $b_k=b+\pi(e_k)$ and $(p_k,q_k,r_k)=(p(b_k),q(b_k),r(b_k))$.
-Observe that for every $k\in[1,n]$, we have $(p_k,q_k,r_k)\in\{(p\pm1,q,r\mp 1),(p,q\pm 1,r\mp 1)\}$.
+Also, for $k\in[1,n]$, let $b_k=b+\pi(e_k)$ and $(p_k,q_k,r_k)=(p(b_k),q(b_k),r(b_k))$, where $\pi:[1,n]\to[1,n]$ is again the permutation sending the first $n/2$ elements to the odd positions and the $n/2$ last ones to the even positions.
+Notice first that for every integer $k\in[1,n]$, it holds that $(p_k,q_k,r_k)\in\{(p\pm1,q,r\mp 1),(p,q\pm 1,r\mp 1)\}$.
 Furthermore, observe that if $k\in[0,n/2]$ and $(p_k,q_k,r_k)=(p+\alpha,q+\beta,r+\gamma)$ for $\{\alpha,\beta,\gamma\}=\{0,\pm 1\}$ with $\gamma\neq 0$, then we have $(p_{k+n/2},q_{k+n/2},r_{k+n/2})=(p+\alpha',q+\beta',r+\gamma')$ for some $\{\alpha',\beta',\gamma'\}=\{0,\pm 1\}$ with $\gamma'\neq 0$ which only depend on $\alpha$, $\beta$ and $\gamma$.
@@
 \]
-For each $1\leq k\leq n/2$, we select $\{\alpha_k,\beta_k,\gamma_k\}=\{0,\pm 1\}$ with $\gamma_k\neq 0$ such that the following expression is defined and maximized:
+
+For each $k\in[1,n/2]$, we select $\{\alpha_k,\beta_k,\gamma_k\}=\{0,\pm 1\}$ with $\gamma_k\neq 0$ such that the following expression, based on the notation introduced in Remark~\ref{rmk:Dnka_dep_pqr}, is defined and maximized:
 \[
@@
 \]
-This implies that $\Dnka{n}{k}{b_k}+\Dnka{n}{k+n/2}{b_{k+n/2}}\leq B_k^{p,q,r}$ for every $1\leq k\leq n/2$, leading to the conclusion that $\sum_{k=1}^n\Dnka nk{b_k}\leq\sum_{k=1}^{n/2} B_k^{p,q,r}$.
+This implies that $\Dnka{n}{k}{b_k}+\Dnka{n}{k+n/2}{b_{k+n/2}}\leq B_k^{p,q,r}$ for every $k\in[1,n/2]$, leading to the conclusion that $\sum_{k=1}^n\Dnka nk{b_k}\leq\sum_{k=1}^{n/2} B_k^{p,q,r}$.
 As a result, we derive the following upper bound:
 \begin{equation}\label{eqn:bound_walsh}
-\max_{a\in\F_2^n}\wt f(a)\leq\max_{p+q+r=n/2}\sum_{k=1}^{n/2} B_k^{p,q,r}.
+\max_{a\in\F_2^n}\wt f(a)\leq 1+\max_{p+q+r=n/2}\sum_{k=1}^{n/2} B_k^{p,q,r}.
 \end{equation}
-Under the assumption that the values of $\mathsf{D}_{n,k}^{p,q,r}$ have already been computed for all triplets $(p,q,r)$ satisfying $p+q+r=n/2$, the bound in equation (\ref{eqn:bound_walsh}) can be determined with a computational complexity of $\mathcal{O}(n^3)$.
-This is because there are $\mathcal{O}(n^2)$ possible triplets $(p,q,r)$ that meet the condition $p+q+r=n/2$, and the summation itself can be computed in $\mathcal{O}(n)$.
-
-We consider now the complexity involved in computing the values of $\mathsf{D}_{n,k}^{p,q,r}$ for all $0 \leq k \leq n$ and for all triplets $(p,q,r)$ where $p+q+r=n/2$.
+
+Under the assumption that the values of $\mathsf{D}_{n,k}^{p,q,r}$ have already been computed for all $k\in[1,n]$ and for all triplets $(p,q,r)$ satisfying $p+q+r=n/2$, the bound in equation (\ref{eqn:bound_walsh}) can be determined with a computational complexity of $\mathcal{O}(n^3)$.
+This is because there are $\mathcal{O}(n^2)$ possible triplets $(p,q,r)$ that meet the condition $p+q+r=n/2$, and the summation itself can be computed in $\mathcal{O}(n)$ steps.
+
+We consider now the complexity involved in computing the values of $\mathsf{D}_{n,k}^{p,q,r}$ for all $k\in[1,n]$ and all triplets $(p,q,r)$ satisfying $p+q+r=n/2$.
 We claim that this computation has a complexity of $\mathcal{O}(n^3 \log n)$.
-Towards this, according to Proposition \ref{proposition:generating_fct}, it is sufficient to expand the polynomials $(-z^2 + 2z + 1)^p \cdot (-z^2 - 2z + 1)^q \cdot (z^2 + 1)^r$ for all triplets $(p,q,r)$ such that $p+q+r=n/2$.
-
-To achieve this, we first precompute the expanded polynomials $(-z^2 + 2z + 1)^p$ for each $1 \leq p \leq n/2$.
+Towards this, it is sufficient to expand $(-z^2 + 2z + 1)^p \cdot (-z^2 - 2z + 1)^q \cdot (z^2 + 1)^r$ for all triplets $(p,q,r)$ such that $p+q+r=n/2$; this is due to Proposition \ref{proposition:generating_fct}.
+To achieve this, we first precompute the expanded polynomial $(-z^2 + 2z + 1)^p$ for each $p\in[1,n/2]$.
 This can be done recursively using the formula $(-z^2 + 2z + 1)^{p+1} = (-z^2 + 2z + 1) \cdot (-z^2 + 2z + 1)^p$.
-For each $p$, we need to compute the product of two expanded polynomials of degree at most $n/2$, which requires $\mathcal{O}(n \log n)$ computations .
-Performing this for every $p$ results in a total complexity of $\mathcal{O}(n^2 \log n)$.
-The same approach is used to expand the polynomials $(-z^2 - 2z + 1)^q$ and $(z^2 + 1)^r$, resulting in an overall complexity of $\mathcal{O}(n^2 \log n)$ for this precomputational step.
-
-Finally, for each triplet $(p,q,r)$ where $p+q+r=n/2$, we multiply the expanded polynomials $(-z^2 + 2z + 1)^p$, $(-z^2 - 2z + 1)^q$, and $(z^2 + 1)^r$.
-These two multiplications are once more performed in $\mathcal{O}(n \log n)$.
-Given that there are $\mathcal{O}(n^2)$ such triplets $(p,q,r)$, the complexity of this step totals $\mathcal{O}(n^3 \log n)$.
-Therefore, this final step is the primary computational bottleneck, making the overall complexity of the procedure also $\mathcal{O}(n^3 \log n)$.
-
-\pmnote{Create a public github with all the code (not the .tex) used relatively to the article.
-We will give this link for the public version.
-Fot the anonymous one we will not mention the git, and only add the files in supplementary material.}
+For each $p$, this requires $\mathcal O(n)$ arithmetic computations.
+Performing this for every $p$ results in a total complexity of $\mathcal{O}(n^2)$.
+The same approach can be used to expand the polynomials $(-z^2 - 2z + 1)^q$ and $(z^2 + 1)^r$, resulting in an overall complexity of $\mathcal{O}(n^2)$ for a fixed triplet $(p,q,r)$.
+Finally, for each such triplet $(p,q,r)$, we multiply the three expanded polynomials $(-z^2 + 2z + 1)^p$, $(-z^2 - 2z + 1)^q$ and $(z^2 + 1)^r$.
+These two multiplications are performed in $\mathcal{O}(n \log n)$ operations by using the fast Fourier transform.
+Given that there are $\mathcal{O}(n^2)$ triplets $(p,q,r)$ to consider, precomputing the values $\mathsf{D}_{n,k}^{p,q,r}$ for all $k\in[1,n]$ and all triplets $(p,q,r)$ has a complexity of $\mathcal{O}(n^3 \log n)$, making the overall complexity of the procedure also $\mathcal{O}(n^3 \log n)$.
 
@@
 
-In Table~\ref{table:max_walsh_vs_bound}, we compare the exact values of $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ for small values of $n$ (calculated using \textsf{SageMath}) to the upper bound $B_n$ obtained through the above method and the one from Corollary~\ref{cor:bound_walsh_cauchy}.
-Additionally, Table~\ref{table:walsh_bounds} provides the values of the bound $B_n$ for all even values of $n$ from $1$ to $80$.
-We observe that the above method provides a much tighter bound than the one from Corollary~\ref{cor:bound_walsh_cauchy}, and its polynomial complexity enables us to extend the analysis far beyond what is feasible with a full computation of the Walsh spectrum (\( \mathcal{O}(n 2^n) \)).
+\bigskip
+In Table~\ref{table:max_walsh_vs_bound}, we compare the exact values of $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ for small values of $n$ (calculated using \textsf{SageMath}) to the bound $B_n$ obtained through the above method and the bound from Corollary~\ref{cor:bound_walsh_cauchy}.
+Additionally, Table~\ref{table:walsh_bounds} provides the values of the bound $B_n$ for all even values of $n\in[1,80]$.
+The method described above offers a significantly tighter bound compared to Corollary~\ref{cor:bound_walsh_cauchy}.
+Its polynomial complexity makes it possible to extend the analysis well beyond the limitations imposed by a full computation of the Walsh spectrum, which requires a complexity of $\mathcal O(n2^n)$.
+We provide a \textsf{SageMath} implementation to obtain the bound $B_n$: \url{https://github.com/se-tim/Revisited-HWBF.git}.
 
 \begin{table}
+	\small
 	\centering
@@
 		\hline
-		$n$ & $\max_{a\in\F_2^n}|W_f(a)|$ & $B_n$  & $\lfloor 1+n \cdot 2^{3n/4} \rfloor$\\ \hline
-		$2$  & $2$     & $4$  &  $6$ \\
-		$4$  & $8$     & $14$  & $33$  \\
-		$6$  & $20$    & $36$   & $136$\\
-		$8$  & $52$    & $114$  & $513$ \\
-		$10$ & $108$   & $288$  & $1\,811$\\
-		$12$ & $292$   & $820$  & $6\,145$ \\
-		$14$ & $700$   & $2\,316$ & $20\,275$ \\
-		$16$ & $2\,176$  & $6\,006$ & $65\,637$ \\
-		$18$ & $4\,964$  & $18\,192$ & $208\,535$ \\
-		$20$ & $14\,968$ & $48\,480$ & $655\,361$ \\
-		$22$ & $34\,232$ & $140\,392$ & $2\,039 \,002$ \\
-		$24$ & $109\,648$ & $392\,168$ & $6\,291 \,457$  \\ \hline
+		$n$ & $\max_{a\in\F_2^n}|\wt f(a)|$ & $B_n$  & $\lfloor 1+n \cdot 2^{3n/4} \rfloor$\\ \hline
+		$2$  & $2$     & $2$  &  $6$ \\
+		$4$  & $8$     & $8$  & $33$  \\
+		$6$  & $20$    & $28$   & $136$\\
+		$8$  & $52$    & $76$  & $513$ \\
+		$10$ & $108$   & $212$  & $1\,811$\\
+		$12$ & $292$   & $596$  & $6\,145$ \\
+		$14$ & $700$   & $1\,828$ & $20\,275$ \\
+		$16$ & $2\,176$  & $5\,196$ & $65\,537$ \\
+		$18$ & $4\,964$  & $14\,668$ & $208\,535$ \\
+		$20$ & $14\,968$ & $41\,468$ & $655\,361$ \\
+		$22$ & $34\,232$ & $118\,544$ & $2\,039 \,002$ \\
+		$24$ & $109\,648$ & $325\,188$ & $6\,291 \,457$  \\ \hline
 	\end{tabular}
-	\tablecaption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ compared to the bound $B_n$ and the one from Corollary~\ref{cor:bound_walsh_cauchy}.}
+
+	\mycaption{The actual $\max_{a\in\F_2^n}|\wt f(a)|$ compared to the bound $B_n$ and the bound from Corollary~\ref{cor:bound_walsh_cauchy}.}
 	\label{table:max_walsh_vs_bound}
@@
 			\hline
-			$2$  & $4.00 \cdot 10^{0}$  \\
-			$4$  & $1.40 \cdot 10^{1}$  \\
-			$6$  & $3.60 \cdot 10^{1}$  \\
-			$8$  & $1.14 \cdot 10^{2}$  \\
-			$10$ & $2.88 \cdot 10^{2}$  \\
-			$12$ & $8.20 \cdot 10^{2}$  \\
-			$14$ & $2.32 \cdot 10^{3}$  \\
-			$16$ & $6.01 \cdot 10^{3}$  \\
-			$18$ & $1.82 \cdot 10^{4}$  \\
-			$20$ & $4.85 \cdot 10^{4}$  \\
+			$2$  & $2.00 \cdot 10^{0}$  \\
+			$4$  & $8.00 \cdot 10^{0}$  \\
+			$6$  & $2.80 \cdot 10^{1}$  \\
+			$8$  & $7.60 \cdot 10^{1}$  \\
+			$10$ & $2.12 \cdot 10^{2}$  \\
+			$12$ & $5.96 \cdot 10^{2}$  \\
+			$14$ & $1.83 \cdot 10^{3}$  \\
+			$16$ & $5.20 \cdot 10^{3}$  \\
+			$18$ & $1.47 \cdot 10^{4}$  \\
+			$20$ & $4.15 \cdot 10^{4}$  \\
 			\hline
@@
 			\hline
-			$22$ & $1.40 \cdot 10^{5}$  \\
-			$24$ & $3.92 \cdot 10^{5}$  \\
-			$26$ & $1.14 \cdot 10^{6}$  \\
-			$28$ & $3.12 \cdot 10^{6}$  \\
-			$30$ & $8.90 \cdot 10^{6}$  \\
-			$32$ & $2.50 \cdot 10^{7}$  \\
-			$34$ & $7.14 \cdot 10^{7}$  \\
-			$36$ & $2.04 \cdot 10^{8}$  \\
-			$38$ & $5.75 \cdot 10^{8}$  \\
-			$40$ & $1.62 \cdot 10^{9}$  \\
+			$22$ & $1.19 \cdot 10^{5}$  \\
+			$24$ & $3.25 \cdot 10^{5}$  \\
+			$26$ & $9.59 \cdot 10^{5}$  \\
+			$28$ & $2.68 \cdot 10^{6}$  \\
+			$30$ & $7.65 \cdot 10^{6}$  \\
+			$32$ & $2.14 \cdot 10^{7}$  \\
+			$34$ & $6.25 \cdot 10^{7}$  \\
+			$36$ & $1.76 \cdot 10^{8}$  \\
+			$38$ & $5.03 \cdot 10^{8}$  \\
+			$40$ & $1.40 \cdot 10^{9}$  \\
 			\hline
@@
 			\hline
-			$42$ & $4.59 \cdot 10^{9}$  \\
-			$44$ & $1.29 \cdot 10^{10}$ \\
-			$46$ & $3.63 \cdot 10^{10}$ \\
-			$48$ & $1.02 \cdot 10^{11}$ \\
-			$50$ & $2.88 \cdot 10^{11}$ \\
-			$52$ & $8.06 \cdot 10^{11}$ \\
-			$54$ & $2.30 \cdot 10^{12}$ \\
-			$56$ & $6.45 \cdot 10^{12}$ \\
-			$58$ & $1.83 \cdot 10^{13}$ \\
-			$60$ & $5.14 \cdot 10^{13}$ \\
+			$42$ & $4.01 \cdot 10^{9}$  \\
+			$44$ & $1.12 \cdot 10^{10}$ \\
+			$46$ & $3.21 \cdot 10^{10}$ \\
+			$48$ & $8.91 \cdot 10^{10}$ \\
+			$50$ & $2.56 \cdot 10^{11}$ \\
+			$52$ & $7.12 \cdot 10^{11}$ \\
+			$54$ & $2.05 \cdot 10^{12}$ \\
+			$56$ & $5.73 \cdot 10^{12}$ \\
+			$58$ & $1.65 \cdot 10^{13}$ \\
+			$60$ & $4.59 \cdot 10^{13}$ \\
 			\hline
@@
 			\hline
-			$62$ & $1.47 \cdot 10^{14}$ \\
-			$64$ & $4.09 \cdot 10^{14}$ \\
-			$66$ & $1.17 \cdot 10^{15}$ \\
-			$68$ & $3.25 \cdot 10^{15}$ \\
-			$70$ & $9.34 \cdot 10^{15}$ \\
-			$72$ & $2.60 \cdot 10^{16}$ \\
-			$74$ & $7.44 \cdot 10^{16}$ \\
-			$76$ & $2.08 \cdot 10^{17}$ \\
-			$78$ & $5.97 \cdot 10^{17}$ \\
-			$80$ & $1.65 \cdot 10^{18}$ \\
+			$62$ & $1.32 \cdot 10^{14}$ \\
+			$64$ & $3.66 \cdot 10^{14}$ \\
+			$66$ & $1.05 \cdot 10^{15}$ \\
+			$68$ & $2.93 \cdot 10^{15}$ \\
+			$70$ & $8.40 \cdot 10^{15}$ \\
+			$72$ & $2.33 \cdot 10^{16}$ \\
+			$74$ & $6.71 \cdot 10^{16}$ \\
+			$76$ & $1.87 \cdot 10^{17}$ \\
+			$78$ & $5.39 \cdot 10^{17}$ \\
+			$80$ & $1.51 \cdot 10^{18}$ \\
 			\hline
@@
 	\end{minipage}
-	\tablecaption{Approximate values of $B_n$ for various values of $n$.}
+
+	\mycaption{Approximate values of $B_n$ for various values of $n$.}
 	\label{table:walsh_bounds}
@@
 
-In this part we compare the nonlinearity of the function $f$ from Definition~\ref{def:revHWBF} to other weightwise quadratic functions considered for similar use-cases, such as majority, \hwbf{} and the cyclic weighwise functions studied in~\cite{DAM:MeaOza24}.
+In this part, we compare the nonlinearity of the revisited \hwbf{} $f\in\BN$ to other weightwise quadratic functions considered for similar use-cases, such as the majority function, the \hwbf{} and the cyclic weightwise functions studied in~\cite{DAM:MeaOza24}.
 
@@
 The violet and orange curves represent the upper bounds  in~\cite{DAM:MeaOza24}.
-The violet curve corresponds to the bound that holds for all cyclic weightwise linear functions where $ f_0(x) = b \cdot x $ with $\w(b)$ odd, providing, for example, an upper bound for the \hwbf{}.
-The orange curve corresponds to the bound for the cyclic weightwise quadratic function defined by $f_0(x) = x_1 + x_2 x_3$.
-The blue curve represents both the majority and \hwbf{} functions, whose exact nonlinearities are given in Property~\ref{prop:wwd1}.
+More precisely, the violet curve corresponds to the bound that holds for all cyclic weightwise linear functions $f$ that, with the notation from Definition~\ref{def:wwdegd}, satisfy $ f_0(x) = b \cdot x $ for $\w(b)$ odd; therefore, this represents for instance an upper bound for the \hwbf{}.
+The orange curve corresponds to the bound for the cyclic weightwise quadratic function $f$ defined by $f_0(x) = x_1 + x_2 x_3$.
+The blue curve applies to both the majority and \hwbf{} functions, whose exact nonlinearities are given in Property~\ref{prop:wwd1}.
 We use a single curve here because, on a logarithmic scale, the nonlinearity difference between these two functions is too small to distinguish between them.
@@
 	\centering
-	\includegraphics[width=9cm]{comparison_walsh_bound.pdf}
-	\caption{
+	\includegraphics[width=10.5cm]{comparison_walsh_bound.pdf}
+
+	\mycaption{
 		%Maximum of the absolute value of the Walsh spectrum of different functions, in logarithmic scale, for even values of $n$.
@@
 \tsnote{Updated plot, but the description now needs to be changed.}}
-		Maximum absolute values of the Walsh spectrum for various functions, shown on a logarithmic scale for even values of $n$. 
-		The violet and orange curves represent bounds for cyclic weightwise linear functions and a cyclic weightwise quadratic function from~\cite{DAM:MeaOza24}.
-The blue curve shows values for the majority function and \hwbf{}.
-The theoretical bound for the function $f$ (from Corollary~\ref{cor:bound_walsh_cauchy}) is in red, and the experimental bound $B_n$ (Section~\ref{sec:expwt}) is in green.}
+		Bounds on the maxima of absolute values of the Walsh spectrum for various functions, shown on a logarithmic scale for even values of $n$.
+		The violet and orange curves, the orange one mostly covering the violet one, represent bounds for cyclic weightwise linear functions and a cyclic weightwise quadratic function from~\cite{DAM:MeaOza24}, respectively.
+The blue curve shows bounds for the majority function and the \hwbf{}.
+The theoretical bound for the revisited \hwbf{} (from Corollary~\ref{cor:bound_walsh_cauchy}) is in red, and the experimental bound $B_n$ (Section~\ref{sec:expwt}) is in green.}
 	\label{fig:walsh_bound_comparison}
@@
 
-We observe significantly better performance for the newly introduced function $f$ compared to the majority function and \hwbf{}, with the proven bound exhibiting an asymptotic slope of $ 3/4$ as opposed to $1$.
-The two bounds proven in~\cite{DAM:MeaOza24} also have an asymptotic slope of $1$.
-The gap between the red and green curves, both representing upper bounds on $ \max_{a \in \mathbb{F}_2^n} |\wt f(a)| $ (with only the formula for the red curve proven for all even $n$), suggests that the true values may follow an even better slope than $ 3/4$.
-
-In Table~\ref{table:comparisonsNL}, we compare the specific nonlinearity values of the functions under consideration.
-Among the various weightwise quadratic functions studied so far, we observe that $f$ has the highest nonlinearity from $n=10$ onward.
+The revisited \hwbf{} demonstrates significantly better performance compared to the majority function and the original \hwbf{}.
+Its theoretical bound reveals an asymptotic slope of $3/4$ on a logarithmic scale, contrasting with the slope of $1$ for the majority function and the \hwbf{}.
+Notably, the green curve corresponding to the bound of Section~{sec:expwt} appears to share this asymptotic slope of $3/4$, supporting the effectiveness of Corollary~\ref{cor:bound_walsh_cauchy} and the stronger Theorem~\ref{theorem:bound_D_nka_generalized} in capturing asymptotic behavior.
+In contrast, the bounds proven in~\cite{DAM:MeaOza24}, represented by the violet and orange curves, exhibit the less favorable asymptotic slope of $1$.
+
+We also compare in Table~\ref{table:comparisonsNL} the precise nonlinearity values of the functions under consideration.
+Among the various weightwise quadratic functions studied so far, we observe that the revisited \hwbf{} has the highest nonlinearity from $n=10$ onward.
 
 \begin{table}
+	\small
 	\centering
@@
 	\end{tabular}
-	\tablecaption{Comparison of the nonlinearity.}
+
+	\mycaption{Comparison of the nonlinearity.}
 	\label{table:comparisonsNL}
@@
 In Table~\ref{table:comparisonsDeg}, we display the algebraic degree of different weightwise quadratic function.
-We observe that the revisited \hwbf{} is the function with highest degree, together with the \hwbf{}.
+We observe that the revisited \hwbf{} is the function with the highest degree, together with the \hwbf{}.
 
 \begin{table}
+	\small
 	\centering
@@
 	\end{tabular}
-	\tablecaption{Comparison of the degree.}
+
+	\mycaption{Comparison of the degree.}
 	\label{table:comparisonsDeg}
 \end{table}
-
-%\subsection{Algebraic immunity}
 
@@
 	\[g\cdot(q+1) \cdot(h+\varepsilon) = g\cdot(q+1)\cdot(f+q+\varepsilon)=g\cdot(q+1)\cdot(f+\epsilon)+g\cdot(q+1)\cdot q=0+0=0.\]
-	Hence $g\cdot(q+1)$ is an annihilator of $h+ \varepsilon$. 
+	Hence, $g\cdot(q+1)$ is an annihilator of $h+ \varepsilon$. 
 	If $g\cdot(q+1)\ne 0$, it follows that $\AI(h)\leq\degg(g\cdot(q+1))\leq\degg(g)+\degg(q+1)$, and therefore that $\AI(f)=\degg(g)\geq\AI(h)-\degg(q+1)=\AI(h)-2$.
@@
 		 \end{tabular}
-	 \tablecaption{Characteristics of Boolean Functions for Different $n$ Values}
+
+	 \mycaption{Characteristics of Boolean Functions for Different $n$ Values}
 	 \end{table}
@@
 	\end{tabular}
-	\tablecaption{Comparison of the algebraic immunity.}
+
+	\mycaption{Comparison of the algebraic immunity.}
 	\label{table:comparisonsAI}
@@
 
-\bigskip
 Lastly, we also considered the fast algebraic immunity of the revisited \hwbf{} $f$.
@@
 	\end{tabular}
-	\tablecaption{Lowest possible values of $(d, e)$ for different values of $n$.}
+
+	\mycaption{Lowest possible values of $(d, e)$ for different values of $n$.}
 	\label{table:FAI}

### 2024-12-06 RevisedHiddenWeight.tex
Cleanup of tex code (pdf unchanged)

@@
-\def\anon{0} %% set to 1 for anonymous submissions, hides acknowledgements and author names
-\def\full{1} %% set to 0 for springer proceedings
+\def\anon{0} % set to 1 for anonymous submissions, hides acknowledgements and author names
+\def\full{1} % set to 0 for springer proceedings
 
@@
 	\documentclass[11pt]{llncs}
-
 	\addtolength{\parskip}{1pt}
@@
 	\usepackage{times}
-
 \fi
@@
 \begin{document}
+
 \setcounter{page}{1}
+
 \title{The Revisited Hidden Weight Bit Function}
-
 \titlerunning{The Revisited Hidden Weight Bit Function}
-\author{
+
+\ifnum\anon=0
+	\author{%
 		Pierrick M\'eaux\inst{1},
@@
 		Deng Tang\inst{2}
-%	Pierrick M\'eaux\orcidID{0000-0001-5733-4341}\inst{1},
-%	Tim Seuré\inst{1}, 
-%	Deng Tang\orcidID{0000-0002-8373-9200}\inst{2}
+		%Pierrick M\'eaux\orcidID{0000-0001-5733-4341}\inst{1},
+		%Tim Seuré\inst{1}, 
+		%Deng Tang\orcidID{0000-0002-8373-9200}\inst{2}
 	}
 	\authorrunning{P.\ M\'eaux, T.\ Seur\'e, D.\ Tang}
-
-\institute{
-	University of Luxembourg, Luxembourg\\ \email{pierrick.meaux@uni.lu, tim.seure@uni.lu} 
-	%\and
-%		University of Luxembourg, Luxembourg\\ \email{pierrick.meaux@uni.lu}
+	\institute{%
+		University of Luxembourg, Luxembourg\\
+		\email{pierrick.meaux@uni.lu, tim.seure@uni.lu} 
 		\and
@@
 	}
-
-	%----------------------------------------------------------------
+\else
+	\author{}
+	\institute{}
+\fi
+
 \maketitle
-
-\institute{
-	University of Luxembourg, Luxembourg\\
-	\email{pierrick.meaux@uni.lu}		
-}
 
@@
 
-%\pmnote{short intro:
-
-%HWBF introduced in x, interesting for its cryptographic criteria and easy implementation. cryptographic properties studied in y such as balancedness, algebraic immunity and nonlinearity. 
-%New potential uses in a stream cipher, or modifications. Use: transciphering and works aiming at finding Boolean functions easy to evaluate homomorphically, input oblivious algorithms. 
-%Nonlinearity a bit low for direct use.
-
-%Contributions: new function as addition of HWBF and quadratic bent function.
-We show when the function is balanced, formalize and study its nonlinearity.
-Bounds on the nonlinearity of $f$, generalization to a family of function, and an algorithm for estimating the nonlinearity for $n$ up to $80$.
-Comparisons with other functions and practical values of the parameters for $n$ up to $20$.
-
-%}
-
-\iffalse
-%prompt
-
-The Hidden Weight Bit Function (\hwbf{}) has received a lot of attention since its introduction by Bryant
-in $1991$~\cite{IEEE:Bryant91}, it has been considered as the simplest example of function with binary decision
-diagram of exponential size~\cite{IEEE:Bryant91,TIA:BoLSW99}. 
-The facility of implementing this function in different models of computation since it consists in computing the Hamming weight of the input and applying a simple linear function, and it relatively good cryptographic properties exhibited in~\cite{DAM:WCST14} (balancedness, nonlinearity, degree and algebraic immunity) made it an interesting starting point candidate to design the filter of some stream cipher constructions.
-
-Recently, new developments in stream ciphers lead to reconsider this function.
-The new potential uses of stream ciphers with filter functions on a larger number number of variables such as Hybrid Homomorphic Encryption~\cite{CCS:NaeLauVai11} (\textsf{HHE}) gave a regain of interest in these functions.
-\textsf{HHE} aims at finding Boolean functions efficient to evaluate as an input oblivious algorithm.
-For example various new binary stream ciphers have been designed since $2016$ such as Kreyvium~\cite{JOC:CCFLNP18}, FLIP~\cite{EC:MJSC16}, Rasta~\cite{C:Rasta}, FiLIP~\cite{INDO:MCJS19} and Dasta~\cite{TOSC:BeiLea20}.
-Currently, the designs with Boolean functions with more than one hundred variables as a filter are the ones leading to the \textsf{HHE} with best latency~\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24}.
-%cite FHE for MPC?
-
-The nonlinearity of the \hwbf{} being low for a direct use as filter function, several generalizations have been considered recently, aiming at strengthening this parameter and keeping or improving the others cryptographic relevant parameters such as balancedness, algebraic degree and and algebraic immunity.
-In these generalizations we count the functions introduced in~\cite{IEEE:Carlet22,eprint:CarPar23,DAM:MeaOza24}.
-The later article considers some functions obtained by computing the Hamming weight of the input and then simply applying a quadratic Boolean function.
-
-In this article we consider another function that is weightwise quadratic, obtained by \textsf{XOR}-ing the \hwbf{} and a bent quadratic function.
-Therefore, we exhibit a family of Boolean functions both easy to compute and with good parameters, improving over the ones exhibited in~\cite{DAM:MeaOza24}.
-Various of the techniques we introduce to determine the nonlinearity are of independent interest, and allow to bound the maximum of the absolute Walsh spectrum for a wider family of weightwise quadratic functions.
-Our contributions are the following:
-
-\begin{itemize}
-	\item In Section~\ref{sec:defAndBal}, we define the revisited \hwbf{} $f$, and study its balancedness.
-This part is done by studying the (restricted) Walsh transform of some quadratic functions over sets of fixed Hamming weight, called slices.
-A recursive relation between these values allows to determine for which values of $n$ the function is balanced.
-	\item In Section~\ref{sec:dnk}, we link the maximum Walsh coefficients of the revisited \hwbf{} to the coefficients of generating functions and use techniques from complex analysis to prove lower bounds on the nonlinearity of $f$.
-	Differing from usual results in Boolean function used in cryptography, this allows us to determine a good enough bound on the nonlinearity for a larger family of functions, and for all even number of variables $n$.
-	\item In Section~\ref{sec:expAndComp}, we explain techniques to get a better bound for bounded values of $n$, giving a tighter bound for the nonlinearity of $f$ up to $n=80$.
-In this parts with experiments, we compare the bounds we obtain and the real value of the nonlinearity between $f$ and other weightwise quadratic functions such as the majority function, the \hwbf{}, and the two main examples from~\cite{DAM:MeaOza24}.
-These results show a neat advantage for the revisited \hwbf{} relatively the nonlinearity compared to function with similar computation costs.
-	\item In Section~\ref{sec:otherParameters} we analyze the other cryptographic relevant parameters of $f$, such as degree, algebraic immunity and fast algebraic immunity.
-Similarly to the comparison for the nonlinearity the revisited \hwbf{} performs better or similarly to the function with similar computation costs.
-
-\end{itemize}
-
-\fi
-
 The Hidden Weight Bit Function (\hwbf{}) has attracted significant attention since its introduction by Bryant in 1991~\cite{IEEE:Bryant91}.
@@
 \bigskip
+
 In this article, we propose a new generalization of the \hwbf{}, a weightwise quadratic function constructed by \textsf{XOR}-ing the \hwbf{} with a bent quadratic function.
@@
 Our contributions are as follows:
+
 \begin{itemize}
@@
 By establishing recursive relations for these values, we determine for which values of $n$ the function is balanced.
-
     \item \emph{Nonlinearity bounds} (Section~\ref{sec:dnk}):
@@
     Unlike most studies on Boolean functions used in cryptography, this approach yields strong nonlinearity bounds for a broader class of functions and for all even $n$.
-
     \item \emph{Experimental results and comparisons} (Section~\ref{sec:expAndComp}): 
@@
     Our results highlight the revisited \hwbf{}'s superior nonlinearity relative to functions with similar computational costs.
-
     \item \emph{Analysis of other cryptographic parameters} (Section~\ref{sec:otherParameters}):  
@@
 
-%Accordingly, the Boolean hypercube is partitioned into $n+1$ slices where the elements have the same Hamming weight.
-
 \begin{definition}[Slice]
@@
 	We call Algebraic Normal Form of a Boolean function $f\in\BN$ its unique representation as an element of the ring $\F_2[x_1,\dots,x_n]/(x_1^2+x_1,\dots,x_n^2+x_n)$, and we represent it as follows:
-	\[f(x_1,\dots,x_n)= \sum_{I \subseteq [1,n]} a_I \left( \prod_{i \in I} x_i \right), \]%x_1,\dots,x_n=\sum_{I \subseteq [1,n]} a_I x^I,\]
+	\[
+		f(x_1,\dots,x_n)= \sum_{I \subseteq [1,n]} a_I \left( \prod_{i \in I} x_i \right),
+	\]
 	where $a_I\in \F_2$. The (algebraic) degree of $f$ is defined by $\degg(f)=0$ in case $f$ is the null function, and $\degg(f)=\max\{ |I|:I\subseteq[1,n],a_I=1\}$ otherwise.
@@
 
-%\begin{definition}[Algebraic Immunity] \label{def:ai}
-%	The algebraic immunity of a Boolean function $f\in \Bfn{n}$, denoted as $\AI(f)$, is defined as:
-%	\[ \AI(f) = \min_{g \neq 0}\{ \degg(g) \; | \; fg = 0 \; \text{or} \; (f + 1)g = 0 \}{,} \]
-%	where $\degg(g)$ is the algebraic degree of $g$.
-%	The function $g$ is called an annihilator of $f$ (or $f + 1$). 
-%	Additionally we denote $\AN(f) = \min_{g \neq 0}\{ \degg(g) \; | \; fg = 0\}$.
-%\end{definition}
-
 \begin{definition}[Balancedness]
@@
 	The nonlinearity $\NL(f)$ of a Boolean function $f\in \BN$ is the minimum Hamming distance between $f$ and all the affine functions in $\BN$:
-	\[ \NL(f) = \min\{ \hd(f,g):g\in\BN,\degg(g)\leq 1\}{,} \]
+	\[
+		\NL(f) = \min\{ \hd(f,g):g\in\BN,\degg(g)\leq 1\},
+	\]
 	where the Hamming distance between $f$ and $g$ is defined as $\hd(f,g)=|\{x\in\F_2^n:f(x)\neq g(x)\}|$.
 Alternatively, the nonlinearity of $f\in\BN$ can also be defined in terms of its Walsh transform:
-	\[ \NL(f) = 2^{n-1}- \frac{1}{2} \max_{a\in \F_2^n}{|\wt{f}(a)|}. \]
+	\[
+		\NL(f) = 2^{n-1}- \frac{1}{2} \max_{a\in \F_2^n}{|\wt{f}(a)|}.
+	\]
 \end{definition}
@@
 \bigskip
+
 The algebraic degree of multiples of a Boolean function is a crucial quantity for various attacks on stream ciphers that utilize a Boolean function as a filter. 
@@
 
-\begin{definition}[Fast algebraic immunity, \eg{} \cite{EC:ACGKMR06}]\label{def:FAI} The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined as:
-\[
-    \FAI(f)=\min \{ 2 \AI(f), \min\{\degg(g)+ \degg(fg):g\in\BN,1\leq\degg(g)<\AI(f)\}\}
-\]
-
+\begin{definition}[Fast algebraic immunity, \eg{} \cite{EC:ACGKMR06}]\label{def:FAI}
+	The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined as:
+	\[
+		\FAI(f)=\min \{ 2 \AI(f), \min\{\degg(g)+ \degg(fg):g\in\BN,1\leq\degg(g)<\AI(f)\}\}.
+	\]
 \end{definition}
@@
 In this article, the symmetric functions that we consider will mainly be the slice indicator function and the majority function.
-%\begin{definition}[Elementary symmetric functions]
-%Let $i\in [0,n]$, the elementary symmetric function of degree $i$ in $n$ variables, denoted $\sigma_{i,n}$, is the function which ANF contains all monomials of degree $i$ and no monomials of other degrees.
-%\end{definition}
-\begin{definition}[Slice indicator functions]\label{def:slice} The indicator function of the slice of weight $k\in[0,n]$ is the function $\phikn kn\in\BN$ defined by $\phikn kn(x)=1$ if and only if $\w(x)=k$.
+
+\begin{definition}[Slice indicator functions]\label{def:slice}
+	The indicator function of the slice of weight $k\in[0,n]$ is the function $\phikn kn\in\BN$ defined by $\phikn kn(x)=1$ if and only if $\w(x)=k$.
 \end{definition}
@@
 	\end{array} \right. \] 
-
 \end{definition}
@@
 For simplicity, in the following we provide only the nonlinearity values of the majority function and \hwbf{}, as these bounds will be used for comparison.
-
-%We summarize the known results on the cryptographic criteria of weightwise affine functions we will use in this article in the following property.
 
@@
 \subsection{Krawtchouk polynomials}
+
 We use Krawtchouk polynomials and some of their properties to prove one of our main results. We give the necessary definition here and refer to \eg{}~\cite{book:MacSlo78} for more details.
@@
 \section{Revisited \hwbf{} and balancedness}\label{sec:defAndBal}
-%\subsection{Restricted Walsh transform of $f$ in a recursive fashion}
 
@@
 	For an even integer $n\geq 0$, we call revisited \hwbf{} the Boolean function $f\in\BN$ defined as:
-\[f(x)=\sum_{i=1}^{n/2}(x_i+1) x_{i+\frac{n}{2}} + \sum_{k=1}^nx_k\phikn{k}{n}(x).\]
+	\[
+		f(x)=\sum_{i=1}^{n/2}(x_i+1) x_{i+\frac{n}{2}} + \sum_{k=1}^nx_k\phikn{k}{n}(x).
+	\]
 \end{definition}
@@
 This form allows to derive the restricted Walsh transform of $f$, which can be a useful tool to study the balancedness and bound the nonlinearity of a function.
-%Maybe add examples, such as OM24, M24
-%We study the restricted Walsh transform  of $f$ to bound its nonlinearity.
+
 \begin{proposition}\label{prop:restrWT}
@@
 Then the restricted Walsh transform of $f$ satisfies:
-\[\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+n/2}+ c \cdot x}.\]
+	\[
+		\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+n/2}+ c \cdot x}.
+	\]
 \end{proposition}
+
 \begin{proof}
 	We compute:
-%\begin{align*}
-%	\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+a \cdot x}
-%	=\sum_{x \in \Ekn{k}{n}} (-1)^{x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}+ a \cdot x}\\
-%	&=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x},
-%\end{align*}
-%\begin{align*}
 	\begin{align*}
@@
 \end{proof}
-
-%\begin{align*}
-%\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}\\
-%&=\sum_{x \in \Ekn{k}{n}} (-1)^{x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}+ ax}\\
-%&=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ (c)x},
-%\end{align*}
-%where $c$ is the $n$-length binary vector such that $c=a+e_k+\sum_{i=n/2+1}^n e_i$ where the $e_i$ denotes the canonical vector with “1” in position $i$.
 
@@
 		\item If $n\geq 2$, then for $b=(a_1,\dots,a_{n-2})\in\F_2^{n-2}$, we have:
-    \[\Dnka{n}{k}{a}=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.\]
+		\[
+			\Dnka{n}{k}{a}=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.
+		\]
 	\end{itemize}
@@
 \end{proof}
-
-%The limit case of $n=0$ yields that $\Dnka 0ka=1$ if $k=0$ and $\Dnka 0ka=0$ otherwise.
-
-%With these notations we obtain a recursive relation for $\Dnka{n}{k}{a}$, and therefore for $\wtk{f}{k}(a)$, denoting $b=(a_1,\cdots,a_{n-2})$ and $y=(x_1,\cdots,x_{n-2})$, we get for any even $n\geq 2$:
 
@@
 
-%In this analysis we considered the different cases depending on the values of $a_{n-1}$ and $a_n$, but the same reasoning applies with any $a_i, a_{i+1}$ where $i$ is odd.
-
 \begin{remark}\label{rmk:dependence_dnka}
@@
 	\end{tabular}
-
 	\mycaption{Values of $\Dnka{2}{k}{a}$ for $n=2$.}\label{tab:Dnka}
@@
 	For every $k\in[1,n]$, we have by Proposition~\ref{prop:restrWT} that:
-	%\[
-	%\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x}=\Dnka{n}{k}{d},\]
-	%where $d$ is the permutation of $c$ obtained by sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions. 
 	\begin{align*}
@@
 	\[
-		\wt{f}(0_n)=\left\{\begin{array}{l l}
+		\wt{f}(0_n)=\left\{\begin{array}{ll}
 			0&\text{ if }n\equiv 0\bmod 4\\
@@
 \end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{remark}
+
 \begin{table}
@@
 	\end{tabular}
-
 	\mycaption{Values of $\Dnka{n}{k}{a}$ for small values of $k$.}\label{tab:Dnka_small_k}
@@
         \item The sum and alternating sum over $k$ of the $\Dnka nka$ are, respectively:
- %       \begin{gather*}
- %           \sum_{k=0}^n\Dnka nka=(-1)^{q}2^{n/2},\\
- %           \sum_{k=0}^n(-1)^k\Dnka nka=(-1)^{p}2^{n/2}.
- %       \end{gather*}
 		\[
@@
         \item The sum over the even and the odd $k$ of the $\Dnka nka$ are, respectively:
- %       \begin{gather*}
-  %          \sum_{k=0}^{n/2}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big),\\
-   %         \sum_{k=0}^{n/2-1}\Dnka n{2k+1}a=2^{n/2-1}\big((-1)^{q}-(-1)^{p}\big).
-    %    \end{gather*}   
 		\[
@@
 		\]
-
     \end{enumerate}
@@
 
-%\pmnote{ The point for the remark was to recall that we use the notation "$| \cdot |$" for absolute value over the complex, since before we used it only to denote "cardinal" or absolute value over integers.}
-
-%\begin{remark}
-%    Property~\ref{property:cauchy_estimate} is typically employed to bound the absolute value of complex numbers.
-Naturally, the bound remains valid when the complex number is real, as will be the case in our application.
-%\end{remark}
-
 Applying the property, we get:
@@
     \]
-    where $M$ is the maximum of $|P_a(z)|$ on the complex circle %$|z|=1$. 
-    $\dis=\{ z \in \C: |z|=1  \}$.
+    where $M$ is the maximum of $|P_a(z)|$ on the complex circle $\dis=\{ z \in \C: |z|=1  \}$.
     We claim, and prove below, that the maximum of $\left|-z^2+2z+1\right|$ on $\dis$ is $2\sqrt 2$. 
@@
 	We prove that the maximum of $\left|-z^2+2z+1\right|$ on $\dis$ is $2\sqrt 2$ by showing that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ equals $8$.
-    %It remains to prove that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ equals $8$. 
     Using that $|w|^2=w\overline w$ for every complex number $w$, we obtain for all $z\in \dis$:
@@
     \]
-    Equivalently, it holds that
-    %$\NL(f)\geq 2^{n-1} - \frac{1 + n 2^{\frac{3}{4}n}} {2}$.
-    $\NL(f)\geq 2^{n-1} - \frac{1}{2} -2^{3n/4 + \log_2(n) -1}$.
+    Equivalently, it holds that $\NL(f)\geq 2^{n-1} - \frac{1}{2} -2^{3n/4 + \log_2(n) -1}$.
 \end{Corollary}
@@
 
-\mycomment{One can also prove the following:
-
-\begin{proposition}
-    For a fixed integer $k\geq 1$ and sufficiently large $n\geq b(k)$, it holds that:
-    \[
-        \max_{a\in\F_2^n}|\Dnka nka|=|\Dnka nk{0_n}|=\left(-\frac12\right)^k\sum_{i=\lceil k/2\rceil}^{n/2}(-4)^i\binom{n/2}{i}\binom{i}{k-i}.
-    \]
-\end{proposition}
-
-Also, using the Cauchy estimate on holomorphic functions, we can prove:
-
-\begin{proposition}
-    For any real number $R>0$, we have the following bound:
-    \[
-        |\Dnka nka|\leq\frac{(M_R)^{n/2}}{R^k},
-    \]
-    where $M_R$ is the maximum of $\left|z^2-2z-1\right|$ on the complex disk $|z|=R$. Explicitly, $M_R$ can be expressed as follows:
-    \[
-        M_R=
-        \begin{cases}
-            -R^2+2R+1&\text{if $R\leq\sqrt 2-1$}\\
-            \sqrt 2\left(R^2+1\right)&\text{if $\sqrt 2-1\leq R\leq\sqrt 2+1$}\\
-            R^2+2R-1&\text{if $R\geq\sqrt 2+1$}\\
-        \end{cases}.
-    \]
-\end{proposition}
-
-\begin{remark}
-    Here are some interesting choices for $R$:
-    \begin{itemize}
-        \item Choosing $R=1/\sqrt 2$ yields that $|\Dnka nka|\leq\left(3/\sqrt 2\right)^{n/2}\cdot \sqrt 2^k$.
-        \item Choosing $R=1/2$ gives $|\Dnka nka|\leq (5\sqrt 2/4)^{n/2}\cdot 2^k$.
-        \item Choosing $R=1$ yields $|\Dnka nka|\leq (2\sqrt 2)^{n/2}$. This is particularly useful if $k$ is close to $n/2$.
-    \end{itemize}
-\end{remark}
-
-\begin{remark}
-    We can even go ahead and choose $R=R_{n,k}$ in terms of $n$ and $k$, in such a way that the upper bound of $B_{R,n,k}=(M_R)^{n/2}/R^k$ is minimized.
-To do this, consider any $1\leq k\leq n-1$.
-We can actually assume that $k\leq n/2$: if $k>n/2$, replace it by $n-k$ (recall that $|\Dnka nka|=|\Dnka n{n-k}a|$ by Proposition \ref{proposition:symmetry}).
-One can show that $B_{R,n,k}$ is minimal for the following choice of $R=R_{n,k}$:
-    \[
-        R_{n,k}=\begin{cases}
-            \frac{n-2k-\sqrt{2(n-2k)^2-n^2}}{2(n-k)}&\text{if $k\leq\frac{2-\sqrt 2}{4}\cdot n$}\\
-            \sqrt{\frac{k}{n-k}}&\text{if $k\geq\frac{2-\sqrt 2}{4}\cdot n$}
-        \end{cases}.
-    \]
-    Figure \ref{fig:cauchy_estimate} compares for $n=1\,000$ the two upper bounds we have for $|\Dnka nka|$ on a logarithmic scale: the binomial coefficient $\binom nk$ in red, and the bound $B_{R,n,k}$ with the optimally chosen $R=R_{n,k}$ in blue.
-The $x$-axis represents the values for $k$, while the $y$-axis represents the binary logarithm of the two bounds.
-In case $|k-n/2|\leq\sqrt{2}/4\cdot n$, it can be observed that the Cauchy estimate yields particularly good bounds compared to the binomial coefficients.
-In fact, in this case, we get:
-    \[
-        |\Dnka nka|\leq 2^{n/4}\sqrt{\frac{n^n}{(n-k)^{n-k}\cdot k^k}}.
-    \]
-    \begin{figure}
-        \centering
-        \includegraphics[width=7cm]{cauchy_estimate.pdf}
-
-        \mycaption{Cauchy estimate in blue vs.\ binomial coefficients in red.}
-        \label{fig:cauchy_estimate}
-    \end{figure}
-\end{remark}}
-
 \subsection{Generalization to a family of weightwise quadratic functions}\label{sec:general}
+
 In this part, we generalize the results of Section~\ref{sec:Cauchy} to all weightwise quadratic functions $f$ such that for every $k\in [1,n]$, the function $f_k$ in Definition~\ref{def:wwdegd} has exactly $t$ quadratic terms with no shared variables.
@@
 	For an even integer $n\geq 0$ and any integer $t\in[0,n/2]$, we define the Boolean function $d_{t,n}\in\BN$ by $d_{t,n}(x)=\sum_{i=1}^t x_{2i-1} x_{2i}$.
-	%	by $\Dnka{n}{k}{a}$:
-	%	\[\Dnka{n}{k}{a}= \sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a x}\]
 \end{definition}
@@
 In particular, it holds that $d_{n/2,n}(x)=d_n(x)$. 
-%We focus on the Walsh spectrum restricted to the slices of any function $d_{t,n}$:
 We now focus on the restricted Walsh transform of $d_{t,n}$:
@@
 \end{proposition}
+
 \begin{proof}
     By considering binary vectors $x\in\F_2^n$ as $x=(y,z)$ with $y\in\F_2^{2t}$ and $z\in\F_2^{n-2t}$, we get:	
-
-%	\begin{align*}
-%	\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,t}(y)+by +cz}\\
-%	&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,t}(y)+by +cz}\\
-%	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,t}(y)+by} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{cz}\right)\\
-%	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.%\qedhere
-%	\end{align*}	
-	\begin{align*}
-\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}\\&=\sum_{(y,z)\in\Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
+	\begin{align*}
+		\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}\\
+		&=\sum_{(y,z)\in\Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
+		&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
 		&=\sum_{\ell=0}^{2t}\left(\sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{2t}(y)+b \cdot y}\right)\left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c \cdot z}\right)\\&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b}\cdot\kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
 	\end{align*}
-
 \end{proof}
@@
     Then, for all $a\in\F_2^n$ and all $k\in[0,n]$, the following hold true:
-
     \[
@@
         \vspace{-4mm}
-
     	\mycaption{The curves of $\alpha\mapsto g^{(\lambda)}(\alpha)$ for the values $\lambda=\frac{i}{50}$ from $i=0$ (red) to $i=24$ (blue).}
@@
     \]
-    %This is exactly what we wanted to prove, 
     With this, we have covered the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$ entirely.
@@
     \vspace{-5mm}
-
 	\mycaption{The curve of $\lambda\mapsto\mu(\lambda)$ with $0\leq\lambda\leq\frac 12$ from Theorem~\ref{theorem:bound_D_nka_generalized}.}
@@
 
-%We have just deduced that $|\wt f(a)|\leq 1+n\cdot 2^{3n/4}$ for every Boolean vector $a\in\F_2^n$.
-This is a pessimistic bound.
-In this section, we will discuss how a tighter bound on $|\wt f(a)|$ can be obtained in polynomial time in $n$.
-
 Following Corollary~\ref{cor:bound_walsh_cauchy}, we deduce that $|\wt f(a)|\leq 1+n\cdot 2^{3n/4}$ for every even integer $n\geq 0$ and every Boolean vector $a\in\F_2^n$, where $f\in\BN$ denotes the revisited \hwbf{}.
@@
 
-%This method is based on the identity (\ref{eqn:walsh_from_D}). 
 This method is based on the identity given in Proposition~\ref{prop:WT}.
@@
 
-%\pmnote{add a link to the public github or name of the name of this code in supplementary materials.}
-
-%\tsnote{Is on GitHub now: \texttt{Bounding\_Walsh.ipynb}}
-
-%Table~\ref{table:max_walsh_vs_bound} compares $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ to the upper bound $B_n$ we find using the above method.
-Table~\ref{table:walsh_bounds} gives all values of this bound $B_n$ for all even $1\leq n\leq 80$.
-
 \bigskip
-In Table~\ref{table:max_walsh_vs_bound}, we compare the exact values of $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ for small values of $n$ (calculated using \textsf{SageMath}) to the bound $B_n$ obtained through the above method and the bound from Corollary~\ref{cor:bound_walsh_cauchy}.
+
+In Table~\ref{table:max_walsh_vs_bound}, we compare the exact values of $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ for small values of $n$ (calculated using \textsf{SageMath}) to the bound $B_n$ obtained through the above method and to the bound from Corollary~\ref{cor:bound_walsh_cauchy}.
 Additionally, Table~\ref{table:walsh_bounds} provides the values of the bound $B_n$ for all even values of $n\in[1,80]$.
@@
 	\end{tabular}
-
 	\mycaption{The actual $\max_{a\in\F_2^n}|\wt f(a)|$ compared to the bound $B_n$ and the bound from Corollary~\ref{cor:bound_walsh_cauchy}.}
@@
 	\end{minipage}
-
 	\mycaption{Approximate values of $B_n$ for various values of $n$.}
@@
 In this part, we compare the nonlinearity of the revisited \hwbf{} $f\in\BN$ to other weightwise quadratic functions considered for similar use-cases, such as the majority function, the \hwbf{} and the cyclic weightwise functions studied in~\cite{DAM:MeaOza24}.
-
-%In Figure~\ref{fig:walsh_bound_comparison} we compare the value $\max_{a\in\mathbb F_2^n}|\wt f(a)|$, the smaller the maximum the better the nonlinearity.
-We display the values for $n$ up to $80$, which is sufficient to compare the asymptotic behavior of the different bounds.
-%The violet and orange curves correspond to the upper bounds proven in~\cite{DAM:MeaOza24}.
-The violet one corresponds to the bound holding for all cyclic weightwise linear function such that $f_0(x)=b\cdot x$ with $\w(b)$ odd.
-It gives for example an upper bound for the HWBF.
-The orange one corresponds to the bound holding the cyclic weightwise quadratic function given by $f_0(x)=x_1+x_2x_3$.
-%The blue curve corresponds to both the majority and HWBF function, whose exact nonlinearity are recalled in Property~\ref{prop:wwd1}.
-We use only one curve since on a logarithmic scale the difference of nonlinearity between these two functions is too small to differentiate the curves.
-%Regarding the revisited HWBF introduced in Definition~\ref{def:revHWBF}, the red curve corresponds to the theoretical bound from Corollary~\ref{cor:bound_walsh_cauchy}, and the green one the experimental approach of Section~\ref{sec:expwt}.
 
@@
 	\includegraphics[width=10.5cm]{comparison_walsh_bound.pdf}
-
 	\mycaption{
-		%Maximum of the absolute value of the Walsh spectrum of different functions, in logarithmic scale, for even values of $n$.
-In violet and orange are the bounds for the cyclic weigtwise linear functions and one cyclic weightwise quadratic function from~\cite{DAM:MeaOza24}.
-In blue is the value for the majority function and HWBF.
-The theoretical bound (Corollary~\ref{cor:bound_walsh_cauchy}) for the function $f$ is in red and the experimental one $B_n$ (Section~\ref{sec:expwt}) is in green.}
-		%On a logarithmic scale, our experimental bound $B_n$ in terms of $n$ in red, our theoretical bound $1+n\cdot 2^{3n/4}$ from Proposition \ref{cor:bound_walsh_cauchy} in green, and the bound $\binom{n}{n/2}$ in blue.
-\tsnote{Updated plot, but the description now needs to be changed.}}
 		Bounds on the maxima of absolute values of the Walsh spectrum for various functions, shown on a logarithmic scale for even values of $n$.
@@
 		\hwbf{}   & $4$  & $20$  & $88$  &  $372$ & $1\,544$ & $6\,344$ & $25\,904$  \\  	
-   %4 10 20 44 88 186 372 772 1544 3172 6344 12952 25904
-
 		Majority   & $5$  & $22$  & $93$  &  $386$ & $1\,586$ & $6\,476$ & $26\,333$  \\
-
-		%cyclic $f_0=x_1+x_2x_3$
 		$t$~\cite{DAM:MeaOza24}   & $4$  & $22$  & $96$  &  $404$ & $1\,672$ & $6\,854$ & $27\,884$\\
-    	%4 10 22 46 96 196 404 816 1672 3358 6854 13722 27884
-
-%$f_0= x_1 + \sum_{i=1}^{n/2-1}x_{2i}x_{2i+1}$	
 		$u$~\cite{DAM:MeaOza24}   & $4$  & $24$  & $104$  &  $456$ & $1\,888$ & $7\,816$ & $31\,616$ \\
-    	%4 10 24 48 104 220 456 924 1888 3862 7816 15748 31616
-
 		Revisited \hwbf{}  & $4$  & $22$  & $102$  &  $458$ & $1\,902$ & $7\,842$ & $31\,680$\\
@@
 	\end{tabular}
-
 	\mycaption{Comparison of the nonlinearity.}
@@
 
-%\pmnote{under construction, waiting for the parameters for the FAI}
-
-%\subsection{Degree}
-
 \begin{proposition}
@@
 	\centering
-	\begin{tabular}{|c| c|c|c|c| c|c|c|}
+	\begin{tabular}{|c|c|c|c|c|c|c|c|}
 		\hline
@@
 		\hwbf{}   & $3$  & $5$  & $7$  &  $9$ & $11$ & $13$ & $15$  \\  	
-
 		Majority   & $4$  & $4$  & $8$  &  $8$ & $8$ & $8$ & $16$  \\
-
-		%cyclic $f_0=x_1+x_2x_3$
 		$t$~\cite{DAM:MeaOza24}   & $2$  & $5$  & $6$  &  $9$ & $11$ & $13$ & $14$\\
-
-		%$f_0= x_1 + \sum_{i=1}^{n/2-1}x_{2i}x_{2i+1}$	
 		$u$~\cite{DAM:MeaOza24}   & $2$  & $4$  & $6$  &  $8$ & $10$ & $12$ & $14$ \\
-
 		Revisited \hwbf{}  & $3$  & $5$  & $7$  &  $9$ & $11$ & $13$ & $15$\\
@@
 	\end{tabular}
-
 	\mycaption{Comparison of the degree.}
@@
 
-\iffalse
- \begin{table}[h!]
-	 \centering
-	 \begin{tabular}{|c|c|c|c|c|}
-		 \hline
-		 $n$ & Nonlinearity & Is Balanced & Algebraic Degree & Algebraic Immunity \\
-		 \hline
-		 2   & 1             & False       & 2               & 1                   \\
-		 4   & 4             & True        & 3               & 2                   \\
-		 6   & 22            & False       & 5               & 3                   \\
-		 8   & 102           & True        & 7               & 4                   \\
-		 10  & 458           & False       & 9               & 5                   \\
-		 12  & 1902          & True        & 11              & 6                   \\
-		 14  & 7842          & False       & 13              & 6                   \\
-		 16  & 31680         & True        & 15              & 7                   \\
-		 \hline
-		 \end{tabular}
-
-	 \mycaption{Characteristics of Boolean Functions for Different $n$ Values}
-	 \end{table}
-\fi
-
 \begin{table}
@@
 		Majority   & $2$  & $3$  & $4$  &  $5$ & $6$ & $7$ & $8$  \\
-		%cyclic $f_0=x_1+x_2x_3$
 		$t$~\cite{DAM:MeaOza24}   & $2$  & $3$  & $4$  &  $5$ & $5$ & $6$ & $7$\\
-		%$f_0= x_1 + \sum_{i=1}^{n/2-1}x_{2i}x_{2i+1}$	
 		$u$~\cite{DAM:MeaOza24}   & $2$  & $3$  & $4$  &  $5$ & $6$ & $6$ & $7$ \\					
@@
 	\end{tabular}
-
 	\mycaption{Comparison of the algebraic immunity.}
@@
 \bigskip
+
 These various results on the algebraic properties of $f$ suggest that it possesses strong resistance against standard attacks.
@@
 	\end{tabular}
-
 	\mycaption{Lowest possible values of $(d, e)$ for different values of $n$.}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \ifnum\full=0
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 	\bibliographystyle{splncs04}
 	\bibliography{add}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \else
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 	\bibliographystyle{alpha}
 	\bibliography{add}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \fi

### 2024-12-08 RevisedHiddenWeight.tex
Finalized proofreading

@@
     We relate the maximum Walsh coefficients of the revisited \hwbf{} to the coefficients of generating functions and employ complex analysis techniques to prove lower bounds on the nonlinearity of $f$.
-    Unlike most studies on Boolean functions used in cryptography, this approach yields strong nonlinearity bounds for a broader class of functions and for all even $n$.
+    Unlike most studies on Boolean functions used in cryptography, this approach yields strong nonlinearity bounds for a broader class of functions in an even number of variables.
     \item \emph{Experimental results and comparisons} (Section~\ref{sec:expAndComp}): 
@@
 Further, our intervals will only contain integers, so that for instance $[0,n]=\{0,1,\dots,n\}$.
-The set of binary vectors of length $n$ will be denoted by $\F_2^n$, with zero vector written as $0_n$.
-The canonical basis of $\F_2^n$ will be written as $\{e_1,\dots,e_n\}$; therefore, $e_i\in\F_2^n$ is the vector which is zero everywhere, except at position $i$.
+The set of binary vectors of length $n$ will be denoted by $\F_2^n$, with the zero vector written as $0_n$.
+The canonical basis of $\F_2^n$ will be written as $\{e_1,\dots,e_n\}$; therefore, $e_i\in\F_2^n$ is the vector which is zero everywhere except at position $i$.
 The entries of a binary vector $x\in\F_2^n$ will always be denoted by $x_1,\dots,x_n$.
@@
 
-In this part we recall general concepts on Boolean functions and their cryptographic properties we use in this article. 
+In this part, we recall general concepts on Boolean functions and their cryptographic properties we use in this article. 
 For a deeper introduction on Boolean functions and their cryptographic parameters, we refer to the book~\cite{Carlet20}, and to~\cite{TOSC:CarMeaRot17} for properties on slices, so-called weightwise properties.
@@
 \begin{definition}[Slice]
-    For $k \in [0,n]$, we introduce the set $\Ekn{k}{n}=\{x\in \F_2^n:\w(x)=k\}$, and call it the $k$-th slice of the Boolean hypercube (of dimension $n$). 
+    For any integer $k$, we introduce the set $\Ekn{k}{n}=\{x\in \F_2^n:\w(x)=k\}$, and call it the $k$-th slice of the Boolean hypercube (of dimension $n$); note that if $k\not\in[0,n]$, then $\Ekn kn=\varnothing$.
 \end{definition}
@@
 	A Boolean function in $n$ variables is a function from $\F_2^n$ to $\F_2$.
-The set of all Boolean functions in $n$ variables is denoted by $\BN$, and we denote this set without the null function by $\BN^*$.
+The set of all Boolean functions in $n$ variables is denoted by $\BN$, and we denote this set without the null function by~$\BN^*$.
 \end{definition}
@@
 \begin{definition}[Algebraic Normal Form, degree]\label{def:anf}
-	We call Algebraic Normal Form of a Boolean function $f\in\BN$ its unique representation as an element of the ring $\F_2[x_1,\dots,x_n]/(x_1^2+x_1,\dots,x_n^2+x_n)$, and we represent it as follows:
+	We call Algebraic Normal Form of a Boolean function $f\in\BN$ its unique representation as an element of the ring $\F_2[x_1,\dots,x_n]/(x_1^2+x_1,\dots,x_n^2+x_n)$, and we express it as follows:
 	\[
@@
     \[  \wt{f,S} (a) = \sum_{x\in S} (-1)^{f(x)+a \cdot x}.\]
-    The Walsh transform of $f$ is then defined as $\wt{f}=\wt{f,\F_2^n}$. For $k\in[0,n]$, we also set $\wt{f,k}=\wt{f,\Ekn{k}{n}}$.
+    The (unrestricted) Walsh transform of $f$ is then defined as $\wt{f}=\wt{f,\F_2^n}$. For any integer $k$, we also set $\wt{f,k}=\wt{f,\Ekn{k}{n}}$.
 \end{definition}
@@
 
-\begin{definition}[Nonlinearity, \eg{} page 79 in \cite{Carlet20}]%and weightwise nonlinearity
+\begin{definition}[Nonlinearity, \eg, page 79 in \cite{Carlet20}]%and weightwise nonlinearity
 	\label{def:nl}
@@
 Functions reaching this maximum are called bent functions.
-Due to their broad applications and importance, they have been the focus of multiple works, \eg{} \cite{Rothaus76,FSE:Dobbertin95,DBLP:conf/itw/BudaghyanCH11,Tokareva15,Mesnager16}.
+Due to their broad applications and importance, they have been the focus of multiple works, \eg, \cite{Rothaus76,FSE:Dobbertin95,DBLP:conf/itw/BudaghyanCH11,Tokareva15,Mesnager16}.
 The quadratic function $d_n\in\BN$ given by $d_n(x)=\sum_{i=1}^{n/2}x_{2i-1}x_{2i}$ is an example for such a bent function.
@@
 The algebraic degree of multiples of a Boolean function is a crucial quantity for various attacks on stream ciphers that utilize a Boolean function as a filter. 
-The well-known algebraic attack~\cite{EC:CouMei03} and fast algebraic attack~\cite{C:Courtois03} on filtered \textsf{LFSR}s have motivated the study of cryptographic properties such as algebraic immunity and fast algebraic immunity, investigated in numerous works, \eg{} \cite{FSE:Armknecht04,C:HawRos04,ISC:JiaZhaWan13})).
+The well-known algebraic attack~\cite{EC:CouMei03} and fast algebraic attack~\cite{C:Courtois03} on filtered \textsf{LFSR}s have motivated the study of cryptographic properties such as algebraic immunity and fast algebraic immunity, \eg, \cite{FSE:Armknecht04,C:HawRos04,ISC:JiaZhaWan13}.
 Nowadays, these parameters are systematically determined for any function considered as a filter.
@@
 
-\begin{definition}[Fast algebraic immunity, \eg{} \cite{EC:ACGKMR06}]\label{def:FAI}
+\begin{definition}[Fast algebraic immunity, \eg, \cite{EC:ACGKMR06}]\label{def:FAI}
 	The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined as:
@@
 
-\subsection{Symmetric Functions, \hwbf{} and weightwise degree-d functions}
+\subsection{Symmetric Functions, \hwbf{} and weightwise degree-$d$ functions}
 
 Recall that the Boolean symmetric functions in $n$ variables are those that are constant on the slice $\Ekn{k}{n}$ for every $k\in [0,n]$. 
-This class of functions has been thoroughly studied in the context of cryptography, see \eg{} \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,IEEE:CheLu11,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
+This class of functions has been thoroughly studied in the context of cryptography, see \eg, \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,IEEE:CheLu11,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
 In this article, the symmetric functions that we consider will mainly be the slice indicator function and the majority function.
@@
 
-Various weightwise affine functions (\ie{} belonging to $\WD{1}{n}$) have been exhibited, such as in~\cite{TOSC:CarMeaRot17} where the bent functions in Propositions $1$ and $2$ are weightwise affine, or in~\cite{DAM:GinMea22} to show than no weightwise perfectly balanced function is weightwise affine for $n\geq 8$.
-The arguably best known example of weightwise affine function is the hidden weight bit function introduced in~\cite{IEEE:Bryant91}, the one obtained by fixing $f_0=0$ and $f_k=x_k$ for $k \in [1,n]$.
+Various weightwise affine functions (\ie, belonging to $\WD{1}{n}$) have been exhibited, such as in~\cite{TOSC:CarMeaRot17} where the bent functions in Propositions $1$ and $2$ are weightwise affine, or in~\cite{DAM:GinMea22} to show than no weightwise perfectly balanced function is weightwise affine for $n\geq 8$.
+The arguably best known example of weightwise affine function is the Hidden Weight Bit Function introduced in~\cite{IEEE:Bryant91}, the one obtained by fixing $f_0=0$ and $f_k=x_k$ for $k \in [1,n]$.
 The cryptographic properties of this function have been studied in~\cite{DAM:WCST14}, showing good algebraic properties for this function.
@@
 \begin{definition}[Hidden Weight Bit Function]\label{def:hwbf}
-    We call Hidden Weight Bit Function (\hwbf{}) the Boolean function $h\in\BN$ defined by:
-	\[h(x)= \left\{ 
-	\begin{array}{l l}
-		0 & \quad \text{ if } \w(x) =0, \\
-		x_k & \quad \text{ if } \w(x)=k.
-	\end{array} \right. \] 
+    We call Hidden Weight Bit Function (\hwbf{}) the Boolean function $h\in\BN$ defined as:
+	\[
+		h(x)=\sum_{k=1}^{n}x_k\phikn{k}{n}(x).
+	\]
 \end{definition}
@@
 	\begin{itemize}
-		\item (\eg{} Theorem $3$ in~\cite{DCC:DalMaiSar06}) The majority function $\mathsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
+		\item (\eg, Theorem $3$ in~\cite{DCC:DalMaiSar06}) The majority function $\mathsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
 		\[
@@
 		\]	
-		\item (Theorem $1$ in \cite{DAM:WCST14}) The \hwbf{} $h$ introduced in Definition~\ref{def:hwbf} satisfies $\degg(h)=n-1$ for all $n\geq 4$.
+		\item (Theorem $1$ in \cite{DAM:WCST14}) The \hwbf{} $h$ introduced in Definition~\ref{def:hwbf} satisfies $\degg(h)=n-1$ if $n\geq 4$.
 	\end{itemize}
@@
 
-We use Krawtchouk polynomials and some of their properties to prove one of our main results. We give the necessary definition here and refer to \eg{}~\cite{book:MacSlo78} for more details.
+We use Krawtchouk polynomials and some of their properties to prove one of our main results. We give the necessary definition here and refer to \cite{book:MacSlo78} for more details, for instance.
 
 \begin{definition}[Krawtchouk polynomials]\label{def:Kraw}
-	The $n$-th Krawtchouk polynomial of degree $k\in[0,n]$ is given by:
+	The $n$-th Krawtchouk polynomial of degree $k\in\Z$ is given by:
     \[
@@
     \]
-    If $k<0$, we further define $\kraw{k}{x}{n}=0$.
     The Krawtchouk polynomials can alternatively be characterized as the coefficients in the generating function for $(1+z)^{n-x} (1-z)^x$ in the variable $z$:
@@
 	\[
-		f(x)=\sum_{i=1}^{n/2}(x_i+1) x_{i+\frac{n}{2}} + \sum_{k=1}^nx_k\phikn{k}{n}(x).
+		f(x)=\sum_{k=1}^nx_k\phikn{k}{n}(x)+\sum_{i=1}^{n/2}(x_i+1) x_{i+n/2}.
 	\]
@@
 	Let $n\geq 0$ be an even integer, and let $f\in\BN$ be the revisited \hwbf{}.
-Consider any binary vector $a\in\F_2^n$, and define $c=a+e_k+\sum_{i=n/2+1}^n e_i$.
+Consider any binary vector $a\in\F_2^n$ and any integer $k\in[1,n]$.
+Define $c=a+e_k+\sum_{i=n/2+1}^n e_i$.
 Then the restricted Walsh transform of $f$ satisfies:
@@
 
-Accordingly, we can study the restricted Walsh transform of the revisited \hwbf{} by analyzing the one of the following Boolean function $d_n\in\BN$:
+Accordingly, we can study the restricted Walsh transform of the revisited \hwbf{} by analyzing the one of the following Boolean function $d_n\in\BN$.
 
 \begin{definition}
-Let $n\geq 0$ be an even integer.
-Then we define the Boolean function $d_n\in\BN$ by $d_n(x)=\sum_{i=1}^{n/2}x_{2i-1}x_{2i}$.
-Further, for an integer $k$ and a binary vector $a\in\F_2^n$, we define $\Dnka{n}{k}{a}=0$ if $n\not\in[0,n]$, and otherwise:
-\[
-    \Dnka{n}{k}{a}=\sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a\cdot x}.
-\]
-\end{definition}
-
-The $\Dnka{n}{k}{a}$ satisfy a recursive relation:
+	Let $n\geq 0$ be an even integer. Then we define the Boolean function $d_n\in\BN$ by:
+	\[
+		d_n(x)=\sum_{i=1}^{n/2}x_{2i-1}x_{2i}.
+	\]
+	Further, for an integer $k$ and a binary vector $a\in\F_2^n$, we define:
+	\[
+		\Dnka{n}{k}{a}=\wtk{d_n}{k}(a)=\sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a\cdot x}.
+	\]
+\end{definition}
+
+The $\Dnka{n}{k}{a}$ satisfy a recursive relation.
 
 \begin{proposition}\label{prop:recursiveDnka}
-Let $n\geq 0$ be an even integer. Then for all $k\in[0,n]$ and $a\in\F_2^n$, the following hold true:
+Let $n\geq 0$ be an even integer. Then for all integers $k$ and all binary vectors $a\in\F_2^n$, the following hold true:
 	\begin{itemize}
@@
 \begin{proof}
-    We have that $\Dnka 00a=(-1)^0=0$ since $\Ekn 00=\{\epsilon\}$ for the empty vector $\epsilon\in\F_2^0$.
-That $\Dnka 0ka=0$ if $k\neq 0$ follows directly from the definition.
+    We have that $\Dnka 00a=(-1)^0=1$ since $\Ekn 00=\{\varepsilon\}$ for the empty vector $\varepsilon=a\in\F_2^0$.
+That $\Dnka 0ka=0$ if $k\neq 0$ follows from $\Ekn k0$ being empty if $k\neq 0$.
 Assume now that $n\geq 2$.
@@
 	\begin{itemize}
-		\item if $a_{n-1}=0=a_n$, then $\Dnka{n}{k}{a}=\Dnka{n}{k}{b}+2\Dnka{n}{k-1}{b}-\Dnka{n}{k-2}{b}$,
-		\item if $a_{n-1} \ne a_n$, then $\Dnka{n}{k}{a}=\Dnka{n}{k}{b}+\Dnka{n}{k-2}{b}$,
-		\item if $a_{n-1}=1=a_n$, then $\Dnka{n}{k}{a}=\Dnka{n}{k}{b}-2\Dnka{n}{k-1}{b}-\Dnka{n}{k-2}{b}$.
+		\item if $a_{n-1}=0=a_n$, then $\Dnka{n}{k}{a}=\Dnka{n-2}{k}{b}+2\Dnka{n-2}{k-1}{b}-\Dnka{n-2}{k-2}{b}$,
+		\item if $a_{n-1} \ne a_n$, then $\Dnka{n}{k}{a}=\Dnka{n-2}{k}{b}+\Dnka{n-2}{k-2}{b}$,
+		\item if $a_{n-1}=1=a_n$, then $\Dnka{n}{k}{a}=\Dnka{n-2}{k}{b}-2\Dnka{n-2}{k-1}{b}-\Dnka{n-2}{k-2}{b}$.
 	\end{itemize}
@@
     The recursive formula of Proposition~\ref{prop:recursiveDnka} gives different cases depending on the values of the pair $(a_{n-1},a_n)$.
-However, the same reasoning applies with any pair of the form $(a_{2i-1}, a_{2i})$ for $i\in[0,n/2]$.
+However, the same reasoning applies with any pair of the form $(a_{2i-1}, a_{2i})$ for $i\in[1,n/2]$.
 Therefore, the value of $\Dnka{n}{k}{a}$ depends only on the number of pairs $(a_{2i-1}, a_{2i})$ in $a$ being $(0,0)$, $(1,1)$, $(0,1)$ or $(1,0)$.
@@
 These values together with Proposition~\ref{prop:recursiveDnka} are sufficient to determine any $\Dnka{n}{k}{a}$.
-We will get back to this in Remark~\ref{rmk:Dnka_dep_pqr}.
 \end{remark}
 
-\begin{table}
+\begin{table}[ht]
 	\small
@@
 	\end{tabular}
-	\mycaption{Values of $\Dnka{2}{k}{a}$ for $n=2$.}\label{tab:Dnka}
+	\mycaption{Values of $\Dnka{2}{k}{a}$.}\label{tab:Dnka}
 \end{table}
 
-In the following, we show how the Walsh transform of $f$ can be written in terms of the $\Dnka{n}{k}{a}$.
-Then, in Section~\ref{sec:balancedness} we use Proposition~\ref{prop:recursiveDnka} to determine the balancedness of $f$, and in Section~\ref{sec:genfunc} we study the value of $\Dnka{n}{k}{a}$ using generating functions.
+In the following, we show how the Walsh transform of the revisited \hwbf{} $f\in\BN$ can be written in terms of the $\Dnka{n}{k}{a}$.
+Then, in Section~\ref{sec:balancedness}, we use Proposition~\ref{prop:recursiveDnka} to determine the balancedness of $f$, and in Section~\ref{sec:genfunc} we study the value of $\Dnka{n}{k}{a}$ using generating functions.
 
@@
 Denote by $\pi:[1,n]\to[1,n]$ the permutation sending the first $n/2$ elements to the odd positions and the $n/2$ last ones to the even positions.
-Let $a\in\F_2^n$ be a binary vector, and let $b=\pi^{-1}(a)+(0,1,0,1,\ldots,0,1)$.
+Let $a\in\F_2^n$ be a binary vector, and let $b=\pi^{-1}(a)+\sum_{i=1}^{n/2}e_{2i}$.
 Then the following holds true:
@@
 	\begin{align*}
-		\wt{f}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+a\cdot x}\\
+		\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+a\cdot x}\\
 		&=\sum_{\pi(x) \in \Ekn{k}{n}} (-1)^{f(\pi(x))+a \cdot \pi(x)}\\
@@
 	\end{align*}
-	We conclude by applying $\wtk{f}{k}(a)=1+\sum_{k=1}^n\wtk{f}{k}(a)$.
+	We conclude by applying $\wt{f}(a)=1+\sum_{k=1}^n\wtk{f}{k}(a)$.
 \end{proof}
@@
 
-In this part, we determine for which values of $n$ the function $f$ is balanced, using the expression of its Walsh transform in terms of $\Dnka{n}{k}{a}$ and the recursive relation of these quantities.
+In this part, we determine for which values of $n$ the revisited \hwbf{} $f\in\BN$ is balanced, using the expression of its Walsh transform in terms of the $\Dnka{n}{k}{a}$ and the recursive relation of these quantities.
 
@@
 		\wt{f}(0_n)=\left\{\begin{array}{ll}
-			0&\text{ if }n\equiv 0\bmod 4\\
+			0&\text{ if }n\equiv 0\bmod 4,\\
 			-2\binom{(n-2)/2}{(n-2)/4}&\text{ if }n\equiv 2\bmod 4.\\
@@
 \begin{proof}
-	Applying Remark~\ref{rmk:dependence_dnka} and that $\pi^{-1}(0_n)=0_n$,
-	Proposition~\ref{prop:WT} gives:
+	We use Proposition~\ref{prop:WT}, applying Remark~\ref{rmk:dependence_dnka} and that $\pi^{-1}(0_n)=0_n$:
 	\begin{align*}
@@
 	\end{align*}
-	Similarly, we get:
-	\[
-		\Dnka{n}{k}{0,0,0,1,\ldots,0,1}=\binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}.\\
-	\]
-	Combining both, we obtain:
+	We similarly get $\Dnka{n}{k}{0,0,0,1,\ldots,0,1}=\binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}$. Then, combining both, we obtain:
 	\begin{align*}
@@
 
-\section{Extensive study of $\Dnka nka$ and bounds on the Walsh spectrum of $f$}\label{sec:dnk}
+\section{Extensive study of the $\Dnka nka$ and bounds on the Walsh spectrum of $f$}\label{sec:dnk}
 
@@
 To begin, in Section~\ref{sec:genfunc}, we determine essential characteristics of these values.
-Subsequently, in Section~\ref{sec:Cauchy}, we employ Cauchy's estimate to bound the absolute values of $\Dnka nka$.
-This approach allows us to also bound the absolute values of the Walsh transform coefficients of the revisited \hwbf{}, thereby constraining the nonlinearity.
+Subsequently, in Section~\ref{sec:Cauchy}, we employ Cauchy's estimate to bound the absolute value of the $\Dnka nka$.
+This approach allows us to also bound the absolute value of the Walsh transform of the revisited \hwbf{}, thereby constraining the nonlinearity.
 Lastly, in Section~\ref{sec:general}, we illustrate how this result can be extended to bound the nonlinearity of a family of weightwise quadratic functions.
 
-\subsection{Study of $\Dnka nka$ through generating functions}\label{sec:genfunc}
+\subsection{Study of the $\Dnka nka$ through generating functions}\label{sec:genfunc}
 
@@
 	We proceed by induction on even $n\geq 0$. 
-	For the base case $n=0$, for $a\in\F_2^0$ (the empty vector), we have $P_a(z)=1$, while $\Dnka 00a=1$ and $\Dnka 0ka=0$ if $k\neq 0$ (from Proposition~\ref{prop:recursiveDnka}). 
-	For the inductive step, let $n\geq 2$ be even, and assume that the corresponding formula holds for $n-2$. Using the recursive formula for $\Dnka nka$ with the notation $a=(b,a_{n-1},a_n)$, we have:
+	For the base case $n=0$, we consider the empty vector $a=\varepsilon\in\F_2^0$; it satisfies $P_a(z)=1$, while $\Dnka 00a=1$ and $\Dnka 0ka=0$ if $k\neq 0$ by Proposition~\ref{prop:recursiveDnka}. 
+	For the inductive step, let $n\geq 2$ be even, and assume that the corresponding formula holds for $n-2$.
+Using the recursive formula for $\Dnka nka$ from Proposition~\ref{prop:recursiveDnka} with $b=(a_1,\dots,a_{n-2})\in\F_2^{n-2}$, we have:
 	\begin{align*}
@@
 This observation can also be obtained from Proposition~\ref{proposition:generating_fct}: since $P_a(z)$ only depends on $p(a)$, $q(a)$ and $r(a)$ (by definition), we deduce that also $\Dnka nka$ only depends on $p(a)$, $q(a)$ and $r(a)$.
-Therefore, for any $p,q,r\geq0$ satisfying $p+q+r=n/2$, it makes sense to introduce the notation $\mathsf D_{n,k}^{p,q,r}=\Dnka nka$, where $a\in\mathbb F_2^n$ is any vector with $(p(a),q(a),r(a))=(p,q,r)$.
-We will make use of this notation later on.
+Therefore, for any $p,q,r\geq0$ satisfying $p+q+r=n/2$, it makes sense to introduce the notation $\mathsf D_{k,n}^{p,q,r}=\Dnka nka$, where $a\in\mathbb F_2^n$ is any vector with $(p(a),q(a),r(a))=(p,q,r)$.
+We will make use of this notation in Section~\ref{sec:expwt}.
 \end{remark}
@@
 \begin{proof}
-	We define the reverse polynomial  $Q_a(z)$ as the degree $n$ polynomial where each coefficient of $z^k$ in $Q_a(z)$ is equal to the coefficient of $z^{n-k}$ in $P_a(z)$. 
+	We define the reverse polynomial  $Q_a(z)$ as the degree $n$ polynomial where each coefficient of $z^k$ in $Q_a(z)$, for any $k$, is equal to the coefficient of $z^{n-k}$ in $P_a(z)$. 
 	Then we have:
@@
 
-Another immediate case for zero coefficients is the following:
+Another immediate case for zero coefficients is the following.
 
@@
 
-\begin{table}
+\begin{table}[ht]
 	\small
@@
 		\hline
-		$k$ & $\Dnka nka$\\ \hline
+		$k$ & $\Dnka 2ka$\\ \hline
 		$0$&$1$\\
@@
 	\end{tabular}
-	\mycaption{Values of $\Dnka{n}{k}{a}$ for small values of $k$.}\label{tab:Dnka_small_k}
+	\mycaption{Values of $\Dnka{2}{k}{a}$ for small values of $k$.}\label{tab:Dnka_small_k}
 \end{table}
 
-From differentiation, we can get more cases in which $\Dnka nka=0$:
+From differentiation, we can get more cases in which $\Dnka nka=0$.
 
@@
 This checking can be autotomized by a computer algebra system.
+	\ifnum\anon=0
 		For this, we refer to the corresponding \textsf{SageMath} implementation, accessible via this link: \url{https://github.com/se-tim/Revisited-HWBF.git}.
+	\fi
 \end{proof}
@@
 
-Using Proposition \ref{proposition:generating_fct}, we can also deduce some sums involving the $\Dnka nka$:
+Using Proposition \ref{proposition:generating_fct}, we can also deduce some sums involving the $\Dnka nka$.
 
@@
     \end{enumerate}
-
 \end{proposition}
@@
 
-We recall Cauchy's estimate on holomorphic functions:
-
-\begin{Prop}[Cauchy's estimate, \eg{} Theorem 10.26 in~\cite{rudin1987}]\label{property:cauchy_estimate}
+We recall Cauchy's estimate on holomorphic functions.
+
+\begin{Prop}[Cauchy's estimate, \eg, Theorem 10.26 in~\cite{rudin1987}]\label{property:cauchy_estimate}
     Let $w$ be a complex number, and let $R>0$ be some radius.
-Let $f$ be a holomorphic function defined on an open set containing every complex number $z$ satisfying $|z-w|\leq R$, and let $M_R$ be the maximum of the absolute value of $f$ on the circle defined by $|z-w|=R$.
+Let $D\subseteq\C$ be a set containing every complex number $z$ satisfying $|z-w|\leq R$.
+Let $f:D\to\C$ be a holomorphic function, and let $M_R$ be the maximum of the absolute value of $f$ on the circle defined by $|z-w|=R$.
 Then for every integer $k\geq 0$, the $k$-th derivative of $f$ evaluated at $w$ can be bounded, in absolute value, as follows:
@@
 \end{Prop}
-
-Applying the property, we get:
 
@@
 
-	We prove that the maximum of $\left|-z^2+2z+1\right|$ on $\dis$ is $2\sqrt 2$ by showing that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ equals $8$.
+	We prove that the maximum of $|-z^2+2z+1|$ on $\dis$ is $2\sqrt 2$ by showing that the one of $|-z^2+2z+1|^2$ on $\dis$ equals $8$.
     Using that $|w|^2=w\overline w$ for every complex number $w$, we obtain for all $z\in \dis$:
@@
     \]
-    Since the minimum of $\mathrm{Re}\left(z^2\right)$ on $\dis$ is $-1$, we conclude that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ is $6-2(-1)=8$.
+    Since the minimum of $\mathrm{Re}\left(z^2\right)$ on $\dis$ is $-1$, we conclude that the maximum of $|-z^2+2z+1|^2$ on $\dis$ is $6-2(-1)=8$.
 \end{proof}
@@
 \begin{definition}
-	For an even integer $n\geq 0$ and any integer $t\in[0,n/2]$, we define the Boolean function $d_{t,n}\in\BN$ by $d_{t,n}(x)=\sum_{i=1}^t x_{2i-1} x_{2i}$.
-\end{definition}
-
-In particular, it holds that $d_{n/2,n}(x)=d_n(x)$. 
-We now focus on the restricted Walsh transform of $d_{t,n}$:
+	For an even integer $n\geq 0$ and an integer $t\in[0,n/2]$, we define the Boolean function $d_{t,n}\in\BN$ by:
+	\[
+		d_{t,n}(x)=\sum_{i=1}^t x_{2i-1} x_{2i}.
+	\]
+	Further, for an integer $k$ and a binary vector $a\in\F_2^n$, we define:
+	\[
+		\Dtkna{t}{k}{n}{a}=\wtk{d_{t,n}}{k}(a)=\sum_{x\in \Ekn{k}{n}} (-1)^{d_{t,n}(x) +a\cdot x}.
+	\]
+\end{definition}
+
+In particular, it holds that $d_{n/2,n}(x)=d_n(x)$ and $\Dtkna{n/2}{k}{n}{a}=\Dkna kna$.
+We now focus on the $\Dtkna{t}{k}{n}{a}$.
 
@@
 Let $a\in\F_2^n$ be a binary vector, and write $a=(b,c)$ with $b\in\F_2^{2t}$ and $c\in\F_2^{n-2t}$.
-Then the following holds for all $k\in [0,n]$:
-	\[\wtk{d_{t,n}}{k}(a)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b}\cdot\kraw{k-\ell}{\w(c)}{n-2t}.\]
+Then the following holds for all integers $k$:
+	\[
+		\Dtkna{t}{k}{n}{a}=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b}\cdot\kraw{k-\ell}{\w(c)}{n-2t}.
+	\]
 \end{proposition}
@@
 	\begin{align*}
-		\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}\\
+		\Dtkna{t}{k}{n}{a}&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}\\
 		&=\sum_{(y,z)\in\Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
@@
 Let $a=(b,c)\in\F_2^n$ be a binary vector with $b\in\F_2^{2t}$ and $c\in\F_2^{n-2t}$.
-By letting $u=u_t(a)=n-2t-\w(c)$ and $v=v_t(a)=\w(c)$, we introduce the polynomial $P_{a,t}(z)$ given by the following expression:
-    \[
-        P_{a,t}(z)=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.
+By letting $u=u_t(a)=n-2t-\w(c)$ and $v=v_t(a)=\w(c)$, we introduce the polynomial $P_{t,a}(z)$ given by the following expression:
+    \[
+        P_{t,a}(z)=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.
     \]
@@
     \[
-        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k=P_{a,t}(z).
+        \sum_{k\in\Z}\Dtkna{t}{k}{n}{a}z^k=P_{t,a}(z).
     \]
@@
     \begin{align*}
-        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k&=\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\sum_{k\in\Z}\kraw{k-\ell}{\w(c)}{n-2t}z^{k-\ell}\\
+        \sum_{k\in\Z}\Dtkna{t}{k}{n}{a}z^k&=\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\sum_{k\in\Z}\kraw{k-\ell}{\w(c)}{n-2t}z^{k-\ell}\\
         &=\left(\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\right)\cdot(1+z)^u\cdot(1-z)^v\\
         &=P_b(z)\cdot(1+z)^u\cdot(1-z)^v\\
-        &=P_{a,t}(z).\qedhere
-    \end{align*}
-\end{proof}
-
-With this, we prove a generalization of Theorem~\ref{theorem:bound_D_nka} below. Before that, we still require a technical preliminary result:
+        &=P_{t,a}(z).\qedhere
+    \end{align*}
+\end{proof}
+
+With this, we prove a generalization of Theorem~\ref{theorem:bound_D_nka} below. Before that, we still require a technical preliminary result.
 
@@
     Let $N\geq 1$ be an integer and $D\subseteq\C$ a set of complex numbers.
-For every $i\in[1,N]$, consider an integer $m_i\geq 0$ as well as complex functions $f_{i,1},\dots,f_{i,k_i}$ defined on the set $D$.
+For every $i\in[1,N]$, consider integers $m_i\geq 0$ and $k_i\geq 1$, as well as complex functions $f_{i,1},\dots,f_{i,k_i}:D\to\C$.
 Assume that the following maximum exists (which holds for instance if the functions $f_{i,j}$ are continuous and $D$ is topologically compact):
@@
     \]
-    Then, for all $a\in\F_2^n$ and all $k\in[0,n]$, the following hold true:
-    \[
-        |\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n}\quad \text{and} \quad  |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}.
+    Then, for all $a\in\F_2^n$ and all $k\in[0,n]$, the following hold:
+    \[
+        |\Dtkna tkna|\leq 2^{\mu n}\quad \text{and} \quad  |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}.
     \]
@@
 \begin{proof}
-    To begin, we observe that the inequality $|\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}$ will follow from the inequality $|\wtk{d_{t,n}}{k}(a)|\leq 2^{\mu n}$ using precisely the arguments of the proof of Corollary~\ref{cor:bound_walsh_cauchy}, so that we are only required to prove the first inequality.
+    To begin, we observe that the inequality $|\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}$ will follow from the inequality $|\Dtkna tkna|\leq 2^{\mu n}$ using precisely the arguments of the proof of Corollary~\ref{cor:bound_walsh_cauchy}, so that we are only required to prove the first inequality.
 Also, since the case $\lambda=1/2$ corresponds to Theorem~\ref{theorem:bound_D_nka}, we will henceforth assume $\lambda<1/2$.
 
-    As before (in the proof of Theorem~\ref{theorem:bound_D_nka}), we want to bound the maximum of $|P_{a,t}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[0,n]$.
+    Similarly to the proof of Theorem~\ref{theorem:bound_D_nka}, we want to bound the maximum of $|P_{t,a}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\Dtkna tkna|$ for every $k\in[0,n]$.
     We write $a=(b,c)$ with $b\in\F_2^{2t}$ and $c\in\F_2^{n-2t}$, and define $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}.    
-	To find a bound for $|P_{a,t}(z)|$ on $\dis$ that applies to all $a\in\F_2^n$, we would like to bound the quantity $\max_{a\in\F_2^n,z\in\dis}|P_{a,t}(z)|$.
+	To find a bound for $|P_{t,a}(z)|$ on $\dis$ that applies to all $a\in\F_2^n$, we would like to bound the quantity $\max_{a\in\F_2^n,z\in\dis}|P_{t,a}(z)|$.
 Moving through all $a\in\F_2^n$ is equivalent to moving through all tuples $(p,q,r;u,v)$ of non-negative integers which satisfy $p+q+r=t$ and $u+v=n-2t$.
@@
     \end{gather*}
-    Since replacing $(p,q)$ and $(u,v)$ by $(q,p)$ and $(v,u)$ has the same effect as replacing $z$ by $-z$ in $P_{a,t}(z)$ and therefore does not change the maximum of $|P_{a,t}(z)|$ on $\dis$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
+    Since simultaneously replacing $(p,q)$ by $(q,p)$ and $(u,v)$ by $(v,u)$ has the same effect as replacing $z$ by $-z$ in $P_{t,a}(z)$ and therefore does not change the maximum of $|P_{t,a}(z)|$ on $\dis$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
     \[
@@
     \]
-    Let us start by bounding $|P_{a,t}(z)|$ on $\dis$ in the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $t=\lambda n$, we can write:
-    \[
-        P_{a,t}(z)=\left((-z^2+2z+1)^{\lambda}(1+z)^{1-2\lambda}\right)^n.
-    \]
-    Further writing $z=\ee^{\ii\alpha}$ and $z^2=\ee^{2\ii\alpha}$ for $\alpha\in[-\pi,\pi]$, and using that $|w|^2=w\overline w$ for every complex number $w$, we get:
+
+    Let us start by bounding $|P_{t,a}(z)|$ on $\dis$ in the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $t=\lambda n$, we can write:
+    \[
+        P_{t,a}(z)=\left((-z^2+2z+1)^{\lambda}(1+z)^{1-2\lambda}\right)^n.
+    \]
+    Writing $z=\ee^{\ii\alpha}$ and $z^2=\ee^{2\ii\alpha}$ for $\alpha\in[-\pi,\pi]$, and using that $|w|^2=w\overline w$ for every complex number $w$, we get:
     \begin{align*}
@@
     \[
-        |P_{a,t}(z)|^2=\left(\left|-z^2+2z+1\right|^{2\lambda}|1+z|^{2(1-2\lambda)}\right)^n=\left((6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}\right)^n.
-    \]
-
-    The goal will be to prove that the maximum of $g^{(\lambda)}(\alpha)=g(\alpha)=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{a,t}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$.
-Since $g$ is an even function, it is enough to focus on the interval $\alpha\in[0,\pi]$; the function $g$ is represented for several values of $0\leq\lambda<1/2$ in Figure~\ref{fig:family_curves_g}.
-
-    \begin{figure}
-    	\centering
-    	\includegraphics[width=11cm]{family_curves_g.pdf}
+        |P_{t,a}(z)|^2=\left(\left|-z^2+2z+1\right|^{2\lambda}|1+z|^{2(1-2\lambda)}\right)^n=\left((6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}\right)^n.
+    \]
+
+    The goal will be to prove that the maximum of $g(\alpha)=g^{(\lambda)}(\alpha)=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{t,a}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$.
+Note that $g$ is an even function, so it is enough to focus on the interval $\alpha\in[0,\pi]$; the function $g$ is represented for several values of $0\leq\lambda<1/2$ in Figure~\ref{fig:family_curves_g}.
+
+    \begin{figure}[ht]
+    	\centering
+    	\includegraphics[width=10cm]{family_curves_g.pdf}
         \vspace{-4mm}
@@
     The only interesting zeros of $\frac{\dd}{\dd\alpha}g(\alpha)$ are those of the last factor 
-    $\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2$: those of the factor $8g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}$ will make $g(\alpha)$ vanish and will therefore not maximize $g(\alpha)$, and those for $\sin\alpha$ are $\alpha=0$ and $\alpha=\pi$, with corresponding values $g(0)=2^{2-2\lambda}$ and $g(\pi)=0$.
+    $\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2$: the factor $8g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}$ has none, and those for $\sin\alpha$ are $\alpha=0$ and $\alpha=\pi$, with corresponding values $g(0)=2^{2-2\lambda}$ and $g(\pi)=0$.
 
@@
 
-    We can exclude the solution $\cos\alpha=-\lambda-\sqrt{\lambda^2-4\lambda+2}$ since $\cos\alpha\in[-1,1]$ (and $\lambda\in [0,1/2)$). 
+    We can exclude the solution $\cos\alpha=-\lambda-\sqrt{\lambda^2-4\lambda+2}$ since $\cos\alpha\in[-1,1]$ and $\lambda\in [0,1/2)$. 
     The other solution needs to be excluded for the same reason if $\lambda<1/6$.
@@
     With this, we have covered the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$ entirely.
-In a similar fashion, it can be proven that $|P_{a,t}(z)|$ is also bounded by $2^{\mu n}$ on $\dis$ for the remaining two cases of $(p,q,r;u,v)$.
+Similarly, it can be proven that $|P_{t,a}(z)|$ is also bounded by $2^{\mu n}$ on $\dis$ for the remaining two cases of $(p,q,r;u,v)$.
 In fact, for $(p,q,r;u,v)=(0,t,0;n-2t,0)$, one can proceed in exactly the same way, and for $(p,q,r;u,v)=(0,0,t;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h(\alpha)=(2+2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$, whose maximum is bounded by the maximum of $g(\alpha)$ because $0\leq h(\alpha)\leq g(\alpha)$.
@@
 The curve of $\lambda\mapsto\mu(\lambda)$ defined in the above Theorem~\ref{theorem:bound_D_nka_generalized} is represented in Figure~\ref{fig:curve_exponents_lambda_mu}.
-
-\begin{figure}
+Observe that $\mu(1/2)=3/4$, which corresponds to Theorem~\ref{theorem:bound_D_nka}.
+
+\begin{figure}[ht]
 	\centering
@@
 In this section, we establish a tighter bound on the absolute value of the Walsh transform of the revisited \hwbf{} for even $n\in[1,80]$. 
-We then compare the nonlinearity of this function to that of other functions suited to similar use cases, such as the \hwbf{} or weightwise cyclic functions from~\cite{DAM:MeaOza24}.
+We then compare the nonlinearity of this function to that of other functions suited to similar use cases, such as the \hwbf{} or the weightwise cyclic functions from~\cite{DAM:MeaOza24}.
 
@@
 
-Following Corollary~\ref{cor:bound_walsh_cauchy}, we deduce that $|\wt f(a)|\leq 1+n\cdot 2^{3n/4}$ for every even integer $n\geq 0$ and every Boolean vector $a\in\F_2^n$, where $f\in\BN$ denotes the revisited \hwbf{}.
-This is a pessimistic bound.
+Following Corollary~\ref{cor:bound_walsh_cauchy}, we deduce that $|\wt f(a)|\leq 1+n\cdot 2^{3n/4}$ for every even integer $n\geq 0$ and every binary vector $a\in\F_2^n$, where $f\in\BN$ denotes the revisited \hwbf{}.
+This is a somewhat pessimistic bound.
 In this part, we discuss how a tighter bound on $|\wt f(a)|$ can be obtained in polynomial time in $n$.
@@
 \[
-	B_k^{p,q,r}=\mathsf D_{n,k}^{p+\alpha_k,q+\beta_k,r+\gamma_k}+\mathsf D_{n,k+n/2}^{p+\alpha_k',q+\beta_k',r+\gamma_k'}.
+	B_k^{p,q,r}=\mathsf D_{k,n}^{p+\alpha_k,q+\beta_k,r+\gamma_k}+\mathsf D_{k+n/2,n}^{p+\alpha_k',q+\beta_k',r+\gamma_k'}.
 \]
@@
 
-Under the assumption that the values of $\mathsf{D}_{n,k}^{p,q,r}$ have already been computed for all $k\in[1,n]$ and for all triplets $(p,q,r)$ satisfying $p+q+r=n/2$, the bound in equation (\ref{eqn:bound_walsh}) can be determined with a computational complexity of $\mathcal{O}(n^3)$.
+Under the assumption that the values of $\mathsf{D}_{k,n}^{p,q,r}$ have already been computed for all $k\in[1,n]$ and for all triplets $(p,q,r)$ satisfying $p+q+r=n/2$, the bound in equation (\ref{eqn:bound_walsh}) can be determined with a computational complexity of $\mathcal{O}(n^3)$.
 This is because there are $\mathcal{O}(n^2)$ possible triplets $(p,q,r)$ that meet the condition $p+q+r=n/2$, and the summation itself can be computed in $\mathcal{O}(n)$ steps.
 
-We consider now the complexity involved in computing the values of $\mathsf{D}_{n,k}^{p,q,r}$ for all $k\in[1,n]$ and all triplets $(p,q,r)$ satisfying $p+q+r=n/2$.
+We consider now the complexity involved in computing the values of $\mathsf{D}_{k,n}^{p,q,r}$ for all $k\in[1,n]$ and all triplets $(p,q,r)$ satisfying $p+q+r=n/2$.
 We claim that this computation has a complexity of $\mathcal{O}(n^3 \log n)$.
 Towards this, it is sufficient to expand $(-z^2 + 2z + 1)^p \cdot (-z^2 - 2z + 1)^q \cdot (z^2 + 1)^r$ for all triplets $(p,q,r)$ such that $p+q+r=n/2$; this is due to Proposition \ref{proposition:generating_fct}.
-To achieve this, we first precompute the expanded polynomial $(-z^2 + 2z + 1)^p$ for each $p\in[1,n/2]$.
+
+To achieve this, we first precompute the expanded polynomial $(-z^2 + 2z + 1)^p$ for each $p\in[0,n/2]$.
 This can be done recursively using the formula $(-z^2 + 2z + 1)^{p+1} = (-z^2 + 2z + 1) \cdot (-z^2 + 2z + 1)^p$.
@@
 Performing this for every $p$ results in a total complexity of $\mathcal{O}(n^2)$.
-The same approach can be used to expand the polynomials $(-z^2 - 2z + 1)^q$ and $(z^2 + 1)^r$, resulting in an overall complexity of $\mathcal{O}(n^2)$ for a fixed triplet $(p,q,r)$.
-Finally, for each such triplet $(p,q,r)$, we multiply the three expanded polynomials $(-z^2 + 2z + 1)^p$, $(-z^2 - 2z + 1)^q$ and $(z^2 + 1)^r$.
+The same approach can be used to expand the polynomials $(-z^2 - 2z + 1)^q$ and $(z^2 + 1)^r$, resulting in an overall complexity of $\mathcal{O}(n^2)$ for all $p,q,r\in[0,n/2]$.
+
+Finally, for each triplet $(p,q,r)$ satisfying $p+q+r=n/2$, we multiply the three expanded polynomials $(-z^2 + 2z + 1)^p$, $(-z^2 - 2z + 1)^q$ and $(z^2 + 1)^r$.
 These two multiplications are performed in $\mathcal{O}(n \log n)$ operations by using the fast Fourier transform.
-Given that there are $\mathcal{O}(n^2)$ triplets $(p,q,r)$ to consider, precomputing the values $\mathsf{D}_{n,k}^{p,q,r}$ for all $k\in[1,n]$ and all triplets $(p,q,r)$ has a complexity of $\mathcal{O}(n^3 \log n)$, making the overall complexity of the procedure also $\mathcal{O}(n^3 \log n)$.
+Given that there are $\mathcal{O}(n^2)$ triplets $(p,q,r)$ to consider, we conclude that precomputing the values $\mathsf{D}_{k,n}^{p,q,r}$ for all $k\in[1,n]$ and all triplets $(p,q,r)$ has a complexity of $\mathcal{O}(n^3 \log n)$, making the overall complexity of the procedure also $\mathcal{O}(n^3 \log n)$.
 
@@
 Additionally, Table~\ref{table:walsh_bounds} provides the values of the bound $B_n$ for all even values of $n\in[1,80]$.
-The method described above offers a significantly tighter bound compared to Corollary~\ref{cor:bound_walsh_cauchy}.
+The method described above offers a tighter bound compared to Corollary~\ref{cor:bound_walsh_cauchy}.
 Its polynomial complexity makes it possible to extend the analysis well beyond the limitations imposed by a full computation of the Walsh spectrum, which requires a complexity of $\mathcal O(n2^n)$.
+\ifnum\anon=0
 	We provide a \textsf{SageMath} implementation to obtain the bound $B_n$: \url{https://github.com/se-tim/Revisited-HWBF.git}.
-
-\begin{table}
+\fi
+
+\begin{table}[ht]
 	\small
@@
 	\end{tabular}
-	\mycaption{The actual $\max_{a\in\F_2^n}|\wt f(a)|$ compared to the bound $B_n$ and the bound from Corollary~\ref{cor:bound_walsh_cauchy}.}
+	\mycaption{The actual $\max_{a\in\F_2^n}|\wt f(a)|$ compared to the bound $B_n$ and the theoretical bound from Corollary~\ref{cor:bound_walsh_cauchy}.}
 	\label{table:max_walsh_vs_bound}
@@
 
-In this part, we compare the nonlinearity of the revisited \hwbf{} $f\in\BN$ to other weightwise quadratic functions considered for similar use-cases, such as the majority function, the \hwbf{} and the cyclic weightwise functions studied in~\cite{DAM:MeaOza24}.
-
-In Figure~\ref{fig:walsh_bound_comparison}, we compare the values of $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$, where a smaller maximum indicates better nonlinearity (see Definition~\ref{def:nl}). 
+In this part, we compare the nonlinearity of the revisited \hwbf{} to other weightwise quadratic functions considered for similar use-cases, such as the majority function, the \hwbf{} and the cyclic weightwise functions studied in~\cite{DAM:MeaOza24}.
+
+In Figure~\ref{fig:walsh_bound_comparison}, we compare bounds for the values of $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$ for various functions $f\in\BN$, where a smaller maximum indicates better nonlinearity, see Definition~\ref{def:nl}.
 We present values for $n$ up to $80$, which is sufficient for examining the asymptotic behavior of the different bounds.
-The violet and orange curves represent the upper bounds  in~\cite{DAM:MeaOza24}.
-More precisely, the violet curve corresponds to the bound that holds for all cyclic weightwise linear functions $f$ that, with the notation from Definition~\ref{def:wwdegd}, satisfy $ f_0(x) = b \cdot x $ for $\w(b)$ odd; therefore, this represents for instance an upper bound for the \hwbf{}.
+The pink and orange curves represent the upper bounds  in~\cite{DAM:MeaOza24}, with the orange curve mostly overlapping the pink one.
+To go into more detail, the pink curve corresponds to the bound that holds for all cyclic weightwise linear functions $f$ that, with the notation from Definition~\ref{def:wwdegd}, satisfy $ f_0(x) = b \cdot x $ for $\w(b)$ odd; therefore, this represents for instance an upper bound for the \hwbf{}.
 The orange curve corresponds to the bound for the cyclic weightwise quadratic function $f$ defined by $f_0(x) = x_1 + x_2 x_3$.
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=10.5cm]{comparison_walsh_bound.pdf}
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=10cm]{comparison_walsh_bound.pdf}
 	\mycaption{
-		Bounds on the maxima of absolute values of the Walsh spectrum for various functions, shown on a logarithmic scale for even values of $n$.
-		The violet and orange curves, the orange one mostly covering the violet one, represent bounds for cyclic weightwise linear functions and a cyclic weightwise quadratic function from~\cite{DAM:MeaOza24}, respectively.
+		Bounds on $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$ for various functions $f\in\BN$ and even values of $n$, shown on a logarithmic scale.
+		The pink and orange curves, the orange one mostly covering the pink one, represent bounds for cyclic weightwise linear functions and a cyclic weightwise quadratic function from~\cite{DAM:MeaOza24}, respectively.
 The blue curve shows bounds for the majority function and the \hwbf{}.
-The theoretical bound for the revisited \hwbf{} (from Corollary~\ref{cor:bound_walsh_cauchy}) is in red, and the experimental bound $B_n$ (Section~\ref{sec:expwt}) is in green.}
+The theoretical bound for the revisited \hwbf{} (Corollary~\ref{cor:bound_walsh_cauchy}) is in red, and the experimental bound $B_n$ (Section~\ref{sec:expwt}) is in green.}
 	\label{fig:walsh_bound_comparison}
@@
 
-The revisited \hwbf{} demonstrates significantly better performance compared to the majority function and the original \hwbf{}.
-Its theoretical bound reveals an asymptotic slope of $3/4$ on a logarithmic scale, contrasting with the slope of $1$ for the majority function and the \hwbf{}.
-Notably, the green curve corresponding to the bound of Section~{sec:expwt} appears to share this asymptotic slope of $3/4$, supporting the effectiveness of Corollary~\ref{cor:bound_walsh_cauchy} and the stronger Theorem~\ref{theorem:bound_D_nka_generalized} in capturing asymptotic behavior.
-In contrast, the bounds proven in~\cite{DAM:MeaOza24}, represented by the violet and orange curves, exhibit the less favorable asymptotic slope of $1$.
+The revisited \hwbf{} demonstrates significantly better performance compared to the majority function, the original \hwbf{} and the functions studied in \cite{DAM:MeaOza24}.
+Its theoretical bound on $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$ reveals an asymptotic slope of $3/4$ on a logarithmic scale, contrasting with the slope of $1$ for the majority function, the \hwbf{}, and the bounds proven in~\cite{DAM:MeaOza24}.
+Notably, the green curve corresponding to the bound of Section~\ref{sec:expwt} appears to share this asymptotic slope of $3/4$, supporting the effectiveness of Corollary~\ref{cor:bound_walsh_cauchy} and the stronger Theorem~\ref{theorem:bound_D_nka_generalized} in capturing asymptotic behavior.
+
+\bigskip
 
@@
 
-In this section, we present additional cryptographic parameters for the revisited \hwbf{} $f\in\BN$.
+In this section, we present additional cryptographic parameters for the revisited \hwbf{}.
 While Theorem~\ref{th:bal} describes its balancedness and Sections~\ref{sec:Cauchy} and \ref{sec:expAndComp} thoroughly explore its nonlinearity, our focus here will be on its algebraic characteristics.
-Specifically, we will examine the degree, the algebraic immunity, and the fast algebraic immunity of $f$, and offer comparisons with other weightwise quadratic functions.
+Specifically, we will examine the degree, the algebraic immunity, and the fast algebraic immunity, and offer comparisons with other weightwise quadratic functions.
 
@@
 \begin{proof}
-	We write $f=q+h$, where $q\in\BN$ is given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}$ and $h\in\BN$ is the \hwbf{}.
+	We write $f=q+h$, where $q\in\BN$ is given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$ and $h\in\BN$ is the \hwbf{}.
 	The function $h$ has degree $n-1\geq 3$ by Property~\ref{prop:wwd1}, and the function $q$ has no monomial of degree higher than $2$, so that $\degg(f)=\degg(h)=n-1$.
@@
 \begin{proof}
-	Denote by $q\in\BN$ the quadratic function given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$, allowing to write $h=f+q$.
+	Again, let $q\in\BN$ be given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$, so that $h=f+q$.
 	Let $g\in\BN^*$ with $\degg(g)=\AI(f)$ be an annihilator of $f+ \varepsilon$ for some $\varepsilon\in\{0,1\}$. Then the following holds:
@@
 
-These various results on the algebraic properties of $f$ suggest that it possesses strong resistance against standard attacks.
+These various results on the algebraic properties of the revisited \hwbf{} suggest that it possesses strong resistance against standard attacks.
 Furthermore, its high nonlinearity makes it a well-suited candidate for use as a filter function in contexts such as filtered \textsf{LFSR}s or in homomorphically-friendly schemes like \textsf{FLIP} and \textsf{FiLIP}.
 
-\begin{table}
+\begin{table}[ht]
 	\small
@@
 
-In this work, we introduced the revisited Hidden Weight Bit Function (\hwbf{}), a weightwise quadratic Boolean function with improved cryptographic properties over existing constructions.
-We analyzed its balancedness, and using generating functions in combination with complex analysis, we derived new lower bounds on its nonlinearity, demonstrating that the revisited \hwbf{} achieves superior nonlinearity compared to other functions with similar computational costs.
+In this work, we introduced the revisited Hidden Weight Bit Function, a weightwise quadratic Boolean function with improved cryptographic properties over existing constructions.
+We analyzed its balancedness, and using generating functions in combination with complex analysis, we derived interesting lower bounds on its nonlinearity, demonstrating that the revisited \hwbf{} achieves superior nonlinearity compared to other functions with similar computational costs.
 We further examined other cryptographic parameters such as degree, algebraic immunity, and fast algebraic immunity, confirming that the revisited \hwbf{} matches or outperforms comparable functions in these aspects.
 
-Our approach makes use of generating functions and Cauchy’s estimate to bound the maximum absolute Walsh spectrum of weightwise quadratic functions.
+Our approach makes use of generating functions and Cauchy’s estimate to bound the nonlinearity of weightwise quadratic functions from below.
 This naturally leads to the following question: do the employed techniques, particularly the use of Cauchy’s estimate, extend to different families of Boolean functions?

### 2024-12-09 RevisedHiddenWeight.tex
minor, getting closer to the end

@@
 We analyze the balancedness, nonlinearity, and other criteria of this function, presenting theoretical bounds and experimental results to highlight its advantages over existing functions in similar use cases.
+
+The different techniques we introduce to study the nonlinearity of this function also enable us to bound the nonlinearity of a broad family of weightwise quadratic functions, both theoretically and practically.
+We believe these methods are of independent interest.
+
+\keywords{Boolean functions, HWBF, Nonlinearity.}
+
 \end{abstract}
@@
 \begin{definition}[Balancedness]
-    A Boolean function $f\in\BN$ is called balanced if $\wt f(0_n)=0$.
+%    A Boolean function $f\in\BN$ is called balanced if $\wt f(0_n)=0$.
+A Boolean function $f\in\BN$ is called balanced if $|\{x \in \F_2^n \mid f(x)=0\}|=|\{x \in \F_2^n \mid f(x)=1\}|=2^{n-1}$. 
+Equivalently, $f$ is balanced if and only if $\wt f(0_n)=0$.
 \end{definition}
@@
 
-\begin{definition}[Fast algebraic immunity, \eg, \cite{EC:ACGKMR06}]\label{def:FAI}
+\begin{definition}[Fast algebraic immunity, \eg, \cite{EC:ACGKMR06,IEEE:LiuLinPei11,DCC:CarTan15}]\label{def:FAI}
 	The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined as:
@@
 
-In this work, we introduced the revisited Hidden Weight Bit Function, a weightwise quadratic Boolean function with improved cryptographic properties over existing constructions.
+In this work, we introduced the revisited hidden weight bit function, a weightwise quadratic Boolean function with improved cryptographic properties over existing constructions. 
 We analyzed its balancedness, and using generating functions in combination with complex analysis, we derived interesting lower bounds on its nonlinearity, demonstrating that the revisited \hwbf{} achieves superior nonlinearity compared to other functions with similar computational costs.
@@
 
-Our approach makes use of generating functions and Cauchy’s estimate to bound the nonlinearity of weightwise quadratic functions from below.
-This naturally leads to the following question: do the employed techniques, particularly the use of Cauchy’s estimate, extend to different families of Boolean functions?
-Exploring this could potentially lead to the discovery of new functions with even better cryptographic properties.
+%Our approach makes use of generating functions and Cauchy’s estimate to bound the nonlinearity of weightwise quadratic functions from below. 
+%This naturally leads to the following question: do the employed techniques, particularly the use of Cauchy’s estimate, extend to different families of Boolean functions? 
+%In particular, the same approach seems possible for other weightwise-degree-$d$ functions such that the $f_k$ are direct sums.
+%Exploring this could potentially lead to the discovery of new functions with similar computational cost and even better cryptographic properties.
+
+Our approach leverages generating functions and Cauchy’s estimate to establish lower bounds on the nonlinearity of weightwise quadratic functions. 
+This naturally raises the question: can the employed techniques, particularly the use of Cauchy’s estimate, be extended to other families of Boolean functions?
+Specifically, this approach appears feasible for other weightwise-degree-$d$ functions where the $f_k$ are direct sums.
+Investigating this could potentially lead to the discovery of new functions with comparable computational costs and even better cryptographic properties.
 

### 2024-12-13 RevisedHiddenWeight.tex
minor

@@
 %    A Boolean function $f\in\BN$ is called balanced if $\wt f(0_n)=0$.
-A Boolean function $f\in\BN$ is called balanced if $|\{x \in \F_2^n \mid f(x)=0\}|=|\{x \in \F_2^n \mid f(x)=1\}|=2^{n-1}$. 
+A Boolean function $f\in\BN$ is called balanced if $|\{x \in \F_2^n : f(x)=0\}|=|\{x \in \F_2^n : f(x)=1\}|=2^{n-1}$. 
 Equivalently, $f$ is balanced if and only if $\wt f(0_n)=0$.
@@
 	By reapplying this $n/2-1$ times, we obtain:
+%	\begin{align*}
+%		\Dnka{n}{k}{1,1,0,1,\ldots,0,1}&=\sum_{i=0}^{n/2-1} \binom{n/2-1}{i} \Dnka{2}{k-2i}{1,1}\\
+%		&=\binom{n/2-1}{k/2} \Dnka{2}{0}{1,1}+ \binom{n/2-1}{(k-1)/2} \Dnka{2}{1}{1,1}\\
+%		&\qquad+ \binom{n/2-1}{k/2-1} \Dnka{2}{2}{1,1}\\
+%		&=\binom{n/2-1}{k/2}-2\binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}.
+%	\end{align*}
 	\begin{align*}
 \Dnka{n}{k}{1,1,0,1,\ldots,0,1}&=\sum_{i=0}^{n/2-1} \binom{n/2-1}{i} \Dnka{2}{k-2i}{1,1}\\
-		&=\binom{n/2-1}{k/2} \Dnka{2}{0}{1,1}+ \binom{n/2-1}{(k-1)/2} \Dnka{2}{1}{1,1}\\
-		&\qquad+ \binom{n/2-1}{k/2-1} \Dnka{2}{2}{1,1}\\
+&=\binom{n/2-1}{k/2} \Dnka{2}{0}{1,1}+ \binom{n/2-1}{(k-1)/2} \Dnka{2}{1}{1,1}+ \binom{n/2-1}{k/2-1} \Dnka{2}{2}{1,1}\\
 &=\binom{n/2-1}{k/2}-2\binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}.
 \end{align*}
+We similarly ge
 	We similarly get $\Dnka{n}{k}{0,0,0,1,\ldots,0,1}=\binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}$. Then, combining both, we obtain:
@@
 	\end{align*}
-	The announced result follows by applying that $\binom{m}{k}=\binom{m}{m-k}$ for all integers $m\geq 0$ and $k$.
+	The final result follows by applying that $\binom{n}{k}=\binom{n}{n-k}$ for all integers $n\geq 0$ and $k$.
 \end{proof}
@@
 \begin{proof}
-    It is enough to use the expressions from Table \ref{tab:Dnka_small_k}, and replace $p$, $q$ and $r$ by their respective values.
+ %   It is enough to use the expressions from Table \ref{tab:Dnka_small_k}, and replace $p$, $q$ and $r$ by their respective values.
 For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$ in the expression $\Dnka n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dnka n2a=0$.
 This checking can be autotomized by a computer algebra system.
+ We use the expressions from Table~\ref{tab:Dnka_small_k}, and replace $p$, $q$ and $r$ by their respective values. 
+ For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$ in the expression $\Dnka n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dnka n2a=0$.
+~\footnote{This checking can be automatized by a computer algebra system.
 	\ifnum\anon=0
@@
 	\fi
+}
 \end{proof}
@@
 \begin{proof}
-	For the sum and the alternating sum, it is enough to compute $P_a(1)$ and $P_a(-1)$, respectively.
+	For the sum and the alternating sum, we compute $P_a(1)$ and $P_a(-1)$, respectively. 
 	The sum of the $\Dnka nka$ over the even (respectively, odd) $k$ is obtained by adding (respectively, subtracting) these two sums and dividing by $2$.
@@
 
-In this part, we generalize the results of Section~\ref{sec:Cauchy} to all weightwise quadratic functions $f$ such that for every $k\in [1,n]$, the function $f_k$ in Definition~\ref{def:wwdegd} has exactly $t$ quadratic terms with no shared variables.
+%In this part, we generalize the results of Section~\ref{sec:Cauchy} to all weightwise quadratic functions $f$ such that for every $k\in [1,n]$, the function $f_k$ in Definition~\ref{def:wwdegd} has exactly $t$ quadratic terms with no shared variables.
+
+In this part, we generalize the results of Section~\ref{sec:Cauchy} to all weightwise quadratic functions $f$ such that, for every $k \in [1, n]$, the function $f_k$ (as defined in Definition~\ref{def:wwdegd}) contains exactly $t$ quadratic terms with no shared variables.
 
@@
 
-    Similarly to the proof of Theorem~\ref{theorem:bound_D_nka}, we want to bound the maximum of $|P_{t,a}(z)|$ on $\dis$ for $a\in\F_2^n$, and this will then be an upper bound on $|\Dtkna tkna|$ for every $k\in[0,n]$.
+    Similarly to the proof of Theorem~\ref{theorem:bound_D_nka}, we want to bound the maximum of $|P_{t,a}(z)|$ on $\dis=\{ z \in \C: |z|=1  \}$ for $a\in\F_2^n$, and this will then be an upper bound on $|\Dtkna tkna|$ for every $k\in[0,n]$.
     We write $a=(b,c)$ with $b\in\F_2^{2t}$ and $c\in\F_2^{n-2t}$, and define $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}.    
@@
 Similarly, it can be proven that $|P_{t,a}(z)|$ is also bounded by $2^{\mu n}$ on $\dis$ for the remaining two cases of $(p,q,r;u,v)$.
-In fact, for $(p,q,r;u,v)=(0,t,0;n-2t,0)$, one can proceed in exactly the same way, and for $(p,q,r;u,v)=(0,0,t;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h(\alpha)=(2+2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$, whose maximum is bounded by the maximum of $g(\alpha)$ because $0\leq h(\alpha)\leq g(\alpha)$.
+    For $(p,q,r;u,v)=(0,t,0;n-2t,0)$, one can proceed in exactly the same way, and for $(p,q,r;u,v)=(0,0,t;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h(\alpha)=(2+2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$, whose maximum is bounded by the maximum of $g(\alpha)$ since $0\leq h(\alpha)\leq g(\alpha)$.
 \end{proof}
@@
 \begin{proof}
-	Again, let $q\in\BN$ be given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$, so that $h=f+q$.
-	Let $g\in\BN^*$ with $\degg(g)=\AI(f)$ be an annihilator of $f+ \varepsilon$ for some $\varepsilon\in\{0,1\}$. Then the following holds:
+	Let $q\in\BN$ be given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$, so that $h=f+q$.
+	Let $g\in\BN^*$ with $\degg(g)=\AI(f)$ be an annihilator of $f+ \varepsilon$ for some $\varepsilon\in\{0,1\}$. 
+	Then the following holds:
 	\[g\cdot(q+1) \cdot(h+\varepsilon) = g\cdot(q+1)\cdot(f+q+\varepsilon)=g\cdot(q+1)\cdot(f+\epsilon)+g\cdot(q+1)\cdot q=0+0=0.\]

### 2024-12-13 RevisedHiddenWeight.tex
Minors

@@
-\def\anon{0} % set to 1 for anonymous submissions, hides acknowledgements and author names
-\def\full{1} % set to 0 for springer proceedings
+\def\anon{0} %Set to 1 for anonymous submissions, hides acknowledgements and author names
+\def\full{1} %Set to 0 for springer proceedings
 
@@
 We analyze the balancedness, nonlinearity, and other criteria of this function, presenting theoretical bounds and experimental results to highlight its advantages over existing functions in similar use cases.
-
 The different techniques we introduce to study the nonlinearity of this function also enable us to bound the nonlinearity of a broad family of weightwise quadratic functions, both theoretically and practically.
@@
 	\keywords{Boolean functions, HWBF, Nonlinearity.}
-
 \end{abstract}
@@
 %    A Boolean function $f\in\BN$ is called balanced if $\wt f(0_n)=0$.
-A Boolean function $f\in\BN$ is called balanced if $|\{x \in \F_2^n : f(x)=0\}|=|\{x \in \F_2^n : f(x)=1\}|=2^{n-1}$. 
+A Boolean function $f\in\BN$ is called balanced if $|\{x \in \F_2^n : f(x)=0\}|=2^{n-1}=|\{x \in \F_2^n : f(x)=1\}|$. 
 Equivalently, $f$ is balanced if and only if $\wt f(0_n)=0$.
@@
 	By reapplying this $n/2-1$ times, we obtain:
-%	\begin{align*}
-%		\Dnka{n}{k}{1,1,0,1,\ldots,0,1}&=\sum_{i=0}^{n/2-1} \binom{n/2-1}{i} \Dnka{2}{k-2i}{1,1}\\
-%		&=\binom{n/2-1}{k/2} \Dnka{2}{0}{1,1}+ \binom{n/2-1}{(k-1)/2} \Dnka{2}{1}{1,1}\\
-%		&\qquad+ \binom{n/2-1}{k/2-1} \Dnka{2}{2}{1,1}\\
-%		&=\binom{n/2-1}{k/2}-2\binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}.
-%	\end{align*}
 	\begin{align*}
@@
 	\end{align*}
-We similarly ge
 	We similarly get $\Dnka{n}{k}{0,0,0,1,\ldots,0,1}=\binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}$. Then, combining both, we obtain:
@@
 \begin{proof}
- %   It is enough to use the expressions from Table \ref{tab:Dnka_small_k}, and replace $p$, $q$ and $r$ by their respective values.
-For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$ in the expression $\Dnka n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dnka n2a=0$.
-This checking can be autotomized by a computer algebra system.
 	We use the expressions from Table~\ref{tab:Dnka_small_k}, and replace $p$, $q$ and $r$ by their respective values. 
- For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$ in the expression $\Dnka n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dnka n2a=0$.
-~\footnote{This checking can be automatized by a computer algebra system.
+	For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$ in the expression $\Dnka n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dnka n2a=0$.~\footnote{This checking can be automatized by a computer algebra system.
 	\ifnum\anon=0
 		For this, we refer to the corresponding \textsf{SageMath} implementation, accessible via this link: \url{https://github.com/se-tim/Revisited-HWBF.git}.
-	\fi
-}
+	\fi}
 \end{proof}
@@
 \subsection{Generalization to a family of weightwise quadratic functions}\label{sec:general}
-
-%In this part, we generalize the results of Section~\ref{sec:Cauchy} to all weightwise quadratic functions $f$ such that for every $k\in [1,n]$, the function $f_k$ in Definition~\ref{def:wwdegd} has exactly $t$ quadratic terms with no shared variables.
 
@@
 
-%Our approach makes use of generating functions and Cauchy’s estimate to bound the nonlinearity of weightwise quadratic functions from below. 
-%This naturally leads to the following question: do the employed techniques, particularly the use of Cauchy’s estimate, extend to different families of Boolean functions? 
-%In particular, the same approach seems possible for other weightwise-degree-$d$ functions such that the $f_k$ are direct sums.
-%Exploring this could potentially lead to the discovery of new functions with similar computational cost and even better cryptographic properties.
-
-Our approach leverages generating functions and Cauchy’s estimate to establish lower bounds on the nonlinearity of weightwise quadratic functions. 
+Our approach utilizes generating functions and Cauchy’s estimate to establish lower bounds on the nonlinearity of weightwise quadratic functions. 
 This naturally raises the question: can the employed techniques, particularly the use of Cauchy’s estimate, be extended to other families of Boolean functions?
-Specifically, this approach appears feasible for other weightwise-degree-$d$ functions where the $f_k$ are direct sums.
+Specifically, this approach appears feasible for other weightwise-degree-$d$ functions $f$ where the $f_k$ are direct sums.
 Investigating this could potentially lead to the discovery of new functions with comparable computational costs and even better cryptographic properties.

### 2025-01-23 RevisedHiddenWeight.tex
Using style for SAC
llncs adjustments

@@
-\def\anon{0} %Set to 1 for anonymous submissions, hides acknowledgements and author names
+\def\anon{1} %Set to 1 for anonymous submissions, hides acknowledgements and author names
 \def\full{1} %Set to 0 for springer proceedings
@@
 \ifnum\full=1
-	\documentclass[11pt]{llncs}
-	\addtolength{\parskip}{1pt}
+	\documentclass{llncs}
 \else
@@
 		Deng Tang\inst{2}
-		%Pierrick M\'eaux\orcidID{0000-0001-5733-4341}\inst{1},
-		%Tim Seuré\inst{1}, 
-		%Deng Tang\orcidID{0000-0002-8373-9200}\inst{2}
 	}
@@
 
+\pagestyle{plain}
+
 \begin{abstract}
@@
 \begin{itemize}
-	\item\emph{Balancedness analysis} (Section~\ref{sec:defAndBal}): We define the revisited \hwbf{} in $n$ variables, hereafter denoted by $f$, and analyze its balancedness.
+	\item\emph{Balancedness analysis} (Section~\ref{sec:defAndBal}):
+	We define the revisited \hwbf{} in $n$ variables, hereafter denoted by $f$, and analyze its balancedness.
 This involves studying the (restricted) Walsh transform of specific quadratic functions over sets of fixed Hamming weights (called slices).
@@
 \begin{definition}[Algebraic Normal Form, degree]\label{def:anf}
-	We call Algebraic Normal Form of a Boolean function $f\in\BN$ its unique representation as an element of the ring $\F_2[x_1,\dots,x_n]/(x_1^2+x_1,\dots,x_n^2+x_n)$, and we express it as follows:
-	\[
-		f(x_1,\dots,x_n)= \sum_{I \subseteq [1,n]} a_I \left( \prod_{i \in I} x_i \right),
-	\]
-	where $a_I\in \F_2$. The (algebraic) degree of $f$ is defined by $\degg(f)=0$ in case $f$ is the null function, and $\degg(f)=\max\{ |I|:I\subseteq[1,n],a_I=1\}$ otherwise.
+	We call Algebraic Normal Form of a Boolean function $f\in\BN$ its unique representation as an element of the ring $\F_2[x_1,\dots,x_n]/(x_1^2+x_1,\dots,x_n^2+x_n)$, and we express it as $f(x_1,\dots,x_n)= \sum_{I \subseteq [1,n]} a_I \left( \prod_{i \in I} x_i \right)$, where $a_I\in \F_2$.
+The (algebraic) degree of $f$ is defined by $\degg(f)=0$ in case $f$ is the null function, and $\degg(f)=\max\{ |I|:I\subseteq[1,n],a_I=1\}$ otherwise.
 \end{definition}
@@
 \begin{definition}[Walsh transform, restricted Walsh transform]\label{def:walsh_transform}
-	The Walsh transform at $a \in \F_2^n$ of a Boolean function $f\in\BN$ restricted to a subset $S\subseteq \F_2^n$ is defined as:
-    \[  \wt{f,S} (a) = \sum_{x\in S} (-1)^{f(x)+a \cdot x}.\]
-    The (unrestricted) Walsh transform of $f$ is then defined as $\wt{f}=\wt{f,\F_2^n}$. For any integer $k$, we also set $\wt{f,k}=\wt{f,\Ekn{k}{n}}$.
+	The Walsh transform at $a \in \F_2^n$ of a Boolean function $f\in\BN$ restricted to a subset $S\subseteq \F_2^n$ is defined as $\wt{f,S} (a) = \sum_{x\in S} (-1)^{f(x)+a \cdot x}$.
+The (unrestricted) Walsh transform of $f$ is then defined as $\wt{f}=\wt{f,\F_2^n}$.
+For any integer $k$, we also set $\wt{f,k}=\wt{f,\Ekn{k}{n}}$.
 \end{definition}
@@
 \begin{definition}[Balancedness]
-%    A Boolean function $f\in\BN$ is called balanced if $\wt f(0_n)=0$.
-A Boolean function $f\in\BN$ is called balanced if $|\{x \in \F_2^n : f(x)=0\}|=2^{n-1}=|\{x \in \F_2^n : f(x)=1\}|$. 
-Equivalently, $f$ is balanced if and only if $\wt f(0_n)=0$.
-\end{definition}
-
-\begin{definition}[Nonlinearity, \eg, page 79 in \cite{Carlet20}]%and weightwise nonlinearity
+	A Boolean function $f\in\BN$ is called balanced if $|\{x \in \F_2^n : f(x)=0\}|=2^{n-1}=|\{x \in \F_2^n : f(x)=1\}|$. Equivalently, $f$ is balanced if and only if $\wt f(0_n)=0$.
+\end{definition}
+
+\begin{definition}[Nonlinearity, \eg, page 79 in \cite{Carlet20}]
 	\label{def:nl}
-	The nonlinearity $\NL(f)$ of a Boolean function $f\in \BN$ is the minimum Hamming distance between $f$ and all the affine functions in $\BN$:
-	\[
-		\NL(f) = \min\{ \hd(f,g):g\in\BN,\degg(g)\leq 1\},
-	\]
-	where the Hamming distance between $f$ and $g$ is defined as $\hd(f,g)=|\{x\in\F_2^n:f(x)\neq g(x)\}|$.
-Alternatively, the nonlinearity of $f\in\BN$ can also be defined in terms of its Walsh transform:
-	\[
-		\NL(f) = 2^{n-1}- \frac{1}{2} \max_{a\in \F_2^n}{|\wt{f}(a)|}.
-	\]
+	The nonlinearity $\NL(f)$ of a Boolean function $f\in \BN$ is the minimum Hamming distance between $f$ and all the affine functions in $\BN$, that is, $\NL(f) = \min\{ \hd(f,g):g\in\BN,\degg(g)\leq 1\}$, where the Hamming distance between $f$ and $g$ is defined as $\hd(f,g)=|\{x\in\F_2^n:f(x)\neq g(x)\}|$.
+Alternatively, the nonlinearity of $f\in\BN$ can also be defined in terms of its Walsh transform: $\NL(f) = 2^{n-1}- \frac{1}{2} \max_{a\in \F_2^n}{|\wt{f}(a)|}$.
 \end{definition}
@@
 \begin{definition}[Annihilator, algebraic immunity~\cite{EC:MeiPasCar04}] \label{def:ai}
-	Let $f\in\BN$ be a Boolean function. Then a function $g\in\BN^*$ is called an annihilator of $f$ if it satisfies $fg=0$. The algebraic immunity of $f$ is then defined as:
-	\[ \AI(f) = \min\{ \degg(g):\text{$g\in\BN^*$ is an annihilator of $f$ or $f+1$}\}.\]
+	Let $f\in\BN$ be a Boolean function.
+Then a function $g\in\BN^*$ is called an annihilator of $f$ if it satisfies $fg=0$.
+The algebraic immunity of $f$ is then defined as $\AI(f) = \min\{ \degg(g):\text{$g\in\BN^*$ is an annihilator of $f$ or $f+1$}\}$.
 \end{definition}
@@
 \begin{definition}[Fast algebraic immunity, \eg, \cite{EC:ACGKMR06,IEEE:LiuLinPei11,DCC:CarTan15}]\label{def:FAI}
-	The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined as:
-	\[
-		\FAI(f)=\min \{ 2 \AI(f), \min\{\degg(g)+ \degg(fg):g\in\BN,1\leq\degg(g)<\AI(f)\}\}.
-	\]
+	The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined to be $\FAI(f)=\min \{ 2 \AI(f), \min\{\degg(g)+ \degg(fg):g\in\BN,1\leq\degg(g)<\AI(f)\}\}$.
 \end{definition}
@@
 	\begin{itemize}
-		\item (\eg, Theorem $3$ in~\cite{DCC:DalMaiSar06}) The majority function $\mathsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
-		\[
-			\NL(\mathsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}.
-		\]
-		\item (Theorem $3$ in~\cite{DAM:WCST14}) The \hwbf{} $h$ introduced in Definition~\ref{def:hwbf} satisfies:
-		\[
-			\NL(h)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}.
-		\]	
+		\item (\textit{E.g.}, Theorem $3$ in~\cite{DCC:DalMaiSar06}) The majority function $\mathsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies $\NL(\mathsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}$.
+		\item (Theorem $3$ in~\cite{DAM:WCST14}) The \hwbf{} $h$ introduced in Definition~\ref{def:hwbf} satisfies $\NL(h)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}$.
 		\item (Theorem $1$ in \cite{DAM:WCST14}) The \hwbf{} $h$ introduced in Definition~\ref{def:hwbf} satisfies $\degg(h)=n-1$ if $n\geq 4$.
@@
 \begin{definition}[Krawtchouk polynomials]\label{def:Kraw}
-	The $n$-th Krawtchouk polynomial of degree $k\in\Z$ is given by:
-    \[
-        \kraw{k}{x}{n}=\sum_{j=0}^{k} (-1)^j \binom{x}{j} \binom{n-x}{k-j}.
-    \]
-    The Krawtchouk polynomials can alternatively be characterized as the coefficients in the generating function for $(1+z)^{n-x} (1-z)^x$ in the variable $z$:
-    \[
-        (1+z)^{n-x} (1-z)^x=\sum_{k\in\Z} \kraw{k}{x}{n} z^k.
-    \]
+	The $n$-th Krawtchouk polynomial of degree $k\in\Z$ is given by $\kraw{k}{x}{n}=\sum_{j=0}^{k} (-1)^j \binom{x}{j} \binom{n-x}{k-j}$.
+The Krawtchouk polynomials can alternatively be characterized as the coefficients in the generating function for $(1+z)^{n-x} (1-z)^x$ in the variable $z$, that is, $(1+z)^{n-x} (1-z)^x=\sum_{k\in\Z} \kraw{k}{x}{n} z^k$.
 \end{definition}
@@
 		\item If $n\geq 2$, then for $b=(a_1,\dots,a_{n-2})\in\F_2^{n-2}$, we have:
-		\[
-			\Dnka{n}{k}{a}=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.
-		\]
+		\begin{align*}
+			\Dnka{n}{k}{a}&=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b}\\
+			&\qquad+ (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.
+		\end{align*}
 	\end{itemize}
@@
 		\sum_{y\in \Ekn{k-1}{n-2}} (-1)^{d_{n-2}(y) +b\cdot y + a_{n-1}}\\
-		&\qquad+\sum_{y\in \Ekn{k-1}{n-2}} (-1)^{d_{n-2}(y) +b\cdot y + a_{n}}
-		+\sum_{y\in \Ekn{k-2}{n-2}} (-1)^{d_{n-2}(y) +b\cdot y +1 + a_{n-1}+ a_{n}}\\
-		&=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b} + (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.\qedhere
+		&\qquad+\sum_{y\in \Ekn{k-1}{n-2}} (-1)^{d_{n-2}(y) +b\cdot y + a_{n}}\\
+		&\qquad+\sum_{y\in \Ekn{k-2}{n-2}} (-1)^{d_{n-2}(y) +b\cdot y +1 + a_{n-1}+ a_{n}}\\
+		&=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}}+ (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b}\\
+		&\qquad+ (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.\qedhere
     \end{align*}
@@
 
-\begin{table}[ht]
-	\small
+\begin{table}
+	\scriptsize
 	\centering
@@
 		\hline
-		$a$ & $(0,0)$ & $(0,1)$ & $(1,1)$ \\ \hline
+		$a$ & $(0,0)$ & $(0,1)$ & $(1,1)$ \\
+		\hline
 		$\Dnka{2}{0}{a}$ &$1$&$1$ & $1$\\
 		$\Dnka{2}{1}{a}$ &$2$& $0$ & $-2$\\
-		$\Dnka{2}{2}{a}$ &$-1$&$1$ & $-1$\\ \hline
+		$\Dnka{2}{2}{a}$ &$-1$&$1$ & $-1$\\
+		\hline
 	\end{tabular}
@@
 	Using the recursive relation from Proposition~\ref{prop:recursiveDnka}, we obtain:
-	\[
-		\Dnka{n}{k}{1,1,0,1,\ldots,0,1}=\Dnka{n-2}{k}{1,1,0,1,\ldots,0,1} +\Dnka{n-2}{k-2}{1,1,0,1,\ldots,0,1}.
-	\]
+	\begin{align*}
+		\Dnka{n}{k}{1,1,0,1,\ldots,0,1}&=\Dnka{n-2}{k}{1,1,0,1,\ldots,0,1}\\
+		&\qquad+\Dnka{n-2}{k-2}{1,1,0,1,\ldots,0,1}.
+	\end{align*}
 	By reapplying this $n/2-1$ times, we obtain:
@@
 		\Dnka{n}{k}{1,1,0,1,\ldots,0,1}&=\sum_{i=0}^{n/2-1} \binom{n/2-1}{i} \Dnka{2}{k-2i}{1,1}\\
-		&=\binom{n/2-1}{k/2} \Dnka{2}{0}{1,1}+ \binom{n/2-1}{(k-1)/2} \Dnka{2}{1}{1,1}+ \binom{n/2-1}{k/2-1} \Dnka{2}{2}{1,1}\\
+		&=\binom{n/2-1}{k/2} \Dnka{2}{0}{1,1}+ \binom{n/2-1}{(k-1)/2} \Dnka{2}{1}{1,1}\\
+		&\qquad+ \binom{n/2-1}{k/2-1} \Dnka{2}{2}{1,1}\\
 		&=\binom{n/2-1}{k/2}-2\binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}.
@@
 		&\qquad+\sum_{k=n/2+1}^{n}\left(\binom{n/2-1}{k/2}+2\binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}\right)\\
-		&=\sum_{k=0}^{n}\left( \binom{n/2-1}{k/2}-\binom{n/2-1}{k/2-1}\right)+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2}\binom{n/2-1}{(k-1)/2}\right)\\
+		&=\sum_{k=0}^{n}\left( \binom{n/2-1}{k/2}-\binom{n/2-1}{k/2-1}\right)\\
+		&\qquad+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2}\binom{n/2-1}{(k-1)/2}\right)\\
 		&=0+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right)\\
@@
 	For every even integer $n\geq 0$, for every binary vector $a\in\F_2^n$, and for every integer $k$, the following holds:
-	\[	\Dnka n{n-k}a=(-1)^{p+q+k}\Dnka nka.	\]
+	\[
+		\Dnka n{n-k}a=(-1)^{p+q+k}\Dnka nka.
+	\]
 \end{proposition}
@@
 \begin{proof}
-	We define the reverse polynomial  $Q_a(z)$ as the degree $n$ polynomial where each coefficient of $z^k$ in $Q_a(z)$, for any $k$, is equal to the coefficient of $z^{n-k}$ in $P_a(z)$. 
-	Then we have:
+	We define the reverse polynomial  $Q_a(z)$ as the degree $n$ polynomial where each coefficient of $z^k$ in $Q_a(z)$, for any $k$, is equal to the coefficient of $z^{n-k}$ in $P_a(z)$. Then we have:
 	\begin{align*}
@@
 \begin{remark}\label{remark:D_nka_differentiation}
-    We can also use Proposition \ref{proposition:generating_fct} to obtain $\Dnka nka$ through differentiation and evaluation at $z=0$:
-    \[
-        k!\cdot\Dnka nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}.
-    \]
+    We can also use Proposition \ref{proposition:generating_fct} to obtain $\Dnka nka$ through differentiation and evaluation at $z=0$, to get $k!\cdot\Dnka nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}$.
 Using this formula, we can for instance use a computer algebra system to deduce $\Dnka nka$ for small values of $k$, see Table \ref{tab:Dnka_small_k}.
@@
 		\hline
-		$k$ & $\Dnka 2ka$\\ \hline
+		$k$ & $\Dnka 2ka$\\
+		\hline
 		$0$&$1$\\
@@
 		$2$&$2(p-q)^2-3(p+q)+r$\\
-		$3$&$\frac 23(p-q)\left(2(p-q)^2-9(p+q)+3r+7\right)$\\ \hline
+		$3$&$\frac 23(p-q)\left(2(p-q)^2-9(p+q)+3r+7\right)$\\
+		\hline
 	\end{tabular}
@@
 		\[
-			\sum_{k\in\Z}\Dnka nka=(-1)^{q}2^{n/2} \quad \text{and} \quad
+			\sum_{k\in\Z}\Dnka nka=(-1)^{q}2^{n/2}, \qquad
 			\sum_{k\in\Z}(-1)^k\Dnka nka=(-1)^{p}2^{n/2}.
@@
         \item The sum over the even and the odd $k$ of the $\Dnka nka$ are, respectively:
-		\[
-			\sum_{k\in\Z}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big) \quad \text{ and } \quad 
+        \begin{gather*}
+			\sum_{k\in\Z}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big),\\
 			\sum_{k\in\Z}\Dnka n{2k+1}a=2^{n/2-1}\big((-1)^{q}-(-1)^{p}\big).
-		\]
+		\end{gather*}
     \end{enumerate}
@@
 Let $f:D\to\C$ be a holomorphic function, and let $M_R$ be the maximum of the absolute value of $f$ on the circle defined by $|z-w|=R$.
-Then for every integer $k\geq 0$, the $k$-th derivative of $f$ evaluated at $w$ can be bounded, in absolute value, as follows:
-    \[
-        \left|\frac{\dd^k}{\dd^k z}f(z)\vert_{z=w}\right|\leq\frac{k!\cdot M_R}{R^k}.
-    \]
+Then for every integer $k\geq 0$, the $k$-th derivative of $f$ evaluated at $w$ can be bounded, in absolute value, by $\left|\frac{\dd^k}{\dd^k z}f(z)\vert_{z=w}\right|\leq\frac{k!\cdot M_R}{R^k}$.
 \end{Prop}
@@
     From Remark~\ref{remark:D_nka_differentiation} we have $k!\cdot\Dnka nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}$.
-Choosing $f=P_a$, $w=0$ and $R=1$ in Property \ref{property:cauchy_estimate} then gives:
-    \[
-        |\Dnka nka|=\frac{1}{k!}\left|\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}\right|\leq M,
-    \]
-    where $M$ is the maximum of $|P_a(z)|$ on the complex circle $\dis=\{ z \in \C: |z|=1  \}$.
+Choosing $f=P_a$, $w=0$ and $R=1$ in Property \ref{property:cauchy_estimate} then gives $|\Dnka nka|=\frac{1}{k!}\left|\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}\right|\leq M$, where $M$ is the maximum of $|P_a(z)|$ on the complex circle $\dis=\{ z \in \C: |z|=1  \}$.
 We claim, and prove below, that the maximum of $\left|-z^2+2z+1\right|$ on $\dis$ is $2\sqrt 2$.
@@
 We have previously established in Proposition~\ref{prop:WT} that $\wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b_k}$ for some vectors $b_k\in\F_2^n$.
-Then, applying the triangle inequality together with Theorem~\ref{theorem:bound_D_nka} yields:
-    \[
-        |\wt{f}(a)|\leq 1+\sum_{k=1}^n\left|\Dnka{n}{k}{b_k}\right|\leq 1+ n\cdot 2^{3n/4}.\qedhere
-    \]
+Then, applying the triangle inequality together with Theorem~\ref{theorem:bound_D_nka} yields $|\wt{f}(a)|\leq 1+\sum_{k=1}^n\left|\Dnka{n}{k}{b_k}\right|\leq 1+ n\cdot 2^{3n/4}$.
 \end{proof}
@@
 In this part, we generalize the results of Section~\ref{sec:Cauchy} to all weightwise quadratic functions $f$ such that, for every $k \in [1, n]$, the function $f_k$ (as defined in Definition~\ref{def:wwdegd}) contains exactly $t$ quadratic terms with no shared variables.
+We skip the proofs of the following results; they are provided in the appendix, see Section~\ref{sec:proofs}.
 
@@
 
-In particular, it holds that $d_{n/2,n}(x)=d_n(x)$ and $\Dtkna{n/2}{k}{n}{a}=\Dkna kna$.
-We now focus on the $\Dtkna{t}{k}{n}{a}$.
+In particular, it holds that $d_{n/2,n}(x)=d_n(x)$ and $\Dtkna{n/2}{k}{n}{a}=\Dkna kna$. We now focus on the $\Dtkna{t}{k}{n}{a}$.
 
@@
 
-\begin{proof}
-    By considering binary vectors $x\in\F_2^n$ as $x=(y,z)$ with $y\in\F_2^{2t}$ and $z\in\F_2^{n-2t}$, we get:	
-	\begin{align*}
-		\Dtkna{t}{k}{n}{a}&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}\\
-		&=\sum_{(y,z)\in\Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
-		&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
-		&=\sum_{\ell=0}^{2t}\left(\sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{2t}(y)+b \cdot y}\right)\left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c \cdot z}\right)\\&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b}\cdot\kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
-	\end{align*}
-\end{proof}
-
 \begin{definition}\label{defi:P_a_t}
@@
 
-\begin{proposition}
+\begin{proposition}\label{proposition:sum_dtn}
     For every even integer $n\geq 0$, every integer $t\in[0,n/2]$ and every binary vector $a\in\F_2^n$, the following holds:
@@
 
-\begin{proof}
-    Applying Proposition \ref{proposition:dtn}, we get:
-    \begin{align*}
-        \sum_{k\in\Z}\Dtkna{t}{k}{n}{a}z^k&=\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\sum_{k\in\Z}\kraw{k-\ell}{\w(c)}{n-2t}z^{k-\ell}\\
-        &=\left(\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\right)\cdot(1+z)^u\cdot(1-z)^v\\
-        &=P_b(z)\cdot(1+z)^u\cdot(1-z)^v\\
-        &=P_{t,a}(z).\qedhere
-    \end{align*}
-\end{proof}
-
-With this, we prove a generalization of Theorem~\ref{theorem:bound_D_nka} below. Before that, we still require a technical preliminary result.
-
-\begin{lemma}\label{lemma:maximizing_args}
-    Let $N\geq 1$ be an integer and $D\subseteq\C$ a set of complex numbers.
-For every $i\in[1,N]$, consider integers $m_i\geq 0$ and $k_i\geq 1$, as well as complex functions $f_{i,1},\dots,f_{i,k_i}:D\to\C$.
-Assume that the following maximum exists (which holds for instance if the functions $f_{i,j}$ are continuous and $D$ is topologically compact):
-    \[
-        M=\max_{\substack{\forall i\in[1,N]:\,p_{i,1}+\cdots+p_{i,k_i}=m_i\\z\in D}}\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|.
-    \]
-    Then there exist integers $j_1,\dots,j_N$ with $j_i\in[1,k_i]$ such that the following holds:
-    \[
-        M=\max_{z\in D}\left|\prod_{i=1}^Nf_{i,j_i}(z)^{m_i}\right|.
-    \]
-\end{lemma}
-
-\begin{proof}
-    Let us choose the integers $p_{i,j}\geq 0$ satisfying $\sum_{j=1}^{k_i}p_{i,j}=m_i$ for every $i\in[1,N]$ together with the complex number $z\in D$ to maximize the quantity $\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|$.
-Next, for every $i\in[1,N]$, choose $j_i\in[1,k_i]$ such that $|f_{i,j_i}(z)|\geq|f_{i,j}(z)|$ for every $j\in[1,k_i]$.
-Then we have:
-    \[
-        M=\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|\leq\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j_i}(z)^{p_{i,j}}\right|=\left|\prod_{i=1}^Nf_{i,j_i}(z)^{\sum_{j=1}^{k_i}p_{i,j}}\right|=\left|\prod_{i=1}^Nf_{i,j_i}(z)^{m_i}\right|\leq M.\qedhere
-    \]
-\end{proof}
+This result can in turn be used to bound the $\Dtkna{t}{k}{n}{a}$.
+The following result is a direct generalization of Theorem~\ref{theorem:bound_D_nka}.
 
@@
     \[
-        |\Dtkna tkna|\leq 2^{\mu n}\quad \text{and} \quad  |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}.
+        |\Dtkna tkna|\leq 2^{\mu n},\qquad  |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}.
     \]
@@
 
-\begin{proof}
+The curve of $\lambda\mapsto\mu(\lambda)$ defined in the above Theorem~\ref{theorem:bound_D_nka_generalized} is represented in Figure~\ref{fig:curve_exponents_lambda_mu}.
+Observe that $\mu(1/2)=3/4$, which corresponds to Theorem~\ref{theorem:bound_D_nka}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=7.5cm]{curve_exponents_lambda_mu.pdf}
+    \vspace{-5mm}
+	\mycaption{The curve of $\lambda\mapsto\mu(\lambda)$ with $0\leq\lambda\leq\frac 12$ from Theorem~\ref{theorem:bound_D_nka_generalized}.}
+	\label{fig:curve_exponents_lambda_mu}
+\end{figure}
+
+\section{Experiments and comparisons}\label{sec:expAndComp}
+
+In this section, we establish a tighter bound on the absolute value of the Walsh transform of the revisited \hwbf{} for even $n\in[1,80]$.
+We then compare the nonlinearity of this function to that of other functions suited to similar use cases, such as the \hwbf{} or the weightwise cyclic functions from~\cite{DAM:MeaOza24}.
+
+\subsection{Bounding the Walsh transform of $f$ experimentally}\label{sec:expwt}
+
+Following Corollary~\ref{cor:bound_walsh_cauchy}, we deduce that $|\wt f(a)|\leq 1+n\cdot 2^{3n/4}$ for every even integer $n\geq 0$ and every binary vector $a\in\F_2^n$, where $f\in\BN$ denotes the revisited \hwbf{}.
+This is a somewhat pessimistic bound.
+In this part, we discuss how a tighter bound on $|\wt f(a)|$ can be obtained in polynomial time in $n$.
+
+This method is based on the identity given in Proposition~\ref{prop:WT}.
+For this, consider a vector $b\in\mathbb F_2^n$; we write $(p,q,r)=(p(b),q(b),r(b))$.
+Also, for $k\in[1,n]$, let $b_k=b+\pi(e_k)$ and $(p_k,q_k,r_k)=(p(b_k),q(b_k),r(b_k))$, where $\pi:[1,n]\to[1,n]$ is again the permutation sending the first $n/2$ elements to the odd positions and the $n/2$ last ones to the even positions.
+Notice first that for every integer $k\in[1,n]$, it holds that $(p_k,q_k,r_k)\in\{(p\pm1,q,r\mp 1),(p,q\pm 1,r\mp 1)\}$.
+Furthermore, observe that if $k\in[0,n/2]$ and $(p_k,q_k,r_k)=(p+\alpha,q+\beta,r+\gamma)$ for $\{\alpha,\beta,\gamma\}=\{0,\pm 1\}$ with $\gamma\neq 0$, then we have $(p_{k+n/2},q_{k+n/2},r_{k+n/2})=(p+\alpha',q+\beta',r+\gamma')$ for some $\{\alpha',\beta',\gamma'\}=\{0,\pm 1\}$ with $\gamma'\neq 0$ which only depend on $\alpha$, $\beta$ and $\gamma$.
+Explicitly, we have $(\alpha',\beta',\gamma')=(\alpha,\beta,\gamma)$ if $\gamma=1$ and $(\alpha',\beta',\gamma')=(\beta,\alpha,\gamma)$ if $\gamma=-1$.
+
+In the following discussion, we outline a method to determine an upper bound on $\max_{a\in\F_2^n}\wt f(a)$.
+A similar approach can be applied to find a lower bound on $\min_{a\in\F_2^n}\wt f(a)$, and by utilizing both, we can also obtain an upper bound on $\max_{a\in\F_2^n}|\wt f(a)|$ by making use of the following identity:
+\[
+	\max_{a\in\F_2^n}|\wt f(a)|=\max\Big(\max_{a\in\F_2^n}\wt f(a),-\min_{a\in\F_2^n}\wt f(a)\Big).
+\]
+
+For each $k\in[1,n/2]$, we select $\{\alpha_k,\beta_k,\gamma_k\}=\{0,\pm 1\}$ with $\gamma_k\neq 0$ such that the following expression, based on the notation introduced in Remark~\ref{rmk:Dnka_dep_pqr}, is defined and maximized:
+\[
+	B_k^{p,q,r}=\mathsf D_{k,n}^{p+\alpha_k,q+\beta_k,r+\gamma_k}+\mathsf D_{k+n/2,n}^{p+\alpha_k',q+\beta_k',r+\gamma_k'}.
+\]
+This implies that $\Dnka{n}{k}{b_k}+\Dnka{n}{k+n/2}{b_{k+n/2}}\leq B_k^{p,q,r}$ for every $k\in[1,n/2]$, leading to the conclusion that $\sum_{k=1}^n\Dnka nk{b_k}\leq\sum_{k=1}^{n/2} B_k^{p,q,r}$.
+As a result, we derive the following upper bound:
+\begin{equation}\label{eqn:bound_walsh}
+	\max_{a\in\F_2^n}\wt f(a)\leq 1+\max_{p+q+r=n/2}\sum_{k=1}^{n/2} B_k^{p,q,r}.
+\end{equation}
+
+Under the assumption that the values of $\mathsf{D}_{k,n}^{p,q,r}$ have already been computed for all $k\in[1,n]$ and for all triplets $(p,q,r)$ satisfying $p+q+r=n/2$, the bound in equation (\ref{eqn:bound_walsh}) can be determined with a computational complexity of $\mathcal{O}(n^3)$.
+This is because there are $\mathcal{O}(n^2)$ possible triplets $(p,q,r)$ that meet the condition $p+q+r=n/2$, and the summation itself can be computed in $\mathcal{O}(n)$ steps.
+
+We consider now the complexity involved in computing the values of $\mathsf{D}_{k,n}^{p,q,r}$ for all $k\in[1,n]$ and all triplets $(p,q,r)$ satisfying $p+q+r=n/2$.
+We claim that this computation has a complexity of $\mathcal{O}(n^3 \log n)$.
+Towards this, it is sufficient to expand $(-z^2 + 2z + 1)^p \cdot (-z^2 - 2z + 1)^q \cdot (z^2 + 1)^r$ for all triplets $(p,q,r)$ such that $p+q+r=n/2$; this is due to Proposition \ref{proposition:generating_fct}.
+
+To achieve this, we first precompute the expanded polynomial $(-z^2 + 2z + 1)^p$ for each $p\in[0,n/2]$.
+This can be done recursively using the formula $(-z^2 + 2z + 1)^{p+1} = (-z^2 + 2z + 1) \cdot (-z^2 + 2z + 1)^p$.
+For each $p$, this requires $\mathcal O(n)$ arithmetic computations.
+Performing this for every $p$ results in a total complexity of $\mathcal{O}(n^2)$.
+The same approach can be used to expand the polynomials $(-z^2 - 2z + 1)^q$ and $(z^2 + 1)^r$, resulting in an overall complexity of $\mathcal{O}(n^2)$ for all $p,q,r\in[0,n/2]$.
+
+Finally, for each triplet $(p,q,r)$ satisfying $p+q+r=n/2$, we multiply the three expanded polynomials $(-z^2 + 2z + 1)^p$, $(-z^2 - 2z + 1)^q$ and $(z^2 + 1)^r$.
+These two multiplications are performed in $\mathcal{O}(n \log n)$ operations by using the fast Fourier transform.
+Given that there are $\mathcal{O}(n^2)$ triplets $(p,q,r)$ to consider, we conclude that precomputing the values $\mathsf{D}_{k,n}^{p,q,r}$ for all $k\in[1,n]$ and all triplets $(p,q,r)$ has a complexity of $\mathcal{O}(n^3 \log n)$, making the overall complexity of the procedure also $\mathcal{O}(n^3 \log n)$.
+
+\bigskip
+
+In Table~\ref{table:max_walsh_vs_bound}, we compare the exact values of $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ for small values of $n$ (calculated using \textsf{SageMath}) to the bound $B_n$ obtained through the above method and to the bound from Corollary~\ref{cor:bound_walsh_cauchy}.
+Additionally, Table~\ref{table:walsh_bounds} provides the values of the bound $B_n$ for all even values of $n\in[1,80]$.
+The method described above offers a tighter bound compared to Corollary~\ref{cor:bound_walsh_cauchy}.
+Its polynomial complexity makes it possible to extend the analysis well beyond the limitations imposed by a full computation of the Walsh spectrum, which requires a complexity of $\mathcal O(n2^n)$.
+\ifnum\anon=0
+	We provide a \textsf{SageMath} implementation to obtain the bound $B_n$: \url{https://github.com/se-tim/Revisited-HWBF.git}.
+\fi
+
+\begin{table}
+	\scriptsize
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		$n$ & $\max_{a\in\F_2^n}|\wt f(a)|$ & $B_n$  & $\lfloor 1+n \cdot 2^{3n/4} \rfloor$\\
+		\hline
+		$2$  & $2$     & $2$  &  $6$ \\
+		$4$  & $8$     & $8$  & $33$  \\
+		$6$  & $20$    & $28$   & $136$\\
+		$8$  & $52$    & $76$  & $513$ \\
+		$10$ & $108$   & $212$  & $1\,811$\\
+		$12$ & $292$   & $596$  & $6\,145$ \\
+		$14$ & $700$   & $1\,828$ & $20\,275$ \\
+		$16$ & $2\,176$  & $5\,196$ & $65\,537$ \\
+		$18$ & $4\,964$  & $14\,668$ & $208\,535$ \\
+		$20$ & $14\,968$ & $41\,468$ & $655\,361$ \\
+		$22$ & $34\,232$ & $118\,544$ & $2\,039 \,002$ \\
+		$24$ & $109\,648$ & $325\,188$ & $6\,291 \,457$  \\
+		\hline
+	\end{tabular}
+	\mycaption{The actual $\max_{a\in\F_2^n}|\wt f(a)|$ compared to the bound $B_n$ and the theoretical bound from Corollary~\ref{cor:bound_walsh_cauchy}.}
+	\label{table:max_walsh_vs_bound}
+\end{table}
+
+\begin{table}
+	\scriptsize
+	\centering
+	\begin{minipage}{0.24\textwidth}
+		\centering
+		\begin{tabular}{|c|c|}
+			\hline
+			$n$ & $\approx B_n$ \\
+			\hline
+			$2$  & $2.00 \cdot 10^{0}$  \\
+			$4$  & $8.00 \cdot 10^{0}$  \\
+			$6$  & $2.80 \cdot 10^{1}$  \\
+			$8$  & $7.60 \cdot 10^{1}$  \\
+			$10$ & $2.12 \cdot 10^{2}$  \\
+			$12$ & $5.96 \cdot 10^{2}$  \\
+			$14$ & $1.83 \cdot 10^{3}$  \\
+			$16$ & $5.20 \cdot 10^{3}$  \\
+			$18$ & $1.47 \cdot 10^{4}$  \\
+			$20$ & $4.15 \cdot 10^{4}$  \\
+			\hline
+		\end{tabular}
+	\end{minipage}%
+	\begin{minipage}{0.24\textwidth}
+		\centering
+		\begin{tabular}{|c|c|}
+			\hline
+			$n$ & $\approx B_n$ \\
+			\hline
+			$22$ & $1.19 \cdot 10^{5}$  \\
+			$24$ & $3.25 \cdot 10^{5}$  \\
+			$26$ & $9.59 \cdot 10^{5}$  \\
+			$28$ & $2.68 \cdot 10^{6}$  \\
+			$30$ & $7.65 \cdot 10^{6}$  \\
+			$32$ & $2.14 \cdot 10^{7}$  \\
+			$34$ & $6.25 \cdot 10^{7}$  \\
+			$36$ & $1.76 \cdot 10^{8}$  \\
+			$38$ & $5.03 \cdot 10^{8}$  \\
+			$40$ & $1.40 \cdot 10^{9}$  \\
+			\hline
+		\end{tabular}
+	\end{minipage}%
+	\begin{minipage}{0.24\textwidth}
+		\centering
+		\begin{tabular}{|c|c|}
+			\hline
+			$n$ & $\approx B_n$ \\
+			\hline
+			$42$ & $4.01 \cdot 10^{9}$  \\
+			$44$ & $1.12 \cdot 10^{10}$ \\
+			$46$ & $3.21 \cdot 10^{10}$ \\
+			$48$ & $8.91 \cdot 10^{10}$ \\
+			$50$ & $2.56 \cdot 10^{11}$ \\
+			$52$ & $7.12 \cdot 10^{11}$ \\
+			$54$ & $2.05 \cdot 10^{12}$ \\
+			$56$ & $5.73 \cdot 10^{12}$ \\
+			$58$ & $1.65 \cdot 10^{13}$ \\
+			$60$ & $4.59 \cdot 10^{13}$ \\
+			\hline
+		\end{tabular}
+	\end{minipage}%
+	\begin{minipage}{0.24\textwidth}
+		\centering
+		\begin{tabular}{|c|c|}
+			\hline
+			$n$ & $\approx B_n$ \\
+			\hline
+			$62$ & $1.32 \cdot 10^{14}$ \\
+			$64$ & $3.66 \cdot 10^{14}$ \\
+			$66$ & $1.05 \cdot 10^{15}$ \\
+			$68$ & $2.93 \cdot 10^{15}$ \\
+			$70$ & $8.40 \cdot 10^{15}$ \\
+			$72$ & $2.33 \cdot 10^{16}$ \\
+			$74$ & $6.71 \cdot 10^{16}$ \\
+			$76$ & $1.87 \cdot 10^{17}$ \\
+			$78$ & $5.39 \cdot 10^{17}$ \\
+			$80$ & $1.51 \cdot 10^{18}$ \\
+			\hline
+		\end{tabular}
+	\end{minipage}
+	\mycaption{Approximate values of $B_n$ for various values of $n$.}
+	\label{table:walsh_bounds}
+\end{table}
+
+\subsection{Comparison of the nonlinearity}
+
+In this part, we compare the nonlinearity of the revisited \hwbf{} to other weightwise quadratic functions considered for similar use-cases, such as the majority function, the \hwbf{} and the cyclic weightwise functions studied in~\cite{DAM:MeaOza24}.
+
+In Figure~\ref{fig:walsh_bound_comparison}, we compare bounds for the values of $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$ for various functions $f\in\BN$, where a smaller maximum indicates better nonlinearity, see Definition~\ref{def:nl}.
+We present values for $n$ up to $80$, which is sufficient for examining the asymptotic behavior of the different bounds.
+The pink and orange curves represent the upper bounds  in~\cite{DAM:MeaOza24}, with the orange curve mostly overlapping the pink one.
+To go into more detail, the pink curve corresponds to the bound that holds for all cyclic weightwise linear functions $f$ that, with the notation from Definition~\ref{def:wwdegd}, satisfy $ f_0(x) = b \cdot x $ for $\w(b)$ odd; therefore, this represents for instance an upper bound for the \hwbf{}.
+The orange curve corresponds to the bound for the cyclic weightwise quadratic function $f$ defined by $f_0(x) = x_1 + x_2 x_3$.
+The blue curve applies to both the majority and \hwbf{} functions, whose exact nonlinearities are given in Property~\ref{prop:wwd1}.
+We use a single curve here because, on a logarithmic scale, the nonlinearity difference between these two functions is too small to distinguish between them.
+For the revisited \hwbf{} introduced in Definition~\ref{def:revHWBF}, the red curve corresponds to the theoretical bound from Corollary~\ref{cor:bound_walsh_cauchy}, while the green curve represents the experimental results from Section~\ref{sec:expwt}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=9cm]{comparison_walsh_bound.pdf}
+	\mycaption{
+		Bounds on $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$ for various functions $f\in\BN$ and even values of $n$, shown on a logarithmic scale.
+The pink and orange curves, the orange one mostly covering the pink one, represent bounds for cyclic weightwise linear functions and a cyclic weightwise quadratic function from~\cite{DAM:MeaOza24}, respectively.
+The blue curve shows bounds for the majority function and the \hwbf{}.
+The theoretical bound for the revisited \hwbf{} (Corollary~\ref{cor:bound_walsh_cauchy}) is in red, and the experimental bound $B_n$ (Section~\ref{sec:expwt}) is in green.}
+	\label{fig:walsh_bound_comparison}
+\end{figure}
+
+The revisited \hwbf{} demonstrates significantly better performance compared to the majority function, the original \hwbf{} and the functions studied in \cite{DAM:MeaOza24}.
+Its theoretical bound on $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$ reveals an asymptotic slope of $3/4$ on a logarithmic scale, contrasting with the slope of $1$ for the majority function, the \hwbf{}, and the bounds proven in~\cite{DAM:MeaOza24}.
+Notably, the green curve corresponding to the bound of Section~\ref{sec:expwt} appears to share this asymptotic slope of $3/4$, supporting the effectiveness of Corollary~\ref{cor:bound_walsh_cauchy} and the stronger Theorem~\ref{theorem:bound_D_nka_generalized} in capturing asymptotic behavior.
+
+\bigskip
+
+We also compare in Table~\ref{table:comparisonsNL} the precise nonlinearity values of the functions under consideration.
+Among the various weightwise quadratic functions studied so far, we observe that the revisited \hwbf{} has the highest nonlinearity from $n=10$ onward.
+
+\begin{table}
+	\scriptsize
+	\centering
+	\begin{tabular}{|c| c|c|c|c| c|c|c|}
+		\hline
+		$n$ & $4$  & $6$  & $8$  &  $10$ & $12$ & $14$ & $16$  \\
+		\hline	
+		\hwbf{}   & $4$  & $20$  & $88$  &  $372$ & $1\,544$ & $6\,344$ & $25\,904$  \\  	
+		Majority   & $5$  & $22$  & $93$  &  $386$ & $1\,586$ & $6\,476$ & $26\,333$  \\
+		$t$~\cite{DAM:MeaOza24}   & $4$  & $22$  & $96$  &  $404$ & $1\,672$ & $6\,854$ & $27\,884$\\
+		$u$~\cite{DAM:MeaOza24}   & $4$  & $24$  & $104$  &  $456$ & $1\,888$ & $7\,816$ & $31\,616$ \\
+		Revisited \hwbf{}  & $4$  & $22$  & $102$  &  $458$ & $1\,902$ & $7\,842$ & $31\,680$\\
+		\hline
+	\end{tabular}
+	\mycaption{Comparison of the nonlinearity.}
+	\label{table:comparisonsNL}
+\end{table}
+
+\section{Other parameters}\label{sec:otherParameters}
+
+In this section, we present additional cryptographic parameters for the revisited \hwbf{}.
+While Theorem~\ref{th:bal} describes its balancedness and Sections~\ref{sec:Cauchy} and \ref{sec:expAndComp} thoroughly explore its nonlinearity, our focus here will be on its algebraic characteristics.
+Specifically, we will examine the degree, the algebraic immunity, and the fast algebraic immunity, and offer comparisons with other weightwise quadratic functions.
+
+\begin{proposition}
+	Let $n\geq 4$ be even, and let $f\in\BN$ be the revisited \hwbf{}. Then $\degg(f)=n-1$.
+\end{proposition}
+\begin{proof}
+	We write $f=q+h$, where $q\in\BN$ is given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$ and $h\in\BN$ is the \hwbf{}.
+The function $h$ has degree $n-1\geq 3$ by Property~\ref{prop:wwd1}, and the function $q$ has no monomial of degree higher than $2$, so that $\degg(f)=\degg(h)=n-1$.
+\end{proof}
+
+In Table~\ref{table:comparisonsDegAI}, we also display the algebraic degree of different weightwise quadratic function.
+We observe that the revisited \hwbf{} is the function with the highest degree, together with the \hwbf{}.
+
+\begin{table}
+	\scriptsize
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|c|c|}
+		\hline
+		$n$ & $4$  & $6$  & $8$  &  $10$ & $12$ & $14$ & $16$  \\
+		\hline
+		\hwbf{}   & $3, 2$  & $5, 3$  & $7, 4$  &  $9, 4$ & $11, 5$ & $13, 5$ & $15, 6$  \\  	
+		Majority   & $4, 2$  & $4, 3$  & $8, 4$  &  $8, 5$ & $8, 6$ & $8, 7$ & $16, 8$  \\
+		$t$~\cite{DAM:MeaOza24}   & $2, 2$  & $5, 3$  & $6, 4$  &  $9, 5$ & $11, 5$ & $13, 6$ & $14, 7$\\
+		$u$~\cite{DAM:MeaOza24}   & $2, 2$  & $4, 3$  & $6, 4$  &  $8, 5$ & $10, 6$ & $12, 6$ & $14, 7$ \\
+		Revisited \hwbf{}  & $3, 2$  & $5, 3$  & $7, 4$  &  $9, 5$ & $11, 6$ & $13, 6$ & $15, 7$\\
+		\hline
+	\end{tabular}
+	\mycaption{Comparison of the degree and algebraic immunity.}
+	\label{table:comparisonsDegAI}
+\end{table}
+
+\begin{proposition}
+	Let $n\geq 4$ be even, let $f\in\BN$ be the revisited \hwbf{}, and let $h\in\BN$ be the \hwbf{}. Then $\AI(f)\geq \AI(h)-2$.
+\end{proposition}
+
+\begin{proof}
+	Let $q\in\BN$ be given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$, so that $h=f+q$.
+	Let $g\in\BN^*$ with $\degg(g)=\AI(f)$ be an annihilator of $f+ \varepsilon$ for some $\varepsilon\in\{0,1\}$. Then the following holds:
+	\begin{align*}
+		g\cdot(q+1) \cdot(h+\varepsilon)&= g\cdot(q+1)\cdot(f+q+\varepsilon)\\
+		&=g\cdot(q+1)\cdot(f+\epsilon)+g\cdot(q+1)\cdot q\\
+		&=0+0\\
+		&=0.
+	\end{align*}
+	Hence, $g\cdot(q+1)$ is an annihilator of $h+ \varepsilon$.
+If $g\cdot(q+1)\ne 0$, it follows that $\AI(h)\leq\degg(g\cdot(q+1))\leq\degg(g)+\degg(q+1)$, and therefore that $\AI(f)=\degg(g)\geq\AI(h)-\degg(q+1)=\AI(h)-2$.
+If $g\cdot(q+1)=0$, then $0=g\cdot(f+\epsilon+q+1)=g\cdot(h+\epsilon+1)$, showing that $\AI(f)=\degg(g)\geq\AI(h)$.
+\end{proof}
+
+From Theorem 4 in~\cite{DAM:WCST14}, the algebraic immunity of the \hwbf{} is at least $\lfloor n/3\rfloor +1$, which leads to $\lfloor n/3\rfloor -1$ for the revisited \hwbf{}.
+In Table~\ref{table:comparisonsDegAI}, we present the algebraic immunity of various weightwise quadratic functions.
+We observe that the revisited \hwbf{} demonstrates the best performance after the majority function; the latter is known to achieve optimal algebraic immunity.
+
+Lastly, we also considered the fast algebraic immunity of the revisited \hwbf{} $f$.
+In Table~\ref{table:FAI}, we give the best couples $(d,e)$ encountered for the function $f$, where $\degg(g)=d$ and $\degg(h)=e$ for functions $g$ and $h$ satisfying $fg=h$.
+
+\bigskip
+
+These various results on the algebraic properties of the revisited \hwbf{} suggest that it possesses strong resistance against standard attacks.
+Furthermore, its high nonlinearity makes it a well-suited candidate for use as a filter function in contexts such as filtered \textsf{LFSR}s or in homomorphically-friendly schemes like \textsf{FLIP} and \textsf{FiLIP}.
+
+\begin{table}
+	\scriptsize
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+		\hline
+		$ n $      & $4$     & $6$     & $8$     & $10$    & $12$    & $14$    & $16$    & $18$    \\
+		\hline
+		$(d, e)$ & $(1,2)$ & $(1,3)$ & $(1,5)$  & $(1,7)$ & $(1,9)$ & $(1,11)$ & $(1,13)$ & $(1,15)$ \\ 
+		&     &    & $(2,4)$  & $(2,6)$ & $(2,8)$ & $(2,10)$ & $(2,12)$ & $(2,14)$\\ 
+		&     &    &     & $(3,5)$ & $(3,6)$ & $(3,9)$ & $(3,11)$ & $(3,13)$\\ 
+		&     &    &     &  &  &  & $(4,9)$ & $(4,11)$\\ 
+	 	&     &    &     &  &  &  &  & $(5,10)$ \\
+		\hline
+	\end{tabular}
+	\mycaption{Lowest possible values of $(d, e)$ for different values of $n$.}
+	\label{table:FAI}
+\end{table}
+
+\section{Conclusion and open questions}
+
+In this work, we introduced the revisited hidden weight bit function, a weightwise quadratic Boolean function with improved cryptographic properties over existing constructions.
+We analyzed its balancedness, and using generating functions in combination with complex analysis, we derived interesting lower bounds on its nonlinearity, demonstrating that the revisited \hwbf{} achieves superior nonlinearity compared to other functions with similar computational costs.
+We further examined other cryptographic parameters such as degree, algebraic immunity, and fast algebraic immunity, confirming that the revisited \hwbf{} matches or outperforms comparable functions in these aspects.
+
+Our approach utilizes generating functions and Cauchy’s estimate to establish lower bounds on the nonlinearity of weightwise quadratic functions.
+This naturally raises the question: can the employed techniques, particularly the use of Cauchy’s estimate, be extended to other families of Boolean functions?
+Specifically, this approach appears feasible for other weightwise-degree-$d$ functions $f$ where the $f_k$ are direct sums.
+Investigating this could potentially lead to the discovery of new functions with comparable computational costs and even better cryptographic properties.
+
+\ifnum\anon=0
+	\section{Acknowledgments}
+	Pierrick Méaux was funded by the European Research Council (\textsf{ERC}) under the Advanced Grant program (reference number: 787390).
+Tim Seuré acknowledges the support of the Luxembourgish “Fonds National de la Recherche” (\textsf{FNR}) through an Individual Grant (reference number: 17936291).
+\fi
+
+\newpage
+
+\ifnum\full=0
+	\bibliographystyle{splncs04}
+	\bibliography{add}
+\else
+	\bibliographystyle{alpha}
+	\bibliography{add}
+\fi
+
+\appendix
+
+\section{Proofs for Section~\ref{sec:general}}\label{sec:proofs}
+
+In this section, we provide the missing proofs for Section~\ref{sec:general}.
+
+\begin{proof}[Proof of Proposition~\ref{proposition:dtn}]
+    By considering binary vectors $x\in\F_2^n$ as $x=(y,z)$ with $y\in\F_2^{2t}$ and $z\in\F_2^{n-2t}$, we get:	
+	\begin{align*}
+		\Dtkna{t}{k}{n}{a}&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}\\
+		&=\sum_{(y,z)\in\Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
+		&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
+		&=\sum_{\ell=0}^{2t}\left(\sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{2t}(y)+b \cdot y}\right)\left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c \cdot z}\right)\\&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b}\cdot\kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
+	\end{align*}
+\end{proof}
+
+\begin{proof}[Proof of Proposition~\ref{proposition:sum_dtn}]
+    Applying Proposition \ref{proposition:dtn}, we get:
+    \begin{align*}
+        \sum_{k\in\Z}\Dtkna{t}{k}{n}{a}z^k&=\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\sum_{k\in\Z}\kraw{k-\ell}{\w(c)}{n-2t}z^{k-\ell}\\
+        &=\left(\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\right)\cdot(1+z)^u\cdot(1-z)^v\\
+        &=P_b(z)\cdot(1+z)^u\cdot(1-z)^v\\
+        &=P_{t,a}(z).\qedhere
+    \end{align*}
+\end{proof}
+
+Lastly, we provide a proof for Theorem~\ref{theorem:bound_D_nka_generalized}.
+We start with a preliminary result that will be required for the proof.
+
+\begin{lemma}\label{lemma:maximizing_args}
+    Let $N\geq 1$ be an integer and $D\subseteq\C$ a set of complex numbers.
+For every $i\in[1,N]$, consider integers $m_i\geq 0$ and $k_i\geq 1$, as well as complex functions $f_{i,1},\dots,f_{i,k_i}:D\to\C$.
+Assume that the following maximum exists (which holds for instance if the functions $f_{i,j}$ are continuous and $D$ is topologically compact):
+    \[
+        M=\max_{\substack{\forall i\in[1,N]:\,p_{i,1}+\cdots+p_{i,k_i}=m_i\\z\in D}}\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|.
+    \]
+    Then there exist integers $j_1,\dots,j_N$ with $j_i\in[1,k_i]$ such that the following holds:
+    \[
+        M=\max_{z\in D}\left|\prod_{i=1}^Nf_{i,j_i}(z)^{m_i}\right|.
+    \]
+\end{lemma}
+
+\begin{proof}
+    Let us choose the integers $p_{i,j}\geq 0$ satisfying $\sum_{j=1}^{k_i}p_{i,j}=m_i$ for every $i\in[1,N]$ together with the complex number $z\in D$ to maximize the quantity $\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|$.
+Next, for every $i\in[1,N]$, choose $j_i\in[1,k_i]$ such that $|f_{i,j_i}(z)|\geq|f_{i,j}(z)|$ for every $j\in[1,k_i]$.
+Then we have:
+    \begin{align*}
+        M&=\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j}(z)^{p_{i,j}}\right|\\
+		&\leq\left|\prod_{i=1}^N\prod_{j=1}^{k_i}f_{i,j_i}(z)^{p_{i,j}}\right|\\
+		&=\left|\prod_{i=1}^Nf_{i,j_i}(z)^{\sum_{j=1}^{k_i}p_{i,j}}\right|\\
+		&=\left|\prod_{i=1}^Nf_{i,j_i}(z)^{m_i}\right|\\
+		&\leq M.\qedhere
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{theorem:bound_D_nka_generalized}]
     To begin, we observe that the inequality $|\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{\mu n}$ will follow from the inequality $|\Dtkna tkna|\leq 2^{\mu n}$ using precisely the arguments of the proof of Corollary~\ref{cor:bound_walsh_cauchy}, so that we are only required to prove the first inequality.
@@
     where the last equality uses that $\ee^{2\ii\alpha}=\cos(2\alpha)+\ii\sin(2\alpha)$. We similarly obtain that $|1+z|^2=2+2\cos\alpha$. Combining both, we get:
-    \[
-        |P_{t,a}(z)|^2=\left(\left|-z^2+2z+1\right|^{2\lambda}|1+z|^{2(1-2\lambda)}\right)^n=\left((6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}\right)^n.
-    \]
-
+	\begin{align*}
+		P_{t,a}(z)|^2&=\left(\left|-z^2+2z+1\right|^{2\lambda}|1+z|^{2(1-2\lambda)}\right)^n\\
+		&=\left((6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}\right)^n.
+	\end{align*}
     The goal will be to prove that the maximum of $g(\alpha)=g^{(\lambda)}(\alpha)=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{t,a}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$.
@@
 
-    \begin{figure}[ht]
+    \begin{figure}
     	\centering
@@
          \frac{\dd}{\dd\alpha}g(\alpha)&=g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}\left(\lambda g_2(\alpha)\frac{\dd}{\dd\alpha}g_1(\alpha)+(1-2\lambda)g_1(\alpha)\frac{\dd}{\dd\alpha}g_2(\alpha)\right)\\
-         &=g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}\left(\lambda(2+2\cos\alpha)\cdot4\sin(2\alpha)+(1-2\lambda)(6-2\cos(2\alpha))(-2\sin\alpha)\right)\\
-         &=g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}\left(\lambda(2+2\cos\alpha)\cdot4\cdot2\cos\alpha\sin\alpha+(1-2\lambda)\left(8-4\cos^2\alpha\right)(-2\sin\alpha)\right)\\
-         &=8g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}\sin\alpha\left(2\lambda \cos\alpha(1+\cos\alpha)-(1-2\lambda)\left(2-\cos^2\alpha\right)\right)\\
+         &=g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}(\lambda(2+2\cos\alpha)\cdot4\sin(2\alpha)\\
+		 &\qquad+(1-2\lambda)(6-2\cos(2\alpha))(-2\sin\alpha))\\
+         &=g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}\big(\lambda(2+2\cos\alpha)\cdot4\cdot2\cos\alpha\sin\alpha\\
+		 &\qquad+(1-2\lambda)\left(8-4\cos^2\alpha\right)(-2\sin\alpha)\big)\\
+         &=8g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}\sin\alpha\big(2\lambda \cos\alpha(1+\cos\alpha)\\
+		 &\qquad-(1-2\lambda)\left(2-\cos^2\alpha\right)\big)\\
          &=8g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}\sin\alpha\left(\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2\right).
     \end{align*}
-
-    The only interesting zeros of $\frac{\dd}{\dd\alpha}g(\alpha)$ are those of the last factor 
-    $\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2$: the factor $8g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}$ has none, and those for $\sin\alpha$ are $\alpha=0$ and $\alpha=\pi$, with corresponding values $g(0)=2^{2-2\lambda}$ and $g(\pi)=0$.
+    The only interesting zeros of $\frac{\dd}{\dd\alpha}g(\alpha)$ are those of the last factor $\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2$: the factor $8g_1(\alpha)^{\lambda-1}g_2(\alpha)^{-2\lambda}$ has none, and those for $\sin\alpha$ are $\alpha=0$ and $\alpha=\pi$, with corresponding values $g(0)=2^{2-2\lambda}$ and $g(\pi)=0$.
 
@@
         &=\lim_{\alpha\to 0}\frac{\frac{\dd}{\dd\alpha}g(\alpha)}{\alpha}\\
-        &=\lim_{\alpha\to 0}8(6-2\cos(2\alpha))^{\lambda-1}(2+2\cos\alpha)^{-2\lambda}\cdot\frac{\sin\alpha}{\alpha}\cdot\left(\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2\right)\\
+        &=\lim_{\alpha\to 0}8(6-2\cos(2\alpha))^{\lambda-1}(2+2\cos\alpha)^{-2\lambda}\\
+		&\qquad\cdot\frac{\sin\alpha}{\alpha}\cdot\left(\cos^2\alpha+2\lambda\cos\alpha+4\lambda-2\right)\\
         &=8\cdot4^{\lambda-1}\cdot 4^{-2\lambda}\cdot 1\cdot(6\lambda -1)\\
@@
 \end{proof}
-
-The curve of $\lambda\mapsto\mu(\lambda)$ defined in the above Theorem~\ref{theorem:bound_D_nka_generalized} is represented in Figure~\ref{fig:curve_exponents_lambda_mu}.
-Observe that $\mu(1/2)=3/4$, which corresponds to Theorem~\ref{theorem:bound_D_nka}.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=9.5cm]{curve_exponents_lambda_mu.pdf}
-    \vspace{-5mm}
-	\mycaption{The curve of $\lambda\mapsto\mu(\lambda)$ with $0\leq\lambda\leq\frac 12$ from Theorem~\ref{theorem:bound_D_nka_generalized}.}
-	\label{fig:curve_exponents_lambda_mu}
-\end{figure}
-
-\section{Experiments and comparisons}\label{sec:expAndComp}
-
-In this section, we establish a tighter bound on the absolute value of the Walsh transform of the revisited \hwbf{} for even $n\in[1,80]$. 
-We then compare the nonlinearity of this function to that of other functions suited to similar use cases, such as the \hwbf{} or the weightwise cyclic functions from~\cite{DAM:MeaOza24}.
-
-\subsection{Bounding the Walsh transform of $f$ experimentally}\label{sec:expwt}
-
-Following Corollary~\ref{cor:bound_walsh_cauchy}, we deduce that $|\wt f(a)|\leq 1+n\cdot 2^{3n/4}$ for every even integer $n\geq 0$ and every binary vector $a\in\F_2^n$, where $f\in\BN$ denotes the revisited \hwbf{}.
-This is a somewhat pessimistic bound.
-In this part, we discuss how a tighter bound on $|\wt f(a)|$ can be obtained in polynomial time in $n$.
-
-This method is based on the identity given in Proposition~\ref{prop:WT}.
-For this, consider a vector $b\in\mathbb F_2^n$; we write $(p,q,r)=(p(b),q(b),r(b))$.
-Also, for $k\in[1,n]$, let $b_k=b+\pi(e_k)$ and $(p_k,q_k,r_k)=(p(b_k),q(b_k),r(b_k))$, where $\pi:[1,n]\to[1,n]$ is again the permutation sending the first $n/2$ elements to the odd positions and the $n/2$ last ones to the even positions.
-Notice first that for every integer $k\in[1,n]$, it holds that $(p_k,q_k,r_k)\in\{(p\pm1,q,r\mp 1),(p,q\pm 1,r\mp 1)\}$.
-Furthermore, observe that if $k\in[0,n/2]$ and $(p_k,q_k,r_k)=(p+\alpha,q+\beta,r+\gamma)$ for $\{\alpha,\beta,\gamma\}=\{0,\pm 1\}$ with $\gamma\neq 0$, then we have $(p_{k+n/2},q_{k+n/2},r_{k+n/2})=(p+\alpha',q+\beta',r+\gamma')$ for some $\{\alpha',\beta',\gamma'\}=\{0,\pm 1\}$ with $\gamma'\neq 0$ which only depend on $\alpha$, $\beta$ and $\gamma$.
-Explicitly, we have $(\alpha',\beta',\gamma')=(\alpha,\beta,\gamma)$ if $\gamma=1$ and $(\alpha',\beta',\gamma')=(\beta,\alpha,\gamma)$ if $\gamma=-1$.
-
-In the following discussion, we outline a method to determine an upper bound on $\max_{a\in\F_2^n}\wt f(a)$.
-A similar approach can be applied to find a lower bound on $\min_{a\in\F_2^n}\wt f(a)$, and by utilizing both, we can also obtain an upper bound on $\max_{a\in\F_2^n}|\wt f(a)|$ by making use of the following identity:
-\[
-	\max_{a\in\F_2^n}|\wt f(a)|=\max\Big(\max_{a\in\F_2^n}\wt f(a),-\min_{a\in\F_2^n}\wt f(a)\Big).
-\]
-
-For each $k\in[1,n/2]$, we select $\{\alpha_k,\beta_k,\gamma_k\}=\{0,\pm 1\}$ with $\gamma_k\neq 0$ such that the following expression, based on the notation introduced in Remark~\ref{rmk:Dnka_dep_pqr}, is defined and maximized:
-\[
-	B_k^{p,q,r}=\mathsf D_{k,n}^{p+\alpha_k,q+\beta_k,r+\gamma_k}+\mathsf D_{k+n/2,n}^{p+\alpha_k',q+\beta_k',r+\gamma_k'}.
-\]
-This implies that $\Dnka{n}{k}{b_k}+\Dnka{n}{k+n/2}{b_{k+n/2}}\leq B_k^{p,q,r}$ for every $k\in[1,n/2]$, leading to the conclusion that $\sum_{k=1}^n\Dnka nk{b_k}\leq\sum_{k=1}^{n/2} B_k^{p,q,r}$.
-As a result, we derive the following upper bound:
-\begin{equation}\label{eqn:bound_walsh}
-	\max_{a\in\F_2^n}\wt f(a)\leq 1+\max_{p+q+r=n/2}\sum_{k=1}^{n/2} B_k^{p,q,r}.
-\end{equation}
-
-Under the assumption that the values of $\mathsf{D}_{k,n}^{p,q,r}$ have already been computed for all $k\in[1,n]$ and for all triplets $(p,q,r)$ satisfying $p+q+r=n/2$, the bound in equation (\ref{eqn:bound_walsh}) can be determined with a computational complexity of $\mathcal{O}(n^3)$.
-This is because there are $\mathcal{O}(n^2)$ possible triplets $(p,q,r)$ that meet the condition $p+q+r=n/2$, and the summation itself can be computed in $\mathcal{O}(n)$ steps.
-
-We consider now the complexity involved in computing the values of $\mathsf{D}_{k,n}^{p,q,r}$ for all $k\in[1,n]$ and all triplets $(p,q,r)$ satisfying $p+q+r=n/2$.
-We claim that this computation has a complexity of $\mathcal{O}(n^3 \log n)$.
-Towards this, it is sufficient to expand $(-z^2 + 2z + 1)^p \cdot (-z^2 - 2z + 1)^q \cdot (z^2 + 1)^r$ for all triplets $(p,q,r)$ such that $p+q+r=n/2$; this is due to Proposition \ref{proposition:generating_fct}.
-
-To achieve this, we first precompute the expanded polynomial $(-z^2 + 2z + 1)^p$ for each $p\in[0,n/2]$.
-This can be done recursively using the formula $(-z^2 + 2z + 1)^{p+1} = (-z^2 + 2z + 1) \cdot (-z^2 + 2z + 1)^p$.
-For each $p$, this requires $\mathcal O(n)$ arithmetic computations.
-Performing this for every $p$ results in a total complexity of $\mathcal{O}(n^2)$.
-The same approach can be used to expand the polynomials $(-z^2 - 2z + 1)^q$ and $(z^2 + 1)^r$, resulting in an overall complexity of $\mathcal{O}(n^2)$ for all $p,q,r\in[0,n/2]$.
-
-Finally, for each triplet $(p,q,r)$ satisfying $p+q+r=n/2$, we multiply the three expanded polynomials $(-z^2 + 2z + 1)^p$, $(-z^2 - 2z + 1)^q$ and $(z^2 + 1)^r$.
-These two multiplications are performed in $\mathcal{O}(n \log n)$ operations by using the fast Fourier transform.
-Given that there are $\mathcal{O}(n^2)$ triplets $(p,q,r)$ to consider, we conclude that precomputing the values $\mathsf{D}_{k,n}^{p,q,r}$ for all $k\in[1,n]$ and all triplets $(p,q,r)$ has a complexity of $\mathcal{O}(n^3 \log n)$, making the overall complexity of the procedure also $\mathcal{O}(n^3 \log n)$.
-
-\bigskip
-
-In Table~\ref{table:max_walsh_vs_bound}, we compare the exact values of $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ for small values of $n$ (calculated using \textsf{SageMath}) to the bound $B_n$ obtained through the above method and to the bound from Corollary~\ref{cor:bound_walsh_cauchy}.
-Additionally, Table~\ref{table:walsh_bounds} provides the values of the bound $B_n$ for all even values of $n\in[1,80]$.
-The method described above offers a tighter bound compared to Corollary~\ref{cor:bound_walsh_cauchy}.
-Its polynomial complexity makes it possible to extend the analysis well beyond the limitations imposed by a full computation of the Walsh spectrum, which requires a complexity of $\mathcal O(n2^n)$.
-\ifnum\anon=0
-	We provide a \textsf{SageMath} implementation to obtain the bound $B_n$: \url{https://github.com/se-tim/Revisited-HWBF.git}.
-\fi
-
-\begin{table}[ht]
-	\small
-	\centering
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		$n$ & $\max_{a\in\F_2^n}|\wt f(a)|$ & $B_n$  & $\lfloor 1+n \cdot 2^{3n/4} \rfloor$\\ \hline
-		$2$  & $2$     & $2$  &  $6$ \\
-		$4$  & $8$     & $8$  & $33$  \\
-		$6$  & $20$    & $28$   & $136$\\
-		$8$  & $52$    & $76$  & $513$ \\
-		$10$ & $108$   & $212$  & $1\,811$\\
-		$12$ & $292$   & $596$  & $6\,145$ \\
-		$14$ & $700$   & $1\,828$ & $20\,275$ \\
-		$16$ & $2\,176$  & $5\,196$ & $65\,537$ \\
-		$18$ & $4\,964$  & $14\,668$ & $208\,535$ \\
-		$20$ & $14\,968$ & $41\,468$ & $655\,361$ \\
-		$22$ & $34\,232$ & $118\,544$ & $2\,039 \,002$ \\
-		$24$ & $109\,648$ & $325\,188$ & $6\,291 \,457$  \\ \hline
-	\end{tabular}
-	\mycaption{The actual $\max_{a\in\F_2^n}|\wt f(a)|$ compared to the bound $B_n$ and the theoretical bound from Corollary~\ref{cor:bound_walsh_cauchy}.}
-	\label{table:max_walsh_vs_bound}
-\end{table}
-
-\begin{table}[ht]
-	\small
-	\centering
-	\begin{minipage}{0.24\textwidth}
-		\centering
-		\begin{tabular}{|c|c|}
-			\hline
-			$n$ & $\approx B_n$ \\
-			\hline
-			$2$  & $2.00 \cdot 10^{0}$  \\
-			$4$  & $8.00 \cdot 10^{0}$  \\
-			$6$  & $2.80 \cdot 10^{1}$  \\
-			$8$  & $7.60 \cdot 10^{1}$  \\
-			$10$ & $2.12 \cdot 10^{2}$  \\
-			$12$ & $5.96 \cdot 10^{2}$  \\
-			$14$ & $1.83 \cdot 10^{3}$  \\
-			$16$ & $5.20 \cdot 10^{3}$  \\
-			$18$ & $1.47 \cdot 10^{4}$  \\
-			$20$ & $4.15 \cdot 10^{4}$  \\
-			\hline
-		\end{tabular}
-	\end{minipage}%
-	\begin{minipage}{0.24\textwidth}
-		\centering
-		\begin{tabular}{|c|c|}
-			\hline
-			$n$ & $\approx B_n$ \\
-			\hline
-			$22$ & $1.19 \cdot 10^{5}$  \\
-			$24$ & $3.25 \cdot 10^{5}$  \\
-			$26$ & $9.59 \cdot 10^{5}$  \\
-			$28$ & $2.68 \cdot 10^{6}$  \\
-			$30$ & $7.65 \cdot 10^{6}$  \\
-			$32$ & $2.14 \cdot 10^{7}$  \\
-			$34$ & $6.25 \cdot 10^{7}$  \\
-			$36$ & $1.76 \cdot 10^{8}$  \\
-			$38$ & $5.03 \cdot 10^{8}$  \\
-			$40$ & $1.40 \cdot 10^{9}$  \\
-			\hline
-		\end{tabular}
-	\end{minipage}%
-	\begin{minipage}{0.24\textwidth}
-		\centering
-		\begin{tabular}{|c|c|}
-			\hline
-			$n$ & $\approx B_n$ \\
-			\hline
-			$42$ & $4.01 \cdot 10^{9}$  \\
-			$44$ & $1.12 \cdot 10^{10}$ \\
-			$46$ & $3.21 \cdot 10^{10}$ \\
-			$48$ & $8.91 \cdot 10^{10}$ \\
-			$50$ & $2.56 \cdot 10^{11}$ \\
-			$52$ & $7.12 \cdot 10^{11}$ \\
-			$54$ & $2.05 \cdot 10^{12}$ \\
-			$56$ & $5.73 \cdot 10^{12}$ \\
-			$58$ & $1.65 \cdot 10^{13}$ \\
-			$60$ & $4.59 \cdot 10^{13}$ \\
-			\hline
-		\end{tabular}
-	\end{minipage}%
-	\begin{minipage}{0.24\textwidth}
-		\centering
-		\begin{tabular}{|c|c|}
-			\hline
-			$n$ & $\approx B_n$ \\
-			\hline
-			$62$ & $1.32 \cdot 10^{14}$ \\
-			$64$ & $3.66 \cdot 10^{14}$ \\
-			$66$ & $1.05 \cdot 10^{15}$ \\
-			$68$ & $2.93 \cdot 10^{15}$ \\
-			$70$ & $8.40 \cdot 10^{15}$ \\
-			$72$ & $2.33 \cdot 10^{16}$ \\
-			$74$ & $6.71 \cdot 10^{16}$ \\
-			$76$ & $1.87 \cdot 10^{17}$ \\
-			$78$ & $5.39 \cdot 10^{17}$ \\
-			$80$ & $1.51 \cdot 10^{18}$ \\
-			\hline
-		\end{tabular}
-	\end{minipage}
-	\mycaption{Approximate values of $B_n$ for various values of $n$.}
-	\label{table:walsh_bounds}
-\end{table}
-
-\subsection{Comparison of the nonlinearity}
-
-In this part, we compare the nonlinearity of the revisited \hwbf{} to other weightwise quadratic functions considered for similar use-cases, such as the majority function, the \hwbf{} and the cyclic weightwise functions studied in~\cite{DAM:MeaOza24}.
-
-In Figure~\ref{fig:walsh_bound_comparison}, we compare bounds for the values of $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$ for various functions $f\in\BN$, where a smaller maximum indicates better nonlinearity, see Definition~\ref{def:nl}.
-We present values for $n$ up to $80$, which is sufficient for examining the asymptotic behavior of the different bounds.
-The pink and orange curves represent the upper bounds  in~\cite{DAM:MeaOza24}, with the orange curve mostly overlapping the pink one.
-To go into more detail, the pink curve corresponds to the bound that holds for all cyclic weightwise linear functions $f$ that, with the notation from Definition~\ref{def:wwdegd}, satisfy $ f_0(x) = b \cdot x $ for $\w(b)$ odd; therefore, this represents for instance an upper bound for the \hwbf{}.
-The orange curve corresponds to the bound for the cyclic weightwise quadratic function $f$ defined by $f_0(x) = x_1 + x_2 x_3$.
-The blue curve applies to both the majority and \hwbf{} functions, whose exact nonlinearities are given in Property~\ref{prop:wwd1}.
-We use a single curve here because, on a logarithmic scale, the nonlinearity difference between these two functions is too small to distinguish between them.
-For the revisited \hwbf{} introduced in Definition~\ref{def:revHWBF}, the red curve corresponds to the theoretical bound from Corollary~\ref{cor:bound_walsh_cauchy}, while the green curve represents the experimental results from Section~\ref{sec:expwt}.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=10cm]{comparison_walsh_bound.pdf}
-	\mycaption{
-		Bounds on $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$ for various functions $f\in\BN$ and even values of $n$, shown on a logarithmic scale.
-		The pink and orange curves, the orange one mostly covering the pink one, represent bounds for cyclic weightwise linear functions and a cyclic weightwise quadratic function from~\cite{DAM:MeaOza24}, respectively.
-The blue curve shows bounds for the majority function and the \hwbf{}.
-The theoretical bound for the revisited \hwbf{} (Corollary~\ref{cor:bound_walsh_cauchy}) is in red, and the experimental bound $B_n$ (Section~\ref{sec:expwt}) is in green.}
-	\label{fig:walsh_bound_comparison}
-\end{figure}
-
-The revisited \hwbf{} demonstrates significantly better performance compared to the majority function, the original \hwbf{} and the functions studied in \cite{DAM:MeaOza24}.
-Its theoretical bound on $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$ reveals an asymptotic slope of $3/4$ on a logarithmic scale, contrasting with the slope of $1$ for the majority function, the \hwbf{}, and the bounds proven in~\cite{DAM:MeaOza24}.
-Notably, the green curve corresponding to the bound of Section~\ref{sec:expwt} appears to share this asymptotic slope of $3/4$, supporting the effectiveness of Corollary~\ref{cor:bound_walsh_cauchy} and the stronger Theorem~\ref{theorem:bound_D_nka_generalized} in capturing asymptotic behavior.
-
-\bigskip
-
-We also compare in Table~\ref{table:comparisonsNL} the precise nonlinearity values of the functions under consideration.
-Among the various weightwise quadratic functions studied so far, we observe that the revisited \hwbf{} has the highest nonlinearity from $n=10$ onward.
-
-\begin{table}[ht]
-	\small
-	\centering
-	\begin{tabular}{|c| c|c|c|c| c|c|c|}
-		\hline
-		$n$ & $4$  & $6$  & $8$  &  $10$ & $12$ & $14$ & $16$  \\
-		\hline	
-		\hwbf{}   & $4$  & $20$  & $88$  &  $372$ & $1\,544$ & $6\,344$ & $25\,904$  \\  	
-		Majority   & $5$  & $22$  & $93$  &  $386$ & $1\,586$ & $6\,476$ & $26\,333$  \\
-		$t$~\cite{DAM:MeaOza24}   & $4$  & $22$  & $96$  &  $404$ & $1\,672$ & $6\,854$ & $27\,884$\\
-		$u$~\cite{DAM:MeaOza24}   & $4$  & $24$  & $104$  &  $456$ & $1\,888$ & $7\,816$ & $31\,616$ \\
-		Revisited \hwbf{}  & $4$  & $22$  & $102$  &  $458$ & $1\,902$ & $7\,842$ & $31\,680$\\
-\hline
-	\end{tabular}
-	\mycaption{Comparison of the nonlinearity.}
-	\label{table:comparisonsNL}
-\end{table}
-
-\section{Other parameters}\label{sec:otherParameters}
-
-In this section, we present additional cryptographic parameters for the revisited \hwbf{}.
-While Theorem~\ref{th:bal} describes its balancedness and Sections~\ref{sec:Cauchy} and \ref{sec:expAndComp} thoroughly explore its nonlinearity, our focus here will be on its algebraic characteristics.
-Specifically, we will examine the degree, the algebraic immunity, and the fast algebraic immunity, and offer comparisons with other weightwise quadratic functions.
-
-\begin{proposition}
-	Let $n\geq 4$ be even, and let $f\in\BN$ be the revisited \hwbf{}. Then $\degg(f)=n-1$.
-\end{proposition}
-\begin{proof}
-	We write $f=q+h$, where $q\in\BN$ is given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$ and $h\in\BN$ is the \hwbf{}.
-	The function $h$ has degree $n-1\geq 3$ by Property~\ref{prop:wwd1}, and the function $q$ has no monomial of degree higher than $2$, so that $\degg(f)=\degg(h)=n-1$.
-\end{proof}
-
-In Table~\ref{table:comparisonsDeg}, we display the algebraic degree of different weightwise quadratic function.
-We observe that the revisited \hwbf{} is the function with the highest degree, together with the \hwbf{}.
-
-\begin{table}[ht]
-	\small
-	\centering
-	\begin{tabular}{|c|c|c|c|c|c|c|c|}
-		\hline
-		$n$ & $4$  & $6$  & $8$  &  $10$ & $12$ & $14$ & $16$  \\
-		\hline
-		\hwbf{}   & $3$  & $5$  & $7$  &  $9$ & $11$ & $13$ & $15$  \\  	
-		Majority   & $4$  & $4$  & $8$  &  $8$ & $8$ & $8$ & $16$  \\
-		$t$~\cite{DAM:MeaOza24}   & $2$  & $5$  & $6$  &  $9$ & $11$ & $13$ & $14$\\
-		$u$~\cite{DAM:MeaOza24}   & $2$  & $4$  & $6$  &  $8$ & $10$ & $12$ & $14$ \\
-		Revisited \hwbf{}  & $3$  & $5$  & $7$  &  $9$ & $11$ & $13$ & $15$\\
-		\hline
-	\end{tabular}
-	\mycaption{Comparison of the degree.}
-	\label{table:comparisonsDeg}
-\end{table}
-
-\begin{proposition}
-	Let $n\geq 4$ be even, let $f\in\BN$ be the revisited \hwbf{}, and let $h\in\BN$ be the \hwbf{}. Then the following holds:
-	\[\AI(f)\geq \AI(h)-2.\]
-\end{proposition}
-
-\begin{proof}
-	Let $q\in\BN$ be given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$, so that $h=f+q$.
-	Let $g\in\BN^*$ with $\degg(g)=\AI(f)$ be an annihilator of $f+ \varepsilon$ for some $\varepsilon\in\{0,1\}$. 
-	Then the following holds:
-	\[g\cdot(q+1) \cdot(h+\varepsilon) = g\cdot(q+1)\cdot(f+q+\varepsilon)=g\cdot(q+1)\cdot(f+\epsilon)+g\cdot(q+1)\cdot q=0+0=0.\]
-	Hence, $g\cdot(q+1)$ is an annihilator of $h+ \varepsilon$. 
-	If $g\cdot(q+1)\ne 0$, it follows that $\AI(h)\leq\degg(g\cdot(q+1))\leq\degg(g)+\degg(q+1)$, and therefore that $\AI(f)=\degg(g)\geq\AI(h)-\degg(q+1)=\AI(h)-2$.
-If $g\cdot(q+1)=0$, then $0=g\cdot(f+\epsilon+q+1)=g\cdot(h+\epsilon+1)$, showing that $\AI(f)=\degg(g)\geq\AI(h)$.
-\end{proof}
-
-From Theorem 4 in~\cite{DAM:WCST14}, the algebraic immunity of the \hwbf{} is at least $\lfloor n/3\rfloor +1$, which leads to $\lfloor n/3\rfloor -1$ for the revisited \hwbf{}.
-In Table~\ref{table:comparisonsAI}, we present the algebraic immunity of various weightwise quadratic functions.
-We observe that the revisited \hwbf{} demonstrates the best performance after the majority function; the latter is known to achieve optimal algebraic immunity.
-
-\begin{table}[ht]
-	\small
-	\centering
-	\begin{tabular}{|c| c|c|c|c| c|c|c|}
-		\hline
-		$n$ & $4$  & $6$  & $8$  &  $10$ & $12$ & $14$ & $16$  \\
-		\hline	
-		\hwbf{}   & $2$  & $3$  & $4$  &  $4$ & $5$ & $5$ & $6$  \\  	
-		Majority   & $2$  & $3$  & $4$  &  $5$ & $6$ & $7$ & $8$  \\
-		$t$~\cite{DAM:MeaOza24}   & $2$  & $3$  & $4$  &  $5$ & $5$ & $6$ & $7$\\
-		$u$~\cite{DAM:MeaOza24}   & $2$  & $3$  & $4$  &  $5$ & $6$ & $6$ & $7$ \\					
-		Revisited \hwbf{}   & $2$  & $3$  & $4$  &  $5$ & $6$ & $6$ & $7$\\
-		\hline
-	\end{tabular}
-	\mycaption{Comparison of the algebraic immunity.}
-	\label{table:comparisonsAI}
-\end{table}
-
-Lastly, we also considered the fast algebraic immunity of the revisited \hwbf{} $f$.
-In Table~\ref{table:FAI}, we give the best couples $(d,e)$ encountered for the function $f$, where $\degg(g)=d$ and $\degg(h)=e$ for functions $g$ and $h$ satisfying $fg=h$.
-
-\bigskip
-
-These various results on the algebraic properties of the revisited \hwbf{} suggest that it possesses strong resistance against standard attacks.
-Furthermore, its high nonlinearity makes it a well-suited candidate for use as a filter function in contexts such as filtered \textsf{LFSR}s or in homomorphically-friendly schemes like \textsf{FLIP} and \textsf{FiLIP}.
-
-\begin{table}[ht]
-	\small
-	\centering
-	\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
-		\hline
-		$ n $      & $4$     & $6$     & $8$     & $10$    & $12$    & $14$    & $16$    & $18$    \\ \hline
-		$(d, e)$ & $(1,2)$ & $(1,3)$ & $(1,5)$  & $(1,7)$ & $(1,9)$ & $(1,11)$ & $(1,13)$ & $(1,15)$ \\ 
-		&     &    & $(2,4)$  & $(2,6)$ & $(2,8)$ & $(2,10)$ & $(2,12)$ & $(2,14)$\\ 
-		&     &    &     & $(3,5)$ & $(3,6)$ & $(3,9)$ & $(3,11)$ & $(3,13)$\\ 
-		&     &    &     &  &  &  & $(4,9)$ & $(4,11)$\\ 
-	 	&     &    &     &  &  &  &  & $(5,10)$ \\ \hline
-	\end{tabular}
-	\mycaption{Lowest possible values of $(d, e)$ for different values of $n$.}
-	\label{table:FAI}
-\end{table}
-
-\section{Conclusion and open questions}
-
-In this work, we introduced the revisited hidden weight bit function, a weightwise quadratic Boolean function with improved cryptographic properties over existing constructions. 
-We analyzed its balancedness, and using generating functions in combination with complex analysis, we derived interesting lower bounds on its nonlinearity, demonstrating that the revisited \hwbf{} achieves superior nonlinearity compared to other functions with similar computational costs.
-We further examined other cryptographic parameters such as degree, algebraic immunity, and fast algebraic immunity, confirming that the revisited \hwbf{} matches or outperforms comparable functions in these aspects.
-
-Our approach utilizes generating functions and Cauchy’s estimate to establish lower bounds on the nonlinearity of weightwise quadratic functions. 
-This naturally raises the question: can the employed techniques, particularly the use of Cauchy’s estimate, be extended to other families of Boolean functions?
-Specifically, this approach appears feasible for other weightwise-degree-$d$ functions $f$ where the $f_k$ are direct sums.
-Investigating this could potentially lead to the discovery of new functions with comparable computational costs and even better cryptographic properties.
-
-\ifnum\anon=0
-	\section{Acknowledgments}
-	Pierrick Méaux was funded by the European Research Council (\textsf{ERC}) under the Advanced Grant program (reference number: 787390).
-Tim Seuré acknowledges the support of the Luxembourgish “Fonds National de la Recherche” (\textsf{FNR}) through an Individual Grant (reference number: 17936291).
-\fi
-
-\newpage
-
-\ifnum\full=0
-	\bibliographystyle{splncs04}
-	\bibliography{add}
-\else
-	\bibliographystyle{alpha}
-	\bibliography{add}
-\fi
-
 \end{document}

### 2025-03-17 RevisedHiddenWeight.tex
Typos and bibliography

@@
 
-\begin{definition}[Walsh transform, restricted Walsh transform]\label{def:walsh_transform}
+\begin{definition}[Walsh transform]\label{def:walsh_transform}
 	The Walsh transform at $a \in \F_2^n$ of a Boolean function $f\in\BN$ restricted to a subset $S\subseteq \F_2^n$ is defined as $\wt{f,S} (a) = \sum_{x\in S} (-1)^{f(x)+a \cdot x}$.
@@
 
-Various weightwise affine functions (\ie, belonging to $\WD{1}{n}$) have been exhibited, such as in~\cite{TOSC:CarMeaRot17} where the bent functions in Propositions $1$ and $2$ are weightwise affine, or in~\cite{DAM:GinMea22} to show than no weightwise perfectly balanced function is weightwise affine for $n\geq 8$.
+Various weightwise affine functions (\ie, belonging to $\WD{1}{n}$) have been exhibited, such as in~\cite{TOSC:CarMeaRot17} where the bent functions in Propositions $1$ and $2$ are weightwise affine, or in~\cite{DAM:GinMea22} to show that no weightwise perfectly balanced function is weightwise affine for $n\geq 8$.
 The arguably best known example of weightwise affine function is the Hidden Weight Bit Function introduced in~\cite{IEEE:Bryant91}, the one obtained by fixing $f_0=0$ and $f_k=x_k$ for $k \in [1,n]$.
@@
 These bounds focus on cyclic weightwise quadratic functions and involve sums of binomial coefficients.
-For simplicity, in the following we provide only the nonlinearity values of the majority function and \hwbf{}, as these bounds will be used for comparison.
+For simplicity, in the following, we provide only the nonlinearity values of the majority function and \hwbf{}, as these bounds will be used for comparison.
 
@@
 
-Accordingly, we can study the restricted Walsh transform of the revisited \hwbf{} by analyzing the one of the following Boolean function $d_n\in\BN$.
+Accordingly, we can study the restricted Walsh transform of the revisited \hwbf{} by analyzing the following Boolean function $d_n\in\BN$.
 
@@
 \begin{proposition}\label{prop:recursiveDnka}
-Let $n\geq 0$ be an even integer. Then for all integers $k$ and all binary vectors $a\in\F_2^n$, the following hold true:
+Let $n\geq 0$ be an even integer. Then for all integers $k$ and all binary vectors $a\in\F_2^n$, the following hold:
 	\begin{itemize}
@@
     The recursive formula of Proposition~\ref{prop:recursiveDnka} gives different cases depending on the values of the pair $(a_{n-1},a_n)$.
-However, the same reasoning applies with any pair of the form $(a_{2i-1}, a_{2i})$ for $i\in[1,n/2]$.
+However, the same reasoning applies to any pair of the form $(a_{2i-1}, a_{2i})$ for $i\in[1,n/2]$.
 Therefore, the value of $\Dnka{n}{k}{a}$ depends only on the number of pairs $(a_{2i-1}, a_{2i})$ in $a$ being $(0,0)$, $(1,1)$, $(0,1)$ or $(1,0)$.
@@
 Thus, the coefficient $\Dnka nka$ in $P_a(z)$ of $z^k$ for odd $k$ must be zero.
-It follows that also $\Dnka n{n-k}a=0$ by Proposition~\ref{proposition:symmetry}.
+It also follows that $\Dnka n{n-k}a=0$ by Proposition~\ref{proposition:symmetry}.
 \end{proof}
@@
 	We use the expressions from Table~\ref{tab:Dnka_small_k}, and replace $p$, $q$ and $r$ by their respective values.
-For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$ in the expression $\Dnka n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dnka n2a=0$.~\footnote{This checking can be automatized by a computer algebra system.
+For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$, respectively, in the expression $\Dnka n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dnka n2a=0$.~\footnote{This checking can be automatized by a computer algebra system.
 	\ifnum\anon=0
@@
 Notice first that for every integer $k\in[1,n]$, it holds that $(p_k,q_k,r_k)\in\{(p\pm1,q,r\mp 1),(p,q\pm 1,r\mp 1)\}$.
-Furthermore, observe that if $k\in[0,n/2]$ and $(p_k,q_k,r_k)=(p+\alpha,q+\beta,r+\gamma)$ for $\{\alpha,\beta,\gamma\}=\{0,\pm 1\}$ with $\gamma\neq 0$, then we have $(p_{k+n/2},q_{k+n/2},r_{k+n/2})=(p+\alpha',q+\beta',r+\gamma')$ for some $\{\alpha',\beta',\gamma'\}=\{0,\pm 1\}$ with $\gamma'\neq 0$ which only depend on $\alpha$, $\beta$ and $\gamma$.
+Furthermore, observe that if $k\in[0,n/2]$ and $(p_k,q_k,r_k)=(p+\alpha,q+\beta,r+\gamma)$ for $\{\alpha,\beta,\gamma\}=\{0,\pm 1\}$ with $\gamma\neq 0$, then we have $(p_{k+n/2},q_{k+n/2},r_{k+n/2})=(p+\alpha',q+\beta',r+\gamma')$ for some $\{\alpha',\beta',\gamma'\}=\{0,\pm 1\}$ with $\gamma'\neq 0$, where $\alpha'$,$\beta'$ and $\gamma'$ only depend on $\alpha$, $\beta$ and $\gamma$.
 Explicitly, we have $(\alpha',\beta',\gamma')=(\alpha,\beta,\gamma)$ if $\gamma=1$ and $(\alpha',\beta',\gamma')=(\beta,\alpha,\gamma)$ if $\gamma=-1$.
@@
 
-In Table~\ref{table:comparisonsDegAI}, we also display the algebraic degree of different weightwise quadratic function.
+In Table~\ref{table:comparisonsDegAI}, we also display the algebraic degree of different weightwise quadratic functions.
 We observe that the revisited \hwbf{} is the function with the highest degree, together with the \hwbf{}.
@@
 
-\ifnum\full=0
 \bibliographystyle{splncs04}
 \bibliography{add}
-\else
-	\bibliographystyle{alpha}
-	\bibliography{add}
-\fi
 

### 2025-03-17 RevisedHiddenWeight.tex
Updated comment of Table 6

@@
 	\centering
-	\includegraphics[width=9cm]{comparison_walsh_bound.pdf}
+	\includegraphics[width=8.5cm]{comparison_walsh_bound.pdf}
 	\mycaption{
@@
 The blue curve shows bounds for the majority function and the \hwbf{}.
-The theoretical bound for the revisited \hwbf{} (Corollary~\ref{cor:bound_walsh_cauchy}) is in red, and the experimental bound $B_n$ (Section~\ref{sec:expwt}) is in green.}
+The theoretical bound for the revisited \hwbf{} (Corollary~\ref{cor:bound_walsh_cauchy}) is in red, the experimental bound $B_n$ (Section~\ref{sec:expwt}) is in green.}
 	\label{fig:walsh_bound_comparison}
@@
 	We write $f=q+h$, where $q\in\BN$ is given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$ and $h\in\BN$ is the \hwbf{}.
-The function $h$ has degree $n-1\geq 3$ by Property~\ref{prop:wwd1}, and the function $q$ has no monomial of degree higher than $2$, so that $\degg(f)=\degg(h)=n-1$.
+The function $h$ has degree $n-1\geq 3$ by Property~\ref{prop:wwd1}, and the function $q$ has no monomial of degree higher than $2$, so $\degg(f)=\degg(h)=n-1$.
 \end{proof}
@@
 In Table~\ref{table:comparisonsDegAI}, we also display the algebraic degree of different weightwise quadratic functions.
-We observe that the revisited \hwbf{} is the function with the highest degree, together with the \hwbf{}.
+We observe that the revisited \hwbf{} has the highest degree along with the original \hwbf{} when $n$ is not a power of $2$.
+However, when $n$ is a power of $2$, the majority function has a degree that is one higher than that of the other two functions.
 

### 2025-03-19 RevisedHiddenWeight.tex
Addressing reviewer comments

@@
 
-In~\cite{DAM:MeaOza24}, the parameters of different functions from $\WD{1}{n}$ and $\WD{2}{n}$ are studied experimentally for $n$ up to $20$, and lower bounds are given for the nonlinearity for all $n$.
+In~\cite{DAM:MeaOza24}, the parameters of different functions from $\WD{1}{n}$ and $\WD{2}{n}$ are studied experimentally for $n\leq 20$, and lower bounds are given for the nonlinearity for all $n$.
 These bounds focus on cyclic weightwise quadratic functions and involve sums of binomial coefficients.
@@
 
-\begin{Prop}\label{prop:wwd1}
-	Let $n\geq 2$ be an even integer.
+\begin{Prop}\label{prop:wwd1}\mbox{}
 	\begin{itemize}
-		\item (\textit{E.g.}, Theorem $3$ in~\cite{DCC:DalMaiSar06}) The majority function $\mathsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies $\NL(\mathsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}$.
-		\item (Theorem $3$ in~\cite{DAM:WCST14}) The \hwbf{} $h$ introduced in Definition~\ref{def:hwbf} satisfies $\NL(h)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}$.
-		\item (Theorem $1$ in \cite{DAM:WCST14}) The \hwbf{} $h$ introduced in Definition~\ref{def:hwbf} satisfies $\degg(h)=n-1$ if $n\geq 4$.
+		\item (\textit{E.g.}, Theorem $3$ and Theorem $2$ in~\cite{DCC:DalMaiSar06}) The majority function $\mathsf{Maj}_n\in\BN$ satisfies $\NL(\mathsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}$ and $\degg(\mathsf{Maj}_n)=2^{\lfloor\log_2(n)\rfloor}$ for even $n\geq 2$.
+		\item (Theorem $3$ and Theorem $1$ in~\cite{DAM:WCST14}) The \hwbf{} $h\in\BN$ satisfies $\NL(h)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}$ for even $n\geq 2$ and $\degg(h)=n-1$ for even $n\geq 4$.
 	\end{itemize}
@@
 
-\begin{definition}[Revisited \hwbf{}]\label{def:revHWBF}
+\subsection{Definition and basic properties}
+
+\begin{definition}[Revisited Hidden Weight Bit Function]\label{def:revHWBF}
 	For an even integer $n\geq 0$, we call revisited \hwbf{} the Boolean function $f\in\BN$ defined as:
@@
 Since $f$ is the sum of a quadratic function and a weightwise affine function, it is a weightwise quadratic function.
+Note that, while the \hwbf{} can be computed by first computing the Hamming weight of the input and then applying a linear function, the revisited \hwbf{} can be computed by first computing the Hamming weight of the input and then applying a quadratic function, leading to a similar computational cost to for both.
+
 Using the formalism of Definition~\ref{def:wwdegd}, $f$ is the weightwise quadratic function defined by $f_0(x)=0$ and $f_k(x)=x_k+\sum_{i=1}^{n/2}(x_i+1) x_{i+n/2}$ for $k\in[1,n]$.
@@
 		&\qquad+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2}\binom{n/2-1}{(k-1)/2}\right)\\
-		&=0+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right)\\
-		&=2\left(\sum_{i=\lceil n/4\rceil}^{n/2-1} \binom {n/2-1}{i} - \sum_{i=0}^{\lfloor(n-2)/4\rfloor} \binom{n/2-1}{i}\right).
-	\end{align*}
+		&=0+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right).
+	\end{align*}
+	Therefore, we get $\wt{f}(0_n)=2\left(\sum_{i=\lceil n/4\rceil}^{n/2-1} \binom {n/2-1}{i} - \sum_{i=0}^{\lfloor(n-2)/4\rfloor} \binom{n/2-1}{i}\right)$.
 The final result follows by applying that $\binom{n}{k}=\binom{n}{n-k}$ for all integers $n\geq 0$ and $k$.
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:deg_rhwbf}
 	Let $n\geq 4$ be even, and let $f\in\BN$ be the revisited \hwbf{}. Then $\degg(f)=n-1$.
@@
 We observe that the revisited \hwbf{} has the highest degree along with the original \hwbf{} when $n$ is not a power of $2$.
-However, when $n$ is a power of $2$, the majority function has a degree that is one higher than that of the other two functions.
+However, when $n$ is a power of $2$, the majority function has a degree that is one higher than that of the other two functions, as explained by Property~\ref{prop:wwd1} and Proposition~\ref{prop:deg_rhwbf}.
 
@@
 
-In this work, we introduced the revisited hidden weight bit function, a weightwise quadratic Boolean function with improved cryptographic properties over existing constructions.
+In this work, we introduced the revisited Hidden Weight Bit Function, a weightwise quadratic Boolean function with improved cryptographic properties over existing constructions.
 We analyzed its balancedness, and using generating functions in combination with complex analysis, we derived interesting lower bounds on its nonlinearity, demonstrating that the revisited \hwbf{} achieves superior nonlinearity compared to other functions with similar computational costs.

### 2025-03-26 RevisedHiddenWeight.tex
draft answer

--- 2025-03-17 RevisedHiddenWeight.tex
@@
 
+\pmnote{For example, the filter functions leading to the best current performances for FiLIP in HHE~\cite{CCS:CDPP22,CIC:MeaParPei24,eprint:AGHM24} are xor-threshold functions, the direct sum of a $k$-variable linear function and an $m$-variable function giving $1$ if and only if the input has Hamming weight at least a threshold $d$ (which generalizes the majority function).
+Using Proposition $7$ in~\cite{IEEE:CarMea21}, the nonlinearity of a xor-threshold function is at most:
+\[2^{n-1}-2^k \cdot M \text{ where }
+M=\left\{\begin{array}{ll}
+\binom{m-1}{\frac{m-1}{2}}&\text{ if }m\equiv 1\bmod 2,\\
+\frac{1}{2} \binom{m}{\frac{m}{2}}&\text{ if }m\equiv 0\bmod 2.\\
+\end{array}\right.
+\]
+The nonlinearity of this whole family of functions is similar to the one of the majority, hence the revisited HWBF provides a better nonlinearity that currently used filters for FiLIP for the same sizes, allowing to thwart correlation-like attacks with functions in less variables.}
+
 \begin{table}
@@
     By considering binary vectors $x\in\F_2^n$ as $x=(y,z)$ with $y\in\F_2^{2t}$ and $z\in\F_2^{n-2t}$, we get:	
-	\begin{align*}
+	\begin{align*}^
 		\Dtkna{t}{k}{n}{a}&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}\\

### 2025-03-26 RevisedHiddenWeight.tex
xthr comment

--- 2025-03-19 RevisedHiddenWeight.tex
@@
 Furthermore, its high nonlinearity makes it a well-suited candidate for use as a filter function in contexts such as filtered \textsf{LFSR}s or in homomorphically-friendly schemes like \textsf{FLIP} and \textsf{FiLIP}.
-
+%\pmnote{For example, the filter functions leading to the best current performances for FiLIP in HHE~\cite{CCS:CDPP22,CIC:MeaParPei24,eprint:AGHM24} are xor-threshold functions, the direct sum of a $k$-variable linear function and an $m$-variable function giving $1$ if and only if the input has Hamming weight at least a threshold $d$ (which generalizes the majority function).
+Using Proposition $7$ in~\cite{IEEE:CarMea21}, the nonlinearity of a xor-threshold function is at most:
+%\[2^{n-1}-2^k \cdot M \text{ where }
+%M=\left\{\begin{array}{ll}
+%\binom{m-1}{\frac{m-1}{2}}&\text{ if }m\equiv 1\bmod 2,\\
+%\frac{1}{2} \binom{m}{\frac{m}{2}}&\text{ if }m\equiv 0\bmod 2.\\
+%\end{array}\right.
+%\]
+%The nonlinearity of this whole family of functions is similar to the one of the majority, hence the revisited HWBF provides a better nonlinearity that currently used filters for FiLIP for the same sizes, allowing to thwart correlation-like attacks with functions in less variables.}
+For example, the best current \textsf{FiLIP} filters in HHE~\cite{CCS:CDPP22,CIC:MeaParPei24,eprint:AGHM24} are xor-threshold functions—the sum of a $k$-variable linear function and an $m$-variable threshold function (generalizing majority).
+By Proposition $7$ in~\cite{IEEE:CarMea21}, their nonlinearity is at most:
+\[
+2^{n-1} - 2^k \cdot M, \quad \text{where } M = \begin{cases}
+\binom{m-1}{\frac{m-1}{2}} & \text{if } m \text{ odd}, \\
+\frac{1}{2} \binom{m}{\frac{m}{2}} & \text{if } m \text{ even}.
+\end{cases}
+\]
+This is similar to majority, whereas the revisited HWBF achieves higher nonlinearity for the same size, offering better resistance to correlation-like attacks with fewer variables.
 \begin{table}

### 2025-03-26 RevisedHiddenWeight.tex
Notation modif's

--- 2025-03-26 RevisedHiddenWeight.tex
@@
-\def\anon{1} %Set to 1 for anonymous submissions, hides acknowledgements and author names
+\def\anon{0} %Set to 1 for anonymous submissions, hides acknowledgements and author names
 \def\full{1} %Set to 0 for springer proceedings
@@
 Furthermore, its high nonlinearity makes it a well-suited candidate for use as a filter function in contexts such as filtered \textsf{LFSR}s or in homomorphically-friendly schemes like \textsf{FLIP} and \textsf{FiLIP}.
-
-\pmnote{For example, the filter functions leading to the best current performances for FiLIP in HHE~\cite{CCS:CDPP22,CIC:MeaParPei24,eprint:AGHM24} are xor-threshold functions, the direct sum of a $k$-variable linear function and an $m$-variable function giving $1$ if and only if the input has Hamming weight at least a threshold $d$ (which generalizes the majority function).
-Using Proposition $7$ in~\cite{IEEE:CarMea21}, the nonlinearity of a xor-threshold function is at most:
-\[2^{n-1}-2^k \cdot M \text{ where }
-M=\left\{\begin{array}{ll}
-\binom{m-1}{\frac{m-1}{2}}&\text{ if }m\equiv 1\bmod 2,\\
-\frac{1}{2} \binom{m}{\frac{m}{2}}&\text{ if }m\equiv 0\bmod 2.\\
-\end{array}\right.
-\]
-The nonlinearity of this whole family of functions is similar to the one of the majority, hence the revisited HWBF provides a better nonlinearity that currently used filters for FiLIP for the same sizes, allowing to thwart correlation-like attacks with functions in less variables.}
-
+For example, the best current \textsf{FiLIP} filters in \textsf{HHE}~\cite{CCS:CDPP22,CIC:MeaParPei24,eprint:AGHM24} are \textsf{XOR}-threshold functions—the sum of a $k$-variable linear function and an $m$-variable threshold function (generalizing majority).
+By Proposition $7$ in~\cite{IEEE:CarMea21}, their nonlinearity is at most:
+\[
+2^{k+m-1} - 2^k \cdot M, \quad \text{where } M = \begin{cases}
+\binom{m-1}{\frac{m-1}{2}} & \text{if } m \text{ is odd}, \\
+\frac{1}{2} \binom{m}{\frac{m}{2}} & \text{if } m \text{ is even}.
+\end{cases}
+\]
+This is similar to the majority function, whereas the revisited \hwbf{} achieves higher nonlinearity for the same size, offering better resistance to correlation-like attacks with fewer variables.
 \begin{table}

### 2025-07-29 RevisedHiddenWeight.tex
Acknowledgment
Minor

@@
 Since $f$ is the sum of a quadratic function and a weightwise affine function, it is a weightwise quadratic function.
-Note that, while the \hwbf{} can be computed by first computing the Hamming weight of the input and then applying a linear function, the revisited \hwbf{} can be computed by first computing the Hamming weight of the input and then applying a quadratic function, leading to a similar computational cost to for both.
+Note that, while the \hwbf{} can be computed by first computing the Hamming weight of the input and then applying a linear function, the revisited \hwbf{} can be computed by first computing the Hamming weight of the input and then applying a quadratic function, leading to a similar computational cost for both.
 
@@
 Tim Seuré acknowledges the support of the Luxembourgish “Fonds National de la Recherche” (\textsf{FNR}) through an Individual Grant (reference number: 17936291).
+The work of Deng Tang was supported in part by the National Natural Science Foundation of China (\textsf{NSFC}, reference number: 62272303).
+We would also like to thank Claude Carlet for discussing the function introduced in this work with Deng Tang some years ago.
 \fi

### 2025-08-26 paper.tex
Springer version

--- 2025-07-29 RevisedHiddenWeight.tex
@@
-\def\anon{0} %Set to 1 for anonymous submissions, hides acknowledgements and author names
-\def\full{1} %Set to 0 for springer proceedings
-
-\ifnum\full=1
-	\documentclass{llncs}
-\else
-	\documentclass[10pt, runningheads]{llncs}
-	\usepackage{times}
-\fi
-
-\input{header.tex}
-
-\begin{document}
-
-\setcounter{page}{1}
+\documentclass[runningheads,orivec]{llncs}
+
+\let\proof\relax
+\let\endproof\relax
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsthm}
+\usepackage[T1]{fontenc}
+\usepackage{graphicx}
+\usepackage{microtype}
+
+\newcommand{\AI}{\mathsf{AI}}
+\newcommand{\Bfn}[1]{\mathcal{B}_{#1}}
+\newcommand{\BN}{\mathcal{B}_n}
+\newcommand{\C}{\mathbb{C}}
+\newcommand{\dd}{\,\mathrm d}
+\newcommand{\degg}{\mathsf{deg}}
+\newcommand{\dis}{\mathsf{c_1}}
+\newcommand{\Dkna}[3]{\mathsf{D}_{#2,#1}(a)}
+\newcommand{\Dtkna}[4]{\mathsf{D}_{#1,#2,#3}(#4)}
+\newcommand{\ee}{\mathrm e\mkern1mu}
+\newcommand{\eg}{\textit{e.g.}}
+\newcommand{\Ekn}[2]{\mathsf{E}_{#1,#2}}
+\newcommand{\F}{\mathbb{F}}
+\newcommand{\FAI}{\mathsf{FAI}}
+\newcommand{\hd}{\mathsf{d_H}}
+\newcommand{\hwbf}{\ensuremath{\mathsf{HWBF}}}
+\newcommand{\ie}{\textit{i.e.}}
+\newcommand{\ii}{\mathrm i\mkern1mu}
+\newcommand{\kraw}[3]{\mathsf{K}_{#1}(#2,#3)}
+\newcommand{\myurl}[1]{\footnote{\texttt{\url{#1}}}}
+\newcommand{\NL}{\mathsf{NL}}
+\newcommand{\phikn}[2]{\varphi_{#1,#2}}
+\newcommand{\w}{\mathsf{w_H}}
+\newcommand{\WD}[2]{\mathcal{WD}^{#1}_{#2}}
+\newcommand{\wt}[1]{\mathcal W_{#1}} 
+\newcommand{\wtk}[2]{\mathcal{W}_{#1,#2}}
+\newcommand{\Z}{\mathbb{Z}}
+
+\let\leq=\leqslant
+\let\geq=\geqslant
 
 \title{The Revisited Hidden Weight Bit Function}
-\titlerunning{The Revisited Hidden Weight Bit Function}
-
-\ifnum\anon=0
+\titlerunning{Revisited \hwbf{}}
+
 \author{%
-		Pierrick M\'eaux\inst{1},
-		Tim Seuré\inst{1}, 
-		Deng Tang\inst{2}
+    Pierrick Méaux\inst{1}\orcidID{0000-0001-5733-4341} \and
+    Tim Seuré\inst{1}\orcidID{0000-0003-4200-7553} \and %Corresponding author
+    Deng Tang\inst{2}\orcidID{0000-0002-8373-9200}
 }
-	\authorrunning{P.\ M\'eaux, T.\ Seur\'e, D.\ Tang}
+\authorrunning{P. Méaux et al.}
+
 \institute{%
@@
 }
-\else
-	\author{}
-	\institute{}
-\fi
-
+
+\begin{document}    
     \maketitle
-
-\pagestyle{plain}
 
@@
     The Hidden Weight Bit Function (\hwbf{}) has attracted significant attention since its introduction by Bryant in 1991~\cite{IEEE:Bryant91}.
-It has been regarded as the simplest example of a function whose binary decision diagram has exponential size~\cite{IEEE:Bryant91,TIA:BoLSW99}.
+It has been regarded as the simplest example of a function whose binary decision diagram has exponential size~\cite{TIA:BoLSW99,IEEE:Bryant91}.
 The ease of implementing this function across various computational models—owing to its reliance on computing the Hamming weight of the input and applying a simple linear function—combined with its relatively strong cryptographic properties as demonstrated in~\cite{DAM:WCST14} (\eg, balancedness, nonlinearity, degree, and algebraic immunity), has made it a noteworthy candidate for use as a filter function in stream cipher constructions.
@@
 For instance, several new binary stream ciphers have been proposed since 2016, including Kreyvium~\cite{JOC:CCFLNP18}, \textsf{FLIP}~\cite{EC:MJSC16}, Rasta~\cite{C:Rasta}, \textsf{FiLIP}~\cite{INDO:MCJS19}, Dasta~\cite{TOSC:BeiLea20} and Fasta~\cite{CTRSA:CidIndRad22}.
-Currently, designs employing Boolean functions with more than one hundred variables as filters lead to \textsf{HHE} schemes with the best latency~\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24,eprint:AGHM24}.
+Currently, designs employing Boolean functions with more than one hundred variables as filters lead to \textsf{HHE} schemes with the best latency~\cite{eprint:AGHM24,CCS:CDPP22,INDO:HofMeaRic20,CIC:MeaParPei24}.
 
@@
 
-\subsection{Boolean functions and cryptographic parameters}
+    \subsection{Boolean Functions and Cryptographic Parameters}
 
@@
 
-\begin{definition}[Algebraic Normal Form, degree]\label{def:anf}
-	We call Algebraic Normal Form of a Boolean function $f\in\BN$ its unique representation as an element of the ring $\F_2[x_1,\dots,x_n]/(x_1^2+x_1,\dots,x_n^2+x_n)$, and we express it as $f(x_1,\dots,x_n)= \sum_{I \subseteq [1,n]} a_I \left( \prod_{i \in I} x_i \right)$, where $a_I\in \F_2$.
+    \begin{definition}[Algebraic normal form, degree]\label{def:anf}
+    	We call algebraic normal form of a Boolean function $f\in\BN$ its unique representation as an element of the ring $\F_2[x_1,\dots,x_n]/(x_1^2+x_1,\dots,x_n^2+x_n)$, and we express it as $f(x_1,\dots,x_n)= \sum_{I \subseteq [1,n]} a_I \left( \prod_{i \in I} x_i \right)$, where $a_I\in \F_2$.
 The (algebraic) degree of $f$ is defined by $\degg(f)=0$ in case $f$ is the null function, and $\degg(f)=\max\{ |I|:I\subseteq[1,n],a_I=1\}$ otherwise.
@@
     \begin{definition}[Walsh transform]\label{def:walsh_transform}
-	The Walsh transform at $a \in \F_2^n$ of a Boolean function $f\in\BN$ restricted to a subset $S\subseteq \F_2^n$ is defined as $\wt{f,S} (a) = \sum_{x\in S} (-1)^{f(x)+a \cdot x}$.
+    	The Walsh transform at $a \in \F_2^n$ of $f\in\BN$ restricted to a subset $S\subseteq \F_2^n$ is defined as $\wt{f,S} (a) = \sum_{x\in S} (-1)^{f(x)+a\cdot x}$.
 The (unrestricted) Walsh transform of $f$ is then defined as $\wt{f}=\wt{f,\F_2^n}$.
@@
 
-\begin{definition}[Fast algebraic immunity, \eg, \cite{EC:ACGKMR06,IEEE:LiuLinPei11,DCC:CarTan15}]\label{def:FAI}
-	The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined to be $\FAI(f)=\min \{ 2 \AI(f), \min\{\degg(g)+ \degg(fg):g\in\BN,1\leq\degg(g)<\AI(f)\}\}$.
-\end{definition}
-
-\subsection{Symmetric Functions, \hwbf{} and weightwise degree-$d$ functions}
+    \begin{definition}[Fast algebraic immunity, \eg, \cite{EC:ACGKMR06,DCC:CarTan15,IEEE:LiuLinPei11}]\label{def:FAI}
+    	The fast algebraic immunity of $f\in \Bfn{n}$ is defined as $\FAI(f)=\min \{ 2 \AI(f), \min\{\degg(g)+ \degg(fg):g\in\BN,1\leq\degg(g)<\AI(f)\}\}$.
+    \end{definition}
+
+    \subsection{Symmetric Functions, \hwbf{} and Weightwise Degree-$d$ Functions}
 
     Recall that the Boolean symmetric functions in $n$ variables are those that are constant on the slice $\Ekn{k}{n}$ for every $k\in [0,n]$.
-This class of functions has been thoroughly studied in the context of cryptography, see \eg, \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,IEEE:CheLu11,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
+This class of functions has been thoroughly studied in the context of cryptography, see \eg, \cite{INDO:BraPre05,IEEE:CanVid05,IEEE:Carlet04,IEEE:CarMea21,IEEE:CheLu11,Latin:Meaux19,CCDS:Meaux21,IEEE:QFLW09,DM:SarMai07}.
 In this article, the symmetric functions that we consider will mainly be the slice indicator function and the majority function.
 
-\begin{definition}[Slice indicator functions]\label{def:slice}
+    \begin{definition}[Slice Indicator Functions]\label{def:slice}
     	The indicator function of the slice of weight $k\in[0,n]$ is the function $\phikn kn\in\BN$ defined by $\phikn kn(x)=1$ if and only if $\w(x)=k$.
@@
 
-\begin{Prop}\label{prop:wwd1}\mbox{}
+    \begin{property}\label{property:wwd1}\mbox{}
     	\begin{itemize}
@@
     	\end{itemize}
-\end{Prop}
-
-\subsection{Krawtchouk polynomials}
+    \end{property}
+
+    \subsection{Krawtchouk Polynomials}
 
@@
     	The $n$-th Krawtchouk polynomial of degree $k\in\Z$ is given by $\kraw{k}{x}{n}=\sum_{j=0}^{k} (-1)^j \binom{x}{j} \binom{n-x}{k-j}$.
-The Krawtchouk polynomials can alternatively be characterized as the coefficients in the generating function for $(1+z)^{n-x} (1-z)^x$ in the variable $z$, that is, $(1+z)^{n-x} (1-z)^x=\sum_{k\in\Z} \kraw{k}{x}{n} z^k$.
-\end{definition}
-
-\section{Revisited \hwbf{} and balancedness}\label{sec:defAndBal}
+Alternatively, the Krawtchouk polynomials can be characterized as the coefficients in the generating function for $(1+z)^{n-x} (1-z)^x$ in the variable $z$, that is, $(1+z)^{n-x} (1-z)^x=\sum_{k\in\Z} \kraw{k}{x}{n} z^k$.
+    \end{definition}
+
+    \section{Revisited \hwbf{} and Balancedness}\label{sec:defAndBal}
 
@@
 
-\subsection{Definition and basic properties}
+    \subsection{Definition and Basic Properties}
 
@@
     	\[
-		\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+n/2}+ c \cdot x}.
+    		\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+n/2}+ c\cdot x}.
     	\]
@@
     \begin{proof}
-	We compute:
-	\begin{align*}
-		\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+a \cdot x}\\
-		&=\sum_{x \in \Ekn{k}{n}} (-1)^{x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}+ a \cdot x}\\
-		&=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+n/2}+\left(x_k+\sum_{i=n/2+1}^{n}x_i+a\cdot x\right)}\\
-		&=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+n/2}+ c \cdot x}.\qedhere
+    	By definition, we have $\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}+ a\cdot x}$. Therefore:
+    	\begin{align*}
+    		\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+n/2}+\left(x_k+\sum_{i=n/2+1}^{n}x_i+a\cdot x\right)}\\
+    		&=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+n/2}+ c\cdot x}.\qedhere
     	\end{align*}
@@
     	\[
-		\Dnka{n}{k}{a}=\wtk{d_n}{k}(a)=\sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a\cdot x}.
-	\]
-\end{definition}
-
-The $\Dnka{n}{k}{a}$ satisfy a recursive relation.
-
-\begin{proposition}\label{prop:recursiveDnka}
+    		\Dkna{n}{k}{a}=\wtk{d_n}{k}(a)=\sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a\cdot x}.
+    	\]
+    \end{definition}
+
+    The $\Dkna{n}{k}{a}$ satisfy a recursive relation.
+
+    \begin{proposition}\label{prop:recursiveDkna}
     Let $n\geq 0$ be an even integer. Then for all integers $k$ and all binary vectors $a\in\F_2^n$, the following hold:
     	\begin{itemize}
-		\item We have $\Dnka 00a=1$ and $\Dnka 0ka=0$ if $k\neq 0$.
+    		\item We have $\Dkna 00a=1$ and $\Dkna 0ka=0$ if $k\neq 0$.
     		\item If $n\geq 2$, then for $b=(a_1,\dots,a_{n-2})\in\F_2^{n-2}$, we have:
     		\begin{align*}
-			\Dnka{n}{k}{a}&=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b}\\
-			&\qquad+ (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.
+    			\Dkna{n}{k}{a}&=\Dkna{n-2}{k}{b}+\left((-1)^{a_{n-1}} + (-1)^{a_{n}}\right)\Dkna{n-2}{k-1}{b}\\
+    			&\qquad+ (-1)^{1+a_{n-1}+a_n} \Dkna{n-2}{k-2}{b}.
     		\end{align*}
@@
     \begin{proof}
-    We have that $\Dnka 00a=(-1)^0=1$ since $\Ekn 00=\{\varepsilon\}$ for the empty vector $\varepsilon=a\in\F_2^0$.
-That $\Dnka 0ka=0$ if $k\neq 0$ follows from $\Ekn k0$ being empty if $k\neq 0$.
+        We have that $\Dkna 00a=(-1)^0=1$ since $\Ekn 00=\{\varepsilon\}$ for the empty vector $\varepsilon=a\in\F_2^0$.
+That $\Dkna 0ka=0$ if $k\neq 0$ follows from $\Ekn k0$ being empty if $k\neq 0$.
 Assume now that $n\geq 2$.
@@
         \begin{align*}
-		\Dnka{n}{k}{a}&=\sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a\cdot x}\\
+    		\Dkna{n}{k}{a}&=\sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a\cdot x}\\
     		&=\sum_{y\in \Ekn{k}{n-2}} (-1)^{d_{n-2}(y) +b\cdot y}+
@@
     		&\qquad+\sum_{y\in \Ekn{k-2}{n-2}} (-1)^{d_{n-2}(y) +b\cdot y +1 + a_{n-1}+ a_{n}}\\
-		&=\Dnka{n-2}{k}{b}+\left((-1)^{a_{n-1}}+ (-1)^{a_{n}}\right)\Dnka{n-2}{k-1}{b}\\
-		&\qquad+ (-1)^{1+a_{n-1}+a_n} \Dnka{n-2}{k-2}{b}.\qedhere
+    		&=\Dkna{n-2}{k}{b}+\left((-1)^{a_{n-1}}+ (-1)^{a_{n}}\right)\Dkna{n-2}{k-1}{b}\\
+    		&\qquad+ (-1)^{1+a_{n-1}+a_n} \Dkna{n-2}{k-2}{b}.\qedhere
         \end{align*}
@@
     \begin{remark}
-    We note that Proposition~\ref{prop:recursiveDnka} gives three different cases depending on the values of the two last elements of $a$:%Then it gives three cases:
+        We note that Proposition~\ref{prop:recursiveDkna} gives three different cases depending on the values of the two last elements of $a$:
     	\begin{itemize}
-		\item if $a_{n-1}=0=a_n$, then $\Dnka{n}{k}{a}=\Dnka{n-2}{k}{b}+2\Dnka{n-2}{k-1}{b}-\Dnka{n-2}{k-2}{b}$,
-		\item if $a_{n-1} \ne a_n$, then $\Dnka{n}{k}{a}=\Dnka{n-2}{k}{b}+\Dnka{n-2}{k-2}{b}$,
-		\item if $a_{n-1}=1=a_n$, then $\Dnka{n}{k}{a}=\Dnka{n-2}{k}{b}-2\Dnka{n-2}{k-1}{b}-\Dnka{n-2}{k-2}{b}$.
+    		\item if $a_{n-1}=0=a_n$, then $\Dkna{n}{k}{a}=\Dkna{n-2}{k}{b}+2\Dkna{n-2}{k-1}{b}-\Dkna{n-2}{k-2}{b}$,
+    		\item if $a_{n-1} \ne a_n$, then $\Dkna{n}{k}{a}=\Dkna{n-2}{k}{b}+\Dkna{n-2}{k-2}{b}$,
+    		\item if $a_{n-1}=1=a_n$, then $\Dkna{n}{k}{a}=\Dkna{n-2}{k}{b}-2\Dkna{n-2}{k-1}{b}-\Dkna{n-2}{k-2}{b}$.
     	\end{itemize}
@@
 
-\begin{remark}\label{rmk:dependence_dnka}
-    The recursive formula of Proposition~\ref{prop:recursiveDnka} gives different cases depending on the values of the pair $(a_{n-1},a_n)$.
+    \begin{remark}\label{rmk:dependence_Dkna}
+        The recursive formula of Proposition~\ref{prop:recursiveDkna} gives different cases depending on the values of the pair $(a_{n-1},a_n)$.
 However, the same reasoning applies to any pair of the form $(a_{2i-1}, a_{2i})$ for $i\in[1,n/2]$.
-Therefore, the value of $\Dnka{n}{k}{a}$ depends only on the number of pairs $(a_{2i-1}, a_{2i})$ in $a$ being $(0,0)$, $(1,1)$, $(0,1)$ or $(1,0)$.
-We give the values of $\Dnka{2}{k}{a}$ for $n=2$ in Table~\ref{tab:Dnka}.
-These values together with Proposition~\ref{prop:recursiveDnka} are sufficient to determine any $\Dnka{n}{k}{a}$.
+Therefore, the value of $\Dkna{n}{k}{a}$ depends only on the number of pairs $(a_{2i-1}, a_{2i})$ in $a$ being $(0,0)$, $(1,1)$, $(0,1)$ or $(1,0)$.
+We give the values of $\Dkna{2}{k}{a}$ for $n=2$ in Table~\ref{tab:Dkna}.
+These values together with Proposition~\ref{prop:recursiveDkna} are sufficient to determine any $\Dkna{n}{k}{a}$.
     \end{remark}
@@
     	\centering
+        \caption{Values of $\Dkna{2}{k}{a}$.}
+        \label{tab:Dkna}
     	\begin{tabular}{|c|c|c|c|}
@@
     		\hline
-		$\Dnka{2}{0}{a}$ &$1$&$1$ & $1$\\
-		$\Dnka{2}{1}{a}$ &$2$& $0$ & $-2$\\
-		$\Dnka{2}{2}{a}$ &$-1$&$1$ & $-1$\\
+    		$\Dkna{2}{0}{a}$ &$1$&$1$ & $1$\\
+    		$\Dkna{2}{1}{a}$ &$2$& $0$ & $-2$\\
+    		$\Dkna{2}{2}{a}$ &$-1$&$1$ & $-1$\\
     		\hline
     	\end{tabular}
-	\mycaption{Values of $\Dnka{2}{k}{a}$.}\label{tab:Dnka}
     \end{table}
 
-In the following, we show how the Walsh transform of the revisited \hwbf{} $f\in\BN$ can be written in terms of the $\Dnka{n}{k}{a}$.
-Then, in Section~\ref{sec:balancedness}, we use Proposition~\ref{prop:recursiveDnka} to determine the balancedness of $f$, and in Section~\ref{sec:genfunc} we study the value of $\Dnka{n}{k}{a}$ using generating functions.
+    In the following, we show how the Walsh transform of the revisited \hwbf{} $f\in\BN$ can be written in terms of the $\Dkna{n}{k}{a}$.
+Then, in Section~\ref{sec:balancedness}, we use Proposition~\ref{prop:recursiveDkna} to determine the balancedness of $f$, and in Section~\ref{sec:genfunc} we study the value of $\Dkna{n}{k}{a}$ using generating functions.
 
@@
 Then the following holds true:
-	\[ \wt{f}(a)=1+\sum_{k=1}^n \Dnka{n}{k}{b+\pi(e_k)}.\]
+    	\[ \wt{f}(a)=1+\sum_{k=1}^n \Dkna{n}{k}{b+\pi(e_k)}.\]
     \end{proposition}
@@
     		\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+a\cdot x}\\
-		&=\sum_{\pi(x) \in \Ekn{k}{n}} (-1)^{f(\pi(x))+a \cdot \pi(x)}\\
-		&=\sum_{\pi(x) \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_{\pi(i)} x_{\pi(i+n/2)}+ x_{\pi(k)}+a \cdot \pi(x)+ \sum_{i=1}^{n/2} x_{\pi(i+n/2)}}\\
+    		&=\sum_{\pi(x) \in \Ekn{k}{n}} (-1)^{f(\pi(x))+a\cdot \pi(x)}\\
+    		&=\sum_{\pi(x) \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_{\pi(i)} x_{\pi(i+n/2)}+ x_{\pi(k)}+a\cdot \pi(x)+ \sum_{i=1}^{n/2} x_{\pi(i+n/2)}}\\
     		&=\sum_{\pi(x) \in \Ekn{k}{n}}(-1)^{d_n(x)+x_{\pi(k)}+\pi^{-1}(a)\cdot x+\sum_{i=1}^{n/2}x_{2i}}\\
     		&=\sum_{x\in \Ekn{k}{n}}(-1)^{d_n(x)+(b+\pi(e_k))\cdot x}\\
-		&=\Dnka{n}{k}{b+\pi(e_k)}.
+    		&=\Dkna{n}{k}{b+\pi(e_k)}.
     	\end{align*}
@@
 
-In this part, we determine for which values of $n$ the revisited \hwbf{} $f\in\BN$ is balanced, using the expression of its Walsh transform in terms of the $\Dnka{n}{k}{a}$ and the recursive relation of these quantities.
+    In this part, we determine for which values of $n$ the revisited \hwbf{} $f\in\BN$ is balanced, using the expression of its Walsh transform in terms of the $\Dkna{n}{k}{a}$ and the recursive relation of these quantities.
 
@@
     \begin{proof}
-	We use Proposition~\ref{prop:WT}, applying Remark~\ref{rmk:dependence_dnka} and that $\pi^{-1}(0_n)=0_n$:
-	\begin{align*}
-		\wt{f}(0_n)&=1+\sum_{k=1}^n\Dnka{n}{k}{\pi^{-1}(0_n)+(0,1,0,1,\ldots,0,1)+\pi(e_k)}\\
-		&=1+\sum_{k=1}^{n/2}\Dnka{n}{k}{1,1,0,1,\ldots,0,1}+\sum_{k=n/2+1}^{n}\Dnka{n}{k}{0,0,0,1,\ldots,0,1}.
-	\end{align*}
-	Using the recursive relation from Proposition~\ref{prop:recursiveDnka}, we obtain:
-	\begin{align*}
-		\Dnka{n}{k}{1,1,0,1,\ldots,0,1}&=\Dnka{n-2}{k}{1,1,0,1,\ldots,0,1}\\
-		&\qquad+\Dnka{n-2}{k-2}{1,1,0,1,\ldots,0,1}.
+    	We use Proposition~\ref{prop:WT}, applying Remark~\ref{rmk:dependence_Dkna} and that $\pi^{-1}(0_n)=0_n$:
+    	\begin{align*}
+    		\wt{f}(0_n)&=1+\sum_{k=1}^n\Dkna{n}{k}{\pi^{-1}(0_n)+(0,1,0,1,\ldots,0,1)+\pi(e_k)}\\
+    		&=1+\sum_{k=1}^{n/2}\Dkna{n}{k}{1,1,0,1,\ldots,0,1}+\sum_{k=n/2+1}^{n}\Dkna{n}{k}{0,0,0,1,\ldots,0,1}.
+    	\end{align*}
+    	Using the recursive relation from Proposition~\ref{prop:recursiveDkna}, we obtain:
+    	\begin{align*}
+    		\Dkna{n}{k}{1,1,0,1,\ldots,0,1}&=\Dkna{n-2}{k}{1,1,0,1,\ldots,0,1}\\
+    		&\qquad+\Dkna{n-2}{k-2}{1,1,0,1,\ldots,0,1}.
     	\end{align*}
@@
     	\begin{align*}
-		\Dnka{n}{k}{1,1,0,1,\ldots,0,1}&=\sum_{i=0}^{n/2-1} \binom{n/2-1}{i} \Dnka{2}{k-2i}{1,1}\\
-		&=\binom{n/2-1}{k/2} \Dnka{2}{0}{1,1}+ \binom{n/2-1}{(k-1)/2} \Dnka{2}{1}{1,1}\\
-		&\qquad+ \binom{n/2-1}{k/2-1} \Dnka{2}{2}{1,1}\\
+    		\Dkna{n}{k}{1,1,0,1,\ldots,0,1}&=\sum_{i=0}^{n/2-1} \binom{n/2-1}{i} \Dkna{2}{k-2i}{1,1}\\
+    		&=\binom{n/2-1}{k/2} \Dkna{2}{0}{1,1}+ \binom{n/2-1}{(k-1)/2} \Dkna{2}{1}{1,1}\\
+    		&\qquad+ \binom{n/2-1}{k/2-1} \Dkna{2}{2}{1,1}\\
     		&=\binom{n/2-1}{k/2}-2\binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}.
     	\end{align*}
-	We similarly get $\Dnka{n}{k}{0,0,0,1,\ldots,0,1}=\binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}$. Then, combining both, we obtain:
-	\begin{align*}
-		\wt{f}(0_n)&=1+\sum_{k=1}^{n/2}\Dnka{n}{k}{1,1,0,1,\ldots,0,1}+ \sum_{k=n/2+1}^{n}\Dnka{n}{k}{0,0,0,1,\ldots,0,1}\\
+    	We similarly get:
+        \[
+            \Dkna{n}{k}{0,0,0,1,\ldots,0,1}=\binom{n/2-1}{k/2} +2 \binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}.
+        \]
+        Then, combining both, we obtain:
+    	\begin{align*}
+    		\wt{f}(0_n)&=1+\sum_{k=1}^{n/2}\Dkna{n}{k}{1,1,0,1,\ldots,0,1}+ \sum_{k=n/2+1}^{n}\Dkna{n}{k}{0,0,0,1,\ldots,0,1}\\
     		&=\sum_{k=0}^{n/2} \left(\binom{n/2-1}{k/2} -2 \binom{n/2-1}{(k-1)/2}-\binom{n/2-1}{k/2-1}\right)\\
@@
 
-\section{Extensive study of the $\Dnka nka$ and bounds on the Walsh spectrum of $f$}\label{sec:dnk}
-
-This section examines the values of $\Dnka nka$ through the use of generating functions.
+    \section{Extensive Study of the $\Dkna nka$ and Bounds on the Walsh Spectrum of $f$}\label{sec:dnk}
+
+    This section examines the values of $\Dkna nka$ through the use of generating functions.
 To begin, in Section~\ref{sec:genfunc}, we determine essential characteristics of these values.
-Subsequently, in Section~\ref{sec:Cauchy}, we employ Cauchy's estimate to bound the absolute value of the $\Dnka nka$.
+Subsequently, in Section~\ref{sec:Cauchy}, we employ Cauchy's estimate to bound the absolute value of the $\Dkna nka$.
 This approach allows us to also bound the absolute value of the Walsh transform of the revisited \hwbf{}, thereby constraining the nonlinearity.
@@
 
-\subsection{Study of the $\Dnka nka$ through generating functions}\label{sec:genfunc}
+    \subsection{Study of the $\Dkna nka$ through Generating Functions}\label{sec:genfunc}
 
@@
         \[
-        \sum_{k\in\Z}\Dnka nka z^k= P_a(z).
+            \sum_{k\in\Z}\Dkna nka z^k= P_a(z).
         \]
@@
     	We proceed by induction on even $n\geq 0$. 
-	For the base case $n=0$, we consider the empty vector $a=\varepsilon\in\F_2^0$; it satisfies $P_a(z)=1$, while $\Dnka 00a=1$ and $\Dnka 0ka=0$ if $k\neq 0$ by Proposition~\ref{prop:recursiveDnka}.
+    	For the base case $n=0$, we consider the empty vector $a=\varepsilon\in\F_2^0$; it satisfies $P_a(z)=1$, while $\Dkna 00a=1$ and $\Dkna 0ka=0$ if $k\neq 0$ by Proposition~\ref{prop:recursiveDkna}.
 For the inductive step, let $n\geq 2$ be even, and assume that the corresponding formula holds for $n-2$.
-Using the recursive formula for $\Dnka nka$ from Proposition~\ref{prop:recursiveDnka} with $b=(a_1,\dots,a_{n-2})\in\F_2^{n-2}$, we have:
+Using the recursive formula for $\Dkna nka$ from Proposition~\ref{prop:recursiveDkna} with $b=(a_1,\dots,a_{n-2})\in\F_2^{n-2}$, we have:
     	\begin{align*}
     	\begin{split}
-		\sum_{k\in\Z}\Dnka nka z^k&=\sum_{k\in\Z}\Dnka{n-2}kbz^k+\big((-1)^{a_{n-1}}+(-1)^{a_{n}}\big)\sum_{k\in\Z}\Dnka{n-2}{k-1}{b}z^k\\
-		&\qquad+(-1)^{1+a_{n-1}+a_n}\sum_{k\in\Z}\Dnka{n-2}{k-2}{b}z^k\\
+    		\sum_{k\in\Z}\Dkna nka z^k&=\sum_{k\in\Z}\Dkna{n-2}kbz^k+\big((-1)^{a_{n-1}}+(-1)^{a_{n}}\big)\sum_{k\in\Z}\Dkna{n-2}{k-1}{b}z^k\\
+    		&\qquad+(-1)^{1+a_{n-1}+a_n}\sum_{k\in\Z}\Dkna{n-2}{k-2}{b}z^k\\
     		&=P_b(z)+\big((-1)^{a_{n-1}}+(-1)^{a_{n}}\big)zP_b(z)+(-1)^{1+a_{n-1}+a_n}z^2P_b(z)\\
@@
 
-\begin{remark}\label{rmk:Dnka_dep_pqr}
-    We have already argued in Remark~\ref{rmk:dependence_dnka} that $\Dnka nka$ only depends on $p(a)$, $q(a)$ and $r(a)$.
-This observation can also be obtained from Proposition~\ref{proposition:generating_fct}: since $P_a(z)$ only depends on $p(a)$, $q(a)$ and $r(a)$ (by definition), we deduce that also $\Dnka nka$ only depends on $p(a)$, $q(a)$ and $r(a)$.
-Therefore, for any $p,q,r\geq0$ satisfying $p+q+r=n/2$, it makes sense to introduce the notation $\mathsf D_{k,n}^{p,q,r}=\Dnka nka$, where $a\in\mathbb F_2^n$ is any vector with $(p(a),q(a),r(a))=(p,q,r)$.
+    \begin{remark}\label{rmk:Dkna_dep_pqr}
+        We have already argued in Remark~\ref{rmk:dependence_Dkna} that $\Dkna nka$ only depends on $p(a)$, $q(a)$ and $r(a)$.
+This observation can also be obtained from Proposition~\ref{proposition:generating_fct}: since $P_a(z)$ only depends on $p(a)$, $q(a)$ and $r(a)$ (by definition), we deduce that also $\Dkna nka$ only depends on $p(a)$, $q(a)$ and $r(a)$.
+Therefore, for any $p,q,r\geq0$ satisfying $p+q+r=n/2$, it makes sense to introduce the notation $\mathsf D_{k,n}^{p,q,r}=\Dkna nka$, where $a\in\mathbb F_2^n$ is any vector with $(p(a),q(a),r(a))=(p,q,r)$.
 We will make use of this notation in Section~\ref{sec:expwt}.
@@
     	\[
-		\Dnka n{n-k}a=(-1)^{p+q+k}\Dnka nka.
+    		\Dkna n{n-k}a=(-1)^{p+q+k}\Dkna nka.
     	\]
@@
     \begin{proof}
-	We define the reverse polynomial  $Q_a(z)$ as the degree $n$ polynomial where each coefficient of $z^k$ in $Q_a(z)$, for any $k$, is equal to the coefficient of $z^{n-k}$ in $P_a(z)$. Then we have:
+    	We define the reverse polynomial  $Q_a(z)$ as the degree $n$ polynomial where each coefficient of $z^k$ in $Q_a(z)$, for any $k$, is equal to the coefficient of $z^{n-k}$ in $P_a(z)$.
+Then we have:
     	\begin{align*}
@@
     	\end{align*}
-	Therefore, the coefficient of $z^k$ in $Q_a(z)$, which is $\Dnka n{n-k}a$, is equal to the coefficient of $z^k$ in $(-1)^{p+q}P_a(-z)$, which is $(-1)^{p+q+k}\Dnka nka$.
-\end{proof}
-
-\begin{Corollary}
-    Let $n\geq 0$ be an even integer, and let $a\in\F_2^n$ be a binary vector. If $r=r(a)$ is odd, then it holds that $\Dnka n{n/2}a=0$.
-\end{Corollary}
-
-\begin{proof}
-	By Proposition \ref{proposition:symmetry}, we have $\Dnka n{n/2}a=(-1)^{p+q+n/2}\Dnka n{n/2}a=-\Dnka n{n/2}a$ because $p+q+n/2$ is odd: $p+q+n/2\equiv n/2-p-q\equiv r\equiv 1\bmod 2$.
+    	Therefore, the coefficient of $z^k$ in $Q_a(z)$, which is $\Dkna n{n-k}a$, is equal to the coefficient of $z^k$ in $(-1)^{p+q}P_a(-z)$, which is $(-1)^{p+q+k}\Dkna nka$.
+    \end{proof}
+
+    \begin{corollary}
+        Let $n\geq 0$ be an even integer, and let $a\in\F_2^n$ be a binary vector. If $r=r(a)$ is odd, then it holds that $\Dkna n{n/2}a=0$.
+    \end{corollary}
+
+    \begin{proof}
+    	By Proposition \ref{proposition:symmetry}, it holds that $\Dkna n{n/2}a=(-1)^{p+q+n/2}\Dkna n{n/2}a=-\Dkna n{n/2}a$ because $p+q+n/2$ is odd: $p+q+n/2\equiv n/2-p-q\equiv r\equiv 1\bmod 2$.
     \end{proof}
@@
     \begin{proposition}
-    Let $n\geq 0$ be an even integer, and let $a\in\F_2^n$ be a binary vector. If $k$ is an odd integer and  $p=q$, then it holds that $\Dnka nka=0=\Dnka n{n-k}a$.
+        Let $n\geq 0$ be an even integer, and let $a\in\F_2^n$ be a binary vector. If $k$ is an odd integer and  $p=q$, then it holds that $\Dkna nka=0=\Dkna n{n-k}a$.
     \end{proposition}
@@
         If $p=q$, we have $P_a(z)=(z^4-6z^2+1)^p\cdot(z^2+1)^r$, which can be seen as a polynomial in $z^2$.
-Thus, the coefficient $\Dnka nka$ in $P_a(z)$ of $z^k$ for odd $k$ must be zero.
-It also follows that $\Dnka n{n-k}a=0$ by Proposition~\ref{proposition:symmetry}.
+Thus, the coefficient $\Dkna nka$ in $P_a(z)$ of $z^k$ for odd $k$ must be zero.
+It also follows that $\Dkna n{n-k}a=0$ by Proposition~\ref{proposition:symmetry}.
     \end{proof}
@@
     \begin{remark}\label{remark:D_nka_differentiation}
-    We can also use Proposition \ref{proposition:generating_fct} to obtain $\Dnka nka$ through differentiation and evaluation at $z=0$, to get $k!\cdot\Dnka nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}$.
-Using this formula, we can for instance use a computer algebra system to deduce $\Dnka nka$ for small values of $k$, see Table \ref{tab:Dnka_small_k}.
-Note that even though the expression for $\Dnka n3a$ involves a division by $3$, its evaluation at specific values for $(p,q,r)$ will always yield integers.
+        We can also use Proposition \ref{proposition:generating_fct} to obtain $\Dkna nka$ through differentiation and evaluation at $z=0$, to get $k!\cdot\Dkna nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}$.
+Using this formula, we can for instance use a computer algebra system to deduce $\Dkna nka$ for small values of $k$, see Table \ref{tab:Dkna_small_k}.
+Note that even though the expression for $\Dkna n3a$ involves a division by $3$, its evaluation at specific values for $(p,q,r)$ will always yield integers.
 Indeed, either $p-q\equiv 0\bmod 3$, or $(p-q)^2\equiv 1\bmod 3$, in which case $2(p-q)^2+7\equiv 0\bmod 3$.
@@
     	\centering
+        \caption{Values of $\Dkna{n}{k}{a}$ for small values of $k$.}\label{tab:Dkna_small_k}
     	\begin{tabular}{|c|c|}
     		\hline
-		$k$ & $\Dnka 2ka$\\
+    		$k$ & $\Dkna nka$\\
     		\hline
@@
     	\end{tabular}
-	\mycaption{Values of $\Dnka{2}{k}{a}$ for small values of $k$.}\label{tab:Dnka_small_k}
     \end{table}
 
-From differentiation, we can get more cases in which $\Dnka nka=0$.
+    From differentiation, we can get more cases in which $\Dkna nka=0$.
 
@@
         \begin{enumerate}
-        \item For every integer $s\geq0$, define $\ell_s=s(s-1)$. If $n=16m$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, then $\Dnka n2a=0=\Dnka n{n-2}a$.
+            \item For every integer $s\geq0$, define $\ell_s=s(s-1)$. If $n=16m$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, then $\Dkna n2a=0=\Dkna n{n-2}a$.
             \item For every integer $s\geq 0$, define $\ell_s=\left(6s^2+6s+(-1)^s(2s+1)-1\right)/8$.
-If $n=16m+2$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+2}\}$ for integers $m,s\geq 0$, then $\Dnka n3a=0=\Dnka n{k-3}a$.
-        \item For every integer $s\geq 0$, define $\ell_s=s^2$. If $n=16m+4$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, then $\Dnka n2a=0=\Dnka n{n-2}a$.
+If $n=16m+2$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+2}\}$ for integers $m,s\geq 0$, then $\Dkna n3a=0=\Dkna n{k-3}a$.
+            \item For every integer $s\geq 0$, define $\ell_s=s^2$. If $n=16m+4$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, then $\Dkna n2a=0=\Dkna n{n-2}a$.
             \item For every integer $s\geq 0$, define $\ell_s=\left(6s^2+6s-(-1)^s(2s+1)+1\right)/8$.
-If $n=16m+6$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+2}\}$ for integers $m,s\geq 0$, then $\Dnka n3a=0=\Dnka n{n-3}a$.
+If $n=16m+6$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+2}\}$ for integers $m,s\geq 0$, then $\Dkna n3a=0=\Dkna n{n-3}a$.
         \end{enumerate}
@@
     \begin{proof}
-	We use the expressions from Table~\ref{tab:Dnka_small_k}, and replace $p$, $q$ and $r$ by their respective values.
-For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$, respectively, in the expression $\Dnka n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dnka n2a=0$.~\footnote{This checking can be automatized by a computer algebra system.
-	\ifnum\anon=0
-		For this, we refer to the corresponding \textsf{SageMath} implementation, accessible via this link: \url{https://github.com/se-tim/Revisited-HWBF.git}.
-	\fi}
+    	We use the expressions from Table~\ref{tab:Dkna_small_k}, and replace $p$, $q$ and $r$ by their respective values.
+For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$, respectively, in the expression $\Dkna n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dkna n2a=0$.
+This checking can be automatized by a computer algebra system, for which we provide a \textsf{SageMath} implementation.\myurl{https://github.com/se-tim/Revisited-HWBF.git}
     \end{proof}
@@
     \begin{remark}
-    There are other instances where $\Dnka nka=0$ which have not been described by any of the previous results. For instance, we have $\Dnka{34}4a=0$ if $\{p,q\}=\{1,2\}$.
+        There are other instances where $\Dkna nka=0$ which have not been described by any of the previous results. For instance, we have $\Dkna{34}4a=0$ if $\{p,q\}=\{1,2\}$.
     \end{remark}
 
-Using Proposition \ref{proposition:generating_fct}, we can also deduce some sums involving the $\Dnka nka$.
+    Using Proposition \ref{proposition:generating_fct}, we can also deduce some sums involving the $\Dkna nka$.
 
@@
         \begin{enumerate}
-        \item The sum and alternating sum over $k$ of the $\Dnka nka$ are, respectively:
-		\[
-			\sum_{k\in\Z}\Dnka nka=(-1)^{q}2^{n/2}, \qquad
-			\sum_{k\in\Z}(-1)^k\Dnka nka=(-1)^{p}2^{n/2}.
-		\]
-        \item The sum over the even and the odd $k$ of the $\Dnka nka$ are, respectively:
+            \item The sum and alternating sum over $k$ of the $\Dkna nka$ are, respectively:
+    		\[
+    			\sum_{k\in\Z}\Dkna nka=(-1)^{q}2^{n/2}, \qquad
+    			\sum_{k\in\Z}(-1)^k\Dkna nka=(-1)^{p}2^{n/2}.
+    		\]
+            \item The sum over the even and the odd $k$ of the $\Dkna nka$ are, respectively:
             \begin{gather*}
-			\sum_{k\in\Z}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big),\\
-			\sum_{k\in\Z}\Dnka n{2k+1}a=2^{n/2-1}\big((-1)^{q}-(-1)^{p}\big).
+    			\sum_{k\in\Z}\Dkna n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big),\\
+    			\sum_{k\in\Z}\Dkna n{2k+1}a=2^{n/2-1}\big((-1)^{q}-(-1)^{p}\big).
     		\end{gather*}
@@
     	For the sum and the alternating sum, we compute $P_a(1)$ and $P_a(-1)$, respectively.
-The sum of the $\Dnka nka$ over the even (respectively, odd) $k$ is obtained by adding (respectively, subtracting) these two sums and dividing by $2$.
-\end{proof}
-
-\subsection{Bounding the Walsh transform of $f$ using the Cauchy estimate}\label{sec:Cauchy}
+The sum of the $\Dkna nka$ over the even (respectively, odd) $k$ is obtained by adding (respectively, subtracting) these two sums and dividing by $2$.
+    \end{proof}
+
+    \subsection{Bounding the Walsh Transform of $f$ using the Cauchy Estimate}\label{sec:Cauchy}
 
@@
 
-\begin{Prop}[Cauchy's estimate, \eg, Theorem 10.26 in~\cite{rudin1987}]\label{property:cauchy_estimate}
+    \begin{property}[Cauchy's estimate, \eg, Theorem 10.26 in~\cite{rudin1987}]\label{property:cauchy_estimate}
         Let $w$ be a complex number, and let $R>0$ be some radius.
@@
 Then for every integer $k\geq 0$, the $k$-th derivative of $f$ evaluated at $w$ can be bounded, in absolute value, by $\left|\frac{\dd^k}{\dd^k z}f(z)\vert_{z=w}\right|\leq\frac{k!\cdot M_R}{R^k}$.
-\end{Prop}
+    \end{property}
 
@@
         \[
-        |\Dnka nka|\leq 2^{3n/4}.
+            |\Dkna nka|\leq 2^{3n/4}.
         \]
@@
     \begin{proof}
-    From Remark~\ref{remark:D_nka_differentiation} we have $k!\cdot\Dnka nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}$.
-Choosing $f=P_a$, $w=0$ and $R=1$ in Property \ref{property:cauchy_estimate} then gives $|\Dnka nka|=\frac{1}{k!}\left|\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}\right|\leq M$, where $M$ is the maximum of $|P_a(z)|$ on the complex circle $\dis=\{ z \in \C: |z|=1  \}$.
+        From Remark~\ref{remark:D_nka_differentiation} we have $k!\cdot\Dkna nka=\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}$.
+Choosing $f=P_a$, $w=0$ and $R=1$ in Property \ref{property:cauchy_estimate} then gives $|\Dkna nka|=\frac{1}{k!}\left|\frac{\dd^k}{\dd^k z}P_a(z)\vert_{z=0}\right|\leq M$, where $M$ is the maximum of $|P_a(z)|$ on the complex circle $\dis=\{ z \in \C: |z|=1  \}$.
 We claim, and prove below, that the maximum of $\left|-z^2+2z+1\right|$ on $\dis$ is $2\sqrt 2$.
 This implies that the maximum of $\left|-z^2-2z+1\right|$ on $\dis$ is $2\sqrt 2$ as well because $-z^2-2z+1=-(-z)^2+2(-z)+1$.
-Since the maximum of $\left|z^2+1\right|$ on $\dis$ is $2<2\sqrt 2$, it follows that $|\Dnka nka|\leq M\leq (2\sqrt 2)^{p+q}2^r\leq (2\sqrt 2)^{n/2}$.
+Since the maximum of $\left|z^2+1\right|$ on $\dis$ is $2<2\sqrt 2$, it follows that $|\Dkna nka|\leq M\leq (2\sqrt 2)^{p+q}2^r\leq (2\sqrt 2)^{n/2}$.
 
@@
 
-\begin{Corollary}\label{cor:bound_walsh_cauchy}
+    \begin{corollary}\label{cor:bound_walsh_cauchy}
         Let $n\geq 0$ be an even integer, and let $f\in\BN$ be the revisited \hwbf{}. Then for every binary vector $a\in\F_2^n$, it holds that:
@@
         Equivalently, it holds that $\NL(f)\geq 2^{n-1} - \frac{1}{2} -2^{3n/4 + \log_2(n) -1}$.
-\end{Corollary}
+    \end{corollary}
 
@@
         It is enough to prove the bound on $|\wt f(a)|$; the bound on the nonlinearity of $f$ comes from the second expression of Definition~\ref{def:nl}.
-We have previously established in Proposition~\ref{prop:WT} that $\wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b_k}$ for some vectors $b_k\in\F_2^n$.
-Then, applying the triangle inequality together with Theorem~\ref{theorem:bound_D_nka} yields $|\wt{f}(a)|\leq 1+\sum_{k=1}^n\left|\Dnka{n}{k}{b_k}\right|\leq 1+ n\cdot 2^{3n/4}$.
-\end{proof}
-
-\subsection{Generalization to a family of weightwise quadratic functions}\label{sec:general}
+We have previously established in Proposition~\ref{prop:WT} that $\wt{f}(a)=1+\sum_{k=1}^n\Dkna{n}{k}{b_k}$ for some vectors $b_k\in\F_2^n$.
+Then, applying the triangle inequality together with Theorem~\ref{theorem:bound_D_nka} yields $|\wt{f}(a)|\leq 1+\sum_{k=1}^n\left|\Dkna{n}{k}{b_k}\right|\leq 1+ n\cdot 2^{3n/4}$.
+    \end{proof}
+
+    \subsection{Generalization to a Family of Weightwise Quadratic Functions}\label{sec:general}
 
@@
 
-In particular, it holds that $d_{n/2,n}(x)=d_n(x)$ and $\Dtkna{n/2}{k}{n}{a}=\Dkna kna$. We now focus on the $\Dtkna{t}{k}{n}{a}$.
+    In particular, it holds that $d_{n/2,n}(x)=d_n(x)$ and $\Dtkna{n/2}{k}{n}{a}=\Dkna nka$. We now focus on the $\Dtkna{t}{k}{n}{a}$.
 
@@
     	\[
-		\Dtkna{t}{k}{n}{a}=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b}\cdot\kraw{k-\ell}{\w(c)}{n-2t}.
+    		\Dtkna{t}{k}{n}{a}=\sum_{\ell=0}^{2t} \Dkna{2t}{\ell}{b}\cdot\kraw{k-\ell}{\w(c)}{n-2t}.
     	\]
@@
     	\centering
-	\includegraphics[width=7.5cm]{curve_exponents_lambda_mu.pdf}
-    \vspace{-5mm}
-	\mycaption{The curve of $\lambda\mapsto\mu(\lambda)$ with $0\leq\lambda\leq\frac 12$ from Theorem~\ref{theorem:bound_D_nka_generalized}.}
+    	\includegraphics[width=7.5cm]{graphs/curve_exponents_lambda_mu.pdf}
+    	\caption{The curve of $\lambda\mapsto\mu(\lambda)$ with $0\leq\lambda\leq\frac 12$ from Theorem~\ref{theorem:bound_D_nka_generalized}.}
     	\label{fig:curve_exponents_lambda_mu}
@@
 
-\section{Experiments and comparisons}\label{sec:expAndComp}
+    \section{Experiments and Comparisons}\label{sec:expAndComp}
 
@@
 
-\subsection{Bounding the Walsh transform of $f$ experimentally}\label{sec:expwt}
+    \subsection{Experimentally Bounding the Walsh Transform of $f$}\label{sec:expwt}
 
@@
 
-For each $k\in[1,n/2]$, we select $\{\alpha_k,\beta_k,\gamma_k\}=\{0,\pm 1\}$ with $\gamma_k\neq 0$ such that the following expression, based on the notation introduced in Remark~\ref{rmk:Dnka_dep_pqr}, is defined and maximized:
+    For each $k\in[1,n/2]$, we select $\{\alpha_k,\beta_k,\gamma_k\}=\{0,\pm 1\}$ with $\gamma_k\neq 0$ such that the following expression, based on the notation introduced in Remark~\ref{rmk:Dkna_dep_pqr}, is defined and maximized:
     \[
@@
     \]
-This implies that $\Dnka{n}{k}{b_k}+\Dnka{n}{k+n/2}{b_{k+n/2}}\leq B_k^{p,q,r}$ for every $k\in[1,n/2]$, leading to the conclusion that $\sum_{k=1}^n\Dnka nk{b_k}\leq\sum_{k=1}^{n/2} B_k^{p,q,r}$.
+    This implies that $\Dkna{n}{k}{b_k}+\Dkna{n}{k+n/2}{b_{k+n/2}}\leq B_k^{p,q,r}$ for every $k\in[1,n/2]$, leading to the conclusion that $\sum_{k=1}^n\Dkna nk{b_k}\leq\sum_{k=1}^{n/2} B_k^{p,q,r}$.
 As a result, we derive the following upper bound:
@@
 We claim that this computation has a complexity of $\mathcal{O}(n^3 \log n)$.
-Towards this, it is sufficient to expand $(-z^2 + 2z + 1)^p \cdot (-z^2 - 2z + 1)^q \cdot (z^2 + 1)^r$ for all triplets $(p,q,r)$ such that $p+q+r=n/2$; this is due to Proposition \ref{proposition:generating_fct}.
+Towards this, it is sufficient to expand $(-z^2 + 2z + 1)^p\cdot (-z^2 - 2z + 1)^q\cdot (z^2 + 1)^r$ for all triplets $(p,q,r)$ such that $p+q+r=n/2$; this is due to Proposition \ref{proposition:generating_fct}.
 
     To achieve this, we first precompute the expanded polynomial $(-z^2 + 2z + 1)^p$ for each $p\in[0,n/2]$.
-This can be done recursively using the formula $(-z^2 + 2z + 1)^{p+1} = (-z^2 + 2z + 1) \cdot (-z^2 + 2z + 1)^p$.
+This can be done recursively using the formula $(-z^2 + 2z + 1)^{p+1} = (-z^2 + 2z + 1)\cdot (-z^2 + 2z + 1)^p$.
 For each $p$, this requires $\mathcal O(n)$ arithmetic computations.
@@
 Its polynomial complexity makes it possible to extend the analysis well beyond the limitations imposed by a full computation of the Walsh spectrum, which requires a complexity of $\mathcal O(n2^n)$.
-\ifnum\anon=0
-	We provide a \textsf{SageMath} implementation to obtain the bound $B_n$: \url{https://github.com/se-tim/Revisited-HWBF.git}.
-\fi
+We provide a \textsf{SageMath} implementation to obtain the bound $B_n$.\myurl{https://github.com/se-tim/Revisited-HWBF.git}
 
@@
     	\centering
+        \caption{The actual $\max_{a\in\F_2^n}|\wt f(a)|$ compared to the bound $B_n$ and the theoretical bound from Corollary~\ref{cor:bound_walsh_cauchy}.}
+    	\label{table:max_walsh_vs_bound}
     	\begin{tabular}{|c|c|c|c|}
     		\hline
-		$n$ & $\max_{a\in\F_2^n}|\wt f(a)|$ & $B_n$  & $\lfloor 1+n \cdot 2^{3n/4} \rfloor$\\
-		\hline
-		$2$  & $2$     & $2$  &  $6$ \\
-		$4$  & $8$     & $8$  & $33$  \\
-		$6$  & $20$    & $28$   & $136$\\
-		$8$  & $52$    & $76$  & $513$ \\
-		$10$ & $108$   & $212$  & $1\,811$\\
-		$12$ & $292$   & $596$  & $6\,145$ \\
-		$14$ & $700$   & $1\,828$ & $20\,275$ \\
-		$16$ & $2\,176$  & $5\,196$ & $65\,537$ \\
-		$18$ & $4\,964$  & $14\,668$ & $208\,535$ \\
-		$20$ & $14\,968$ & $41\,468$ & $655\,361$ \\
-		$22$ & $34\,232$ & $118\,544$ & $2\,039 \,002$ \\
-		$24$ & $109\,648$ & $325\,188$ & $6\,291 \,457$  \\
+    		$n$ & $\max_a|\wt f(a)|$ & $B_n$  & $\lfloor 1+n\cdot 2^{3n/4} \rfloor$\\
+            \hline
+            $2$&$2$&$2$&$6$\\
+            $4$&$8$&$8$&$33$\\
+            $6$&$20$&$28$&$136$\\
+            $8$&$52$&$76$&$513$\\
+            $10$&$108$&$212$&$1\,811$\\
+            $12$&$292$&$596$&$6\,145$\\
+            $14$&$700$&$1\,828$&$20\,275$\\
+            $16$&$2\,176$&$5\,196$&$65\,537$\\
+            $18$&$4\,964$&$14\,668$&$208\,535$\\
+            $20$&$14\,968$&$41\,468$&$655\,361$\\
+            $22$&$34\,232$&$118\,544$&$2\,039\,002$\\
+            $24$&$109\,648$&$325\,188$&$6\,291\,457$\\
     		\hline
     	\end{tabular}
-	\mycaption{The actual $\max_{a\in\F_2^n}|\wt f(a)|$ compared to the bound $B_n$ and the theoretical bound from Corollary~\ref{cor:bound_walsh_cauchy}.}
-	\label{table:max_walsh_vs_bound}
     \end{table}
@@
     	\centering
+        \caption{Approximate values of $B_n$ for various values of $n$.}
+    	\label{table:walsh_bounds}
     	\begin{minipage}{0.24\textwidth}
@@
                 \hline
-			$n$ & $\approx B_n$ \\
-			\hline
-			$2$  & $2.00 \cdot 10^{0}$  \\
-			$4$  & $8.00 \cdot 10^{0}$  \\
-			$6$  & $2.80 \cdot 10^{1}$  \\
-			$8$  & $7.60 \cdot 10^{1}$  \\
-			$10$ & $2.12 \cdot 10^{2}$  \\
-			$12$ & $5.96 \cdot 10^{2}$  \\
-			$14$ & $1.83 \cdot 10^{3}$  \\
-			$16$ & $5.20 \cdot 10^{3}$  \\
-			$18$ & $1.47 \cdot 10^{4}$  \\
-			$20$ & $4.15 \cdot 10^{4}$  \\
+                $n$&$\approx B_n$\\
+                \hline
+                $2$&$2.00\cdot 10^{0}$\\
+                $4$&$8.00\cdot 10^{0}$\\
+                $6$&$2.80\cdot 10^{1}$\\
+                $8$&$7.60\cdot 10^{1}$\\
+                $10$&$2.12\cdot 10^{2}$\\
+                $12$&$5.96\cdot 10^{2}$\\
+                $14$&$1.83\cdot 10^{3}$\\
+                $16$&$5.20\cdot 10^{3}$\\
+                $18$&$1.47\cdot 10^{4}$\\
+                $20$&$4.15\cdot 10^{4}$\\
                 \hline
@@
                 \hline
-			$n$ & $\approx B_n$ \\
-			\hline
-			$22$ & $1.19 \cdot 10^{5}$  \\
-			$24$ & $3.25 \cdot 10^{5}$  \\
-			$26$ & $9.59 \cdot 10^{5}$  \\
-			$28$ & $2.68 \cdot 10^{6}$  \\
-			$30$ & $7.65 \cdot 10^{6}$  \\
-			$32$ & $2.14 \cdot 10^{7}$  \\
-			$34$ & $6.25 \cdot 10^{7}$  \\
-			$36$ & $1.76 \cdot 10^{8}$  \\
-			$38$ & $5.03 \cdot 10^{8}$  \\
-			$40$ & $1.40 \cdot 10^{9}$  \\
+                $n$&$\approx B_n$\\
+                \hline
+                $22$&$1.19\cdot 10^{5}$\\
+                $24$&$3.25\cdot 10^{5}$\\
+                $26$&$9.59\cdot 10^{5}$\\
+                $28$&$2.68\cdot 10^{6}$\\
+                $30$&$7.65\cdot 10^{6}$\\
+                $32$&$2.14\cdot 10^{7}$\\
+                $34$&$6.25\cdot 10^{7}$\\
+                $36$&$1.76\cdot 10^{8}$\\
+                $38$&$5.03\cdot 10^{8}$\\
+                $40$&$1.40\cdot 10^{9}$\\
                 \hline
@@
                 \hline
-			$n$ & $\approx B_n$ \\
-			\hline
-			$42$ & $4.01 \cdot 10^{9}$  \\
-			$44$ & $1.12 \cdot 10^{10}$ \\
-			$46$ & $3.21 \cdot 10^{10}$ \\
-			$48$ & $8.91 \cdot 10^{10}$ \\
-			$50$ & $2.56 \cdot 10^{11}$ \\
-			$52$ & $7.12 \cdot 10^{11}$ \\
-			$54$ & $2.05 \cdot 10^{12}$ \\
-			$56$ & $5.73 \cdot 10^{12}$ \\
-			$58$ & $1.65 \cdot 10^{13}$ \\
-			$60$ & $4.59 \cdot 10^{13}$ \\
+                $n$&$\approx B_n$\\
+                \hline
+                $42$&$4.01\cdot 10^{9}$\\
+                $44$&$1.12\cdot 10^{10}$\\
+                $46$&$3.21\cdot 10^{10}$\\
+                $48$&$8.91\cdot 10^{10}$\\
+                $50$&$2.56\cdot 10^{11}$\\
+                $52$&$7.12\cdot 10^{11}$\\
+                $54$&$2.05\cdot 10^{12}$\\
+                $56$&$5.73\cdot 10^{12}$\\
+                $58$&$1.65\cdot 10^{13}$\\
+                $60$&$4.59\cdot 10^{13}$\\
                 \hline
@@
                 \hline
-			$n$ & $\approx B_n$ \\
-			\hline
-			$62$ & $1.32 \cdot 10^{14}$ \\
-			$64$ & $3.66 \cdot 10^{14}$ \\
-			$66$ & $1.05 \cdot 10^{15}$ \\
-			$68$ & $2.93 \cdot 10^{15}$ \\
-			$70$ & $8.40 \cdot 10^{15}$ \\
-			$72$ & $2.33 \cdot 10^{16}$ \\
-			$74$ & $6.71 \cdot 10^{16}$ \\
-			$76$ & $1.87 \cdot 10^{17}$ \\
-			$78$ & $5.39 \cdot 10^{17}$ \\
-			$80$ & $1.51 \cdot 10^{18}$ \\
+                $n$&$\approx B_n$\\
+                \hline
+                $62$&$1.32\cdot 10^{14}$\\
+                $64$&$3.66\cdot 10^{14}$\\
+                $66$&$1.05\cdot 10^{15}$\\
+                $68$&$2.93\cdot 10^{15}$\\
+                $70$&$8.40\cdot 10^{15}$\\
+                $72$&$2.33\cdot 10^{16}$\\
+                $74$&$6.71\cdot 10^{16}$\\
+                $76$&$1.87\cdot 10^{17}$\\
+                $78$&$5.39\cdot 10^{17}$\\
+                $80$&$1.51\cdot 10^{18}$\\
                 \hline
@@
         \end{minipage}
-	\mycaption{Approximate values of $B_n$ for various values of $n$.}
-	\label{table:walsh_bounds}
     \end{table}
 
-\subsection{Comparison of the nonlinearity}
-
-In this part, we compare the nonlinearity of the revisited \hwbf{} to other weightwise quadratic functions considered for similar use-cases, such as the majority function, the \hwbf{} and the cyclic weightwise functions studied in~\cite{DAM:MeaOza24}.
+    \subsection{Comparison of the Nonlinearity}
+
+    In this part, we compare the nonlinearity of the revisited \hwbf{} with other weightwise quadratic functions considered for similar use-cases, such as the majority function, the \hwbf{} and the cyclic weightwise functions studied in~\cite{DAM:MeaOza24}.
 
@@
 We present values for $n$ up to $80$, which is sufficient for examining the asymptotic behavior of the different bounds.
-The pink and orange curves represent the upper bounds  in~\cite{DAM:MeaOza24}, with the orange curve mostly overlapping the pink one.
-To go into more detail, the pink curve corresponds to the bound that holds for all cyclic weightwise linear functions $f$ that, with the notation from Definition~\ref{def:wwdegd}, satisfy $ f_0(x) = b \cdot x $ for $\w(b)$ odd; therefore, this represents for instance an upper bound for the \hwbf{}.
-The orange curve corresponds to the bound for the cyclic weightwise quadratic function $f$ defined by $f_0(x) = x_1 + x_2 x_3$.
-The blue curve applies to both the majority and \hwbf{} functions, whose exact nonlinearities are given in Property~\ref{prop:wwd1}.
-We use a single curve here because, on a logarithmic scale, the nonlinearity difference between these two functions is too small to distinguish between them.
-For the revisited \hwbf{} introduced in Definition~\ref{def:revHWBF}, the red curve corresponds to the theoretical bound from Corollary~\ref{cor:bound_walsh_cauchy}, while the green curve represents the experimental results from Section~\ref{sec:expwt}.
+The bound on the cyclic weightwise linear functions stems from~\cite{DAM:MeaOza24}.
+With the notation from Definition~\ref{def:wwdegd}, these functions $f$ satisfy $f_0(x)=b\cdot x$ for $\w(b)$ odd; therefore, this represents, for instance, an upper bound for the \hwbf{}.
+The bound also applies to the cyclic weightwise quadratic function $f$ defined by $f_0(x) = x_1 + x_2 x_3$.
+Next, the bound for the majority function and the \hwbf{} comes from Property~\ref{property:wwd1}; we use a single curve here because the nonlinearity difference between these two functions is too small to be distinguished on a logarithmic scale.
+The theoretical and experimental bounds for the revisited \hwbf{} come from Corollary~\ref{cor:bound_walsh_cauchy} and Section~\ref{sec:expwt}, respectively.
 
@@
     	\centering
-	\includegraphics[width=8.5cm]{comparison_walsh_bound.pdf}
-	\mycaption{
-		Bounds on $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$ for various functions $f\in\BN$ and even values of $n$, shown on a logarithmic scale.
-The pink and orange curves, the orange one mostly covering the pink one, represent bounds for cyclic weightwise linear functions and a cyclic weightwise quadratic function from~\cite{DAM:MeaOza24}, respectively.
-The blue curve shows bounds for the majority function and the \hwbf{}.
-The theoretical bound for the revisited \hwbf{} (Corollary~\ref{cor:bound_walsh_cauchy}) is in red, the experimental bound $B_n$ (Section~\ref{sec:expwt}) is in green.}
+    	\includegraphics[width=8.5cm]{graphs/comparison_walsh_bound.pdf}
+    	\caption{%
+    		Bounds on $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$ for various functions $f\in\BN$ for even $n$, shown on a logarithmic scale.
+The bound for the cyclic weightwise linear functions stems from~\cite{DAM:MeaOza24}.
+The bound for the majority function and the \hwbf{} comes from Property~\ref{property:wwd1}.
+The theoretical bound for the revisited \hwbf{} is from Corollary~\ref{cor:bound_walsh_cauchy}, and the experimental bound is from Section~\ref{sec:expwt}.}
     	\label{fig:walsh_bound_comparison}
@@
 Its theoretical bound on $\max_{a \in \mathbb{F}_2^n} |\wt f(a)|$ reveals an asymptotic slope of $3/4$ on a logarithmic scale, contrasting with the slope of $1$ for the majority function, the \hwbf{}, and the bounds proven in~\cite{DAM:MeaOza24}.
-Notably, the green curve corresponding to the bound of Section~\ref{sec:expwt} appears to share this asymptotic slope of $3/4$, supporting the effectiveness of Corollary~\ref{cor:bound_walsh_cauchy} and the stronger Theorem~\ref{theorem:bound_D_nka_generalized} in capturing asymptotic behavior.
+Notably, the two curves for the revisited \hwbf{} appear to share this asymptotic slope of $3/4$, supporting the effectiveness of Corollary~\ref{cor:bound_walsh_cauchy} and the stronger Theorem~\ref{theorem:bound_D_nka_generalized} in capturing asymptotic behavior.
 
@@
     	\centering
-	\begin{tabular}{|c| c|c|c|c| c|c|c|}
-		\hline
-		$n$ & $4$  & $6$  & $8$  &  $10$ & $12$ & $14$ & $16$  \\
-		\hline	
-		\hwbf{}   & $4$  & $20$  & $88$  &  $372$ & $1\,544$ & $6\,344$ & $25\,904$  \\  	
-		Majority   & $5$  & $22$  & $93$  &  $386$ & $1\,586$ & $6\,476$ & $26\,333$  \\
-		$t$~\cite{DAM:MeaOza24}   & $4$  & $22$  & $96$  &  $404$ & $1\,672$ & $6\,854$ & $27\,884$\\
-		$u$~\cite{DAM:MeaOza24}   & $4$  & $24$  & $104$  &  $456$ & $1\,888$ & $7\,816$ & $31\,616$ \\
-		Revisited \hwbf{}  & $4$  & $22$  & $102$  &  $458$ & $1\,902$ & $7\,842$ & $31\,680$\\
+        \caption{Comparison of the nonlinearity.}
+    	\label{table:comparisonsNL}
+    	\begin{tabular}{|c|c|c|c|c|c|c|c|}
+    		\hline
+            $n$&$4$&$6$&$8$&$10$&$12$&$14$&$16$\\
+            \hline	
+            \hwbf{}&$4$&$20$&$88$&$372$&$1\,544$&$6\,344$&$25\,904$\\  	
+            Majority&$5$&$22$&$93$&$386$&$1\,586$&$6\,476$&$26\,333$\\
+            $t$~\cite{DAM:MeaOza24}&$4$&$22$&$96$&$404$&$1\,672$&$6\,854$&$27\,884$\\
+            $u$~\cite{DAM:MeaOza24}&$4$&$24$&$104$&$456$&$1\,888$&$7\,816$&$31\,616$\\
+            Revisited \hwbf{}&$4$&$22$&$102$&$458$&$1\,902$&$7\,842$&$31\,680$\\
     		\hline
     	\end{tabular}
-	\mycaption{Comparison of the nonlinearity.}
-	\label{table:comparisonsNL}
     \end{table}
 
-\section{Other parameters}\label{sec:otherParameters}
+    \section{Other Parameters}\label{sec:otherParameters}
 
@@
     	We write $f=q+h$, where $q\in\BN$ is given by $q(x)=\sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$ and $h\in\BN$ is the \hwbf{}.
-The function $h$ has degree $n-1\geq 3$ by Property~\ref{prop:wwd1}, and the function $q$ has no monomial of degree higher than $2$, so $\degg(f)=\degg(h)=n-1$.
-\end{proof}
-
-In Table~\ref{table:comparisonsDegAI}, we also display the algebraic degree of different weightwise quadratic functions.
+The function $h$ has degree $n-1\geq 3$ by Property~\ref{property:wwd1}, and the function $q$ has no monomial of degree higher than $2$, so $\degg(f)=\degg(h)=n-1$.
+    \end{proof}
+
+    In Table~\ref{table:comparisonsDegAI}, we display the algebraic degree of different weightwise quadratic functions.
 We observe that the revisited \hwbf{} has the highest degree along with the original \hwbf{} when $n$ is not a power of $2$.
-However, when $n$ is a power of $2$, the majority function has a degree that is one higher than that of the other two functions, as explained by Property~\ref{prop:wwd1} and Proposition~\ref{prop:deg_rhwbf}.
+However, when $n$ is a power of $2$, the majority function has a degree that is one higher than that of the other two functions, as explained by Property~\ref{property:wwd1} and Proposition~\ref{prop:deg_rhwbf}.
 
@@
     	\centering
+        \caption{Comparison of the degree and algebraic immunity.}
+    	\label{table:comparisonsDegAI}
     	\begin{tabular}{|c|c|c|c|c|c|c|c|}
     		\hline
-		$n$ & $4$  & $6$  & $8$  &  $10$ & $12$ & $14$ & $16$  \\
-		\hline
-		\hwbf{}   & $3, 2$  & $5, 3$  & $7, 4$  &  $9, 4$ & $11, 5$ & $13, 5$ & $15, 6$  \\  	
-		Majority   & $4, 2$  & $4, 3$  & $8, 4$  &  $8, 5$ & $8, 6$ & $8, 7$ & $16, 8$  \\
-		$t$~\cite{DAM:MeaOza24}   & $2, 2$  & $5, 3$  & $6, 4$  &  $9, 5$ & $11, 5$ & $13, 6$ & $14, 7$\\
-		$u$~\cite{DAM:MeaOza24}   & $2, 2$  & $4, 3$  & $6, 4$  &  $8, 5$ & $10, 6$ & $12, 6$ & $14, 7$ \\
-		Revisited \hwbf{}  & $3, 2$  & $5, 3$  & $7, 4$  &  $9, 5$ & $11, 6$ & $13, 6$ & $15, 7$\\
+            $n$&$4$&$6$&$8$&$10$&$12$&$14$&$16$\\
+            \hline
+            \hwbf{}&$3,2$&$5,3$&$7,4$&$9,4$&$11,5$&$13,5$&$15,6$\\  	
+            Majority&$4,2$&$4,3$&$8,4$&$8,5$&$8,6$&$8,7$&$16,8$\\
+            $t$~\cite{DAM:MeaOza24}&$2,2$&$5,3$&$6,4$&$9,5$&$11,5$&$13,6$&$14,7$\\
+            $u$~\cite{DAM:MeaOza24}&$2,2$&$4,3$&$6,4$&$8,5$&$10,6$&$12,6$&$14,7$\\
+            Revisited \hwbf{}&$3,2$&$5,3$&$7,4$&$9,5$&$11,6$&$13,6$&$15,7$\\
     		\hline
     	\end{tabular}
-	\mycaption{Comparison of the degree and algebraic immunity.}
-	\label{table:comparisonsDegAI}
     \end{table}
@@
     	\begin{align*}
-		g\cdot(q+1) \cdot(h+\varepsilon)&= g\cdot(q+1)\cdot(f+q+\varepsilon)\\
+    		g\cdot(q+1)\cdot(h+\varepsilon)&= g\cdot(q+1)\cdot(f+q+\varepsilon)\\
     		&=g\cdot(q+1)\cdot(f+\epsilon)+g\cdot(q+1)\cdot q\\
@@
 Furthermore, its high nonlinearity makes it a well-suited candidate for use as a filter function in contexts such as filtered \textsf{LFSR}s or in homomorphically-friendly schemes like \textsf{FLIP} and \textsf{FiLIP}.
-For example, the best current \textsf{FiLIP} filters in \textsf{HHE}~\cite{CCS:CDPP22,CIC:MeaParPei24,eprint:AGHM24} are \textsf{XOR}-threshold functions—the sum of a $k$-variable linear function and an $m$-variable threshold function (generalizing majority).
+For example, the best current \textsf{FiLIP} filters in \textsf{HHE}~\cite{eprint:AGHM24,CCS:CDPP22,CIC:MeaParPei24} are \textsf{XOR}-threshold functions—the sum of a $k$-variable linear function and an $m$-variable threshold function (generalizing majority).
     By Proposition $7$ in~\cite{IEEE:CarMea21}, their nonlinearity is at most:
     \[
-2^{k+m-1} - 2^k \cdot M, \quad \text{where } M = \begin{cases}
+    2^{k+m-1} - 2^k\cdot M, \quad \text{where } M = \begin{cases}
     \binom{m-1}{\frac{m-1}{2}} & \text{if } m \text{ is odd}, \\
@@
     	\centering
+        \caption{Lowest possible values of $(d, e)$ for different values of $n$.}
+    	\label{table:FAI}
     	\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
             \hline
-		$ n $      & $4$     & $6$     & $8$     & $10$    & $12$    & $14$    & $16$    & $18$    \\
-		\hline
-		$(d, e)$ & $(1,2)$ & $(1,3)$ & $(1,5)$  & $(1,7)$ & $(1,9)$ & $(1,11)$ & $(1,13)$ & $(1,15)$ \\ 
-		&     &    & $(2,4)$  & $(2,6)$ & $(2,8)$ & $(2,10)$ & $(2,12)$ & $(2,14)$\\ 
-		&     &    &     & $(3,5)$ & $(3,6)$ & $(3,9)$ & $(3,11)$ & $(3,13)$\\ 
-		&     &    &     &  &  &  & $(4,9)$ & $(4,11)$\\ 
-	 	&     &    &     &  &  &  &  & $(5,10)$ \\
+            $n$&$4$&$6$&$8$&$10$&$12$&$14$&$16$&$18$\\
+            \hline
+            $(d,e)$&$(1,2)$&$(1,3)$&$(1,5)$&$(1,7)$&$(1,9)$&$(1,11)$&$(1,13)$&$(1,15)$\\
+            &&&$(2,4)$&$(2,6)$&$(2,8)$&$(2,10)$&$(2,12)$&$(2,14)$\\
+            &&&&$(3,5)$&$(3,6)$&$(3,9)$&$(3,11)$&$(3,13)$\\
+            &&&&&&&$(4,9)$&$(4,11)$\\
+            &&&&&&&&$(5,10)$\\
             \hline
     	\end{tabular}
-	\mycaption{Lowest possible values of $(d, e)$ for different values of $n$.}
-	\label{table:FAI}
     \end{table}
 
-\section{Conclusion and open questions}
+    \section{Conclusion and Open Questions}
 
@@
 
-\ifnum\anon=0
-	\section{Acknowledgments}
+    \begin{credits}
+        \subsubsection{\ackname}
+
         Pierrick Méaux was funded by the European Research Council (\textsf{ERC}) under the Advanced Grant program (reference number: 787390).
@@
 We would also like to thank Claude Carlet for discussing the function introduced in this work with Deng Tang some years ago.
-\fi
-
-\newpage
+    \end{credits}
 
     \bibliographystyle{splncs04}
-\bibliography{add}
+    {\small\bibliography{biblio}}
 
@@
     	\begin{align*}
-		\Dtkna{t}{k}{n}{a}&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}\\
-		&=\sum_{(y,z)\in\Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
-		&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
-		&=\sum_{\ell=0}^{2t}\left(\sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{2t}(y)+b \cdot y}\right)\left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c \cdot z}\right)\\&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b}\cdot\kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
+    		\Dtkna{t}{k}{n}{a}&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a\cdot x}\\
+    		&=\sum_{(y,z)\in\Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b\cdot y +c\cdot z}\\
+    		&=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b\cdot y +c\cdot z}\\
+    		&=\sum_{\ell=0}^{2t}\left(\sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{2t}(y)+b\cdot y}\right)\left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c\cdot z}\right)\\&=\sum_{\ell=0}^{2t} \Dkna{2t}{\ell}{b}\cdot\kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
     	\end{align*}
@@
         \begin{align*}
-        \sum_{k\in\Z}\Dtkna{t}{k}{n}{a}z^k&=\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\sum_{k\in\Z}\kraw{k-\ell}{\w(c)}{n-2t}z^{k-\ell}\\
-        &=\left(\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\right)\cdot(1+z)^u\cdot(1-z)^v\\
+            \sum_{k\in\Z}\Dtkna{t}{k}{n}{a}z^k&=\sum_{\ell=0}^{2t}\Dkna{2t}{\ell}{b}z^\ell\sum_{k\in\Z}\kraw{k-\ell}{\w(c)}{n-2t}z^{k-\ell}\\
+            &=\left(\sum_{\ell=0}^{2t}\Dkna{2t}{\ell}{b}z^\ell\right)\cdot(1+z)^u\cdot(1-z)^v\\
             &=P_b(z)\cdot(1+z)^u\cdot(1-z)^v\\
@@
     	\end{align*}
-    The goal will be to prove that the maximum of $g(\alpha)=g^{(\lambda)}(\alpha)=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{t,a}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$.
+        The goal will be to prove that the maximum of the function $g(\alpha)=g^{(\lambda)}(\alpha)=(6-2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$ for $\alpha\in[-\pi,\pi]$ is equal to $2^{2\mu}$; the maximum of $|P_{t,a}(z)|$ on $\dis$ will then be $\left(2^{2\mu}\right)^{n/2}=2^{\mu n}$.
 Note that $g$ is an even function, so it is enough to focus on the interval $\alpha\in[0,\pi]$; the function $g$ is represented for several values of $0\leq\lambda<1/2$ in Figure~\ref{fig:family_curves_g}.
@@
         	\centering
-    	\includegraphics[width=10cm]{family_curves_g.pdf}
+        	\includegraphics[width=10cm]{graphs/family_curves_g.pdf}
             \vspace{-4mm}
-    	\mycaption{The curves of $\alpha\mapsto g^{(\lambda)}(\alpha)$ for the values $\lambda=\frac{i}{50}$ from $i=0$ (red) to $i=24$ (blue).}
+        	\caption{The curves of $\alpha\mapsto g^{(\lambda)}(\alpha)$ for the values $\lambda=\frac{i}{50}$ from $i=0$ (the curve with the highest value at $\alpha=0$) to $i=24$ (the curve with the lowest value at $\alpha=0$).}
         	\label{fig:family_curves_g}

### 2025-08-27 paper.tex
Minors

@@
 \newcommand{\hd}{\mathsf{d_H}}
-\newcommand{\hwbf}{\ensuremath{\mathsf{HWBF}}}
+\newcommand{\hwbf}{\textsf{HWBF}}
 \newcommand{\ie}{\textit{i.e.}}
@@
 \let\geq=\geqslant
+
+\bibliographystyle{splncs04}
 
@@
     		&\qquad+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2}\binom{n/2-1}{(k-1)/2}\right)\\
-    		&=0+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right).
-    	\end{align*}
-    	Therefore, we get $\wt{f}(0_n)=2\left(\sum_{i=\lceil n/4\rceil}^{n/2-1} \binom {n/2-1}{i} - \sum_{i=0}^{\lfloor(n-2)/4\rfloor} \binom{n/2-1}{i}\right)$.
-The final result follows by applying that $\binom{n}{k}=\binom{n}{n-k}$ for all integers $n\geq 0$ and $k$.
+    		&=0+2\left(\sum_{k=n/2+1}^{n}\binom{n/2-1}{(k-1)/2}-\sum_{k=0}^{n/2} \binom{n/2-1}{(k-1)/2}\right)\\
+            &=2\left(\sum_{i=\lceil n/4\rceil}^{n/2-1} \binom {n/2-1}{i} - \sum_{i=0}^{\lfloor(n-2)/4\rfloor} \binom{n/2-1}{i}\right).
+    	\end{align*}
+    	The result follows by applying that $\binom{n}{k}=\binom{n}{n-k}$ for all integers $n\geq 0$ and $k$.
     \end{proof}
@@
 
-    \bibliographystyle{splncs04}
-    {\small\bibliography{biblio}}
-
     \appendix
@@
         \end{gather*}
-        Since simultaneously replacing $(p,q)$ by $(q,p)$ and $(u,v)$ by $(v,u)$ has the same effect as replacing $z$ by $-z$ in $P_{t,a}(z)$ and therefore does not change the maximum of $|P_{t,a}(z)|$ on $\dis$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
+        Since simultaneously replacing $(p,q)$ by $(q,p)$ and $(u,v)$ by $(v,u)$ has the same effect as replacing $z$ by $-z$ in $P_{t,a}(z)$ and therefore does not change the maximum of $|P_{t,a}(z)|$ on $\dis$, we can restrict ourselves to the following tuples for $(p,q,r;u,v)$:
         \[
@@
         Writing $z=\ee^{\ii\alpha}$ and $z^2=\ee^{2\ii\alpha}$ for $\alpha\in[-\pi,\pi]$, and using that $|w|^2=w\overline w$ for every complex number $w$, we get:
-        \begin{align*}
-            |-z^2+2z+1|^2&=\left(-\ee^{2\ii\alpha}+2\ee^{\ii\alpha}+1\right)\left(-\ee^{-2\ii\alpha}+2\ee^{-\ii\alpha}+1\right)\\
-            &=6-\ee^{2\ii\alpha}-\ee^{-2\ii\alpha}\\
-            &=6-2\cos (2\alpha),
-        \end{align*}
-        where the last equality uses that $\ee^{2\ii\alpha}=\cos(2\alpha)+\ii\sin(2\alpha)$. We similarly obtain that $|1+z|^2=2+2\cos\alpha$. Combining both, we get:
+        \[
+            |-z^2+2z+1|^2=\left(-\ee^{2\ii\alpha}+2\ee^{\ii\alpha}+1\right)\left(-\ee^{-2\ii\alpha}+2\ee^{-\ii\alpha}+1\right).
+        \]
+        Expanding yields $|-z^2+2z+1|^2=6-\ee^{2\ii\alpha}-\ee^{-2\ii\alpha}=6-2\cos(2\alpha)$ because $\ee^{2\ii\alpha}=\cos(2\alpha)+\ii\sin(2\alpha)$.
+We similarly obtain that $|1+z|^2=2+2\cos\alpha$.
+Combining both, we get:
     	\begin{align*}
@@
         	\includegraphics[width=10cm]{graphs/family_curves_g.pdf}
-            \vspace{-4mm}
         	\caption{The curves of $\alpha\mapsto g^{(\lambda)}(\alpha)$ for the values $\lambda=\frac{i}{50}$ from $i=0$ (the curve with the highest value at $\alpha=0$) to $i=24$ (the curve with the lowest value at $\alpha=0$).}
@@
     \end{proof}
+
+    \bibliography{biblio}
 \end{document}

### 2025-08-29 paper.tex
Minor
Minors

@@
 \newcommand{\Ekn}[2]{\mathsf{E}_{#1,#2}}
+\newcommand{\etal}{\textsl{et al.}}
 \newcommand{\F}{\mathbb{F}}
@@
 }
-\authorrunning{P. Méaux et al.}
+\authorrunning{P. Méaux \etal}
 
@@
 
-    	\keywords{Boolean functions, HWBF, Nonlinearity.}
+    	\keywords{Boolean functions \and HWBF \and Nonlinearity.}
     \end{abstract}
@@
 For example, the best current \textsf{FiLIP} filters in \textsf{HHE}~\cite{eprint:AGHM24,CCS:CDPP22,CIC:MeaParPei24} are \textsf{XOR}-threshold functions—the sum of a $k$-variable linear function and an $m$-variable threshold function (generalizing majority).
-    By Proposition $7$ in~\cite{IEEE:CarMea21}, their nonlinearity is at most:
-    \[
-    2^{k+m-1} - 2^k\cdot M, \quad \text{where } M = \begin{cases}
-    \binom{m-1}{\frac{m-1}{2}} & \text{if } m \text{ is odd}, \\
-    \frac{1}{2} \binom{m}{\frac{m}{2}} & \text{if } m \text{ is even}.
-    \end{cases}
-    \]
+By Proposition $7$ in~\cite{IEEE:CarMea21}, their nonlinearity is at most $2^{k+m-1}-2^k\cdot M$, where $M=\binom{m-1}{\frac{m-1}{2}}$ if $M$ is odd, and $M=(1/2)\cdot\binom{m}{\frac{m}{2}}$ if $M$ is even.
 This is similar to the majority function, whereas the revisited \hwbf{} achieves higher nonlinearity for the same size, offering better resistance to correlation-like attacks with fewer variables.
@@
 
-    Our approach utilizes generating functions and Cauchy’s estimate to establish lower bounds on the nonlinearity of weightwise quadratic functions.
-This naturally raises the question: can the employed techniques, particularly the use of Cauchy’s estimate, be extended to other families of Boolean functions?
+    Our approach utilizes generating functions and Cauchy's estimate to establish lower bounds on the nonlinearity of weightwise quadratic functions.
+This naturally raises the question: can the employed techniques, particularly the use of Cauchy's estimate, be extended to other families of Boolean functions?
 Specifically, this approach appears feasible for other weightwise-degree-$d$ functions $f$ where the $f_k$ are direct sums.
@@
 We would also like to thank Claude Carlet for discussing the function introduced in this work with Deng Tang some years ago.
+
+        \subsubsection{\discintname}
+        The authors have no competing interests to declare
+        that are relevant to the content of this article.
     \end{credits}

### 2025-08-29 paper.tex
M

@@
 \usepackage{graphicx}
+\usepackage{hyperref}
 \usepackage{microtype}
@@
 \newcommand{\kraw}[3]{\mathsf{K}_{#1}(#2,#3)}
-\newcommand{\myurl}[1]{\footnote{\texttt{\url{#1}}}}
 \newcommand{\NL}{\mathsf{NL}}
@@
 For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$, respectively, in the expression $\Dkna n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dkna n2a=0$.
-This checking can be automatized by a computer algebra system, for which we provide a \textsf{SageMath} implementation.\myurl{https://github.com/se-tim/Revisited-HWBF.git}
+This checking can be automatized by a computer algebra system, for which we provide a \textsf{SageMath} implementation.\footnote{\url{https://github.com/se-tim/Revisited-HWBF.git}}
     \end{proof}
@@
 Its polynomial complexity makes it possible to extend the analysis well beyond the limitations imposed by a full computation of the Walsh spectrum, which requires a complexity of $\mathcal O(n2^n)$.
-We provide a \textsf{SageMath} implementation to obtain the bound $B_n$.\myurl{https://github.com/se-tim/Revisited-HWBF.git}
+We provide a \textsf{SageMath} implementation to obtain the bound $B_n$.\footnote{\url{https://github.com/se-tim/Revisited-HWBF.git}}
 
@@
         \subsubsection{\discintname}
-        The authors have no competing interests to declare
-        that are relevant to the content of this article.
+
+        The authors have no competing interests to declare that are relevant to the content of this article.
     \end{credits}

### 2025-11-28 paper.tex
M

@@
 \usepackage{hyperref}
+\usepackage{marvosym}
 \usepackage{microtype}
+\usepackage{orcidlink}
 
@@
 \author{%
-    Pierrick Méaux\inst{1}\orcidID{0000-0001-5733-4341} \and
-    Tim Seuré\inst{1}\orcidID{0000-0003-4200-7553} \and %Corresponding author
-    Deng Tang\inst{2}\orcidID{0000-0002-8373-9200}
+    Pierrick Méaux\inst{1}\orcidlink{0000-0001-5733-4341} \and
+    Tim Seuré\textsuperscript{(\Letter)}\inst{1}\orcidlink{0000-0003-4200-7553} \and
+    Deng Tang\inst{2}\orcidlink{0000-0002-8373-9200}
 }
@@
 \institute{%
-    University of Luxembourg, Luxembourg\\
+    University of Luxembourg, Esch-sur-Alzette, Luxembourg\\
     \email{pierrick.meaux@uni.lu, tim.seure@uni.lu} 
